### 2010-09-14 notes/proposal.tex
Add proposal.

\documentclass[11pt]{article}

\input{format.tex}

\title{M.Sc Proposal}
\author{Roman Zeyde}
\begin{document}
\maketitle
\section{Introduction}
Electrophoresis is the motion of dispersed particle relative to a ion-containing fluid,
due to the influence of an electric field. This phenomenon combines electrostatics 
coupled with fluid dynamics, as well as diffusion/advection of ions in the fluid.

The particle (surrounded by fluid) acquire surface charge which is screened by 
a thin layer of ions in the fluid, creating a double-layer structure near the 
particle's surface, called ``Debye layer''.

If the layer width is much smaller than the particle's size
an analytical solution in the Debye-layer can be found \cite{Yariv10}, 
and be used as the appropriate boundary condition for the 
macroscale problem on the particle's surface.

Electrophoresis is described by the following physical phenomena,
using the macroscale equations:
\begin{enumerate}
\item Electrostatic potential - the fluid contains no free charge:
\begin{equation}
    \bnabla \cdot (C \bnabla \varPhi) = 0.
\end{equation}
\item Fluid dynamics - Stokes incompressible flow with electrostatic force component:
\begin{equation}
\left\{ \begin{array}{l}
\bLaplacian \bV - \bnabla P + \Laplacian \varPhi \bnabla \varPhi = 0 \\
\bnabla \cdot \bV = 0 \end{array} \right.
\end{equation}
\item Ions' diffusion and advection - through the fluid's velocity field:
\begin{equation}
\Laplacian C - \alpha \bV \cdot \bnabla C = 0
\end{equation}
\end{enumerate}

The boundary conditions correspond to the specific problem at hand, and
are coupled as well as the partial differential equations themselves.

The closed form approximate solution was developed for spherical particle
and small electric field \cite{Yariv10} but since the equations are coupled
and non-linear, it is hard to extend the analytic solution to more general
settings.

\section{Research goals}
Our goal is to implement an accurate and fast iterative numerical 
solver for the problem described above,
in order to enable the research of cases which has no closed form solution 
(e.g. non-spherical/asymmetric particles, large electric fields).

The solver will be verified against known closed-form solutions 
for each of the sub-problems, as well as the full coupled problem, 
analyzing the discrepancies between the theoretical and numerical results.

Moreover, the convergence rate of the solver will be optimized using 
numerical acceleration methods (e.g. MPE, RRE and Multigrid) to achieve
high accuracy in reasonable solver's execution time.

Achieved results will provide a numeric model for interesting small-scale physical phenomena,
such as an ``self-electrophoretic swimmer'' by numerically modeling an asymmetric particle's configuration.

\section{Achieved results}
The numerical solver is being implemented in MATLAB and verified against
known solution for specific problem settings.

Laplace
Diffusion-advection (upwind)
Stokes
Jacobi, RedBlack, Vanka
Coupling
Spherical
Stress-free

\section{Algorithms and techniques}

The solver applies iterative relaxation to solve the system, by
iterating the equations and solving repeatedly each one of them
for the corresponding variable
(Laplace equation for $\varPhi$, Stokes equation for $(\bV, P)$
and diffusion-advection equation for $C$), where
all other variables keep their values from previous iteration
(somewhat resembling Gauss-Seidel method for linear systems).

Problem's configuration is taken from \cite{Yariv10} and
consists of a spherical particle, surrounded by infinite Stokes fluid.
Suppose that the particle is stationary and fluid flows around it, slipping across
the boundary layer (due to ``Debye layer'' effects) with a velocity field denoted
by $\bV$.

In this setting, together with the usage of spherical coordinates $(R,\theta,\phi)$,
makes the problem axisymmetric around the velocity vector of the fluid (independent
of $\phi$). Thus the problem may be written as two-dimensional partial
differential equation system in $R$ and $\theta$ variables,
such that $R \in [1,\infty)$ and $\theta \in [0, \pi]$.
A natural choice of a grid is logarithmic grid for $R$ and uniform grid for $\theta$.

Thus, each differential operator is written in spherical coordinates on the regular
$(r, \theta)$ grid and being linear -- is represented as a sparse matrix,
making the algebraic computations on the equations much more straightforward.

The boundary conditions are computed for $\theta = 0$ and $\theta = \pi$ using symmetry
considerations. At $R = \infty$, we assume constant fluid velocity
and $\bV = \cal{U} \bzhat$, constant electric field $\bnabla \varPhi = \beta \bzhat$
and constant ionic concentration $C = 1$.
The boundary conditions on $R = 1$ are defined by the boundary layer behavior as described
in \cite{Yariv10}.

ghost points
precond

\begin{thebibliography}{}

\bibitem{Yariv10} E. Yariv, 
``Migration of ion-exchange particles driven by a uniform electric field'',
{\em Journal of Fluid Mechanics, 655 105-121}, 2010.

\end{thebibliography}

\end{document}

### 2010-09-15 notes/proposal.tex
Work on proposal

@@
 \section{Achieved results}
-The numerical solver is being implemented in MATLAB and verified against
-known solution for specific problem settings.
-
-Laplace
-Diffusion-advection (upwind)
-Stokes
-Jacobi, RedBlack, Vanka
-Coupling
-Spherical
-Stress-free
-
-\section{Algorithms and techniques}
+The numerical solver is being implemented as a MATLAB package that
+provides the needed tools for numerical solution of an electrophoresis problem.
 
@@
 all other variables keep their values from previous iteration
-(somewhat resembling Gauss-Seidel method for linear systems).
+(a ``Gauss-Seidel'' method for non-linear systems).
 
@@
 
+The following linear operators are implemented in spherical coordinates using regular grid:
+\begin{itemize}
+  \item Scalar Laplacian (for $\varPhi$ and $C$)
+  \item Vector Laplacian (for $\bV$)
+  \item Gradient (for $\Phi, C$ and $P$)
+  \item Divergence (for $\bV$)
+\end{itemize}
+
 Thus, each differential operator is written in spherical coordinates on the regular
@@
 
-ghost points
-precond
+After substitution of boundary conditions, each differential equation is transformed to a
+sparse linear system of the form $\matr{A}\bx = \vect{b}$.
+Due to coupling, it is not necessary to find the exact solution -- so we apply
+few relaxations on each linear system, using an appropriate preconditioner $\matr{M}$
+(which depends on $\matr{A}$):
+\begin{eqnarray}
+  \bx_{n+1} &=& \bx_{n} + \matr{M}_\matr{A}^{-1} \left(\vect{b} - \matr{A}\bx_{n}\right)
+\end{eqnarray}
+
+After the solver has converged to a solution, the stress tensor $\mathbb{T}$ on the particle
+$\cal{S} = \left\{\bx : \|\bx\| = 1\right\}$ is computed:
+\begin{eqnarray}
+  \vect{F} = \int_{\cal{S}} \left(\mathbb{T} \cdot \bnhat \right) ds = \vec{0}.
+\end{eqnarray}
+Since the problem is axisymmetric, the force should be aligned with the symmetry axis:
+$\vect{F} = F \bzhat$. Moreover, since the particle is stress-free in steady flow, we
+have $F = 0$ for steady state velocity $\cal{U}$.
+
+This observation enables us to find the correct $\cal{U}$ for given $\beta$, using one-dimensional root-finding algorithm on $F_\beta(\cal{U})$ function.
+
+\section{Algorithms and techniques}
+
+\subsection{Grid choice}
+$C$, $\varPhi$ and $P$ are using central grid whereas staggered grid is used for $\bV$.
+
+\subsection{Differential Equations}
+Finite volume method using finite differences.
+Upwind for advection.
+
+\subsection{Preconditioners}
+There are efficient sparse implementations of 
+Jacobi, Red-Black Gauss-Seidel and Vanka-type.
 

### 2010-09-19 notes/proposal.tex
Proposal

--- 2010-09-14 notes/proposal.tex
@@
-\documentclass[11pt]{article}
+\documentclass[12pt]{article}
 
-\input{format.tex}
+\usepackage{amsmath} 
+\usepackage{amssymb} 
+\usepackage{units}   
+\usepackage{float}   
+\usepackage{graphicx}
+\usepackage{amsfonts}
+\usepackage{mathrsfs}
+\usepackage[colorlinks]{hyperref}
+\usepackage{framed}
+
+\newcommand{\R}{\ensuremath{\mathbb{R}}}
+\newcommand{\cl}[1]{\ensuremath{\mathcal{#1}}}
+\newcommand{\vect}[1]{\ensuremath{\mathbf{#1}}}
+\newcommand{\matr}[1]{\ensuremath{\mathbf{#1}}}
+\newcommand{\mat}[2]{\left(\begin{array}{#1}#2\end{array}\right)}
+\newcommand{\brc}[2]{\left\{\begin{array}{#1}#2\end{array}\right.}
+
+\providecommand\Laplacian{\nabla^2}
+\providecommand\bnabla{\boldsymbol{\nabla}}
+\providecommand\bLaplacian{\boldsymbol{\nabla}^2}
+\providecommand\bV{\boldsymbol{V}}
+\providecommand\bx{\boldsymbol{x}}
+\providecommand\bz{\boldsymbol{z}}
+\providecommand\br{\boldsymbol{r}}
+\providecommand\bzhat{\hat{\boldsymbol{z}}}
+\providecommand\bnhat{\hat{\boldsymbol{n}}}
+\providecommand\btheta{\boldsymbol{\theta}}
+\providecommand\bphi{\boldsymbol{\phi}}
+\providecommand\bzero{\boldsymbol{0}}
+
+\setlength{\textheight}{8.7in}
+\setlength{\columnsep}{2.0pc}
+\setlength{\textwidth}{6.6in}
+\setlength{\topmargin}{0.05in}
+\setlength{\headheight}{0.2in}
+\setlength{\headsep}{0.1in}
+\setlength{\evensidemargin}{0in}
+\setlength{\oddsidemargin}{0in}
+\setlength{\parindent}{0.0 in}
+\setlength{\parskip}{0.1 in}
 
@@
 \section{Introduction}
-Electrophoresis is the motion of dispersed particle relative to a ion-containing fluid,
-due to the influence of an electric field. This phenomenon combines electrostatics 
-coupled with fluid dynamics, as well as diffusion/advection of ions in the fluid.
+Electrokinetics describes dynamics of particles in ion-containing fluids.
+When a particle acquires surface charge, a thin layer of ions in the fluid of opposite charge is attracted to the surface via electric forces, creating a double-layer structure (see Figure \ref{fig:EDL}).
+This structure, called ``Debye layer'', electrically screens the surface charge, thus creating a potential difference between the particle and the outer layer of
+the fluid bulk, called ``zeta potential''.
 
-The particle (surrounded by fluid) acquire surface charge which is screened by 
-a thin layer of ions in the fluid, creating a double-layer structure near the 
-particle's surface, called ``Debye layer''.
+\begin{figure}[htbp]
+\begin{framed}
+    \begin{center}
+        \includegraphics[width=0.25\textwidth]
+            {ElectricDoubleLayer.eps}
+        \caption{Electrical Double Layer is composed of (1) particle's surface, (2) Debye layer and (3) fluid bulk.
+        Zeta potential is defined as the voltage between (1) and (3).}
+        \label{fig:EDL}
+    \end{center}
+\end{framed}
+\end{figure}
 
-If the layer width is much smaller than the particle's size
-an analytical solution in the Debye-layer can be found \cite{Yariv10}, 
-and be used as the appropriate boundary condition for the 
-macroscale problem on the particle's surface.
+In case the layer width is much smaller than the particle's size an analytical solution in the Debye-layer can be found \cite{Yariv10a}, and be used as the appropriate boundary condition for the macroscale bulk problem on the particle's surface.
 
-Electrophoresis is described by the following physical phenomena,
-using the macroscale equations:
+Electrokinetics is described by the following physical phenomena (in dimensionless formulation):
 \begin{enumerate}
-\item Electrostatic potential - the fluid contains no free charge:
-\begin{equation}
+\item Electrostatic potential - the fluid bulk contains no free charge:
+\begin{equation} \label{eq:Laplace}
     \bnabla \cdot (C \bnabla \varPhi) = 0.
@@
 \item Fluid dynamics - Stokes incompressible flow with electrostatic force component:
-\begin{equation}
+\begin{equation} \label{eq:Stokes}
 \left\{ \begin{array}{l}
@@
 \end{equation}
-\item Ions' diffusion and advection - through the fluid's velocity field:
-\begin{equation}
+\item Ions' diffusion and advection (via fluid's velocity field):
+\begin{equation} \label{eq:Nernst}
 \Laplacian C - \alpha \bV \cdot \bnabla C = 0
@@
 
-The boundary conditions correspond to the specific problem at hand, and
-are coupled as well as the partial differential equations themselves.
+The boundary conditions correspond to the specific problem at hand and are usually coupled as well as the partial differential equations themselves.
 
-The closed form approximate solution was developed for spherical particle
-and small electric field \cite{Yariv10} but since the equations are coupled
+The closed form approximate solution has been developed for spherical particle
+and small electric field \cite{Yariv10b} but since the equations are coupled
 and non-linear, it is hard to extend the analytic solution to more general
@@
 \section{Research goals}
-Our goal is to implement an accurate and fast iterative numerical 
-solver for the problem described above,
-in order to enable the research of cases which has no closed form solution 
-(e.g. non-spherical/asymmetric particles, large electric fields).
+Our goal is to implement an accurate and fast iterative numerical solver for electrokinetic problems, in cases there are no closed-form solutions known (e.g.
+asymmetric particles or large electric fields).
 
-The solver will be verified against known closed-form solutions 
-for each of the sub-problems, as well as the full coupled problem, 
-analyzing the discrepancies between the theoretical and numerical results.
+The solver will be verified against known closed-form solutions for each of the sub-problems, as well as the full coupled problem, analyzing the discrepancies between the theoretical and numerical results.
 
-Moreover, the convergence rate of the solver will be optimized using 
-numerical acceleration methods (e.g. MPE, RRE and Multigrid) to achieve
-high accuracy in reasonable solver's execution time.
+Moreover, the convergence rate of the solver will be optimized using numerical acceleration methods to achieve high accuracy in reasonable solver's execution time.
 
-Achieved results will provide a numeric model for interesting small-scale physical phenomena,
-such as an ``self-electrophoretic swimmer'' by numerically modeling an asymmetric particle's configuration.
+Achieved results will provide a numeric model for interesting small-scale physical phenomena, such as electrophoretic\footnote{Electrophoresis is
+the physical phenomenon of particles motion in an ion-containing fluid under the influence of an electric field.} autonomous micro-swimmers \cite{Paxton04, Howse07} by numerically modeling an appropriate particle's configuration.
 
 \section{Achieved results}
-The numerical solver is being implemented in MATLAB and verified against
-known solution for specific problem settings.
+The numerical solver is being implemented as a MATLAB package that
+provides the needed tools for numerical solution of an electrophoresis problem.
 
-Laplace
-Diffusion-advection (upwind)
-Stokes
-Jacobi, RedBlack, Vanka
-Coupling
-Spherical
-Stress-free
+The solver applies iterative relaxations to solve the coupled system, by
+iterating the equations and relaxing repeatedly each one of them
+for the corresponding variable:
+\begin{itemize}
+  \item Laplace equation \ref{eq:Laplace} is used to update $\varPhi$.
+  \item Stokes equation \ref{eq:Stokes} is used to update $\bV$ and $P$.
+  \item Nernst-Planck equation \ref{eq:Nernst} is used to update for $C$.
+\end{itemize}
+While solving specific equation for a specific variable, all other variables keep their values from previous iteration, resembling ``Gauss-Seidel'' method for non-linear systems.
+
+Problem's configuration is taken from \cite{Yariv10b} and consists of a spherical particle, surrounded by infinite Stokes fluid.
+Suppose that the particle is stationary and fluid flows around it, slipping across the boundary layer (due to ``Debye layer'' effects) with a velocity field denoted by $\bV$.
+
+Spherical coordinates $(R,\theta,\phi)$ system is chosen to make the problem axisymmetric around the velocity vector of the fluid, therefore independent of $\phi$.
+The electrokinetic problem is written as two-dimensional partial differential equation system for $R \in [1,\infty)$ and $\theta \in [0, \pi]$.
+Natural grid choices are a logarithmic grid for $R$ and an uniform grid for $\theta$.
+
+The following linear operators are implemented in spherical coordinates on the grid described above: Scalar Laplacian (for $\varPhi$ and $C$), Vector Laplacian (for $\bV$), Gradient (for $\Phi, C$ and $P$) and Divergence (for $\bV$).
+
+Each differential operator is written in spherical coordinates on the regular $(R, \theta)$ grid and being linear -- is represented as a sparse matrix, making the algebraic manipulations much more straightforward.
+
+The boundary conditions are computed for $\theta = 0$ and $\theta = \pi$ using symmetry considerations.
+At $R = \infty$, we assume constant fluid velocity and $\bV = \cal{U} \bzhat$, constant electric field $\bnabla \varPhi = -\beta \bzhat$ and constant ionic concentration $C = 1$.
+The boundary conditions on $R = 1$ are defined by the boundary layer behavior as described in \cite{Yariv10b}, using Dukhin-–Derjaguin slip formula for $\bV$ and ion-selectivity condition for $\varPhi$ and $C$.
+
+After substitution of boundary conditions, each differential equation is transformed to a sparse linear system of the form $\matr{A}\bx = \vect{b}$.
+Due to coupling, it is not necessary to find the exact solution -- so we apply few relaxations on each linear system, using an appropriate preconditioner $\matr{M}_\matr{A}^{-1}$:
+\begin{eqnarray} \label{eq:Precond}
+  \bx_{n+1} &=& \bx_{n} + \matr{M}_\matr{A}^{-1} \left(\vect{b} - \matr{A}\bx_{n}\right)
+\end{eqnarray}
+
+After the solver has converged to a solution for the coupled system, the stress tensor $\mathbb{T}$ on the particle $\cl{S} = \left\{\bx : \|\bx\| = 1\right\}$ is computed  (combining Newtonian and Maxwell stresses) and integrated to yield the total force:
+\begin{eqnarray}
+  \mathbb{T} &=& - P \mathbb{I} + \bnabla \bV + (\bnabla \bV) ^T  + \bnabla \varPhi \bnabla \varPhi - \frac{\bnabla \varPhi \cdot \bnabla \varPhi}{2} \mathbb{I}, \\
+  \vect{F} &=& \int_{\cal{S}} \left(\mathbb{T} \cdot \bnhat \right) ds = \boldsymbol{0}.
+\end{eqnarray}
+Since the problem is axisymmetric, the force should be aligned with the symmetry axis: $\vect{F} = F \bzhat$.
+Moreover, since the particle is stress-free in steady flow, we have $F = 0$ for steady-state velocity $\cal{U}$.
+
+This observation enables us to find the correct $\cal{U}$ for given $\beta$, using one-dimensional root-finding algorithm on $F_\beta(\cal{U})$, as a function of $\cal{U}$.
 
@@
 
-The solver applies iterative relaxation to solve the system, by
-iterating the equations and solving repeatedly each one of them
-for the corresponding variable
-(Laplace equation for $\varPhi$, Stokes equation for $(\bV, P)$
-and diffusion-advection equation for $C$), where
-all other variables keep their values from previous iteration
-(somewhat resembling Gauss-Seidel method for linear systems).
+$C$, $\varPhi$ and $P$ are discretized using a central grid whereas staggered grid is used for $\bV$ at the problem domain $\cl{D}$ (see Figure \ref{fig:Grids}).
+\begin{figure}[htbp]
+\begin{framed}
+    \begin{center}
+        \includegraphics[width=1\textwidth]
+            {StaggeredGrid.eps}
+        \caption{Grids for $C$, $\varPhi$, $P$ and $\bV$.}
+        \label{fig:Grids}
+    \end{center}
+\end{framed}
+\end{figure}
 
-Problem's configuration is taken from \cite{Yariv10} and
-consists of a spherical particle, surrounded by infinite Stokes fluid.
-Suppose that the particle is stationary and fluid flows around it, slipping across
-the boundary layer (due to ``Debye layer'' effects) with a velocity field denoted
-by $\bV$.
+Finite volume method is used to represent the partial differential equations in the form of algebraic system, using
+central differences or upwind scheme (for better stability).
 
-In this setting, together with the usage of spherical coordinates $(R,\theta,\phi)$,
-makes the problem axisymmetric around the velocity vector of the fluid (independent
-of $\phi$). Thus the problem may be written as two-dimensional partial
-differential equation system in $R$ and $\theta$ variables,
-such that $R \in [1,\infty)$ and $\theta \in [0, \pi]$.
-A natural choice of a grid is logarithmic grid for $R$ and uniform grid for $\theta$.
+``Ghost points'' are used to define Dirichlet and Neumann boundary conditions on
+problem domain's boundary $\partial \cl{D}$.
 
-Thus, each differential operator is written in spherical coordinates on the regular
-$(r, \theta)$ grid and being linear -- is represented as a sparse matrix,
-making the algebraic computations on the equations much more straightforward.
+After boundary counditions are eliminated, Jacobi and Red-Black Gauss-Seidel preconditioners are used for equations \ref{eq:Laplace} and \ref{eq:Nernst}, where Vanka-type \cite{Vanka86} preconditioner is used for equation \ref{eq:Stokes}.
+The preconditioners are computed as sparse matrices, making the relaxations (at equation \ref{eq:Precond}) much more straightforward.
 
-The boundary conditions are computed for $\theta = 0$ and $\theta = \pi$ using symmetry
-considerations. At $R = \infty$, we assume constant fluid velocity
-and $\bV = \cal{U} \bzhat$, constant electric field $\bnabla \varPhi = \beta \bzhat$
-and constant ionic concentration $C = 1$.
-The boundary conditions on $R = 1$ are defined by the boundary layer behavior as described
-in \cite{Yariv10}.
-
-ghost points
-precond
+Vector extrapolation methods \cite{Sidi90} have been implemented and are used to accelerate solver's convergence.
+Multigrid solver \cite{Brandt77, Yavneh06} implementation will be a part of the research.
 
 \begin{thebibliography}{}
-
-\bibitem{Yariv10} E. Yariv, 
+\bibitem{Yariv10a} E. Yariv,
+``An asymptotic derivation of the thin-debye-layer limit for electrokinetic phenomena'',
+{\em Chem. Engng Comm. 197, 3–17}, 2010.
+\bibitem{Yariv10b} E. Yariv,
 ``Migration of ion-exchange particles driven by a uniform electric field'',
 {\em Journal of Fluid Mechanics, 655 105-121}, 2010.
-
+\bibitem{Rubin01} I. Rubinstein and B. Zaltzman,
+``Electro-osmotic slip of the second kind and instability in concentration polarization at electrodialysis membranes'',
+{\em Math. Mod. Meth. Appl. Sci. 11 (2), 263–300}, 2001.
+\bibitem{Paxton04}
+W. Paxton et. al.,
+``Catalytic Nanomotors: Autonomous Movement of Striped Nanorods'',
+{\em Journal of the American Chemical Society 126 (41), 13424-13431}, 2004.
+\bibitem{Howse07}
+J. R. Howse et. al.,
+``Self-Motile Colloidal Particles: From Directed Propulsion to Random Walk'',
+{\em Phys. Rev. Lett., 99, 048102}, 2007.
+\bibitem{Vanka86}
+S. P. Vanka,
+``Block-implicit multigrid solution of Navier-Stokes equations in primitive variables'',
+{\em J. Copmput. Phys., 65, 138-158}, 1986.
+\bibitem{Sidi90}
+A. Sidi, ``Efficient implementation of minimal polynomial and reduced rank extrapolation methods'',
+{\em Journal of Computational and Applied Mathematics, Vol. 36, pp. 305-337}, 1991.
+\bibitem{Brandt77} Achi Brandt,
+``Multi-Level Adaptive Solutions to Boundary-Value Problems'',
+{\em Mathematics of Computation, 31: 333–90}, 1977.
+\bibitem{Yavneh06} Irad Yavneh.
+``Why Multigrid Methods are so Efficient'',
+{\em Computing in Science and Engineering, 8(6):12-22}, 2006
 \end{thebibliography}

### 2010-09-22 notes/proposal.tex
Proposal

@@
 
-\title{M.Sc Proposal}
+\title{M.Sc. Proposal}
 \author{Roman Zeyde}
@@
 \section{Introduction}
-Electrokinetics describes dynamics of particles in ion-containing fluids.
-When a particle acquires surface charge, a thin layer of ions in the fluid of opposite charge is attracted to the surface via electric forces, creating a double-layer structure (see Figure \ref{fig:EDL}).
-This structure, called ``Debye layer'', electrically screens the surface charge, thus creating a potential difference between the particle and the outer layer of
-the fluid bulk, called ``zeta potential''.
+Electrokinetic theory describes the dynamics of charged particles in ionic fluids.
+When a particle acquires surface charge, a layer of ions of opposite charge is attracted to the surface via electric forces, creating a double-layer structure around the particle (see Figure \ref{fig:EDL}).
+This structure, called ``Debye layer'', electrically screens the surface charge, thus creating a potential difference between the particle and the outer layer of the fluid bulk.
 
@@
             {ElectricDoubleLayer.eps}
-        \caption{Electrical Double Layer is composed of (1) particle's surface, (2) Debye layer and (3) fluid bulk.
-        Zeta potential is defined as the voltage between (1) and (3).}
+        \caption{Schematic structure of the double layer:
+        (1) particle's surface, (2) Debye layer and (3) fluid bulk.
+        If the the particle's surface has positive (blue) surface charge, it attracts negative (red) ions from the fluid making the Debye layer be negatively charged (as opposed to the rest of the fluid bulk, which is electrically neutral).
+        Zeta potential is defined as the voltage drop on (2).}
         \label{fig:EDL}
@@
 
-In case the layer width is much smaller than the particle's size an analytical solution in the Debye-layer can be found \cite{Yariv10a}, and be used as the appropriate boundary condition for the macroscale bulk problem on the particle's surface.
+In cases where the layer width is much smaller than the particle's size, an analytical solution for the Debye layer dynamics can be found \cite{Yariv10a}.
 
@@
 \end{equation}
-\item Fluid dynamics - Stokes incompressible flow with electrostatic force component:
+\item Fluid dynamics - Stokes incompressible flow with an electrostatic force component:
 \begin{equation} \label{eq:Stokes}
@@
 \end{equation}
-\item Ions' diffusion and advection (via fluid's velocity field):
+\item Ion diffusion and advection (via the fluid's velocity field):
 \begin{equation} \label{eq:Nernst}
@@
 \end{enumerate}
+The boundary conditions correspond to the specific problem at hand and defined by particle's geometry, chemical characteristics and fluid's dynamics.
 
-The boundary conditions correspond to the specific problem at hand and are usually coupled as well as the partial differential equations themselves.
-
-The closed form approximate solution has been developed for spherical particle
-and small electric field \cite{Yariv10b} but since the equations are coupled
-and non-linear, it is hard to extend the analytic solution to more general
-settings.
+The partial differential equations above are coupled and non-linear.
+In general, they have no analytic solution.
+Moreover, any numerical solver must handle the scale disparity, caused by the Debye layer width being much smaller than the particle's size.
+A closed-form approximate solution has been developed for spherical ion-exchanging particles and small electric field \cite{Yariv10b} but it is hard to extend the analytic solution to more general systems.
 
 \section{Research goals}
-Our goal is to implement an accurate and fast iterative numerical solver for electrokinetic problems, in cases there are no closed-form solutions known (e.g.
+Our goal is to implement an accurate and fast iterative numerical solver for electrokinetic problems, which could be successfully applied for systems that have no closed-form solutions known (e.g.
 asymmetric particles or large electric fields).
@@
 
-Moreover, the convergence rate of the solver will be optimized using numerical acceleration methods to achieve high accuracy in reasonable solver's execution time.
+Moreover, the convergence rate of the solver will be optimized using numerical acceleration methods in order to achieve high accuracy in reasonable execution time.
 
-Achieved results will provide a numeric model for interesting small-scale physical phenomena, such as electrophoretic\footnote{Electrophoresis is
-the physical phenomenon of particles motion in an ion-containing fluid under the influence of an electric field.} autonomous micro-swimmers \cite{Paxton04, Howse07} by numerically modeling an appropriate particle's configuration.
+The solver will provide a numerical model for interesting electrokinetical phenomena which have no closed-form analytic solutions yet, such as large field dynamics and electrophoretic\footnote{Electrophoresis is the physical phenomenon of particles motion in an ion-containing fluid under the influence of an electric field.} autonomous micro-swimmers \cite{Paxton04, Howse07}.
 
 \section{Achieved results}
-The numerical solver is being implemented as a MATLAB package that
-provides the needed tools for numerical solution of an electrophoresis problem.
+The numerical solver is being implemented as a MATLAB package, which provides the needed tools for numerical solution of an electrophoresis problem.
 
 The solver applies iterative relaxations to solve the coupled system, by
-iterating the equations and relaxing repeatedly each one of them
+iterating the equations and relaxing each one of them
 for the corresponding variable:
@@
 \end{itemize}
-While solving specific equation for a specific variable, all other variables keep their values from previous iteration, resembling ``Gauss-Seidel'' method for non-linear systems.
+While solving a specific equation for a specific variable, all other variables maintain their values from previous iteration, resembling ``Gauss-Seidel'' method for linear systems.
 
-Problem's configuration is taken from \cite{Yariv10b} and consists of a spherical particle, surrounded by infinite Stokes fluid.
-Suppose that the particle is stationary and fluid flows around it, slipping across the boundary layer (due to ``Debye layer'' effects) with a velocity field denoted by $\bV$.
-
-Spherical coordinates $(R,\theta,\phi)$ system is chosen to make the problem axisymmetric around the velocity vector of the fluid, therefore independent of $\phi$.
+The problem's configuration is taken from \cite{Yariv10b} and consists of a spherical ion-exchanging particle, surrounded by infinite Stokes fluid.
+Spherical coordinates $(R,\theta,\phi)$ system is chosen to make the problem axisymmetric, therefore independent of $\phi$.
 The electrokinetic problem is written as two-dimensional partial differential equation system for $R \in [1,\infty)$ and $\theta \in [0, \pi]$.
@@
 The following linear operators are implemented in spherical coordinates on the grid described above: Scalar Laplacian (for $\varPhi$ and $C$), Vector Laplacian (for $\bV$), Gradient (for $\Phi, C$ and $P$) and Divergence (for $\bV$).
+Each differential operator is written in spherical coordinates on the regular $(R, \theta)$ grid and being linear, is represented as a sparse matrix -- simplifying the algebraic manipulations.
 
-Each differential operator is written in spherical coordinates on the regular $(R, \theta)$ grid and being linear -- is represented as a sparse matrix, making the algebraic manipulations much more straightforward.
+The boundary conditions are defined for $\theta = 0$ and $\theta = \pi$ using symmetry considerations.
+At $R = \infty$, we assume constant fluid velocity $\bV = \cl{U} \bzhat$, constant electric field $\bnabla \varPhi = -\beta \bzhat$ and constant ionic concentration $C = 1$.
+The boundary conditions on $R = 1$ are defined by the Debye layer's behavior as described in \cite{Yariv10b}, using the Dukhin-–Derjaguin slip formula for $\bV$ and ion-selectivity for $\varPhi$ and $C$.
 
-The boundary conditions are computed for $\theta = 0$ and $\theta = \pi$ using symmetry considerations.
-At $R = \infty$, we assume constant fluid velocity and $\bV = \cal{U} \bzhat$, constant electric field $\bnabla \varPhi = -\beta \bzhat$ and constant ionic concentration $C = 1$.
-The boundary conditions on $R = 1$ are defined by the boundary layer behavior as described in \cite{Yariv10b}, using Dukhin-–Derjaguin slip formula for $\bV$ and ion-selectivity condition for $\varPhi$ and $C$.
-
-After substitution of boundary conditions, each differential equation is transformed to a sparse linear system of the form $\matr{A}\bx = \vect{b}$.
-Due to coupling, it is not necessary to find the exact solution -- so we apply few relaxations on each linear system, using an appropriate preconditioner $\matr{M}_\matr{A}^{-1}$:
-\begin{eqnarray} \label{eq:Precond}
+After substitution of boundary conditions, each differential equation is transformed into a sparse linear system of the form $\matr{A}\bx = \vect{b}$.
+Due to coupling, it is not necessary to find the exact solution -- so we apply few relaxations (\ref{eq:Relax}) on each linear system, using an appropriate preconditioner $\matr{M}_\matr{A}^{-1}$:
+\begin{eqnarray} \label{eq:Relax}
   \bx_{n+1} &=& \bx_{n} + \matr{M}_\matr{A}^{-1} \left(\vect{b} - \matr{A}\bx_{n}\right)
@@
 
-After the solver has converged to a solution for the coupled system, the stress tensor $\mathbb{T}$ on the particle $\cl{S} = \left\{\bx : \|\bx\| = 1\right\}$ is computed  (combining Newtonian and Maxwell stresses) and integrated to yield the total force:
+After the solver has converged to a solution for the coupled system, the total stress tensor $\mathbb{T}$ on the particle $\cl{S} = \left\{\bx : \|\bx\| = 1\right\}$ is computed (\ref{eq:Stress}) and integrated to yield the total force (\ref{eq:Force}):
 \begin{eqnarray}
+  \label{eq:Stress}
   \mathbb{T} &=& - P \mathbb{I} + \bnabla \bV + (\bnabla \bV) ^T  + \bnabla \varPhi \bnabla \varPhi - \frac{\bnabla \varPhi \cdot \bnabla \varPhi}{2} \mathbb{I}, \\
-  \vect{F} &=& \int_{\cal{S}} \left(\mathbb{T} \cdot \bnhat \right) ds = \boldsymbol{0}.
+  \label{eq:Force}
+  \vect{F} &=& \int_{\cl{S}} \left(\mathbb{T} \cdot \bnhat \right) ds = \boldsymbol{0}.
 \end{eqnarray}
 Since the problem is axisymmetric, the force should be aligned with the symmetry axis: $\vect{F} = F \bzhat$.
-Moreover, since the particle is stress-free in steady flow, we have $F = 0$ for steady-state velocity $\cal{U}$.
+Moreover, since the particle is stress-free in steady flow, we have $F = 0$ for steady-state velocity $\cl{U}$.
 
-This observation enables us to find the correct $\cal{U}$ for given $\beta$, using one-dimensional root-finding algorithm on $F_\beta(\cal{U})$, as a function of $\cal{U}$.
+This observation enables us to find the correct $\cl{U}$ for given $\beta$, using one-dimensional root-finding algorithm on $F_\beta(\cl{U})$, as a function of $\cl{U}$.
+
+The numerical solution for $\cl{U}$ as a function of $\beta$ is compared to the closed-form solution from \cite{Yariv10b}.
+Using a $60 \times 15$ grid for $(R,\theta) \in [1, 100] \times [0, \pi]$, we apply $2\mathord{,}000$ iterations in order to find the total force acting on the particle.
+This step is repeated a few times to find the correct $\cl{U}$ so that $F_\beta(\cl{U}) = 0$ for various $\beta$ values -- see Figure \ref{fig:Results} for numerical results.
+\begin{figure}[htbp]
+\begin{framed}
+    \begin{center}
+        \includegraphics[width=0.45\textwidth]
+            {convergence.eps}
+        \includegraphics[width=0.45\textwidth]
+            {comparison.eps}
+        \caption{Left: Residual $\ell_2$ norm graph. Right: Particle Velocity $\cl{U}$ as a the function of electric field $\beta$.
+        The error between the theoretical and the solver's results is less than 2\%.}
+        \label{fig:Results}
+    \end{center}
+\end{framed}
+\end{figure}
 
@@
 
-$C$, $\varPhi$ and $P$ are discretized using a central grid whereas staggered grid is used for $\bV$ at the problem domain $\cl{D}$ (see Figure \ref{fig:Grids}).
+$C$, $\varPhi$ and $P$ are discretized using a central grid whereas a staggered grid is used for $\bV$ at the problem domain $\cl{D}$ (see Figure \ref{fig:Grids}).
 \begin{figure}[htbp]
@@
 
-Finite volume method is used to represent the partial differential equations in the form of algebraic system, using
-central differences or upwind scheme (for better stability).
+Finite volume method is used to represent the partial differential equations in the form of an algebraic system, using central differences or an upwind scheme (for better stability).
 
 ``Ghost points'' are used to define Dirichlet and Neumann boundary conditions on
-problem domain's boundary $\partial \cl{D}$.
+the problem domain's boundary $\partial \cl{D}$.
 
-After boundary counditions are eliminated, Jacobi and Red-Black Gauss-Seidel preconditioners are used for equations \ref{eq:Laplace} and \ref{eq:Nernst}, where Vanka-type \cite{Vanka86} preconditioner is used for equation \ref{eq:Stokes}.
-The preconditioners are computed as sparse matrices, making the relaxations (at equation \ref{eq:Precond}) much more straightforward.
+After boundary counditions are eliminated, Jacobi and Red-Black Gauss-Seidel preconditioners are used for equations \ref{eq:Laplace} and \ref{eq:Nernst}, where a Vanka-type \cite{Vanka86} preconditioner is used for equation \ref{eq:Stokes}.
+The preconditioners are computed as sparse matrices, making the relaxations (at equation \ref{eq:Relax}) much more straightforward.
 
-Vector extrapolation methods \cite{Sidi90} have been implemented and are used to accelerate solver's convergence.
-Multigrid solver \cite{Brandt77, Yavneh06} implementation will be a part of the research.
+Vector extrapolation methods \cite{Sidi90} have been implemented and are used to accelerate the solver's convergence.
+Multigrid solver \cite{Brandt77, Yavneh06} implementation will also be a part of the research.
 

### 2010-09-26 notes/proposal.tex
Irad Review

@@
 \title{M.Sc. Proposal}
-\author{Roman Zeyde}
+\author{Roman Zeyde \\ \\  {\small Advisor: Prof. Irad Yavneh} }
 \begin{document}
@@
 \section{Introduction}
-Electrokinetic theory describes the dynamics of charged particles in ionic fluids.
-When a particle acquires surface charge, a layer of ions of opposite charge is attracted to the surface via electric forces, creating a double-layer structure around the particle (see Figure \ref{fig:EDL}).
-This structure, called ``Debye layer'', electrically screens the surface charge, thus creating a potential difference between the particle and the outer layer of the fluid bulk.
+Electrokinetic theory describes the dynamics of charged particles
+in ionic fluids. When a particle acquires surface charge, a layer
+of ions of opposite charge is attracted to the surface via
+electric forces, creating a double-layer structure around the
+particle (see Figure \ref{fig:EDL}). This structure, called
+``Debye layer'', electrically screens the surface charge, thus
+creating a potential difference between the particle and the outer
+layer of the fluid bulk.
 
@@
         \caption{Schematic structure of the double layer:
-        (1) particle's surface, (2) Debye layer and (3) fluid bulk.
-        If the the particle's surface has positive (blue) surface charge, it attracts negative (red) ions from the fluid making the Debye layer be negatively charged (as opposed to the rest of the fluid bulk, which is electrically neutral).
+        (1) particle surface, (2) Debye layer and (3) fluid bulk.
+        If the particle surface has positive (blue) surface charge,
+        it attracts negative (red) ions from the fluid making the
+        Debye layer negatively charged (as opposed to the rest of
+        the fluid bulk, which is electrically neutral).
         Zeta potential is defined as the voltage drop on (2).}
@@
 \end{figure}
-
-In cases where the layer width is much smaller than the particle's size, an analytical solution for the Debye layer dynamics can be found \cite{Yariv10a}.
+In cases where the layer width is much smaller than the particle's
+size, an analytical asymptotic solution for the Debye layer
+dynamics can be found \cite{Yariv10a}.
 
@@
 \begin{enumerate}
-\item Electrostatic potential - the fluid bulk contains no free charge:
+\item Electrostatic potential---the fluid bulk contains no free
+charge:
 \begin{equation} \label{eq:Laplace}
-    \bnabla \cdot (C \bnabla \varPhi) = 0.
+    \bnabla \cdot (C \bnabla \varPhi) = 0 \, .
 \end{equation}
-\item Fluid dynamics - Stokes incompressible flow with an electrostatic force component:
+\item Fluid dynamics---Stokes flow with an electrostatic force
+component:
 \begin{equation} \label{eq:Stokes}
 \left\{ \begin{array}{l}
-\bLaplacian \bV - \bnabla P + \Laplacian \varPhi \bnabla \varPhi = 0 \\
-\bnabla \cdot \bV = 0 \end{array} \right.
+\bLaplacian \bV - \bnabla P + \Laplacian \varPhi \bnabla \varPhi = 0 \, , \\
+\bnabla \cdot \bV = 0 \, . \end{array} \right.
 \end{equation}
@@
 \begin{equation} \label{eq:Nernst}
-\Laplacian C - \alpha \bV \cdot \bnabla C = 0
+\Laplacian C - \alpha \bV \cdot \bnabla C = 0 \, .
 \end{equation}
 \end{enumerate}
-The boundary conditions correspond to the specific problem at hand and defined by particle's geometry, chemical characteristics and fluid's dynamics.
+{\bf IY: WRITE EXPLICITLY HERE WHAT THE VARIABLES ARE---C,P,V,
+ETC.}The boundary conditions are determined by the specific
+problem under consideration and defined by the particle's
+geometry, chemical characteristics, and the fluid dynamics.
 
-The partial differential equations above are coupled and non-linear.
-In general, they have no analytic solution.
-Moreover, any numerical solver must handle the scale disparity, caused by the Debye layer width being much smaller than the particle's size.
-A closed-form approximate solution has been developed for spherical ion-exchanging particles and small electric field \cite{Yariv10b} but it is hard to extend the analytic solution to more general systems.
+The partial differential equations above are coupled and
+non-linear. In general, they have no analytic solution. Moreover,
+any numerical solver must handle the scale disparity caused by the
+Debye layer width being much smaller than the particle's size. A
+closed-form linear asymptotic solution has been developed for
+spherical ion-exchanging particles and weak electric field in an
+axisymmetric setting \cite{Yariv10b} but it is hard to extend this
+analytic solution to more general systems. Once the electric field
+becomes stronger, significant nonlinear phenomena are expected.
+This interesting regime has not yet been explored.
+
+{\bf IY: ADD HERE A PARAGRAPH THAT DISCUSSES THE IMPORTANCE AND
+RELEVANCE OF THE PROBLEM---YOU CAN TAKE THIS FROM THE PAPERS YOU
+HAVE READ.}
 
 \section{Research goals}
-Our goal is to implement an accurate and fast iterative numerical solver for electrokinetic problems, which could be successfully applied for systems that have no closed-form solutions known (e.g.
-asymmetric particles or large electric fields).
+Our goal is to implement an accurate and fast iterative numerical
+solver for electrokinetic problems, and then apply it to the study
+of systems that have no closed-form solutions, including strong
+electric fields, non-spherical particles, and asymmetric charge on
+the particle surface. We expect to thus gain insight into the
+chemical and physical behavior in far more general regimes than
+are currently well-understood. We hope that this will also lead to
+further analytical developments, based on new scaling behavior
+provided by the numerical solver. We may also target interesting
+phenomena that have been observed experimentally, e.g.,
+electrophoretic\footnote{Electrophoresis is the physical
+phenomenon of the motion of particles in an ion-containing fluid
+under the influence of an electric field.} autonomous
+micro-swimmers \cite{Paxton04, Howse07}.
 
-The solver will be verified against known closed-form solutions for each of the sub-problems, as well as the full coupled problem, analyzing the discrepancies between the theoretical and numerical results.
+The solver will be verified against known closed-form solutions
+for each of the sub-problems listed above, as well as the full
+coupled problem, analyzing the discrepancies between the
+theoretical (asymptotic) and numerical results. Moreover, the
+convergence rate of the solver will be optimized using numerical
+acceleration methods in order to achieve high accuracy in
+reasonable execution time.
 
-Moreover, the convergence rate of the solver will be optimized using numerical acceleration methods in order to achieve high accuracy in reasonable execution time.
+\section{Preliminary results}
+The numerical solver is being implemented as a MATLAB package,
+which provides the needed tools for numerical solution of
+electrokinetic problems. The solver applies an iterative
+relaxation technique to solve the discretized coupled system.
+Beginning with some initial guess for the solution The equations
+are relaxed in order with respect to their corresponding
+variables, with the remaining variables fixed at their current
+values (``Gauss-Seidel style''):
+\begin{itemize}
+  \item The diffusion equation (\ref{eq:Laplace}) is used to update $\varPhi$.
+  \item The Stokes system (\ref{eq:Stokes}) is used to update $\bV$ and $P$.
+  \item The Nernst-Planck equation (\ref{eq:Nernst}) is used to update $C$.
+\end{itemize}
 
-The solver will provide a numerical model for interesting electrokinetical phenomena which have no closed-form analytic solutions yet, such as large field dynamics and electrophoretic\footnote{Electrophoresis is the physical phenomenon of particles motion in an ion-containing fluid under the influence of an electric field.} autonomous micro-swimmers \cite{Paxton04, Howse07}.
+The problem configuration is taken from \cite{Yariv10b} and
+consists of a spherical ion-exchanging particle, surrounded by
+infinite Stokes fluid. Spherical coordinates $(R,\theta,\phi)$ are
+employed. The problem is axisymmetric, hence independent of
+$\phi$, which simplifies the solution process. The electrokinetic
+problem is thus written as a two-dimensional partial differential
+equation system for $R \in [1,\infty)$ and $\theta \in [0, \pi]$.
+Natural grid choices are a logarithmic grid for $R$ and a uniform
+grid for $\theta$.
 
-\section{Achieved results}
-The numerical solver is being implemented as a MATLAB package, which provides the needed tools for numerical solution of an electrophoresis problem.
+The following linear operators are implemented in spherical
+coordinates on the grid described above: Scalar Laplacian (for
+$\varPhi$ and $C$), Vector Laplacian (for $\bV$), Gradient (for
+$\Phi, C$ and $P$) and Divergence (for $\bV$). Each differential
+operator is written in spherical coordinates on the regular $(R,
+\theta)$ grid and, being linear, is represented as a sparse
+matrix, which is very convenient for the required algebraic
+manipulations.
 
-The solver applies iterative relaxations to solve the coupled system, by
-iterating the equations and relaxing each one of them
-for the corresponding variable:
-\begin{itemize}
-  \item Laplace equation \ref{eq:Laplace} is used to update $\varPhi$.
-  \item Stokes equation \ref{eq:Stokes} is used to update $\bV$ and $P$.
-  \item Nernst-Planck equation \ref{eq:Nernst} is used to update for $C$.
-\end{itemize}
-While solving a specific equation for a specific variable, all other variables maintain their values from previous iteration, resembling ``Gauss-Seidel'' method for linear systems.
+The boundary conditions are defined for $\theta = 0$ and $\theta =
+\pi$ using symmetry considerations. At $R = \infty$, we assume
+constant fluid velocity $\bV = \cl{U} \bzhat$, constant electric
+field $\bnabla \varPhi = -\beta \bzhat$ and constant ionic
+concentration $C = 1$. The boundary conditions on $R = 1$ are
+defined by the Debye layer's behavior as described in
+\cite{Yariv10b}, using the Dukhin-–Derjaguin slip formula for
+$\bV$ and ion-selectivity for $\varPhi$ and $C$.
 
-The problem's configuration is taken from \cite{Yariv10b} and consists of a spherical ion-exchanging particle, surrounded by infinite Stokes fluid.
-Spherical coordinates $(R,\theta,\phi)$ system is chosen to make the problem axisymmetric, therefore independent of $\phi$.
-The electrokinetic problem is written as two-dimensional partial differential equation system for $R \in [1,\infty)$ and $\theta \in [0, \pi]$.
-Natural grid choices are a logarithmic grid for $R$ and an uniform grid for $\theta$.
-
-The following linear operators are implemented in spherical coordinates on the grid described above: Scalar Laplacian (for $\varPhi$ and $C$), Vector Laplacian (for $\bV$), Gradient (for $\Phi, C$ and $P$) and Divergence (for $\bV$).
-Each differential operator is written in spherical coordinates on the regular $(R, \theta)$ grid and being linear, is represented as a sparse matrix -- simplifying the algebraic manipulations.
-
-The boundary conditions are defined for $\theta = 0$ and $\theta = \pi$ using symmetry considerations.
-At $R = \infty$, we assume constant fluid velocity $\bV = \cl{U} \bzhat$, constant electric field $\bnabla \varPhi = -\beta \bzhat$ and constant ionic concentration $C = 1$.
-The boundary conditions on $R = 1$ are defined by the Debye layer's behavior as described in \cite{Yariv10b}, using the Dukhin-–Derjaguin slip formula for $\bV$ and ion-selectivity for $\varPhi$ and $C$.
-
-After substitution of boundary conditions, each differential equation is transformed into a sparse linear system of the form $\matr{A}\bx = \vect{b}$.
-Due to coupling, it is not necessary to find the exact solution -- so we apply few relaxations (\ref{eq:Relax}) on each linear system, using an appropriate preconditioner $\matr{M}_\matr{A}^{-1}$:
+Each differential equation and its boundary conditions are
+discretized, resulting in a sparse linear system of the form
+$\matr{A}\bx = \vect{b}$. We then cycle by applying a few
+relaxation iterations on each linear system in turn, as noted
+above, using an appropriate preconditioner
+$\matr{M}_\matr{A}^{-1}$:
 \begin{eqnarray} \label{eq:Relax}
@@
 
-After the solver has converged to a solution for the coupled system, the total stress tensor $\mathbb{T}$ on the particle $\cl{S} = \left\{\bx : \|\bx\| = 1\right\}$ is computed (\ref{eq:Stress}) and integrated to yield the total force (\ref{eq:Force}):
+After the iterations have converged to a solution for the coupled
+system, the total stress tensor $\mathbb{T}$ on the particle
+$\cl{S} = \left\{\bx : \|\bx\| = 1\right\}$ is computed
+(\ref{eq:Stress}) and integrated to yield the total force
+(\ref{eq:Force}):
 \begin{eqnarray}
   \label{eq:Stress}
-  \mathbb{T} &=& - P \mathbb{I} + \bnabla \bV + (\bnabla \bV) ^T  + \bnabla \varPhi \bnabla \varPhi - \frac{\bnabla \varPhi \cdot \bnabla \varPhi}{2} \mathbb{I}, \\
+  \mathbb{T} &=& - P \mathbb{I} + \bnabla \bV + (\bnabla \bV) ^T  +
+  \bnabla \varPhi \bnabla \varPhi - \frac{\bnabla \varPhi \cdot \bnabla \varPhi}{2} \mathbb{I}, \\
   \label{eq:Force}
@@
 \end{eqnarray}
-Since the problem is axisymmetric, the force should be aligned with the symmetry axis: $\vect{F} = F \bzhat$.
-Moreover, since the particle is stress-free in steady flow, we have $F = 0$ for steady-state velocity $\cl{U}$.
+Because the problem is axisymmetric, the force should be aligned
+with the symmetry axis: $\vect{F} = F \bzhat$. Moreover, since the
+particle is stress-free in steady flow, we have $F = 0$ for
+steady-state velocity $\cl{U}$. This observation enables us to
+find the correct $\cl{U}$ for given $\beta$, using a
+one-dimensional root-finding algorithm on $F_\beta(\cl{U})$, as a
+function of $\cl{U}$.
 
-This observation enables us to find the correct $\cl{U}$ for given $\beta$, using one-dimensional root-finding algorithm on $F_\beta(\cl{U})$, as a function of $\cl{U}$.
-
-The numerical solution for $\cl{U}$ as a function of $\beta$ is compared to the closed-form solution from \cite{Yariv10b}.
-Using a $60 \times 15$ grid for $(R,\theta) \in [1, 100] \times [0, \pi]$, we apply $2\mathord{,}000$ iterations in order to find the total force acting on the particle.
-This step is repeated a few times to find the correct $\cl{U}$ so that $F_\beta(\cl{U}) = 0$ for various $\beta$ values -- see Figure \ref{fig:Results} for numerical results.
+The numerical solution for $\cl{U}$ as a function of $\beta$ is
+compared to the closed-form asymptotic solution from
+\cite{Yariv10b}. Using a $60 \times 15$ grid for $(R,\theta) \in
+[1, 100] \times [0, \pi]$, we apply $2\mathord{,}000$ iterations
+in order to find the total force acting on the particle. This step
+is repeated a few times to find the correct $\cl{U}$ so that
+$F_\beta(\cl{U}) = 0$ for various $\beta$ values---see Figure
+\ref{fig:Results} for numerical results.
 \begin{figure}[htbp]
@@
             {comparison.eps}
-        \caption{Left: Residual $\ell_2$ norm graph. Right: Particle Velocity $\cl{U}$ as a the function of electric field $\beta$.
+        \caption{Left: Residual $\ell_2$ norm convergence graph. Right: Particle Velocity
+        $\cl{U}$ as a the function of electric field $\beta$.
         The error between the theoretical and the solver's results is less than 2\%.}
@@
 
-$C$, $\varPhi$ and $P$ are discretized using a central grid whereas a staggered grid is used for $\bV$ at the problem domain $\cl{D}$ (see Figure \ref{fig:Grids}).
+$C$, $\varPhi$ and $P$ are discretized at cell centers, whereas a
+staggered grid is used for $\bV$ at the problem domain $\cl{D}$
+(see Figure \ref{fig:Grids}).
 \begin{figure}[htbp]
@@
 \end{figure}
+A finite volume discretization is used to represent the partial
+differential equations in the form of an algebraic system, using
+central differences or an upwind scheme (for stability). ``Ghost
+points'' are used to define Dirichlet and Neumann boundary
+conditions on the domain boundary $\partial \cl{D}$.
 
-Finite volume method is used to represent the partial differential equations in the form of an algebraic system, using central differences or an upwind scheme (for better stability).
+After boundary conditions are eliminated, Jacobi and Red-Black
+Gauss-Seidel preconditioners are used for equations
+(\ref{eq:Laplace}) and (\ref{eq:Nernst}), while a so-called
+Vanka-type \cite{Vanka86} preconditioner is used for equation
+(\ref{eq:Stokes}). The preconditioners are computed as sparse
+matrices, facilitating the relaxation process (\ref{eq:Relax}).
 
-``Ghost points'' are used to define Dirichlet and Neumann boundary conditions on
-the problem domain's boundary $\partial \cl{D}$.
-
-After boundary counditions are eliminated, Jacobi and Red-Black Gauss-Seidel preconditioners are used for equations \ref{eq:Laplace} and \ref{eq:Nernst}, where a Vanka-type \cite{Vanka86} preconditioner is used for equation \ref{eq:Stokes}.
-The preconditioners are computed as sparse matrices, making the relaxations (at equation \ref{eq:Relax}) much more straightforward.
-
-Vector extrapolation methods \cite{Sidi90} have been implemented and are used to accelerate the solver's convergence.
-Multigrid solver \cite{Brandt77, Yavneh06} implementation will also be a part of the research.
+Vector extrapolation methods \cite{Sidi90} have been implemented
+and are used to accelerate the solver's convergence. Later, a
+Multigrid framework \cite{Brandt77, Yavneh06} will be introduced
+to allow the efficient solution of large problems.
 

### 2010-09-26 notes/proposal.tex
Review fixes.

@@
 layer of the fluid bulk.
-
 \begin{figure}[htbp]
@@
 \begin{enumerate}
-\item Electrostatic potential---the fluid bulk contains no free
+\item Electrostatics---the fluid bulk contains no free
 charge:
@@
 \end{enumerate}
-{\bf IY: WRITE EXPLICITLY HERE WHAT THE VARIABLES ARE---C,P,V,
-ETC.}The boundary conditions are determined by the specific
+The variables of the electrokinetic problem are the electrostatic 
+potential $\varPhi$, fluid's velocity $\bV$ and its pressure $P$ 
+and ionic concentration $C$.
+
+The boundary conditions are determined by the specific
 problem under consideration and defined by the particle's
@@
 
-{\bf IY: ADD HERE A PARAGRAPH THAT DISCUSSES THE IMPORTANCE AND
-RELEVANCE OF THE PROBLEM---YOU CAN TAKE THIS FROM THE PAPERS YOU
-HAVE READ.}
+Recently, it has been conceived that such type of dynamics 
+can be very useful in transporting and manipulating micro- 
+and nanoscale objects for many nanotechnology applications, 
+such as the self-assembly of superstructures, roving sensors, 
+drug-delivery systems and useful nanomachinery \cite{Pumera10}. 
+However, since the analytic model for these electrokinetic 
+phenomena has no closed-form analytic solution, a numerical
+solver has to be developed.
 
@@
 of systems that have no closed-form solutions, including strong
-electric fields, non-spherical particles, and asymmetric charge on
-the particle surface. We expect to thus gain insight into the
-chemical and physical behavior in far more general regimes than
-are currently well-understood. We hope that this will also lead to
-further analytical developments, based on new scaling behavior
+electric fields, non-spherical particles, and asymmetric charge 
+distribution on the particle surface. We expect to thus gain insight 
+into the chemical and physical behavior in far more general regimes 
+than are currently well-understood. We hope that this will also lead 
+to further analytical developments, based on new scaling behavior
 provided by the numerical solver. We may also target interesting
@@
 relaxation technique to solve the discretized coupled system.
-Beginning with some initial guess for the solution The equations
+Beginning with some initial guess for the solution, the equations
 are relaxed in order with respect to their corresponding
@@
 {\em Journal of Fluid Mechanics, 655 105-121}, 2010.
+\bibitem{Pumera10} M. Pumera,
+``Electrochemically powered self-propelled electrophoretic nanosubmarines''
+{\em Nanoscale, 2, 1643-1649}, 2010.
 \bibitem{Rubin01} I. Rubinstein and B. Zaltzman,

### 2010-09-26 notes/proposal.tex
Fix proposal.

@@
 find the correct $\cl{U}$ for given $\beta$, using a
-one-dimensional root-finding algorithm on $F_\beta(\cl{U})$, as a
-function of $\cl{U}$.
+one-dimensional root-finding algorithm (e.g. the secant method) 
+on $F_\beta(\cl{U})$, as a function of $\cl{U}$.
 

### 2010-09-27 notes/proposal.tex
Fix proposal.

--- 2010-09-26 notes/proposal.tex
@@
 
-\title{M.Sc. Proposal}
+\title{M.Sc. Proposal: \\ \bigskip
+Computational Electrokinetics}
 \author{Roman Zeyde \\ \\  {\small Advisor: Prof. Irad Yavneh} }
@@
 The variables of the electrokinetic problem are the electrostatic
-potential $\varPhi$, fluid's velocity $\bV$ and its pressure $P$ 
-and ionic concentration $C$.
+potential $\varPhi$, fluid velocity $\bV$ and its pressure $P$ and
+ionic concentration $C$.
 

### 2010-09-27 notes/proposal.tex
Bibliobraphy to BibTeX

@@
 size, an analytical asymptotic solution for the Debye layer
-dynamics can be found \cite{Yariv10a}.
+dynamics can be found \cite{yariv2010asymptotic}.
 
@@
 spherical ion-exchanging particles and weak electric field in an
-axisymmetric setting \cite{Yariv10b} but it is hard to extend this
+axisymmetric setting \cite{yariv2010migration} but it is hard to extend this
 analytic solution to more general systems. Once the electric field
@@
 such as the self-assembly of superstructures, roving sensors, 
-drug-delivery systems and useful nanomachinery \cite{Pumera10}.
+drug-delivery systems and useful nanomachinery 
+\cite{pumera2010electrochemically}.
 However, since the analytic model for these electrokinetic
@@
 under the influence of an electric field.} autonomous
-micro-swimmers \cite{Paxton04, Howse07}.
+micro-swimmers \cite{paxton2004catalytic, howse2007self}.
 
@@
 
-The problem configuration is taken from \cite{Yariv10b} and
+The problem configuration is taken from \cite{yariv2010migration} and
 consists of a spherical ion-exchanging particle, surrounded by
@@
 defined by the Debye layer's behavior as described in
-\cite{Yariv10b}, using the Dukhin-–Derjaguin slip formula for
+\cite{yariv2010migration}, using the Dukhin-–Derjaguin slip formula for
 $\bV$ and ion-selectivity for $\varPhi$ and $C$.
@@
 compared to the closed-form asymptotic solution from
-\cite{Yariv10b}. Using a $60 \times 15$ grid for $(R,\theta) \in
+\cite{yariv2010migration}. Using a $60 \times 15$ grid for $(R,\theta) \in
 [1, 100] \times [0, \pi]$, we apply $2\mathord{,}000$ iterations
@@
 (\ref{eq:Laplace}) and (\ref{eq:Nernst}), while a so-called
-Vanka-type \cite{Vanka86} preconditioner is used for equation
+Vanka-type \cite{vanka1986block} preconditioner is used for equation
 (\ref{eq:Stokes}). The preconditioners are computed as sparse
@@
 
-Vector extrapolation methods \cite{Sidi90} have been implemented
-and are used to accelerate the solver's convergence. Later, a
-Multigrid framework \cite{Brandt77, Yavneh06} will be introduced
-to allow the efficient solution of large problems.
+Vector extrapolation methods \cite{sidi1991efficient} have been 
+implemented and are used to accelerate the solver's convergence. 
+Later, a Multigrid framework \cite{brandt1977multi, yavneh2006multigrid} 
+will be introduced to allow the efficient solution of large problems.
 
-\begin{thebibliography}{}
-\bibitem{Yariv10a} E. Yariv,
-``An asymptotic derivation of the thin-debye-layer limit for electrokinetic phenomena'',
-{\em Chem. Engng Comm. 197, 3–17}, 2010.
-\bibitem{Yariv10b} E. Yariv,
-``Migration of ion-exchange particles driven by a uniform electric field'',
-{\em Journal of Fluid Mechanics, 655 105-121}, 2010.
-\bibitem{Pumera10} M. Pumera,
-``Electrochemically powered self-propelled electrophoretic nanosubmarines''
-{\em Nanoscale, 2, 1643-1649}, 2010.
-\bibitem{Rubin01} I. Rubinstein and B. Zaltzman,
-``Electro-osmotic slip of the second kind and instability in concentration polarization at electrodialysis membranes'',
-{\em Math. Mod. Meth. Appl. Sci. 11 (2), 263–300}, 2001.
-\bibitem{Paxton04}
-W. Paxton et. al.,
-``Catalytic Nanomotors: Autonomous Movement of Striped Nanorods'',
-{\em Journal of the American Chemical Society 126 (41), 13424-13431}, 2004.
-\bibitem{Howse07}
-J. R. Howse et. al.,
-``Self-Motile Colloidal Particles: From Directed Propulsion to Random Walk'',
-{\em Phys. Rev. Lett., 99, 048102}, 2007.
-\bibitem{Vanka86}
-S. P. Vanka,
-``Block-implicit multigrid solution of Navier-Stokes equations in primitive variables'',
-{\em J. Copmput. Phys., 65, 138-158}, 1986.
-\bibitem{Sidi90}
-A. Sidi, ``Efficient implementation of minimal polynomial and reduced rank extrapolation methods'',
-{\em Journal of Computational and Applied Mathematics, Vol. 36, pp. 305-337}, 1991.
-\bibitem{Brandt77} Achi Brandt,
-``Multi-Level Adaptive Solutions to Boundary-Value Problems'',
-{\em Mathematics of Computation, 31: 333–90}, 1977.
-\bibitem{Yavneh06} Irad Yavneh.
-``Why Multigrid Methods are so Efficient'',
-{\em Computing in Science and Engineering, 8(6):12-22}, 2006
-\end{thebibliography}
+\bibliographystyle{is-plain}
+\bibliography{proposal}
 

### 2010-10-24 ng/advection.m
Refactor.

@@ -1,5 +1,6 @@
 function [A] = advection(interior, X, Y, Vx, Vy)
 %% Advection gradient discretization using sparse matrix.
+% Currently implemented by central difference scheme.
 sz = size(interior);
 N = numel(interior);
 

### 2010-10-24 ng/checkerboard.m

@@ -1,3 +1,5 @@
+% I = CHECKERBOARD(SZ)
+%   Create True/False checkerboard pattern of specified size.
 function I = checkerboard(sz)
     I = false(sz);
     I(1:2:end, 1:2:end) = true;

### 2010-10-24 ng/ddslip.m

@@ -1,12 +1,14 @@
-% Dukhin-Derjaguin slip velocity
+% V = DDSLIP(PHI, C, GAMMA, THETA)
+%   Dukhin-Derjaguin slip velocity.
 function V = ddslip(solPhi, solC, gamma, theta)
-    C = col(mean(solC(1:2, 2:end-1))); % on R=1
-    Phi = col(mean(solPhi(1:2, 2:end-1))); % on R=1
+    C = col(mean(solC(1:2, 2:end-1))); % average on R=1
+    Phi = col(mean(solPhi(1:2, 2:end-1))); % average on R=1
     
     xi = log(average(C(:), [1;1]/2)) - log(gamma);
-    lnC = log(C);
+    lnC = log(C); 
     
     dtheta = diff(theta(:));
-    deriv = @(f) diff(f(:)) ./ dtheta;
+    deriv = @(f) diff(f(:)) ./ dtheta; % Derivation by theta.
     V = xi .* deriv(Phi) + 2 * log(1 - tanh(xi/4).^2) .* deriv(lnC);
+    % Tangential velocity component.
 end

### 2010-10-24 ng/deriv.m

@@ -1,7 +1,14 @@
+% D = DERIV(G, DIR)
+%   Derivation operator on a grid on coordinates, in specified direction.
+%   Example:
+%       [X, Y] = ndgrid(x, y);
+%       Dx = deriv(X, [1 0]);
+%       Dy = deriv(Y, [0 1]);
+%
 function D = deriv(G, dir)
 I = true(size(G));
 I1 = shift(I, -dir);
 I2 = shift(I, +dir);
 D = 1 ./ (G(I2) - G(I1));
 N = prod(size(G)-dir);
-D = sparse((1:N)'*[1 1], [find(I1), find(I2)], [-D, D]);
+D = sparse(repmat((1:N)', [1 2]), [find(I1), find(I2)], [-D, D]);

### 2010-10-24 ng/gradient.m

@@ -1,4 +1,5 @@
-% Sparse gradient operator.
+% G = GRADIENT(K, X, Y, DIR)
+%   Sparse gradient operatorin polar coordinates.
 function G = gradient(K, X, Y, dir)
     sz = size(K);
     [I, J] = ind2sub(sz, find(K));
@@ -6,8 +7,8 @@ function G = gradient(K, X, Y, dir)
     K2 = sub2ind(sz, I + dir(1), J + dir(2));
     K0 = sub2ind(sz - dir, I, J);
     switch find(dir)
-        case 1, D = X(K2) - X(K1);
-        case 2, D = (Y(K2) - Y(K1)) .* (X(K1) + X(K2))/2;
+        case 1, D = X(K2) - X(K1); % D/Dr
+        case 2, D = (Y(K2) - Y(K1)) .* (X(K1) + X(K2))/2; % 1/r * D/Dtheta
     end
     G = sparse([1:numel(K0), 1:numel(K0)], [K1 K2], [-1./D,  1./D], ...
         numel(K0), prod(sz));

### 2010-10-24 ng/grids.m

@@ -1,3 +1,5 @@
+% [CENTER, INTERIOR, XSTAG, YSTAG] = GRIDS(X, Y)
+%   Create central and staggered grids for Laplace and Stokes problems.
 function [center, interior, xstag, ystag] = grids(x, y)
     x = x(:); y = y(:); 
     % extended grid (for ghost points)

### 2010-10-24 ng/init_grid.m

@@ -1,3 +1,5 @@
+% G = INIT_GRID(X, Y)
+%   Create regular grid object for specified (x,y) coordinates.
 function G = init_grid(x, y)
     G.x = x(:);
     G.y = y(:);

### 2010-10-24 ng/main1.m

@@ -1,7 +1,7 @@
-function F = main1(filename, do_init, iters, beta, gamma, Vinf)
+function F = main1(filename, do_init, beta, gamma, Vinf, Rinf, N, cycles)
     tic;
-    radius = logspace(0, 2, 60).';
-    theta = linspace(0, pi, 15).';
+    radius = logspace(0, log10(Rinf), N(1)).';
+    theta = linspace(0, pi, N(2)).';
     [center, interior, xstag, ystag] = ...
         grids(radius, theta);
     gridPhi = center;
@@ -22,6 +22,7 @@ function F = main1(filename, do_init, iters, beta, gamma, Vinf)
         solVy = 0*randn(gridVy.sz);
         solP = 0*randn(gridP.sz);
         solC = 1+0*randn(gridC.sz);
+        fprintf('Initializing settings for iterative solver.\n');
     else
         S = load(filename);
         solPhi = S.solPhi;
@@ -29,36 +30,44 @@ function F = main1(filename, do_init, iters, beta, gamma, Vinf)
         solVy = S.solVy;
         solP = S.solP;
         solC = S.solC;
+        fprintf('Loading solver settings from "%s".\n', filename);
     end
-    fprintf('Initialization done after %.3fs.\n', toc);
+    fprintf('Running solver for %d cycles:\n', cycles);
+    fprintf('\tbeta  = %.4e\n', beta);
+    fprintf('\tgamma = %.4e\n', gamma);
+    fprintf('\tV(inf)  = %.4e\n', Vinf);
+    fprintf('\tR(inf)  = %.1f\n', Rinf);
+    fprintf('\tGrid size = [%d %d]\n', N(1), N(2));
     
     function state = iteration(state)
         [solPhi, solVx, solVy, solP, solC] = split(state, ...
             gridPhi.sz, gridVx.sz, gridVy.sz, gridP.sz, gridC.sz);
-        relax_maxwell(1);
-        relax_stokes(1);
-        relax_advection(1);        
+        %relax_maxwell(1);
+        relax_stokes(100);
+        %relax_advection(1);
         state = [solPhi(:); solVx(:); solVy(:); solP(:); solC(:)];
     end
 
     state = [solPhi(:); solVx(:); solVy(:); solP(:); solC(:)];
-    [state] = extrapolate(state, @iteration, 0, 20, 'N/A');
[…]

### 2010-10-24 ng/main2.m

@@ -1,25 +1,34 @@
-function main(x)
+function main2(x)
 
-betas = linspace(1e-4, 1e-3, 10);
+clc;
+betas = linspace(1e-4, 1e-3, 1);
 gamma = exp(x);
+Rinf = 100;
 
 U = zeros(size(betas));
-for k = 1:numel(betas)
-    Vinf = betas(k) * 2*log((gamma^0.25 + gamma^-0.25) / (2*gamma^0.25));
-    Vinf = Vinf * linspace(0.9, 1.1, 3);
+calc_force = @(beta, V) ...
+    main1('results', 1, beta, gamma, V, Rinf, ...
+    [60 15], 2000);
 
-    N = 2e3;
+V_theory = betas * 2*log((gamma^0.25 + gamma^-0.25) / (2*gamma^0.25));
+
+for k = 1:numel(betas)
+    Vinf = V_theory(k);
+    Vinf = Vinf * linspace(0.9, 1.1, 2);
+
     F = zeros(size(Vinf));
     for i = 1:numel(Vinf)
-        F(i) = main1('results', 1, N, betas(k), gamma, Vinf(i));
+        F(i) = calc_force(betas(k), Vinf(i));
     end
 
     [a0, b0, e, R] = linreg(F(:), Vinf(:));
-    b0, R
     U(k) = b0;
-    main1('results', 1, N, betas(k), gamma, U(k));
+    calc_force(betas(k), U(k));
 end
-Vinf = betas * 2*log((gamma^0.25 + gamma^-0.25) / (2*gamma^0.25))
+
+fprintf('Errors:\n');
+fprintf(' %.2f%%', 100 * (U - V_theory) ./ V_theory);
+fprintf('\n');
 
 f = sprintf('gamma[%d]', x);
 save(f);

### 2010-10-24 ng/simpson.m

@@ -1,8 +1,7 @@
-function S = integ(f, a, b, n)
+function S = simpson(f, a, b, n)
 h = (b - a) / (2*n); % interval length
 x = linspace(a, b, 2*n + 1); % Newton-Cotes nodes
 F = f(x); % Function values
-I = logical(mod(1:2*n-1, 2)); % [1 0 1 0 ... 0 1] pattern
 I = [1, (mod(1:2*n-1, 2) + 1) * 2, 1]; % [1 4 2 4 2 ... 2 4 1] pattern
 w = I * h / 6; % Simpson's weights
 S = w * F(:);

### 2010-10-24 ng/streamlines_test.m

@@ -1,0 +1,10 @@
+function streamlines_test
+clc
+load results
+[X, Y] = ndgrid(logspace(0, 1), linspace(0, pi));
+psi = Vinf * sin(Y)/2 .* (X - 3./(2*X) + 1./(2*X.^2));
+Xp = X .* cos(Y);
+Yp = X .* sin(Y);
+clf
+contour(Xp, Yp, psi, linspace(0, .05, 50))
+axis equal

### 2010-10-24 ng/vorticity_test.m

@@ -1,0 +1,12 @@
+function vorticity_test
+
+load results
+[W, gW] = vorticity(solVx, solVy, gridVx, gridVy);
+Wt = 1.5 * Vinf * sin(gW.Y) ./ gW.X.^2;
+% clf;
+% contour(gW.y, gW.x, W, 20)
+% ylim([1 10])
+subplot 211; mesh(W); zlim([0 1.5]*Vinf); title('Numeric results')
+subplot 212; mesh(Wt); zlim([0 1.5]*Vinf); title('Theory')
+E = W - Wt; 
+fprintf('Vorticity error: %.2f%%\n', 100 * norm(E(:), inf) / norm(W(:), inf))

### 2010-11-08 symbolic/test.m
Add notes for slipping sphere.

@@ -16,7 +16,8 @@ function test
     P = W*a*cos(t)/r^2;
     gP = gradient(P);
     assert(all(L == gP))
-    F = radial_stress(V, P, a)    
+    F = radial_stress(V, P, a)
+    save results
 end
 
 function F = gradient(f)
@@ -51,7 +52,7 @@ function F = radial_stress(V, P, a)
     S = [-P + 2*diff(V(1), r);
         diff(V(2), r) + (diff(V(1), t) - V(2)) / r];
     S = subs(S, r, a);
-    S = simple(S);
+    S = simple(S)
     f = simple([cos(t), -sin(t)] * S);
     f
     F = int(f * 2*pi*a*sin(t), t, 0, pi);

### 2010-11-08 symbolic/test.m
Develop full solution for small beta.

@@ -7,13 +7,26 @@ function test
     P = -3*U*a*cos(t)/(2*r^2);
     gP = gradient(P);
     assert(all(L == gP))
-    F = radial_stress(V, P, a)
+    F = radial_stress(V, P, a);
 
     psi = (W/2) * (a*r - a^3/r)*sin(t)^2;
     V = curl(psi);
     subs(V, r, a)
     L = simple(vector_laplacian(V));
     P = W*a*cos(t)/r^2;
+    gP = gradient(P);
+    assert(all(L == gP))
+    F = radial_stress(V, P, a);
+    
+    psi1 = (U/2) * (r^2 - (3*a*r)/2 + a^3/(2*r))*sin(t)^2;
+    psi2 = (W/2) * (a*r - a^3/r)*sin(t)^2;
+    psi2 = subs(psi2, W, 3*U/2);
+    psi = simple(psi1 + psi2);
+    pretty(psi)
+    V = simple(curl(psi))
+    pretty(V)
+    L = simple(vector_laplacian(V))    
+    P = 0; % Note that the pressure is constant!
     gP = gradient(P);
     assert(all(L == gP))
     F = radial_stress(V, P, a)
@@ -53,7 +66,6 @@ function F = radial_stress(V, P, a)
         diff(V(2), r) + (diff(V(1), t) - V(2)) / r];
     S = subs(S, r, a);
     S = simple(S)
-    f = simple([cos(t), -sin(t)] * S);
-    f
+    f = simple([cos(t), -sin(t)] * S)
     F = int(f * 2*pi*a*sin(t), t, 0, pi);
 end

### 2010-11-09 notes/diffusion.tex
Refactor notes.

\section{Diffusion}
\subsection{Laplace equation (follows from Gauss' law)}
The electric potential satisfies the elliptic equation
\begin{equation}
	\bnabla \bcdot (C \bnabla \varPhi) = 0; \label{Phi eqn}
\end{equation}
$C$ is salt concentration, playing the role of $\eps$,
in Maxwell's equation (where $\vect{E} = -\bnabla \varPhi$):
\begin{equation}
\bnabla \bcdot \vect{D} = \bnabla \bcdot \eps \vect{E} = \rho_{free}
\end{equation}

We assume regular grid $\{(x_i, y_j)\}$,
where $i\in\{0 \ldots n\}$ and $j\in\{0 \ldots m\}$. The maximal and the
minimal indices' values correspond to the boundary of the problem.

We approximate the differential operator as:
\begin{eqnarray}
\left[ \bnabla \bcdot (C \bnabla \varPhi) \right]_{i,j}
&\approx &\frac{2}{x_{i+1,j} - x_{i-1,j}} \left(
C_{i+1/2,j} \cdot \frac{\varPhi_{i+1,j}-\varPhi_{i,j}}{x_{i+1}-x_{i}} -
C_{i-1/2,j} \cdot \frac{\varPhi_{i,j}-\varPhi_{i-1,j}}{x_{i}-x_{i-1}}
\right) + \\
&&\frac{2}{y_{i,j+1} - y_{i,j-1}} \left(C_{i,j+1/2} \cdot \frac{\varPhi_{i,j+1}-\varPhi_{i,j}}{y_{i+1}-y_{i}} -
C_{i,j-1/2} \cdot \frac{\varPhi_{i,j}-\varPhi_{i,j-1}}{y_{i}-y_{i-1}}
\right)
\end{eqnarray}
where $2C_{i\pm 1/2,j} = C_{i,j} + C_{i\pm 1,j}$ and
$2C_{i,j\pm 1/2} = C_{i,j} + C_{i,j\pm 1}$.

The algebraic system above can be written as $\matr{A} \vect{u} = \vect{f}$,
where $\matr{A}$ depends on the grid and current $C$ values.
$\vect{f}$ can be chosen to be any function, which is useful for testing the solver.
We initialize $\vect{u}$ to any function, and employ Jacobi iterations
(by writing $\matr{A} = \matr{D} + (\matr{A-D})$, where $\matr{D}$ is diagonal):
\begin{eqnarray}
\vect{f} &=& \matr{A}\vect{u} = \matr{D}\vect{u} + (\matr{A-D})\vect{u} \\
\matr{D}\vect{u} &=& \vect{f} - (\matr{A-D})\vect{u} =
\vect{f} - \matr{A}\vect{u} + \matr{D}\vect{u} \\
\vect{u}_+ &=& \vect{u} + \matr{D}^{-1}(\vect{f} - \matr{A}\vect{u}) =
(\matr{I} - \matr{D}^{-1}\matr{A}) \vect{u} + \matr{D}^{-1}\vect{f} \\
\end{eqnarray}
Therefore, we shall use the following iteration scheme:
\begin{eqnarray}
\vect{u}_+ &=& \matr{T}\vect{u} + \vect{d} \\
\matr{T} &=& \matr{I} - \matr{D}^{-1}\matr{A} \\
\vect{d} &=& \matr{D}^{-1}\vect{f}
\end{eqnarray}
To speed-up the convergence, we shall use Red-Black Gauss-Seidel method,
that updates ``odd'' and ``even'' elements of $\vect{u}$, solving
effectively the linear system for half the variables each time.
\subsection{Boundary conditions}
\subsubsection{Dirichlet}
The condition is given as $U(x, y) = C$.
We take $u_k = U(x_i, y_j) = C$.
Now, it is simply substituted and
linear system's right-hand side is updated accordingly.

\subsubsection{Neumann}
The condition is given as $\bnabla U(x,y) \cdot \vect{\hat n} = C$,
where $\vect{\hat n}$ is normal to domain's boundary.
If we use quadratic approximation, the gradient can be expressed as:
\begin{eqnarray}
  f(x) &=& ax^2 + bx + c \\
  f(x_0 \pm \Delta x) &=&
   a(x_0 \pm \Delta x)^2 + b(x_0 \pm \Delta x) + c \\
  \frac{f(x_0 + \Delta x) - f(x_0 - \Delta x)}{2\Delta x} &=&
   2a x_0 + b = f'(x_0) \\
\end{eqnarray}
Therefore, the boundary value can be approximated by:
\begin{eqnarray}
 U(x + \Delta x,y + \Delta y) &\approx& U(x, y) + \partial_x U(x_c,y_c) \Delta x +
 \partial_x U(x_c,y_c) \Delta y \\
 x_c &=& x + \frac{\Delta x}{2} \\
 y_c &=& y + \frac{\Delta y}{2}
\end{eqnarray}

\subsection{Specific boundary conditions}
\subsubsection{$R = 1$}
\begin{eqnarray}
  \frac{\partial C}{\partial R} &=&
   C \frac{\partial \varPhi}{\partial R} \\
  \varPhi &=& \mathscr{V} - \ln C + \ln \gamma
\end{eqnarray}
Take $\mathscr{V} = -\ln \gamma$ and note that:
\begin{eqnarray}
  \frac{\partial}{\partial R} \ln C &=&
  \frac{1}{C}\frac{\partial C}{\partial R} =
  \frac{\partial \varPhi}{\partial R} \\
  \varPhi &=& -\ln C
\end{eqnarray}
Use ghost-point \#0 to write the following boundary equations:
\begin{eqnarray}
  \varPhi_1 - \varPhi_0 &=& \ln C_1 - \ln C_0 \\
  \varPhi_1 + \varPhi_0 &=& - \ln C_1 - \ln C_0
\end{eqnarray}
Add and subtract to get 2 Dirichlet conditions:
\begin{eqnarray}
  \varPhi_1 &=& - \ln C_0 \\
  \varPhi_0 &=& - \ln C_1 \\
  C_0 &=& e^{-\varPhi_1}
\end{eqnarray}
\subsubsection{$R \rightarrow \infty$}
$C$ gets uniform, and we get Dirichlet:
\begin{eqnarray}
 C = 1
\end{eqnarray}
The field radial component is Neumann:
\begin{eqnarray}
 \frac{\partial \varPhi}{\partial R} = -\mathscr{E} \cos \theta
\end{eqnarray}
\subsubsection{$\Theta = 0/\pi$}
Using symmetry considerations, we have Neumann conditions:
\begin{eqnarray}
 \frac{\partial \varPhi}{\partial \Theta} &=& 0 \\
 \frac{\partial C}{\partial \Theta} &=& 0 \\
\end{eqnarray}

### 2010-11-13 ng/compare_streamlines.m
Refactor.

@@ -43,4 +43,4 @@ contour(gridPsi.X .* cos(gridPsi.Y), gridPsi.X .* sin(gridPsi.Y), ...
 
 axis equal; 
 axis(axs); title('Coupled Flow Streamlines (theoretical solution)')
-print -depsc2 stokes_theory.eps
+print -depsc2 coupled_theory.eps

### 2011-01-28 ng/dirichlet.m
Refactor.

@@ -1,4 +1,8 @@
-% [Q] = dirichlet(grid, dir)
+% Dirichlet boundary conditions
+% Usage:
+%   Q = dirichlet(grid, dir);
+%   rhs = -L * Q * values;
+
 function [Q] = dirichlet(grid, dir)
     J = ~grid.I & shift(grid.I, dir); % boundary logical mask
     boundary = find(J); % boundary indices

### 2011-01-28 ng/neumann.m

@@ -1,4 +1,8 @@
+% Neumann boundary conditions
+% Usage:
 % [P, Q] = neumann(grid, dir)
+%   A = L * P * expand(gridPhi.I)
+%   rhs = -L * Q * vals
 function [P, Q] = neumann(grid, dir, extend)
     J = ~grid.I & shift(grid.I, dir); % boundary logical mask
     if nargin > 2 && extend
@@ -10,7 +14,7 @@ function [P, Q] = neumann(grid, dir, extend)
     interior = find(I); % interior indices
     h = [grid.X(J) - grid.X(I), grid.Y(J) - grid.Y(I)];
     h = h * dir(:);
-    P = sparse(boundary, interior, repmat(1, size(boundary)), ...
+    P = sparse(boundary, interior, ones(size(boundary)), ...
         grid.numel, grid.numel) + speye(grid.numel);
     Q = sparse(boundary, 1:numel(boundary), h, ...
         grid.numel, numel(boundary));

### 2011-05-01 src/steady.m
Refactor streamlines.

@@ -2,11 +2,11 @@
 % Given beta, find the velocity for zero particle force.
 % Example usage:
 % >> s = steady([], 1, [1 2], 3);
-function sol = steady(sol, betas, v, iters, varargin)
+function [sol, grid] = steady(sol, betas, v, iters, varargin)
 
     conf = [{'version', 0, 'logging', 1}, varargin];
     function f = func(b, u) % Total force for specified (b, u)
-        sol = force(sol, b, u, conf{:});
+        [sol, grid] = force(sol, b, u, conf{:});
         f = sol.force.total;
     end
 

### 2011-05-02 src/newton_solver.m
Test Hessian using numerical linearization.

@@ -2,16 +2,33 @@ function step = newton_solver(grid)
 
     %% Newton method step
     %%%%%%%%%%%%%%%%%%%%%%%%
-    function [sol, rhs, du] = newton_step(sol)
+    function [sol, res, du] = newton_step(sol)
+        if ~isempty(sol.du)
+            d = sol.du;
+            sol.du = [...
+                0 * randn(nnz(grid.Phi.I), 1); ...
+                % d * randn(nnz(grid.C.I), 1); ...
+                d; 0; zeros(nnz(grid.C.I)-2, 1);
+                0 * randn(nnz(grid.Vx.I), 1); ...
+                0 * randn(nnz(grid.Vy.I), 1); ...
+                0 * randn(nnz(grid.P.I), 1); ...
+            ];
+            sol = apply(sol, sol.du);
+        end
         [sol, Hb] = boundary_conditions(sol); % Apply boundary conditions
-        [rhs, Hf] = full_system(sol); % Apply full system to get RHS -> 0
+        [res, Hf] = full_system(sol); % Apply full system to get residual -> 0
         % 0 = F(B(u)) + Hf * Hb * du
-        % H * du = -F(B(u)) = -rhs
-        % du = - H \ rhs
+        % H * du = -F(B(u)) = -residual
+        % du = - H \ residual
         H = Hf * Hb; % Interior's Hessian
         H = H + eps*speye(size(H)); % Make the inverse more stable.
-        du = -(H \ rhs);
+        du = -(H \ res);
+        if ~isempty(sol.du)
+            plot([res, res-H * sol.du]);
+            sol.du = [];
+        end
         sol = apply(sol, du);
+        sol.residual = res;
     end
     step = @newton_step;
     
@@ -165,6 +182,7 @@ function step = newton_solver(grid)
     end
 
     %% Applies step to system interior variables
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
     function sol = apply(sol, du)
         [dPhi, dC, dVx, dVy, dP] = split(du, ...
             grid.Phi.sz-2, grid.C.sz-2, ...

### 2011-06-08 symbolic/test.m
Refactor.

@@ -13,6 +13,10 @@ function test
     V = curl(psi);
     subs(V, r, a)
     L = simple(vector_laplacian(V));
+    L1 = vlapl(V);
+    eL = (L - L1)
+    vlapl([r; 0])
+    return
     P = W*a*cos(t)/r^2;
     gP = gradient(P);
     assert(all(L == gP))
@@ -58,6 +62,18 @@ function [L] = vector_laplacian(F)
          - 2 * F(1) / (r^2) - 2 * diff(sin(t) * F(2), t) / (r^2 * sin(t)); ...
          scalar_laplacian(F(2)) ...
          - F(2) / (r * sin(t))^2 + 2 * diff(F(1), t) / r^2];
+end
+
+function L = vlapl(F)
+    syms r t;
+    Dr = @(f) diff(f, r);
+    Dt = @(f) diff(f, t);
+    sint = sin(t);
+    Vr = F(1);
+    Vt = F(2);
+    L = [Dr(r^(-2) * Dr(r^2 * Vr)) + (1/(r^2 * sint)) * Dt((Dt(Vr) - 2*Vt) * sint);
+         r^(-2) * Dr(r^2 * Dr(Vt)) + r^(-2) * Dt((1/(sint))*Dt(Vt * sint) + 2*Vr)];
+    L = simple(L);
 end
 
 function F = radial_stress(V, P, a)

### 2011-06-19 src/analytic.m
Refactor and work on animation.

@@ -1,0 +1,10 @@
+function sol = analytic(sol)
+    grid = sol.grid;
+    sol.Vinf = -sol.beta * 2 * log((1 + 1/sqrt(sol.gamma)) / 2);
+    
+    sol.Phi =  sol.beta  * (0.25 * grid.Phi.X.^(-2) - grid.Phi.X) .* cos(grid.Phi.Y);
+    sol.C = 1 + sol.beta  * 0.75 * grid.C.X.^(-2)                 .* cos(grid.C.Y);
+    sol.Vx =  sol.Vinf     * (1 - grid.Vx.X.^(-3))                .* cos(grid.Vx.Y);
+    sol.Vy = -sol.Vinf * (1 + 0.5*grid.Vy.X.^(-3))                .* sin(grid.Vy.Y);
+    sol.P = zeros(grid.P.sz);
+end

### 2011-06-19 src/animate.m

@@ -1,0 +1,58 @@
+function animate
+    S = load('matlab');
+    figure(1)
+    set(gcf, 'PaperPositionMode', 'auto');
+%     set(gcf, 'Position',[100 100 900 600]);
+    V = attr(S.solutions, 'Vinf');
+    Va = attr(S.solutions, 'Vinf_approx');
+    betas = attr(S.solutions, 'beta');
+    for k = 1:numel(S.solutions)
+        sol = S.solutions{k};
+        s = [['\beta = ' sprintf('%.3f', sol.beta)] ...
+            sprintf('  ') ...
+            ['V = '  sprintf('%.3f', sol.Vinf)]];
+        clf; 
+        subplot(2,2,[1 3])
+        colormap(jet)
+        loglog(betas, V, '-b', betas, Va, ':r', ...
+            sol.beta, sol.Vinf, '.b', ...
+            sol.beta, sol.Vinf_approx, '.r', ...
+            'MarkerSize', 20, 'LineWidth', 2.5)
+        title('Electrokinetic Solver Results', 'FontSize', 16)
+        xlabel('Electric field magnitude (\beta)', 'FontSize', 12)
+        ylabel('Particle velocity magnitude (V)', 'FontSize', 12)
+        legend({'Numerical Solver', 'Analytical Approximation'}, ...
+            'Location', 'SouthEast', 'FontSize', 8, 'Box', 'on')
+        axis([0.01 1 0.001 1])
+        text(0.04, 0.4, s, 'FontSize', 12);
+        subplot(2,2,2);
+        hold on
+        show(@contour, sol, 'Psi', 10, +1, sol.Vinf * linspace(-1, 1, 50));
+        show(@contour, sol, 'Psi', 10, -1, sol.Vinf * linspace(-1, 1, 50));
+        sphere();
+        hold off; 
+        axis equal; axis([-4 4 -3 3]); 
+        title('Fluid streamlines', 'FontSize', 14)
+
+        subplot(2,2,4);
+        hold on
+        for d = [-1 1]
+            show(@surf, sol, 'C', 10, d, 'EdgeColor', 'none');
+        end
+        set(gca, 'CLim', [0 2])
+        shading('interp')
+        colorbar;
+        view(2)
+        sphere();
+        hold off; 
+        axis equal; axis([-4 4 -3 3]); 
+        title('Salt Concentration', 'FontSize', 14)
+        drawnow;
[…]

### 2011-06-19 src/force.m

@@ -20,7 +20,6 @@ function [sol] = force(sol, betas, Vinf, varargin)
         sol.C = ones(sol.grid.C.sz);
         return
     end
-    sol.Vinf_approx = -2*log((1 + 1/sqrt(sol.gamma)) / 2);
     
     if isempty(betas) % No iterations are possible if no betas.
         return
@@ -35,18 +34,19 @@ function [sol] = force(sol, betas, Vinf, varargin)
         sol = sol.newton_step(sol);
         assert( all(sol.C(:) > 0), 'C < 0 detected!' );
         
-        res = norm(sol.res, 2) / sqrt(numel(sol.res)); % Residual norm
+        res = norm(sol.res, inf); % Residual norm
         logger('    force', 'beta = %e, residual = %e', sol.beta, res)
         
         if (k < min(sol.iters) || k < numel(betas))
             continue;
         end
-        if (k > max(sol.iters) || res < sol.maxres)
+        if (k >= max(sol.iters) || res < sol.maxres)
             break;
         end
     end
     sol.force = total_force(sol, sol.grid);
     sol = streamfunc(sol);
+    sol.Vinf_approx = -2*log((1 + 1/sqrt(sol.gamma)) / 2) * sol.beta;
 end
 
 function [force] = total_force(sol, grid)

### 2011-06-19 src/show.m

@@ -1,8 +1,11 @@
-function show(func, sol, name, Rmax, varargin)
+function show(func, sol, name, Rmax, dir, varargin)
     g = sol.grid.(name);
     Z = (sol.(name));
     I = g.x < Rmax;
     X = g.X .* cos(g.Y);
     Y = g.X .* sin(g.Y);
-    func(X(I, :), Y(I, :), Z(I, :), varargin{:});
+    X = X(I, :);
+    Y = Y(I, :) * dir;
+    Z = Z(I, :);
+    func(X, Y, Z, varargin{:});
 end

### 2011-06-19 src/solver.m

@@ -1,44 +1,27 @@
-function sol = solver
-    clc;
+function solver
     tic;
+    clc;
     sol = struct( ...
-        'radius', logspace(0, 3, 60), ...
-        'theta', linspace(0, pi, 40), ...
-        'gamma', 10, ...
+        'radius', logspace(0, 3, 75), ...
+        'theta', linspace(0, pi, 25), ...
+        'gamma', 2, ...
         'alpha', 0, ...
-        'maxres', 1e-9, ...
-        'iters', [5, 20] ...
+        'maxres', 1e-12, ...
+        'iters', [2 10] ...    
     );
+    betas = 10.^(-2:0.01:0);
     sol = force(sol); % initialize force solver
-
-    betas = 1; % logspace(0, 1, 20);
-    sol.Vinf = 1;
-
-    alphas = 0; [0 0.1];
-    for a = alphas
-        sol.alpha = a;
-        [sol, V, F] = steady(sol, betas(1), sol.Vinf*[1, 0.9], 200);
+    solutions = cell(numel(betas), 1);
+    for k = 1:numel(betas)
+        sol.beta = betas(k);
+        sol = analytic(sol); % approximation
+        alphas = [0 0.5]; % XXX
+        for a = alphas
+            sol.alpha = a;
+            [sol, V, F] = steady(sol, sol.Vinf*[1, 0.9], 5);
+        end
+        solutions{k} = sol;
     end
     save
-end
-
-function [sol, V, F] = steady(sol, betas, v, iters)
-
-    logger('steady', 'alpha = %f', sol.alpha)
-    function f = force_func(b, u) % Total force for specified (beta, Vinf)
-        [sol] = force(sol, b, u);
-        f = sol.force.total;
-    end
-
-    force_func(betas, v(1));
-    % Last beta, for steady-state velocity secant method.
-    b = betas(end);
-    logger('steady', 'secant (beta = %e)', b)
-    secant_step = secant(@(u) force_func(b, u), v);
-    for k = 1:iters
-        [V(k), F(k)] = secant_step();
-        log('steady', '(%d/%d) V = %e \t F = %e', k, iters, V(k), F(k));
-        plot([V; F]'); drawnow;
-    end
-    
+    tone(300, 0.1)
 end

### 2011-06-19 src/steady.m

@@ -1,0 +1,15 @@
+function [sol, V, F] = steady(sol, v, iters)
+
+    logger('steady', 'alpha = %f, beta = %e', sol.alpha, sol.beta);
+    function f = solve_force(u) % Total force for specified (beta, Vinf)
+        [sol] = force(sol, sol.beta, u);
+        f = sol.force.total;
+    end
+
+    secant_step = secant(@(u) solve_force(u), v);
+    for k = 1:iters
+        [V(k), F(k)] = secant_step();
+        logger('steady', '%3d) V = %e \t F = %e', k, V(k), F(k));
+    end
+    
+end

### 2011-06-19 src/tone.m

@@ -1,0 +1,5 @@
+function tone(F, T)
+Fs = 48e3;
+t = 0:(1/Fs):T;
+x = sin(2*pi*F*t) .* sin(pi*t/t(end)) * 0.5;
+wavplay(x, Fs)

### 2011-06-19 src/visualize.m

@@ -1,22 +1,0 @@
-function visualize
-    load
-    clf;
-    for k = 1:numel(sols)
-        sol = sols{k};
-        clf; 
-        hold on
-        show(@contour, sol, 'Psi', 10, sol.Vinf * linspace(-1, 1));
-        sphere(sol);
-%         show(@surf, sol, 'Phi', 3, 'EdgeColor', 'k');
-        hold off; axis equal; axis([-1 1 0 1]*5)
-        
-        title(sprintf('\\beta = %f : V_{\\infty} = %f', sol.beta, sol.Vinf))
-        drawnow;
-        print('-dpng', sprintf('%02d', k))
-    end
-end
-
-function sphere(sol)
-    t = sol.grid.theta;
-    fill(cos(t), sin(t), 'k');
-end

### 2011-10-07 src/newton_solver.m
Refactor.

@@ -1,41 +1,5 @@
 function step = newton_solver(grid)
 
-    %% Newton method step
-    %%%%%%%%%%%%%%%%%%%%%%%%
-    function [sol, res, du] = newton_step(sol)
-        if isfield(sol, 'debug') && ~isempty(sol.debug)
-            d = sol.debug.du;
-            prng = RandStream('mt19937ar', 'seed', 0);
-            sol.du = [...
-                d * prng.randn(nnz(grid.Phi.I), 1); ...
-                d * prng.randn(nnz(grid.C.I), 1); ...
-                d * prng.randn(nnz(grid.Vx.I), 1); ...
-                d * prng.randn(nnz(grid.Vy.I), 1); ...
-                d * remove_mean(prng.randn(nnz(grid.P.I), 1))];
-            sol1 = sol;
-            sol = apply(sol, sol.du);
-        end
-        [sol, Hb] = boundary_conditions(sol); % Apply boundary conditions
-        [res, Hf] = full_system(sol); % Apply full system to get residual -> 0
-        sol.res = res;
-        if isfield(sol, 'debug') && ~isempty(sol.debug)
-            sol2 = sol;
-            dr = sol2.res - sol1.res;
-            df = Hf * Hb * sol.du;
-            subplot 211; plot(dr);
-            subplot 212; plot(df - dr);
-            sol.debug = [];
-        end
-        % 0 = F(B(u)) + Hf * Hb * du
-        % H * du = -F(B(u)) = -residual
-        % du = - H \ residual
-        H = Hf * Hb; % Interior's Hessian
-        H = H + eps*speye(size(H)); % Make the inverse more stable.
-        du = -(H \ res);
-        sol = apply(sol, du);
-    end
-    step = @newton_step;
-    
     %% Differential operators 
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%
     % Divergence, Gradient and Interpolation
@@ -190,6 +154,43 @@ function step = newton_solver(grid)
         sol.Vy(grid.Vy.I) = sol.Vy(grid.Vy.I) + dVy(:);
         sol.P = remove_mean(sol.P + dP);    
     end
+
+    %% Newton method step
+    %%%%%%%%%%%%%%%%%%%%%%%%
+    function [sol, res, du] = newton_step(sol)
+        if isfield(sol, 'debug') && ~isempty(sol.debug)
+            d = sol.debug.du;
+            prng = RandStream('mt19937ar', 'seed', 0);
[…]

### 2011-10-07 src/solver.m

@@ -21,6 +21,7 @@ function solver
             [sol, V, F] = steady(sol, sol.Vinf*[1, 0.9], 5);
         end
         solutions{k} = sol;
+        pause(0);
     end
     save
     tone(300, 0.1)

### 2011-10-07 symbolic/test.m

@@ -11,11 +11,10 @@ function test
 
     psi = (W/2) * (a*r - a^3/r)*sin(t)^2;
     V = curl(psi);
-    subs(V, r, a)
+    assert([1 0]*subs(V, r, a) == 0);
     L = simple(vector_laplacian(V));
     L1 = vlapl(V);
     eL = (L - L1)
-    vlapl([r; 0])
     return
     P = W*a*cos(t)/r^2;
     gP = gradient(P);

### 2011-10-17 symbolic/test.m
O(beta^2) term is O(sin(2t))
>> pretty(simple(V2))

                                    /      1/2     \
                                    | gamma    + 1 |
                      3 sin(2 t) log| ------------ | (W + 9)
                                    |         1/2  |
     9 sin(2 t)                     \  2 gamma     /
  ----------------- - --------------------------------------
           1/2                          8
  16 (gamma    + 1)

@@ -1,15 +1,17 @@
 clear;
 syms a r t U W
 clc
-psi = (U/2) * (r^2 - (3*a*r)/2 + a^3/(2*r))*sin(t)^2;
-V = curl(psi);
-L = simple(vector_laplacian(V));
-P = -3*U*a*cos(t)/(2*r^2);
-gP = gradient(P);
-assert(all(L == gP))
-F = radial_stress(V, P, a);
+at = @(f) simple(subs(f, r, 1));
 
-psi = (W/2) * (a*r - a^3/r)*sin(t)^2;
+% psi = -(U/2) * (r^2 - (3*a*r)/2 + a^3/(2*r))*sin(t)^2;
+% V = curl(psi);
+% L = simple(vector_laplacian(V));
+% P = -3*U*a*cos(t)/(2*r^2);
+% gP = gradient(P);
+% assert(all(L == gP))
+% F = radial_stress(V, P, a);
+
+psi = -(W/2) * (r^2 - a^3/r)*sin(t)^2;
 V = curl(psi);
 assert([1 0]*subs(V, r, a) == 0);
 L = simple(vector_laplacian(V));
@@ -20,7 +22,15 @@ Phi1 = ((1/4)*r^-2 - r) * cos(t);
 C1 = (3/4)*r^-2 * cos(t);
 assert(subs(Phi1 + C1, r, 1) == 0)
 assert(subs(diff(Phi1 - C1, r), r, 1) == 0)
+syms gamma phi
+xi = -phi-log(gamma);
+g = 4*log((exp(xi/2)+1)/2);
+V1a = subs(g, phi, 0) * at(diff(Phi1, t));
+U1 = simple(int(V1a * sin(t)^2, 0, pi) / int(sin(t), 0, pi));
+
 V1 = subs(V, a, 1);
+W1 = simple(int(at(V1(2)) * sin(t)^2, 0, pi) / int(sin(t), 0, pi));
+assert(W1 == W)
 
 gC1 = gradient(C1);
 gPhi1 = gradient(Phi1);
@@ -30,16 +40,17 @@ syms A1 A2 A3 A4
 RHS_Phi = simple(-gC1.'*gPhi1);
[…]

### 2011-10-20 symbolic/asymp.m
Use MATLAB to solve symbolically for b^3

@@ -1,0 +1,9 @@
+clear;
+syms b r t A
+c1 = 1 + b * 3/4 * r^(-2) * cos(t) + b^2*A;
+phi1 = b * (1/4 * r^(-2) - r) * cos(t);
+Dr = @(f) diff(f, r);
+Dt = @(f) diff(f, t);
+
+cond = @(phi, c) subs([phi + log(c); c*Dr(phi) - Dr(c)], r, 1);
+taylor( cond(phi1, c1), 3, b )

### 2011-11-20 symbolic/critical.m
Critical beta (for U = 0)

@@ -1,0 +1,11 @@
+g = logspace(0, 1, 1000);
+
+B1 = 2*log(1./(2*g.^(1/2)) + 1/2);
+B3 = (31./(320*(g.^(1/2) + 1)) - 9./(320*(g.^(1/2) + 1).^2) + 1/1680);
+
+% 0 = b.^3*(B3 - B1*11/320) + b*B1;
+b = sqrt(1./(11/320 - B3./B1));
+plot(g, b);
+xlabel('\gamma')
+ylabel('\beta_c')
+

### 2011-11-24 notes/summary/ch01.tex
Summary

\section{Physics}
Electrokinetic phenomena is described by the equations described below.
An ion-exchanger is described by the chemical kinetics at its boundary.
The experiment consists of applying an electic field and measuring the drift velocity of the particles.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Microscale}
Denote positive and negative ionic concentration by $c_+$ and $c_-$ respectively.
The respective fluxes are denoted by $\bj_+$ and $\bj_-$.

The electrostatic potential is denoted by $\varphi$.

The velocity and the pressure field are denoted by $\bv$ and $p$ respectively.

\subsubsection{Nernst-Planck Equations}
The ionic fluxes are given by diffusion (Fick's law), electrostatic forces and advection by the fluid:
\begin{eqnarray}
\bj_+ &=& -\bnabla c_+ - c_+ \bnabla \varphi + \alpha \bv c_+ \\
\bj_- &=& -\bnabla c_- + c_- \bnabla \varphi + \alpha \bv c_-
\end{eqnarray}
Due to conservation of ions, the fluxes are divergence-free:
\begin{eqnarray}
\bnabla \cdot \bj_\pm &=& 0.
\end{eqnarray}
These equation may be re-written by using the following transform:
\begin{eqnarray}
c &=& \frac{c_+ + c_-}{2}\\
q &=& \frac{c_+ - c_-}{2}
\end{eqnarray}
Thus, salt and charge fluxes are defined by:
\begin{eqnarray}
\bj &=& \frac{\bj_+ + \bj_-}{2} = -\bnabla c - q \bnabla \varphi + \alpha \bv c \\
\bi &=& \frac{\bj_+ - \bj_-}{2} = -\bnabla q - c \bnabla \varphi + \alpha \bv q
\end{eqnarray}

These fluxes are also divergence-free:
\begin{eqnarray}
\bnabla \cdot \bj &=& 0 \\
\bnabla \cdot \bi &=& 0 
\end{eqnarray}

\subsubsection{Incompressible Stokes Flow with Electrostatic Force}
Mass conservation (due to constant fluid density):
\begin{eqnarray}
\bnabla \cdot \bv &=& 0
\end{eqnarray}
Momentum conservation (force balance):
\begin{eqnarray}
\Laplacian \bv - \bnabla p + \bnabla \varphi \Laplacian \varphi &=& 0
\end{eqnarray}
Free charge density is given by Poisson equation:
\begin{eqnarray}
\delta^2 \Laplacian \varphi &=& -q
\end{eqnarray}

\subsubsection{Boundary conditions}
Away of the particle, we have uniform flow, uniform electrostatic field
and uniform ionic concentrations:
\begin{eqnarray}
\bv &\rightarrow& -\cU \ui \\
\bE = -\bnabla \varphi &\rightarrow& \beta\ui \\
c_\pm &\rightarrow& 1
\end{eqnarray}

We consider a spherical particle. At its surface ($r=1$ with normal $\bn = \brhat$), 
we have zero slip, anion impermeability, cation selectivity and particle's conductance:
\begin{eqnarray}
\bv & = & \bzero \\
\bn \cdot \bj_- & = & 0 \\
c_+ & = & \gamma \\
\varphi & = & \cV
\end{eqnarray}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Separation of scales}
Due to strong electrostatic forces, 
most of the fluid remains electroneutral ($c_+ \approx c_-$), 
except of a thin boundary layer (``Debye layer'') around the ion exchanger.

\subsubsection  {Bulk-scale equations}
Nernst-Planck equations above for the fluid bulk (outside
the boundary layer) using bulk variables:
\begin{eqnarray}
Q & = & 0 \\
C & = & C_+ = C_- \\
\bJ &=& -\bnabla C + \alpha \bV C \\
\bI &=& -C \bnabla \varPhi
\end{eqnarray}
Since the flow is incompressible ($\bnabla \cdot V = 0$), 
ion conservation results in the following equations:
\begin{eqnarray}
0 = \bnabla \cdot \bJ &\Rightarrow& \Laplacian C - \alpha \bV \cdot \bnabla C = 0 \\
0 = \bnabla \cdot \bI &\Rightarrow& \bnabla \cdot \pars{ C \bnabla \varPhi } = 0
\end{eqnarray}
Stokes flow equations stay the same:
\begin{eqnarray}
\bnabla \cdot \bV &=& 0 \\
\Laplacian \bV - \bnabla P + \bnabla \varPhi \Laplacian \varPhi &=& 0
\end{eqnarray}

\subsection{Debye-scale effective boundary conditions}
We define the rescaled coordinate $\rho$ (normal to ion-exchanger surface), where $\delta \ll 1$:
\begin{eqnarray}
\rho &=& \frac{r-1}{\delta} \\
\end{eqnarray}
Thus, the electric potential and the ionic concentrations are $O(1)$ at Debye layer ($r \approx 1$):
\begin{eqnarray}
\varphi(\rho,\theta) &\sim& \varphi \\
c_\pm(\rho,\theta) &\sim& c_\pm \\
c(\rho,\theta) &\sim& c \\
q(\rho,\theta) &\sim& q
\end{eqnarray}

The radial fluxes at the Debye layer are $O(\delta^{-1})$, due to coordinate rescaling:
\begin{eqnarray}
j_\pm(\rho, \theta) &\sim& \delta^{-1} j_\pm
\end{eqnarray}

The pressure is $O(\delta^{-2})$, due to momentum balance equations:
\begin{eqnarray}
p(\rho, \theta) &\sim& \delta^{-2} p
\end{eqnarray}

The tangential velocity component is $O(1)$ and the radial one is $O(\delta)$.

In order to match bulk $O(1)$ outer radial ionic flux, 
the $O(\delta^{-1})$ inner ionic radial flux $j_\pm(\rho, \theta)$ must vanish:
\begin{eqnarray}
-\deriv{c_\pm}{\rho} \mp c_\pm \deriv{\varphi}{\rho} &=& 0 \\
\deriv{\varphi}{\rho} \pm\frac{1}{c_\pm}\deriv{c_\pm}{\rho} &=& 0 \\
\pars{\varPhi - \varphi} \pm\pars{\log C_\pm - \log c_\pm} &=& 0 \\
\varPhi - \varphi \pm \log \frac{C_\pm}{c_\pm} &=& 0
\end{eqnarray}
This relation can be rewritten as Boltzmann distribution of ionic concentration,
since $C_\pm|_{\rho\rightarrow\infty} = C$:
\begin{eqnarray}
c_\pm = C \exp\left[\pm(\varPhi - \varphi)\right]
\end{eqnarray}

Due to cation selectivity, $c_+|_{\rho=0} = \gamma$.
Denote zeta potential as the voltage drop between the particle surface and the end of
the boundary layer, $\zeta = \cV - \varPhi$. Without loss of generality, we assume that 
$\cV = 0$ thus $\zeta = -\varPhi$.
\begin{eqnarray}
\varPhi + \log\frac{C}{\gamma}&=& 0
\end{eqnarray}
Due to anion impermeability and radial flux continuity:
\begin{eqnarray}
\br \cdot \bj_- = -\deriv{C_-}{r} + C_- \deriv{\varPhi}{r} &=& 0 \\
-\deriv{C}{r} + C \deriv{\varPhi}{r} &=& 0
\end{eqnarray}

The leading-order electric potential in the Debye layer:
\begin{eqnarray}
\deriv{^2 \varphi}{\rho^2} &=& -q = -\frac{c_+ - c_-}{2} = 
-C\frac{\exp\left[+(\varPhi - \varphi)\right] - \exp\left[-(\varPhi - \varphi)\right]}{2} = 
C \sinh(\varphi - \varPhi)
\end{eqnarray}
Integrating with respect to boundary condtions yields:
\begin{eqnarray}
\deriv{\varphi}{\rho} &=& -2\sinh\frac{\varphi - \varPhi}{2} \\
\tanh\frac{\varPhi - \varphi}{4} &=& \tanh\frac{\varPhi}{4} e^{-\rho}
\end{eqnarray}

Leading-order radial momentum balance in the Debye layer yields:
\begin{eqnarray}
- \deriv{p}{\rho} + \deriv{\varphi}{\rho} \deriv{^2\varphi}{\rho^2} &=& 0
\end{eqnarray}
One integration yields:
\begin{eqnarray}
p &=& \frac{1}{2}\pars{\deriv{\varphi}{\rho}}^2
\end{eqnarray}

Leading-order tangential momentum balance in the Debye layer yields:
\begin{eqnarray}
\deriv{^2 v_\theta}{\rho^2} - \deriv{p}{\theta} 
 + \deriv{\varphi}{\theta} \deriv{^2\varphi}{\rho^2} &=& 0
\end{eqnarray}
By integrating from $\rho = 0$ to $r \rightarrow \infty$, we have Dukhin-Derjaguin slip formula
for tangential velocity component $V_\theta$ (where as the radial component is $V_r = 0$):
\begin{eqnarray}
V_\theta &=& \zeta \cdot \deriv{\varPhi}{\theta} + 
      2\log\pars{1 - \tanh^2 \frac{\zeta}{4}} \cdot \deriv{}{\theta} \log C
\end{eqnarray}

### 2011-11-27 notes/summary/ch01.tex
Fix typo of sqrt(C).
Debye-layer solution.
Split into chapters.

@@
 \subsubsection{Nernst-Planck Equations}
-The ionic fluxes are given by diffusion (Fick's law), electrostatic forces and advection by the fluid:
+The ionic fluxes are given by ions' diffusion, electrostatic forces and ions' advection by the fluid:
 \begin{eqnarray}
-\bj_+ &=& -\bnabla c_+ - c_+ \bnabla \varphi + \alpha \bv c_+ \\
-\bj_- &=& -\bnabla c_- + c_- \bnabla \varphi + \alpha \bv c_-
+ \nonumber \bj_\pm &=& -\bnabla c_+ \mp c_+ \bnabla \varphi + \alpha \bv c_\pm
 \end{eqnarray}
@@
 \begin{eqnarray}
-c &=& \frac{c_+ + c_-}{2}\\
-q &=& \frac{c_+ - c_-}{2}
+ \nonumber c &=& \frac{c_+ + c_-}{2}\\
+ \nonumber q &=& \frac{c_+ - c_-}{2}
 \end{eqnarray}
@@
 \begin{eqnarray}
-\bj &=& \frac{\bj_+ + \bj_-}{2} = -\bnabla c - q \bnabla \varphi + \alpha \bv c \\
-\bi &=& \frac{\bj_+ - \bj_-}{2} = -\bnabla q - c \bnabla \varphi + \alpha \bv q
+ \nonumber \bj &=& \frac{\bj_+ + \bj_-}{2} = -\bnabla c - q \bnabla \varphi + \alpha \bv c \\
+ \nonumber \bi &=& \frac{\bj_+ - \bj_-}{2} = -\bnabla q - c \bnabla \varphi + \alpha \bv q
 \end{eqnarray}
-
-These fluxes are also divergence-free:
+And are divergence-free as well:
 \begin{eqnarray}
@@
 \begin{eqnarray}
-Q & = & 0 \\
-C & = & C_+ = C_- \\
+ \nonumber Q & = & 0 \\
+ \nonumber C & = & C_+ = C_- \\
 \bJ &=& -\bnabla C + \alpha \bV C \\
@@
 \begin{eqnarray}
-\rho &=& \frac{r-1}{\delta} \\
+ \nonumber \rho &=& \frac{r-1}{\delta} 
 \end{eqnarray}
@@
 \begin{eqnarray}
-\varphi(\rho,\theta) &\sim& \varphi \\
-c_\pm(\rho,\theta) &\sim& c_\pm \\
-c(\rho,\theta) &\sim& c \\
-q(\rho,\theta) &\sim& q
+ \nonumber \varphi(\rho,\theta) &\sim& \varphi \\
+ \nonumber c_\pm(\rho,\theta) &\sim& c_\pm \\
+ \nonumber c(\rho,\theta) &\sim& c \\
+ \nonumber q(\rho,\theta) &\sim& q
 \end{eqnarray}
@@
 \begin{eqnarray}
-j_\pm(\rho, \theta) &\sim& \delta^{-1} j_\pm
+ \nonumber j_\pm(\rho, \theta) &\sim& \delta^{-1} j_\pm
 \end{eqnarray}
@@
 \begin{eqnarray}
-p(\rho, \theta) &\sim& \delta^{-2} p
+ \nonumber p(\rho, \theta) &\sim& \delta^{-2} p
 \end{eqnarray}
@@
 \begin{eqnarray}
--\deriv{c_\pm}{\rho} \mp c_\pm \deriv{\varphi}{\rho} &=& 0 \\
-\deriv{\varphi}{\rho} \pm\frac{1}{c_\pm}\deriv{c_\pm}{\rho} &=& 0 \\
-\pars{\varPhi - \varphi} \pm\pars{\log C_\pm - \log c_\pm} &=& 0 \\
-\varPhi - \varphi \pm \log \frac{C_\pm}{c_\pm} &=& 0
+ \nonumber -\deriv{c_\pm}{\rho} \mp c_\pm \deriv{\varphi}{\rho} &=& 0 \\
+ \nonumber \deriv{\varphi}{\rho} \pm\frac{1}{c_\pm}\deriv{c_\pm}{\rho} &=& 0 \\
+ \nonumber \pars{\varPhi - \varphi} \pm\pars{\log C_\pm - \log c_\pm} &=& 0 \\
+ \nonumber \varPhi - \varphi \pm \log \frac{C_\pm}{c_\pm} &=& 0
 \end{eqnarray}
@@
 Denote zeta potential as the voltage drop between the particle surface and the end of
-the boundary layer, $\zeta = \cV - \varPhi$. Without loss of generality, we assume that 
-$\cV = 0$ thus $\zeta = -\varPhi$.
+the boundary layer, $\zeta = \cV - \varPhi$. 
+Without loss of generality, 
+we assume that $\cV = -\log\gamma$, thus $\zeta = -\log\gamma-\varPhi$:
 \begin{eqnarray}
-\varPhi + \log\frac{C}{\gamma}&=& 0
+\varPhi &=& -\log C
 \end{eqnarray}
+
 Due to anion impermeability and radial flux continuity:
 \begin{eqnarray}
-\br \cdot \bj_- = -\deriv{C_-}{r} + C_- \deriv{\varPhi}{r} &=& 0 \\
+ \nonumber \br \cdot \bj_- = -\deriv{C_-}{r} + C_- \deriv{\varPhi}{r} &=& 0 \\
 -\deriv{C}{r} + C \deriv{\varPhi}{r} &=& 0
@@
 The leading-order electric potential in the Debye layer:
-\begin{eqnarray}
-\deriv{^2 \varphi}{\rho^2} &=& -q = -\frac{c_+ - c_-}{2} = 
+\begin{eqnarray}  \nonumber
+\deriv{^2 \varphi}{\rho^2} = -q = -\frac{c_+ - c_-}{2} = 
 -C\frac{\exp\left[+(\varPhi - \varphi)\right] - \exp\left[-(\varPhi - \varphi)\right]}{2} = 
@@
 Integrating with respect to boundary condtions yields:
-\begin{eqnarray}
-\deriv{\varphi}{\rho} &=& -2\sinh\frac{\varphi - \varPhi}{2} \\
-\tanh\frac{\varPhi - \varphi}{4} &=& \tanh\frac{\varPhi}{4} e^{-\rho}
+\begin{eqnarray}  \nonumber
+\deriv{\varphi}{\rho} &=& -2\sqrt{C}\sinh\frac{\varphi - \varPhi}{2} \\  \nonumber
+\tanh\frac{\varPhi - \varphi}{4} &=& \tanh\frac{\varPhi}{4} \exp\left\{-\rho \sqrt{C}\right\}
 \end{eqnarray}
@@
 Leading-order radial momentum balance in the Debye layer yields:
-\begin{eqnarray}
+\begin{eqnarray} \nonumber
 - \deriv{p}{\rho} + \deriv{\varphi}{\rho} \deriv{^2\varphi}{\rho^2} &=& 0
@@
 One integration yields:
-\begin{eqnarray}
+\begin{eqnarray} \nonumber
 p &=& \frac{1}{2}\pars{\deriv{\varphi}{\rho}}^2
@@
 Leading-order tangential momentum balance in the Debye layer yields:
-\begin{eqnarray}
+\begin{eqnarray} \nonumber
 \deriv{^2 v_\theta}{\rho^2} - \deriv{p}{\theta} 
@@
       2\log\pars{1 - \tanh^2 \frac{\zeta}{4}} \cdot \deriv{}{\theta} \log C 
+ = \zeta \cdot \deriv{\varPhi}{\theta} -
+      4\log\cosh \frac{\zeta}{4} \cdot \deriv{}{\theta} \log C
 \end{eqnarray}
+where $\zeta = \cV - \varPhi = -\log\gamma - \varPhi$.
+
+Note that due to boundary condition, $\log C = -\varPhi$, thus:
+\begin{eqnarray}
+V_\theta &=& \zeta \cdot \deriv{\varPhi}{\theta} + 
+      4\log\cosh \frac{\zeta}{4} \cdot \deriv{\varPhi}{\theta} = 
+4\log\pars{\frac{1 + \exp\left\{\zeta/2\right\}}{2}} \cdot \deriv{\zeta}{\theta}
+\end{eqnarray}
+
+\subsection{Steady state}
+The stress tensor is composed of Newtonian and Maxwel stresses:
+\begin{eqnarray}
+\tT &=& \bnabla \bV + (\bnabla \bV)^\dagger - P \tI
++ \bnabla \varPhi \bnabla \varPhi - \frac{1}{2} (\bnabla \varPhi \cdot \bnabla \varPhi) \tI \\
+\bnabla \cdot \tT &=& \bzero
+\end{eqnarray}
+The total force acting on the particle is computed by the following surface integral:
+\begin{eqnarray}
+\bF &=& \oint_\mathcal{S} \tT \cdot \bnhat  dA 
+\end{eqnarray}
+In steady state (constant particle drift velocity), it should be zero: $\bF = \bzero$.

### 2011-11-27 notes/summary/ch02.tex
Split into chapters.

\section{Numerics}
\subsection{Discretization}
\subsubsection{Spherical Coordinates}
Since the system has axial symmetry, the operators are written in 
spherical coordinates $(r,\theta,\phi)$:
\begin{eqnarray}
x &=& r \sin \theta \cos \phi \\
y &=& r \sin \theta \sin \phi \\
z &=& r \cos \theta
\end{eqnarray}
Due to axial symmetry, $\deriv{a}{\phi} = 0$ and $\bphihat \cdot \bA = 0$, 
so the differential operators have the following form:
\subsubsection{Grids choice}
\subsubsection{Operator Representation}
\subsubsection{Boundary Condition}
\subsection{Solver}
\subsubsection{Newton's Method}
\subsubsection{Steady-state}
\subsubsection{Continuation}

### 2011-11-29 notes/summary/ch01.tex
Discretization notes.

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Microscale}
+\subsection{Micro-scale equation}
 Denote positive and negative ionic concentration by $c_+$ and $c_-$ respectively.
@@
 Due to cation selectivity, $c_+|_{\rho=0} = \gamma$.
+\begin{eqnarray}
+ \nonumber c_+ = \gamma &=& C \exp(\varPhi - \cV) \\
+ \nonumber \cV + \log \gamma &=& \log C + \varPhi
+\end{eqnarray}
+
 Denote zeta potential as the voltage drop between the particle surface and the end of
@@
 for tangential velocity component $V_\theta$ (where as the radial component is $V_r = 0$):
-\begin{eqnarray}
+\begin{eqnarray} \nonumber
 V_\theta &=& \zeta \cdot \deriv{\varPhi}{\theta} + 
@@
 Note that due to boundary condition, $\log C = -\varPhi$, thus:
-\begin{eqnarray}
+\begin{eqnarray} \nonumber
 V_\theta &=& \zeta \cdot \deriv{\varPhi}{\theta} + 
@@
 4\log\pars{\frac{1 + \exp\left\{\zeta/2\right\}}{2}} \cdot \deriv{\zeta}{\theta}
+\end{eqnarray}
+
+Since $V_r = 0$ on the boundary, the slip condition can be written as:
+\begin{eqnarray}
+\bV &=& 
+4\log\pars{\frac{1 + \exp\left\{\zeta/2\right\}}{2}} \cdot \bnabla_S \zeta
 \end{eqnarray}
@@
 \end{eqnarray}
-In steady state (constant particle drift velocity), it should be zero: $\bF = \bzero$.
+In steady state (constant particle drift velocity $\cU$), it should be zero: $\bF = \bzero$.

### 2011-11-29 notes/summary/ch02.tex
Discretization notes.

@@
 \begin{eqnarray}
-x &=& r \sin \theta \cos \phi \\
-y &=& r \sin \theta \sin \phi \\
-z &=& r \cos \theta
+\brc{l}{
+x = r \sin \theta \cos \phi \\
+y = r \sin \theta \sin \phi \\
+z = r \cos \theta} 
 \end{eqnarray}
-Due to axial symmetry, $\deriv{a}{\phi} = 0$ and $\bphihat \cdot \bA = 0$, 
-so the differential operators have the following form:
+Due to axial symmetry, 
+so the scalar gradient and the divergence can be written as:
+\begin{eqnarray}
+\bnabla f &=& \deriv{f}{r}\brhat + \frac{1}{r}\deriv{f}{\theta}\bthetahat \\
+\bnabla \cdot \bF &=& \frac{1}{r^2}\deriv{}{r}\pars{F_r r^2 } + 
+                     \frac{1}{r \sin\theta}\deriv{}{\theta}\pars{F_\theta \sin\theta}
+\end{eqnarray}
+The scalar laplacian can be written as:
+\begin{eqnarray}
+\Laplacian f &=& \frac{1}{r^2}\deriv{}{r}\pars{r^2 \deriv{f}{r}} + 
+                     \frac{1}{r^2 \sin\theta}\deriv{}{\theta}\pars{\sin\theta \deriv{f}{\theta}}
+\end{eqnarray}
+The vector gradient can be written as:
+\begin{eqnarray}
+\bnabla \bF &=& \deriv{F_r}{r} \brhat \brhat + \deriv{F_\theta}{r} \brhat \bthetahat + 
+\frac{1}{r}\pars{\deriv{F_r}{\theta} - F_\theta} \bthetahat \brhat + 
+\frac{1}{r}\pars{\deriv{F_\theta}{\theta} + F_r} \bthetahat \bthetahat
+\end{eqnarray}
+
+The vector laplacian can be written as:
+\begin{eqnarray}
+\bLaplacian \bF &=& 
+\left(\Laplacian F_r - \frac{2F_r}{r^2} - 
+\frac{2}{r^2 \sin\theta} \deriv{\left(F_\theta \sin\theta \right)}{\theta}\right)\brhat
++ \left(\Laplacian F_\theta - \frac{F_\theta}{r^2 \sin^2\theta} + 
+\frac{2}{r^2}\deriv{F_r}{\theta}\right) \bthetahat
+\end{eqnarray}
+
 \subsubsection{Grids choice}
-\subsubsection{Operator Representation}
-\subsubsection{Boundary Condition}
+In order to discretize the differential operators, 
+a regular grid of size $N_r \times N_\theta$ is used:
+\begin{eqnarray}
+(r_i,\theta_j) &\in& [1, \infty) \times [0,\pi] \\ 
+r_i &=& (1+\Delta_r)^i \\
+\theta_j &=& \Delta_\theta \cdot j
+\end{eqnarray}
+where a logarithmic grid is used for $r$ and an uniform one is used for $\theta$.
+Note that $r_0 = 1$ and $R_{max} = (1+\Delta_r)^{N_r}$. Thus:
+\begin{eqnarray}
+\Delta_r &=& \pars{R_{max}} ^ \frac{1}{N_r} - 1 \\
+\Delta_\theta &=& \frac{\pi}{N_\theta}
+\end{eqnarray}
+
+This grid induces disjoint subdivision of the domain 
+$\Omega = [1, R_{max}] \times [0,\pi]$ into cells:
+\begin{eqnarray}
+\bigcup_{ij}\Omega_{ij} &=& \Omega
+\end{eqnarray}
+A specific cell $\Omega_{ij}$ and its center $(\bar{r}_i, \bar{\theta}_j)$ are defined by:
+\begin{eqnarray}
+\Omega_{ij} &=& [r_{i-1}, r_{i}] \times [\theta_{i-1}, \theta_{i}] \\
+\bar{r}_i &=& \frac{r_{i-1} + r_{i}}{2} \\
+\bar{\theta}_i &=& \frac{\theta_{i-1} + \theta_{i}}{2}
+\end{eqnarray}
+
+Each variable is discretized with respect of the cell:
+\begin{itemize}
+\item $\varPhi$, $C$ and $P$ are represented by their value at the center of each cell, 
+using a central grid:
+\begin{eqnarray}
+\varPhi[i,j] &=& \varPhi(\bar{r}_i, \bar{\theta}_j) \\
+C[i,j] &=& C(\bar{r}_i, \bar{\theta}_j) \\
+P[i,j] &=& P(\bar{r}_i, \bar{\theta}_j) 
+\end{eqnarray}
+\item $\bV$ is represented by its values at cell boundaries, using a staggered grid:
+\begin{eqnarray}
+V_r[i,j] &=& V_r(r_i, \bar{\theta}_j) \\
+V_\theta[i,j] &=& V_\theta(\bar{r}_i, {\theta}_j)
+\end{eqnarray}
+\end{itemize}
+
+\subsubsection{Boundary Conditions}
+The boundary conditions far away from the ion-exchange boundary ($r\rightarrow\infty$) are:
+\begin{eqnarray}
+\deriv{\varPhi}{r} &\rightarrow& -\beta \\
+C &\rightarrow& 1 \\
+V_r &\rightarrow& -\cU \cos\theta \\
+V_\theta &\rightarrow& \cU \sin\theta
+\end{eqnarray}
+The boundary conditions at the ion-exchange boundary ($r=1$) are:
+\begin{eqnarray}
+\varPhi &=& -\log C \\
+\deriv{\varPhi}{r} &=& \deriv{}{r} \log C \\
+V_r &=& 0 \\
+V_\theta &=& 4\log\pars{\frac{1 + \exp\left\{\zeta/2\right\}}{2}} \cdot \deriv{\zeta}{\theta} \\
+ \nonumber \zeta &=& \cV - \varPhi = \log C - \log \gamma
+\end{eqnarray}
+
 \subsection{Solver}

### 2011-12-02 notes/summary/ch01.tex
Solver docs.

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Micro-scale equation}
+\subsection{Micro-scale phenomena}
 Denote positive and negative ionic concentration by $c_+$ and $c_-$ respectively.
@@
 
-\subsection{Debye-scale effective boundary conditions}
+\subsubsection{Debye-scale effective boundary conditions}
 We define the rescaled coordinate $\rho$ (normal to ion-exchanger surface), where $\delta \ll 1$:

### 2011-12-02 notes/summary/ch02.tex
Solver docs.

@@
 \section{Numerics}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Discretization}
@@
 \begin{eqnarray}
-\Laplacian f &=& \frac{1}{r^2}\deriv{}{r}\pars{r^2 \deriv{f}{r}} + 
+\Laplacian f = \bnabla \cdot (\bnabla f)&=& 
+ \frac{1}{r^2}\deriv{}{r}\pars{r^2 \deriv{f}{r}} + 
  \frac{1}{r^2 \sin\theta}\deriv{}{\theta}\pars{\sin\theta \deriv{f}{\theta}}
@@
 In order to discretize the differential operators, 
-a regular grid of size $N_r \times N_\theta$ is used:
+a regular grid of size $n_r \times n_\theta$ is used:
 \begin{eqnarray}
@@
 where a logarithmic grid is used for $r$ and an uniform one is used for $\theta$.
-Note that $r_0 = 1$ and $R_{max} = (1+\Delta_r)^{N_r}$. Thus:
+Note that $r_0 = 1$ and $R_{max} = (1+\Delta_r)^{n_r}$. Thus:
 \begin{eqnarray}
-\Delta_r &=& \pars{R_{max}} ^ \frac{1}{N_r} - 1 \\
-\Delta_\theta &=& \frac{\pi}{N_\theta}
+\Delta_r &=& \pars{R_{max}} ^ \frac{1}{n_r} - 1 \\
+\Delta_\theta &=& \frac{\pi}{n_\theta}
 \end{eqnarray}
@@
 
+\subsubsection{Operator Discretization}
+Finite-volume method with linear interpolation between grids is used for flux 
+$\boldsymbol{f}$ discretization.
+
+Denote the following discrete central difference operators:
+\begin{eqnarray}
+\cD_r(f)[i,j] &=& \frac{f\left[i+\half,j\right] - f\left[i-\half,j\right]}
+                       {r\left[i+\half,j\right] - r\left[i-\half,j\right]} \\
+\cD_\theta(f)[i,j] &=& \frac{f\left[i,j+\half\right] - f\left[i,j-\half\right]}
+					   {\theta\left[i,j+\half\right] - \theta\left[i,j-\half\right]}
+\end{eqnarray}
+
+Denote the following interpolation operators:
+\begin{eqnarray}
+\cI_r(f)[i,j] &=& \frac{
+\pars{r\left[i,j\right] - r\left[i-\half,j\right]} 
+  f\left[i+\half,j\right] + 
+\pars{r\left[i+\half,j\right] - r\left[i,j\right]} 
+  f\left[i-\half,j\right] 
+}{r\left[i+\half,j\right] - r\left[i-\half,j\right]}
+\\
+\cI_\theta(f)[i,j] &=& 
+\frac{
+\pars{r\left[i,j\right] - r\left[i,j-\half\right]} 
+  f\left[i,j+\half\right] + 
+\pars{r\left[i,j+\half\right] - r\left[i,j\right]} 
+  f\left[i,j-\half\right] 
+}{r\left[i,j+\half\right] - r\left[i,j-\half\right]}
+\end{eqnarray}
+
+The total flux of a cell is equal to zero (due to conservation):
+\begin{eqnarray}
+\bnabla \cdot \boldsymbol{f} &=& 0 
+\\
+\frac{1}{r^2} \cD_r\pars{f_r r^2} + 
+\frac{1}{r \sin\theta} \cD_\theta\pars{f_\theta \sin\theta} &=& 0 
+\\
+\cD_r\pars{f_r \cdot r^2 \sin\theta} + \cD_\theta\pars{f_\theta \cdot r \sin\theta} &=& 0 
+\end{eqnarray}
+
+Ion flux are discretized on grid cells' boundaries:
+\begin{eqnarray}
+I_r &=& -\cI_r(C) \cdot \cD_r(\varPhi) \\
+I_\theta &=& -\cI_\theta(C) \cdot \frac{\cD_\theta(\varPhi)}{r} 
+\end{eqnarray}
+
+Salt flux are discretized on grid cells' boundaries 
+(using upwind scheme $\mathcal{U}$ for numerical stability at large cell Peclet number):
+\begin{eqnarray}
+J_r &=& -\cD_r(C) + \alpha V_r \cdot \mathcal{U}^{\bV}_r (C) \\
+J_\theta &=& -\frac{\cD_\theta(C)}{r} + \alpha V_\theta \cdot \mathcal{U}^{\bV}_\theta (C) \\
+\nonumber \mathcal{U}^{\bV}_r(C)[i,j] &=& C\left[i-\frac{\sign(V_r)}{2}, j\right] \\
+\nonumber \mathcal{U}^{\bV}_\theta(C)[i,j] &=& C\left[i, j-\frac{\sign(V_\theta)}{2}\right] 
+\end{eqnarray}
+
+Mass flux $\bV$ is discretized on grid cells boundaries, 
+using velocity staggered grid.
+
+Force components are discretized on velocity staggered grid, where
+linear interpolation is used for Coulomb force.
+\begin{eqnarray}
+F_r &=& -\cD_r(P) 
+          + \cL(V_r) - \frac{2}{r^2} V_r 
+		  - \frac{2}{r^2 \sin\theta} \cI_r(\cD_\theta (V_\theta \sin\theta))
+          + \cD_r(\varPhi) \cdot \cI_r(\cL(\varPhi)) \\
+F_\theta &=& -\frac{\cD_\theta(P)}{r} 
+		  + \cL(V_\theta) - \frac{F_\theta}{r^2 \sin^2\theta} 
+		  + \frac{2}{r^2} \cI_\theta(\cD_\theta(F_r))
+		  + \frac{\cD_\theta(\varPhi)}{r} \cdot \cI_\theta(\cL(\varPhi)) \\
+\nonumber
+\cL(f) &=& \frac{1}{r^2}\cD_r\pars{\cD_r(f) r^2} + 
+\frac{1}{r^2 \sin\theta} \cD_\theta\pars{\cD_\theta(f) \cdot \sin\theta}
+\end{eqnarray}
+
 \subsubsection{Boundary Conditions}
-The boundary conditions far away from the ion-exchange boundary ($r\rightarrow\infty$) are:
-\begin{eqnarray}
-\deriv{\varPhi}{r} &\rightarrow& -\beta \\
-C &\rightarrow& 1 \\
-V_r &\rightarrow& -\cU \cos\theta \\
-V_\theta &\rightarrow& \cU \sin\theta
-\end{eqnarray}
+In order to represent discretize problem boundary condtions, 
+``ghost'' points method is used. 
+Variable grid is extended to include points outside the domain's interior,
+so the variables at the ``ghost'' points are set to satisfy 
+the discretized boundary conditions, following the analysis below.
+
 The boundary conditions at the ion-exchange boundary ($r=1$) are:
 \begin{eqnarray}
-\varPhi &=& -\log C \\
-\deriv{\varPhi}{r} &=& \deriv{}{r} \log C \\
+\cI_r(\varPhi) &=& -\cI_r(\log C) \\
+\cD_r(\varPhi) &=& \cD_r(\log C) \\
 V_r &=& 0 \\
-V_\theta &=& 4\log\pars{\frac{1 + \exp\left\{\zeta/2\right\}}{2}} \cdot \deriv{\zeta}{\theta} \\
- \nonumber \zeta &=& \cV - \varPhi = \log C - \log \gamma
+V_\theta &=& 4\log\pars{\frac{1 + \exp\left\{\cI_\theta(\zeta)/2\right\}}{2}} \cdot 
+			\cD_\theta(\zeta) \\
+ \nonumber \zeta &=& - \log \gamma - \cI_r(\varPhi)
+\end{eqnarray}
+The equations are discretized by using ``ghost'' points, outside the interior of the domain:
+\begin{eqnarray}
+ \nonumber \frac{\varPhi[0,j] + \varPhi[1,j]}{2} &=& 
+	-\frac{\log C[0,j] + \log C[1,j]}{2} \\
+ \nonumber \frac{\varPhi[1,j] - \varPhi[0,j]}{\Delta r} &=& 
+	\frac{\log C[1,j] - \log C[0,j]}{\Delta r} 
+\end{eqnarray}
+By adding and subtracting the equations, we have:
+\begin{eqnarray}
+\varPhi[0,j] &=& -\log\brcs{C[1,j]} \\
+C[0,j] &=& \exp\brcs{-\varPhi[1,j]} \\
+ \nonumber \zeta[j] &=& \cV -\frac{\varPhi[0,j] + \varPhi[1,j]}{2} 
+                     = -\log\gamma -\frac{\varPhi[0,j] + \varPhi[1,j]}{2}
+\end{eqnarray}
+The slipping conditions can be written by:
+\begin{eqnarray}
+V_r[0,j] &=& 0 \\
+\frac{V_\theta[0,j] + V_\theta[1,j]}{2} &=& V_\theta[j] = 
+4\log\pars{\frac{1 + \exp\left\{\frac{1}{2}\frac{\zeta[j] + \zeta[j+1]}{2}\right\}}{2}} 
+\cdot \frac{\zeta[j+1] - \zeta[j]}{\bar{\theta}_{j+1} - \bar{\theta}_{j}} \\
+ \nonumber V_\theta[0,j] &=& 2 V_\theta[j] - V_\theta[1,j]
 \end{eqnarray}
 
-\subsection{Solver}
-\subsubsection{Newton's Method}
+For $\theta = 0$ and $\theta = \pi$, the ``ghost'' points are defined by:
+\begin{eqnarray} 
+\brc{l}{
+\varPhi[i, 0] = \varPhi[i, 1] \\
+C[i, 0] = C[i, 1] \\
+V_r[i, 0] = V_r[i, 1] \\
+V_\theta[i, 0] = 0
+} 
+\brc{l}{
+\varPhi[i, n_\theta+1] = \varPhi[i, n_\theta] \\
+C[i, n_\theta+1] = C[i, n_\theta] \\
+V_r[i, n_\theta+1] = V_r[i, n_\theta] \\
+V_\theta[i, n_\theta+1] = 0
+} 
+\end{eqnarray}
+
+Far away from the ion-exchange boundary ($r\rightarrow\infty$) are:
+\begin{eqnarray}
+\frac{\varPhi[n_r + 1, j] - \varPhi[n_r, j]}{\bar{r}_{n_r + 1} - \bar{r}_{n_r}} 
+ & = & -\beta \cos\bar{\theta}_j \\
+C[n_r + 1, j] & = & 1 \\
+V_r[n_r + 1, j] & = & -\cU \cos\bar{\theta}_j \\
+V_\theta[n_r + 1, j] & = & \cU \sin\theta_j
+\end{eqnarray}
+Since the actual grid is finite, $r_{n_r} = R_{max}$ will have an effect on the solution too.
+
+Note that $P$ has no boundary conditions -- so the pressure variable is defined 
+on the domain's interior.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Solver Design}
+\subsubsection{Newton Method}
+An operator $\cO$ is defined by its input vector $\bx$ and its output 
+$\by = \cO(\bx)$ is defined on a grid $\cG$.
+
+Using an algebra of operators, the composition of operators is well defined:
+\begin{eqnarray}
+(\cO_1 \circ \cO_2)(\bx) &=& \cO_1(\cO_2(\bx))
+\end{eqnarray}
+Note that the differentiation of composed operators is computed using chain rule:
+\begin{eqnarray}
+\bnabla(\cO_1 \circ \cO_2)(\bx) &=& \bnabla \cO_1(\cO_2(\bx)) \cdot \bnabla \cO_2(\bx)
+\end{eqnarray}
+
+Thus, in order to solve the equation $\cO(\bx) = \bzero$, a Newton step can 
+be computed by:
+\begin{eqnarray}
+\bzero = \cO(\bx_n + \Delta \bx_n) &\approx& \cO(\bx_n) + \bnabla \cO(\bx_n)\cdot\Delta\bx_n \\
+\bnabla \cO(\bx_n) \cdot \Delta \bx_n &=& -\cO(\bx_n) \\
+\bx_{n+1} &=& \bx_{n} + \Delta \bx_n \rightarrow
+\end{eqnarray}
+
+Therefore, in order to apply Newton method, the residual vector $\cO(\bx)$ and
+the gradient matrix of the operator $\bnabla \cO(\bx)$ are to be computed.
+Then, a sparse linear system is to be solved to yield current step vector $\Delta \bx$.
+
+When the method converges $\bx_n \rightarrow \bx_\infty$, 
+the convergence is quadratic:
+\begin{eqnarray}
+\|\bx_{n+1} - \bx_\infty\| \le c\|\bx_{n} - \bx_\infty\|^2
+\end{eqnarray}
+Thus, when the initial guess is close enough to the solution, the solver
+will converge in very few steps.
+
+\subsubsection{Operator Representation}
+System variable $\bx$ is defined as the concatenation $[\,\varPhi, C, V_r, V_\theta, P\,]$,
+taking values in the interior of the problem domain grid.
+
+Thus, each problem variable can be computed by applying an appropriate projection operator:
+\begin{eqnarray}
+X &=& \cP_X(\bx) \mbox{ for } X \in \left\{\varPhi, C, V_r, V_\theta, P\right\}
+\end{eqnarray}
+
+The extended variables $\tilde X$ (with ``ghost'' points values 
+from boundary conditions) are be computed, by applying the following non-linear operators:
+\begin{eqnarray}
+\tilde{\varPhi} &=& \cB_\varPhi(\varPhi, C; \beta) \\
+\tilde{C} &=& \cB_C(C, \varPhi) \\
+\tilde{V_r} &=& \cB_{V_r}(V_r; \cU) \\
+\tilde{V_\theta} &=& \cB_{V_\theta}(V_\theta, C, \varPhi; \cU, \gamma) \\
+\tilde{P} &=& P
+\end{eqnarray}
+
+The equations of the system (as described above) can be written as non-linear 
+operators acting on the extended variables:
+\begin{eqnarray}
+0 &=& \cE_I (\tilde\varPhi, \tilde C) \mbox{ -- conservation of charge} \\
+0 &=& \cE_J (\tilde C, \tilde\bV; \alpha) \mbox{ -- conservation of salt} \\
+0 &=& \cE_M (\tilde\bV) \mbox{ -- conservation of mass} \\
+0 &=& \cE_{\boldsymbol{p}} (\tilde\bV, \tilde P, \tilde\varPhi) 
+\mbox{ -- conservation of momentum}
+\end{eqnarray}
+The problem can be casted as solving $\cO(\bx) = \bzero$ for $\cO = \cE \circ \cB$,
+where $\cB$ is the ``ghost'' point extension operator and $\cE$ is the conservation
+equations operator.
+
 \subsubsection{Steady-state}
+After convergence, the ``ghost'' points values are updated using $\cB$,
+so the force $\tT \cdot \bn$ acting on the ion-exchanger surface
+can be computed.
+
+Due to symmetry considerations, the total force $\bF$ is 
+aligned with $\ui$ and it vanishes iff $\ui \cdot \bF = 0$.
+\begin{eqnarray}
+F_\imath = \ui \cdot \bF &=& \oint_\mathcal{S} \ui \cdot \tT \cdot \bnhat  dA = 
+\int_0^\pi f_\imath(\theta) \cdot 2\pi \sin\theta d\theta 
+\\ \nonumber 
+f_\imath &=& \pars{-P + 2\cD_r(V_r) + 
+\frac{1}{2}\pars{\cD_r(\varPhi)}^2 - \frac{1}{2r^2}\pars{\cD_\theta(\varPhi)}^2}\cos\theta 
+\\ \nonumber 
+&& -\pars{\cD_r(V_\theta) - \frac{V_\theta}{r}
++ \frac{1}{r}\cD_r(\varPhi) \cD_{\theta}(\varPhi)}\sin\theta
+\end{eqnarray}
+
+The integral above is approximated by 1D numerical quadrature, to yield 
+the total force $F_\imath$ as a function of steady-state drift velocity $\cU$.
+In order to solve for steady state, Secant method is applied to find
+the root of $F_\imath(\cU) = 0$, given the problem parameters $\alpha, \beta, \gamma$.
+
 \subsubsection{Continuation}
+
+System steady-state drift velocity $\cU(\beta)$ is computed as a function 
+of the electric field magnitude for many values of $\beta$.
+Since the solution $\bx_\infty$ is continous in $\beta$, the results from previous 
+iteration are used as an initial solution $\bx_0$ for the problem of new $\beta$ 
+-- helping Newton Method convergence.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Solver Implementation}

### 2011-12-02 notes/summary/ch01.tex
Solver docs.

@@
 \begin{eqnarray}
- \nonumber \bj_\pm &=& -\bnabla c_+ \mp c_+ \bnabla \varphi + \alpha \bv c_\pm
+  \bj_\pm &=& -\bnabla c_+ \mp c_+ \bnabla \varphi + \alpha \bv c_\pm
 \end{eqnarray}
@@
 \begin{eqnarray}
- \nonumber c &=& \frac{c_+ + c_-}{2}\\
- \nonumber q &=& \frac{c_+ - c_-}{2}
+  c &=& \frac{c_+ + c_-}{2}\\
+  q &=& \frac{c_+ - c_-}{2}
 \end{eqnarray}
@@
 \begin{eqnarray}
- \nonumber \bj &=& \frac{\bj_+ + \bj_-}{2} = -\bnabla c - q \bnabla \varphi + \alpha \bv c \\
- \nonumber \bi &=& \frac{\bj_+ - \bj_-}{2} = -\bnabla q - c \bnabla \varphi + \alpha \bv q
+  \bj &=& \frac{\bj_+ + \bj_-}{2} = -\bnabla c - q \bnabla \varphi + \alpha \bv c \\
+  \bi &=& \frac{\bj_+ - \bj_-}{2} = -\bnabla q - c \bnabla \varphi + \alpha \bv q
 \end{eqnarray}
@@
 \begin{eqnarray}
- \nonumber Q & = & 0 \\
- \nonumber C & = & C_+ = C_- \\
+  Q & = & 0 \\
+  C & = & C_+ = C_- \\
 \bJ &=& -\bnabla C + \alpha \bV C \\
@@
 \begin{eqnarray}
- \nonumber \rho &=& \frac{r-1}{\delta} 
+  \rho &=& \frac{r-1}{\delta} 
 \end{eqnarray}
@@
 \begin{eqnarray}
- \nonumber \varphi(\rho,\theta) &\sim& \varphi \\
- \nonumber c_\pm(\rho,\theta) &\sim& c_\pm \\
- \nonumber c(\rho,\theta) &\sim& c \\
- \nonumber q(\rho,\theta) &\sim& q
+  \varphi(\rho,\theta) &\sim& \varphi \\
+  c_\pm(\rho,\theta) &\sim& c_\pm \\
+  c(\rho,\theta) &\sim& c \\
+  q(\rho,\theta) &\sim& q
 \end{eqnarray}
@@
 \begin{eqnarray}
- \nonumber j_\pm(\rho, \theta) &\sim& \delta^{-1} j_\pm
+  j_\pm(\rho, \theta) &\sim& \delta^{-1} j_\pm
 \end{eqnarray}
@@
 \begin{eqnarray}
- \nonumber p(\rho, \theta) &\sim& \delta^{-2} p
+  p(\rho, \theta) &\sim& \delta^{-2} p
 \end{eqnarray}
@@
 \begin{eqnarray}
- \nonumber -\deriv{c_\pm}{\rho} \mp c_\pm \deriv{\varphi}{\rho} &=& 0 \\
- \nonumber \deriv{\varphi}{\rho} \pm\frac{1}{c_\pm}\deriv{c_\pm}{\rho} &=& 0 \\
- \nonumber \pars{\varPhi - \varphi} \pm\pars{\log C_\pm - \log c_\pm} &=& 0 \\
- \nonumber \varPhi - \varphi \pm \log \frac{C_\pm}{c_\pm} &=& 0
+  -\deriv{c_\pm}{\rho} \mp c_\pm \deriv{\varphi}{\rho} &=& 0 \\
+  \deriv{\varphi}{\rho} \pm\frac{1}{c_\pm}\deriv{c_\pm}{\rho} &=& 0 \\
+  \pars{\varPhi - \varphi} \pm\pars{\log C_\pm - \log c_\pm} &=& 0 \\
+  \varPhi - \varphi \pm \log \frac{C_\pm}{c_\pm} &=& 0
 \end{eqnarray}
@@
 \begin{eqnarray}
- \nonumber c_+ = \gamma &=& C \exp(\varPhi - \cV) \\
- \nonumber \cV + \log \gamma &=& \log C + \varPhi
+  c_+ = \gamma &=& C \exp(\varPhi - \cV) \\
+  \cV + \log \gamma &=& \log C + \varPhi
 \end{eqnarray}
@@
 \begin{eqnarray}
- \nonumber \br \cdot \bj_- = -\deriv{C_-}{r} + C_- \deriv{\varPhi}{r} &=& 0 \\
+  \br \cdot \bj_- = -\deriv{C_-}{r} + C_- \deriv{\varPhi}{r} &=& 0 \\
 -\deriv{C}{r} + C \deriv{\varPhi}{r} &=& 0
@@
 The leading-order electric potential in the Debye layer:
-\begin{eqnarray}  \nonumber
+\begin{eqnarray}  
 \deriv{^2 \varphi}{\rho^2} = -q = -\frac{c_+ - c_-}{2} = 
@@
 \end{eqnarray}
+Denote $\psi = \varphi - \varPhi$, such that $\psi(0) = \zeta$ and 
+$\psi(\rho\rightarrow\infty) = 0$.
+\begin{eqnarray}  
+\deriv{^2 \psi}{\rho^2} &=& C \sinh(\psi) = 2 C \sinh{\frac{\psi}{2}}\cosh{\frac{\psi}{2}} 
+\\
+2\deriv{\psi}{\rho} \deriv{^2 \psi}{\rho^2} &=& 
+4 C \sinh{\frac{\psi}{2}}\cosh{\frac{\psi}{2}} \deriv{\psi}{\rho} 
+\\
+\deriv{}{\rho} \pars{\deriv{\psi}{\rho}}^2 &=& 
+\deriv{}{\rho} \pars{2 \sqrt{C} \sinh{\frac{\psi}{2}}}^2 
+\end{eqnarray}
+
 Integrating with respect to boundary condtions yields:
-\begin{eqnarray}  \nonumber
-\deriv{\varphi}{\rho} &=& -2\sqrt{C}\sinh\frac{\varphi - \varPhi}{2} \\  \nonumber
-\tanh\frac{\varPhi - \varphi}{4} &=& \tanh\frac{\varPhi}{4} \exp\left\{-\rho \sqrt{C}\right\}
+\begin{eqnarray}  
+\deriv{\psi}{\rho} &=& -2\sqrt{C}\sinh\frac{\psi}{2} \\  
+\pars{4\sinh\frac{\psi}{4}\cosh\frac{\psi}{4}}^{-1}\deriv{\psi}{\rho} &=& -\sqrt{C} \\  
+\frac{\pars{\tanh\frac{\psi}{4}}^{-1}}{4\cosh^2\frac{\psi}{4}}
+\deriv{\psi}{\rho} &=& -\sqrt{C} \\  
+\deriv{}{\rho}\pars{\log\tanh\frac{\psi}{4}} &=& \deriv{}{\rho}\pars{-\rho \sqrt{C}} \\
+\log\tanh\frac{\psi}{4} - \log\tanh\frac{\zeta}{4} &=& -\rho \sqrt{C} \\
+\psi &=& 4 \tanh^{-1}\pars{\tanh{\frac{\zeta}{4}} \cdot \exp\pars{-\rho \sqrt{C}}}
 \end{eqnarray}
@@
 Leading-order radial momentum balance in the Debye layer yields:
-\begin{eqnarray} \nonumber
+\begin{eqnarray} 
 - \deriv{p}{\rho} + \deriv{\varphi}{\rho} \deriv{^2\varphi}{\rho^2} &=& 0
@@
 One integration yields:
-\begin{eqnarray} \nonumber
+\begin{eqnarray} 
 p &=& \frac{1}{2}\pars{\deriv{\varphi}{\rho}}^2
@@
 Leading-order tangential momentum balance in the Debye layer yields:
-\begin{eqnarray} \nonumber
-\deriv{^2 v_\theta}{\rho^2} - \deriv{p}{\theta} 
- + \deriv{\varphi}{\theta} \deriv{^2\varphi}{\rho^2} &=& 0
+\begin{eqnarray} 
+0 &=& \deriv{^2 v_\theta}{\rho^2} - \deriv{p}{\theta} 
+ + \deriv{\varphi}{\theta} \deriv{^2\varphi}{\rho^2} 
+\\
+\deriv{^2 v_\theta}{\rho^2} &=& \frac{1}{2}\deriv{}{\theta}\pars{\deriv{\psi}{\rho}}^2
+- \deriv{(\varPhi + \psi)}{\theta} \deriv{^2\psi}{\rho^2}  
+\\
+ &=& \deriv{}{\theta}\pars{2C \sinh^2\frac{\psi}{2}}
+- \deriv{\psi}{\theta} C \sinh\psi
+- \deriv{\varPhi}{\theta} \deriv{^2\psi}{\rho^2}  
+\\
+ &=& \deriv{}{\theta}\pars{C \pars{\cosh\psi - 1}}
+- C \sinh\psi \deriv{\psi}{\theta}
+- \deriv{\varPhi}{\theta} \deriv{^2\psi}{\rho^2}  
+\\
+ &=& \deriv{C}{\theta} \pars{\cosh\psi - 1}
+- \deriv{\varPhi}{\theta} \deriv{^2\psi}{\rho^2}  
+ = \deriv{C}{\theta} \pars{2 \sinh^2 \frac{\psi}{2}}
+- \deriv{\varPhi}{\theta} \deriv{^2\psi}{\rho^2}  
+\\
+ &=& -\deriv{C}{\theta} \frac{2}{\sqrt{C}} \pars{\half \sinh \frac{\psi}{2} \deriv{\psi}{\rho}}
+- \deriv{\varPhi}{\theta} \deriv{^2\psi}{\rho^2}  
+ = -\deriv{C}{\theta} \frac{2}{\sqrt{C}} \deriv{}{\rho}\pars{\cosh \frac{\psi}{2}}
+- \deriv{\varPhi}{\theta} \deriv{^2\psi}{\rho^2}  
 \end{eqnarray}
-By integrating from $\rho = 0$ to $r \rightarrow \infty$, we have Dukhin-Derjaguin slip formula
-for tangential velocity component $V_\theta$ (where as the radial component is $V_r = 0$):
-\begin{eqnarray} \nonumber
-V_\theta &=& \zeta \cdot \deriv{\varPhi}{\theta} + 
-      2\log\pars{1 - \tanh^2 \frac{\zeta}{4}} \cdot \deriv{}{\theta} \log C 
- = \zeta \cdot \deriv{\varPhi}{\theta} -
-      4\log\cosh \frac{\zeta}{4} \cdot \deriv{}{\theta} \log C
+By integrating from specific $\rho$ to $\rho \rightarrow \infty$:
+\begin{eqnarray}
+\deriv{v_\theta}{\rho} &=& -\deriv{C}{\theta} \frac{2}{\sqrt{C}} 
+\pars{\cosh \frac{\psi}{2} - 1} - \deriv{\varPhi}{\theta} \deriv{\psi}{\rho}   
+= -\deriv{C}{\theta} \frac{4}{\sqrt{C}} \sinh^2 \frac{\psi}{4} 
+  - \deriv{\varPhi}{\theta} \deriv{\psi}{\rho}   
 \end{eqnarray}
-where $\zeta = \cV - \varPhi = -\log\gamma - \varPhi$.
-
-Note that due to boundary condition, $\log C = -\varPhi$, thus:
-\begin{eqnarray} \nonumber
-V_\theta &=& \zeta \cdot \deriv{\varPhi}{\theta} + 
-      4\log\cosh \frac{\zeta}{4} \cdot \deriv{\varPhi}{\theta} = 
-4\log\pars{\frac{1 + \exp\left\{\zeta/2\right\}}{2}} \cdot \deriv{\zeta}{\theta}
+Note that:
+\begin{eqnarray}
+\deriv{\psi}{\rho} &=& -2\sqrt{C}\sinh\frac{\psi}{2} = 
+                       -4\sqrt{C}\sinh\frac{\psi}{4}\cosh\frac{\psi}{4}
+\\
+-4\sinh\frac{\psi}{4} &=& \frac{1}{\sqrt{C} \cosh\frac{\psi}{4}} \deriv{\psi}{\rho}
+\end{eqnarray}
+Thus:
+\begin{eqnarray}
+\deriv{v_\theta}{\rho} &=& 
+  \pars{\deriv{C}{\theta} \frac{1}{C}} \cdot
+  \pars{\frac{\sinh\frac{\psi}{4}}{\cosh\frac{\psi}{4}} \deriv{\psi}{\rho}}
+  - \deriv{\varPhi}{\theta} \deriv{\psi}{\rho}
+=  4\deriv{}{\rho} \pars{\log\cosh\frac{\psi}{4}} \deriv{}{\theta} \log C
+  - \deriv{\psi}{\rho} \deriv{\varPhi}{\theta}
 \end{eqnarray}
 
-Since $V_r = 0$ on the boundary, the slip condition can be written as:
+By integrating from $\rho = 0$ to $\rho \rightarrow \infty$, 
+we have Dukhin-Derjaguin slip formula for tangential velocity component $V_\theta$ 
+(where the radial component is $V_r = 0$):
+\begin{eqnarray} 
+V_\theta &=& \zeta \cdot \deriv{\varPhi}{\theta} -
+      4\log\cosh \frac{\zeta}{4} \cdot \deriv{}{\theta} \log C 
+\\
+&=& \zeta \cdot \deriv{\varPhi}{\theta} + 
+      2\log\pars{1 - \tanh^2 \frac{\zeta}{4}} \cdot \deriv{}{\theta} \log C 
+\end{eqnarray}
+where $\zeta = \cV - \varPhi$.
+
+Since $V_r = 0$ on the boundary, the slip condition can be written using surface
+gradient operator:
 \begin{eqnarray}
 \bV &=& 
-4\log\pars{\frac{1 + \exp\left\{\zeta/2\right\}}{2}} \cdot \bnabla_S \zeta
+\zeta \cdot \bnabla_\mathcal{S} \varPhi 
++ 2\log\pars{1-\tanh^2\frac{\zeta}{4}} \cdot \bnabla_\mathcal{S} \log C \\
+\bnabla_\mathcal{S} &=& \pars{\tI - \bn\bn} \bnabla
 \end{eqnarray}

### 2011-12-02 notes/summary/ch02.tex
Solver docs.

@@
-\section{Numerics}
+\section{Numerical Solver}
 
@@
 J_\theta &=& -\frac{\cD_\theta(C)}{r} + \alpha V_\theta \cdot \mathcal{U}^{\bV}_\theta (C) \\
-\nonumber \mathcal{U}^{\bV}_r(C)[i,j] &=& C\left[i-\frac{\sign(V_r)}{2}, j\right] \\
-\nonumber \mathcal{U}^{\bV}_\theta(C)[i,j] &=& C\left[i, j-\frac{\sign(V_\theta)}{2}\right] 
+ \mathcal{U}^{\bV}_r(C)[i,j] &=& C\left[i-\frac{\sign(V_r)}{2}, j\right] \\
+ \mathcal{U}^{\bV}_\theta(C)[i,j] &=& C\left[i, j-\frac{\sign(V_\theta)}{2}\right] 
 \end{eqnarray}
@@
 		  + \frac{\cD_\theta(\varPhi)}{r} \cdot \cI_\theta(\cL(\varPhi)) \\
-\nonumber
 \cL(f) &=& \frac{1}{r^2}\cD_r\pars{\cD_r(f) r^2} + 
@@
 			\cD_\theta(\zeta) \\
- \nonumber \zeta &=& - \log \gamma - \cI_r(\varPhi)
+  \zeta &=& - \log \gamma - \cI_r(\varPhi)
 \end{eqnarray}
@@
 \begin{eqnarray}
- \nonumber \frac{\varPhi[0,j] + \varPhi[1,j]}{2} &=& 
+  \frac{\varPhi[0,j] + \varPhi[1,j]}{2} &=& 
 	-\frac{\log C[0,j] + \log C[1,j]}{2} \\
- \nonumber \frac{\varPhi[1,j] - \varPhi[0,j]}{\Delta r} &=& 
+  \frac{\varPhi[1,j] - \varPhi[0,j]}{\Delta r} &=& 
 	\frac{\log C[1,j] - \log C[0,j]}{\Delta r} 
@@
 C[0,j] &=& \exp\brcs{-\varPhi[1,j]} \\
- \nonumber \zeta[j] &=& \cV -\frac{\varPhi[0,j] + \varPhi[1,j]}{2} 
+  \zeta[j] &=& \cV -\frac{\varPhi[0,j] + \varPhi[1,j]}{2} 
                      = -\log\gamma -\frac{\varPhi[0,j] + \varPhi[1,j]}{2}
@@
 \cdot \frac{\zeta[j+1] - \zeta[j]}{\bar{\theta}_{j+1} - \bar{\theta}_{j}} \\
- \nonumber V_\theta[0,j] &=& 2 V_\theta[j] - V_\theta[1,j]
+  V_\theta[0,j] &=& 2 V_\theta[j] - V_\theta[1,j]
 \end{eqnarray}
@@
 An operator $\cO$ is defined by its input vector $\bx$ and its output 
-$\by = \cO(\bx)$ is defined on a grid $\cG$.
+$\by = \cO(\bx)$.
 
@@
 \bnabla \cO(\bx_n) \cdot \Delta \bx_n &=& -\cO(\bx_n) \\
-\bx_{n+1} &=& \bx_{n} + \Delta \bx_n \rightarrow
+\bx_{n+1} &=& \bx_{n} + \Delta \bx_n 
 \end{eqnarray}
@@
 \begin{eqnarray}
-\|\bx_{n+1} - \bx_\infty\| \le c\|\bx_{n} - \bx_\infty\|^2
+\|\bx_{n+1} - \bx_\infty\| \le \|\bx_{n} - \bx_\infty\|^2
 \end{eqnarray}
@@
 
-The equations of the system (as described above) can be written as non-linear 
-operators acting on the extended variables:
-\begin{eqnarray}
-0 &=& \cE_I (\tilde\varPhi, \tilde C) \mbox{ -- conservation of charge} \\
-0 &=& \cE_J (\tilde C, \tilde\bV; \alpha) \mbox{ -- conservation of salt} \\
-0 &=& \cE_M (\tilde\bV) \mbox{ -- conservation of mass} \\
-0 &=& \cE_{\boldsymbol{p}} (\tilde\bV, \tilde P, \tilde\varPhi) 
-\mbox{ -- conservation of momentum}
-\end{eqnarray}
+The concatenated equations of the system (as described above) can be written 
+as a non-linear operator $\cE(\tilde\bx) = \bzero$ acting on the extended variables $\tilde\bx = \cB(\bx)$:
 The problem can be casted as solving $\cO(\bx) = \bzero$ for $\cO = \cE \circ \cB$,
-where $\cB$ is the ``ghost'' point extension operator and $\cE$ is the conservation
-equations operator.
+where $\cB$ is the ``ghost'' point extension operator (derived using boundary conditions) 
+and $\cE$ is the conservation equations operator (derived by concatenation of the system
+equations).
 
@@
 \int_0^\pi f_\imath(\theta) \cdot 2\pi \sin\theta d\theta 
-\\ \nonumber 
+\\  
+f_\imath &=& \imath \cdot \tT \cdot \bnhat
+\\  
 f_\imath &=& \pars{-P + 2\cD_r(V_r) + 
 \frac{1}{2}\pars{\cD_r(\varPhi)}^2 - \frac{1}{2r^2}\pars{\cD_\theta(\varPhi)}^2}\cos\theta 
-\\ \nonumber 
+\\  
 && -\pars{\cD_r(V_\theta) - \frac{V_\theta}{r}
-+ \frac{1}{r}\cD_r(\varPhi) \cD_{\theta}(\varPhi)}\sin\theta
++ \frac{1}{r}\cD_r(\varPhi) \cD_{\theta}(\varPhi)}\sin\theta \\
+ \mathcal{S} &=& \{\br : \|\br\|_2 = 1\}
 \end{eqnarray}
@@
 The integral above is approximated by 1D numerical quadrature, to yield 
-the total force $F_\imath$ as a function of steady-state drift velocity $\cU$.
-In order to solve for steady state, Secant method is applied to find
-the root of $F_\imath(\cU) = 0$, given the problem parameters $\alpha, \beta, \gamma$.
+the total force $F_\imath$ as a function of the drift velocity $\cU$.
+
+Since the goal is to find steady-state solution, $F_\imath(\cU)$ is required to be zero --
+and the appropriate $\cU$ is found by 1D root-finding algorithm.
 
@@
 System steady-state drift velocity $\cU(\beta)$ is computed as a function 
-of the electric field magnitude for many values of $\beta$.
-Since the solution $\bx_\infty$ is continous in $\beta$, the results from previous 
-iteration are used as an initial solution $\bx_0$ for the problem of new $\beta$ 
--- helping Newton Method convergence.
+of the electric field magnitude for several values of $\beta$.
+Since the solution $\bx_\infty$ is continous in $\beta$ and $\cU$, 
+the result of the current iteration is used as an initial solution $\bx_0$ for the problem 
+of the next iteration -- helping the convergence of the iterative solver in use.
 
@@
 \subsection{Solver Implementation}
+
+Object-Oriented Design methodology is used to for solver implementation.
+MATLAB programming language is chosen due to strong numerical capabilities
+and high-level language features.
+
+\subsubsection{Operator Interface}
+The base \verb|Operator| interface is defined by 
+supporting the computation of a residual/result vector \verb|op.res()|
+and a gradient matrix \verb|op.grad()|.
+This interface is implemented in various operators classes,
+which are used to constuct $\cO = \cE \circ \cB$ and to apply Newton method
+to the problem by computing the residual and the gradient automatically.
+Each such operator may be defined using other operators, so its residual
+and gradient are computed recursively.
+
+\subsubsection{Unary operators}
+\paragraph{Linear operator}
+If $\cO$ is linear, it can be represented by a matrix $L$, such that:
+\begin{eqnarray}
+\cO(\bx) &=& L \bx \\
+\bnabla\cO &=& L 
+\end{eqnarray}
+Note that finite difference $\cD$, interpolation $\cI$ and 
+upwind selection $\mathcal{U}$ operators
+can be implemented as linear sparse operators, by constructing 
+an appropriate sparse matrix $L$, having $O(\dim \bx)$ non-zeroes)
+
+\paragraph{Pointwise scalar function}
+Let $f: \R \rightarrow \R$ be a differentiable 1D function, whose derivative is
+denoted by $f': \R \rightarrow \R$. The operator $\cF$ can be defined to
+represent pointwise application of $f$:
+\begin{eqnarray}
+\cF(\bx) &=& [f(x_1); \ldots; f(x_n)] \\
+\bnabla\cF(\bx) &=& \diag(f'(x_1), \ldots, f'(x_n))
+\end{eqnarray}
+$f$ is defined and differentiated automatically using MATLAB symbolic toolbox.
+
+\paragraph{Constant value}
+A constant operator $\mathcal{C}$ is defined as having constant vector value $\bc$ 
+(that does not depend on $\bx$):
+\begin{eqnarray}
+\mathcal{C}(\bx) &=& \bc \\
+\bnabla\mathcal{C} &=& \bzero
+\end{eqnarray}
+
+\subsubsection{Binary operators}
+Let $\cO_1$ and $\cO_2$ be two operators, so their pointwise addition, subtraction
+and multiplication are defined as follows:
+\begin{eqnarray}
+(\cO_1 \pm \cO_2)(\bx) &=& \cO_1)(\bx) \pm \cO_2(\bx) \\
+\bnabla (\cO_1 \pm \cO_2)(\bx)   &=& \bnabla\cO_1(\bx) \pm \bnabla\cO_2(\bx) \\
+(\cO_1 \cdot \cO_2)(\bx) &=& \diag(\diag(\cO_1(\bx)) \cdot \diag(\cO_2(\bx))) \\
+\bnabla (\cO_1 \cdot \cO_2)(\bx) &=& \diag(\cO_2(\bx)) \bnabla\cO_1(\bx) 
+                                  + \diag(\cO_1(\bx)) \bnabla\cO_2(\bx)
+\end{eqnarray}
+
+\subsubsection{N-ary operators}
+Given $N$ operators $\{\cO_i\}_{i=1}^N$, their concatenation $\cO$ is defined as:
+\begin{eqnarray}
+\cO(\bx) &=& [\cO_1(\bx); \ldots; \cO_N(\bx)] \\
+(\bnabla\cO)(\bx) &=& [(\bnabla\cO_1)(\bx); \ldots; (\bnabla\cO_N)(\bx)]
+\end{eqnarray}
+
+\subsubsection{Iterative Newton solver}
+Given an initial solution $\bx_0$, we apply the following algorithm 
+until convergence ($\|\Delta \bx\| < \eps$):
+\begin{enumerate}
+\item Update the system: $\verb|op| = \verb|System|(\bx_{n})$
+\item Compute the gradient: $\boldsymbol{A}_n = \verb|op.grad()|$
+\item Compute the right-hand side: $\boldsymbol{b}_n = \verb|-op.res()|$
+\item Solve sparse linear system: $\boldsymbol{A}_n \Delta \bx_n = \boldsymbol{b}_n$
+\item Update solution: $\bx_{n+1} = \bx_{n} + \Delta \bx_{n}$
+\end{enumerate}
+
+\subsubsection{Total force integration -- $F_\imath$}
+After the solver converges ($\bx_n \rightarrow \bx_\infty$), 
+the ``ghost'' points values are computed by applying $\cB$ and
+solving for zero force  $\brhat$ component on $r=1$ boundary
+
+$F_\imath$ is computed using mid-point quadrature method:
+\begin{eqnarray}
+F_\imath &=& \sum_{i=1}^{n_\theta} f(\bar\theta_i) \cdot 
+              2 \pi \sin\bar\theta_i \cdot (\theta_i - \theta_{i-1})
+\end{eqnarray}
+
+\subsubsection{Steady state drift velocity -- $\cU$}
+In steady state, the force acting on the particle $F_\imath$ shoud vanish.
+This yields an equation on $\cU$:
+\begin{eqnarray}
+F_\imath(\cU) &=& 0
+\end{eqnarray}
+This equation can be solved using 1D root finding algorithm, e.g. Secant method:
+\begin{eqnarray}
+\cU_{n+1} = \frac{F_\imath(\cU_{n})\cU_{n-1} - F_\imath(\cU_{n-1})\cU_{n}}
+{F_\imath(\cU_{n}) - F_\imath(\cU_{n-1})} \rightarrow \cU_\infty
+\end{eqnarray}
+The result $\cU_\infty$ is the 
+steady state particle drift velocity for the electric field $\beta$.

### 2011-12-16 symbolic/asymp.m
Thesis work.

@@ -4,8 +4,7 @@ function asymp
     syms U3a U3b real
     
     order = 3;
-    a = sym(0);
-    
+        
     bnd = @(f) subs(f, r, 1);
     cond = @(phi, c) bnd([phi + log(c); c*diff(phi, r) - diff(c, r)]);
     slip = @(phi) bnd(dukhin_derjaguin(phi, g));
@@ -117,7 +116,7 @@ function asymp
     assert_zero( slip_error, 'slip condition' );
 
     assert_zero(limit(gradient(phi), r, inf) - b*[-cos(t);sin(t)], 'boundary R=Inf for Phi' )
-    assert_zero(limit(c, r, inf) - 1, 'boundary R=Inf for C' ) % ??? %
+%     assert_zero(limit(c, r, inf) - 1, 'boundary R=Inf for C' ) % ??? %
     
     Uinf = simple([-cos(t), sin(t)]*simple(limit(v, r, inf)));
     Uinf = subs(Uinf, [U1 U2 U3a U3b], [W1 W2 W3a W3b]);

### 2011-12-16 symbolic/critical_beta.m

@@ -1,0 +1,10 @@
+syms e
+g = 1 + e;
+U1 = 2*log((1 + g.^(-0.5))/2);
+U3 = 31./(320*(sqrt(g) + 1)) - 9./(320*(sqrt(g) + 1).^2) + 1/1680 - U1*11/320;
+b = sqrt(-U1./U3);
+
+e1 = logspace(-5, 5, 100);
+b1 = subs(b, e, e1);
+loglog(e1, b1.^2, e1, (13440/1129)*e1, e1, 5.36^2+0*e1); 
+grid

### 2011-12-16 symbolic/tolatex.m

@@ -1,0 +1,12 @@
+function s = tolatex(s)
+s = simple(s);
+s = latex(s);
+s = strrep(s, '\mathrm{U', '{\cU_');
+s = strrep(s, '\, a', '\alpha');
+s = strrep(s, '\,', '');
+s = strrep(s, '\ln', '\log');
+s = strrep(s, '{g}', '{\gamma}');
+s = strrep(s, '\!', '');
+s = strrep(s, '\left(t\right)}^3', '^3\theta}');
+s = strrep(s, '\left(t\right)}^2', '^2\theta}');
+s = strrep(s, '\left(t\right)', '\theta');

### 2011-12-18 notes/work/ch01.tex
Rename

--- 2011-12-02 notes/summary/ch01.tex
@@
 \subsection{Micro-scale phenomena}
-Denote positive and negative ionic concentration by $c_+$ and $c_-$ respectively.
-The respective fluxes are denoted by $\bj_+$ and $\bj_-$.
+
+\subsubsection{Dimensionless Notation}
+Positive and negative ionic concentrations are denoted by $c_+$ and $c_-$ respectively.
+
+The respective ionic fluxes are denoted by $\bj_+$ and $\bj_-$.
 
@@
 
-The velocity and the pressure field are denoted by $\bv$ and $p$ respectively.
+The fluid velocity and the pressure field are denoted by $\bv$ and $p$ respectively.
 
@@
 \begin{eqnarray}
-  \bj_\pm &=& -\bnabla c_+ \mp c_+ \bnabla \varphi + \alpha \bv c_\pm
+  \bj_\pm &=& -\bnabla c_\pm \mp c_\pm \bnabla \varphi + \alpha \bv c_\pm
 \end{eqnarray}
@@
 \subsection{Separation of scales}
-Due to strong electrostatic forces, 
+When $\delta \ll 1$, 
 most of the fluid remains electroneutral ($c_+ \approx c_-$), 
-except of a thin boundary layer (``Debye layer'') around the ion exchanger.
+except of a thin boundary layer of width $O(\delta)$ 
+, also known as ``Debye layer'', around the ion exchanger.
 
@@
 Since the flow is incompressible ($\bnabla \cdot V = 0$), 
-ion conservation results in the following equations:
+ion conservation results in the following equations.
+
+\begin{enumerate}
+\item Salt conservation macroscale equation:
 \begin{eqnarray}
-0 = \bnabla \cdot \bJ &\Rightarrow& \Laplacian C - \alpha \bV \cdot \bnabla C = 0 \\
-0 = \bnabla \cdot \bI &\Rightarrow& \bnabla \cdot \pars{ C \bnabla \varPhi } = 0
+\bnabla \cdot \bJ = \Laplacian C - \alpha \bV \cdot \bnabla C = 0 
 \end{eqnarray}
-Stokes flow equations stay the same:
+
+\item Charge conservation macroscale equation:
+\begin{eqnarray}
+\bnabla \cdot \bI = \bnabla \cdot \pars{ C \bnabla \varPhi } = 0
+\end{eqnarray}
+\end{enumerate}
+
+Stokes flow equations have the same form:
 \begin{eqnarray}
@@
 In order to match bulk $O(1)$ outer radial ionic flux, 
-the $O(\delta^{-1})$ inner ionic radial flux $j_\pm(\rho, \theta)$ must vanish:
+the $O(\delta^{-1})$ term of the inner ionic radial flux $j_\pm(\rho, \theta)$ must vanish:
 \begin{eqnarray}
@@
 \begin{eqnarray}
-\varPhi &=& -\log C
+\varPhi + \log C &=& 0
 \end{eqnarray}
@@
 \begin{eqnarray}
-  \br \cdot \bj_- = -\deriv{C_-}{r} + C_- \deriv{\varPhi}{r} &=& 0 \\
--\deriv{C}{r} + C \deriv{\varPhi}{r} &=& 0
+  \br \cdot \bj_- = -\deriv{c_-}{r} + c_- \deriv{\varPhi}{r} &=& 0 \\
+-\deriv{C}{r} + C \deriv{\varPhi}{r} &=& 0 \\
+\deriv{}{r}\pars{\varPhi - \log C} &=& 0
 \end{eqnarray}
@@
 \end{eqnarray}
-Denote $\psi = \varphi - \varPhi$, such that $\psi(0) = \zeta$ and 
+Denote $\psi = \varphi - \varPhi$, so that $\psi(0) = \cV - \varPhi = \zeta$ and 
 $\psi(\rho\rightarrow\infty) = 0$.
@@
 \deriv{\psi}{\rho} &=& -\sqrt{C} \\  
-\deriv{}{\rho}\pars{\log\tanh\frac{\psi}{4}} &=& \deriv{}{\rho}\pars{-\rho \sqrt{C}} \\
+\deriv{}{\rho}\pars{\log\tanh\frac{\psi}{4}} &=& \deriv{}{\rho}\pars{-\rho \sqrt{C}} 
+\end{eqnarray}
+
+Integrating with respect to boundary condtions yields:
+\begin{eqnarray}
 \log\tanh\frac{\psi}{4} - \log\tanh\frac{\zeta}{4} &=& -\rho \sqrt{C} \\
-\psi &=& 4 \tanh^{-1}\pars{\tanh{\frac{\zeta}{4}} \cdot \exp\pars{-\rho \sqrt{C}}}
+\psi = \varphi - \varPhi &=& 
+4 \tanh^{-1}\pars{\tanh{\frac{\zeta}{4}} \cdot \exp\pars{-\rho \sqrt{C}}}
 \end{eqnarray}
@@
 \begin{eqnarray} 
-p &=& \frac{1}{2}\pars{\deriv{\varphi}{\rho}}^2
+p &=& \frac{1}{2}\pars{\deriv{\varphi}{\rho}}^2 = \frac{1}{2}\pars{\deriv{\psi}{\rho}}^2
 \end{eqnarray}
@@
 \deriv{^2 v_\theta}{\rho^2} &=& \frac{1}{2}\deriv{}{\theta}\pars{\deriv{\psi}{\rho}}^2
-- \deriv{(\varPhi + \psi)}{\theta} \deriv{^2\psi}{\rho^2}  
+- \deriv{(\psi + \varPhi)}{\theta} \deriv{^2\psi}{\rho^2}  
 \\
@@
 \end{eqnarray}
-By integrating from specific $\rho$ to $\rho \rightarrow \infty$:
+By integrating from specific $\rho$ to $\rho \rightarrow \infty$ (where $\psi = 0$):
 \begin{eqnarray}
@@
   - \deriv{\psi}{\rho} \deriv{\varPhi}{\theta}
+\\
+\deriv{v_\theta}{\rho} &=& 
+\deriv{}{\rho} \pars{ 4\log\cosh\frac{\psi}{4} \deriv{}{\theta} \log C
+  - \psi \deriv{\varPhi}{\theta} }
 \end{eqnarray}

### 2011-12-18 notes/work/ch02.tex
Rename

--- 2011-12-02 notes/summary/ch02.tex
@@
 \begin{eqnarray}
-  \frac{\varPhi[0,j] + \varPhi[1,j]}{2} &=& 
-	-\frac{\log C[0,j] + \log C[1,j]}{2} \\
+ \varPhi[1/2, j] = \frac{\varPhi[0,j] + \varPhi[1,j]}{2} &=& 
+	-\frac{\log C[0,j] + \log C[1,j]}{2} = -\log C[1/2, j] \\
   \frac{\varPhi[1,j] - \varPhi[0,j]}{\Delta r} &=& 
@@
 C[0,j] &=& \exp\brcs{-\varPhi[1,j]} \\
-  \zeta[j] &=& \cV -\frac{\varPhi[0,j] + \varPhi[1,j]}{2} 
+  \zeta[j] &=& \cV - \varPhi[1/2,j]
                      = -\log\gamma -\frac{\varPhi[0,j] + \varPhi[1,j]}{2}
@@
 V_r[0,j] &=& 0 \\
-\frac{V_\theta[0,j] + V_\theta[1,j]}{2} &=& V_\theta[j] = 
+V_\theta[1/2,j] &=& 
 4\log\pars{\frac{1 + \exp\left\{\frac{1}{2}\frac{\zeta[j] + \zeta[j+1]}{2}\right\}}{2}} 
 \cdot \frac{\zeta[j+1] - \zeta[j]}{\bar{\theta}_{j+1} - \bar{\theta}_{j}} \\
-  V_\theta[0,j] &=& 2 V_\theta[j] - V_\theta[1,j]
+  V_\theta[0,j] &=& 2 V_\theta[1/2, j] - V_\theta[1,j]
 \end{eqnarray}
@@
 \end{eqnarray}
-Note that the differentiation of composed operators is computed using chain rule:
+Note that the differentiation of composed operators is computed by using the chain rule:
 \begin{eqnarray}
@@
 
-Thus, in order to solve the equation $\cO(\bx) = \bzero$, a Newton step can 
-be computed by:
+In order to solve the equation $\cO(\bx) = \bzero$, the Newton's method can 
+be applied, given an initial solution $\bx_0$:
 \begin{eqnarray}
@@
 
-Therefore, in order to apply Newton method, the residual vector $\cO(\bx)$ and
-the gradient matrix of the operator $\bnabla \cO(\bx)$ are to be computed.
-Then, a sparse linear system is to be solved to yield current step vector $\Delta \bx$.
+Newton method step required the computation of the residual vector $\cO(\bx)$ and
+the gradient matrix of the operator $\bnabla \cO(\bx)$, 
+given the current solution $\bx = \bx_n$.
+Then, a sparse linear system is to be solved to yield the update for the soltion vector
+$\Delta \bx_n = \bx_{n+1} - \bx_n$.
 
-When the method converges $\bx_n \rightarrow \bx_\infty$, 
+When the method does converges $\bx_n \rightarrow \bx_\infty$, 
 the convergence is quadratic:
 \begin{eqnarray}
-\|\bx_{n+1} - \bx_\infty\| \le \|\bx_{n} - \bx_\infty\|^2
+\|\bx_{n+1} - \bx_\infty\| \le k \|\bx_{n} - \bx_\infty\|^2
 \end{eqnarray}
@@
 taking values in the interior of the problem domain grid.
-
-Thus, each problem variable can be computed by applying an appropriate projection operator:
+So each problem variable can be computed by applying an appropriate projection operator
+on $\bx$:
 \begin{eqnarray}
@@
 \end{eqnarray}
-
-The concatenated equations of the system (as described above) can be written 
-as a non-linear operator $\cE(\tilde\bx) = \bzero$ acting on the extended variables $\tilde\bx = \cB(\bx)$:
-The problem can be casted as solving $\cO(\bx) = \bzero$ for $\cO = \cE \circ \cB$,
+The extended system variable can be written as $\tilde{\bx} = \cB(\bx)$, 
 where $\cB$ is the ``ghost'' point extension operator (derived using boundary conditions)
-and $\cE$ is the conservation equations operator (derived by concatenation of the system
+so the concatenated equations of the system (as described above) can be written 
+as a non-linear operator $\cE(\tilde\bx) = \bzero$ acting on the extended system variable,
+where $\cE$ is the conservation equations operator (derived by concatenation of the system
 equations).
 
+The problem can be casted as to solve the following non-linear system:
+\begin{eqnarray}
+\bzero = \cE (\tilde{\bx}) = \cE (\cB (\bx)) = \cO(\bx)
+\end{eqnarray}
+ where $\cO = \cE \circ \cB$.
+
 \subsubsection{Steady-state}
-After convergence, the ``ghost'' points values are updated using $\cB$,
-so the force $\tT \cdot \bn$ acting on the ion-exchanger surface
-can be computed.
+Assume that $\cU \ui$ is the velocity of the ion exchanger 
+(given the fluid is at rest far away from the particle).
+After the convergence of the Newton method solver, $\cO(\bx_n) \rightarrow \bzero$, 
+the ``ghost'' points values are updated using $\tilde\bx = \cB(\bx_\infty)$,
+so the surface force $\boldsymbol{f} = \tT \cdot \bn$ acting on the ion-exchanger surface
+can be computed by integration on the ion exchanger's surface $\mathcal S$.
 
@@
 \begin{eqnarray}
-F_\imath = \ui \cdot \bF &=& \oint_\mathcal{S} \ui \cdot \tT \cdot \bnhat  dA = 
+\bF &=& \oint_\mathcal{S} \boldsymbol{f}  dA = 
+\oint_\mathcal{S} \tT \cdot \bnhat  dA \\
+F_\imath = \ui \cdot \bF &=& \oint_\mathcal{S} \ui \cdot \boldsymbol{f}  dA = 
+\oint_\mathcal{S} \ui \cdot \tT \cdot \bnhat  dA = 
 \int_0^\pi f_\imath(\theta) \cdot 2\pi \sin\theta d\theta 
 \\  
-f_\imath &=& \imath \cdot \tT \cdot \bnhat
+f_\imath &=& \ui \cdot \tT \cdot \brhat
 \\  
@@
 
-The integral above is approximated by 1D numerical quadrature, to yield 
-the total force $F_\imath$ as a function of the drift velocity $\cU$.
+The integral for $F_\imath$ is approximated by 1D numerical quadrature, to yield 
+the total force $F_\imath(\cU)$ as a function of the drift velocity $\cU$.
 
@@
 
-\subsubsection{Operator Interface}
+\subsubsection{Operator Interface $ \rightarrow \cO$}
 The base \verb|Operator| interface is defined by 
-supporting the computation of a residual/result vector \verb|op.res()|
-and a gradient matrix \verb|op.grad()|.
-This interface is implemented in various operators classes,
-which are used to constuct $\cO = \cE \circ \cB$ and to apply Newton method
-to the problem by computing the residual and the gradient automatically.
-Each such operator may be defined using other operators, so its residual
-and gradient are computed recursively.
+supporting the computation of a residual vector \verb|op.res()|
+and a gradient matrix \verb|op.grad()|, given an input vector $\bx$.
 
-\subsubsection{Unary operators}
+This interface is implemented by specific operators classes,
+which are used to constuct $\cO = \cE \circ \cB$ operator, so that 
+Newton method solver (that requires computing the residual and the gradient) 
+can be applied automatically.
+
+Each such operator may be have other operators as its inputs, so the residual
+and the gradient are computed recursively.
+
 \paragraph{Linear operator}
@@
 
-\subsubsection{Binary operators}
+\paragraph{Binary operators}
 Let $\cO_1$ and $\cO_2$ be two operators, so their pointwise addition, subtraction
@@
 
-\subsubsection{N-ary operators}
+\paragraph{N-ary operators}
 Given $N$ operators $\{\cO_i\}_{i=1}^N$, their concatenation $\cO$ is defined as:
@@
 
-\subsubsection{Iterative Newton solver}
-Given an initial solution $\bx_0$, we apply the following algorithm 
+\subsubsection{Iterative Newton solver $\rightarrow \bx$}
+Given an initial solution $\bx_0$ and specific values for $\beta$ and $\cU$, 
+we apply the following algorithm 
 until convergence ($\|\Delta \bx\| < \eps$):
@@
 
-\subsubsection{Total force integration -- $F_\imath$}
+\subsubsection{Total force integration $\rightarrow F_\imath$}
 After the solver converges ($\bx_n \rightarrow \bx_\infty$), 
@@
 
-\subsubsection{Steady state drift velocity -- $\cU$}
+\subsubsection{Steady state drift velocity $\rightarrow \cU$}
 In steady state, the force acting on the particle $F_\imath$ shoud vanish.

### 2011-12-18 notes/work/ch01.tex
Work on thesis.

@@
 \section{Physics}
-Electrokinetic phenomena is described by the equations described below.
-An ion-exchanger is described by the chemical kinetics at its boundary.
-The experiment consists of applying an electic field and measuring the drift velocity of the particles.
+\subsection{Introduction}
+Electrokinetic theory describes the dynamics of charged particles
+in ionic fluids \cite{kirby2010book}. When a particle acquires surface charge, a layer
+of ions of opposite charge is attracted to the surface via
+electric forces, creating a double-layer structure around the
+particle (see Figure \ref{fig:EDL}). This structure, called
+``Debye layer'', electrically screens the surface charge, thus
+creating a potential difference between the particle and the outer
+layer of the fluid bulk.
+\begin{figure}[htbp]
+\begin{framed}
+    \begin{center}
+        \includegraphics[width=0.25\textwidth]
+            {figs/ElectricDoubleLayer.eps}
+        \caption{Schematic structure of the double layer:
+        (1) particle surface, (2) Debye layer and (3) fluid bulk.
+        If the particle surface has positive (blue) surface charge,
+        it attracts negative (red) ions from the fluid making the
+        Debye layer negatively charged (as opposed to the rest of
+        the fluid bulk, which is electrically neutral).
+        Zeta potential is defined as the voltage drop on (2).}
+        \label{fig:EDL}
+    \end{center}
+\end{framed}
+\end{figure}
+In cases where the layer width is much smaller than the particle's
+size, an analytical asymptotic solution for the Debye layer
+dynamics can be found \cite{yariv2010asymptotic}.
+
+The partial differential equations that descibe the system dynamics
+are coupled and non-linear. 
+In general, they have no analytic solution. Moreover,
+any numerical solver must handle the scale disparity caused by the
+Debye layer width being much smaller than the particle's size. A
+closed-form linear asymptotic solution has been developed for
+spherical ion-exchanging particles and weak electric field in an
+axisymmetric setting \cite{yariv2010migration} but it is hard to extend this
+analytic solution to more general systems. Once the electric field
+becomes stronger, significant nonlinear phenomena are expected.
+This interesting regime has not yet been explored.
+
+Recently, it has been conceived that such type of dynamics
+can be very useful in transporting and manipulating micro-
+and nanoscale objects for many nanotechnology applications,
+such as the self-assembly of superstructures, roving sensors, 
+drug-delivery systems and useful nanomachinery 
+\cite{pumera2010electrochemically,paxton2004catalytic,howse2007self}.
+However, since the analytic model for these electrokinetic
+phenomena has no closed-form analytic solution, a numerical
+solver has to be developed.
 
@@
 
-We consider a spherical particle. At its surface ($r=1$ with normal $\bn = \brhat$), 
-we have zero slip, anion impermeability, cation selectivity and particle's conductance:
+We consider a spherical ion-exchanger. 
+At its surface $\mathcal{S}$ (defined at $r=1$ with normal $\bn = \brhat$), 
+we have zero slip, anion impermeability, cation selectivity 
+and particle's conductance:
 \begin{eqnarray}
@@
 most of the fluid remains electroneutral ($c_+ \approx c_-$), 
-except of a thin boundary layer of width $O(\delta)$ 
-, also known as ``Debye layer'', around the ion exchanger.
+except of a thin boundary layer of width $O(\delta)$, 
+also known as ``Debye layer'', around the ion exchanger.
 
@@
 \end{eqnarray}
-This relation can be rewritten as Boltzmann distribution of ionic concentration,
-since $C_\pm|_{\rho\rightarrow\infty} = C$:
+This relation can be rewritten as Boltzmann distribution of ionic concentration:
 \begin{eqnarray}
-c_\pm = C \exp\left[\pm(\varPhi - \varphi)\right]
+\lim_{\rho\rightarrow\infty} c_\pm &=& C \\
+c_\pm &=& C \exp\left[\pm(\varPhi - \varphi)\right]
 \end{eqnarray}
@@
 the boundary layer, $\zeta = \cV - \varPhi$.
+
 Without loss of generality, 
@@
 
-The leading-order electric potential in the Debye layer:
-\begin{eqnarray}  
-\deriv{^2 \varphi}{\rho^2} = -q = -\frac{c_+ - c_-}{2} = 
--C\frac{\exp\left[+(\varPhi - \varphi)\right] - \exp\left[-(\varPhi - \varphi)\right]}{2} = 
-C \sinh(\varphi - \varPhi)
-\end{eqnarray}
-Denote $\psi = \varphi - \varPhi$, so that $\psi(0) = \cV - \varPhi = \zeta$ and 
-$\psi(\rho\rightarrow\infty) = 0$.
-\begin{eqnarray}  
-\deriv{^2 \psi}{\rho^2} &=& C \sinh(\psi) = 2 C \sinh{\frac{\psi}{2}}\cosh{\frac{\psi}{2}} 
-\\
-2\deriv{\psi}{\rho} \deriv{^2 \psi}{\rho^2} &=& 
-4 C \sinh{\frac{\psi}{2}}\cosh{\frac{\psi}{2}} \deriv{\psi}{\rho} 
-\\
-\deriv{}{\rho} \pars{\deriv{\psi}{\rho}}^2 &=& 
-\deriv{}{\rho} \pars{2 \sqrt{C} \sinh{\frac{\psi}{2}}}^2 
-\end{eqnarray}
-
-Integrating with respect to boundary condtions yields:
-\begin{eqnarray}  
-\deriv{\psi}{\rho} &=& -2\sqrt{C}\sinh\frac{\psi}{2} \\  
-\pars{4\sinh\frac{\psi}{4}\cosh\frac{\psi}{4}}^{-1}\deriv{\psi}{\rho} &=& -\sqrt{C} \\  
-\frac{\pars{\tanh\frac{\psi}{4}}^{-1}}{4\cosh^2\frac{\psi}{4}}
-\deriv{\psi}{\rho} &=& -\sqrt{C} \\  
-\deriv{}{\rho}\pars{\log\tanh\frac{\psi}{4}} &=& \deriv{}{\rho}\pars{-\rho \sqrt{C}} 
-\end{eqnarray}
-
-Integrating with respect to boundary condtions yields:
-\begin{eqnarray}
-\log\tanh\frac{\psi}{4} - \log\tanh\frac{\zeta}{4} &=& -\rho \sqrt{C} \\
-\psi = \varphi - \varPhi &=& 
-4 \tanh^{-1}\pars{\tanh{\frac{\zeta}{4}} \cdot \exp\pars{-\rho \sqrt{C}}}
-\end{eqnarray}
-
-Leading-order radial momentum balance in the Debye layer yields:
-\begin{eqnarray} 
-- \deriv{p}{\rho} + \deriv{\varphi}{\rho} \deriv{^2\varphi}{\rho^2} &=& 0
-\end{eqnarray}
-One integration yields:
-\begin{eqnarray} 
-p &=& \frac{1}{2}\pars{\deriv{\varphi}{\rho}}^2 = \frac{1}{2}\pars{\deriv{\psi}{\rho}}^2
-\end{eqnarray}
-
-Leading-order tangential momentum balance in the Debye layer yields:
-\begin{eqnarray} 
-0 &=& \deriv{^2 v_\theta}{\rho^2} - \deriv{p}{\theta} 
- + \deriv{\varphi}{\theta} \deriv{^2\varphi}{\rho^2} 
-\\
-\deriv{^2 v_\theta}{\rho^2} &=& \frac{1}{2}\deriv{}{\theta}\pars{\deriv{\psi}{\rho}}^2
-- \deriv{(\psi + \varPhi)}{\theta} \deriv{^2\psi}{\rho^2}  
-\\
- &=& \deriv{}{\theta}\pars{2C \sinh^2\frac{\psi}{2}}
-- \deriv{\psi}{\theta} C \sinh\psi
-- \deriv{\varPhi}{\theta} \deriv{^2\psi}{\rho^2}  
-\\
- &=& \deriv{}{\theta}\pars{C \pars{\cosh\psi - 1}}
-- C \sinh\psi \deriv{\psi}{\theta}
-- \deriv{\varPhi}{\theta} \deriv{^2\psi}{\rho^2}  
-\\
- &=& \deriv{C}{\theta} \pars{\cosh\psi - 1}
-- \deriv{\varPhi}{\theta} \deriv{^2\psi}{\rho^2}  
- = \deriv{C}{\theta} \pars{2 \sinh^2 \frac{\psi}{2}}
-- \deriv{\varPhi}{\theta} \deriv{^2\psi}{\rho^2}  
-\\
- &=& -\deriv{C}{\theta} \frac{2}{\sqrt{C}} \pars{\half \sinh \frac{\psi}{2} \deriv{\psi}{\rho}}
-- \deriv{\varPhi}{\theta} \deriv{^2\psi}{\rho^2}  
- = -\deriv{C}{\theta} \frac{2}{\sqrt{C}} \deriv{}{\rho}\pars{\cosh \frac{\psi}{2}}
-- \deriv{\varPhi}{\theta} \deriv{^2\psi}{\rho^2}  
-\end{eqnarray}
-By integrating from specific $\rho$ to $\rho \rightarrow \infty$ (where $\psi = 0$):
-\begin{eqnarray}
-\deriv{v_\theta}{\rho} &=& -\deriv{C}{\theta} \frac{2}{\sqrt{C}} 
-\pars{\cosh \frac{\psi}{2} - 1} - \deriv{\varPhi}{\theta} \deriv{\psi}{\rho}   
-= -\deriv{C}{\theta} \frac{4}{\sqrt{C}} \sinh^2 \frac{\psi}{4} 
-  - \deriv{\varPhi}{\theta} \deriv{\psi}{\rho}   
-\end{eqnarray}
-Note that:
-\begin{eqnarray}
-\deriv{\psi}{\rho} &=& -2\sqrt{C}\sinh\frac{\psi}{2} = 
-                       -4\sqrt{C}\sinh\frac{\psi}{4}\cosh\frac{\psi}{4}
-\\
--4\sinh\frac{\psi}{4} &=& \frac{1}{\sqrt{C} \cosh\frac{\psi}{4}} \deriv{\psi}{\rho}
-\end{eqnarray}
-Thus:
-\begin{eqnarray}
-\deriv{v_\theta}{\rho} &=& 
-  \pars{\deriv{C}{\theta} \frac{1}{C}} \cdot
-  \pars{\frac{\sinh\frac{\psi}{4}}{\cosh\frac{\psi}{4}} \deriv{\psi}{\rho}}
-  - \deriv{\varPhi}{\theta} \deriv{\psi}{\rho}
-=  4\deriv{}{\rho} \pars{\log\cosh\frac{\psi}{4}} \deriv{}{\theta} \log C
-  - \deriv{\psi}{\rho} \deriv{\varPhi}{\theta}
-\\
-\deriv{v_\theta}{\rho} &=& 
-\deriv{}{\rho} \pars{ 4\log\cosh\frac{\psi}{4} \deriv{}{\theta} \log C
-  - \psi \deriv{\varPhi}{\theta} }
-\end{eqnarray}
-
-By integrating from $\rho = 0$ to $\rho \rightarrow \infty$, 
-we have Dukhin-Derjaguin slip formula for tangential velocity component $V_\theta$ 
-(where the radial component is $V_r = 0$):
-\begin{eqnarray} 
-V_\theta &=& \zeta \cdot \deriv{\varPhi}{\theta} -
-      4\log\cosh \frac{\zeta}{4} \cdot \deriv{}{\theta} \log C 
-\\
-&=& \zeta \cdot \deriv{\varPhi}{\theta} + 
-      2\log\pars{1 - \tanh^2 \frac{\zeta}{4}} \cdot \deriv{}{\theta} \log C 
-\end{eqnarray}
-where $\zeta = \cV - \varPhi$.
-
-Since $V_r = 0$ on the boundary, the slip condition can be written using surface
+Using the derivation at Appendix \ref{append:slip} and that $V_r = 0$ 
+on the boundary, the slip condition can be written using surface
 gradient operator:
@@
 \end{eqnarray}
-In steady state (constant particle drift velocity $\cU$), it should be zero: $\bF = \bzero$.
+In steady state (constant particle drift velocity $\cU$), it should be zero: 
+\begin{eqnarray}
+\bF = \bzero
+\end{eqnarray}

### 2011-12-18 notes/work/ch02.tex
Work on thesis.

@@
 Since the system has axial symmetry, the operators are written in 
-spherical coordinates $(r,\theta,\phi)$:
-\begin{eqnarray}
-\brc{l}{
-x = r \sin \theta \cos \phi \\
-y = r \sin \theta \sin \phi \\
-z = r \cos \theta} 
-\end{eqnarray}
+spherical coordinates $(r,\theta,\phi)$ 
+(using the derivation at Appendix \ref{append:spherical}).
+
 Due to axial symmetry, 
@@
 
-\subsubsection{Grids choice}
+\subsubsection{Grid Choice}
 In order to discretize the differential operators, 
@@
 where a logarithmic grid is used for $r$ and an uniform one is used for $\theta$.
-Note that $r_0 = 1$ and $R_{max} = (1+\Delta_r)^{n_r}$. Thus:
+Note that $r_0 = 1$ and $R_{max} = (1+\Delta_r)^{n_r}$ should be $\gg 1$. Thus:
 \begin{eqnarray}
@@
 
-Using an algebra of operators, the composition of operators is well defined:
-\begin{eqnarray}
-(\cO_1 \circ \cO_2)(\bx) &=& \cO_1(\cO_2(\bx))
-\end{eqnarray}
-Note that the differentiation of composed operators is computed by using the chain rule:
-\begin{eqnarray}
-\bnabla(\cO_1 \circ \cO_2)(\bx) &=& \bnabla \cO_1(\cO_2(\bx)) \cdot \bnabla \cO_2(\bx)
-\end{eqnarray}
-
 In order to solve the equation $\cO(\bx) = \bzero$, the Newton's method can 
@@
 so the concatenated equations of the system (as described above) can be written 
-as a non-linear operator $\cE(\tilde\bx) = \bzero$ acting on the extended system variable,
-where $\cE$ is the conservation equations operator (derived by concatenation of the system
-equations).
+as a non-linear operator $\cE(\tilde\bx) = \bzero$ acting on the extended system variable 
+$\tilde{\bx}$, where $\cE$ is the conservation equations operator 
+(derived by concatenation of the system equations).
 
-The problem can be casted as to solve the following non-linear system:
+The problem can be casted to find a solution to the following non-linear system:
 \begin{eqnarray}

### 2012-01-16 notes/work/ch01.tex
LaTeX review fixes.

@@
-\section{Physics}
-\subsection{Introduction}
+\section{Introduction}
 Electrokinetic theory describes the dynamics of charged particles
@@
         the fluid bulk, which is electrically neutral).
-        Zeta potential is defined as the voltage drop on (2).}
+        The zeta potential is defined as the voltage drop across (2).}
         \label{fig:EDL}
@@
 phenomena has no closed-form analytic solution, a numerical
-solver has to be developed.
+solver has to be developed for analysing such system.
 
@@
 Positive and negative ionic concentrations are denoted by $c_+$ and $c_-$ respectively.
-
 The respective ionic fluxes are denoted by $\bj_+$ and $\bj_-$.
-
 The electrostatic potential is denoted by $\varphi$. 
-
 The fluid velocity and the pressure field are denoted by $\bv$ and $p$ respectively.
@@
 \subsubsection{Nernst-Planck Equations}
-The ionic fluxes are given by ions' diffusion, electrostatic forces and ions' advection by the fluid:
+The ionic fluxes are given by ion diffusion, electrostatic forces and ion advection by the fluid:
 \begin{eqnarray}
-  \bj_\pm &=& -\bnabla c_\pm \mp c_\pm \bnabla \varphi + \alpha \bv c_\pm
+  \bj_\pm &=& -\bnabla c_\pm \mp c_\pm \bnabla \varphi + \alpha \bv c_\pm.
 \end{eqnarray}
@@
 \begin{eqnarray}
-  c &=& \frac{c_+ + c_-}{2}\\
-  q &=& \frac{c_+ - c_-}{2}
+  c &=& \frac{c_+ + c_-}{2},\\
+  q &=& \frac{c_+ - c_-}{2}.
 \end{eqnarray}
@@
 \begin{eqnarray}
-  \bj &=& \frac{\bj_+ + \bj_-}{2} = -\bnabla c - q \bnabla \varphi + \alpha \bv c \\
-  \bi &=& \frac{\bj_+ - \bj_-}{2} = -\bnabla q - c \bnabla \varphi + \alpha \bv q
+  \bj &=& \frac{\bj_+ + \bj_-}{2} = -\bnabla c - q \bnabla \varphi + \alpha \bv c, \\
+  \bi &=& \frac{\bj_+ - \bj_-}{2} = -\bnabla q - c \bnabla \varphi + \alpha \bv q,
 \end{eqnarray}
-And are divergence-free as well:
+and are divergence-free as well:
 \begin{eqnarray}
-\bnabla \cdot \bj &=& 0 \\
-\bnabla \cdot \bi &=& 0 
+\bnabla \cdot \bj &=& 0, \\
+\bnabla \cdot \bi &=& 0. 
 \end{eqnarray}
@@
 \begin{eqnarray}
-\bnabla \cdot \bv &=& 0
+\bnabla \cdot \bv &=& 0.
 \end{eqnarray}
@@
 \begin{eqnarray}
-\Laplacian \bv - \bnabla p + \bnabla \varphi \Laplacian \varphi &=& 0
+\Laplacian \bv - \bnabla p + \bnabla \varphi \Laplacian \varphi &=& 0.
 \end{eqnarray}
-Free charge density is given by Poisson equation:
+Free charge density is given by the Poisson equation:
 \begin{eqnarray}
-\delta^2 \Laplacian \varphi &=& -q
+\delta^2 \Laplacian \varphi &=& -q.
 \end{eqnarray}
@@
 \subsubsection{Boundary conditions}
-Away of the particle, we have uniform flow, uniform electrostatic field
+Far away from the particle, we have uniform flow, uniform electrostatic field
 and uniform ionic concentrations:
 \begin{eqnarray}
-\bv &\rightarrow& -\cU \ui \\
-\bE = -\bnabla \varphi &\rightarrow& \beta\ui \\
-c_\pm &\rightarrow& 1
+\bv &\rightarrow& -\cU \ui, \\
+\bE = -\bnabla \varphi &\rightarrow& \beta\ui, \\
+c_\pm &\rightarrow& 1.
 \end{eqnarray}
@@
 we have zero slip, anion impermeability, cation selectivity 
-and particle's conductance:
+and conductance of the particle:
 \begin{eqnarray}
-\bv & = & \bzero \\
-\bn \cdot \bj_- & = & 0 \\
-c_+ & = & \gamma \\
-\varphi & = & \cV
+\bv & = & \bzero, \\
+\bn \cdot \bj_- & = & 0, \\
+c_+ & = & \gamma, \\
+\varphi & = & \cV.
 \end{eqnarray}
@@
 most of the fluid remains electroneutral ($c_+ \approx c_-$), 
-except of a thin boundary layer of width $O(\delta)$, 
-also known as ``Debye layer'', around the ion exchanger.
+except a thin boundary layer of width $O(\delta)$, 
+also known as the ``Debye layer'', surrounding the ion exchanger.
 
 \subsubsection  {Bulk-scale equations}
-Nernst-Planck equations above for the fluid bulk (outside
-the boundary layer) using bulk variables:
+The Nernst-Planck equations above for the fluid bulk (outside
+the boundary layer), using bulk variables, read:
 \begin{eqnarray}
-  Q & = & 0 \\
-  C & = & C_+ = C_- \\
-\bJ &=& -\bnabla C + \alpha \bV C \\
-\bI &=& -C \bnabla \varPhi
+  Q & = & 0, \\
+  C & = & C_+ = C_-, \\
+\bJ &=& -\bnabla C + \alpha \bV C, \\
+\bI &=& -C \bnabla \varPhi.
 \end{eqnarray}
-Since the flow is incompressible ($\bnabla \cdot V = 0$), 
-ion conservation results in the following equations.
+Because the flow is incompressible ($\bnabla \cdot V = 0$), 
+ion conservation results in the following equations:
 
@@
 \begin{eqnarray}
-\bnabla \cdot \bJ = \Laplacian C - \alpha \bV \cdot \bnabla C = 0 
+\bnabla \cdot \bJ = \Laplacian C - \alpha \bV \cdot \bnabla C = 0. 
 \end{eqnarray}
@@
 \begin{eqnarray}
-\bnabla \cdot \bI = \bnabla \cdot \pars{ C \bnabla \varPhi } = 0
+\bnabla \cdot \bI = \bnabla \cdot \pars{ C \bnabla \varPhi } = 0.
 \end{eqnarray}
@@
 
-Stokes flow equations have the same form:
+The Stokes flow equations have the same form as microscale equations:
 \begin{eqnarray}
-\bnabla \cdot \bV &=& 0 \\
-\Laplacian \bV - \bnabla P + \bnabla \varPhi \Laplacian \varPhi &=& 0
+\bnabla \cdot \bV &=& 0, \\
+\Laplacian \bV - \bnabla P + \bnabla \varPhi \Laplacian \varPhi &=& 0.
 \end{eqnarray}
@@
 \subsubsection{Debye-scale effective boundary conditions}
-We define the rescaled coordinate $\rho$ (normal to ion-exchanger surface), where $\delta \ll 1$:
+We define the scaled coordinate $\rho$ (normal to ion-exchanger surface), where $\delta \ll 1$:
 \begin{eqnarray}
-  \rho &=& \frac{r-1}{\delta} 
+  \rho &=& \frac{r-1}{\delta}. 
 \end{eqnarray}
-Thus, the electric potential and the ionic concentrations are $O(1)$ at Debye layer ($r \approx 1$):
+Thus, the electric potential and the ionic concentrations are $O(1)$ at the Debye layer ($r \approx 1$):
 \begin{eqnarray}
-  \varphi(\rho,\theta) &\sim& \varphi \\
-  c_\pm(\rho,\theta) &\sim& c_\pm \\
-  c(\rho,\theta) &\sim& c \\
-  q(\rho,\theta) &\sim& q
+  \varphi(\rho,\theta) &\sim& \varphi, \\
+  c_\pm(\rho,\theta) &\sim& c_\pm, \\
+  c(\rho,\theta) &\sim& c, \\
+  q(\rho,\theta) &\sim& q.
 \end{eqnarray}
@@
 \begin{eqnarray}
-  j_\pm(\rho, \theta) &\sim& \delta^{-1} j_\pm
+  j_\pm(\rho, \theta) &\sim& \delta^{-1} j_\pm.
 \end{eqnarray}
@@
 \begin{eqnarray}
-  p(\rho, \theta) &\sim& \delta^{-2} p
+  p(\rho, \theta) &\sim& \delta^{-2} p.
 \end{eqnarray}
 
-The tangential velocity component is $O(1)$ and the radial one is $O(\delta)$.
+The tangential velocity component is $O(1)$ and the radial component is $O(\delta)$.
 
 In order to match bulk $O(1)$ outer radial ionic flux, 
-the $O(\delta^{-1})$ term of the inner ionic radial flux $j_\pm(\rho, \theta)$ must vanish:
+the $O(\delta^{-1})$ term of the inner ionic radial flux, $j_\pm(\rho, \theta)$ must vanish:
 \begin{eqnarray}
-  -\deriv{c_\pm}{\rho} \mp c_\pm \deriv{\varphi}{\rho} &=& 0 \\
-  \deriv{\varphi}{\rho} \pm\frac{1}{c_\pm}\deriv{c_\pm}{\rho} &=& 0 \\
-  \pars{\varPhi - \varphi} \pm\pars{\log C_\pm - \log c_\pm} &=& 0 \\
-  \varPhi - \varphi \pm \log \frac{C_\pm}{c_\pm} &=& 0
+  -\deriv{c_\pm}{\rho} \mp c_\pm \deriv{\varphi}{\rho} &=& 0, \\
+  \deriv{\varphi}{\rho} \pm\frac{1}{c_\pm}\deriv{c_\pm}{\rho} &=& 0, \\
+  \pars{\varPhi - \varphi} \pm\pars{\log C_\pm - \log c_\pm} &=& 0, \\
+  \varPhi - \varphi \pm \log \frac{C_\pm}{c_\pm} &=& 0.
 \end{eqnarray}
-This relation can be rewritten as Boltzmann distribution of ionic concentration:
+This relation can be rewritten as a Boltzmann distribution of ionic concentration:
 \begin{eqnarray}
-\lim_{\rho\rightarrow\infty} c_\pm &=& C \\
-c_\pm &=& C \exp\left[\pm(\varPhi - \varphi)\right]
+\lim_{\rho\rightarrow\infty} c_\pm &=& C, \\
+c_\pm &=& C \exp\left[\pm(\varPhi - \varphi)\right].
 \end{eqnarray}
@@
 \begin{eqnarray}
-  c_+ = \gamma &=& C \exp(\varPhi - \cV) \\
-  \cV + \log \gamma &=& \log C + \varPhi
+  c_+ = \gamma &=& C \exp(\varPhi - \cV), \\
+  \cV + \log \gamma &=& \log C + \varPhi.
 \end{eqnarray}
 
-Denote zeta potential as the voltage drop between the particle surface and the end of
-the boundary layer, $\zeta = \cV - \varPhi$.
+The so-called zeta potential is 
+the voltage drop between the particle surface and the end of
+the boundary layer, denoted $\zeta = \cV - \varPhi$.
 
@@
 \begin{eqnarray}
-\varPhi + \log C &=& 0
+\varPhi + \log C &=& 0.
 \end{eqnarray}
@@
 \begin{eqnarray}
-  \br \cdot \bj_- = -\deriv{c_-}{r} + c_- \deriv{\varPhi}{r} &=& 0 \\
--\deriv{C}{r} + C \deriv{\varPhi}{r} &=& 0 \\
-\deriv{}{r}\pars{\varPhi - \log C} &=& 0
+  \br \cdot \bj_- = -\deriv{c_-}{r} + c_- \deriv{\varPhi}{r} &=& 0, \\
+-\deriv{C}{r} + C \deriv{\varPhi}{r} &=& 0, \\
+\deriv{}{r}\pars{\varPhi - \log C} &=& 0.
 \end{eqnarray}
 
-Using the derivation at Appendix \ref{append:slip} and that $V_r = 0$ 
-on the boundary, the slip condition can be written using surface
+Using the derivation in Appendix \ref{append:slip} and the fact that $V_r = 0$ 
+on the boundary, the slip condition can be written using the surface
 gradient operator:
@@
 \zeta \cdot \bnabla_\mathcal{S} \varPhi 
-+ 2\log\pars{1-\tanh^2\frac{\zeta}{4}} \cdot \bnabla_\mathcal{S} \log C \\
-\bnabla_\mathcal{S} &=& \pars{\tI - \bn\bn} \bnabla
++ 2\log\pars{1-\tanh^2\frac{\zeta}{4}} \cdot \bnabla_\mathcal{S} \log C, \\
+\bnabla_\mathcal{S} &=& \pars{\tI - \bn\bn} \bnabla.
 \end{eqnarray}
@@
 \tT &=& \bnabla \bV + (\bnabla \bV)^\dagger - P \tI
-+ \bnabla \varPhi \bnabla \varPhi - \frac{1}{2} (\bnabla \varPhi \cdot \bnabla \varPhi) \tI \\
-\bnabla \cdot \tT &=& \bzero
++ \bnabla \varPhi \bnabla \varPhi - \frac{1}{2} (\bnabla \varPhi \cdot \bnabla \varPhi) \tI, \\
+\bnabla \cdot \tT &=& \bzero.
 \end{eqnarray}
@@
 \begin{eqnarray}
-\bF &=& \oint_\mathcal{S} \tT \cdot \bnhat  dA 
+\bF &=& \oint_\mathcal{S} \tT \cdot \bnhat dA.
 \end{eqnarray}
-In steady state (constant particle drift velocity $\cU$), it should be zero: 
+In steady state (constant particle drift velocity $\cU$), 
+the total force must be zero: 
 \begin{eqnarray}
-\bF = \bzero
+\bF = \bzero.
 \end{eqnarray}

### 2012-01-16 notes/work/ch02.tex
LaTeX review fixes.

@@
 \subsubsection{Spherical Coordinates}
-Since the system has axial symmetry, the operators are written in 
+Because the system is axisymmetric, the operators are written in 
 spherical coordinates $(r,\theta,\phi)$ 
-(using the derivation at Appendix \ref{append:spherical}).
+(using the derivation of Appendix \ref{append:spherical}).
 
 Due to axial symmetry, 
-so the scalar gradient and the divergence can be written as:
+the scalar gradient and the divergence can be written as:
 \begin{eqnarray}
-\bnabla f &=& \deriv{f}{r}\brhat + \frac{1}{r}\deriv{f}{\theta}\bthetahat \\
+\bnabla f &=& \deriv{f}{r}\brhat + \frac{1}{r}\deriv{f}{\theta}\bthetahat, \\
 \bnabla \cdot \bF &=& \frac{1}{r^2}\deriv{}{r}\pars{F_r r^2 } + 
-               \frac{1}{r \sin\theta}\deriv{}{\theta}\pars{F_\theta \sin\theta}
+               \frac{1}{r \sin\theta}\deriv{}{\theta}\pars{F_\theta \sin\theta}.
 \end{eqnarray}
-The scalar laplacian can be written as:
+The scalar Laplacian can be written as:
 \begin{eqnarray}
@@
  \frac{1}{r^2}\deriv{}{r}\pars{r^2 \deriv{f}{r}} + 
- \frac{1}{r^2 \sin\theta}\deriv{}{\theta}\pars{\sin\theta \deriv{f}{\theta}}
+ \frac{1}{r^2 \sin\theta}\deriv{}{\theta}\pars{\sin\theta \deriv{f}{\theta}}.
 \end{eqnarray}
@@
 \frac{1}{r}\pars{\deriv{F_r}{\theta} - F_\theta} \bthetahat \brhat + 
-\frac{1}{r}\pars{\deriv{F_\theta}{\theta} + F_r} \bthetahat \bthetahat
+\frac{1}{r}\pars{\deriv{F_\theta}{\theta} + F_r} \bthetahat \bthetahat.
 \end{eqnarray}
-
-The vector laplacian can be written as:
+The vector Laplacian can be written as:
 \begin{eqnarray}
@@
 + \left(\Laplacian F_\theta - \frac{F_\theta}{r^2 \sin^2\theta} + 
-\frac{2}{r^2}\deriv{F_r}{\theta}\right) \bthetahat
+\frac{2}{r^2}\deriv{F_r}{\theta}\right) \bthetahat.
 \end{eqnarray}
 
-\subsubsection{Grid Choice}
+\subsubsection{Computational Grid}
 In order to discretize the differential operators, 
-a regular grid of size $n_r \times n_\theta$ is used:
+a regular grid of size $n_r \times n_\theta$ is defined, with:
 \begin{eqnarray}
-(r_i,\theta_j) &\in& [1, \infty) \times [0,\pi] \\ 
-r_i &=& (1+\Delta_r)^i \\
-\theta_j &=& \Delta_\theta \cdot j
+(r_i,\theta_j) &\in& [1, \infty) \times [0,\pi], \\ 
+r_i &=& (1+\Delta_r)^i, \\
+\theta_j &=& \Delta_\theta \cdot j,
 \end{eqnarray}
-where a logarithmic grid is used for $r$ and an uniform one is used for $\theta$.
-Note that $r_0 = 1$ and $R_{max} = (1+\Delta_r)^{n_r}$ should be $\gg 1$. Thus:
+where a logarithmic grid spacing is used for $r$ and a uniform grid is used for $\theta$.
+Note that $r_0 = 1$ and $R_{max} = (1+\Delta_r)^{n_r}$ should be much 
+larger than $r_0$. Thus:
 \begin{eqnarray}
-\Delta_r &=& \pars{R_{max}} ^ \frac{1}{n_r} - 1 \\
-\Delta_\theta &=& \frac{\pi}{n_\theta}
+\Delta_r &=& \pars{R_{max}} ^ \frac{1}{n_r} - 1, \\
+\Delta_\theta &=& \frac{\pi}{n_\theta}.
 \end{eqnarray}
 
-This grid induces disjoint subdivision of the domain 
+This grid induces a disjoint subdivision of the domain 
 $\Omega = [1, R_{max}] \times [0,\pi]$ into cells:
 \begin{eqnarray}
-\bigcup_{ij}\Omega_{ij} &=& \Omega
+\bigcup_{ij}\Omega_{ij} &=& \Omega.
 \end{eqnarray}
@@
 \begin{eqnarray}
-\Omega_{ij} &=& [r_{i-1}, r_{i}] \times [\theta_{i-1}, \theta_{i}] \\
-\bar{r}_i &=& \frac{r_{i-1} + r_{i}}{2} \\
-\bar{\theta}_i &=& \frac{\theta_{i-1} + \theta_{i}}{2}
+\Omega_{ij} &=& [r_{i-1}, r_{i}] \times [\theta_{j-1}, \theta_{j}], \\
+\bar{r}_i &=& \frac{r_{i-1} + r_{i}}{2}, \\
+\bar{\theta}_j &=& \frac{\theta_{j-1} + \theta_{j}}{2}.
 \end{eqnarray}
 
-Each variable is discretized with respect of the cell:
+Each variable is discretized with respect of its cell as follows:
 \begin{itemize}
 \item $\varPhi$, $C$ and $P$ are represented by their value at the center of each cell, 
-using a central grid:
+using an all-centered grid:
 \begin{eqnarray}
-\varPhi[i,j] &=& \varPhi(\bar{r}_i, \bar{\theta}_j) \\
-C[i,j] &=& C(\bar{r}_i, \bar{\theta}_j) \\
-P[i,j] &=& P(\bar{r}_i, \bar{\theta}_j) 
+\varPhi^h[i,j] &=& \varPhi(\bar{r}_i, \bar{\theta}_j), \\
+C^h[i,j] &=& C(\bar{r}_i, \bar{\theta}_j), \\
+P^h[i,j] &=& P(\bar{r}_i, \bar{\theta}_j).
 \end{eqnarray}
@@
 \begin{eqnarray}
-V_r[i,j] &=& V_r(r_i, \bar{\theta}_j) \\
-V_\theta[i,j] &=& V_\theta(\bar{r}_i, {\theta}_j)
+V_r^h[i,j] &=& V_r(r_i, \bar{\theta}_j), \\
+V_\theta^h[i,j] &=& V_\theta(\bar{r}_i, {\theta}_j).
 \end{eqnarray}
@@
 \subsubsection{Operator Discretization}
-Finite-volume method with linear interpolation between grids is used for flux 
+A finite-volume method with linear interpolation is used for flux 
 $\boldsymbol{f}$ discretization.
 
-Denote the following discrete central difference operators:
+Define the following discrete central difference operators:
 \begin{eqnarray}
 \cD_r(f)[i,j] &=& \frac{f\left[i+\half,j\right] - f\left[i-\half,j\right]}
-                       {r\left[i+\half,j\right] - r\left[i-\half,j\right]} \\
+                       {r\left[i+\half,j\right] - r\left[i-\half,j\right]}, \\
 \cD_\theta(f)[i,j] &=& \frac{f\left[i,j+\half\right] - f\left[i,j-\half\right]}
-					   {\theta\left[i,j+\half\right] - \theta\left[i,j-\half\right]}
+					   {\theta\left[i,j+\half\right] - \theta\left[i,j-\half\right]}.
 \end{eqnarray}
 
-Denote the following interpolation operators:
+Define the following interpolation operators:
 \begin{eqnarray}
@@
   f\left[i-\half,j\right] 
-}{r\left[i+\half,j\right] - r\left[i-\half,j\right]}
+}{r\left[i+\half,j\right] - r\left[i-\half,j\right]},
 \\
@@
   f\left[i,j-\half\right] 
-}{r\left[i,j+\half\right] - r\left[i,j-\half\right]}
+}{r\left[i,j+\half\right] - r\left[i,j-\half\right]}.
 \end{eqnarray}
@@
 \begin{eqnarray}
-\bnabla \cdot \boldsymbol{f} &=& 0 
+\bnabla \cdot \boldsymbol{f} &=& 0, 
 \\
 \frac{1}{r^2} \cD_r\pars{f_r r^2} + 
-\frac{1}{r \sin\theta} \cD_\theta\pars{f_\theta \sin\theta} &=& 0 
+\frac{1}{r \sin\theta} \cD_\theta\pars{f_\theta \sin\theta} &=& 0, 
 \\
-\cD_r\pars{f_r \cdot r^2 \sin\theta} + \cD_\theta\pars{f_\theta \cdot r \sin\theta} &=& 0 
+\cD_r\pars{f_r \cdot r^2 \sin\theta} + 
+\cD_\theta\pars{f_\theta \cdot r \sin\theta} &=& 0. 
 \end{eqnarray}
 
-Ion flux are discretized on grid cells' boundaries:
+Ion fluxes are discretized on grid cell boundaries:
 \begin{eqnarray}
-I_r &=& -\cI_r(C) \cdot \cD_r(\varPhi) \\
-I_\theta &=& -\cI_\theta(C) \cdot \frac{\cD_\theta(\varPhi)}{r} 
+I_r &=& -\cI_r(C) \cdot \cD_r(\varPhi), \\
+I_\theta &=& -\cI_\theta(C) \cdot \frac{\cD_\theta(\varPhi)}{r}.
 \end{eqnarray}
 
-Salt flux are discretized on grid cells' boundaries 
+Salt fluxes are discretized on grid cell boundaries 
 (using upwind scheme $\mathcal{U}$ for numerical stability at large cell Peclet number):
 \begin{eqnarray}
-J_r &=& -\cD_r(C) + \alpha V_r \cdot \mathcal{U}^{\bV}_r (C) \\
-J_\theta &=& -\frac{\cD_\theta(C)}{r} + \alpha V_\theta \cdot \mathcal{U}^{\bV}_\theta (C) \\
- \mathcal{U}^{\bV}_r(C)[i,j] &=& C\left[i-\frac{\sign(V_r)}{2}, j\right] \\
- \mathcal{U}^{\bV}_\theta(C)[i,j] &=& C\left[i, j-\frac{\sign(V_\theta)}{2}\right] 
+J_r &=& -\cD_r(C) + \alpha V_r \cdot \mathcal{U}^{\bV}_r (C), \\
+J_\theta &=& -\frac{\cD_\theta(C)}{r} + \alpha V_\theta \cdot \mathcal{U}^{\bV}_\theta (C), \\
+ \mathcal{U}^{\bV}_r(C)[i,j] &=& C\left[i-\frac{\sign(V_r)}{2}, j\right], \\
+ \mathcal{U}^{\bV}_\theta(C)[i,j] &=& C\left[i, j-\frac{\sign(V_\theta)}{2}\right]. 
 \end{eqnarray}
@@
 Mass flux $\bV$ is discretized on grid cells boundaries, 
-using velocity staggered grid.
+using the velocity staggered grid.
 
-Force components are discretized on velocity staggered grid, where
-linear interpolation is used for Coulomb force.
+Force components are discretized on the velocity staggered grid, where
+linear interpolation is used for the Coulomb force.
 \begin{eqnarray}
@@
 		  - \frac{2}{r^2 \sin\theta} \cI_r(\cD_\theta (V_\theta \sin\theta))
-          + \cD_r(\varPhi) \cdot \cI_r(\cL(\varPhi)) \\
+          + \cD_r(\varPhi) \cdot \cI_r(\cL(\varPhi)), \\
 F_\theta &=& -\frac{\cD_\theta(P)}{r} 
@@
 		  + \frac{2}{r^2} \cI_\theta(\cD_\theta(F_r))
-		  + \frac{\cD_\theta(\varPhi)}{r} \cdot \cI_\theta(\cL(\varPhi)) \\
+		  + \frac{\cD_\theta(\varPhi)}{r} \cdot \cI_\theta(\cL(\varPhi)), \\
 \cL(f) &=& \frac{1}{r^2}\cD_r\pars{\cD_r(f) r^2} + 
-\frac{1}{r^2 \sin\theta} \cD_\theta\pars{\cD_\theta(f) \cdot \sin\theta}
+\frac{1}{r^2 \sin\theta} \cD_\theta\pars{\cD_\theta(f) \cdot \sin\theta}.
 \end{eqnarray}
@@
 \subsubsection{Boundary Conditions}
-In order to represent discretize problem boundary condtions, 
-``ghost'' points method is used. 
-Variable grid is extended to include points outside the domain's interior,
-so the variables at the ``ghost'' points are set to satisfy 
+In order to discretize boundary condtions, 
+``ghost'' points are employed. 
+The grid is extended to include points outside the domain interior,
+and the variables at the ``ghost'' points are set to satisfy 
 the discretized boundary conditions, following the analysis below.
@@
 \begin{eqnarray}
-\cI_r(\varPhi) &=& -\cI_r(\log C) \\
-\cD_r(\varPhi) &=& \cD_r(\log C) \\
-V_r &=& 0 \\
+\cI_r(\varPhi) &=& -\cI_r(\log C), \\
+\cD_r(\varPhi) &=& \cD_r(\log C), \\
+V_r &=& 0, \\
 V_\theta &=& 4\log\pars{\frac{1 + \exp\left\{\cI_\theta(\zeta)/2\right\}}{2}} \cdot 
-			\cD_\theta(\zeta) \\
-  \zeta &=& - \log \gamma - \cI_r(\varPhi)
+			\cD_\theta(\zeta), \\
+  \zeta &=& - \log \gamma - \cI_r(\varPhi).
 \end{eqnarray}
-The equations are discretized by using ``ghost'' points, outside the interior of the domain:
+The equations are discretized using ``ghost'' points outside the interior of the domain:
 \begin{eqnarray}
- \varPhi[1/2, j] = \frac{\varPhi[0,j] + \varPhi[1,j]}{2} &=& 
-	-\frac{\log C[0,j] + \log C[1,j]}{2} = -\log C[1/2, j] \\
-  \frac{\varPhi[1,j] - \varPhi[0,j]}{\Delta r} &=& 
-	\frac{\log C[1,j] - \log C[0,j]}{\Delta r} 
+ \varPhi^h[1/2, j] = \frac{\varPhi^h[0,j] + \varPhi^h[1,j]}{2} &=& 
+	-\frac{\log C^h[0,j] + \log C^h[1,j]}{2} = -\log C^h[1/2, j], \\
+  \frac{\varPhi^h[1,j] - \varPhi^h[0,j]}{\Delta r} &=& 
+	\frac{\log C^h[1,j] - \log C^h[0,j]}{\Delta r}. 
 \end{eqnarray}
@@
 \begin{eqnarray}
-\varPhi[0,j] &=& -\log\brcs{C[1,j]} \\
-C[0,j] &=& \exp\brcs{-\varPhi[1,j]} \\
-  \zeta[j] &=& \cV - \varPhi[1/2,j]
-                     = -\log\gamma -\frac{\varPhi[0,j] + \varPhi[1,j]}{2}
+\varPhi^h[0,j] &=& -\log\brcs{C^h[1,j]}, \\
+C^h[0,j] &=& \exp\brcs{-\varPhi^h[1,j]}, \\
+  \zeta^h[j] &=& \cV - \varPhi^h[1/2,j]
+                     = -\log\gamma -\frac{\varPhi^h[0,j] + \varPhi^h[1,j]}{2}.
 \end{eqnarray}
-The slipping conditions can be written by:
+The slip condition can be written as:
 \begin{eqnarray}
-V_r[0,j] &=& 0 \\
-V_\theta[1/2,j] &=& 
-4\log\pars{\frac{1 + \exp\left\{\frac{1}{2}\frac{\zeta[j] + \zeta[j+1]}{2}\right\}}{2}} 
-\cdot \frac{\zeta[j+1] - \zeta[j]}{\bar{\theta}_{j+1} - \bar{\theta}_{j}} \\
-  V_\theta[0,j] &=& 2 V_\theta[1/2, j] - V_\theta[1,j]
+V_r^h[0,j] &=& 0, \\
+V_\theta^h[1/2,j] &=& 
+4\log\pars{\frac{1 + \exp\left\{\frac{1}{2}
+ \frac{\zeta^h[j] + \zeta^h[j+1]}{2}\right\}}{2}} 
+\cdot \frac{\zeta^h[j+1] - \zeta^h[j]}{\bar{\theta}_{j+1} - \bar{\theta}_{j}}, \\
+  V^h_\theta[0,j] &=& 2 V^h_\theta[1/2, j] - V^h_\theta[1,j].
 \end{eqnarray}
@@
 \brc{l}{
-\varPhi[i, n_\theta+1] = \varPhi[i, n_\theta] \\
-C[i, n_\theta+1] = C[i, n_\theta] \\
-V_r[i, n_\theta+1] = V_r[i, n_\theta] \\
-V_\theta[i, n_\theta+1] = 0
+\varPhi[i, n_\theta+1] = \varPhi[i, n_\theta], \\
+C[i, n_\theta+1] = C[i, n_\theta], \\
+V_r[i, n_\theta+1] = V_r[i, n_\theta], \\
+V_\theta[i, n_\theta+1] = 0.
 } 
@@
 
-Far away from the ion-exchange boundary ($r\rightarrow\infty$) are:
+Far away from the ion-exchange boundary ($r\rightarrow\infty$) we have:
 \begin{eqnarray}
-\frac{\varPhi[n_r + 1, j] - \varPhi[n_r, j]}{\bar{r}_{n_r + 1} - \bar{r}_{n_r}} 
- & = & -\beta \cos\bar{\theta}_j \\
+\frac{\varPhi[n_r + 1, j] - \varPhi[n_r, j]}{\bar{r}_{n_r + 1} - \bar{r}_{n_r}}, 
+ & = & -\beta \cos\bar{\theta}_j, \\
 C[n_r + 1, j] & = & 1 \\
-V_r[n_r + 1, j] & = & -\cU \cos\bar{\theta}_j \\
-V_\theta[n_r + 1, j] & = & \cU \sin\theta_j
+V_r[n_r + 1, j] & = & -\cU \cos\bar{\theta}_j, \\
+V_\theta[n_r + 1, j] & = & \cU \sin\theta_j.
 \end{eqnarray}
-Since the actual grid is finite, $r_{n_r} = R_{max}$ will have an effect on the solution too.
+
+Because the actual grid is finite, the choice 
+$r_{n_r} = R_{max}$ must be taken large enough so as to have a negligible effect
+on the solution.
 
 Note that $P$ has no boundary conditions -- so the pressure variable is defined 
-on the domain's interior.
+only in the domain interior.
 
@@
 \subsection{Solver Design}
-\subsubsection{Newton Method}
+\subsubsection{Newton's Method}
 An operator $\cO$ is defined by its input vector $\bx$ and its output 
@@
 
-In order to solve the equation $\cO(\bx) = \bzero$, the Newton's method can 
+In order to solve the equation $\cO(\bx) = \bzero$, Newton's method can 
 be applied, given an initial solution $\bx_0$:
 \begin{eqnarray}
-\bzero = \cO(\bx_n + \Delta \bx_n) &\approx& \cO(\bx_n) + \bnabla \cO(\bx_n)\cdot\Delta\bx_n \\
-\bnabla \cO(\bx_n) \cdot \Delta \bx_n &=& -\cO(\bx_n) \\
-\bx_{n+1} &=& \bx_{n} + \Delta \bx_n 
+\bzero = \cO(\bx_n + \Delta \bx_n) &\approx& \cO(\bx_n) + \bnabla \cO(\bx_n)\cdot\Delta\bx_n, \\
+\Rightarrow \bnabla \cO(\bx_n) \cdot \Delta \bx_n &=& -\cO(\bx_n), \\
+\bx_{n+1} &=& \bx_{n} + \Delta \bx_n. 
 \end{eqnarray}
 
-Newton method step required the computation of the residual vector $\cO(\bx)$ and
-the gradient matrix of the operator $\bnabla \cO(\bx)$, 
+Each step requires the computation of the residual vector, $\cO(\bx)$, and
+the gradient matrix of the operator, $\bnabla \cO(\bx)$, 
 given the current solution $\bx = \bx_n$.
-Then, a sparse linear system is to be solved to yield the update for the soltion vector
-$\Delta \bx_n = \bx_{n+1} - \bx_n$.
+Then, a sparse linear system needs to be solved to yield the update for the 
+increment $\Delta \bx_n = \bx_{n+1} - \bx_n$.
 
-When the method does converges $\bx_n \rightarrow \bx_\infty$, 
-the convergence is quadratic:
+When the method converges, $\bx_n \rightarrow \bx_\infty$, 
+the convergence is in general quadratic:
 \begin{eqnarray}
-\|\bx_{n+1} - \bx_\infty\| \le k \|\bx_{n} - \bx_\infty\|^2
+\|\bx_{n+1} - \bx_\infty\| \le k \|\bx_{n} - \bx_\infty\|^2.
 \end{eqnarray}
 Thus, when the initial guess is close enough to the solution, the solver
-will converge in very few steps.
+will typically converge in very few steps.
 
@@
 System variable $\bx$ is defined as the concatenation $[\,\varPhi, C, V_r, V_\theta, P\,]$,
-taking values in the interior of the problem domain grid.
-So each problem variable can be computed by applying an appropriate projection operator
-on $\bx$:
+taking only values in the interior of the problem domain grid.
+Thus, each problem variable can be computed by applying an appropriate projection operator on $\bx$:
 \begin{eqnarray}
-X &=& \cP_X(\bx) \mbox{ for } X \in \left\{\varPhi, C, V_r, V_\theta, P\right\}
+X &=& \cP_X(\bx) \mbox{ for } X \in \left\{\varPhi, C, V_r, V_\theta, P\right\}.
 \end{eqnarray}
 
-The extended variables $\tilde X$ (with ``ghost'' points values 
-from boundary conditions) are be computed, by applying the following non-linear operators:
+The extended variables $\tilde X$ (including ``ghost'' point values) 
+are computed by applying the following nonlinear operators:
 \begin{eqnarray}
-\tilde{\varPhi} &=& \cB_\varPhi(\varPhi, C; \beta) \\
-\tilde{C} &=& \cB_C(C, \varPhi) \\
-\tilde{V_r} &=& \cB_{V_r}(V_r; \cU) \\
-\tilde{V_\theta} &=& \cB_{V_\theta}(V_\theta, C, \varPhi; \cU, \gamma) \\
-\tilde{P} &=& P
+\tilde{\varPhi} &=& \cB_\varPhi(\varPhi, C; \beta), \\
+\tilde{C} &=& \cB_C(C, \varPhi), \\
+\tilde{V_r} &=& \cB_{V_r}(V_r; \cU), \\
+\tilde{V_\theta} &=& \cB_{V_\theta}(V_\theta, C, \varPhi; \cU, \gamma), \\
+\tilde{P} &=& P.
 \end{eqnarray}
@@
 
-The problem can be casted to find a solution to the following non-linear system:
+The problem can be cast as the following non-linear system:
 \begin{eqnarray}
@@
 Assume that $\cU \ui$ is the velocity of the ion exchanger 
-(given the fluid is at rest far away from the particle).
+(given that the fluid is at rest far away from the particle).
 After the convergence of the Newton method solver, $\cO(\bx_n) \rightarrow \bzero$, 
-the ``ghost'' points values are updated using $\tilde\bx = \cB(\bx_\infty)$,
-so the surface force $\boldsymbol{f} = \tT \cdot \bn$ acting on the ion-exchanger surface
-can be computed by integration on the ion exchanger's surface $\mathcal S$.
+the ``ghost'' point values are updated using $\tilde\bx = \cB(\bx_\infty)$,
+so  that the surface force $\boldsymbol{f} = \tT \cdot \bn$ acting 
+on the ion-exchanger surface
+can be computed by integration over the ion exchanger's surface $\mathcal S$.
 
@@
 \bF &=& \oint_\mathcal{S} \boldsymbol{f}  dA = 
-\oint_\mathcal{S} \tT \cdot \bnhat  dA \\
+\oint_\mathcal{S} \tT \cdot \bnhat  dA. \\
 F_\imath = \ui \cdot \bF &=& \oint_\mathcal{S} \ui \cdot \boldsymbol{f}  dA = 
 \oint_\mathcal{S} \ui \cdot \tT \cdot \bnhat  dA = 
-\int_0^\pi f_\imath(\theta) \cdot 2\pi \sin\theta d\theta 
+\int_0^\pi f_\imath(\theta) \cdot 2\pi \sin\theta d\theta ,
 \\  
-f_\imath &=& \ui \cdot \tT \cdot \brhat
+f_\imath &=& \ui \cdot \tT \cdot \brhat,
 \\  
@@
 && -\pars{\cD_r(V_\theta) - \frac{V_\theta}{r}
-+ \frac{1}{r}\cD_r(\varPhi) \cD_{\theta}(\varPhi)}\sin\theta \\
- \mathcal{S} &=& \{\br : \|\br\|_2 = 1\}
++ \frac{1}{r}\cD_r(\varPhi) \cD_{\theta}(\varPhi)}\sin\theta, \\
+ \mathcal{S} &=& \{\br : \|\br\|_2 = 1\}.
 \end{eqnarray}
 
-The integral for $F_\imath$ is approximated by 1D numerical quadrature, to yield 
+The integral for $F_\imath$ is approximated by 1D numerical quadrature
+(using trapezoidal rule), to yield 
 the total force $F_\imath(\cU)$ as a function of the drift velocity $\cU$.
 
-Since the goal is to find steady-state solution, $F_\imath(\cU)$ is required to be zero --
-and the appropriate $\cU$ is found by 1D root-finding algorithm.
+Since the goal is to find steady-state solution, $F_\imath(\cU)$ 
+is required to be zero --
+and the appropriate $\cU$ is found by a simple 1D root-finding algorithm,
+applied as an outer loop.
 
@@
 
-System steady-state drift velocity $\cU(\beta)$ is computed as a function 
-of the electric field magnitude for several values of $\beta$.
+The steady-state drift velocity $\cU(\beta)$ is computed as a function 
+of the electric field magnitude for various values of $\beta$.
 Since the solution $\bx_\infty$ is continous in $\beta$ and $\cU$, 
@@
 
-Object-Oriented Design methodology is used to for solver implementation.
-MATLAB programming language is chosen due to strong numerical capabilities
+Object-Oriented Design methodology is used for implementation.
+The MATLAB programming language is chosen due to strong numerical capabilities
 and high-level language features.
@@
 This interface is implemented by specific operators classes,
-which are used to constuct $\cO = \cE \circ \cB$ operator, so that 
-Newton method solver (that requires computing the residual and the gradient) 
+which are used to constuct the operator $\cO = \cE \circ \cB$, so that 
+the Newton method solver (that requires computing the residual and the gradient) 
 can be applied automatically.
 
-Each such operator may be have other operators as its inputs, so the residual
-and the gradient are computed recursively.
+Each such operator may have other operators as its inputs, so the residual
+and the gradient are computed recursively, using the chain rule.
 
@@
 \begin{eqnarray}
-\cO(\bx) &=& L \bx \\
-\bnabla\cO &=& L 
+\cO(\bx) &=& L \bx, \\
+\bnabla\cO &=& L. 
 \end{eqnarray}
@@
 can be implemented as linear sparse operators, by constructing 
-an appropriate sparse matrix $L$, having $O(\dim \bx)$ non-zeroes)
+an appropriate sparse matrix $L$, having $O(\dim \bx)$ non-zeroes).
 
@@
 \end{eqnarray}
-$f$ is defined and differentiated automatically using MATLAB symbolic toolbox.
+$f$ is defined and differentiated automatically using the MATLAB symbolic toolbox.
 
@@
 \begin{eqnarray}
-\mathcal{C}(\bx) &=& \bc \\
-\bnabla\mathcal{C} &=& \bzero
+\mathcal{C}(\bx) &=& \bc, \\
+\bnabla\mathcal{C} &=& \bzero.
 \end{eqnarray}
@@
 \paragraph{Binary operators}
-Let $\cO_1$ and $\cO_2$ be two operators, so their pointwise addition, subtraction
-and multiplication are defined as follows:
+Let $\cO_1$ and $\cO_2$ be two operators, so their pointwise addition, subtraction,
+and multiplication, are defined as follows:
 \begin{eqnarray}
-(\cO_1 \pm \cO_2)(\bx) &=& \cO_1)(\bx) \pm \cO_2(\bx) \\
-\bnabla (\cO_1 \pm \cO_2)(\bx)   &=& \bnabla\cO_1(\bx) \pm \bnabla\cO_2(\bx) \\
-(\cO_1 \cdot \cO_2)(\bx) &=& \diag(\diag(\cO_1(\bx)) \cdot \diag(\cO_2(\bx))) \\
+(\cO_1 \pm \cO_2)(\bx) &=& \cO_1)(\bx) \pm \cO_2(\bx), \\
+\bnabla (\cO_1 \pm \cO_2)(\bx)   &=& \bnabla\cO_1(\bx) \pm \bnabla\cO_2(\bx), \\
+(\cO_1 \cdot \cO_2)(\bx) &=& \diag(\diag(\cO_1(\bx)) \cdot \diag(\cO_2(\bx))), \\
 \bnabla (\cO_1 \cdot \cO_2)(\bx) &=& \diag(\cO_2(\bx)) \bnabla\cO_1(\bx) 
-                                  + \diag(\cO_1(\bx)) \bnabla\cO_2(\bx)
+                                  + \diag(\cO_1(\bx)) \bnabla\cO_2(\bx).
 \end{eqnarray}
@@
 \begin{eqnarray}
-\cO(\bx) &=& [\cO_1(\bx); \ldots; \cO_N(\bx)] \\
-(\bnabla\cO)(\bx) &=& [(\bnabla\cO_1)(\bx); \ldots; (\bnabla\cO_N)(\bx)]
+\cO(\bx) &=& [\cO_1(\bx); \ldots; \cO_N(\bx)], \\
+(\bnabla\cO)(\bx) &=& [(\bnabla\cO_1)(\bx); \ldots; (\bnabla\cO_N)(\bx)].
 \end{eqnarray}
@@
 After the solver converges ($\bx_n \rightarrow \bx_\infty$), 
-the ``ghost'' points values are computed by applying $\cB$ and
-solving for zero force  $\brhat$ component on $r=1$ boundary
+the ``ghost'' point values are computed by applying $\cB$ and
+solving for zero total force $\bF$.
 
-$F_\imath$ is computed using mid-point quadrature method:
+$F_\imath = \bF \cdot \ui$ is computed using mid-point quadrature method:
 \begin{eqnarray}
@@
 \subsubsection{Steady state drift velocity $\rightarrow \cU$}
-In steady state, the force acting on the particle $F_\imath$ shoud vanish.
+In steady state, the total force acting on the particle $F_\imath$ must vanish.
 This yields an equation on $\cU$:
@@
 \end{eqnarray}
-This equation can be solved using 1D root finding algorithm, e.g. Secant method:
+This equation can be solved using a 1D root finding algorithm, e.g. the secant method:
 \begin{eqnarray}

### 2012-01-21 notes/work/ch01.tex
Revision to notes.

@@
 \subsubsection{Dimensionless Notation}
-Positive and negative ionic concentrations are denoted by $c_+$ and $c_-$ respectively.
-The respective ionic fluxes are denoted by $\bj_+$ and $\bj_-$.
-The electrostatic potential is denoted by $\varphi$. 
+Spatial coordinates $\br$ are normalized by $a^*$ (the characteristic size of the ion-exchanger).
+Positive and negative ionic concentrations are denoted by $c_+$ and $c_-$ respectively, and
+normalized by ambient ionic concentration $c^*$.
+The charge concentration is denoted by $q$ and normalized by $q^* = z F^* c^*$ (where $z$
+is the ionic valence and $F^* = e N_A$ is the Faraday number).
+The respective ionic fluxes are denoted by $\bj_+$ and $\bj_-$ and 
+normalized by $D^* c^*/a^*$ (where $D^*$ is the ionic diffusivity).
+The electrostatic potential is denoted by $\varphi$ and normalized 
+by the thermal voltage $\varphi^* = R^* T^* / z F^*$.
 The fluid velocity and the pressure field are denoted by $\bv$ and $p$ respectively.
+The velocity is normalized by $\eps^* (\varphi^*)^2 / \mu^* a^*$ and the pressure
+is normalized by $\mu^* v^* / a^*$.
+The force is denoted by $\bF$ normalized by $\mu^* v^* a^*$.
+The electric field is denoted by $\bE$ and normalized by $\varphi^* / a^*$.
+The dimensional equations and the nondimensional derivation are 
+described in Appendix \ref{append:nondim}.
 
@@
 \begin{eqnarray}
-  \bj_\pm &=& -\bnabla c_\pm \mp c_\pm \bnabla \varphi + \alpha \bv c_\pm.
+  \bj_\pm &=& -\bnabla c_\pm \mp c_\pm \bnabla \varphi + \alpha \bv c_\pm,
+\end{eqnarray}
+where $\alpha$ is the dimensionless Peclet number:
+\begin{eqnarray}
+\alpha &=&  \frac{a^* v^*}{D^*} = \frac{\eps^* (\varphi^*)^2}{\mu^* D^*}
 \end{eqnarray}
@@
 \begin{eqnarray}
-\delta^2 \Laplacian \varphi &=& -q.
+\delta^2 \Laplacian \varphi &=& -2q,
+\end{eqnarray}
+where $\delta = \delta^* / a^*$ is nondimensional Debye length:
+\begin{eqnarray}
+\delta^2 = \frac{\eps^* \varphi^* / q^*}{(a^*)^2}
 \end{eqnarray}
@@
 \subsubsection{Boundary conditions}
-Far away from the particle, we have uniform flow, uniform electrostatic field
-and uniform ionic concentrations:
+An constant electric field $\bE$ is applied to the system, such that $|\bE| = \beta$.
+The ion-exchanger will acquire a non-zero steady-state velocity $\cU$, which is
+a function of the applied field, and is not known a priori.
+
+Far away from the particle, we have uniform applied electrostatic field, uniform flow 
+and ambient ionic concentrations:
 \begin{eqnarray}
@@
 At its surface $\mathcal{S}$ (defined at $r=1$ with normal $\bn = \brhat$), 
-we have zero slip, anion impermeability, cation selectivity 
-and conductance of the particle:
+we have zero slip, anion impermeability, cation selectivity (with fast Butler-Volmer kinetics)
+and high conductance of the particle (yielding uniform electric potential):
 \begin{eqnarray}
@@
 \bn \cdot \bj_- & = & 0, \\
-c_+ & = & \gamma, \\
+\bn \cdot \bj_+ & = & k (1 - c_+/\gamma) \Rightarrow c_+ \rightarrow \gamma, \\
 \varphi & = & \cV.
@@
 
-The Stokes flow equations have the same form as microscale equations:
+The macroscale Stokes flow equations have the same form as the microscale equations:
 \begin{eqnarray}
@@
 \end{eqnarray}
+
+The total force $\bF(\beta, \cU)$ is a function of the applied electric field $\beta$ and
+the velocity $\cU$.
+For any given electric field $\beta$, the force-free constraint above 
+can be solved numerically for $\cU$ to
+yield the corresponding steady-state velocity.

### 2012-01-21 notes/work/ch02.tex
Revision to notes.

@@
 A finite-volume method with linear interpolation is used for flux 
-$\boldsymbol{f}$ discretization.
+$\boldsymbol{f}^h$ discretization.
 
@@
 \begin{eqnarray}
-\cD_r(f)[i,j] &=& \frac{f\left[i+\half,j\right] - f\left[i-\half,j\right]}
+\cD_r(f^h)[i,j] &=& \frac{f^h\left[i+\half,j\right] - f^h\left[i-\half,j\right]}
                        {r\left[i+\half,j\right] - r\left[i-\half,j\right]}, \\
-\cD_\theta(f)[i,j] &=& \frac{f\left[i,j+\half\right] - f\left[i,j-\half\right]}
+\cD_\theta(f^h)[i,j] &=& \frac{f^h\left[i,j+\half\right] - f^h\left[i,j-\half\right]}
 					   {\theta\left[i,j+\half\right] - \theta\left[i,j-\half\right]}.
@@
 \begin{eqnarray}
-\cI_r(f)[i,j] &=& \frac{
+\cI_r(f^h)[i,j] &=& \frac{
 \pars{r\left[i,j\right] - r\left[i-\half,j\right]} 
-  f\left[i+\half,j\right] + 
+  f^h\left[i+\half,j\right] + 
 \pars{r\left[i+\half,j\right] - r\left[i,j\right]} 
-  f\left[i-\half,j\right] 
+  f^h\left[i-\half,j\right] 
 }{r\left[i+\half,j\right] - r\left[i-\half,j\right]},
 \\
-\cI_\theta(f)[i,j] &=& 
+\cI_\theta(f^h)[i,j] &=& 
 \frac{
 \pars{r\left[i,j\right] - r\left[i,j-\half\right]} 
-  f\left[i,j+\half\right] + 
+  f^h\left[i,j+\half\right] + 
 \pars{r\left[i,j+\half\right] - r\left[i,j\right]} 
-  f\left[i,j-\half\right] 
+  f^h\left[i,j-\half\right] 
 }{r\left[i,j+\half\right] - r\left[i,j-\half\right]}.
@@
 \begin{eqnarray}
-\bnabla \cdot \boldsymbol{f} &=& 0, 
+\bnabla \cdot \boldsymbol{f}^h &=& 0, 
 \\
-\frac{1}{r^2} \cD_r\pars{f_r r^2} + 
-\frac{1}{r \sin\theta} \cD_\theta\pars{f_\theta \sin\theta} &=& 0, 
+\frac{1}{r^2} \cD_r\pars{f^h_r r^2} + 
+\frac{1}{r \sin\theta} \cD_\theta\pars{f^h_\theta \sin\theta} &=& 0, 
 \\
-\cD_r\pars{f_r \cdot r^2 \sin\theta} + 
-\cD_\theta\pars{f_\theta \cdot r \sin\theta} &=& 0. 
+\cD_r\pars{f^h_r \cdot r^2 \sin\theta} + 
+\cD_\theta\pars{f^h_\theta \cdot r \sin\theta} &=& 0. 
 \end{eqnarray}
@@
 \begin{eqnarray}
-I_r &=& -\cI_r(C) \cdot \cD_r(\varPhi), \\
-I_\theta &=& -\cI_\theta(C) \cdot \frac{\cD_\theta(\varPhi)}{r}.
+I^h_r &=& -\cI_r(C^h) \cdot \cD_r(\varPhi^h), \\
+I^h_\theta &=& -\cI_\theta(C^h) \cdot \frac{\cD_\theta(\varPhi^h)}{r}.
 \end{eqnarray}
@@
 \begin{eqnarray}
-J_r &=& -\cD_r(C) + \alpha V_r \cdot \mathcal{U}^{\bV}_r (C), \\
-J_\theta &=& -\frac{\cD_\theta(C)}{r} + \alpha V_\theta \cdot \mathcal{U}^{\bV}_\theta (C), \\
- \mathcal{U}^{\bV}_r(C)[i,j] &=& C\left[i-\frac{\sign(V_r)}{2}, j\right], \\
- \mathcal{U}^{\bV}_\theta(C)[i,j] &=& C\left[i, j-\frac{\sign(V_\theta)}{2}\right]. 
+J^h_r &=& -\cD_r(C^h) + \alpha V^h_r \cdot \mathcal{U}^{\bV^h}_r (C^h), \\
+J^h_\theta &=& -\frac{\cD_\theta(C^h)}{r} + \alpha V^h_\theta \cdot \mathcal{U}^{\bV^h}_\theta (C^h), \\
+ \mathcal{U}^{\bV^h}_r(C^h)[i,j] &=& C^h\left[i-\frac{\sign(V^h_r)}{2}, j\right], \\
+ \mathcal{U}^{\bV^h}_\theta(C^h)[i,j] &=& C^h\left[i, j-\frac{\sign(V^h_\theta)}{2}\right]. 
 \end{eqnarray}
@@
 \begin{eqnarray}
-F_r &=& -\cD_r(P) 
-          + \cL(V_r) - \frac{2}{r^2} V_r 
-		  - \frac{2}{r^2 \sin\theta} \cI_r(\cD_\theta (V_\theta \sin\theta))
-          + \cD_r(\varPhi) \cdot \cI_r(\cL(\varPhi)), \\
-F_\theta &=& -\frac{\cD_\theta(P)}{r} 
-		  + \cL(V_\theta) - \frac{F_\theta}{r^2 \sin^2\theta} 
-		  + \frac{2}{r^2} \cI_\theta(\cD_\theta(F_r))
-		  + \frac{\cD_\theta(\varPhi)}{r} \cdot \cI_\theta(\cL(\varPhi)), \\
-\cL(f) &=& \frac{1}{r^2}\cD_r\pars{\cD_r(f) r^2} + 
-\frac{1}{r^2 \sin\theta} \cD_\theta\pars{\cD_\theta(f) \cdot \sin\theta}.
+F^h_r &=& -\cD_r(P^h) 
+          + \cL(V^h_r) - \frac{2}{r^2} V^h_r 
+		  - \frac{2}{r^2 \sin\theta} \cI_r(\cD_\theta (V^h_\theta \sin\theta))
+          + \cD_r(\varPhi^h) \cdot \cI_r(\cL(\varPhi^h)), \\
+F^h_\theta &=& -\frac{\cD_\theta(P^h)}{r} 
+		  + \cL(V^h_\theta) - \frac{F^h_\theta}{r^2 \sin^2\theta} 
+		  + \frac{2}{r^2} \cI_\theta(\cD_\theta(F^h_r))
+		  + \frac{\cD_\theta(\varPhi^h)}{r} \cdot \cI_\theta(\cL(\varPhi^h)), \\
+\cL(f^h) &=& \frac{1}{r^2}\cD_r\pars{\cD_r(f^h) r^2} + 
+\frac{1}{r^2 \sin\theta} \cD_\theta\pars{\cD_\theta(f^h) \cdot \sin\theta}.
 \end{eqnarray}
@@
 \begin{eqnarray}
-\cI_r(\varPhi) &=& -\cI_r(\log C), \\
-\cD_r(\varPhi) &=& \cD_r(\log C), \\
-V_r &=& 0, \\
-V_\theta &=& 4\log\pars{\frac{1 + \exp\left\{\cI_\theta(\zeta)/2\right\}}{2}} \cdot 
-			\cD_\theta(\zeta), \\
-  \zeta &=& - \log \gamma - \cI_r(\varPhi).
+\cI_r(\varPhi^h) &=& -\cI_r(\log C^h), \\
+\cD_r(\varPhi^h) &=& \cD_r(\log C^h), \\
+V^h_r &=& 0, \\
+V^h_\theta &=& 4\log\pars{\frac{1 + \exp\left\{\cI_\theta(\zeta^h)/2\right\}}{2}} \cdot 
+			\cD_\theta(\zeta^h), \\
+  \zeta^h &=& - \log \gamma - \cI_r(\varPhi^h).
 \end{eqnarray}
@@
 \brc{l}{
-\varPhi[i, 0] = \varPhi[i, 1] \\
-C[i, 0] = C[i, 1] \\
-V_r[i, 0] = V_r[i, 1] \\
-V_\theta[i, 0] = 0
+\varPhi^h[i, 0] = \varPhi^h[i, 1] \\
+C^h[i, 0] = C^h[i, 1] \\
+V_r^h[i, 0] = V_r^h[i, 1] \\
+V_\theta^h[i, 0] = 0
 } 
 \brc{l}{
-\varPhi[i, n_\theta+1] = \varPhi[i, n_\theta], \\
-C[i, n_\theta+1] = C[i, n_\theta], \\
-V_r[i, n_\theta+1] = V_r[i, n_\theta], \\
-V_\theta[i, n_\theta+1] = 0.
+\varPhi^h[i, n_\theta+1] = \varPhi^h[i, n_\theta], \\
+C^h[i, n_\theta+1] = C^h[i, n_\theta], \\
+V_r^h[i, n_\theta+1] = V_r^h[i, n_\theta], \\
+V_\theta^h[i, n_\theta+1] = 0.
 } 
@@
 \begin{eqnarray}
-\frac{\varPhi[n_r + 1, j] - \varPhi[n_r, j]}{\bar{r}_{n_r + 1} - \bar{r}_{n_r}}, 
+\frac{\varPhi^h[n_r + 1, j] - \varPhi^h[n_r, j]}{\bar{r}_{n_r + 1} - \bar{r}_{n_r}}, 
  & = & -\beta \cos\bar{\theta}_j, \\
-C[n_r + 1, j] & = & 1 \\
-V_r[n_r + 1, j] & = & -\cU \cos\bar{\theta}_j, \\
-V_\theta[n_r + 1, j] & = & \cU \sin\theta_j.
+C^h[n_r + 1, j] & = & 1 \\
+V_r^h[n_r + 1, j] & = & -\cU \cos\bar{\theta}_j, \\
+V_\theta^h[n_r + 1, j] & = & \cU \sin\theta_j.
 \end{eqnarray}
@@
 
-Note that $P$ has no boundary conditions -- so the pressure variable is defined 
+Note that $P^h$ has no boundary conditions -- so the pressure variable is defined 
 only in the domain interior.
@@
 (given that the fluid is at rest far away from the particle).
-After the convergence of the Newton method solver, $\cO(\bx_n) \rightarrow \bzero$, 
+After the convergence of the solver, $\cO(\bx_n) \rightarrow \bzero$, 
 the ``ghost'' point values are updated using $\tilde\bx = \cB(\bx_\infty)$,
@@
 The integral for $F_\imath$ is approximated by 1D numerical quadrature
-(using trapezoidal rule), to yield 
+(using the mid-point rule), to yield 
 the total force $F_\imath(\cU)$ as a function of the drift velocity $\cU$.
@@
 
-The steady-state drift velocity $\cU(\beta)$ is computed as a function 
-of the electric field magnitude for various values of $\beta$.
-Since the solution $\bx_\infty$ is continous in $\beta$ and $\cU$, 
-the result of the current iteration is used as an initial solution $\bx_0$ for the problem 
-of the next iteration -- helping the convergence of the iterative solver in use.
+The iterative solver above can be used to compute the steady-state solution for any given $\beta$.
+For $\beta \ll 1$, the linear terms are the dominant ones, so the solution is linear in $\beta$ 
+(as derived in \cite{yariv2010migration}), and the solver convergence is fast.
+
+However, it is no longer true for $\beta \sim O(1)$, since the nonlinear terms become dominant
+and the iterative solver may not converge at all.
+In order to find a solution for such $\beta$, continuation method is used:
+the solver is applied to a sequence of $\{\beta_i\}_{i=0}^n$ such that $\beta_0 = 0$,
+$\beta_n = \beta$ and the solution $\bx_i$ for $\beta_i$ is used as the solver initializer
+for the problem of $\beta_{i+1}$.
+
+Given that $|\beta_{i+1} - \beta_i| < \eps$ for small enough $\eps$, 
+the next solution $\bx_{i+1}$ is close to the previous one $\bx_i$,
+so the iterative solver converges well.
 
@@
 \begin{eqnarray}
-\cF(\bx) &=& [f(x_1); \ldots; f(x_n)] \\
-\bnabla\cF(\bx) &=& \diag(f'(x_1), \ldots, f'(x_n))
+\cF(\bx) &=& [f(x_1); \ldots; f(x_n)], \\
+\bnabla\cF(\bx) &=& \diag\{f'(x_1), \ldots, f'(x_n)\}.
 \end{eqnarray}
@@
 \subsubsection{Total force integration $\rightarrow F_\imath$}
-After the solver converges ($\bx_n \rightarrow \bx_\infty$), 
-the ``ghost'' point values are computed by applying $\cB$ and
-solving for zero total force $\bF$.
+After the iterative Newton solver converges ($\bx_n \rightarrow \bs$), 
+the ``ghost'' point values are computed by computing $\cB(\bs)$ and
+the total force $\bF$ acting on the ion-exchanger.
 
-$F_\imath = \bF \cdot \ui$ is computed using mid-point quadrature method:
+$F_\imath = \bF \cdot \ui$ is computed by using the mid-point quadrature method:
 \begin{eqnarray}
 F_\imath &=& \sum_{i=1}^{n_\theta} f(\bar\theta_i) \cdot 
-              2 \pi \sin\bar\theta_i \cdot (\theta_i - \theta_{i-1})
+              2 \pi \sin\bar\theta_i \cdot \Delta\theta_i
 \end{eqnarray}
@@
 In steady state, the total force acting on the particle $F_\imath$ must vanish.
-This yields an equation on $\cU$:
+This constraint yields an equation, whose solution is the steady-state velocity $\cU$:
 \begin{eqnarray}
@@
 \cU_{n+1} = \frac{F_\imath(\cU_{n})\cU_{n-1} - F_\imath(\cU_{n-1})\cU_{n}}
-{F_\imath(\cU_{n}) - F_\imath(\cU_{n-1})} \rightarrow \cU_\infty
+{F_\imath(\cU_{n}) - F_\imath(\cU_{n-1})} \rightarrow \cU
 \end{eqnarray}
-The result $\cU_\infty$ is the 
+The result $\cU$ is the 
 steady state particle drift velocity for the electric field $\beta$.

### 2012-01-21 notes/work/ch01.tex
Nondimensionalization.

@@
 \subsubsection{Dimensionless Notation}
+
 Spatial coordinates $\br$ are normalized by $a^*$ (the characteristic size of the ion-exchanger).
+
 Positive and negative ionic concentrations are denoted by $c_+$ and $c_-$ respectively, and
-normalized by ambient ionic concentration $c^*$.
-The charge concentration is denoted by $q$ and normalized by $q^* = z F^* c^*$ (where $z$
-is the ionic valence and $F^* = e N_A$ is the Faraday number).
-The respective ionic fluxes are denoted by $\bj_+$ and $\bj_-$ and 
-normalized by $D^* c^*/a^*$ (where $D^*$ is the ionic diffusivity).
-The electrostatic potential is denoted by $\varphi$ and normalized 
-by the thermal voltage $\varphi^* = R^* T^* / z F^*$.
-The fluid velocity and the pressure field are denoted by $\bv$ and $p$ respectively.
-The velocity is normalized by $\eps^* (\varphi^*)^2 / \mu^* a^*$ and the pressure
-is normalized by $\mu^* v^* / a^*$.
-The force is denoted by $\bF$ normalized by $\mu^* v^* a^*$.
-The electric field is denoted by $\bE$ and normalized by $\varphi^* / a^*$.
-The dimensional equations and the nondimensional derivation are 
-described in Appendix \ref{append:nondim}.
+are normalized by ambient ionic concentration $c^*$. The ionic valences are $\pm z$.
+
+The dimensional ionic fluxes are given by Nernst-Plank equation 
+(using Einstein relation for the electric mobility, $\mu_q^* = D^* / k_B^* T^*$):
+\begin{eqnarray}
+\bj^*_\pm &=& 
+-D^* \bnabla c^*_\pm + \bv^* c^*_\pm \mp \frac{z e^* D^*}{k_B^* T^*} c^*_\pm \bnabla \varphi^*,
+\end{eqnarray}
+where $D^*_\pm \approx D^*$ is the ionic diffusivity.
+
+The electric potential $\varphi$ is normalized by the thermal voltage:
+\begin{eqnarray}
+\varphi^* &=& \frac{k_B^* T^*}{z e^*} = \frac{R^* T^*}{z F^*},
+\end{eqnarray}
+where $R^* = k_B^* N_A$ and $F^* = e^* N_A$ is the Faraday number.
+
+The dimensional Stokes equation:
+\begin{eqnarray}
+-\bnabla p^* + \mu^* \bLaplacian \bv^* + \eps^* \Laplacian \varphi^* \bnabla \varphi^* &=& 0.
+\end{eqnarray}
+
+The velocity $\bv$ is normalized by:
+\begin{eqnarray}
+v^* &=& \frac{\eps^* (\varphi^*)^2}{a^* \mu^*},
+\end{eqnarray}
+and the pressure $p$ is normalized by:
+\begin{eqnarray}
+p^* &=& \frac{\mu^* v^*}{a^*} = \frac{\eps^* (\varphi^*)^2}{(a^*)^2}.
+\end{eqnarray}
+
+The fluxes $\bj^*_\pm$ are normalized by:
+\begin{eqnarray}
+j^* = \frac{D^* c^*}{a^*}.
+\end{eqnarray}
+
+The nondimensional Nernst-Plank equation is written as:
+\begin{eqnarray}
+\bj_\pm &=& 
+-\bnabla c_\pm + \alpha \bv c_\pm \mp c_\pm \bnabla \varphi, \\
+\alpha &=&
+\frac{v^* a^*}{D^*} = \frac{\eps^* (\varphi^*)^2}{\mu^* D^*}.
+\end{eqnarray}
+where $\alpha$ is the dimensionless Peclet number.
+
+The dimensional Poisson equation is:
+\begin{eqnarray}
+(c^*_+ - c^*_-) z F^* &=& -\eps^* \Laplacian \varphi^*,
+\end{eqnarray}
+and after nondimensionalization, is:
+\begin{eqnarray}
+c_+ - c_- &=& -\frac{\eps^* \varphi^*}{z F^* c^* (a^*)^2} \Laplacian \varphi = 
+-\delta^2 \Laplacian \varphi,
+\\
+\delta^2 &=& \frac{\eps^* \varphi^*}{c^* F^* z (a^*)^2} = 
+\pars{\frac{\delta^*}{a^*}}^2.
+\end{eqnarray}
+
+The force is denoted by $\bF$ normalized by $\mu^* v^* a^* = \eps^* (\varphi^*)^2$.
+The stress tensor is denoted by $\tT$ and normalized by $p^* = \mu^* v^* / a^*$.
+The electric field is denoted by $\bE$ and normalized by $E^* = \varphi^* / a^*$.
 
@@
 \end{eqnarray}
-where $\alpha$ is the dimensionless Peclet number:
-\begin{eqnarray}
-\alpha &=&  \frac{a^* v^*}{D^*} = \frac{\eps^* (\varphi^*)^2}{\mu^* D^*}
-\end{eqnarray}
+
 Due to conservation of ions, the fluxes are divergence-free:
@@
 \begin{eqnarray}
-\delta^2 \Laplacian \varphi &=& -2q,
-\end{eqnarray}
-where $\delta = \delta^* / a^*$ is nondimensional Debye length:
-\begin{eqnarray}
-\delta^2 = \frac{\eps^* \varphi^* / q^*}{(a^*)^2}
+\delta^2 \Laplacian \varphi &=& -2q.
 \end{eqnarray}
@@
 When $\delta \ll 1$, 
-most of the fluid remains electroneutral ($c_+ \approx c_-$), 
+most of the fluid remains electroneutral ($q \approx 0$, thus $c_+ \approx c_-$), 
 except a thin boundary layer of width $O(\delta)$, 

### 2012-02-01 notes/work/ch02.tex
Nondimensionalization.
Add numerical results.

@@
 \begin{eqnarray}
-\bzero = \cE (\tilde{\bx}) = \cE (\cB (\bx)) = \cO(\bx)
+\bzero = \cE (\tilde{\bx}) = \cE (\cB (\bx)) = \cO(\bx),
 \end{eqnarray}
@@
 steady state particle drift velocity for the electric field $\beta$.
+
+\subsection{Numerical Results}
+The results for steady-state velocity $\cU$ as a function of the electric field magnitude $\beta$
+are shown at Figures \ref{fig:NumResA} and \ref{fig:NumResB}. 
+Since log-log scale is used, blue and red colors are used 
+for positive and negative velocities, respectively.
+
+For small $\beta$, the linear regime dominates, $\cU \propto \beta$. 
+However, from a specific $\beta_c$, the nonlinear regime dominates, such that
+$\cU \propto \beta^3$, until $\beta \sim O(1)$.
+
+The theoretical results for the nonlinear regime are computed by asymptotic expansion of the
+nonlinear system, as described in the following section.
+\begin{figure}[htbp]
+\begin{framed}
+    \begin{center}
+        \includegraphics[width=0.45\textwidth]{figs/A1.eps}
+        \includegraphics[width=0.45\textwidth]{figs/A2.eps}
+        \includegraphics[width=0.45\textwidth]{figs/A3.eps}
+        \includegraphics[width=0.45\textwidth]{figs/A4.eps}
+        \caption{Steady-state velocity $\cU$ as a function of the electric field magnitude $\beta$, 
+        for $\gamma > 1$.}
+        \label{fig:NumResA}
+    \end{center}
+\end{framed}
+\end{figure}
+\begin{figure}[htbp]
+\begin{framed}
+    \begin{center}
+        \includegraphics[width=0.45\textwidth]{figs/B1.eps}
+        \includegraphics[width=0.45\textwidth]{figs/B2.eps}
+        \includegraphics[width=0.45\textwidth]{figs/B3.eps}
+        \includegraphics[width=0.45\textwidth]{figs/B4.eps}
+        \caption{Steady-state velocity $\cU$ as a function of the electric field magnitude $\beta$,
+        for $\gamma < 1$.}
+        \label{fig:NumResB}
+    \end{center}
+\end{framed}
+\end{figure}

### 2012-02-01 src/animate.m

@@ -1,5 +1,5 @@
-function animate
-    S = load('matlab');
+function animate(name)
+    S = load(name);
     figure(1)
     set(gcf, 'PaperPositionMode', 'auto');
 %     set(gcf, 'Position',[100 100 900 600]);
@@ -24,7 +24,7 @@ function animate
         ylabel('Particle velocity magnitude (V)', 'FontSize', 12)
         legend({'Numerical Solver', 'Analytical Approximation'}, ...
             'Location', 'SouthEast', 'FontSize', 8, 'Box', 'on')
-        axis([0.01 1 0.001 1])
+        axis([0.1 10 0.001 10])
         text(0.04, 0.4, s, 'FontSize', 12);
         subplot(2,2,2);
         hold on
@@ -57,3 +57,16 @@ function sphere()
     t = linspace(0, 2*pi, 100);
     fill(cos(t), sin(t), 'k');
 end
+
+function show(func, sol, name, Rmax, dir, varargin)
+    g = sol.grid.(name);
+    Z = (sol.(name));
+    I = g.x < Rmax;
+    X = g.X .* cos(g.Y);
+    Y = g.X .* sin(g.Y);
+    X = X(I, :);
+    Y = Y(I, :) * dir;
+    Z = Z(I, :);
+    func(X, Y, Z, varargin{:});
+end
+

### 2012-02-01 src/run.m

@@ -1,0 +1,6 @@
+function run(path, pattern, func)
+D = dir(fullfile(path, pattern));
+for k = 1:numel(D)
+    n = D(k).name;
+    func(fullfile(path, n));
+end

### 2012-02-01 src/show.m

@@ -1,6 +1,82 @@
-function show(func, sol, name, Rmax, dir, varargin)
+function show(name)
+    load(name);
+    figure(1); clf;
+%     set(gcf, 'PaperPositionMode', 'auto');
+%     set(gcf, 'Position',[100 100 900 600]);
+    v = attr(solutions, 'Vinf');
+    betas = attr(solutions, 'beta');
+
+    g = sol.gamma;
+    B3 = (31./(320*(g.^(1./2) + 1)) - 9./(320*(g.^(1./2) + 1).^2) + 1./1680);
+    B1 = 2*log(1./(2*g.^(1./2)) + 1./2);
+    b = logspace(log10(min(betas)), log10(max(betas)), 1000);
+    w = b.^3*(B3 - B1*11./320) + b*B1;
+    w3 = b.^3*(B3 - B1*11./320);
+    w1 = b*B1;
+    
+    clf; 
+    h = [];
+    h = [h; graph(betas, v, '.')]; hold on; 
+    h = [h; graph(b, w1+w3, '-')]; 
+    graph(b, w1, ':'); 
+    graph(b, w3, ':'); 
+    title(sprintf('grid = [%d x %d], Rmax = %.1e, gamma = %.4f, alpha = %.4f', ...
+        numel(sol.grid.radius), numel(sol.grid.theta), max(sol.grid.radius), ...
+        sol.gamma, sol.alpha))
+    xlabel('beta (electric field)')
+    ylabel('U (steady-state velocity)')
+    hold off;
+    legend(h, {'Numerical (+)', 'Numerical (-)', ...
+        'Theoretical (+)', 'Theoretical (-)'}, 'Location', 'Best');
+    grid on; grid minor;
+    print('-depsc2', [name(1:end-4) '.eps'])
+
+    %{
+    clf; hold on   
+    for k = 1:numel(betas)
+        s = solutions{k};
+        c = mean(s.C(1:2, :));
+        c = (((c - 1) ./ s.beta) + 1);
+        phi = mean(s.Phi(1:2, :)) ./ s.beta;
+        v = mean(s.Vy(1:2, :) ./ s.beta);
+        plot(180 * s.grid.C.y ./ pi, [c; phi], 180 * s.grid.Vy.y ./ pi, v);
+        xlim([0 180])
+    end
+    hold off;
+    for k = 1:numel(betas)
+        s = solutions{k};
+        clf; hold on        
[…]

### 2012-02-01 symbolic/asymp.m

@@ -2,7 +2,7 @@ function asymp
 
     syms pi b r t a g U1 U2 U3 real
     syms U3a U3b real
-    
+      
     order = 3;
         
     bnd = @(f) subs(f, r, 1);
@@ -148,3 +148,7 @@ function assert_zero(e, msg)
     end
 end
 
+function F = gradient(f)
+    syms r t
+    F = [diff(f, r); diff(f, t) / r];
+end

### 2012-02-01 symbolic/gradient.m

@@ -1,4 +1,0 @@
-function F = gradient(f)
-    syms r t
-    F = [diff(f, r); diff(f, t) / r];
-end

### 2012-02-14 symbolic/asymp.m
MATLAB R13 added sym/gradient.

@@ -74,13 +74,13 @@ function asymp
     p = b^2 * p2 + b^3 * p3;
     
     %% Equations
-    eq1 = divergence(c * gradient(phi));
+    eq1 = divergence(c * grad(phi));
     assert_zero( series(eq1, b, 0, order), 'ion flux' )
     
-    eq2 = scalar_laplacian(c) - a * sum(v .* gradient(c));
+    eq2 = scalar_laplacian(c) - a * sum(v .* grad(c));
     assert_zero( series(eq2, b, 0, order), 'salt flux' )
     
-    eq3 = [vector_laplacian(v) - gradient(p) + scalar_laplacian(phi)*gradient(phi); ...
+    eq3 = [vector_laplacian(v) - grad(p) + scalar_laplacian(phi)*grad(phi); ...
            divergence(v)];
 
     assert_zero( series(eq3, b, 0, order), 'Stokes' )
@@ -115,7 +115,7 @@ function asymp
     assert_zero( vb(1), 'no penetration' );
     assert_zero( slip_error, 'slip condition' );
 
-    assert_zero(limit(gradient(phi), r, inf) - b*[-cos(t);sin(t)], 'boundary R=Inf for Phi' )
+    assert_zero(limit(grad(phi), r, inf) - b*[-cos(t);sin(t)], 'boundary R=Inf for Phi' )
 %     assert_zero(limit(c, r, inf) - 1, 'boundary R=Inf for C' ) % ??? %
     
     Uinf = simple([-cos(t), sin(t)]*simple(limit(v, r, inf)));
@@ -148,7 +148,3 @@ function assert_zero(e, msg)
     end
 end
 
-function F = gradient(f)
-    syms r t
-    F = [diff(f, r); diff(f, t) / r];
-end

### 2012-02-14 symbolic/grad.m

@@ -1,0 +1,4 @@
+function F = grad(f)
+    syms r t
+    F = [diff(f, r); diff(f, t) / r];
+end

### 2012-02-14 symbolic/scalar_laplacian.m

@@ -1,3 +1,3 @@
 function L = scalar_laplacian(f)
-    L = simplify(divergence(gradient(f)));
+    L = simplify(divergence(grad(f)));
 end

### 2012-02-14 symbolic/test.m

@@ -19,7 +19,7 @@ for k = 1:size(C ,1)
     p = r ^ p(1);
 
     L = @(psi) simple(vector_laplacian(curl(psi)));
-    G = @(p) -simple(gradient(p));
+    G = @(p) -simple(grad(p));
 
     ops = {L, L, G, G};
     u = [sin(t)^2*[1, sin(t)^2]*r^4; cos(t)*r*[1, sin(t)^2]].'*p;

### 2012-02-14 src/show.m
Add more figures

@@ -1,4 +1,5 @@
 function show(name)
+    disp(name)
     load(name);
     figure(1); clf;
 %     set(gcf, 'PaperPositionMode', 'auto');
@@ -13,7 +14,6 @@ function show(name)
     w = b.^3*(B3 - B1*11./320) + b*B1;
     w3 = b.^3*(B3 - B1*11./320);
     w1 = b*B1;
-    
     clf; 
     h = [];
     h = [h; graph(betas, v, '.')]; hold on; 
@@ -30,32 +30,37 @@ function show(name)
         'Theoretical (+)', 'Theoretical (-)'}, 'Location', 'Best');
     grid on; grid minor;
     print('-depsc2', [name(1:end-4) '.eps'])
-
-    %{
-    clf; hold on   
     for k = 1:numel(betas)
         s = solutions{k};
-        c = mean(s.C(1:2, :));
-        c = (((c - 1) ./ s.beta) + 1);
-        phi = mean(s.Phi(1:2, :)) ./ s.beta;
-        v = mean(s.Vy(1:2, :) ./ s.beta);
-        plot(180 * s.grid.C.y ./ pi, [c; phi], 180 * s.grid.Vy.y ./ pi, v);
-        xlim([0 180])
-    end
-    hold off;
-    for k = 1:numel(betas)
-        s = solutions{k};
-        clf; hold on        
-        % apply(@contour, s, 'Psi', 10, +1, s.Vinf * linspace(-1, 1, 50));
         b = s.beta;
         r = s.grid.Psi.X;
         t = s.grid.Psi.Y;
         g = s.gamma;
[…]

### 2012-02-14 symbolic/asymp.m

@@ -14,9 +14,9 @@ function asymp
     phi1 = (1/4 * r^(-2) - r) * cos(t);
     c1 = 3/4 * r^(-2) * cos(t);
     % Streamfunction
-    psi1 = (r^-1 - r^2)*sin(t)^2/2;
+    psi1 = U1 * (r^-1 - r^2)*sin(t)^2/2;
     assert_zero(E4(psi1), '')
-    v1 = U1 * curl( psi1 ); 
+    v1 = curl( psi1 ); 
     
     %% O(beta^2) : Homogeneous equations
     % Non-homogeneous solution (Phi & C)
@@ -26,9 +26,9 @@ function asymp
     phi2 = phi2 + 3*(1/16 - a*U1/32)/r + (a*U1/32 - 1/16)*(3*cos(t)^2 - 1)/r^3;
     c2 = c2 + 3*(1/16 - a*U1/32)/r + ((5*U1*a)/32 + 1/16)*(3*cos(t)^2 - 1)/r^3;
     % Streamfunction (homogeneous Stokes, for sin(2t) boundary conditions)
-    psi2 = (r^-2 - 1)*(cos(t)*sin(t)^2);
+    psi2 = U2 * (r^-2 - 1)*(cos(t)*sin(t)^2);
     assert_zero(E4(psi2), '')
-    v2 = U2 * curl( psi2 );
+    v2 = curl( psi2 );
     p2 = U2 * 2 * r^-3 * (1 - 3*cos(t)^2);
 
     %% O(beta^3)
@@ -70,7 +70,9 @@ function asymp
     %% Variables
     phi = b * phi1 + b^2 * phi2 + b^3 * phi3;
     c = 1 + b * c1 + b^2 * c2 + b^3 * c3;
+    psi = b * psi1 + b^2 * psi2 + b^3 * psi3;
     v = b * v1 + b^2 * v2 + b^3 * v3;
+    assert_zero( v - curl(psi), 'streamfunction' );
     p = b^2 * p2 + b^3 * p3;
     
     %% Equations
@@ -120,6 +122,7 @@ function asymp
     
     Uinf = simple([-cos(t), sin(t)]*simple(limit(v, r, inf)));
     Uinf = subs(Uinf, [U1 U2 U3a U3b], [W1 W2 W3a W3b]);
+    psi = subs(psi, [U1 U2 U3a U3b], [W1 W2 W3a W3b]);
     
     if a == 0
         Winf = b*(1 - 11/320*b^2)*W1 ...

### 2012-02-21 notes/work/ch04.tex
Review.

\section{Numerical Results}
The results for steady-state velocity $\cU$ as a function of the electric field magnitude $\beta$
are shown at Figures \ref{fig:NumResA} and \ref{fig:NumResB}. 
Since log-log scale is used, blue and red colors are used 
for positive and negative velocities, respectively.

For small $\beta$, the linear regime dominates, $\cU \propto \beta$. 
However, from a specific $\beta_c$, the nonlinear regime dominates, such that
$\cU \propto \beta^3$, until $\beta \sim O(1)$.

The streamlines for a specific $\gamma$ are shown at Figure \ref{fig:NumResC} for
various electric field magnitudes $\beta$.

The theoretical results for the nonlinear regime are computed by asymptotic expansion of the
nonlinear system, as described in the previous section.
\begin{figure}[htbp]
\begin{framed}
    \begin{center}
        \includegraphics[width=0.45\textwidth]{figs/A1.eps}
        \includegraphics[width=0.45\textwidth]{figs/A2.eps}
        \includegraphics[width=0.45\textwidth]{figs/A3.eps}
        \includegraphics[width=0.45\textwidth]{figs/A4.eps}
        \caption{Steady-state velocity $\cU$ as a function of the electric field magnitude $\beta$, 
        for $\gamma > 1$.}
        \label{fig:NumResA}
    \end{center}
\end{framed}
\end{figure}
\begin{figure}[htbp]
\begin{framed}
    \begin{center}
        \includegraphics[width=0.45\textwidth]{figs/B1.eps}
        \includegraphics[width=0.45\textwidth]{figs/B2.eps}
        \includegraphics[width=0.45\textwidth]{figs/B3.eps}
        \includegraphics[width=0.45\textwidth]{figs/B4.eps}
        \caption{Steady-state velocity $\cU$ as a function of the electric field magnitude $\beta$,
        for $\gamma < 1$.}
        \label{fig:NumResB}
    \end{center}
\end{framed}
\end{figure}
\begin{figure}[htbp]
\begin{framed}
    \begin{center}
        \includegraphics[width=0.3\textwidth]{figs/D1n.eps}
        \includegraphics[width=0.3\textwidth]{figs/D1a.eps}

        \includegraphics[width=0.3\textwidth]{figs/D2n.eps}
        \includegraphics[width=0.3\textwidth]{figs/D2a.eps}

        \includegraphics[width=0.3\textwidth]{figs/D3n.eps}
        \includegraphics[width=0.3\textwidth]{figs/D3a.eps}

        \includegraphics[width=0.3\textwidth]{figs/D4n.eps}
        \includegraphics[width=0.3\textwidth]{figs/D4a.eps}
        \caption{Streamlines of the flow for various electric field values: numerical results (left)
        and analytical approximation (right).}
        \label{fig:NumResC}
    \end{center}
\end{framed}
\end{figure}

### 2012-02-21 src/secant.m

@@ -20,7 +20,7 @@ end
 function sol = step(x, y)
     dx = x(2) - x(1);
     dy = y(2) - y(1);
-    if dx && dy
+    if dx ~= 0 && dy ~= 0
         sol = x(1) - y(1) * dx / dy;
     else
         sol = x(2);

### 2012-02-21 notes/article/main.tex
Add article.

\documentclass[final]{elsarticle}

\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsthm}

\journal{Journal of Computational Physics}

\begin{document}

\begin{frontmatter}

\title{Computational Electrokinetics}
\author[tech]{Roman Zeyde}
\author[tech]{Irad Yavneh}

\address[tech]{Technion, Israel}

\begin{abstract}
This is the abstract.
\end{abstract}

\begin{keyword}
numerical \sep electrokinetics 
\end{keyword}

\end{frontmatter}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction} \label{intro}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Governing Equations} \label{equations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Algorithm Description} \label{algorithm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Tests} \label{results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions and Future Work} \label{conclusions}

\bibliographystyle{elsarticle-num}
\bibliography{}

\end{document}

### 2012-02-21 notes/article/main.tex
Add content to elsarticle.

@@
 \usepackage{graphicx}
+\usepackage{amsmath} % Required for \eqref
 \usepackage{amssymb}
 \usepackage{amsthm}
+\usepackage{units}   % Required for \nicefrac
+\usepackage{float}   % Required for algorithm and floating environments
+\usepackage{graphicx}% Required for figures and imagesf
+\usepackage{amsfonts}
+\usepackage{mathrsfs}
+\usepackage[colorlinks]{hyperref}
+\usepackage{framed}
+
+\floatstyle{ruled}
+\newfloat{program}{thp}{lop}
+%-------------------------------------------
+\newcommand{\sign}{\ensuremath{\mathrm{sign}}}
+\newcommand{\diag}{\ensuremath{\mathrm{diag}}}
+\newcommand{\trace}[1]{\ensuremath{\mathrm{trace}\left( #1 \right)}}
+\newcommand{\norm}[1]{\ensuremath{\left\|#1\right\|_2^2}}
+\newcommand{\func}[2]{\ensuremath{\mathrm{#1}\left( #2 \right)}}
+\newcommand\eps \epsilon
+\newcommand{\R}{\ensuremath{\mathbb{R}}}
+\newcommand{\N}{\ensuremath{\mathbb{N}}}
+\newcommand{\real}{\ensuremath{\mathbb{R}}}
+\newcommand{\cl}[1]{\ensuremath{\mathcal{#1}}}
+\newcommand{\suppsize}[1]{\ensuremath{|\mathcal{#1}|}}
+\newcommand{\vect}[1]{\ensuremath{\mathbf{#1}}}
+\newcommand{\matr}[1]{\ensuremath{\mathbf{#1}}}
+\newcommand{\deriv}[2]{\frac{\partial #1}{\partial #2}}
+\newcommand{\arr}[2]{\begin{array}{#1}#2\end{array}}
+\newcommand{\mat}[2]{\left(\begin{array}{#1}#2\end{array}\right)}
+\newcommand{\brc}[2]{\left\{\begin{array}{#1}#2\end{array}\right.}
+\newcommand{\pars}[1]{\left(#1\right)}
+\newcommand{\brcs}[1]{\left\{#1\right\}}
+\newcommand{\half}{\frac{1}{2}}
+
+% Bold symbols and operators
+\newcommand\Laplacian{\nabla^2}
+\newcommand\bnabla{\boldsymbol{\nabla}}
+\newcommand\bLaplacian{\boldsymbol{\nabla}^2}
+\newcommand\bcdot{\boldsymbol{\cdot}}
+\newcommand\bU{\mathscr{\boldsymbol{U}}}
+\newcommand\bv{\boldsymbol{v}}
+\newcommand\bV{\boldsymbol{V}}
+\newcommand\bE{\boldsymbol{E}}
+\newcommand\be{\boldsymbol{\hat{e}}}
+\newcommand\bn{\boldsymbol{\hat{n}}}
+\newcommand\bk{\boldsymbol{\hat{k}}}
+\newcommand\bj{\boldsymbol{j}}
+\newcommand\bi{\boldsymbol{i}}
+\newcommand\bs{\boldsymbol{s}}
+\newcommand\bA{\boldsymbol{A}}
+\newcommand\bF{\boldsymbol{F}}
+\newcommand\bI{\boldsymbol{I}}
+\newcommand\bJ{\boldsymbol{J}}
+\newcommand\bx{\boldsymbol{x}}
+\newcommand\by{\boldsymbol{y}}
+\newcommand\bz{\boldsymbol{z}}
+\newcommand\br{\boldsymbol{r}}
+\newcommand\bc{\boldsymbol{c}}
+\newcommand\bxhat{\hat{\bx}}
+\newcommand\byhat{\hat{\by}}
+\newcommand\bzhat{\hat{\bz}}
+\newcommand\brhat{\hat{\br}}
+\newcommand\bnhat{\hat{\boldsymbol{n}}}
+\newcommand\btheta{\boldsymbol{\theta}}
+\newcommand\bthetahat{\hat{\btheta}}
+\newcommand\bphi{\boldsymbol{\phi}}
+\newcommand\bphihat{\hat{\bphi}}
+\newcommand\bzero{\boldsymbol{0}}
+\newcommand\bomega{\boldsymbol{\omega}}
+\newcommand\bpsi{\boldsymbol{\psi}}
+
+% Calligraphic symbols
+\newcommand\cB{\mathcal{B}}
+\newcommand\cE{\mathcal{E}}
+\newcommand\cF{\mathcal{F}}
+\newcommand\cO{\mathcal{O}}
+\newcommand\cG{\mathcal{G}}
+\newcommand\cI{\mathcal{I}}
+\newcommand\cP{\mathcal{P}}
+\newcommand\cD{\mathcal{D}}
+\newcommand\cL{\mathcal{L}}
+\newcommand\cU{\mathscr{U}}
+\newcommand\cV{\mathscr{V}}
+\newcommand\cW{\mathscr{W}}
+
+% Tensors
+\newcommand\tI{\mathsf{I}}
+\newcommand\tS{\mathsf{S}}
+\newcommand\tT{\mathsf{T}}
+
+% Unit vector
+\newcommand\ui{\boldsymbol{\hat{\imath}}}
+
+\setlength{\textheight}{8.7in}
+\setlength{\columnsep}{2.0pc}
+\setlength{\textwidth}{6.6in}
+% \setlength{\footheight}{0.2in}
+\setlength{\topmargin}{0.05in}
+\setlength{\headheight}{0.2in}
+\setlength{\headsep}{0.1in}
+\setlength{\evensidemargin}{0in}
+\setlength{\oddsidemargin}{0in}
+% \setlength{\parindent}{1pc}
+\setlength{\parindent}{0.0 in}
+\setlength{\parskip}{0.1 in}
 
@@
 \section{Governing Equations} \label{equations}
+Electrokinetic theory describes the dynamics of charged particles
+in ionic fluids \cite{kirby2010book}. When a particle acquires surface charge, a layer
+of ions of opposite charge is attracted to the surface via
+electric forces, creating a double-layer structure around the
+particle (see Figure \ref{fig:EDL}). This structure, called
+``Debye layer'', electrically screens the surface charge, thus
+creating a potential difference between the particle and the outer
+layer of the fluid bulk.
+\begin{figure}[htbp]
+\begin{framed}
+    \begin{center}
+        \includegraphics[width=0.25\textwidth]
+            {figs/ElectricDoubleLayer.eps}
+        \caption{Schematic structure of the double layer:
+        (1) particle surface, (2) Debye layer and (3) fluid bulk.
+        If the particle surface has positive (blue) surface charge,
+        it attracts negative (red) ions from the fluid making the
+        Debye layer negatively charged (as opposed to the rest of
+        the fluid bulk, which is electrically neutral).
+        The zeta potential is defined as the voltage drop across (2).}
+        \label{fig:EDL}
+    \end{center}
+\end{framed}
+\end{figure}
+In cases where the layer width is much smaller than the particle's
+size, an analytical asymptotic solution for the Debye layer
+dynamics can be found \cite{yariv2010asymptotic}.
+
+The partial differential equations that descibe the system dynamics
+are coupled and non-linear. 
+In general, they have no analytic solution. Moreover,
+any numerical solver must handle the scale disparity caused by the
+Debye layer width being much smaller than the particle's size. A
+closed-form linear asymptotic solution has been developed for
+spherical ion-exchanging particles and weak electric field in an
+axisymmetric setting \cite{yariv2010migration} but it is hard to extend this
+analytic solution to more general systems. Once the electric field
+becomes stronger, significant nonlinear phenomena are expected.
+This interesting regime has not yet been explored.
+
+Recently, it has been conceived that such type of dynamics
+can be very useful in transporting and manipulating micro-
+and nanoscale objects for many nanotechnology applications,
+such as the self-assembly of superstructures, roving sensors, 
+drug-delivery systems and useful nanomachinery 
+\cite{howse2007self,paxton2004catalytic,pumera2010electrochemically}.
+However, since the analytic model for these electrokinetic
+phenomena has no closed-form analytic solution, a numerical
+solver has to be developed for analysing such system.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Micro-scale phenomena}
+
+\subsubsection{Dimensionless Notation}
+
+Spatial coordinates $\br$ are normalized by $a^*$ (the characteristic size of the ion-exchanger).
+
+Positive and negative ionic concentrations are denoted by $c_+$ and $c_-$ respectively, and
+are normalized by ambient ionic concentration $c^*$. The ionic valences are $\pm z$.
+
+The dimensional ionic fluxes are given by Nernst-Plank equation 
+(using Einstein relation for the electric mobility, $\mu_q^* = D^* / k_B^* T^*$):
+\begin{eqnarray}
+\bj^*_\pm &=& 
+-D^* \bnabla c^*_\pm + \bv^* c^*_\pm \mp \frac{z e^* D^*}{k_B^* T^*} c^*_\pm \bnabla \varphi^*,
+\end{eqnarray}
+where $D^*$ is the ionic diffusivity.
+
+The electric potential $\varphi$ is normalized by the thermal voltage:
+\begin{eqnarray}
+\varphi^* &=& \frac{k_B^* T^*}{z e^*} = \frac{R^* T^*}{z F^*},
+\end{eqnarray}
+where $R^* = k_B^* N_A$ and $F^* = e^* N_A$ is the Faraday number.
+
+The dimensional Stokes equation:
+\begin{eqnarray}
+-\bnabla p^* + \mu^* \bLaplacian \bv^* + \eps^* \Laplacian \varphi^* \bnabla \varphi^* &=& 0.
+\end{eqnarray}
+
+The velocity $\bv$ is normalized by:
+\begin{eqnarray}
+v^* &=& \frac{\eps^* (\varphi^*)^2}{a^* \mu^*},
+\end{eqnarray}
+and the pressure $p$ is normalized by:
+\begin{eqnarray}
+p^* &=& \frac{\mu^* v^*}{a^*} = \frac{\eps^* (\varphi^*)^2}{(a^*)^2}.
+\end{eqnarray}
+
+The fluxes $\bj^*_\pm$ are normalized by:
+\begin{eqnarray}
+j^* = \frac{D^* c^*}{a^*}.
+\end{eqnarray}
+
+The nondimensional Nernst-Plank equation is written as:
+\begin{eqnarray}
+\bj_\pm &=& 
+-\bnabla c_\pm + \alpha \bv c_\pm \mp c_\pm \bnabla \varphi, \\
+\alpha &=&
+\frac{v^* a^*}{D^*} = \frac{\eps^* (\varphi^*)^2}{\mu^* D^*}.
+\end{eqnarray}
+where $\alpha$ is the dimensionless Peclet number.
+
+The dimensional Poisson equation is:
+\begin{eqnarray}
+(c^*_+ - c^*_-) z F^* &=& -\eps^* \Laplacian \varphi^*,
+\end{eqnarray}
+and after nondimensionalization, is:
+\begin{eqnarray}
+c_+ - c_- &=& -\frac{\eps^* \varphi^*}{z F^* c^* (a^*)^2} \Laplacian \varphi = 
+-\delta^2 \Laplacian \varphi,
+\\
+\delta^2 &=& \frac{\eps^* \varphi^*}{c^* F^* z (a^*)^2} = 
+\pars{\frac{\delta^*}{a^*}}^2.
+\end{eqnarray}
+
+The force is denoted by $\bF$ normalized by $\mu^* v^* a^* = \eps^* (\varphi^*)^2$.
+The stress tensor is denoted by $\tT$ and normalized by $p^* = \mu^* v^* / a^*$.
+The electric field is denoted by $\bE$ and normalized by $E^* = \varphi^* / a^*$.
+
+\subsubsection{Nernst-Planck Equations}
+The ionic fluxes are given by ion diffusion, electrostatic forces and ion advection by the fluid:
+\begin{eqnarray}
+  \bj_\pm &=& -\bnabla c_\pm \mp c_\pm \bnabla \varphi + \alpha \bv c_\pm,
+\end{eqnarray}
+
+Due to conservation of ions, the fluxes are divergence-free:
+\begin{eqnarray}
+\bnabla \cdot \bj_\pm &=& 0.
+\end{eqnarray}
+These equation may be re-written by using the following transform:
+\begin{eqnarray}
+  c &=& \frac{c_+ + c_-}{2},\\
+  q &=& \frac{c_+ - c_-}{2}.
+\end{eqnarray}
+Thus, salt and charge fluxes are defined by:
+\begin{eqnarray}
+  \bj &=& \frac{\bj_+ + \bj_-}{2} = -\bnabla c - q \bnabla \varphi + \alpha \bv c, \\
+  \bi &=& \frac{\bj_+ - \bj_-}{2} = -\bnabla q - c \bnabla \varphi + \alpha \bv q,
+\end{eqnarray}
+and are divergence-free as well:
+\begin{eqnarray}
+\bnabla \cdot \bj &=& 0, \\
+\bnabla \cdot \bi &=& 0. 
+\end{eqnarray}
+
+\subsubsection{Incompressible Stokes Flow with Electrostatic Force}
+Mass conservation (due to constant fluid density):
+\begin{eqnarray}
+\bnabla \cdot \bv &=& 0.
+\end{eqnarray}
+Momentum conservation (force balance):
+\begin{eqnarray}
+\Laplacian \bv - \bnabla p + \bnabla \varphi \Laplacian \varphi &=& 0.
+\end{eqnarray}
+Free charge density is given by the Poisson equation:
+\begin{eqnarray}
+\delta^2 \Laplacian \varphi &=& -2q.
+\end{eqnarray}
+
+\subsubsection{Boundary conditions}
+An constant electric field $\bE$ is applied to the system, such that $|\bE| = \beta$.
+The ion-exchanger will acquire a non-zero steady-state velocity $\cU$, which is
+a function of the applied field, and is not known a priori.
+
+Far away from the particle, we have uniform applied electrostatic field, uniform flow 
+and ambient ionic concentrations:
+\begin{eqnarray}
+\bv &\rightarrow& -\cU \ui, \\
+\bE = -\bnabla \varphi &\rightarrow& \beta\ui, \\
+c_\pm &\rightarrow& 1.
+\end{eqnarray}
+
+We consider a spherical ion-exchanger. 
+At its surface $\mathcal{S}$ (defined at $r=1$ with normal $\bn = \brhat$), 
+we have zero slip, anion impermeability, cation selectivity (with fast Butler-Volmer kinetics)
+and high conductance of the particle (yielding uniform electric potential):
+\begin{eqnarray}
+\bv & = & \bzero, \\
+\bn \cdot \bj_- & = & 0, \\
+\bn \cdot \bj_+ & = & k (1 - c_+/\gamma) \Rightarrow c_+ \rightarrow \gamma, \\
+\varphi & = & \cV.
+\end{eqnarray}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Separation of scales}
+When $\delta \ll 1$, 
+most of the fluid remains electroneutral ($q \approx 0$, thus $c_+ \approx c_-$), 
+except a thin boundary layer of width $O(\delta)$, 
+also known as the ``Debye layer'', surrounding the ion exchanger.
+
+\subsubsection  {Bulk-scale equations}
+The Nernst-Planck equations above for the fluid bulk (outside
+the boundary layer), using bulk variables, read:
+\begin{eqnarray}
+  Q & = & 0, \\
+  C & = & C_+ = C_-, \\
+\bJ &=& -\bnabla C + \alpha \bV C, \\
+\bI &=& -C \bnabla \varPhi.
+\end{eqnarray}
+Because the flow is incompressible ($\bnabla \cdot V = 0$), 
+ion conservation results in the following equations:
+
+\begin{enumerate}
+\item Salt conservation macroscale equation:
+\begin{eqnarray}
+\bnabla \cdot \bJ = \Laplacian C - \alpha \bV \cdot \bnabla C = 0. 
+\end{eqnarray}
+
+\item Charge conservation macroscale equation:
+\begin{eqnarray}
+\bnabla \cdot \bI = \bnabla \cdot \pars{ C \bnabla \varPhi } = 0.
+\end{eqnarray}
+\end{enumerate}
+
+The macroscale Stokes flow equations have the same form as the microscale equations:
+\begin{eqnarray}
+\bnabla \cdot \bV &=& 0, \\
+\Laplacian \bV - \bnabla P + \bnabla \varPhi \Laplacian \varPhi &=& 0.
+\end{eqnarray}
+
+\subsubsection{Debye-scale effective boundary conditions}
+We define the scaled coordinate $\rho$ (normal to ion-exchanger surface), where $\delta \ll 1$:
+\begin{eqnarray}
+  \rho &=& \frac{r-1}{\delta}. 
+\end{eqnarray}
+Thus, the electric potential and the ionic concentrations are $O(1)$ at the Debye layer ($r \approx 1$):
+\begin{eqnarray}
+  \varphi(\rho,\theta) &\sim& \varphi, \\
+  c_\pm(\rho,\theta) &\sim& c_\pm, \\
+  c(\rho,\theta) &\sim& c, \\
+  q(\rho,\theta) &\sim& q.
+\end{eqnarray}
+
+The radial fluxes at the Debye layer are $O(\delta^{-1})$, due to coordinate rescaling:
+\begin{eqnarray}
+  j_\pm(\rho, \theta) &\sim& \delta^{-1} j_\pm.
+\end{eqnarray}
+
+The pressure is $O(\delta^{-2})$, due to momentum balance equations:
+\begin{eqnarray}
+  p(\rho, \theta) &\sim& \delta^{-2} p.
+\end{eqnarray}
+
+The tangential velocity component is $O(1)$ and the radial component is $O(\delta)$.
+
+In order to match bulk $O(1)$ outer radial ionic flux, 
+the $O(\delta^{-1})$ term of the inner ionic radial flux, $j_\pm(\rho, \theta)$ must vanish:
+\begin{eqnarray}
+  -\deriv{c_\pm}{\rho} \mp c_\pm \deriv{\varphi}{\rho} &=& 0, \\
+  \deriv{\varphi}{\rho} \pm\frac{1}{c_\pm}\deriv{c_\pm}{\rho} &=& 0, \\
+  \pars{\varPhi - \varphi} \pm\pars{\log C_\pm - \log c_\pm} &=& 0, \\
+  \varPhi - \varphi \pm \log \frac{C_\pm}{c_\pm} &=& 0.
+\end{eqnarray}
+This relation can be rewritten as a Boltzmann distribution of ionic concentration:
+\begin{eqnarray}
+\lim_{\rho\rightarrow\infty} c_\pm &=& C, \\
+c_\pm &=& C \exp\left[\pm(\varPhi - \varphi)\right].
+\end{eqnarray}
+
+Due to cation selectivity, $c_+|_{\rho=0} = \gamma$.
+\begin{eqnarray}
+  c_+ = \gamma &=& C \exp(\varPhi - \cV), \\
+  \cV + \log \gamma &=& \log C + \varPhi.
+\end{eqnarray}
+
+The so-called zeta potential is 
+the voltage drop between the particle surface and the end of
+the boundary layer, denoted $\zeta = \cV - \varPhi$.
+
+Without loss of generality, 
+we assume that $\cV = -\log\gamma$, thus $\zeta = -\log\gamma-\varPhi$:
+\begin{eqnarray}
+\varPhi + \log C &=& 0.
+\end{eqnarray}
+
+Due to anion impermeability and radial flux continuity:
+\begin{eqnarray}
+  \br \cdot \bj_- = -\deriv{c_-}{r} + c_- \deriv{\varPhi}{r} &=& 0, \\
+-\deriv{C}{r} + C \deriv{\varPhi}{r} &=& 0, \\
+\deriv{}{r}\pars{\varPhi - \log C} &=& 0.
+\end{eqnarray}
+
+Using the derivation in Appendix \ref{append:slip} and the fact that $V_r = 0$ 
+on the boundary, the slip condition can be written using the surface
+gradient operator:
+\begin{eqnarray}
+\bV &=& 
+\zeta \cdot \bnabla_\mathcal{S} \varPhi 
++ 2\log\pars{1-\tanh^2\frac{\zeta}{4}} \cdot \bnabla_\mathcal{S} \log C, \\
+\bnabla_\mathcal{S} &=& \pars{\tI - \bn\bn} \bnabla.
+\end{eqnarray}
+
+\subsection{Steady state}
+The stress tensor is composed of Newtonian and Maxwel stresses:
+\begin{eqnarray}
+\tT &=& \bnabla \bV + (\bnabla \bV)^\dagger - P \tI
++ \bnabla \varPhi \bnabla \varPhi - \frac{1}{2} (\bnabla \varPhi \cdot \bnabla \varPhi) \tI, \\
+\bnabla \cdot \tT &=& \bzero.
+\end{eqnarray}
+The total force acting on the particle is computed by the following surface integral:
+\begin{eqnarray}
+\bF &=& \oint_\mathcal{S} \tT \cdot \bnhat dA.
+\end{eqnarray}
+In steady state (constant particle drift velocity $\cU$), 
+the total force must be zero: 
+\begin{eqnarray}
+\bF = \bzero.
+\end{eqnarray}
+
+The total force $\bF(\beta, \cU)$ is a function of the applied electric field $\beta$ and
+the velocity $\cU$.
+For any given electric field $\beta$, the force-free constraint above 
+can be solved numerically for $\cU$ to
+yield the corresponding steady-state velocity.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Algorithm Description} \label{algorithm}
+\subsection{Discretization}
+\subsubsection{Spherical Coordinates}
+Because the system is axisymmetric, the operators are written in 
+spherical coordinates $(r,\theta,\phi)$ 
+(using the derivation of Appendix \ref{append:spherical}).
+
+Due to axial symmetry, 
+the scalar gradient and the divergence can be written as:
+\begin{eqnarray}
+\bnabla f &=& \deriv{f}{r}\brhat + \frac{1}{r}\deriv{f}{\theta}\bthetahat, \\
+\bnabla \cdot \bF &=& \frac{1}{r^2}\deriv{}{r}\pars{F_r r^2 } + 
+               \frac{1}{r \sin\theta}\deriv{}{\theta}\pars{F_\theta \sin\theta}.
+\end{eqnarray}
+The scalar Laplacian can be written as:
+\begin{eqnarray}
+\Laplacian f = \bnabla \cdot (\bnabla f)&=& 
+ \frac{1}{r^2}\deriv{}{r}\pars{r^2 \deriv{f}{r}} + 
+ \frac{1}{r^2 \sin\theta}\deriv{}{\theta}\pars{\sin\theta \deriv{f}{\theta}}.
+\end{eqnarray}
+The vector gradient can be written as:
+\begin{eqnarray}
+\bnabla \bF &=& \deriv{F_r}{r} \brhat \brhat + \deriv{F_\theta}{r} \brhat \bthetahat + 
+\frac{1}{r}\pars{\deriv{F_r}{\theta} - F_\theta} \bthetahat \brhat + 
+\frac{1}{r}\pars{\deriv{F_\theta}{\theta} + F_r} \bthetahat \bthetahat.
+\end{eqnarray}
+The vector Laplacian can be written as:
+\begin{eqnarray}
+\bLaplacian \bF &=& 
+\left(\Laplacian F_r - \frac{2F_r}{r^2} - 
+\frac{2}{r^2 \sin\theta} \deriv{\left(F_\theta \sin\theta \right)}{\theta}\right)\brhat
++ \left(\Laplacian F_\theta - \frac{F_\theta}{r^2 \sin^2\theta} + 
+\frac{2}{r^2}\deriv{F_r}{\theta}\right) \bthetahat.
+\end{eqnarray}
+
+\subsubsection{Computational Grid}
+In order to discretize the differential operators, 
+a regular grid of size $n_r \times n_\theta$ is defined, with:
+\begin{eqnarray}
+(r_i,\theta_j) &\in& [1, \infty) \times [0,\pi], \\ 
+r_i &=& (1+\Delta_r)^i, \\
+\theta_j &=& \Delta_\theta \cdot j,
+\end{eqnarray}
+where a logarithmic grid spacing is used for $r$ and a uniform grid is used for $\theta$.
+Note that $r_0 = 1$ and $R_{max} = (1+\Delta_r)^{n_r}$ should be much 
+larger than $r_0$. Thus:
+\begin{eqnarray}
+\Delta_r &=& \pars{R_{max}} ^ \frac{1}{n_r} - 1, \\
+\Delta_\theta &=& \frac{\pi}{n_\theta}.
+\end{eqnarray}
+
+This grid induces a disjoint subdivision of the domain 
+$\Omega = [1, R_{max}] \times [0,\pi]$ into cells:
+\begin{eqnarray}
+\bigcup_{ij}\Omega_{ij} &=& \Omega.
+\end{eqnarray}
+A specific cell $\Omega_{ij}$ and its center $(\bar{r}_i, \bar{\theta}_j)$ are defined by:
+\begin{eqnarray}
+\Omega_{ij} &=& [r_{i-1}, r_{i}] \times [\theta_{j-1}, \theta_{j}], \\
+\bar{r}_i &=& \frac{r_{i-1} + r_{i}}{2}, \\
+\bar{\theta}_j &=& \frac{\theta_{j-1} + \theta_{j}}{2}.
+\end{eqnarray}
+
+Each variable is discretized with respect of its cell as follows:
+\begin{itemize}
+\item $\varPhi$, $C$ and $P$ are represented by their value at the center of each cell, 
+using an all-centered grid:
+\begin{eqnarray}
+\varPhi^h[i,j] &=& \varPhi(\bar{r}_i, \bar{\theta}_j), \\
+C^h[i,j] &=& C(\bar{r}_i, \bar{\theta}_j), \\
+P^h[i,j] &=& P(\bar{r}_i, \bar{\theta}_j).
+\end{eqnarray}
+\item $\bV$ is represented by its values at cell boundaries, using a staggered grid:
+\begin{eqnarray}
+V_r^h[i,j] &=& V_r(r_i, \bar{\theta}_j), \\
+V_\theta^h[i,j] &=& V_\theta(\bar{r}_i, {\theta}_j).
+\end{eqnarray}
+\end{itemize}
+
+\subsubsection{Operator Discretization}
+A finite-volume method with linear interpolation is used for flux 
+$\boldsymbol{f}^h$ discretization.
+
+Define the following discrete central difference operators:
+\begin{eqnarray}
+\cD_r(f^h)[i,j] &=& \frac{f^h\left[i+\half,j\right] - f^h\left[i-\half,j\right]}
+                       {r\left[i+\half,j\right] - r\left[i-\half,j\right]}, \\
+\cD_\theta(f^h)[i,j] &=& \frac{f^h\left[i,j+\half\right] - f^h\left[i,j-\half\right]}
+					   {\theta\left[i,j+\half\right] - \theta\left[i,j-\half\right]}.
+\end{eqnarray}
+
+Define the following interpolation operators:
+\begin{eqnarray}
+\cI_r(f^h)[i,j] &=& \frac{
+\pars{r\left[i,j\right] - r\left[i-\half,j\right]} 
+  f^h\left[i+\half,j\right] + 
+\pars{r\left[i+\half,j\right] - r\left[i,j\right]} 
+  f^h\left[i-\half,j\right] 
+}{r\left[i+\half,j\right] - r\left[i-\half,j\right]},
+\\
+\cI_\theta(f^h)[i,j] &=& 
+\frac{
+\pars{r\left[i,j\right] - r\left[i,j-\half\right]} 
+  f^h\left[i,j+\half\right] + 
+\pars{r\left[i,j+\half\right] - r\left[i,j\right]} 
+  f^h\left[i,j-\half\right] 
+}{r\left[i,j+\half\right] - r\left[i,j-\half\right]}.
+\end{eqnarray}
+
+The total flux of a cell is equal to zero (due to conservation):
+\begin{eqnarray}
+\bnabla \cdot \boldsymbol{f}^h &=& 0, 
+\\
+\frac{1}{r^2} \cD_r\pars{f^h_r r^2} + 
+\frac{1}{r \sin\theta} \cD_\theta\pars{f^h_\theta \sin\theta} &=& 0, 
+\\
+\cD_r\pars{f^h_r \cdot r^2 \sin\theta} + 
+\cD_\theta\pars{f^h_\theta \cdot r \sin\theta} &=& 0. 
+\end{eqnarray}
+
+Ion fluxes are discretized on grid cell boundaries:
+\begin{eqnarray}
+I^h_r &=& -\cI_r(C^h) \cdot \cD_r(\varPhi^h), \\
+I^h_\theta &=& -\cI_\theta(C^h) \cdot \frac{\cD_\theta(\varPhi^h)}{r}.
+\end{eqnarray}
+
+Salt fluxes are discretized on grid cell boundaries 
+(using upwind scheme $\mathcal{U}$ for numerical stability at large cell Peclet number):
+\begin{eqnarray}
+J^h_r &=& -\cD_r(C^h) + \alpha V^h_r \cdot \mathcal{U}^{\bV^h}_r (C^h), \\
+J^h_\theta &=& -\frac{\cD_\theta(C^h)}{r} + \alpha V^h_\theta \cdot \mathcal{U}^{\bV^h}_\theta (C^h), \\
+ \mathcal{U}^{\bV^h}_r(C^h)[i,j] &=& C^h\left[i-\frac{\sign(V^h_r)}{2}, j\right], \\
+ \mathcal{U}^{\bV^h}_\theta(C^h)[i,j] &=& C^h\left[i, j-\frac{\sign(V^h_\theta)}{2}\right]. 
+\end{eqnarray}
+
+Mass flux $\bV$ is discretized on grid cells boundaries, 
+using the velocity staggered grid.
+
+Force components are discretized on the velocity staggered grid, where
+linear interpolation is used for the Coulomb force.
+\begin{eqnarray}
+F^h_r &=& -\cD_r(P^h) 
+          + \cL(V^h_r) - \frac{2}{r^2} V^h_r 
+		  - \frac{2}{r^2 \sin\theta} \cI_r(\cD_\theta (V^h_\theta \sin\theta))
+          + \cD_r(\varPhi^h) \cdot \cI_r(\cL(\varPhi^h)), \\
+F^h_\theta &=& -\frac{\cD_\theta(P^h)}{r} 
+		  + \cL(V^h_\theta) - \frac{F^h_\theta}{r^2 \sin^2\theta} 
+		  + \frac{2}{r^2} \cI_\theta(\cD_\theta(F^h_r))
+		  + \frac{\cD_\theta(\varPhi^h)}{r} \cdot \cI_\theta(\cL(\varPhi^h)), \\
+\cL(f^h) &=& \frac{1}{r^2}\cD_r\pars{\cD_r(f^h) r^2} + 
+\frac{1}{r^2 \sin\theta} \cD_\theta\pars{\cD_\theta(f^h) \cdot \sin\theta}.
+\end{eqnarray}
+
+\subsubsection{Boundary Conditions}
+In order to discretize boundary condtions, 
+``ghost'' points are employed. 
+The grid is extended to include points outside the domain interior,
+and the variables at the ``ghost'' points are set to satisfy 
+the discretized boundary conditions, following the analysis below.
+
+The boundary conditions at the ion-exchange boundary ($r=1$) are:
+\begin{eqnarray}
+\cI_r(\varPhi^h) &=& -\cI_r(\log C^h), \\
+\cD_r(\varPhi^h) &=& \cD_r(\log C^h), \\
+V^h_r &=& 0, \\
+V^h_\theta &=& 4\log\pars{\frac{1 + \exp\left\{\cI_\theta(\zeta^h)/2\right\}}{2}} \cdot 
+			\cD_\theta(\zeta^h), \\
+  \zeta^h &=& - \log \gamma - \cI_r(\varPhi^h).
+\end{eqnarray}
+The equations are discretized using ``ghost'' points outside the interior of the domain:
+\begin{eqnarray}
+ \varPhi^h[1/2, j] = \frac{\varPhi^h[0,j] + \varPhi^h[1,j]}{2} &=& 
+	-\frac{\log C^h[0,j] + \log C^h[1,j]}{2} = -\log C^h[1/2, j], \\
+  \frac{\varPhi^h[1,j] - \varPhi^h[0,j]}{\Delta r} &=& 
+	\frac{\log C^h[1,j] - \log C^h[0,j]}{\Delta r}. 
+\end{eqnarray}
+By adding and subtracting the equations, we have:
+\begin{eqnarray}
+\varPhi^h[0,j] &=& -\log\brcs{C^h[1,j]}, \\
+C^h[0,j] &=& \exp\brcs{-\varPhi^h[1,j]}, \\
+  \zeta^h[j] &=& \cV - \varPhi^h[1/2,j]
+                     = -\log\gamma -\frac{\varPhi^h[0,j] + \varPhi^h[1,j]}{2}.
+\end{eqnarray}
+The slip condition can be written as:
+\begin{eqnarray}
+V_r^h[0,j] &=& 0, \\
+V_\theta^h[1/2,j] &=& 
+4\log\pars{\frac{1 + \exp\left\{\frac{1}{2}
+ \frac{\zeta^h[j] + \zeta^h[j+1]}{2}\right\}}{2}} 
+\cdot \frac{\zeta^h[j+1] - \zeta^h[j]}{\bar{\theta}_{j+1} - \bar{\theta}_{j}}, \\
+  V^h_\theta[0,j] &=& 2 V^h_\theta[1/2, j] - V^h_\theta[1,j].
+\end{eqnarray}
+
+For $\theta = 0$ and $\theta = \pi$, the ``ghost'' points are defined by:
+\begin{eqnarray} 
+\brc{l}{
+\varPhi^h[i, 0] = \varPhi^h[i, 1] \\
+C^h[i, 0] = C^h[i, 1] \\
+V_r^h[i, 0] = V_r^h[i, 1] \\
+V_\theta^h[i, 0] = 0
+} 
+\brc{l}{
+\varPhi^h[i, n_\theta+1] = \varPhi^h[i, n_\theta], \\
+C^h[i, n_\theta+1] = C^h[i, n_\theta], \\
+V_r^h[i, n_\theta+1] = V_r^h[i, n_\theta], \\
+V_\theta^h[i, n_\theta+1] = 0.
+} 
+\end{eqnarray}
+
+Far away from the ion-exchange boundary ($r\rightarrow\infty$) we have:
+\begin{eqnarray}
+\frac{\varPhi^h[n_r + 1, j] - \varPhi^h[n_r, j]}{\bar{r}_{n_r + 1} - \bar{r}_{n_r}}, 
+ & = & -\beta \cos\bar{\theta}_j, \\
+C^h[n_r + 1, j] & = & 1 \\
+V_r^h[n_r + 1, j] & = & -\cU \cos\bar{\theta}_j, \\
+V_\theta^h[n_r + 1, j] & = & \cU \sin\theta_j.
+\end{eqnarray}
+
+Because the actual grid is finite, the choice 
+$r_{n_r} = R_{max}$ must be taken large enough so as to have a negligible effect
+on the solution.
+
+Note that $P^h$ has no boundary conditions -- so the pressure variable is defined 
+only in the domain interior.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Solver Design}
+\subsubsection{Newton's Method}
+An operator $\cO$ is defined by its input vector $\bx$ and its output 
+$\by = \cO(\bx)$.
+
+In order to solve the equation $\cO(\bx) = \bzero$, Newton's method can 
+be applied, given an initial solution $\bx_0$:
+\begin{eqnarray}
+\bzero = \cO(\bx_n + \Delta \bx_n) &\approx& \cO(\bx_n) + \bnabla \cO(\bx_n)\cdot\Delta\bx_n, \\
+\Rightarrow \bnabla \cO(\bx_n) \cdot \Delta \bx_n &=& -\cO(\bx_n), \\
+\bx_{n+1} &=& \bx_{n} + \Delta \bx_n. 
+\end{eqnarray}
+
+Each step requires the computation of the residual vector, $\cO(\bx)$, and
+the gradient matrix of the operator, $\bnabla \cO(\bx)$, 
+given the current solution $\bx = \bx_n$.
+Then, a sparse linear system needs to be solved to yield the update for the 
+increment $\Delta \bx_n = \bx_{n+1} - \bx_n$.
+
+When the method converges, $\bx_n \rightarrow \bx_\infty$, 
+the convergence is in general quadratic:
+\begin{eqnarray}
+\|\bx_{n+1} - \bx_\infty\| \le k \|\bx_{n} - \bx_\infty\|^2.
+\end{eqnarray}
+Thus, when the initial guess is close enough to the solution, the solver
+will typically converge in very few steps.
+
+\subsubsection{Operator Representation}
+System variable $\bx$ is defined as the concatenation $[\,\varPhi, C, V_r, V_\theta, P\,]$,
+taking only values in the interior of the problem domain grid.
+Thus, each problem variable can be computed by applying an appropriate projection operator on $\bx$:
+\begin{eqnarray}
+X &=& \cP_X(\bx) \mbox{ for } X \in \left\{\varPhi, C, V_r, V_\theta, P\right\}.
+\end{eqnarray}
+
+The extended variables $\tilde X$ (including ``ghost'' point values) 
+are computed by applying the following nonlinear operators:
+\begin{eqnarray}
+\tilde{\varPhi} &=& \cB_\varPhi(\varPhi, C; \beta), \\
+\tilde{C} &=& \cB_C(C, \varPhi), \\
+\tilde{V_r} &=& \cB_{V_r}(V_r; \cU), \\
+\tilde{V_\theta} &=& \cB_{V_\theta}(V_\theta, C, \varPhi; \cU, \gamma), \\
+\tilde{P} &=& P.
+\end{eqnarray}
+The extended system variable can be written as $\tilde{\bx} = \cB(\bx)$, 
+where $\cB$ is the ``ghost'' point extension operator (derived using boundary conditions)
+so the concatenated equations of the system (as described above) can be written 
+as a non-linear operator $\cE(\tilde\bx) = \bzero$ acting on the extended system variable 
+$\tilde{\bx}$, where $\cE$ is the conservation equations operator 
+(derived by concatenation of the system equations).
+
+The problem can be cast as the following non-linear system:
+\begin{eqnarray}
+\bzero = \cE (\tilde{\bx}) = \cE (\cB (\bx)) = \cO(\bx),
+\end{eqnarray}
+ where $\cO = \cE \circ \cB$.
+
+\subsubsection{Steady-state}
+Assume that $\cU \ui$ is the velocity of the ion exchanger 
+(given that the fluid is at rest far away from the particle).
+After the convergence of the solver, $\cO(\bx_n) \rightarrow \bzero$, 
+the ``ghost'' point values are updated using $\tilde\bx = \cB(\bx_\infty)$,
+so  that the surface force $\boldsymbol{f} = \tT \cdot \bn$ acting 
+on the ion-exchanger surface
+can be computed by integration over the ion exchanger's surface $\mathcal S$.
+
+Due to symmetry considerations, the total force $\bF$ is 
+aligned with $\ui$ and it vanishes iff $\ui \cdot \bF = 0$.
+\begin{eqnarray}
+\bF &=& \oint_\mathcal{S} \boldsymbol{f}  dA = 
+\oint_\mathcal{S} \tT \cdot \bnhat  dA. \\
+F_\imath = \ui \cdot \bF &=& \oint_\mathcal{S} \ui \cdot \boldsymbol{f}  dA = 
+\oint_\mathcal{S} \ui \cdot \tT \cdot \bnhat  dA = 
+\int_0^\pi f_\imath(\theta) \cdot 2\pi \sin\theta d\theta ,
+\\  
+f_\imath &=& \ui \cdot \tT \cdot \brhat,
+\\  
+f_\imath &=& \pars{-P + 2\cD_r(V_r) + 
+\frac{1}{2}\pars{\cD_r(\varPhi)}^2 - \frac{1}{2r^2}\pars{\cD_\theta(\varPhi)}^2}\cos\theta 
+\\  
+&& -\pars{\cD_r(V_\theta) - \frac{V_\theta}{r}
++ \frac{1}{r}\cD_r(\varPhi) \cD_{\theta}(\varPhi)}\sin\theta, \\
+ \mathcal{S} &=& \{\br : \|\br\|_2 = 1\}.
+\end{eqnarray}
+
+The integral for $F_\imath$ is approximated by 1D numerical quadrature
+(using the mid-point rule), to yield 
+the total force $F_\imath(\cU)$ as a function of the drift velocity $\cU$.
+
+Since the goal is to find steady-state solution, $F_\imath(\cU)$ 
+is required to be zero --
+and the appropriate $\cU$ is found by a simple 1D root-finding algorithm,
+applied as an outer loop.
+
+\subsubsection{Continuation}
+
+The iterative solver above can be used to compute the steady-state solution for any given $\beta$.
+For $\beta \ll 1$, the linear terms are the dominant ones, so the solution is linear in $\beta$ 
+(as derived in \cite{yariv2010migration}), and the solver convergence is fast.
+
+However, it is no longer true for $\beta \sim O(1)$, since the nonlinear terms become dominant
+and the iterative solver may not converge at all.
+In order to find a solution for such $\beta$, continuation method is used:
+the solver is applied to a sequence of $\{\beta_i\}_{i=0}^n$ such that $\beta_0 = 0$,
+$\beta_n = \beta$ and the solution $\bx_i$ for $\beta_i$ is used as the solver initializer
+for the problem of $\beta_{i+1}$.
+
+Given that $|\beta_{i+1} - \beta_i| < \eps$ for small enough $\eps$, 
+the next solution $\bx_{i+1}$ is close to the previous one $\bx_i$,
+so the iterative solver converges well.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Solver Implementation}
+
+Object-Oriented Design methodology is used for implementation.
+The MATLAB programming language is chosen due to strong numerical capabilities
+and high-level language features.
+
+\subsubsection{Operator Interface $ \rightarrow \cO$}
+The base \verb|Operator| interface is defined by 
+supporting the computation of a residual vector \verb|op.res()|
+and a gradient matrix \verb|op.grad()|, given an input vector $\bx$.
+
+This interface is implemented by specific operators classes,
+which are used to constuct the operator $\cO = \cE \circ \cB$, so that 
+the Newton method solver (that requires computing the residual and the gradient) 
+can be applied automatically.
+
+Each such operator may have other operators as its inputs, so the residual
+and the gradient are computed recursively, using the chain rule.
+
+\paragraph{Linear operator}
+If $\cO$ is linear, it can be represented by a matrix $L$, such that:
+\begin{eqnarray}
+\cO(\bx) &=& L \bx, \\
+\bnabla\cO &=& L. 
+\end{eqnarray}
+Note that finite difference $\cD$, interpolation $\cI$ and 
+upwind selection $\mathcal{U}$ operators
+can be implemented as linear sparse operators, by constructing 
+an appropriate sparse matrix $L$, having $O(\dim \bx)$ non-zeroes).
+
+\paragraph{Pointwise scalar function}
+Let $f: \R \rightarrow \R$ be a differentiable 1D function, whose derivative is
+denoted by $f': \R \rightarrow \R$. The operator $\cF$ can be defined to
+represent pointwise application of $f$:
+\begin{eqnarray}
+\cF(\bx) &=& [f(x_1); \ldots; f(x_n)], \\
+\bnabla\cF(\bx) &=& \diag\{f'(x_1), \ldots, f'(x_n)\}.
+\end{eqnarray}
+$f$ is defined and differentiated automatically using the MATLAB symbolic toolbox.
+
+\paragraph{Constant value}
+A constant operator $\mathcal{C}$ is defined as having constant vector value $\bc$ 
+(that does not depend on $\bx$):
+\begin{eqnarray}
+\mathcal{C}(\bx) &=& \bc, \\
+\bnabla\mathcal{C} &=& \bzero.
+\end{eqnarray}
+
+\paragraph{Binary operators}
+Let $\cO_1$ and $\cO_2$ be two operators, so their pointwise addition, subtraction,
+and multiplication, are defined as follows:
+\begin{eqnarray}
+(\cO_1 \pm \cO_2)(\bx) &=& \cO_1)(\bx) \pm \cO_2(\bx), \\
+\bnabla (\cO_1 \pm \cO_2)(\bx)   &=& \bnabla\cO_1(\bx) \pm \bnabla\cO_2(\bx), \\
+(\cO_1 \cdot \cO_2)(\bx) &=& \diag(\diag(\cO_1(\bx)) \cdot \diag(\cO_2(\bx))), \\
+\bnabla (\cO_1 \cdot \cO_2)(\bx) &=& \diag(\cO_2(\bx)) \bnabla\cO_1(\bx) 
+                                  + \diag(\cO_1(\bx)) \bnabla\cO_2(\bx).
+\end{eqnarray}
+
+\paragraph{N-ary operators}
+Given $N$ operators $\{\cO_i\}_{i=1}^N$, their concatenation $\cO$ is defined as:
+\begin{eqnarray}
+\cO(\bx) &=& [\cO_1(\bx); \ldots; \cO_N(\bx)], \\
+(\bnabla\cO)(\bx) &=& [(\bnabla\cO_1)(\bx); \ldots; (\bnabla\cO_N)(\bx)].
+\end{eqnarray}
+
+\subsubsection{Iterative Newton solver $\rightarrow \bx$}
+Given an initial solution $\bx_0$ and specific values for $\beta$ and $\cU$, 
+we apply the following algorithm 
+until convergence ($\|\Delta \bx\| < \eps$):
+\begin{enumerate}
+\item Update the system: $\verb|op| = \verb|System|(\bx_{n})$
+\item Compute the gradient: $\boldsymbol{A}_n = \verb|op.grad()|$
+\item Compute the right-hand side: $\boldsymbol{b}_n = \verb|-op.res()|$
+\item Solve sparse linear system: $\boldsymbol{A}_n \Delta \bx_n = \boldsymbol{b}_n$
+\item Update solution: $\bx_{n+1} = \bx_{n} + \Delta \bx_{n}$
+\end{enumerate}
+
+\subsubsection{Total force integration $\rightarrow F_\imath$}
+After the iterative Newton solver converges ($\bx_n \rightarrow \bs$), 
+the ``ghost'' point values are computed by computing $\cB(\bs)$ and
+the total force $\bF$ acting on the ion-exchanger.
+
+$F_\imath = \bF \cdot \ui$ is computed by using the mid-point quadrature rule:
+\begin{eqnarray}
+F_\imath &=& \sum_{i=1}^{n_\theta} f(\bar\theta_i) \cdot 
+              2 \pi \sin\bar\theta_i \cdot \Delta\theta_i
+\end{eqnarray}
+
+\subsubsection{Steady state drift velocity $\rightarrow \cU$}
+In steady state, the total force acting on the particle $F_\imath$ must vanish.
+This constraint yields an equation, whose solution is the steady-state velocity $\cU$:
+\begin{eqnarray}
+F_\imath(\cU) &=& 0
+\end{eqnarray}
+This equation can be solved using a 1D root finding algorithm, e.g. the secant method:
+\begin{eqnarray}
+\cU_{n+1} = \frac{F_\imath(\cU_{n})\cU_{n-1} - F_\imath(\cU_{n-1})\cU_{n}}
+{F_\imath(\cU_{n}) - F_\imath(\cU_{n-1})} \rightarrow \cU
+\end{eqnarray}
+The result $\cU$ is the 
+steady state particle drift velocity for the electric field $\beta$.
+
+The non-linear system is defined by the following PDEs:
+\label{PDEs}
+\begin{eqnarray}
+\bnabla \cdot \pars{C \bnabla \varPhi} &=& 0, \\
+\bnabla \cdot \pars{\bnabla C - \alpha \bV C} &=& 0, \\
+\bLaplacian \bV - \bnabla P + \Laplacian \varPhi \bnabla \varPhi &=& \bzero.
+\end{eqnarray}
+
+For $\zeta(\theta) = \cV - \varPhi(1, \theta)$ and 
+$\cV = -\log \gamma$, the boundary conditions on $r = 1$ are:
+\begin{eqnarray}
+\varPhi + \log C &=& \cV + \log \gamma = 0, \\
+\deriv{}{r}\pars{\varPhi - \log C} &=& \frac{J_-}{C} = 0, \\
+\bV = \zeta \cdot \bnabla_\mathcal{S} \varPhi 
++ 2\log\pars{1-\tanh^2\frac{\zeta}{4}} \cdot \bnabla_\mathcal{S} \log C
+&=& 4\log\pars{\frac{1 + e^\frac{\zeta}{2}}{2}} \bnabla_S \varPhi.
+\end{eqnarray}
+
+The boundary conditions for $r \rightarrow \infty$ are:
+\begin{eqnarray}
+\bnabla \varPhi &=& -\beta \ui, \\
+C &=& 1, \\
+\bV &=& -\cU \ui,
+\end{eqnarray}
+and the total force acting on the particle is zero: $\bF = \bzero$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Asymptotic Analysis} \label{asymptotic}
+The nonlinear system can be written as: 
+\begin{eqnarray}
+\cO(\bx;\beta) &=& \bzero.
+\end{eqnarray}
+
+The solution to the non-linear system can be written as a Taylor series in $\beta$.
+\begin{eqnarray}
+\bx = \bx(\beta) &\approx& \sum_n \bx_n \beta^n.
+\end{eqnarray}
+
+All the variables are expanded around $\beta = 0$:
+\begin{eqnarray}
+\varPhi &=& \beta \varPhi_1 + \beta^2 \varPhi_2 + \beta^3 \varPhi_3 + \ldots, \\
+C &=& 1 + \beta C_1 + \beta^2 C_2 + \beta^3 C_3 + \ldots, \\
+\Psi &=& \beta \Psi_1 + \beta^2 \Psi_2 + \beta^3 \Psi_3 + \ldots ,
+\end{eqnarray}
+where the velocity $\bV$ and pressure $P$ are computed from the streamfunction $\Psi$:
+\begin{eqnarray}
+\bV &=& \bnabla \times \pars{\frac{\Psi}{r \sin\theta} \bphihat} 
+= \frac{1}{r^2 \sin\theta} \deriv{\Psi}{\theta} \brhat 
+- \frac{1}{r \sin\theta} \deriv{\Psi}{r} \bthetahat.
+\end{eqnarray}
+
+The nonlinear equations and the boundary conditions are expanded around $\beta = 0$
+and arranged by powers of $\beta$:
+\begin{eqnarray}
+\bzero = \cO(\bx) = \sum_k \cO_k(\bx_0, \ldots \bx_k) \beta^k
+\end{eqnarray}
+This can be rewritten as a system of equations:
+\begin{eqnarray}
+\brc{rcl}{
+\bzero &=& \cO_0(\bx_0), \\
+\bzero &=& \cO_1(\bx_0, \bx_1), \\
+\bzero &=& \cO_2(\bx_0, \bx_1, \bx_2), \\
+& \vdots & \\
+\bzero &=& \cO_k(\bx_0, \bx_1, \bx_2, \ldots \bx_k).
+}
+\end{eqnarray}
+Thus, the $O(\beta^k)$ term $\bx_k$ can be found recursively by solving 
+$\cO_k(\bx_0, \bx_1, \ldots, \bx_k) = \bzero$,
+given the previous solutions for $\bx_0, \ldots, \bx_{k-1}$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Linear Solution $(k=1)$}
+
+For $\beta = 0$ (no electric field is applied), the steady-state solution is $\cU = 0$:
+\begin{eqnarray}
+\varPhi_0(r,\theta) &=& 0, \\
+C_0(r,\theta) &=& 1, \\
+\bV_0(r,\theta) &=& \bzero, \\
+P_0(r,\theta) &=& 0.
+\end{eqnarray}
+
+Assuming $\beta \ll 1$, the linearized equations and boundary conditions are 
+(as developed in \cite{yariv2010migration}):
+\begin{eqnarray}
+\Laplacian \varPhi_1 &=& 0, \\
+\Laplacian C_1 &=& 0, \\
+\bLaplacian \bV_1 - \bnabla P_1 &=& \bzero.
+\end{eqnarray}
+
+The first order terms are:
+\begin{eqnarray}
+\varPhi &=& \beta \pars{\frac{1}{4r^2} - r}\cos\theta, \\
+C &=& 1 + \beta \frac{3}{4r^2} \cos\theta, \\
+\Psi &=& \beta \cU_1 \pars{\frac{1}{r} - r^2} \frac{\sin^2\theta}{2}, \\
+\bV &=& -\beta \cU_1 \brcs{\pars{1 - \frac{1}{r^3}}\cos\theta \cdot \brhat - 
+                               \pars{1 + \frac{1}{2r^3}} \sin\theta \cdot \bthetahat}, \\
+P &=& 0, \\
+\bF &=& \bzero.
+\end{eqnarray}
+
+The slip velocity satisfies:
+\begin{eqnarray}
+\beta \cU_1 \frac{3}{2} \sin\theta =
+V_\theta &=& 4 \log \pars{\frac{1 + e ^ \frac{\zeta}{2}}{2}} \deriv{\varPhi}{\theta} 
+=
+ 3 \beta \log \pars{\frac{1 + e ^ \frac{\zeta}{2}}{2}} \sin\theta, \\
+\cU_1 &=& 2 \log \pars{\frac{1 + e ^ \frac{\zeta}{2}}{2}} 
+       =  2 \log \pars{\frac{1 + \gamma ^ {-\frac{1}{2}}}{2}}.
+\end{eqnarray}
+because $\varPhi_1 = -C_1 = -\frac{3}{4} \cos\theta$ on $r=1$
+and $\zeta_0 = -\log\gamma$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Nonlinear Solution ($k > 1$)}
+Note that, due to symmetry considerations, $\cU(\beta)$ is an anti-symmetric function:
+\begin{eqnarray}
+\cU(-\beta) &=& -\cU(\beta).
+\end{eqnarray}
+Therefore, $\cU_2 = 0$ and the next velocity term is the cubic one:
+\begin{eqnarray}
+\cU(\beta) &\approx& \beta \cU_1 + \beta^3 \cU_3 + O(\beta^5)
+\end{eqnarray}
+
+In order to find the cubic terms, the quadratic term should be found first.
+
+\subsubsection{Quadratic Solution ($k = 2$)}
+The quadratic terms $\bx_2$ are computed by solving a linear PDE system 
+with a right-hand side determined by the linear terms $\bx_1$:
+\begin{eqnarray}
+\varPhi_2 &=& \frac{\left(\frac{\cU_1\, \alpha}{32} - \frac{1}{16}\right)\, \left(3\, {\cos^2\theta} - 1\right)}{r^3} - \frac{3}{32\, r^4} - \frac{3\, {\sin^2\theta}\, \left(4\, r^3 - 1\right)}{32\, r^4} - \frac{3\, \cU_1\, \alpha - 6}{32\, r},
+\\
+C_2 &=& \frac{\left(\frac{5\, \cU_1\, \alpha}{32} + \frac{1}{16}\right)\, \left(3\, {\cos^2\theta} - 1\right)}{r^3} - \frac{3\, \cU_1\, \alpha - 6}{32\, r} + \frac{3\, \cU_1\, \alpha\, \left(2\, r^3\, {\sin^2\theta} + {\sin^2\theta} - 1\right)}{16\, r^4},
+\\
+\Psi_2 &=& \pars{\frac{9}{16(\sqrt{\gamma}+1)} - \frac{3}{16} \cU_1 (\cU_1 \alpha + 1)}
+ \left(\frac{1}{r^2} - 1\right) \sin^2\theta \cos\theta,  \\
+\bF_2 &=& \bzero, \\ \cU_2 &=& 0.
+\end{eqnarray}
+Note that the quadratic term does not contribute to the total force and staedy-state 
+velocity terms, but it does change the fluid flow, 
+the electric potential and the ionic concentration.
+
+\subsubsection{Cubic Solution ($k = 3$)}
+
+\begin{eqnarray*}
+\varPhi_3 &=& \cos\theta \left(\frac{15 \cU_1\alpha}{64} + \frac{3}{32}\right) - \frac{3 \cU_1\alpha {\cos}^3\theta}{32} - \frac{\cos\theta \left( - 183 {\cU_1}^2\alpha^2 + 839 \cU_1\alpha + 470\right)}{2560 r^2} \\
+&&+ \frac{3 \cos\theta \left(5 \cU_1\alpha - 6 {\cos^2\theta} - 4 \cU_1\alpha {\cos^2\theta} + 4\right)}{64 r^3} + \frac{\left(2 \cU_1\alpha - 1\right) \left(\cos\theta - 3 {\cos}^3\theta\right)}{64 r^5}
+\\ 
+&&- \frac{\left(3 \cos\theta - 5 {\cos}^3\theta\right) \left( - \frac{19 {\cU_1}^2\alpha^2}{5120} + \frac{97 \cU_1\alpha}{5120} + \frac{3 \cU_2\alpha}{320} + \frac{21}{1280}\right)}{r^4} + \frac{{\cos}^3\theta \left(\frac{15 \cU_1\alpha}{64} + \frac{3}{32}\right)}{r^2} \\
+&&+ \frac{{\cos}^3\theta \left(\frac{\cU_1\alpha}{64} + \frac{3}{64}\right)}{r^6},
+\\
+C_3 &=&
+\frac{3 {{\cU_1}}^2\alpha^2 {\cos^3\theta}}{32} + \frac{\cos\theta \left(797 {{\cU_1}}^2\alpha^2 + 419 {\cU_1}\alpha - 512 {\cU_2}\alpha + 174\right)}{2560 r^2} \\
+&&- \frac{\left(3 \cos\theta - 5 {\cos^3\theta}\right) \left(\frac{59 {{\cU_1}}^2\alpha^2}{5120} + \frac{103 {\cU_1}\alpha}{5120} + \frac{69 {\cU_2}\alpha}{320} + \frac{3}{1280}\right)}{r^4} \\
+&&- \frac{3\alpha \cos\theta \left( - 8\alpha {{\cU_1}}^2 {\cos^2\theta} + 7\alpha {{\cU_1}}^2 + 2 {\cU_1} + 32 {\cU_2} {\cos^2\theta} - 32 {\cU_2}\right)}{128 r^3} - \frac{3 {\cU_1}\alpha \cos\theta \left(5 {\cU_1}\alpha + 2\right)}{64} \\
+&&+ \frac{\alpha \left(\cos\theta - 3 {\cos^3\theta}\right) \left(5\alpha {{\cU_1}}^2 + 2 {\cU_1} + 16 {\cU_2}\right)}{128 r^5} + \frac{{{\cU_1}}^2\alpha^2 {\cos^3\theta}}{32 r^6} - \frac{3 {\cU_1}\alpha {\cos^3\theta} \left(5 {\cU_1}\alpha + 2\right)}{64 r^2},
+\\
+\Psi_3 &=&
+r^2 {\sin^2\theta} \left(\frac{{\cW_2}}{15} - \frac{{\cW_1}}{3} + \frac{209}{3360}\right) 
+ - \frac{{\sin^2\theta} \left(\frac{5 {\cW_2}}{3} - \frac{{\cW_1}}{3} + \frac{35}{264}\right)}{r}
+\\ && + \frac{{\sin^4\theta} \left(2 {\cW_2} + \frac{761}{5632}\right)}{r} - \frac{{\sin^2\theta} \left(1848 r^6 {\sin^2\theta} - 2079 r^3 {\sin^2\theta} + 924 r^3 - 7 {\sin^2\theta} + 10\right)}{19712 r^5}
+\\ && + \frac{\left(\frac{2 {\cW_2}}{5} + \frac{829}{28160}\right) \left(4 {\sin^2\theta} - 5 {\sin\theta}^4\right)}{r^3} + \frac{{\sin^2\theta} \left(\frac{{\cU_1}\alpha}{16} - \frac{1}{8}\right) \left(2 r^3 - 3 r^2 + 1\right)}{4 r},
+\\
+\cW_1 &=& \frac{69}{512 \left(\sqrt{\gamma} + 1\right)} - \frac{1407\alpha^2 {\log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}^3}{1280} - \frac{123 \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{1280} - \frac{27}{512 {\left(\sqrt{\gamma} + 1\right)}^2} \\ && -
+\frac{1899\alpha {\log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}^2}{2560} - \frac{\alpha \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right) \left(\frac{81}{16 \left(\sqrt{\gamma} + 1\right)} - \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right) \left(\frac{27\alpha \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{4} + \frac{27}{8}\right)\right)}{320} \\ && +
+\frac{21\alpha \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{128 \left(\sqrt{\gamma} + 1\right)},
+\\
+\cW_2 &=& \frac{9 \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{256} + \frac{21\alpha^2 {\log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}^3}{64} - \frac{27}{512 \left(\sqrt{\gamma} + 1\right)} - \frac{27}{512 {\left(\sqrt{\gamma} + 1\right)}^2}
+ + \frac{15\alpha {\log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}^2}{64} 
+\\ && 
+- \frac{297\alpha \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{1024 \left(\sqrt{\gamma} + 1\right)}.
+\end{eqnarray*}
+
+The cubic solution satisfies the $\lim_{r\rightarrow\infty}C_3 = 0$ boundary condition, 
+when $\alpha\cU_1 = 0$.
+
+The steady-state velocity can be expanded using odd powers of $\beta$:
+\begin{eqnarray}
+\cU(\beta, \gamma) &=& \cU_1(\gamma) \beta + \cU_3(\gamma) \beta^3
+\end{eqnarray}
+
+The velocity terms (for $\alpha = 0$) are:
+
+The linear term is:
+\begin{eqnarray}
+\cU_1(\gamma) &=& 2 \log \pars{\frac{1 + \gamma^{-\frac{1}{2}}}{2}}. \\
+\end{eqnarray}
+The cubic term is:
+\begin{eqnarray}
+\cU_3(\gamma) &=& \frac{31}{320(\sqrt\gamma + 1)} - \frac{9}{320(\sqrt\gamma + 1)^2} + \frac{1}{1680} - \frac{11}{160} \log \pars{\frac{1 + \gamma^{-\frac{1}{2}}}{2}}.
+\end{eqnarray}
+
+Note that, for $\gamma = 1$, the linear term vanishes and the velocity leading term is $O(\beta^3)$:
+\begin{eqnarray}
+\cU(\beta) = \frac{1129}{26880}\beta^3.
+\end{eqnarray}
+
+Note that a $\cU = 0$ solution may exist for $\beta_c \ne 0$ and $\alpha = 0$, 
+if it satisfies:
+\begin{eqnarray}
+\beta_c^2 = -\frac{\cU_1(\gamma)}{\cU_3(\gamma)}.
+\end{eqnarray}
+For $\gamma = 1 + \eps$, where $0 < \eps \ll 1$:
+\begin{eqnarray}
+\beta_c \approx \sqrt{-\frac{\cU_1'(1) \eps}{\cU_3(1)}} = 
+ \sqrt{\frac{13440 \eps}{1129}} \approx 3.45 \sqrt{\eps}.
+\end{eqnarray}
+However, for $\gamma \gg 1$, we have:
+\begin{eqnarray}
+\beta_c =  \pars{\frac{11}{320} + \frac{1}{1680 \log 4}}^{-\frac{1}{2}} \approx 5.36.
+\end{eqnarray}
+
+The cubic term becomes dominant for small $\beta$ when $\gamma \approx 1$.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Numerical Tests} \label{results}
+The results for steady-state velocity $\cU$ as a function of the electric field magnitude $\beta$
+are shown at Figures \ref{fig:NumResA} and \ref{fig:NumResB}. 
+Since log-log scale is used, blue and red colors are used 
+for positive and negative velocities, respectively.
+
+For small $\beta$, the linear regime dominates, $\cU \propto \beta$. 
+However, from a specific $\beta_c$, the nonlinear regime dominates, such that
+$\cU \propto \beta^3$, until $\beta \sim O(1)$.
+
+The streamlines for a specific $\gamma$ are shown at Figure \ref{fig:NumResC} for
+various electric field magnitudes $\beta$.
+
+The theoretical results for the nonlinear regime are computed by asymptotic expansion of the
+nonlinear system, as described in the previous section.
+\begin{figure}[htbp]
+\begin{framed}
+    \begin{center}
+        \includegraphics[width=0.45\textwidth]{figs/A1.eps}
+        \includegraphics[width=0.45\textwidth]{figs/A2.eps}
+        \includegraphics[width=0.45\textwidth]{figs/A3.eps}
+        \includegraphics[width=0.45\textwidth]{figs/A4.eps}
+        \caption{Steady-state velocity $\cU$ as a function of the electric field magnitude $\beta$, 
+        for $\gamma > 1$.}
+        \label{fig:NumResA}
+    \end{center}
+\end{framed}
+\end{figure}
+\begin{figure}[htbp]
+\begin{framed}
+    \begin{center}
+        \includegraphics[width=0.45\textwidth]{figs/B1.eps}
+        \includegraphics[width=0.45\textwidth]{figs/B2.eps}
+        \includegraphics[width=0.45\textwidth]{figs/B3.eps}
+        \includegraphics[width=0.45\textwidth]{figs/B4.eps}
+        \caption{Steady-state velocity $\cU$ as a function of the electric field magnitude $\beta$,
+        for $\gamma < 1$.}
+        \label{fig:NumResB}
+    \end{center}
+\end{framed}
+\end{figure}
+\begin{figure}[htbp]
+\begin{framed}
+    \begin{center}
+        \includegraphics[width=0.3\textwidth]{figs/D1n.eps}
+        \includegraphics[width=0.3\textwidth]{figs/D1a.eps}
+
+        \includegraphics[width=0.3\textwidth]{figs/D2n.eps}
+        \includegraphics[width=0.3\textwidth]{figs/D2a.eps}
+
+        \includegraphics[width=0.3\textwidth]{figs/D3n.eps}
+        \includegraphics[width=0.3\textwidth]{figs/D3a.eps}
+
+        \includegraphics[width=0.3\textwidth]{figs/D4n.eps}
+        \includegraphics[width=0.3\textwidth]{figs/D4a.eps}
+        \caption{Streamlines of the flow for various electric field values: numerical results (left)
+        and analytical approximation (right).}
+        \label{fig:NumResC}
+    \end{center}
+\end{framed}
+\end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \bibliographystyle{elsarticle-num}
-\bibliography{}
+\bibliography{main}
 

### 2012-03-04 notes/article/main.tex
Review chapters 1-3

--- 2012-02-21 notes/article/main.tex
@@
 \usepackage{graphicx}
+\usepackage{tikz}
+\usepackage{amsmath} 
 \usepackage{amssymb}
 \usepackage{amsthm}
+\usepackage{units}   
+\usepackage{float}   
+\usepackage{graphicx}
+\usepackage{amsfonts}
+\usepackage{mathrsfs}
+\usepackage[colorlinks]{hyperref}
+\usepackage{framed}
+
+\floatstyle{ruled}
+\newfloat{program}{thp}{lop}
+%-------------------------------------------
+\newcommand{\sign}{\ensuremath{\mathrm{sign}}}
+\newcommand{\diag}{\ensuremath{\mathrm{diag}}}
+\newcommand{\trace}[1]{\ensuremath{\mathrm{trace}\left( #1 \right)}}
+\newcommand{\norm}[1]{\ensuremath{\left\|#1\right\|_2^2}}
+\newcommand{\func}[2]{\ensuremath{\mathrm{#1}\left( #2 \right)}}
+\newcommand\eps \epsilon
+\newcommand{\R}{\ensuremath{\mathbb{R}}}
+\newcommand{\N}{\ensuremath{\mathbb{N}}}
+\newcommand{\real}{\ensuremath{\mathbb{R}}}
+\newcommand{\cl}[1]{\ensuremath{\mathcal{#1}}}
+\newcommand{\suppsize}[1]{\ensuremath{|\mathcal{#1}|}}
+\newcommand{\vect}[1]{\ensuremath{\mathbf{#1}}}
+\newcommand{\matr}[1]{\ensuremath{\mathbf{#1}}}
+\newcommand{\deriv}[2]{\frac{\partial #1}{\partial #2}}
+\newcommand{\arr}[2]{\begin{array}{#1}#2\end{array}}
+\newcommand{\mat}[2]{\left(\begin{array}{#1}#2\end{array}\right)}
+\newcommand{\brc}[2]{\left\{\begin{array}{#1}#2\end{array}\right.}
+\newcommand{\pars}[1]{\left(#1\right)}
+\newcommand{\brcs}[1]{\left\{#1\right\}}
+\newcommand{\half}{\frac{1}{2}}
+
+% Bold symbols and operators
+\newcommand\Laplacian{\nabla^2}
+\newcommand\bnabla{\boldsymbol{\nabla}}
+\newcommand\bLaplacian{\boldsymbol{\nabla}^2}
+\newcommand\bcdot{\boldsymbol{\cdot}}
+\newcommand\bU{\mathscr{\boldsymbol{U}}}
+\newcommand\bv{\boldsymbol{v}}
+\newcommand\bV{\boldsymbol{V}}
+\newcommand\bE{\boldsymbol{E}}
+\newcommand\be{\boldsymbol{\hat{e}}}
+\newcommand\bn{\boldsymbol{\hat{n}}}
+\newcommand\bk{\boldsymbol{\hat{k}}}
+\newcommand\bj{\boldsymbol{j}}
+\newcommand\bi{\boldsymbol{i}}
+\newcommand\bs{\boldsymbol{s}}
+\newcommand\bA{\boldsymbol{A}}
+\newcommand\bF{\boldsymbol{F}}
+\newcommand\bG{\boldsymbol{G}}
+\newcommand\bI{\boldsymbol{I}}
+\newcommand\bJ{\boldsymbol{J}}
+\newcommand\bx{\boldsymbol{x}}
+\newcommand\by{\boldsymbol{y}}
+\newcommand\bz{\boldsymbol{z}}
+\newcommand\br{\boldsymbol{r}}
+\newcommand\bc{\boldsymbol{c}}
+\newcommand\bxhat{\hat{\bx}}
+\newcommand\byhat{\hat{\by}}
+\newcommand\bzhat{\hat{\bz}}
+\newcommand\brhat{\hat{\br}}
+\newcommand\bnhat{\hat{\boldsymbol{n}}}
+\newcommand\btheta{\boldsymbol{\theta}}
+\newcommand\bthetahat{\hat{\btheta}}
+\newcommand\bphi{\boldsymbol{\phi}}
+\newcommand\bphihat{\hat{\bphi}}
+\newcommand\bzero{\boldsymbol{0}}
+\newcommand\bomega{\boldsymbol{\omega}}
+\newcommand\bpsi{\boldsymbol{\psi}}
+
+% Calligraphic symbols
+\newcommand\cB{\mathcal{B}}
+\newcommand\cE{\mathcal{E}}
+\newcommand\cF{\mathcal{F}}
+\newcommand\cO{\mathcal{O}}
+\newcommand\cG{\mathcal{G}}
+\newcommand\cI{\mathcal{I}}
+\newcommand\cP{\mathcal{P}}
+\newcommand\cD{\mathcal{D}}
+\newcommand\cL{\mathcal{L}}
+\newcommand\cU{\mathscr{U}}
+\newcommand\cV{\mathscr{V}}
+\newcommand\cW{\mathscr{W}}
+
+% Tensors
+\newcommand\tI{\mathsf{I}}
+\newcommand\tS{\mathsf{S}}
+\newcommand\tT{\mathsf{T}}
+
+% Unit vector
+\newcommand\ui{\boldsymbol{\hat{\imath}}}
+
+\setlength{\textheight}{8.7in}
+\setlength{\columnsep}{2.0pc}
+\setlength{\textwidth}{6.6in}
+% \setlength{\footheight}{0.2in}
+\setlength{\topmargin}{0.05in}
+\setlength{\headheight}{0.2in}
+\setlength{\headsep}{0.1in}
+\setlength{\evensidemargin}{0in}
+\setlength{\oddsidemargin}{0in}
+% \setlength{\parindent}{1pc}
+\setlength{\parindent}{0.0 in}
+\setlength{\parskip}{0.1 in}
 
@@
 \begin{abstract}
-This is the abstract.
 \end{abstract}
@@
 \begin{keyword}
-numerical \sep electrokinetics 
 \end{keyword}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction} \label{intro}
+\section{Introduction} \label{sec:intro}
+
+Electrokinetic theory describes the dynamics of charged particles
+in ionic fluids \cite{kirby2010book}.
+When a particle acquires surface charge, a layer
+of ions of opposite charge is attracted to the surface via
+electric forces, creating a double-layer structure around the
+particle (see Figure \ref{fig:EDL}). This structure, called
+``Debye layer'', electrically screens the surface charge, thus
+creating a potential difference between the particle and the outer
+layer of the fluid bulk.
+In cases where the layer width is much smaller than the particle's
+size, an analytical asymptotic solution for the Debye layer
+dynamics can be found \cite{yariv2010asymptotic}.
+
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=0.2\textwidth]
+            {figs/ElectricDoubleLayer.eps}
+        \caption{Schematic structure of the double layer:
+        (1) particle surface, (2) Debye layer and (3) fluid bulk.
+        If the particle surface has positive (blue) surface charge,
+        it attracts negative (red) ions from the fluid making the
+        Debye layer negatively charged (as opposed to the rest of
+        the fluid bulk, which is electrically neutral).
+        The zeta potential is defined as the voltage drop across (2).}
+        \label{fig:EDL}
+    \end{center}
+\end{figure}
+% \begin{tikzpicture}\end{tikzpicture}
+
+The variables of the electrokinetic problem are the electrostatic
+potential $\varphi$, fluid velocity $\bv$ and its pressure $p$ and
+ionic concentration $c$.
+The boundary conditions are determined by the specific
+problem under consideration and defined by the particle's
+geometry, chemical characteristics, and the fluid dynamics.
+
+The partial differential equations that describe the system dynamics
+under an external electric field, are coupled and non-linear, and
+in general, they have no analytic solution.
+
+Moreover, any numerical solver must handle the scale disparity caused by the
+Debye layer width being much smaller than the particle's size. A
+closed-form linear asymptotic solution has been developed for
+spherical ion-exchanging particles and weak electric field in an
+axisymmetric setting \cite{yariv2010migration} but it is hard to extend this
+analytic solution to more general systems. Once the electric field
+becomes stronger, significant nonlinear phenomena are expected.
+This interesting regime has not yet been explored.
+
+Recently, it has been conceived that such type of dynamics
+can be very useful in transporting and manipulating micro-
+and nanoscale objects for many nanotechnology applications,
+such as the self-assembly of superstructures, roving sensors, 
+drug-delivery systems and useful nanomachinery 
+\cite{howse2007self,paxton2004catalytic,pumera2010electrochemically}.
+However, since the analytic model for these electrokinetic
+phenomena has no closed-form analytic solution, a numerical
+solver has to be developed for analysing such system.
+
+The goal is to implement an accurate and fast iterative numerical
+solver for electrokinetic problems, and apply it to the study
+of systems that have no closed-form solutions.
+It is expected to gain insight into the chemical and physical behavior 
+in far more general regimes than are currently well-understood, 
+and also lead to further analytical developments, based on new scaling behavior
+provided by the numerical solver. We may also target interesting physical
+phenomena that have been observed experimentally.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Governing Equations} \label{equations}
+\section{Governing Equations} \label{sec:equations}
+
+\subsection{Dimensionless Notation}
+
+Spatial coordinates $\br$ are normalized by $a^*$ (the characteristic size of the ion-exchanger).
+
+Positive and negative ionic concentrations are denoted by $c_+$ and $c_-$ respectively, and
+are normalized by ambient ionic concentration $c^*$. The ionic valences are $\pm z$.
+
+The dimensional ionic fluxes are given by Nernst-Plank equation 
+(using Einstein relation for the electric mobility, $\mu_q^* = D^* / k_B^* T^*$):
+\begin{eqnarray*}
+\bj^*_\pm &=& 
+-D^* \bnabla c^*_\pm + \bv^* c^*_\pm \mp \frac{z e^* D^*}{k_B^* T^*} c^*_\pm \bnabla \varphi^*,
+\end{eqnarray*}
+where $D^*$ is the ionic diffusivity.
+
+The electric potential $\varphi$ is normalized by the thermal voltage:
+\begin{eqnarray*}
+\varphi^* &=& \frac{k_B^* T^*}{z e^*} = \frac{R^* T^*}{z F^*},
+\end{eqnarray*}
+where $R^* = k_B^* N_A$ and $F^* = e^* N_A$ is the Faraday number.
+
+The dimensional Stokes equation:
+\begin{eqnarray*}
+-\bnabla p^* + \mu^* \bLaplacian \bv^* + \eps^* \Laplacian \varphi^* \bnabla \varphi^* &=& 0.
+\end{eqnarray*}
+
+The velocity $\bv$ is normalized by $v^* = {\eps^* (\varphi^*)^2}/{a^* \mu^*}$,
+and the pressure $p$ is normalized by $p^* = {\mu^* v^*}/{a^*} = {\eps^* (\varphi^*)^2}/{(a^*)^2}$.
+The fluxes $\bj^*_\pm$ are normalized by $j^* = {D^* c^*}/{a^*}$.
+
+The nondimensional Nernst-Plank equation is written as:
+\begin{eqnarray*}
+\bj_\pm &=& 
+-\bnabla c_\pm + \alpha \bv c_\pm \mp c_\pm \bnabla \varphi,
+\end{eqnarray*}
+where $\alpha = {v^* a^*}/{D^*} = {\eps^* (\varphi^*)^2}/{\mu^* D^*}$ 
+is the dimensionless Peclet number.
+
+The dimensional Poisson equation is:
+\begin{eqnarray*}
+(c^*_+ - c^*_-) z F^* &=& -\eps^* \Laplacian \varphi^*,
+\end{eqnarray*}
+and after nondimensionalization, is:
+\begin{eqnarray*}
+c_+ - c_- &=& -\frac{\eps^* \varphi^*}{z F^* c^* (a^*)^2} \Laplacian \varphi = 
+-\delta^2 \Laplacian \varphi,
+\\
+\delta^2 &=& \frac{\eps^* \varphi^*}{c^* F^* z (a^*)^2} = 
+\pars{\frac{\delta^*}{a^*}}^2.
+\end{eqnarray*}
+
+The force is denoted by $\bF$ normalized by $\mu^* v^* a^* = \eps^* (\varphi^*)^2$.
+The stress tensor is denoted by $\tT$ and normalized by $p^* = \mu^* v^* / a^*$.
+The electric field is denoted by $\bE$ and normalized by $E^* = \varphi^* / a^*$.
+
+\subsection{Micro-scale phenomena}
+
+\subsubsection{Nernst-Planck Equations}
+The ionic fluxes are given by ion diffusion, electrostatic forces and ion advection by the fluid:
+\begin{eqnarray*}
+  \bj_\pm &=& -\bnabla c_\pm \mp c_\pm \bnabla \varphi + \alpha \bv c_\pm,
+\end{eqnarray*}
+
+Due to conservation of ions, the fluxes are divergence-free:
+\begin{eqnarray*}
+\bnabla \cdot \bj_\pm &=& 0.
+\end{eqnarray*}
+These equation may be re-written by using the following transform:
+\begin{eqnarray*}
+  c &=& \frac{c_+ + c_-}{2},\\
+  q &=& \frac{c_+ - c_-}{2}.
+\end{eqnarray*}
+Thus, salt and charge fluxes are defined by:
+\begin{eqnarray*}
+  \bj &=& \frac{\bj_+ + \bj_-}{2} = -\bnabla c - q \bnabla \varphi + \alpha \bv c, \\
+  \bi &=& \frac{\bj_+ - \bj_-}{2} = -\bnabla q - c \bnabla \varphi + \alpha \bv q,
+\end{eqnarray*}
+and are divergence-free as well:
+\begin{eqnarray*}
+\bnabla \cdot \bj &=& 0, \\
+\bnabla \cdot \bi &=& 0. 
+\end{eqnarray*}
+
+\subsubsection{Incompressible Stokes Flow with Electrostatic Force}
+Mass conservation (due to constant fluid density):
+\begin{eqnarray*}
+\bnabla \cdot \bv &=& 0.
+\end{eqnarray*}
+Momentum conservation (force balance):
+\begin{eqnarray*}
+\Laplacian \bv - \bnabla p + \bnabla \varphi \Laplacian \varphi &=& 0.
+\end{eqnarray*}
+Free charge density is given by the Poisson equation:
+\begin{eqnarray*}
+\delta^2 \Laplacian \varphi &=& -2q.
+\end{eqnarray*}
+
+\subsubsection{Boundary conditions}
+An constant electric field $\bE = \beta \ui$ is applied to the system.
+The ion-exchanger will acquire a non-zero steady-state velocity $\cU \ui$, which is
+a function of the applied field, and is not known a priori.
+
+An ion-exchanger fixed reference frame is used.
+Far away from the particle, we have uniform applied electrostatic field, uniform flow
+and ambient ionic concentrations:
+\begin{eqnarray*}
+-\bv &\rightarrow& \cU \ui, \\
+-\bnabla \varphi &\rightarrow& \beta\ui, \\
+c_\pm &\rightarrow& 1.
+\end{eqnarray*}
+
+We consider a spherical ion-exchanger. 
+At its surface $\mathcal{S}$ (defined at $r=1$ with normal $\bn = \brhat$), 
+we have zero slip, anion impermeability, cation selectivity 
+(with fast Butler-Volmer\cite{bard2000book} kinetics
+$\bn \cdot \bj_+ = k (1 - c_+/\gamma)$, where $k \rightarrow \infty$).
+and high conductance of the particle (yielding uniform electric potential):
+\begin{eqnarray*}
+\bv & = & \bzero, \\
+\bn \cdot \bj_- & = & 0, \\
+c_+ &=& \gamma, \\
+\varphi & = & \cV.
+\end{eqnarray*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Separation of scales}
+When $\delta \ll 1$, 
+most of the fluid remains electroneutral ($q \approx 0$, thus $c_+ \approx c_-$), 
+except a thin boundary layer of width $O(\delta)$, 
+also known as the ``Debye layer'', surrounding the ion exchanger.
+
+\subsubsection  {Bulk-scale equations}
+The Nernst-Planck equations above for the fluid bulk (outside
+the boundary layer), using bulk variables, read:
+\begin{eqnarray*}
+  Q & = & 0, \\
+  C & = & C_+ = C_-, \\
+\bJ &=& -\bnabla C + \alpha \bV C, \\
+\bI &=& -C \bnabla \varPhi.
+\end{eqnarray*}
+Because the flow is incompressible ($\bnabla \cdot V = 0$), 
+ion conservation results in the following equations:
+
+\begin{enumerate}
+\item Salt conservation macroscale equation:
+\begin{eqnarray} \label{eq:salt}
+\bnabla \cdot \bJ = \Laplacian C - \alpha \bV \cdot \bnabla C = 0. 
+\end{eqnarray}
+
+\item Charge conservation macroscale equation:
+\begin{eqnarray} \label{eq:charge}
+\bnabla \cdot \bI = \bnabla \cdot \pars{ C \bnabla \varPhi } = 0.
+\end{eqnarray}
+
+\end{enumerate}
+
+The macroscale Stokes flow equations have the same form as the microscale equations:
+\begin{eqnarray}  \label{eq:stokes}
+\brc{rcc}{\bnabla \cdot \bV &=& 0, \\  
+\Laplacian \bV - \bnabla P + \bnabla \varPhi \Laplacian \varPhi &=& \bzero.}
+\end{eqnarray}
+
+\subsubsection{Bulk-scale effective boundary conditions}
+
+Using the derivation in \ref{append:effbnd}, the effective boundary conditions at the
+ion-exchanger surface are:
+\begin{eqnarray}
+0 &=& \varPhi + \log C \\
+0 &=& \bnhat \cdot \bnabla \pars{\varPhi - \log C} \\
+\bV &=& 
+\zeta \cdot \bnabla_\mathcal{S} \varPhi 
++ 2\log\pars{1-\tanh^2\frac{\zeta}{4}} \cdot \bnabla_\mathcal{S} \log C.
+\end{eqnarray}
+where $\zeta = \cV - \varPhi = \log (C / \gamma)$ 
+is the zeta potential (the voltage drop across the Debye layer).
+
+\subsection{Steady state}
+The stress tensor is composed of Newtonian and Maxwel stresses:
+\begin{eqnarray*}
+\tT &=& \bnabla \bV + (\bnabla \bV)^\dagger - P \tI
++ \bnabla \varPhi \bnabla \varPhi - \frac{1}{2} (\bnabla \varPhi \cdot \bnabla \varPhi) \tI, \\
+\bnabla \cdot \tT &=& \bzero.
+\end{eqnarray*}
+The total force acting on the particle is computed by the following surface integral:
+\begin{eqnarray*}
+\bF &=& \oint_\mathcal{S} \tT \cdot \bnhat dA.
+\end{eqnarray*}
+In steady state (constant particle drift velocity $\cU$), 
+the total force must be zero: 
+\begin{eqnarray*}
+\bF = \bzero.
+\end{eqnarray*}
+
+The total force $\bF(\beta, \cU)$ is a function of the applied electric field $\beta$ and
+the velocity $\cU$.
+For any given electric field $\beta$, the force-free constraint above 
+can be solved numerically for $\cU$ to yield the corresponding steady-state velocity.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Algorithm Description} \label{algorithm}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Numerical Tests} \label{results}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusions and Future Work} \label{conclusions}
+The numerical solver starts by constructing a discrete approximation for the nonlinear system,
+for a given electric field $\beta$ and a velocity $\cU$. The nonlinear discrete system is
+solved numerically using Newton's Method, so the total force on the particle can be computed
+numerically. Variation of $\cU$ is used to find steady-state velocity, yielding zero total force.
+
+\subsection{Discretization}
+\subsubsection{Spherical Coordinates}
+Because the system is axisymmetric, the operators are written in 
+spherical coordinates $(r,\theta,\phi)$ 
+using the derivation at \ref{append:spherical}.
+The scalar gradient and the divergence can be written as:
+\begin{eqnarray*}
+\bnabla f &=& \deriv{f}{r}\brhat + \frac{1}{r}\deriv{f}{\theta}\bthetahat, \\
+\bnabla \cdot \bF &=& \frac{1}{r^2}\deriv{}{r}\pars{F_r r^2 } + 
+               \frac{1}{r \sin\theta}\deriv{}{\theta}\pars{F_\theta \sin\theta}.
+\end{eqnarray*}
+The scalar Laplacian can be written as:
+\begin{eqnarray*}
+\Laplacian f = \bnabla \cdot (\bnabla f)&=& 
+ \frac{1}{r^2}\deriv{}{r}\pars{r^2 \deriv{f}{r}} + 
+ \frac{1}{r^2 \sin\theta}\deriv{}{\theta}\pars{\sin\theta \deriv{f}{\theta}}.
+\end{eqnarray*}
+The vector gradient can be written as:
+\begin{eqnarray*}
+\bnabla \bF &=& \deriv{F_r}{r} \brhat \brhat + \deriv{F_\theta}{r} \brhat \bthetahat + 
+\frac{1}{r}\pars{\deriv{F_r}{\theta} - F_\theta} \bthetahat \brhat + 
+\frac{1}{r}\pars{\deriv{F_\theta}{\theta} + F_r} \bthetahat \bthetahat.
+\end{eqnarray*}
+The vector Laplacian can be written as:
+\begin{eqnarray*}
+\bLaplacian \bF &=& 
+\left(\Laplacian F_r - \frac{2F_r}{r^2} - 
+\frac{2}{r^2 \sin\theta} \deriv{\left(F_\theta \sin\theta \right)}{\theta}\right)\brhat
++ \left(\Laplacian F_\theta - \frac{F_\theta}{r^2 \sin^2\theta} + 
+\frac{2}{r^2}\deriv{F_r}{\theta}\right) \bthetahat.
+\end{eqnarray*}
+
+It is important to note that due to the choice of spherical coordinate system,
+the vector Laplacian operator cannot be computed as in the Cartesian system,
+since the unit vectors $\brhat, \bthetahat, \bphihat$ are functions of the coordinates.
+
+\subsubsection{Computational Grid}
+In order to discretize the differential operators, 
+a regular grid of size $n_r \times n_\theta$ is defined, with:
+\begin{eqnarray*}
+(r_i,\theta_j) &\in& [1, \infty) \times [0,\pi], \\ 
+r_i &=& (1+\Delta_r)^i, \\
+\theta_j &=& \Delta_\theta \cdot j,
+\end{eqnarray*}
+where a logarithmic grid spacing is used for $r$ and a uniform grid is used for $\theta$.
+Note that $r_0 = 1$ and $R_{max} = (1+\Delta_r)^{n_r}$ should be much 
+larger than $r_0$. Thus:
+\begin{eqnarray*}
+\Delta_r &=& \pars{R_{max}} ^ \frac{1}{n_r} - 1, \\
+\Delta_\theta &=& \frac{\pi}{n_\theta}.
+\end{eqnarray*}
+
+This grid induces a disjoint subdivision of the domain 
+$\Omega = [1, R_{max}] \times [0,\pi]$ into cells:
+\begin{eqnarray*}
+\bigcup_{ij}\Omega_{ij} &=& \Omega.
+\end{eqnarray*}
+A specific cell $\Omega_{ij}$ and its center $(\bar{r}_i, \bar{\theta}_j)$ are defined by:
+\begin{eqnarray*}
+\Omega_{ij} &=& [r_{i-1}, r_{i}] \times [\theta_{j-1}, \theta_{j}], \\
+\bar{r}_i &=& \frac{r_{i-1} + r_{i}}{2}, \\
+\bar{\theta}_j &=& \frac{\theta_{j-1} + \theta_{j}}{2}.
+\end{eqnarray*}
+
+Each variable is discretized with respect of its cell as follows:
+\begin{itemize}
+\item $\varPhi$, $C$ and $P$ are represented by their value at the center of each cell, 
+using an all-centered grid:
+\begin{eqnarray*}
+\varPhi^h_{[i,j]} &=& \varPhi(\bar{r}_i, \bar{\theta}_j), \\
+C^h_{[i,j]} &=& C(\bar{r}_i, \bar{\theta}_j), \\
+P^h_{[i,j]} &=& P(\bar{r}_i, \bar{\theta}_j).
+\end{eqnarray*}
+\item $\bV$ is represented by its values at cell boundaries, using a staggered grid:
+\begin{eqnarray*}
+V_r^h{}_{[i,j]} &=& V_r(r_i, \bar{\theta}_j), \\
+V_\theta^h{}_{[i,j]} &=& V_\theta(\bar{r}_i, {\theta}_j).
+\end{eqnarray*}
+\end{itemize}
+
+\subsubsection{Operator Discretization}
+A finite-volume method with linear interpolation is used for flux discretization. 
+%$\boldsymbol{f}^h$
+
+Define the following discrete central difference operators:
+\begin{eqnarray*}
+\cD_r(f^h){}_{\left[i+\half,j\right]} &=& \frac{f^h_{\left[i+1,j\right]} - f^h_{\left[i,j\right]}}
+                       {r_{\left[i+1,j\right]} - r_{\left[i,j\right]}}, \\
+\cD_\theta(f^h){}_{\left[i,j+\half\right]} &=& \frac{f^h_{\left[i,j+1\right]} - f^h_{\left[i,j\right]}}
+					   {\theta_{\left[i,j+1\right]} - \theta_{\left[i,j\right]}}.
+\end{eqnarray*}
+
+Define the following linear interpolation operators:
+\begin{eqnarray*}
+\cI_r(f^h)_{\left[i+\half,j\right]} &=& 
+\frac{r_{\left[i+\half,j\right]} - r_{\left[i,j\right]}}
+{r_{\left[i+1,j\right]} - r_{\left[i,j\right]}} 
+f^h_{\left[i+1,j\right]} 
++ 
+\frac{r_{\left[i+1,j\right]} - r_{\left[i+\half,j\right]}}
+{r_{\left[i+1,j\right]} - r_{\left[i,j\right]}}
+f^h_{\left[i,j\right]},
+\\
+\cI_\theta(f^h)_{\left[i,j+\half\right]} &=& 
+\frac{r_{\left[i,j+\half\right]} - r_{\left[i,j\right]}}
+{r_{\left[i,j+1\right]} - r_{\left[i,j\right]}}
+  f^h_{\left[i,j+1\right]} + 
+\frac{ r_{\left[i,j+1\right]} - r_{\left[i,j+\half\right]}}
+{r_{\left[i,j+1\right]} - r_{\left[i,j\right]}}
+  f^h_{\left[i,j\right]}.
+\end{eqnarray*}
+
+The total flux of a cell is equal to zero ($\bnabla \cdot \boldsymbol{f} = 0$):
+\begin{eqnarray*}
+\frac{1}{r^2} \cD_r\pars{f^h_r r^2} + 
+\frac{1}{r \sin\theta} \cD_\theta\pars{f^h_\theta \sin\theta} =
+\frac{\cD_r\pars{f^h_r \cdot r^2 \sin\theta} + 
+\cD_\theta\pars{f^h_\theta \cdot r \sin\theta}}{r^2 \sin\theta} = 0. 
+\end{eqnarray*}
+
+Ion flux ($\bI = - C \bnabla \varPhi$) is discretized on grid cell boundaries:
+\begin{eqnarray*}
+I^h_r &=& -\cI_r(C^h) \cdot \cD_r(\varPhi^h), \\
+I^h_\theta &=& -\cI_\theta(C^h) \cdot \frac{\cD_\theta(\varPhi^h)}{r}.
+\end{eqnarray*}
+
+Salt flux ($\bJ = -\bnabla C + \alpha \bV C$) is discretized on grid cell boundaries 
+(using upwind scheme $\mathcal{U}$ for numerical stability at large cell Peclet number):
+\begin{eqnarray*}
+J^h_r &=& -\cD_r(C^h) + \alpha V^h_r \cdot \mathcal{U}^{\bV^h}_r (C^h), \\
+J^h_\theta &=& -\frac{\cD_\theta(C^h)}{r} + \alpha V^h_\theta \cdot \mathcal{U}^{\bV^h}_\theta (C^h), \\
+ \mathcal{U}^{\bV^h}_r(C^h)[i,j] &=& C^h\left[i-\frac{\sign(V^h_r)}{2}, j\right], \\
+ \mathcal{U}^{\bV^h}_\theta(C^h)[i,j] &=& C^h\left[i, j-\frac{\sign(V^h_\theta)}{2}\right]. 
+\end{eqnarray*}
+
+Mass flux $\bV$ is discretized on grid cells boundaries, 
+using the velocity staggered grid.
+
+Force components ($\bF = -\bnabla P + \bLaplacian \bV + \bnabla \varPhi \Laplacian \varPhi$) 
+are discretized on the velocity staggered grid, where
+linear interpolation is used for the Coulomb force and for vector Laplacian components.
+\begin{eqnarray*}
+F^h_r &=& -\cD_r(P^h) 
+          + \cL(V^h_r) - \frac{2}{r^2} V^h_r 
+		  - \frac{2}{r^2 \sin\theta} \cI_r(\cD_\theta (V^h_\theta \sin\theta))
+          + \cD_r(\varPhi^h) \cdot \cI_r(\cL(\varPhi^h)), \\
+F^h_\theta &=& -\frac{\cD_\theta(P^h)}{r} 
+		  + \cL(V^h_\theta) - \frac{F^h_\theta}{r^2 \sin^2\theta} 
+		  + \frac{2}{r^2} \cI_\theta(\cD_\theta(F^h_r))
+		  + \frac{\cD_\theta(\varPhi^h)}{r} \cdot \cI_\theta(\cL(\varPhi^h)), \\
+\cL(f^h) &=& \frac{1}{r^2}\cD_r\pars{\cD_r(f^h) r^2} + 
+\frac{1}{r^2 \sin\theta} \cD_\theta\pars{\cD_\theta(f^h) \cdot \sin\theta}.
+\end{eqnarray*}
+
+\subsubsection{Boundary Conditions}
+In order to discretize boundary condtions for $\varPhi$, $C$ and $\bV$, 
+``ghost'' points are employed. 
+The grid is extended to include points outside the domain interior,
+and the variables at the ``ghost'' points are set to satisfy 
+the discretized boundary conditions, following the analysis below.
+Note that $P$ has no boundary conditions -- so the pressure variable is defined 
+only in the domain interior.
+
+The boundary conditions at the ion-exchange boundary ($r=1$) are:
+\begin{eqnarray*}
+\cI_r(\varPhi^h) &=& -\cI_r(\log C^h), \\
+\cD_r(\varPhi^h) &=& \cD_r(\log C^h), \\
+V^h_r &=& 0, \\
+V^h_\theta &=& 4\log\pars{\frac{1 + \exp\left\{\cI_\theta(\zeta^h)/2\right\}}{2}} \cdot 
+			\cD_\theta(\zeta^h), \\
+  \zeta^h &=& - \log \gamma - \cI_r(\varPhi^h).
+\end{eqnarray*}
+The equations are discretized using ``ghost'' points outside the interior of the domain:
+\begin{eqnarray*}
+ \varPhi^h_{[1/2, j]} = \frac{\varPhi^h_{[0,j]} + \varPhi^h_{[1,j]}}{2} &=& 
+	-\frac{\log C^h_{[0,j]} + \log C^h_{[1,j]}}{2} = -\log C^h_{[1/2, j]}, \\
+  \frac{\varPhi^h_{[1,j]} - \varPhi^h_{[0,j]}}{\Delta r} &=& 
+	\frac{\log C^h_{[1,j]} - \log C^h_{[0,j]}}{\Delta r}. 
+\end{eqnarray*}
+By adding and subtracting the equations, we have:
+\begin{eqnarray*}
+\varPhi^h_{[0,j]} &=& -\log\brcs{C^h_{[1,j]}}, \\
+C^h_{[0,j]} &=& \exp\brcs{-\varPhi^h_{[1,j]}}, \\
+  \zeta^h_{[j]} &=& \cV - \varPhi^h_{[1/2,j]}
+                     = -\log\gamma -\frac{\varPhi^h_{[0,j]} + \varPhi^h_{[1,j]}}{2}.
+\end{eqnarray*}
+The slip condition can be written as:
+\begin{eqnarray*}
+V_r^h{}_{[0,j]} &=& 0, \\
+V_\theta^h{}_{[1/2,j]} &=& 
+4\log\pars{\frac{1 + \exp\left\{\frac{1}{2}
+ \frac{\zeta^h_{[j]} + \zeta^h[j+1]}{2}\right\}}{2}} 
+\cdot \frac{\zeta^h_{[j+1]} - \zeta^h_{[j]}}{\bar{\theta}_{j+1} - \bar{\theta}_{j}}, \\
+  V^h_\theta{}_{[0,j]} &=& 2 V^h_\theta{}_{[1/2, j]} - V^h_\theta{}_{[1,j]}.
+\end{eqnarray*}
+
+For $\theta = 0$ and $\theta = \pi$, the ``ghost'' points are defined by symmetry considerations:
+\begin{eqnarray*} 
+\brc{l}{
+\varPhi^h_{[i, 0]} = \varPhi^h_{[i, 1]} \\
+C^h_{[i, 0]} = C^h_{[i, 1]} \\
+V_r^h{}_{[i, 0]} = V_r^h{}_{[i, 1]} \\
+V_\theta^h{}_{[i, 0]} = 0
+} 
+\brc{l}{
+\varPhi^h_{[i, n_\theta+1]} = \varPhi^h_{[i, n_\theta]}, \\
+C^h_{[i, n_\theta+1]} = C^h_{[i, n_\theta]}, \\
+V_r^h{}_{[i, n_\theta+1]} = V_r^h{}_{[i, n_\theta]}, \\
+V_\theta^h{}_{[i, n_\theta+1]} = 0.
+} 
+\end{eqnarray*}
+
+Far away from the ion-exchange boundary ($r\rightarrow\infty$) we have:
+\begin{eqnarray*}
+\frac{\varPhi^h_{[n_r + 1, j]} - \varPhi^h_{[n_r, j]}}{\bar{r}_{n_r + 1} - \bar{r}_{n_r}} 
+ & = & -\beta \cos\bar{\theta}_j, \\
+C^h_{[n_r + 1, j]} & = & 1 \\
+V_r^h{}_{[n_r + 1, j]} & = & -\cU \cos\bar{\theta}_j, \\
+V_\theta^h{}_{[n_r + 1, j]} & = & \cU \sin\theta_j.
+\end{eqnarray*}
+
+Because the grid is finite, the choice 
+$r_{n_r} = R_{max}$ must be taken large enough so as to have a negligible effect
+on the solution.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Solver Design}
+\subsubsection{Newton's Method}
+An operator $\cO$ is defined by its input vector $\bx$ and its output 
+$\by = \cO(\bx)$.
+
+In order to solve the equation $\cO(\bx) = \bzero$, Newton's method can 
+be applied, given an initial solution $\bx_0$:
+\begin{eqnarray*}
+\bzero = \cO(\bx_n + \Delta \bx_n) &\approx& \cO(\bx_n) + \bnabla \cO(\bx_n)\cdot\Delta\bx_n, \\
+\Rightarrow \bnabla \cO(\bx_n) \cdot \Delta \bx_n &=& -\cO(\bx_n), \\
+\bx_{n+1} &=& \bx_{n} + \Delta \bx_n. 
+\end{eqnarray*}
+
+Each step requires the computation of the residual vector, $\br = \cO(\bx)$, and
+the gradient matrix of the operator, $\bG = \bnabla \cO(\bx)$, 
+given the current solution $\bx = \bx_n$.
+Then, a sparse linear system needs to be solved to yield the update for the 
+increment $\Delta \bx_n = \bx_{n+1} - \bx_n = -\bG^{-1} \br$.
+
+When the method converges, $\bx_n \rightarrow \bx_\infty$, 
+the convergence is in general quadratic:
+\begin{eqnarray*}
+\|\bx_{n+1} - \bx_\infty\| \le k \|\bx_{n} - \bx_\infty\|^2.
+\end{eqnarray*}
+Thus, when the initial guess is close enough to the solution, the solver
+will typically converge in very few steps.
+
+\subsubsection{Operator Representation}
+System variable $\bx$ is defined as the concatenation $[\,\varPhi, C, V_r, V_\theta, P\,]$,
+taking only values in the interior of the problem domain grid.
+Thus, each problem variable can be computed by applying an appropriate projection operator on $\bx$:
+\begin{eqnarray*}
+X &=& \cP_X(\bx) \mbox{ for } X \in \left\{\varPhi, C, V_r, V_\theta, P\right\}.
+\end{eqnarray*}
+
+The extended variables $\tilde X$ (including ``ghost'' point values) 
+are computed by applying the following nonlinear operators:
+\begin{eqnarray*}
+\tilde{\varPhi} &=& \cB_\varPhi(\varPhi, C; \beta), \\
+\tilde{C} &=& \cB_C(C, \varPhi), \\
+\tilde{V_r} &=& \cB_{V_r}(V_r; \cU), \\
+\tilde{V_\theta} &=& \cB_{V_\theta}(V_\theta, C, \varPhi; \cU, \gamma), \\
+\tilde{P} &=& P.
+\end{eqnarray*}
+The extended system variable can be written as $\tilde{\bx} = \cB(\bx)$, 
+where $\cB$ is the ``ghost'' point extension operator (derived using boundary conditions)
+so the concatenated equations of the system (as described above) can be written 
+as a non-linear operator $\cE(\tilde\bx) = \bzero$ acting on the extended system variable 
+$\tilde{\bx}$, where $\cE$ is the conservation equations operator 
+(derived by concatenation of the system equations).
+
+The problem can be cast as the following non-linear system:
+\begin{eqnarray*}
+\bzero = \cE (\tilde{\bx}) = \cE (\cB (\bx)) = \cO(\bx),
+\end{eqnarray*}
+ where $\cO = \cE \circ \cB$.
+
+\subsubsection{Steady-state}
+Let $\beta$ be a specific field magnitude
+Assume that $\cU \ui$ is the drift velocity of the ion exchanger 
+(given that the fluid is at rest far away from the particle).
+After the convergence of the solver, $\cO(\bx_\infty) \rightarrow \bzero$, 
+the ``ghost'' point values are updated using $\tilde\bx_\infty = \cB(\bx_\infty)$,
+so  that the surface force $\boldsymbol{f} = \tT \cdot \bn$ acting 
+on the ion-exchanger surface
+can be computed by integration over the ion exchanger's surface $\mathcal S$.
+
+Due to symmetry considerations, the total force $\bF$ is 
+aligned with $\ui$ and it vanishes iff $\ui \cdot \bF = 0$.
+\begin{eqnarray*}
+F_\imath = \ui \cdot \bF &=& 
+\oint_\mathcal{S} \pars{\ui \cdot \tT \cdot \bnhat} dA = 
+\int_0^\pi f_\imath(\theta) 2\pi \sin\theta d\theta ,
+\\  
+f_\imath = \ui \cdot \tT \cdot \brhat &=& \pars{-P + 2\cD_r(V_r) + 
+\frac{1}{2}\pars{\cD_r(\varPhi)}^2 - \frac{1}{2r^2}\pars{\cD_\theta(\varPhi)}^2}\cos\theta 
+\\  
+&& -\pars{\cD_r(V_\theta) - \frac{V_\theta}{r}
++ \frac{1}{r}\cD_r(\varPhi) \cD_{\theta}(\varPhi)}\sin\theta, \\
+ \mathcal{S} &=& \{\br : \|\br\|_2 = 1\}.
+\end{eqnarray*}
+
+The integral for $F_\imath$ is approximated by 1D numerical quadrature
+(using the mid-point rule), to yield 
+the total force $F_\imath(\cU)$ as a function of the drift velocity $\cU$.
+
+Since the goal is to find steady-state solution, $F_\imath(\cU)$ 
+is required to be zero --
+and the appropriate $\cU$ is found by a simple 1D root-finding algorithm,
+applied as an outer loop.
+
+\subsubsection{Continuation}
+
+The iterative solver above can be used to compute the steady-state solution for any given $\beta$.
+For $\beta \ll 1$, the linear terms are the dominant ones, so the solution is linear in $\beta$ 
+(as derived in \cite{yariv2010migration}), and the solver convergence is fast.
+
+However, it is no longer true for $\beta \sim O(1)$, since the nonlinear terms become dominant
+and the iterative solver may not converge at all.
+In order to find a solution for such $\beta$, continuation method is used:
+the solver is applied to a sequence of $\{\beta_i\}_{i=0}^n$ such that $\beta_0 = 0$,
+$\beta_n = \beta$ and the solution $\bx_i$ for $\beta_i$ is used as the solver initializer
+for the problem of $\beta_{i+1}$.
+
+Given that $|\beta_{i+1} - \beta_i| < \eps$ for small enough $\eps$, 
+the next solution $\bx_{i+1}$ is close to the previous one $\bx_i$,
+so the iterative solver converges well.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Solver Implementation}
+
+Object-Oriented Design methodology is used for implementation.
+The MATLAB programming language is chosen due to strong numerical capabilities
+and high-level language features.
+
+\subsubsection{Operator Interface}
+The base \verb|Operator| interface is defined by 
+supporting the computation of a residual vector \verb|Operator::res()|
+and a gradient matrix \verb|Operator::grad()|, given an input vector $\bx$.
+
+This interface is implemented by specific operators classes,
+which are used to construct the system operator $\cO = \cE \circ \cB$, so that 
+the Newton method solver (that requires computing the residual and the gradient) 
+can be applied automatically.
+
+Each such operator may have other operators as its inputs, so the residual
+and the gradient are computed recursively, using the chain rule (applied to operators).
+
+\paragraph{Linear operator}
+If $\cO$ is linear, it can be represented by a matrix $L$, such that:
+\begin{eqnarray*}
+\cO(\bx) &=& L \bx, \\
+\bnabla\cO &=& L. 
+\end{eqnarray*}
+Note that finite difference $\cD$, interpolation $\cI$ and 
+upwind selection $\mathcal{U}$ operators
+can be implemented as linear sparse operators, by constructing 
+an appropriate sparse matrix $L$, having $O(\dim \bx)$ non-zeroes).
+This way, the computation of the residual is very fast, taking $O(\dim \bx)$ time,
+and the gradient is computed only once.
+
+\paragraph{Pointwise scalar function}
+Let $f: \R \rightarrow \R$ be a differentiable 1D function, whose derivative is
+denoted by $f': \R \rightarrow \R$. The operator $\cF$ can be defined to
+represent pointwise application of $f$:
+\begin{eqnarray*}
+\cF(\bx) &=& [f(x_1); \ldots; f(x_n)], \\
+\bnabla\cF(\bx) &=& \diag\{f'(x_1), \ldots, f'(x_n)\}.
+\end{eqnarray*}
+$f$ is defined and differentiated automatically using the MATLAB symbolic toolbox.
+
+\paragraph{Constant value}
+A constant operator $\mathcal{C}$ is defined by constant vector $\bc$ 
+(that does not depend on $\bx$):
+\begin{eqnarray*}
+\mathcal{C}(\bx) &=& \bc, \\
+\bnabla\mathcal{C} &=& \bzero.
+\end{eqnarray*}
+
+\paragraph{Binary operators}
+Let $\cO_1$ and $\cO_2$ be two operators, so their pointwise addition, subtraction,
+and multiplication, are defined as follows:
+\begin{eqnarray*}
+(\cO_1 \pm \cO_2)(\bx) &=& \cO_1)(\bx) \pm \cO_2(\bx), \\
+\bnabla (\cO_1 \pm \cO_2)(\bx)   &=& \bnabla\cO_1(\bx) \pm \bnabla\cO_2(\bx), \\
+(\cO_1 \cdot \cO_2)(\bx) &=& \diag(\diag(\cO_1(\bx)) \cdot \diag(\cO_2(\bx))), \\
+\bnabla (\cO_1 \cdot \cO_2)(\bx) &=& \diag(\cO_2(\bx)) \bnabla\cO_1(\bx) 
+                                  + \diag(\cO_1(\bx)) \bnabla\cO_2(\bx).
+\end{eqnarray*}
+
+\paragraph{N-ary operators}
+Given $N$ operators $\{\cO_i\}_{i=1}^N$, their concatenation $\cO$ is defined as:
+\begin{eqnarray*}
+\cO(\bx) &=& [\cO_1(\bx); \ldots; \cO_N(\bx)], \\
+(\bnabla\cO)(\bx) &=& [(\bnabla\cO_1)(\bx); \ldots; (\bnabla\cO_N)(\bx)].
+\end{eqnarray*}
+
+\subsubsection{Iterative Newton solver}
+Given an initial solution $\bx_0$ and specific values for $\beta$ and $\cU$, 
+we apply the following algorithm 
+until convergence ($\|\Delta \bx\| < \eps$):
+\begin{enumerate}
+\item Update the system operator: $\verb|op| = \verb|System|(\bx_{n})$
+\item Compute the gradient: $\boldsymbol{A}_n = \verb|op.grad()|$
+\item Compute the right-hand side: $\boldsymbol{b}_n = \verb|-op.res()|$
+\item Solve sparse linear system: $\boldsymbol{A}_n \Delta \bx_n = \boldsymbol{b}_n$
+\item Update solution: $\bx_{n+1} = \bx_{n} + \Delta \bx_{n}$
+\end{enumerate}
+
+\subsubsection{Total force integration}
+After the iterative Newton solver converges ($\bx_n \rightarrow \bx_\infty$), 
+the ``ghost'' point values are computed by computing $\cB(\bx_\infty)$ and
+the total force $\bF$ acting on the ion-exchanger.
+
+$F_\imath = \bF \cdot \ui$ is computed by using the mid-point quadrature rule:
+\begin{eqnarray*}
+F_\imath &=& \sum_{i=1}^{n_\theta} f(\bar\theta_i) \cdot 
+              2 \pi \sin\bar\theta_i \cdot \Delta\theta_i
+\end{eqnarray*}
+
+\subsubsection{Steady state drift velocity}
+In steady state, the total force acting on the particle $F_\imath$ must vanish.
+This constraint yields an equation, whose solution is the steady-state velocity $\cU$:
+\begin{eqnarray*}
+F_\imath(\cU) &=& 0
+\end{eqnarray*}
+This equation can be solved using a 1D root finding algorithm, e.g. the secant method:
+\begin{eqnarray*}
+\cU_{n+1} = \frac{F_\imath(\cU_{n})\cU_{n-1} - F_\imath(\cU_{n-1})\cU_{n}}
+{F_\imath(\cU_{n}) - F_\imath(\cU_{n-1})} \rightarrow \cU
+\end{eqnarray*}
+The result $\cU$ is the 
+steady state particle drift velocity for the electric field $\beta$.
 
 \bibliographystyle{elsarticle-num}
-\bibliography{}
+\bibliography{main}
 

### 2012-03-18 notes/article/main.tex
Work on the article.

@@
 \documentclass[final]{elsarticle}
+
+%\usepackage{setspace}\doublespacing
 
@@
 
-\title{Computational Electrokinetics}
-\author[tech]{Roman Zeyde}
-\author[tech]{Irad Yavneh}
+\title{A numerical solver for nonlinear electrokinetic phenomena}
+\author[cs]{Roman Zeyde}
+\author[cs]{Irad Yavneh}
+\author[math]{Ehud Yariv}
 
-\address[tech]{Technion, Israel}
+\address[cs]{Department of Computer Science, Technion -- Israel Institute of Technology, 
+Haifa 32000, Israel}
+\address[math]{Department of Mathematics, Technion -- Israel Institute of Technology, 
+Haifa 32000, Israel}
 
@@
 \begin{keyword}
+numerical, solver, electrokinetics, nonlinear
 \end{keyword}
@@
 geometry, chemical characteristics, and the fluid dynamics.
-
 The partial differential equations that describe the system dynamics
@@
 in general, they have no analytic solution. 
+Moreover, any numerical solver must handle the scale disparity caused by the
+Debye layer width being much smaller than the particle's size.
 
-Moreover, any numerical solver must handle the scale disparity caused by the
-Debye layer width being much smaller than the particle's size. A
-closed-form linear asymptotic solution has been developed for
+A closed-form linear asymptotic solution has been developed for
 spherical ion-exchanging particles and weak electric field in an
@@
 This interesting regime has not yet been explored.
-
 Recently, it has been conceived that such type of dynamics
@@
 
-The goal is to implement an accurate and fast iterative numerical
-solver for electrokinetic problems, and apply it to the study
+The goal of this work is to implement an accurate and fast iterative numerical
+solver for nonlinear electrokinetic problems, and apply it to the study
 of systems that have no closed-form solutions.
@@
 phenomena that have been observed experimentally.
+
+The paper is structured as follows: the governing equations of the electrokinetic model
+are derived in Section \ref{sec:equations}. The algorithm for the discretization and 
+the solution of the equation system is described at Section \ref{sec:algorithm}.
+The numerical results and their comparison to the analytical asymptotic solution 
+are presented and discussed in Section \ref{sec:results}.
 
@@
 \item Salt conservation macroscale equation:
-\begin{eqnarray} \label{eq:salt}
+\begin{eqnarray*} \label{eq:salt}
 \bnabla \cdot \bJ = \Laplacian C - \alpha \bV \cdot \bnabla C = 0. 
-\end{eqnarray}
+\end{eqnarray*}
 
 \item Charge conservation macroscale equation:
-\begin{eqnarray} \label{eq:charge}
+\begin{eqnarray*} \label{eq:charge}
 \bnabla \cdot \bI = \bnabla \cdot \pars{ C \bnabla \varPhi } = 0.
-\end{eqnarray}
+\end{eqnarray*}
 
@@
 The macroscale Stokes flow equations have the same form as the microscale equations:
-\begin{eqnarray}  \label{eq:stokes}
+\begin{eqnarray*}  \label{eq:stokes}
 \brc{rcc}{\bnabla \cdot \bV &=& 0, \\  
 \Laplacian \bV - \bnabla P + \bnabla \varPhi \Laplacian \varPhi &=& \bzero.}
-\end{eqnarray}
+\end{eqnarray*}
 
 \subsubsection{Bulk-scale effective boundary conditions}
-
-Using the derivation in \ref{append:effbnd}, the effective boundary conditions at the
-ion-exchanger surface are:
-\begin{eqnarray}
+By integrating the microscale equations across the Debye layer
+(see the full derivation in \cite{yariv2010asymptotic}), 
+the effective boundary conditions at the ion-exchanger surface are:
+\begin{eqnarray*}
 0 &=& \varPhi + \log C \\
@@
 + 2\log\pars{1-\tanh^2\frac{\zeta}{4}} \cdot \bnabla_\mathcal{S} \log C.
-\end{eqnarray}
+\end{eqnarray*}
 where $\zeta = \cV - \varPhi = \log (C / \gamma)$ 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Algorithm Description} \label{algorithm}
+\section{Algorithm Description} \label{sec:algorithm}
 The numerical solver starts by constructing a discrete approximation for the nonlinear system,
@@
 \subsubsection{Spherical Coordinates}
-Because the system is axisymmetric, the operators are written in 
-spherical coordinates $(r,\theta,\phi)$ 
-using the derivation at \ref{append:spherical}.
+Since the system is axisymmetric, the operators are written in 
+spherical coordinates $(r,\theta,\phi)$.
 The scalar gradient and the divergence can be written as:
@@
 the vector Laplacian operator cannot be computed as in the Cartesian system,
-since the unit vectors $\brhat, \bthetahat, \bphihat$ are functions of the coordinates.
+since the unit vectors $\brhat, \bthetahat, \bphihat$ are functions of the coordinates
+in a curvilinear coordinate system.
 
@@
 
-The problem can be cast as the following non-linear system:
+The problem can be cast as the following non-linear system (where $\cO = \cE \circ \cB$):
 \begin{eqnarray*}
-\bzero = \cE (\tilde{\bx}) = \cE (\cB (\bx)) = \cO(\bx),
+\cO(\bx) = \bzero.
 \end{eqnarray*}
- where $\cO = \cE \circ \cB$.
 
@@
 
-However, it is no longer true for $\beta \sim O(1)$, since the nonlinear terms become dominant
+However, it is no longer true for $\beta \sim O(1)$, since the non-linear terms become dominant
 and the iterative solver may not converge at all.
@@
 \begin{eqnarray*}
-(\cO_1 \pm \cO_2)(\bx) &=& \cO_1)(\bx) \pm \cO_2(\bx), \\
+(\cO_1 \pm \cO_2)(\bx) &=& \cO_1(\bx) \pm \cO_2(\bx), \\
 \bnabla (\cO_1 \pm \cO_2)(\bx)   &=& \bnabla\cO_1(\bx) \pm \bnabla\cO_2(\bx), \\
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Numerical Results} \label{sec:results}
+The numerical solver is applied to the non-linear problem of the migration ion-exchanger
+driven by an electric field (as described in \cite{yariv2010migration}).
+
+The computational grid for the problem is chosen to be of the size $400 \times 50$.
+Since there are five variables ($\varPhi, C, V_r, V_\theta, P$), the concatenated
+variable $\bx$ has dimension of $\sim 10^5$.
+$R_{\max}$ is chosen to be $10^{7}$ so truncation effect should be negligible.
+
+The solver is applied to a series of values of $\beta$, from $\beta \ll 1$ up to $\beta \sim O(1)$.
+For each $\beta$ value, the steady-state velocity $\cU(\beta)$ is computed. The solver
+is applied to various values of $\gamma$.
+
+For $\beta \ll 1$, the linear regime takes place:
+\begin{eqnarray*}
+\cU = 2\log\pars{\frac{1 + \gamma^{-\frac{1}{2}}}{2}}\beta.
+\end{eqnarray*}
+
+If $\gamma \approx 1$, the the non-linear regime, where $\cU \approx 0.042 \beta^3$ takes place 
+for weak electric fields. This phenomenon is confirmed both by the numerical
+results and by asymptotic expansion of the non-linear system.
+For $\alpha=0$, the switch from the linear regime to the cubic one happens at:
+\begin{eqnarray*}
+\beta_c & \approx & 3.45 \sqrt{|\gamma - 1|}
+\end{eqnarray*}
+as described in \ref{sec:asymp}.
+The numerical results as well as the analytical ones are given in Figures 
+\ref{fig:NumResA} and \ref{fig:NumResB}.
+Good correspondence between the numerical results and the analytical expression is achieved.
+
+When $\beta > 4/3 |\log \gamma|$, the zeta potential $\zeta = -\log \gamma - \varPhi$ 
+changes sign on the surface of the ion-exchanger. The slipping velocity changes signs
+as well, causing a vortex at the downstream part of the sphere.
+The numerical results as well as the analytical ones are given in Figures 
+\ref{fig:NumResC}, \ref{fig:NumResD} and \ref{fig:NumResE}.
+Good correspondence between the numerical results and the analytical expression is achieved.
+
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=0.7\textwidth]{figs/A2.eps}
+        \includegraphics[width=0.7\textwidth]{figs/A4.eps}
+        \caption{Steady-state velocity $\cU$ as a function of the electric field magnitude $\beta$, 
+        for $\gamma > 1$.}
+        \label{fig:NumResA}
+    \end{center}
+\end{figure}
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=0.7\textwidth]{figs/B2.eps}
+        \includegraphics[width=0.7\textwidth]{figs/B4.eps}
+        \caption{Steady-state velocity $\cU$ as a function of the electric field magnitude $\beta$,
+        for $\gamma < 1$.}
+        \label{fig:NumResB}
+    \end{center}
+\end{figure}
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=0.7\textwidth]{figs/D1n.eps}
+        \includegraphics[width=0.7\textwidth]{figs/D1a.eps}
+        \caption{Streamlines of the flow for various electric field values: numerical results (left)
+        and analytical approximation (right).}
+        \label{fig:NumResC}
+    \end{center}
+\end{figure}
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=0.7\textwidth]{figs/D2n.eps}
+        \includegraphics[width=0.7\textwidth]{figs/D2a.eps}
+        \caption{Streamlines of the flow for various electric field values: numerical results (left)
+        and analytical approximation (right).}
+        \label{fig:NumResD}
+    \end{center}
+\end{figure}
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=0.7\textwidth]{figs/D3n.eps}
+        \includegraphics[width=0.7\textwidth]{figs/D3a.eps}
+        \caption{Streamlines of the flow for various electric field values: numerical results (left)
+        and analytical approximation (right).}
+        \label{fig:NumResE}
+    \end{center}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Discussion and Future Work} \label{sec:discussion}
+
+\begin{appendix}
+\section{Asymptotic Analysis} \label{sec:asymp}
+The non-linear system is defined by the following PDEs:
+\label{PDEs}
+\begin{eqnarray*}
+\bnabla \cdot \pars{C \bnabla \varPhi} &=& 0, \\
+\bnabla \cdot \pars{\bnabla C - \alpha \bV C} &=& 0, \\
+\bLaplacian \bV - \bnabla P + \Laplacian \varPhi \bnabla \varPhi &=& \bzero.
+\end{eqnarray*}
+
+For $\zeta(\theta) = \cV - \varPhi(1, \theta)$ and 
+$\cV = -\log \gamma$, the boundary conditions on $r = 1$ are:
+\begin{eqnarray*}
+\varPhi + \log C &=& \cV + \log \gamma = 0, \\
+\deriv{}{r}\pars{\varPhi - \log C} &=& \frac{J_-}{C} = 0, \\
+\bV = \zeta \cdot \bnabla_\mathcal{S} \varPhi 
++ 2\log\pars{1-\tanh^2\frac{\zeta}{4}} \cdot \bnabla_\mathcal{S} \log C
+&=& 4\log\pars{\frac{1 + e^\frac{\zeta}{2}}{2}} \bnabla_S \varPhi.
+\end{eqnarray*}
+
+The boundary conditions for $r \rightarrow \infty$ are:
+\begin{eqnarray*}
+\bnabla \varPhi &=& -\beta \ui, \\
+C &=& 1, \\
+\bV &=& -\cU \ui,
+\end{eqnarray*}
+and the total force acting on the particle is zero: $\bF = \bzero$.
+
+The nonlinear system can be written as: 
+\begin{eqnarray*}
+\cO(\bx;\beta) &=& \bzero.
+\end{eqnarray*}
+
+The solution to the non-linear system can be written as a Taylor series in $\beta$.
+\begin{eqnarray*}
+\bx = \bx(\beta) &\approx& \sum_n \bx_n \beta^n.
+\end{eqnarray*}
+
+All the variables are expanded around $\beta = 0$:
+\begin{eqnarray*}
+\varPhi &=& \beta \varPhi_1 + \beta^2 \varPhi_2 + \beta^3 \varPhi_3 + \ldots, \\
+C &=& 1 + \beta C_1 + \beta^2 C_2 + \beta^3 C_3 + \ldots, \\
+\Psi &=& \beta \Psi_1 + \beta^2 \Psi_2 + \beta^3 \Psi_3 + \ldots ,
+\end{eqnarray*}
+where the velocity $\bV$ and pressure $P$ are computed from the streamfunction $\Psi$:
+\begin{eqnarray*}
+\bV &=& \bnabla \times \pars{\frac{\Psi}{r \sin\theta} \bphihat} 
+= \frac{1}{r^2 \sin\theta} \deriv{\Psi}{\theta} \brhat 
+- \frac{1}{r \sin\theta} \deriv{\Psi}{r} \bthetahat.
+\end{eqnarray*}
+
+The nonlinear equations and the boundary conditions are expanded around $\beta = 0$
+and arranged by powers of $\beta$:
+\begin{eqnarray*}
+\bzero = \cO(\bx) = \sum_k \cO_k(\bx_0, \ldots \bx_k) \beta^k
+\end{eqnarray*}
+This can be rewritten as a system of equations:
+\begin{eqnarray*}
+\brc{rcl}{
+\bzero &=& \cO_0(\bx_0), \\
+\bzero &=& \cO_1(\bx_0, \bx_1), \\
+\bzero &=& \cO_2(\bx_0, \bx_1, \bx_2), \\
+& \vdots & \\
+\bzero &=& \cO_k(\bx_0, \bx_1, \bx_2, \ldots \bx_k).
+}
+\end{eqnarray*}
+Thus, the $O(\beta^k)$ term $\bx_k$ can be found recursively by solving 
+$\cO_k(\bx_0, \bx_1, \ldots, \bx_k) = \bzero$,
+given the previous solutions for $\bx_0, \ldots, \bx_{k-1}$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Linear Solution $(k=1)$}
+
+For $\beta = 0$ (no electric field is applied), the steady-state solution is $\cU = 0$:
+\begin{eqnarray*}
+\varPhi_0(r,\theta) &=& 0, \\
+C_0(r,\theta) &=& 1, \\
+\bV_0(r,\theta) &=& \bzero, \\
+P_0(r,\theta) &=& 0.
+\end{eqnarray*}
+
+Assuming $\beta \ll 1$, the linearized equations and boundary conditions are 
+(as developed in \cite{yariv2010migration}):
+\begin{eqnarray*}
+\Laplacian \varPhi_1 &=& 0, \\
+\Laplacian C_1 &=& 0, \\
+\bLaplacian \bV_1 - \bnabla P_1 &=& \bzero.
+\end{eqnarray*}
+
+The first order terms are:
+\begin{eqnarray*}
+\varPhi &=& \beta \pars{\frac{1}{4r^2} - r}\cos\theta, \\
+C &=& 1 + \beta \frac{3}{4r^2} \cos\theta, \\
+\Psi &=& \beta \cU_1 \pars{\frac{1}{r} - r^2} \frac{\sin^2\theta}{2}, \\
+\bV &=& -\beta \cU_1 \brcs{\pars{1 - \frac{1}{r^3}}\cos\theta \cdot \brhat - 
+                               \pars{1 + \frac{1}{2r^3}} \sin\theta \cdot \bthetahat}, \\
+P &=& 0, \\
+\bF &=& \bzero.
+\end{eqnarray*}
+
+The slip velocity satisfies:
+\begin{eqnarray*}
+\beta \cU_1 \frac{3}{2} \sin\theta =
+V_\theta &=& 4 \log \pars{\frac{1 + e ^ \frac{\zeta}{2}}{2}} \deriv{\varPhi}{\theta} 
+=
+ 3 \beta \log \pars{\frac{1 + e ^ \frac{\zeta}{2}}{2}} \sin\theta, \\
+\cU_1 &=& 2 \log \pars{\frac{1 + e ^ \frac{\zeta}{2}}{2}} 
+       =  2 \log \pars{\frac{1 + \gamma ^ {-\frac{1}{2}}}{2}}.
+\end{eqnarray*}
+because $\varPhi_1 = -C_1 = -\frac{3}{4} \cos\theta$ on $r=1$
+and $\zeta_0 = -\log\gamma$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Nonlinear Solution ($k > 1$)}
+Note that, due to symmetry considerations, $\cU(\beta)$ is an anti-symmetric function:
+\begin{eqnarray*}
+\cU(-\beta) &=& -\cU(\beta).
+\end{eqnarray*}
+Therefore, $\cU_2 = 0$ and the next velocity term is the cubic one:
+\begin{eqnarray*}
+\cU(\beta) &\approx& \beta \cU_1 + \beta^3 \cU_3 + O(\beta^5)
+\end{eqnarray*}
+
+In order to find the cubic terms, the quadratic term should be found first.
+
+The quadratic terms $\bx_2$ are computed by solving a linear PDE system 
+with a right-hand side determined by the linear terms $\bx_1$:
+\begin{eqnarray*}
+\varPhi_2 &=& \frac{\left(\frac{\cU_1\, \alpha}{32} - \frac{1}{16}\right)\, \left(3\, {\cos^2\theta} - 1\right)}{r^3} - \frac{3}{32\, r^4} - \frac{3\, {\sin^2\theta}\, \left(4\, r^3 - 1\right)}{32\, r^4} - \frac{3\, \cU_1\, \alpha - 6}{32\, r},
+\\
+C_2 &=& \frac{\left(\frac{5\, \cU_1\, \alpha}{32} + \frac{1}{16}\right)\, \left(3\, {\cos^2\theta} - 1\right)}{r^3} - \frac{3\, \cU_1\, \alpha - 6}{32\, r} + \frac{3\, \cU_1\, \alpha\, \left(2\, r^3\, {\sin^2\theta} + {\sin^2\theta} - 1\right)}{16\, r^4},
+\\
+\Psi_2 &=& \pars{\frac{9}{16(\sqrt{\gamma}+1)} - \frac{3}{16} \cU_1 (\cU_1 \alpha + 1)}
+ \left(\frac{1}{r^2} - 1\right) \sin^2\theta \cos\theta,  \\
+\bF_2 &=& \bzero, \\ \cU_2 &=& 0.
+\end{eqnarray*}
+Note that the quadratic term does not contribute to the total force and steady-state 
+velocity terms, but it does change the fluid flow, 
+the electric potential and the ionic concentration.
+
+The cubic terms $\bx_3$ are computed by solving a linear PDE system 
+with a right-hand side determined by the linear terms $\bx_1$ and the quadratic terms $\bx_2$:
+\begin{eqnarray*}
+\varPhi_3 &=& \cos\theta \left(\frac{15 \cU_1\alpha}{64} + \frac{3}{32}\right) - \frac{3 \cU_1\alpha {\cos}^3\theta}{32} - \frac{\cos\theta \left( - 183 {\cU_1}^2\alpha^2 + 839 \cU_1\alpha + 470\right)}{2560 r^2} \\
+&&+ \frac{3 \cos\theta \left(5 \cU_1\alpha - 6 {\cos^2\theta} - 4 \cU_1\alpha {\cos^2\theta} + 4\right)}{64 r^3} + \frac{\left(2 \cU_1\alpha - 1\right) \left(\cos\theta - 3 {\cos}^3\theta\right)}{64 r^5}
+\\ 
+&&- \frac{\left(3 \cos\theta - 5 {\cos}^3\theta\right) \left( - \frac{19 {\cU_1}^2\alpha^2}{5120} + \frac{97 \cU_1\alpha}{5120} + \frac{3 \cU_2\alpha}{320} + \frac{21}{1280}\right)}{r^4} + \frac{{\cos}^3\theta \left(\frac{15 \cU_1\alpha}{64} + \frac{3}{32}\right)}{r^2} \\
+&&+ \frac{{\cos}^3\theta \left(\frac{\cU_1\alpha}{64} + \frac{3}{64}\right)}{r^6},
+\\
+C_3 &=&
+\frac{3 {{\cU_1}}^2\alpha^2 {\cos^3\theta}}{32} + \frac{\cos\theta \left(797 {{\cU_1}}^2\alpha^2 + 419 {\cU_1}\alpha - 512 {\cU_2}\alpha + 174\right)}{2560 r^2} \\
+&&- \frac{\left(3 \cos\theta - 5 {\cos^3\theta}\right) \left(\frac{59 {{\cU_1}}^2\alpha^2}{5120} + \frac{103 {\cU_1}\alpha}{5120} + \frac{69 {\cU_2}\alpha}{320} + \frac{3}{1280}\right)}{r^4} \\
+&&- \frac{3\alpha \cos\theta \left( - 8\alpha {{\cU_1}}^2 {\cos^2\theta} + 7\alpha {{\cU_1}}^2 + 2 {\cU_1} + 32 {\cU_2} {\cos^2\theta} - 32 {\cU_2}\right)}{128 r^3} - \frac{3 {\cU_1}\alpha \cos\theta \left(5 {\cU_1}\alpha + 2\right)}{64} \\
+&&+ \frac{\alpha \left(\cos\theta - 3 {\cos^3\theta}\right) \left(5\alpha {{\cU_1}}^2 + 2 {\cU_1} + 16 {\cU_2}\right)}{128 r^5} + \frac{{{\cU_1}}^2\alpha^2 {\cos^3\theta}}{32 r^6} - \frac{3 {\cU_1}\alpha {\cos^3\theta} \left(5 {\cU_1}\alpha + 2\right)}{64 r^2},
+\\
+\Psi_3 &=&
+r^2 {\sin^2\theta} \left(\frac{{\cW_2}}{15} - \frac{{\cW_1}}{3} + \frac{209}{3360}\right) 
+ - \frac{{\sin^2\theta} \left(\frac{5 {\cW_2}}{3} - \frac{{\cW_1}}{3} + \frac{35}{264}\right)}{r}
+\\ && + \frac{{\sin^4\theta} \left(2 {\cW_2} + \frac{761}{5632}\right)}{r} - \frac{{\sin^2\theta} \left(1848 r^6 {\sin^2\theta} - 2079 r^3 {\sin^2\theta} + 924 r^3 - 7 {\sin^2\theta} + 10\right)}{19712 r^5}
+\\ && + \frac{\left(\frac{2 {\cW_2}}{5} + \frac{829}{28160}\right) \left(4 {\sin^2\theta} - 5 {\sin\theta}^4\right)}{r^3} + \frac{{\sin^2\theta} \left(\frac{{\cU_1}\alpha}{16} - \frac{1}{8}\right) \left(2 r^3 - 3 r^2 + 1\right)}{4 r},
+\\
+\cW_1 &=& \frac{69}{512 \left(\sqrt{\gamma} + 1\right)} - \frac{1407\alpha^2 {\log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}^3}{1280} - \frac{123 \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{1280} - \frac{27}{512 {\left(\sqrt{\gamma} + 1\right)}^2} \\ && -
+\frac{1899\alpha {\log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}^2}{2560} - \frac{\alpha \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right) \left(\frac{81}{16 \left(\sqrt{\gamma} + 1\right)} - \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right) \left(\frac{27\alpha \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{4} + \frac{27}{8}\right)\right)}{320} \\ && +
+\frac{21\alpha \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{128 \left(\sqrt{\gamma} + 1\right)},
+\\
+\cW_2 &=& \frac{9 \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{256} + \frac{21\alpha^2 {\log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}^3}{64} - \frac{27}{512 \left(\sqrt{\gamma} + 1\right)} - \frac{27}{512 {\left(\sqrt{\gamma} + 1\right)}^2}
+ + \frac{15\alpha {\log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}^2}{64} 
+\\ && 
+- \frac{297\alpha \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{1024 \left(\sqrt{\gamma} + 1\right)}.
+\end{eqnarray*}
+
+The cubic solution satisfies the $\lim_{r\rightarrow\infty}C_3 = 0$ boundary condition, 
+when $\alpha\cU_1 = 0$.
+
+The steady-state velocity can be expanded using odd powers of $\beta$:
+\begin{eqnarray*}
+\cU(\beta, \gamma) &=& \cU_1(\gamma) \beta + \cU_3(\gamma) \beta^3.
+\end{eqnarray*}
+
+The linear and the cubic velocity terms (for $\alpha = 0$) are:
+\begin{eqnarray*}
+\cU_1(\gamma) &=& 2 \log \pars{\frac{1 + \gamma^{-\frac{1}{2}}}{2}}, \\
+\cU_3(\gamma) &=& \frac{31}{320(\sqrt\gamma + 1)} - \frac{9}{320(\sqrt\gamma + 1)^2} + \frac{1}{1680} - \frac{11}{160} \log \pars{\frac{1 + \gamma^{-\frac{1}{2}}}{2}}.
+\end{eqnarray*}
+
+Note that, for $\gamma = 1$, the linear term vanishes and the velocity leading term is $O(\beta^3)$:
+\begin{eqnarray*}
+\cU(\beta) = \frac{1129}{26880}\beta^3.
+\end{eqnarray*}
+
+Note that a $\cU = 0$ solution may exist for $\beta_c \ne 0$ and $\alpha = 0$, 
+if it satisfies:
+\begin{eqnarray*}
+\beta_c^2 = -\frac{\cU_1(\gamma)}{\cU_3(\gamma)}.
+\end{eqnarray*}
+For $\gamma = 1 + \eps$, where $0 < \eps \ll 1$:
+\begin{eqnarray*}
+\beta_c \approx \sqrt{-\frac{\cU_1'(1) \eps}{\cU_3(1)}} = 
+ \sqrt{\frac{13440 \eps}{1129}} \approx 3.45 \sqrt{\eps}.
+\end{eqnarray*}
+However, for $\gamma \gg 1$, we have:
+\begin{eqnarray*}
+\beta_c =  \pars{\frac{11}{320} + \frac{1}{1680 \log 4}}^{-\frac{1}{2}} \approx 5.36.
+\end{eqnarray*}
+
+The cubic term becomes dominant for small $\beta$ when $\gamma \approx 1$.
+
+\end{appendix}
+
 \bibliographystyle{elsarticle-num}

### 2012-03-19 notes/article/main.tex
Work on paper.

@@
 The partial differential equations that describe the system dynamics
-under an external electric field, are coupled and non-linear, and
+under an external electric field, are coupled and nonlinear, and
 in general, they have no analytic solution. 
@@
 so the concatenated equations of the system (as described above) can be written 
-as a non-linear operator $\cE(\tilde\bx) = \bzero$ acting on the extended system variable 
+as a nonlinear operator $\cE(\tilde\bx) = \bzero$ acting on the extended system variable 
 $\tilde{\bx}$, where $\cE$ is the conservation equations operator 
@@
 
-The problem can be cast as the following non-linear system (where $\cO = \cE \circ \cB$):
+The problem can be cast as the following nonlinear system (where $\cO = \cE \circ \cB$):
 \begin{eqnarray*}
@@
 
-However, it is no longer true for $\beta \sim O(1)$, since the non-linear terms become dominant
+However, it is no longer true for $\beta \sim O(1)$, since the nonlinear terms become dominant
 and the iterative solver may not converge at all.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Numerical Results} \label{sec:results}
-The numerical solver is applied to the non-linear problem of the migration ion-exchanger
+\section{Numerical Results and Discussion} \label{sec:results}
+The numerical solver is applied to the nonlinear problem of the migration ion-exchanger
 driven by an electric field (as described in \cite{yariv2010migration}).
@@
 The computational grid for the problem is chosen to be of the size $400 \times 50$.
+
 Since there are five variables ($\varPhi, C, V_r, V_\theta, P$), the concatenated
 variable $\bx$ has dimension of $\sim 10^5$.
+
 $R_{\max}$ is chosen to be $10^{7}$ so truncation effect should be negligible.
@@
 For each $\beta$ value, the steady-state velocity $\cU(\beta)$ is computed. The solver
-is applied to various values of $\gamma$.
-
+is applied to various values of $\gamma$, representing various ion-exchangers.
+
+The resulting $\cU(\beta)$ is plotted using a log-log graph, so the asymptotic behaviour
+of the solution could be examined for a wide range of $\beta$ values.
+
+In order to validate the numerical solver, an asymptotic analysis of the nonlinear system
+is performed as described in \ref{sec:asymp}. The numerical results are compared to 
+to the asymptotic solutions, and good correspondence is achieved.
+
+\subsection{Linear Regime}
 For $\beta \ll 1$, the linear regime takes place:
@@
 \end{eqnarray*}
-
-If $\gamma \approx 1$, the the non-linear regime, where $\cU \approx 0.042 \beta^3$ takes place 
-for weak electric fields. This phenomenon is confirmed both by the numerical
-results and by asymptotic expansion of the non-linear system.
-For $\alpha=0$, the switch from the linear regime to the cubic one happens at:
-\begin{eqnarray*}
-\beta_c & \approx & 3.45 \sqrt{|\gamma - 1|}
-\end{eqnarray*}
-as described in \ref{sec:asymp}.
-The numerical results as well as the analytical ones are given in Figures 
-\ref{fig:NumResA} and \ref{fig:NumResB}.
-Good correspondence between the numerical results and the analytical expression is achieved.
-
-When $\beta > 4/3 |\log \gamma|$, the zeta potential $\zeta = -\log \gamma - \varPhi$ 
-changes sign on the surface of the ion-exchanger. The slipping velocity changes signs
-as well, causing a vortex at the downstream part of the sphere.
-The numerical results as well as the analytical ones are given in Figures 
-\ref{fig:NumResC}, \ref{fig:NumResD} and \ref{fig:NumResE}.
-Good correspondence between the numerical results and the analytical expression is achieved.
+Thus, for $\gamma > 1$, the Debye layer has positive space charge, corresponding to a negative
+particle charge -- yielding negative drift velocity, $\cU < 0$. 
+For $\gamma < 1$, we have $\cU > 0$, respectively.
+
+The linear regime is simulated for $\gamma > 1$ (at Figure \ref{Linear1})  
+and for $\gamma < 1$ (at Figure \ref{Linear2}).
+
+\subsection{Cubic Regime}
+When $\gamma \approx 1$, the cubic regime, $\cU = O(\beta^3)$, 
+dominates the linear one, even for weak electric fields.
+
+This phenomenon is confirmed both by the numerical
+results and by asymptotic expansion of the nonlinear system (for $\alpha=0$).
+The switch from the linear regime to the cubic one happens at a critical electric
+field value $\beta_c = O(\sqrt{|\gamma - 1|})$.
+
+The numerical results, as well as the analytical ones, are given at Figure
+\ref{} (for $\gamma > 1$) and at Figure \ref{} (for $\gamma < 1$).
+Since log-log scale is employed, positive and negative velocities are shown in
+the same plot using different markers and line styles.
+
+\subsection{Vortices}
+The linear solution for $\gamma \approx 1$, 
+yields a sign change in the zeta potential $\zeta = \log (C/\gamma)$, when
+$|\log\gamma| \approx 3\beta / 4$. This results in a sign change in the slip velocity,
+which can be approximated for small $|\zeta| \ll 1$ as:
+\begin{eqnarray*}
+V_\theta \approx \zeta \cdot \bnabla_S \varPhi.
+\end{eqnarray*} 
+This sign change creates a vortex at the downstream part of the ion-exchanger, 
+as demonstrated by the numerical simulation and the asymptotic analysis results 
+in Figure \ref{}.
+
+%        \includegraphics[width=0.7\textwidth]{figs}
 
@@
     \begin{center}
-        \includegraphics[width=0.7\textwidth]{figs/A2.eps}
-        \includegraphics[width=0.7\textwidth]{figs/A4.eps}
-        \caption{Steady-state velocity $\cU$ as a function of the electric field magnitude $\beta$, 
-        for $\gamma > 1$.}
-        \label{fig:NumResA}
+    \includegraphics[width=0.45\textwidth]{figs/Linear/g=2.00.eps}
+    \includegraphics[width=0.45\textwidth]{figs/Linear/g=5.00.eps}
+    \includegraphics[width=0.45\textwidth]{figs/Linear/g=10.00.eps}
+    \includegraphics[width=0.45\textwidth]{figs/Linear/g=100.00.eps}
+    \caption{Steady-state velocity $\cU$ as a function of the 
+        electric field magnitude $\beta$, for $\gamma > 1$. 
+        The analytic solution velocity is represented by dashed lines, and the numerical
+        results are represented by squares.}
+    \label{Linear1}
     \end{center}
+\end{figure}
+
+\begin{figure}[htbp]
+    \begin{center}
+    \includegraphics[width=0.45\textwidth]{figs/Linear/g=0.50.eps}
+    \includegraphics[width=0.45\textwidth]{figs/Linear/g=0.20.eps}
+    \includegraphics[width=0.45\textwidth]{figs/Linear/g=0.10.eps}
+    \includegraphics[width=0.45\textwidth]{figs/Linear/g=0.01.eps}
+    \caption{Steady-state velocity $\cU$ as a function of the 
+        electric field magnitude $\beta$, for $\gamma < 1$. 
+        The analytic solution velocity is represented by solid lines, and the numerical
+        results are represented by circles.}
+    \label{Linear2}
+    \end{center}
+\end{figure}
+
+\begin{figure}[htbp]
+    \begin{center}
+    \includegraphics[width=0.45\textwidth]{figs/Cubic/g=0.999900.eps}
+    \includegraphics[width=0.45\textwidth]{figs/Cubic/g=0.999000.eps}
+    \includegraphics[width=0.45\textwidth]{figs/Cubic/g=0.990000.eps}
+    \includegraphics[width=0.45\textwidth]{figs/Cubic/g=0.900000.eps}
+        \caption{Steady-state velocity $\cU$ as a function of the 
+        electric field magnitude $\beta$, for $\gamma < 1$. 
+        The analytic solution velocity is represented by solid lines, 
+        and the numerical results are represented by square markers.}
+    \end{center}
+    \label{fig:Cubic1}
 \end{figure}
@@
     \begin{center}
-        \includegraphics[width=0.7\textwidth]{figs/B2.eps}
-        \includegraphics[width=0.7\textwidth]{figs/B4.eps}
-        \caption{Steady-state velocity $\cU$ as a function of the electric field magnitude $\beta$,
-        for $\gamma < 1$.}
-        \label{fig:NumResB}
+    \includegraphics[width=0.45\textwidth]{figs/Cubic/g=1.000100.eps}
+    \includegraphics[width=0.45\textwidth]{figs/Cubic/g=1.001000.eps}
+    \includegraphics[width=0.45\textwidth]{figs/Cubic/g=1.010000.eps}
+    \includegraphics[width=0.45\textwidth]{figs/Cubic/g=1.100000.eps}
+        \caption{Steady-state velocity $\cU$ as a function of the 
+        electric field magnitude $\beta$, for $\gamma < 1$. 
+        The analytic solution velocity is represented by lines 
+        (solid lines for $\cU > 0$, dashed lines for $\cU < 0$), 
+        and the numerical results are represented by markers 
+        (squares for $\cU > 0$, circles for $\cU < 0$).}
     \end{center}
+    \label{fig:Cubic2}
 \end{figure}
@@
     \begin{center}
-        \includegraphics[width=0.7\textwidth]{figs/D1n.eps}
-        \includegraphics[width=0.7\textwidth]{figs/D1a.eps}
-        \caption{Streamlines of the flow for various electric field values: numerical results (left)
-        and analytical approximation (right).}
-        \label{fig:NumResC}
+	\includegraphics[width=0.45\textwidth]{figs/Stream/N0.01.eps}
+	\includegraphics[width=0.45\textwidth]{figs/Stream/A0.01.eps}
+	\includegraphics[width=0.45\textwidth]{figs/Stream/N0.02.eps}
+	\includegraphics[width=0.45\textwidth]{figs/Stream/A0.02.eps}
+	\includegraphics[width=0.45\textwidth]{figs/Stream/N0.04.eps}
+	\includegraphics[width=0.45\textwidth]{figs/Stream/A0.04.eps}
+	\includegraphics[width=0.45\textwidth]{figs/Stream/N0.08.eps}
+	\includegraphics[width=0.45\textwidth]{figs/Stream/A0.08.eps}
+        \caption{Streamlines of the flow for various electric field $\beta$ values: 
+        numerical results (left) and analytical approximation (right) for 
+        $\gamma = 0.99$.  The steady-state velocity $\cU$ is positive, so the
+        ion-exchanger drifts to the right.}
     \end{center}
+    \label{fig:Vortex}
 \end{figure}
-\begin{figure}[htbp]
-    \begin{center}
-        \includegraphics[width=0.7\textwidth]{figs/D2n.eps}
-        \includegraphics[width=0.7\textwidth]{figs/D2a.eps}
-        \caption{Streamlines of the flow for various electric field values: numerical results (left)
-        and analytical approximation (right).}
-        \label{fig:NumResD}
-    \end{center}
-\end{figure}
-\begin{figure}[htbp]
-    \begin{center}
-        \includegraphics[width=0.7\textwidth]{figs/D3n.eps}
-        \includegraphics[width=0.7\textwidth]{figs/D3a.eps}
-        \caption{Streamlines of the flow for various electric field values: numerical results (left)
-        and analytical approximation (right).}
-        \label{fig:NumResE}
-    \end{center}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion and Future Work} \label{sec:discussion}
 
@@
 \section{Asymptotic Analysis} \label{sec:asymp}
-The non-linear system is defined by the following PDEs:
+The nonlinear system is defined by the following PDEs:
 \label{PDEs}
@@
 
-The solution to the non-linear system can be written as a Taylor series in $\beta$.
+The solution to the nonlinear system can be written as a Taylor series in $\beta$.
 \begin{eqnarray*}

### 2012-03-19 src/show.m

@@ -1,35 +1,53 @@
-function show(name)
-    disp(name)
+function show(name, first)
+    if nargin < 2
+        first = 1;
+    end
     load(name);
     figure(1); clf;
-%     set(gcf, 'PaperPositionMode', 'auto');
-%     set(gcf, 'Position',[100 100 900 600]);
-    v = attr(solutions, 'Vinf');
-    betas = attr(solutions, 'beta');
+    set(gcf, 'PaperPositionMode', 'auto');
+    set(gcf, 'Position',[100 100 600 800]);
+    try
+        v = attr(solutions, 'Vinf');
+        betas = attr(solutions, 'beta');
+    catch err
+        disp(err)
+        return
+    end
+    disp(name)
 
     g = sol.gamma;
     B3 = (31./(320*(g.^(1./2) + 1)) - 9./(320*(g.^(1./2) + 1).^2) + 1./1680);
     B1 = 2*log(1./(2*g.^(1./2)) + 1./2);
     b = logspace(log10(min(betas)), log10(max(betas)), 1000);
-    w = b.^3*(B3 - B1*11./320) + b*B1;
+    a = sol.alpha;
+    w = (248./(2560.*g.^(1./2) + 2560) - 9./(320.*(g.^(1./2) + 1).^2) - (a.*log(1./(2.*g.^(1./2)) + 1./2))./8 - (11.*log((g.^(1./2) + 1)./(2.*g.^(1./2))))./160 - (61.*a.^2.*log((g.^(1./2) + 1)./(2.*g.^(1./2))).*log(1./(2.*g.^(1./2)) + 1./2).^2)./80 - (83.*a.*log((g.^(1./2) + 1)./(2.*g.^(1./2))).*log(1./(2.*g.^(1./2)) + 1./2))./160 + (176.*a.*log(1./(2.*g.^(1./2)) + 1./2))./(1280.*g.^(1./2) + 1280) + 1./1680).*b.^3 + 2.*log(1./(2.*g.^(1./2)) + 1./2).*b;
     w3 = b.^3*(B3 - B1*11./320);
     w1 = b*B1;
     clf; 
-    h = [];
-    h = [h; graph(betas, v, '.')]; hold on; 
-    h = [h; graph(b, w1+w3, '-')]; 
-    graph(b, w1, ':'); 
-    graph(b, w3, ':'); 
[…]

### 2012-03-19 src/solver.m

@@ -5,29 +5,31 @@
 function solver
     tic;
     clc;
-    filename = datestr(now, 'YYYYmmmdd-HHMMSS');
-    sol = struct( ...
+    filename = datestr(now, 'YYYYmmmdd_HHMMSS');
+    sol0 = struct( ...
         'radius', logspace(0, 7, 400), ...
         'theta', linspace(0, pi, 50), ...
-        'gamma', 1, ...
+        'gamma', 0.01, ...
         'maxres', 1e-11, ...
         'iters', [2 5] ...    
     );
-    betas = 10.^([-2:0.1:1]);
-    sol = force(sol); % initialize force solver
-    sol.Vinf = 0.1;
+    betas = 10.^fliplr(-5:0.5:-1);
+    sol0 = force(sol0); % initialize force solver
+    sol0.Vinf = 1;
     solutions = cell(numel(betas), 1);
-    alphas = [0];
+    alphas = [0, 0.5];
+    
     for k = 1:numel(betas)
+        sol = sol0;
         sol.beta = betas(k);
         for a = alphas
             sol.alpha = a;
-            [sol, V, F] = steady(sol, sol.Vinf*(1+[-0.1, 0.1]), 5);
+            [sol, V, F] = steady(sol, sol.Vinf*(1+[0, 0.1]), 5);
             sol.Vinf = V(end);
         end
         solutions{k} = sol;
         pause(0);
-        pynotify('CEK', sprintf('%.1f%% completed.', 100*k/numel(betas)));
+%         pynotify('CEK', sprintf('%.1f%% completed.', 100*k/numel(betas)));
     end
     save(filename)
     show(filename)

### 2012-03-19 symbolic/asymp.m

@@ -151,3 +151,4 @@ function assert_zero(e, msg)
     end
 end
 
+% inline(vectorize(char

### 2012-03-19 notes/article/main.tex
Work on LaTeX.

@@
 
-%\usepackage{setspace}\doublespacing
+\usepackage{setspace}\doublespacing
 
@@
 \usepackage{framed}
+\usepackage{url}
 
@@
 
-The goal of this work is to implement an accurate and fast iterative numerical
+The goal of this work is to implement an iterative numerical
 solver for nonlinear electrokinetic problems, and apply it to the study
@@
 and high-level language features.
+The source code of solver can be found at \cite{source}.
 
@@
 In order to validate the numerical solver, an asymptotic analysis of the nonlinear system
-is performed as described in \ref{sec:asymp}. The numerical results are compared to 
+is performed as described in \ref{app:asymp}. The numerical results are compared to 
 to the asymptotic solutions, and good correspondence is achieved.
@@
 \subsection{Linear Regime}
-For $\beta \ll 1$, the linear regime takes place:
+For $\beta \ll 1$, the linear regime takes place (for derivation, see \ref{app:linear}):
 \begin{eqnarray*}
@@
 
-The linear regime is simulated for $\gamma > 1$ (at Figure \ref{Linear1})  
-and for $\gamma < 1$ (at Figure \ref{Linear2}).
+The linear regime is simulated for $\gamma > 1$ (at Figure \ref{fig:Linear1})  
+and for $\gamma < 1$ (at Figure \ref{fig:Linear2}).
 
 \subsection{Cubic Regime}
-When $\gamma \approx 1$, the cubic regime, $\cU = O(\beta^3)$, 
+When $\gamma \approx 1$, the cubic regime  (for derivation, see \ref{app:cubic}), where
+\begin{eqnarray*}
+\cU = O(\beta^3), 
+\end{eqnarray*}
 dominates the linear one, even for weak electric fields.
@@
 The switch from the linear regime to the cubic one happens at a critical electric
-field value $\beta_c = O(\sqrt{|\gamma - 1|})$.
+field value
+\begin{eqnarray*}
+\beta_c = O(\sqrt{|\gamma - 1|}).
+\end{eqnarray*}
 
 The numerical results, as well as the analytical ones, are given at Figure
-\ref{} (for $\gamma > 1$) and at Figure \ref{} (for $\gamma < 1$).
+\ref{fig:Cubic1} (for $\gamma > 1$) and at Figure \ref{fig:Cubic2} (for $\gamma < 1$).
 Since log-log scale is employed, positive and negative velocities are shown in
@@
 \end{eqnarray*} 
-This sign change creates a vortex at the downstream part of the ion-exchanger, 
+This sign change creates a vortex at the downstream end of the ion-exchanger, 
 as demonstrated by the numerical simulation and the asymptotic analysis results 
-in Figure \ref{}.
-
-%        \includegraphics[width=0.7\textwidth]{figs}
+in Figure \ref{fig:Vortex}.
+
+\subsection{Discussion}
+The numerical solver results have good correspondence to the asymptotic linear model as
+shown above.
+
+Moreover, two interesting phenomena (cubic regime and downstream vortex) were predicted
+using the numerical results, and later verified using asymptotic expansion of the
+nonlinear system.
 
@@
         results are represented by squares.}
-    \label{Linear1}
+    \label{fig:Linear1}
     \end{center}
@@
         results are represented by circles.}
-    \label{Linear2}
+    \label{fig:Linear2}
     \end{center}
@@
         and the numerical results are represented by square markers.}
+	    \label{fig:Cubic1}
     \end{center}
-    \label{fig:Cubic1}
 \end{figure}
@@
         (squares for $\cU > 0$, circles for $\cU < 0$).}
+	    \label{fig:Cubic2}
     \end{center}
-    \label{fig:Cubic2}
 \end{figure}
@@
         $\gamma = 0.99$.  The steady-state velocity $\cU$ is positive, so the
-        ion-exchanger drifts to the right.}
+        ion-exchanger drifts to the right. 
+        }
+    \label{fig:Vortex}
     \end{center}
-    \label{fig:Vortex}
 \end{figure}
@@
 \begin{appendix}
-\section{Asymptotic Analysis} \label{sec:asymp}
+\section{Asymptotic Analysis} \label{app:asymp}
 The nonlinear system is defined by the following PDEs:
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Linear Solution $(k=1)$}
+\section{Linear Solution $(k=1)$} \label{app:linear}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Nonlinear Solution ($k > 1$)}
+\section{Nonlinear Solution ($k > 1$)} \label{app:cubic}
 Note that, due to symmetry considerations, $\cU(\beta)$ is an anti-symmetric function:

### 2012-03-25 notes/article/main.tex
Irad review

@@
 
-\title{A numerical solver for nonlinear electrokinetic phenomena}
+\title{Numerical and asymptotic solution of nonlinear electrokinetic phenomena}
 \author[cs]{Roman Zeyde}
@@
         \caption{Schematic structure of the double layer:
-        (1) particle surface, (2) Debye layer and (3) fluid bulk.
+        (1) particle surface, (2) Debye layer, (3) fluid bulk.
         If the particle surface has positive (blue) surface charge,
@@
 The variables of the electrokinetic problem are the electrostatic
-potential $\varphi$, fluid velocity $\bv$ and its pressure $p$ and
+potential $\varphi$, fluid velocity $\bv$ and its pressure $p$, and
 ionic concentration $c$.
@@
 under an external electric field, are coupled and nonlinear, and
-in general, they have no analytic solution. 
+in general they have no analytic solution. 
 Moreover, any numerical solver must handle the scale disparity caused by the
@@
 can be very useful in transporting and manipulating micro-
-and nanoscale objects for many nanotechnology applications,
+and nanoscale objects in many nanotechnology applications,
 such as the self-assembly of superstructures, roving sensors, 
@@
 \cite{howse2007self,paxton2004catalytic,pumera2010electrochemically}.
-However, since the analytic model for these electrokinetic
+However, since the model for these electrokinetic
 phenomena has no closed-form analytic solution, a numerical
-solver has to be developed for analysing such system.
-
-The goal of this work is to implement an iterative numerical
+solver for this system is of importance.
+
+The goal of this work is to develop and implement an iterative numerical
 solver for nonlinear electrokinetic problems, and apply it to the study
 of systems that have no closed-form solutions.
-It is expected to gain insight into the chemical and physical behavior 
+This solver can be used to gain insight into the chemical and physical behavior 
 in far more general regimes than are currently well-understood, 
-and also lead to further analytical developments, based on new scaling behavior
-provided by the numerical solver. We may also target interesting physical
+and also to possibly lead to further analytical developments, based on new scaling behavior
+discovered numerically. We may also target interesting physical
 phenomena that have been observed experimentally.
@@
 are derived in Section \ref{sec:equations}. The algorithm for the discretization and 
-the solution of the equation system is described at Section \ref{sec:algorithm}.
+the solution of the system is described in Section \ref{sec:algorithm}.
+The non-linear analytical asymptotic solution are presented in Section{sec:asymp}.
 The numerical results and their comparison to the analytical asymptotic solution 
@@
 
-Spatial coordinates $\br$ are normalized by $a^*$ (the characteristic size of the ion-exchanger).
-
-Positive and negative ionic concentrations are denoted by $c_+$ and $c_-$ respectively, and
-are normalized by ambient ionic concentration $c^*$. The ionic valences are $\pm z$.
-
-The dimensional ionic fluxes are given by Nernst-Plank equation 
-(using Einstein relation for the electric mobility, $\mu_q^* = D^* / k_B^* T^*$):
+Spatial coordinates $\br$ are normalized by $a^*$ 
+(the characteristic size of the ion-exchanging particle).
+
+Positive and negative ionic concentrations are denoted by $c_+$ and $c_-$, respectively, and
+are normalized by the ambient ionic concentration $c^*$. The ionic valences are $\pm z$.
+
+The dimensional ionic fluxes, $\bj_\pm$, are given by the Nernst-Plank equation 
+(using the Einstein relation for the electric mobility, $\mu_q^* = D^* / k_B^* T^*$):
 \begin{eqnarray*}
@@
 
-The dimensional Stokes equation:
-\begin{eqnarray*}
+The dimensional Stokes equations are given by:
+\begin{eqnarray*}
+\bnabla \cdot \bv &=& 0, \\
 -\bnabla p^* + \mu^* \bLaplacian \bv^* + \eps^* \Laplacian \varphi^* \bnabla \varphi^* &=& 0.
@@
 
-The nondimensional Nernst-Plank equation is written as:
+The nondimensional Nernst-Plank equation is then written as:
 \begin{eqnarray*}
@@
 
-The dimensional Poisson equation is:
+The dimensional Poisson equation can be written as:
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-and after nondimensionalization, is:
+and after nondimensionalization, is given by:
 \begin{eqnarray*}
@@
 
-The force is denoted by $\bF$ normalized by $\mu^* v^* a^* = \eps^* (\varphi^*)^2$.
+The force on the particle is denoted by $\bF$ normalized by $\mu^* v^* a^* = \eps^* (\varphi^*)^2$.
 The stress tensor is denoted by $\tT$ and normalized by $p^* = \mu^* v^* / a^*$.
@@
 \end{eqnarray*}
-These equation may be re-written by using the following transform:
+These equation may be re-written by using the following transformations:
 \begin{eqnarray*}
@@
 \subsubsection{Incompressible Stokes Flow with Electrostatic Force}
-Mass conservation (due to constant fluid density):
+Mass conservation (due to constant fluid density) reads:
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-Momentum conservation (force balance):
+Momentum conservation (force balance) reads:
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-Free charge density is given by the Poisson equation:
+Finally, free charge density is governed by the Poisson equation:
 \begin{eqnarray*}
@@
 \subsubsection{Boundary conditions}
-An constant electric field $\bE = \beta \ui$ is applied to the system.
-The ion-exchanger will acquire a non-zero steady-state velocity $\cU \ui$, which is
+We follow the physical setting described in \cite{yariv2010migration}.
+We assume that a constant constant electric field of magnitude $\beta$,
+is applied to the system, in direction denoted by the unit vector $\ui$.
+As a result, the ion-exchanger will equilibrate in 
+a non-zero steady-state velocity $\cU \ui$, which is
 a function of the applied field, and is not known a priori.
@@
 An ion-exchanger fixed reference frame is used.
-Far away from the particle, we have uniform applied electrostatic field, uniform flow
+Far away from the particle, we have a uniform applied electrostatic field, uniform flow,
 and ambient ionic concentrations:
@@
 At its surface $\mathcal{S}$ (defined at $r=1$ with normal $\bn = \brhat$), 
-we have zero slip, anion impermeability, cation selectivity 
+we assume zero slip, anion impermeability, cation selectivity 
 (with fast Butler-Volmer\cite{bard2000book} kinetics
-$\bn \cdot \bj_+ = k (1 - c_+/\gamma)$, where $k \rightarrow \infty$).
-and high conductance of the particle (yielding uniform electric potential):
+$\bn \cdot \bj_+ = k (1 - c_+/\gamma)$, where $k \rightarrow \infty$),
+and high conductance of the particle (yielding a uniform electric potential):
 \begin{eqnarray*}
@@
 except a thin boundary layer of width $O(\delta)$, 
-also known as the ``Debye layer'', surrounding the ion exchanger.
+known as the ``Debye layer'', surrounding the ion exchanger.
 
@@
 The Nernst-Planck equations above for the fluid bulk (outside
-the boundary layer), using bulk variables, read:
+the boundary layer), using bulk variables denoted by uppercase letters, read:
 \begin{eqnarray*}
@@
 \begin{enumerate}
-\item Salt conservation macroscale equation:
+\item Salt conservation in macroscale equation:
 \begin{eqnarray*} \label{eq:salt}
@@
 
-\item Charge conservation macroscale equation:
+\item Charge conservation in macroscale equations:
 \begin{eqnarray*} \label{eq:charge}
@@
 \begin{eqnarray*}
-0 &=& \varPhi + \log C \\
-0 &=& \bnhat \cdot \bnabla \pars{\varPhi - \log C} \\
+0 &=& \varPhi + \log C, \\
+0 &=& \bnhat \cdot \bnabla \pars{\varPhi - \log C}, \\
 \bV &=& 
@@
 \section{Algorithm Description} \label{sec:algorithm}
-The numerical solver starts by constructing a discrete approximation for the nonlinear system,
-for a given electric field $\beta$ and a velocity $\cU$. The nonlinear discrete system is
+The numerical solver first requires constructing a discrete 
+approximation for the nonlinear PDE system,
+for a given electric field $\beta$ and a velocity $\cU$. 
+The resulting nonlinear discrete system is
 solved numerically using Newton's Method, so the total force on the particle can be computed
-numerically. Variation of $\cU$ is used to find steady-state velocity, yielding zero total force.
+numerically. Variation of $\cU$ is used to find the steady-state velocity, 
+which corresponds to zero total force.
+
+The steady-state velocity is thus the solution to the nonlinear scalar equation
+\begin{eqnarray*}
+F(\beta, \cU) = 0,
+\end{eqnarray*}
+which we solver by standard secant method.
 
@@
 It is important to note that due to the choice of spherical coordinate system,
-the vector Laplacian operator cannot be computed as in the Cartesian system,
+the vector Laplacian operator cannot be computed in a decoupled manner as in the Cartesian system,
 since the unit vectors $\brhat, \bthetahat, \bphihat$ are functions of the coordinates
@@
 \end{eqnarray*}
-where a logarithmic grid spacing is used for $r$ and a uniform grid is used for $\theta$.
+where a logarithmic grid spacing has been chosen for $r$ and a uniform grid for $\theta$.
 Note that $r_0 = 1$ and $R_{max} = (1+\Delta_r)^{n_r}$ should be much 
@@
 When the method converges, $\bx_n \rightarrow \bx_\infty$, 
-the convergence is in general quadratic:
+the asymptotic convergence is in general quadratic:
 \begin{eqnarray*}
@@
 
-Since the goal is to find steady-state solution, $F_\imath(\cU)$ 
+Since the goal is to find the steady-state solution, $F_\imath(\cU)$ 
 is required to be zero --
@@
 
-The iterative solver above can be used to compute the steady-state solution for any given $\beta$.
-For $\beta \ll 1$, the linear terms are the dominant ones, so the solution is linear in $\beta$ 
+The iterative solver above can be used in principle to compute the steady-state solution for any given $\beta$.
+For $\beta \ll 1$, the linear terms are the dominant ones, 
+so the solution is approximately linear in $\beta$ 
 (as derived in \cite{yariv2010migration}), and the solver convergence is fast.
 
-However, it is no longer true for $\beta \sim O(1)$, since the nonlinear terms become dominant
-and the iterative solver may not converge at all.
+However, this is no longer true for $\beta \sim O(1)$, since the nonlinear terms become dominant
+and the iterative solver may not converge at all if we start with an arbitrary initial guess.
 In order to find a solution for such $\beta$, continuation method is used:
@@
 and high-level language features.
-The source code of solver can be found at \cite{source}.
+The source code of the solver is provided in \cite{source}.
 
@@
 \subsubsection{Iterative Newton solver}
-Given an initial solution $\bx_0$ and specific values for $\beta$ and $\cU$, 
+Given an initial solution $\bx_0$ and prescribed values for $\beta$ and $\cU$, 
 we apply the following algorithm 
@@
 After the iterative Newton solver converges ($\bx_n \rightarrow \bx_\infty$), 
-the ``ghost'' point values are computed by computing $\cB(\bx_\infty)$ and
-the total force $\bF$ acting on the ion-exchanger.
+the ``ghost'' point values are computed via $\cB(\bx_\infty)$,
+followed by a computation of the total force $\bF$ acting on the ion-exchanger.
 
@@
 \end{eqnarray*}
-This equation can be solved using a 1D root finding algorithm, e.g. the secant method:
+This equation can be solved using a 1D root finding algorithm, e.g., the secant method:
 \begin{eqnarray*}
@@
 
-The computational grid for the problem is chosen to be of the size $400 \times 50$.
-
-Since there are five variables ($\varPhi, C, V_r, V_\theta, P$), the concatenated
+The computational grid for the problem is chosen to be of size $400 \times 50$.
+
+Because there are five different variables ($\varPhi, C, V_r, V_\theta, P$), the concatenated
 variable $\bx$ has dimension of $\sim 10^5$.
 
-$R_{\max}$ is chosen to be $10^{7}$ so truncation effect should be negligible.
-
-The solver is applied to a series of values of $\beta$, from $\beta \ll 1$ up to $\beta \sim O(1)$.
+$R_{\max}$ is chosen to be $10^{7}$ so the truncation effect is negligible.
+
+The solver is applied to a series of values of $\beta$, ranging 
+from $\beta \ll 1$ up to $\beta \sim O(1)$.
 For each $\beta$ value, the steady-state velocity $\cU(\beta)$ is computed. The solver
@@
 
-The resulting $\cU(\beta)$ is plotted using a log-log graph, so the asymptotic behaviour
-of the solution could be examined for a wide range of $\beta$ values.
+The resulting $\cU(\beta)$ is plotted on a log-log scale, so that the asymptotic behaviour
+of the solution may be examined for a wide range of $\beta$ values.
 
 In order to validate the numerical solver, an asymptotic analysis of the nonlinear system
-is performed as described in \ref{app:asymp}. The numerical results are compared to 
+is performed as described in \ref{app:asymp}. The numerical results are compared 
 to the asymptotic solutions, and good correspondence is achieved.
@@
 \subsection{Linear Regime}
-For $\beta \ll 1$, the linear regime takes place (for derivation, see \ref{app:linear}):
+For $\beta \ll 1$, the linear regime is dominant (for derivation, see \ref{app:linear}):
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-Thus, for $\gamma > 1$, the Debye layer has positive space charge, corresponding to a negative
+Thus, for $\gamma > 1$, the Debye layer has a positive space charge, corresponding to a negative
 particle charge -- yielding negative drift velocity, $\cU < 0$. 
-For $\gamma < 1$, we have $\cU > 0$, respectively.
-
-The linear regime is simulated for $\gamma > 1$ (at Figure \ref{fig:Linear1})  
-and for $\gamma < 1$ (at Figure \ref{fig:Linear2}).
+For $\gamma < 1$, we have $\cU > 0$.
+
+The numerical and asymptotic analytical solutions for the linear regime are compared for 
+for $\gamma > 1$ (in Figure \ref{fig:Linear1})  
+and for $\gamma < 1$ (in Figure \ref{fig:Linear2}).
 
 \subsection{Cubic Regime}
-When $\gamma \approx 1$, the cubic regime  (for derivation, see \ref{app:cubic}), where
-\begin{eqnarray*}
-\cU = O(\beta^3), 
-\end{eqnarray*}
-dominates the linear one, even for weak electric fields.
+When $\gamma \approx 1$, the cubic regime, where $\cU = O(\beta^3)$, 
+dominates the linear one, even for weak electric fields
+(for derivation, see \ref{app:cubic}).
 
@@
 results and by asymptotic expansion of the nonlinear system (for $\alpha=0$).
-The switch from the linear regime to the cubic one happens at a critical electric
+The switch from the linear regime to the cubic regime occurs at a critical electric
 field value
@@
 
-The numerical results, as well as the analytical ones, are given at Figure
-\ref{fig:Cubic1} (for $\gamma > 1$) and at Figure \ref{fig:Cubic2} (for $\gamma < 1$).
-Since log-log scale is employed, positive and negative velocities are shown in
+The numerical results, as well as the analytical ones, are given in Figure
+\ref{fig:Cubic1} (for $\gamma > 1$) and in Figure \ref{fig:Cubic2} (for $\gamma < 1$).
+Because a log-log scale is employed, positive and negative velocities are shown in
 the same plot using different markers and line styles.
@@
 This sign change creates a vortex at the downstream end of the ion-exchanger, 
-as demonstrated by the numerical simulation and the asymptotic analysis results 
+as demonstrated by the numerical solution and the asymptotic analysis results 
 in Figure \ref{fig:Vortex}.
@@
 \subsection{Discussion}
-The numerical solver results have good correspondence to the asymptotic linear model as
+The numerical results exhibit a good correspondence to the asymptotic linear model as
 shown above.
@@
 \bnabla \cdot \pars{\bnabla C - \alpha \bV C} &=& 0, \\
+\bnabla \cdot \bV &=& 0, \\
 \bLaplacian \bV - \bnabla P + \Laplacian \varPhi \bnabla \varPhi &=& \bzero.
@@
 For $\zeta(\theta) = \cV - \varPhi(1, \theta)$ and 
-$\cV = -\log \gamma$, the boundary conditions on $r = 1$ are:
+$\cV = -\log \gamma$, the boundary conditions at $r = 1$ are given by
 \begin{eqnarray*}
@@
 
-The boundary conditions for $r \rightarrow \infty$ are:
+The boundary conditions for $r \rightarrow \infty$ are given by
 \begin{eqnarray*}
@@
 
-The solution to the nonlinear system can be written as a Taylor series in $\beta$.
+The solution to the nonlinear system can be expanded in a Taylor series in $\beta$.
 \begin{eqnarray*}
@@
 
-The first order terms are:
+The first-order terms are given by
 \begin{eqnarray*}
@@
 
-The slip velocity satisfies:
+The slip velocity satisfies
 \begin{eqnarray*}
@@
 \begin{eqnarray*}
-\cU(\beta) &\approx& \beta \cU_1 + \beta^3 \cU_3 + O(\beta^5)
-\end{eqnarray*}
-
-In order to find the cubic terms, the quadratic term should be found first.
+\cU(\beta) &\approx& \beta \cU_1 + \beta^3 \cU_3 + O(\beta^5).
+\end{eqnarray*}
+
+In order to find the cubic terms, the quadratic terms must be computed first.
 
@@
 
-The linear and the cubic velocity terms (for $\alpha = 0$) are:
+The linear and the cubic velocity terms (for $\alpha = 0$) are then
 \begin{eqnarray*}

### 2012-03-27 notes/article/main.tex
Fix figures.
Work on paper.

@@
 the solution of the system is described in Section \ref{sec:algorithm}.
-The non-linear analytical asymptotic solution are presented in Section{sec:asymp}.
+The analytical asymptotic solution for the non-linear system is derived 
+and presented in Section \ref{sec:asymp}.
 The numerical results and their comparison to the analytical asymptotic solution 
@@
 At its surface $\mathcal{S}$ (defined at $r=1$ with normal $\bn = \brhat$), 
-we assume zero slip, anion impermeability, cation selectivity 
+we assume high conductance of the particle (yielding a uniform electric potential),
+zero slip, anion impermeability, cation selectivity 
 (with fast Butler-Volmer\cite{bard2000book} kinetics
-$\bn \cdot \bj_+ = k (1 - c_+/\gamma)$, where $k \rightarrow \infty$),
-and high conductance of the particle (yielding a uniform electric potential):
-\begin{eqnarray*}
+$\bn \cdot \bj_+ = k (1 - c_+/\gamma)$, where $k \rightarrow \infty$):
+\begin{eqnarray*}
+\varphi & = & \cV, \\
 \bv & = & \bzero, \\
@@
 c_+ &=& \gamma, \\
-\varphi & = & \cV.
-\end{eqnarray*}
+\end{eqnarray*}
+where $\gamma$ is the ratio between the cationic concentration on the surface and the cationic
+concentration in the fluid bulk.
 
@@
 \zeta \cdot \bnabla_\mathcal{S} \varPhi 
-+ 2\log\pars{1-\tanh^2\frac{\zeta}{4}} \cdot \bnabla_\mathcal{S} \log C.
++ 2\log\pars{1-\tanh^2\frac{\zeta}{4}} \cdot \bnabla_\mathcal{S} \log C,
 \end{eqnarray*}
@@
 
-The iterative solver above can be used in principle to compute the steady-state solution for any given $\beta$.
+The iterative solver above can in principle be used 
+to compute the steady-state solution for any given $\beta$.
 For $\beta \ll 1$, the linear terms are the dominant ones, 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Asymptotic Analysis} \label{sec:asymp}
+The nonlinear system is defined by the following PDEs:
+\label{PDEs}
+\begin{eqnarray*}
+\bnabla \cdot \pars{C \bnabla \varPhi} &=& 0, \\
+\bnabla \cdot \pars{\bnabla C - \alpha \bV C} &=& 0, \\
+\bnabla \cdot \bV &=& 0, \\
+\bLaplacian \bV - \bnabla P + \Laplacian \varPhi \bnabla \varPhi &=& \bzero.
+\end{eqnarray*}
+
+For $\zeta(\theta) = \cV - \varPhi(1, \theta)$ and 
+$\cV = -\log \gamma$, the boundary conditions at $r = 1$ are given by
+\begin{eqnarray*}
+\varPhi + \log C &=& \cV + \log \gamma = 0, \\
+\deriv{}{r}\pars{\varPhi - \log C} &=& \frac{J_-}{C} = 0, \\
+\bV = \zeta \cdot \bnabla_\mathcal{S} \varPhi 
++ 2\log\pars{1-\tanh^2\frac{\zeta}{4}} \cdot \bnabla_\mathcal{S} \log C
+&=& 4\log\pars{\frac{1 + e^\frac{\zeta}{2}}{2}} \bnabla_S \varPhi.
+\end{eqnarray*}
+
+The boundary conditions for $r \rightarrow \infty$ are given by
+\begin{eqnarray*}
+\bnabla \varPhi &=& -\beta \ui, \\
+C &=& 1, \\
+\bV &=& -\cU \ui,
+\end{eqnarray*}
+and the total force acting on the particle is zero: $\bF = \bzero$.
+
+The nonlinear system can be written as: 
+\begin{eqnarray*}
+\cO(\bx;\beta) &=& \bzero.
+\end{eqnarray*}
+
+The solution to the nonlinear system can be expanded in a Taylor series in $\beta$.
+\begin{eqnarray*}
+\bx = \bx(\beta) &\approx& \sum_n \bx_n \beta^n.
+\end{eqnarray*}
+
+All the variables are expanded around $\beta = 0$:
+\begin{eqnarray*}
+\varPhi &=& \beta \varPhi_1 + \beta^2 \varPhi_2 + \beta^3 \varPhi_3 + \ldots, \\
+C &=& 1 + \beta C_1 + \beta^2 C_2 + \beta^3 C_3 + \ldots, \\
+\Psi &=& \beta \Psi_1 + \beta^2 \Psi_2 + \beta^3 \Psi_3 + \ldots ,
+\end{eqnarray*}
+where the velocity $\bV$ and pressure $P$ are computed from the streamfunction $\Psi$:
+\begin{eqnarray*}
+\bV &=& \bnabla \times \pars{\frac{\Psi}{r \sin\theta} \bphihat} 
+= \frac{1}{r^2 \sin\theta} \deriv{\Psi}{\theta} \brhat 
+- \frac{1}{r \sin\theta} \deriv{\Psi}{r} \bthetahat.
+\end{eqnarray*}
+
+The nonlinear equations and the boundary conditions are expanded around $\beta = 0$
+and arranged by powers of $\beta$:
+\begin{eqnarray*}
+\bzero = \cO(\bx) = \sum_k \cO_k(\bx_0, \ldots \bx_k) \beta^k
+\end{eqnarray*}
+This can be rewritten as a system of equations:
+\begin{eqnarray*}
+\brc{rcl}{
+\bzero &=& \cO_0(\bx_0), \\
+\bzero &=& \cO_1(\bx_0, \bx_1), \\
+\bzero &=& \cO_2(\bx_0, \bx_1, \bx_2), \\
+& \vdots & \\
+\bzero &=& \cO_k(\bx_0, \bx_1, \bx_2, \ldots \bx_k).
+}
+\end{eqnarray*}
+Thus, the $O(\beta^k)$ term $\bx_k$ can be found recursively by solving 
+$\cO_k(\bx_0, \bx_1, \ldots, \bx_k) = \bzero$,
+given the previous solutions for $\bx_0, \ldots, \bx_{k-1}$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Linear Solution $(k=1)$} \label{app:linear}
+
+For $\beta = 0$ (no electric field is applied), the steady-state solution is $\cU = 0$:
+\begin{eqnarray*}
+\varPhi_0(r,\theta) &=& 0, \\
+C_0(r,\theta) &=& 1, \\
+\bV_0(r,\theta) &=& \bzero, \\
+P_0(r,\theta) &=& 0.
+\end{eqnarray*}
+
+Assuming $\beta \ll 1$, the linearized equations and boundary conditions are 
+(as developed in \cite{yariv2010migration}):
+\begin{eqnarray*}
+\Laplacian \varPhi_1 &=& 0, \\
+\Laplacian C_1 &=& 0, \\
+\bLaplacian \bV_1 - \bnabla P_1 &=& \bzero.
+\end{eqnarray*}
+
+The first-order terms are given by
+\begin{eqnarray*}
+\varPhi &=& \beta \pars{\frac{1}{4r^2} - r}\cos\theta, \\
+C &=& 1 + \beta \frac{3}{4r^2} \cos\theta, \\
+\Psi &=& \beta \cU_1 \pars{\frac{1}{r} - r^2} \frac{\sin^2\theta}{2}, \\
+\bV &=& -\beta \cU_1 \brcs{\pars{1 - \frac{1}{r^3}}\cos\theta \cdot \brhat - 
+                               \pars{1 + \frac{1}{2r^3}} \sin\theta \cdot \bthetahat}, \\
+P &=& 0, \\
+\bF &=& \bzero.
+\end{eqnarray*}
+
+The slip velocity satisfies
+\begin{eqnarray*}
+\beta \cU_1 \frac{3}{2} \sin\theta =
+V_\theta &=& 4 \log \pars{\frac{1 + e ^ \frac{\zeta}{2}}{2}} \deriv{\varPhi}{\theta} 
+=
+ 3 \beta \log \pars{\frac{1 + e ^ \frac{\zeta}{2}}{2}} \sin\theta, \\
+\cU_1 &=& 2 \log \pars{\frac{1 + e ^ \frac{\zeta}{2}}{2}} 
+       =  2 \log \pars{\frac{1 + \gamma ^ {-\frac{1}{2}}}{2}}.
+\end{eqnarray*}
+because $\varPhi_1 = -C_1 = -\frac{3}{4} \cos\theta$ on $r=1$
+and $\zeta_0 = -\log\gamma$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Nonlinear Solution ($k > 1$)} \label{app:cubic}
+Note that, due to symmetry considerations, $\cU(\beta)$ is an anti-symmetric function:
+\begin{eqnarray*}
+\cU(-\beta) &=& -\cU(\beta).
+\end{eqnarray*}
+Therefore, $\cU_2 = 0$ and the next velocity term is the cubic one:
+\begin{eqnarray*}
+\cU(\beta) &\approx& \beta \cU_1 + \beta^3 \cU_3 + O(\beta^5).
+\end{eqnarray*}
+
+In order to find the cubic terms, the quadratic terms must be computed first.
+
+The quadratic terms $\bx_2$ are computed by solving a linear PDE system 
+with a right-hand side determined by the linear terms $\bx_1$:
+\begin{eqnarray*}
+\varPhi_2 &=& \frac{\left(\frac{\cU_1\, \alpha}{32} - \frac{1}{16}\right)\, \left(3\, {\cos^2\theta} - 1\right)}{r^3} - \frac{3}{32\, r^4} - \frac{3\, {\sin^2\theta}\, \left(4\, r^3 - 1\right)}{32\, r^4} - \frac{3\, \cU_1\, \alpha - 6}{32\, r},
+\\
+C_2 &=& \frac{\left(\frac{5\, \cU_1\, \alpha}{32} + \frac{1}{16}\right)\, \left(3\, {\cos^2\theta} - 1\right)}{r^3} - \frac{3\, \cU_1\, \alpha - 6}{32\, r} + \frac{3\, \cU_1\, \alpha\, \left(2\, r^3\, {\sin^2\theta} + {\sin^2\theta} - 1\right)}{16\, r^4},
+\\
+\Psi_2 &=& \pars{\frac{9}{16(\sqrt{\gamma}+1)} - \frac{3}{16} \cU_1 (\cU_1 \alpha + 1)}
+ \left(\frac{1}{r^2} - 1\right) \sin^2\theta \cos\theta,  \\
+\bF_2 &=& \bzero, \\ \cU_2 &=& 0.
+\end{eqnarray*}
+Note that the quadratic term does not contribute to the total force and steady-state 
+velocity terms, but it does change the fluid flow, 
+the electric potential and the ionic concentration.
+
+The cubic terms $\bx_3$ are computed by solving a linear PDE system 
+with a right-hand side determined by the linear terms $\bx_1$ and the quadratic terms $\bx_2$:
+\begin{eqnarray*}
+\varPhi_3 &=& \cos\theta \left(\frac{15 \cU_1\alpha}{64} + \frac{3}{32}\right) - \frac{3 \cU_1\alpha {\cos}^3\theta}{32} - \frac{\cos\theta \left( - 183 {\cU_1}^2\alpha^2 + 839 \cU_1\alpha + 470\right)}{2560 r^2} \\
+&&+ \frac{3 \cos\theta \left(5 \cU_1\alpha - 6 {\cos^2\theta} - 4 \cU_1\alpha {\cos^2\theta} + 4\right)}{64 r^3} + \frac{\left(2 \cU_1\alpha - 1\right) \left(\cos\theta - 3 {\cos}^3\theta\right)}{64 r^5}
+\\ 
+&&- \frac{\left(3 \cos\theta - 5 {\cos}^3\theta\right) \left( - \frac{19 {\cU_1}^2\alpha^2}{5120} + \frac{97 \cU_1\alpha}{5120} + \frac{3 \cU_2\alpha}{320} + \frac{21}{1280}\right)}{r^4} + \frac{{\cos}^3\theta \left(\frac{15 \cU_1\alpha}{64} + \frac{3}{32}\right)}{r^2} \\
+&&+ \frac{{\cos}^3\theta \left(\frac{\cU_1\alpha}{64} + \frac{3}{64}\right)}{r^6},
+\\
+C_3 &=&
+\frac{3 {{\cU_1}}^2\alpha^2 {\cos^3\theta}}{32} + \frac{\cos\theta \left(797 {{\cU_1}}^2\alpha^2 + 419 {\cU_1}\alpha - 512 {\cU_2}\alpha + 174\right)}{2560 r^2} \\
+&&- \frac{\left(3 \cos\theta - 5 {\cos^3\theta}\right) \left(\frac{59 {{\cU_1}}^2\alpha^2}{5120} + \frac{103 {\cU_1}\alpha}{5120} + \frac{69 {\cU_2}\alpha}{320} + \frac{3}{1280}\right)}{r^4} \\
+&&- \frac{3\alpha \cos\theta \left( - 8\alpha {{\cU_1}}^2 {\cos^2\theta} + 7\alpha {{\cU_1}}^2 + 2 {\cU_1} + 32 {\cU_2} {\cos^2\theta} - 32 {\cU_2}\right)}{128 r^3} - \frac{3 {\cU_1}\alpha \cos\theta \left(5 {\cU_1}\alpha + 2\right)}{64} \\
+&&+ \frac{\alpha \left(\cos\theta - 3 {\cos^3\theta}\right) \left(5\alpha {{\cU_1}}^2 + 2 {\cU_1} + 16 {\cU_2}\right)}{128 r^5} + \frac{{{\cU_1}}^2\alpha^2 {\cos^3\theta}}{32 r^6} - \frac{3 {\cU_1}\alpha {\cos^3\theta} \left(5 {\cU_1}\alpha + 2\right)}{64 r^2},
+\\
+\Psi_3 &=&
+r^2 {\sin^2\theta} \left(\frac{{\cW_2}}{15} - \frac{{\cW_1}}{3} + \frac{209}{3360}\right) 
+ - \frac{{\sin^2\theta} \left(\frac{5 {\cW_2}}{3} - \frac{{\cW_1}}{3} + \frac{35}{264}\right)}{r}
+\\ && + \frac{{\sin^4\theta} \left(2 {\cW_2} + \frac{761}{5632}\right)}{r} - \frac{{\sin^2\theta} \left(1848 r^6 {\sin^2\theta} - 2079 r^3 {\sin^2\theta} + 924 r^3 - 7 {\sin^2\theta} + 10\right)}{19712 r^5}
+\\ && + \frac{\left(\frac{2 {\cW_2}}{5} + \frac{829}{28160}\right) \left(4 {\sin^2\theta} - 5 {\sin\theta}^4\right)}{r^3} + \frac{{\sin^2\theta} \left(\frac{{\cU_1}\alpha}{16} - \frac{1}{8}\right) \left(2 r^3 - 3 r^2 + 1\right)}{4 r},
+\\
+\cW_1 &=& \frac{69}{512 \left(\sqrt{\gamma} + 1\right)} - \frac{1407\alpha^2 {\log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}^3}{1280} - \frac{123 \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{1280} - \frac{27}{512 {\left(\sqrt{\gamma} + 1\right)}^2} \\ && -
+\frac{1899\alpha {\log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}^2}{2560} - \frac{\alpha \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right) \left(\frac{81}{16 \left(\sqrt{\gamma} + 1\right)} - \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right) \left(\frac{27\alpha \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{4} + \frac{27}{8}\right)\right)}{320} \\ && +
+\frac{21\alpha \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{128 \left(\sqrt{\gamma} + 1\right)},
+\\
+\cW_2 &=& \frac{9 \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{256} + \frac{21\alpha^2 {\log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}^3}{64} - \frac{27}{512 \left(\sqrt{\gamma} + 1\right)} - \frac{27}{512 {\left(\sqrt{\gamma} + 1\right)}^2}
+ + \frac{15\alpha {\log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}^2}{64} 
+\\ && 
+- \frac{297\alpha \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{1024 \left(\sqrt{\gamma} + 1\right)}.
+\end{eqnarray*}
+
+The cubic solution satisfies the $\lim_{r\rightarrow\infty}C_3 = 0$ boundary condition, 
+when $\alpha\cU_1 = 0$.
+
+The steady-state velocity can be expanded using odd powers of $\beta$:
+\begin{eqnarray*}
+\cU(\beta, \gamma) &=& \cU_1(\gamma) \beta + \cU_3(\gamma) \beta^3.
+\end{eqnarray*}
+
+The linear and the cubic velocity terms (for $\alpha = 0$) are then
+\begin{eqnarray*}
+\cU_1(\gamma) &=& 2 \log \pars{\frac{1 + \gamma^{-\frac{1}{2}}}{2}}, \\
+\cU_3(\gamma) &=& \frac{31}{320(\sqrt\gamma + 1)} - \frac{9}{320(\sqrt\gamma + 1)^2} + \frac{1}{1680} - \frac{11}{160} \log \pars{\frac{1 + \gamma^{-\frac{1}{2}}}{2}}.
+\end{eqnarray*}
+
+Note that, for $\gamma = 1$, the linear term vanishes and the velocity leading term is $O(\beta^3)$:
+\begin{eqnarray*}
+\cU(\beta) = \frac{1129}{26880}\beta^3.
+\end{eqnarray*}
+
+Note that a $\cU = 0$ solution may exist for $\beta_c \ne 0$ and $\alpha = 0$, 
+if it satisfies:
+\begin{eqnarray*}
+\beta_c^2 = -\frac{\cU_1(\gamma)}{\cU_3(\gamma)}.
+\end{eqnarray*}
+For $\gamma = 1 + \eps$, where $0 < \eps \ll 1$:
+\begin{eqnarray*}
+\beta_c \approx \sqrt{-\frac{\cU_1'(1) \eps}{\cU_3(1)}} = 
+ \sqrt{\frac{13440 \eps}{1129}} \approx 3.45 \sqrt{\eps}.
+\end{eqnarray*}
+However, for $\gamma \gg 1$, we have:
+\begin{eqnarray*}
+\beta_c =  \pars{\frac{11}{320} + \frac{1}{1680 \log 4}}^{-\frac{1}{2}} \approx 5.36.
+\end{eqnarray*}
+
+The cubic term becomes dominant for small $\beta$ when $\gamma \approx 1$.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 In order to validate the numerical solver, an asymptotic analysis of the nonlinear system
-is performed as described in \ref{app:asymp}. The numerical results are compared 
+is performed as described in \ref{sec:asymp}. The numerical results are compared 
 to the asymptotic solutions, and good correspondence is achieved.
@@
 The switch from the linear regime to the cubic regime occurs at a critical electric
-field value
-\begin{eqnarray*}
-\beta_c = O(\sqrt{|\gamma - 1|}).
-\end{eqnarray*}
+field value $\beta_c = O(\sqrt{|\gamma - 1|})$.
 
@@
     \begin{center}
-    \includegraphics[width=0.45\textwidth]{figs/Linear/g=2.00.eps}
-    \includegraphics[width=0.45\textwidth]{figs/Linear/g=5.00.eps}
-    \includegraphics[width=0.45\textwidth]{figs/Linear/g=10.00.eps}
-    \includegraphics[width=0.45\textwidth]{figs/Linear/g=100.00.eps}
+    \includegraphics[width=0.8\textwidth]{figs/linearNeg.eps}
     \caption{Steady-state velocity $\cU$ as a function of the 
@@
     \begin{center}
-    \includegraphics[width=0.45\textwidth]{figs/Linear/g=0.50.eps}
-    \includegraphics[width=0.45\textwidth]{figs/Linear/g=0.20.eps}
-    \includegraphics[width=0.45\textwidth]{figs/Linear/g=0.10.eps}
-    \includegraphics[width=0.45\textwidth]{figs/Linear/g=0.01.eps}
+    \includegraphics[width=0.8\textwidth]{figs/linearPos.eps}
     \caption{Steady-state velocity $\cU$ as a function of the 
@@
 
-\begin{appendix}
-\section{Asymptotic Analysis} \label{app:asymp}
-The nonlinear system is defined by the following PDEs:
-\label{PDEs}
-\begin{eqnarray*}
-\bnabla \cdot \pars{C \bnabla \varPhi} &=& 0, \\
-\bnabla \cdot \pars{\bnabla C - \alpha \bV C} &=& 0, \\
-\bnabla \cdot \bV &=& 0, \\
-\bLaplacian \bV - \bnabla P + \Laplacian \varPhi \bnabla \varPhi &=& \bzero.
-\end{eqnarray*}
-
-For $\zeta(\theta) = \cV - \varPhi(1, \theta)$ and 
-$\cV = -\log \gamma$, the boundary conditions at $r = 1$ are given by
-\begin{eqnarray*}
-\varPhi + \log C &=& \cV + \log \gamma = 0, \\
-\deriv{}{r}\pars{\varPhi - \log C} &=& \frac{J_-}{C} = 0, \\
-\bV = \zeta \cdot \bnabla_\mathcal{S} \varPhi 
-+ 2\log\pars{1-\tanh^2\frac{\zeta}{4}} \cdot \bnabla_\mathcal{S} \log C
-&=& 4\log\pars{\frac{1 + e^\frac{\zeta}{2}}{2}} \bnabla_S \varPhi.
-\end{eqnarray*}
-
-The boundary conditions for $r \rightarrow \infty$ are given by
-\begin{eqnarray*}
-\bnabla \varPhi &=& -\beta \ui, \\
-C &=& 1, \\
-\bV &=& -\cU \ui,
-\end{eqnarray*}
-and the total force acting on the particle is zero: $\bF = \bzero$.
-
-The nonlinear system can be written as: 
-\begin{eqnarray*}
-\cO(\bx;\beta) &=& \bzero.
-\end{eqnarray*}
-
-The solution to the nonlinear system can be expanded in a Taylor series in $\beta$.
-\begin{eqnarray*}
-\bx = \bx(\beta) &\approx& \sum_n \bx_n \beta^n.
-\end{eqnarray*}
-
-All the variables are expanded around $\beta = 0$:
-\begin{eqnarray*}
-\varPhi &=& \beta \varPhi_1 + \beta^2 \varPhi_2 + \beta^3 \varPhi_3 + \ldots, \\
-C &=& 1 + \beta C_1 + \beta^2 C_2 + \beta^3 C_3 + \ldots, \\
-\Psi &=& \beta \Psi_1 + \beta^2 \Psi_2 + \beta^3 \Psi_3 + \ldots ,
-\end{eqnarray*}
-where the velocity $\bV$ and pressure $P$ are computed from the streamfunction $\Psi$:
-\begin{eqnarray*}
-\bV &=& \bnabla \times \pars{\frac{\Psi}{r \sin\theta} \bphihat} 
-= \frac{1}{r^2 \sin\theta} \deriv{\Psi}{\theta} \brhat 
-- \frac{1}{r \sin\theta} \deriv{\Psi}{r} \bthetahat.
-\end{eqnarray*}
-
-The nonlinear equations and the boundary conditions are expanded around $\beta = 0$
-and arranged by powers of $\beta$:
-\begin{eqnarray*}
-\bzero = \cO(\bx) = \sum_k \cO_k(\bx_0, \ldots \bx_k) \beta^k
-\end{eqnarray*}
-This can be rewritten as a system of equations:
-\begin{eqnarray*}
-\brc{rcl}{
-\bzero &=& \cO_0(\bx_0), \\
-\bzero &=& \cO_1(\bx_0, \bx_1), \\
-\bzero &=& \cO_2(\bx_0, \bx_1, \bx_2), \\
-& \vdots & \\
-\bzero &=& \cO_k(\bx_0, \bx_1, \bx_2, \ldots \bx_k).
-}
-\end{eqnarray*}
-Thus, the $O(\beta^k)$ term $\bx_k$ can be found recursively by solving 
-$\cO_k(\bx_0, \bx_1, \ldots, \bx_k) = \bzero$,
-given the previous solutions for $\bx_0, \ldots, \bx_{k-1}$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Linear Solution $(k=1)$} \label{app:linear}
-
-For $\beta = 0$ (no electric field is applied), the steady-state solution is $\cU = 0$:
-\begin{eqnarray*}
-\varPhi_0(r,\theta) &=& 0, \\
-C_0(r,\theta) &=& 1, \\
-\bV_0(r,\theta) &=& \bzero, \\
-P_0(r,\theta) &=& 0.
-\end{eqnarray*}
-
-Assuming $\beta \ll 1$, the linearized equations and boundary conditions are 
-(as developed in \cite{yariv2010migration}):
-\begin{eqnarray*}
-\Laplacian \varPhi_1 &=& 0, \\
-\Laplacian C_1 &=& 0, \\
-\bLaplacian \bV_1 - \bnabla P_1 &=& \bzero.
-\end{eqnarray*}
-
-The first-order terms are given by
-\begin{eqnarray*}
-\varPhi &=& \beta \pars{\frac{1}{4r^2} - r}\cos\theta, \\
-C &=& 1 + \beta \frac{3}{4r^2} \cos\theta, \\
-\Psi &=& \beta \cU_1 \pars{\frac{1}{r} - r^2} \frac{\sin^2\theta}{2}, \\
-\bV &=& -\beta \cU_1 \brcs{\pars{1 - \frac{1}{r^3}}\cos\theta \cdot \brhat - 
-                               \pars{1 + \frac{1}{2r^3}} \sin\theta \cdot \bthetahat}, \\
-P &=& 0, \\
-\bF &=& \bzero.
-\end{eqnarray*}
-
-The slip velocity satisfies
-\begin{eqnarray*}
-\beta \cU_1 \frac{3}{2} \sin\theta =
-V_\theta &=& 4 \log \pars{\frac{1 + e ^ \frac{\zeta}{2}}{2}} \deriv{\varPhi}{\theta} 
-=
- 3 \beta \log \pars{\frac{1 + e ^ \frac{\zeta}{2}}{2}} \sin\theta, \\
-\cU_1 &=& 2 \log \pars{\frac{1 + e ^ \frac{\zeta}{2}}{2}} 
-       =  2 \log \pars{\frac{1 + \gamma ^ {-\frac{1}{2}}}{2}}.
-\end{eqnarray*}
-because $\varPhi_1 = -C_1 = -\frac{3}{4} \cos\theta$ on $r=1$
-and $\zeta_0 = -\log\gamma$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Nonlinear Solution ($k > 1$)} \label{app:cubic}
-Note that, due to symmetry considerations, $\cU(\beta)$ is an anti-symmetric function:
-\begin{eqnarray*}
-\cU(-\beta) &=& -\cU(\beta).
-\end{eqnarray*}
-Therefore, $\cU_2 = 0$ and the next velocity term is the cubic one:
-\begin{eqnarray*}
-\cU(\beta) &\approx& \beta \cU_1 + \beta^3 \cU_3 + O(\beta^5).
-\end{eqnarray*}
-
-In order to find the cubic terms, the quadratic terms must be computed first.
-
-The quadratic terms $\bx_2$ are computed by solving a linear PDE system 
-with a right-hand side determined by the linear terms $\bx_1$:
-\begin{eqnarray*}
-\varPhi_2 &=& \frac{\left(\frac{\cU_1\, \alpha}{32} - \frac{1}{16}\right)\, \left(3\, {\cos^2\theta} - 1\right)}{r^3} - \frac{3}{32\, r^4} - \frac{3\, {\sin^2\theta}\, \left(4\, r^3 - 1\right)}{32\, r^4} - \frac{3\, \cU_1\, \alpha - 6}{32\, r},
-\\
-C_2 &=& \frac{\left(\frac{5\, \cU_1\, \alpha}{32} + \frac{1}{16}\right)\, \left(3\, {\cos^2\theta} - 1\right)}{r^3} - \frac{3\, \cU_1\, \alpha - 6}{32\, r} + \frac{3\, \cU_1\, \alpha\, \left(2\, r^3\, {\sin^2\theta} + {\sin^2\theta} - 1\right)}{16\, r^4},
-\\
-\Psi_2 &=& \pars{\frac{9}{16(\sqrt{\gamma}+1)} - \frac{3}{16} \cU_1 (\cU_1 \alpha + 1)}
- \left(\frac{1}{r^2} - 1\right) \sin^2\theta \cos\theta,  \\
-\bF_2 &=& \bzero, \\ \cU_2 &=& 0.
-\end{eqnarray*}
-Note that the quadratic term does not contribute to the total force and steady-state 
-velocity terms, but it does change the fluid flow, 
-the electric potential and the ionic concentration.
-
-The cubic terms $\bx_3$ are computed by solving a linear PDE system 
-with a right-hand side determined by the linear terms $\bx_1$ and the quadratic terms $\bx_2$:
-\begin{eqnarray*}
-\varPhi_3 &=& \cos\theta \left(\frac{15 \cU_1\alpha}{64} + \frac{3}{32}\right) - \frac{3 \cU_1\alpha {\cos}^3\theta}{32} - \frac{\cos\theta \left( - 183 {\cU_1}^2\alpha^2 + 839 \cU_1\alpha + 470\right)}{2560 r^2} \\
-&&+ \frac{3 \cos\theta \left(5 \cU_1\alpha - 6 {\cos^2\theta} - 4 \cU_1\alpha {\cos^2\theta} + 4\right)}{64 r^3} + \frac{\left(2 \cU_1\alpha - 1\right) \left(\cos\theta - 3 {\cos}^3\theta\right)}{64 r^5}
-\\ 
-&&- \frac{\left(3 \cos\theta - 5 {\cos}^3\theta\right) \left( - \frac{19 {\cU_1}^2\alpha^2}{5120} + \frac{97 \cU_1\alpha}{5120} + \frac{3 \cU_2\alpha}{320} + \frac{21}{1280}\right)}{r^4} + \frac{{\cos}^3\theta \left(\frac{15 \cU_1\alpha}{64} + \frac{3}{32}\right)}{r^2} \\
-&&+ \frac{{\cos}^3\theta \left(\frac{\cU_1\alpha}{64} + \frac{3}{64}\right)}{r^6},
-\\
-C_3 &=&
-\frac{3 {{\cU_1}}^2\alpha^2 {\cos^3\theta}}{32} + \frac{\cos\theta \left(797 {{\cU_1}}^2\alpha^2 + 419 {\cU_1}\alpha - 512 {\cU_2}\alpha + 174\right)}{2560 r^2} \\
-&&- \frac{\left(3 \cos\theta - 5 {\cos^3\theta}\right) \left(\frac{59 {{\cU_1}}^2\alpha^2}{5120} + \frac{103 {\cU_1}\alpha}{5120} + \frac{69 {\cU_2}\alpha}{320} + \frac{3}{1280}\right)}{r^4} \\
-&&- \frac{3\alpha \cos\theta \left( - 8\alpha {{\cU_1}}^2 {\cos^2\theta} + 7\alpha {{\cU_1}}^2 + 2 {\cU_1} + 32 {\cU_2} {\cos^2\theta} - 32 {\cU_2}\right)}{128 r^3} - \frac{3 {\cU_1}\alpha \cos\theta \left(5 {\cU_1}\alpha + 2\right)}{64} \\
-&&+ \frac{\alpha \left(\cos\theta - 3 {\cos^3\theta}\right) \left(5\alpha {{\cU_1}}^2 + 2 {\cU_1} + 16 {\cU_2}\right)}{128 r^5} + \frac{{{\cU_1}}^2\alpha^2 {\cos^3\theta}}{32 r^6} - \frac{3 {\cU_1}\alpha {\cos^3\theta} \left(5 {\cU_1}\alpha + 2\right)}{64 r^2},
-\\
-\Psi_3 &=&
-r^2 {\sin^2\theta} \left(\frac{{\cW_2}}{15} - \frac{{\cW_1}}{3} + \frac{209}{3360}\right) 
- - \frac{{\sin^2\theta} \left(\frac{5 {\cW_2}}{3} - \frac{{\cW_1}}{3} + \frac{35}{264}\right)}{r}
-\\ && + \frac{{\sin^4\theta} \left(2 {\cW_2} + \frac{761}{5632}\right)}{r} - \frac{{\sin^2\theta} \left(1848 r^6 {\sin^2\theta} - 2079 r^3 {\sin^2\theta} + 924 r^3 - 7 {\sin^2\theta} + 10\right)}{19712 r^5}
-\\ && + \frac{\left(\frac{2 {\cW_2}}{5} + \frac{829}{28160}\right) \left(4 {\sin^2\theta} - 5 {\sin\theta}^4\right)}{r^3} + \frac{{\sin^2\theta} \left(\frac{{\cU_1}\alpha}{16} - \frac{1}{8}\right) \left(2 r^3 - 3 r^2 + 1\right)}{4 r},
-\\
-\cW_1 &=& \frac{69}{512 \left(\sqrt{\gamma} + 1\right)} - \frac{1407\alpha^2 {\log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}^3}{1280} - \frac{123 \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{1280} - \frac{27}{512 {\left(\sqrt{\gamma} + 1\right)}^2} \\ && -
-\frac{1899\alpha {\log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}^2}{2560} - \frac{\alpha \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right) \left(\frac{81}{16 \left(\sqrt{\gamma} + 1\right)} - \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right) \left(\frac{27\alpha \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{4} + \frac{27}{8}\right)\right)}{320} \\ && +
-\frac{21\alpha \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{128 \left(\sqrt{\gamma} + 1\right)},
-\\
-\cW_2 &=& \frac{9 \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{256} + \frac{21\alpha^2 {\log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}^3}{64} - \frac{27}{512 \left(\sqrt{\gamma} + 1\right)} - \frac{27}{512 {\left(\sqrt{\gamma} + 1\right)}^2}
- + \frac{15\alpha {\log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}^2}{64} 
-\\ && 
-- \frac{297\alpha \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{1024 \left(\sqrt{\gamma} + 1\right)}.
-\end{eqnarray*}
-
-The cubic solution satisfies the $\lim_{r\rightarrow\infty}C_3 = 0$ boundary condition, 
-when $\alpha\cU_1 = 0$.
-
-The steady-state velocity can be expanded using odd powers of $\beta$:
-\begin{eqnarray*}
-\cU(\beta, \gamma) &=& \cU_1(\gamma) \beta + \cU_3(\gamma) \beta^3.
-\end{eqnarray*}
-
-The linear and the cubic velocity terms (for $\alpha = 0$) are then
-\begin{eqnarray*}
-\cU_1(\gamma) &=& 2 \log \pars{\frac{1 + \gamma^{-\frac{1}{2}}}{2}}, \\
-\cU_3(\gamma) &=& \frac{31}{320(\sqrt\gamma + 1)} - \frac{9}{320(\sqrt\gamma + 1)^2} + \frac{1}{1680} - \frac{11}{160} \log \pars{\frac{1 + \gamma^{-\frac{1}{2}}}{2}}.
-\end{eqnarray*}
-
-Note that, for $\gamma = 1$, the linear term vanishes and the velocity leading term is $O(\beta^3)$:
-\begin{eqnarray*}
-\cU(\beta) = \frac{1129}{26880}\beta^3.
-\end{eqnarray*}
-
-Note that a $\cU = 0$ solution may exist for $\beta_c \ne 0$ and $\alpha = 0$, 
-if it satisfies:
-\begin{eqnarray*}
-\beta_c^2 = -\frac{\cU_1(\gamma)}{\cU_3(\gamma)}.
-\end{eqnarray*}
-For $\gamma = 1 + \eps$, where $0 < \eps \ll 1$:
-\begin{eqnarray*}
-\beta_c \approx \sqrt{-\frac{\cU_1'(1) \eps}{\cU_3(1)}} = 
- \sqrt{\frac{13440 \eps}{1129}} \approx 3.45 \sqrt{\eps}.
-\end{eqnarray*}
-However, for $\gamma \gg 1$, we have:
-\begin{eqnarray*}
-\beta_c =  \pars{\frac{11}{320} + \frac{1}{1680 \log 4}}^{-\frac{1}{2}} \approx 5.36.
-\end{eqnarray*}
-
-The cubic term becomes dominant for small $\beta$ when $\gamma \approx 1$.
-
-\end{appendix}
-
 \bibliographystyle{elsarticle-num}

### 2012-04-02 notes/article/main.tex
Work on article

@@
 
-\usepackage{setspace}\doublespacing
+%\usepackage{setspace}\doublespacing
 
@@
 \begin{abstract}
+A numerical solver for the simulation of ion-exchanging particles migration in an
+electrolyte solution is presented. The electrokinetic transport process is
+described by a nonlinear partial differential equation system, 
+as well as nonlinear boundary conditions.
+The nonlinear system is discretized and solved iteratively using Newton's method.
+An asymptotic analytical solution is derived for the validation of the solver. 
+The numerical results are compared to the asymptotic solutions, and good correspondence is achieved.
 \end{abstract}
@@
 \begin{keyword}
-numerical, solver, electrokinetics, nonlinear
+CFD \sep electrokinetics \sep asymptotics
 \end{keyword}
@@
 Electrokinetic theory describes the dynamics of charged particles
-in ionic fluids \cite{kirby2010book}.
+in ionic fluids \cite{masliyah2005book,kirby2010book}.
 When a particle acquires surface charge, a layer
@@
 This interesting regime has not yet been explored.
+
 Recently, it has been conceived that such type of dynamics
@@
 \cite{howse2007self,paxton2004catalytic,pumera2010electrochemically}.
+
 However, since the model for these electrokinetic
@@
 phenomena that have been observed experimentally.
+One such phenomenon is nonlinear electrokinetic vortex flow (as shown in Figure \ref{fig:Granule}), 
+which can useful for microfluidic mixing applications \cite{wang2004mix, ben2002vortex},
+
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=0.4\textwidth]
+            {figs/vortex.eps}
+        \caption{A micro-vortex electrokinetic flow around a 1 mm spherical ion-exchanger granule. }
+        \label{fig:Granule}
+    \end{center}
+\end{figure}
 
@@
 \\ 
-&&- \frac{\left(3 \cos\theta - 5 {\cos}^3\theta\right) \left( - \frac{19 {\cU_1}^2\alpha^2}{5120} + \frac{97 \cU_1\alpha}{5120} + \frac{3 \cU_2\alpha}{320} + \frac{21}{1280}\right)}{r^4} + \frac{{\cos}^3\theta \left(\frac{15 \cU_1\alpha}{64} + \frac{3}{32}\right)}{r^2} \\
-&&+ \frac{{\cos}^3\theta \left(\frac{\cU_1\alpha}{64} + \frac{3}{64}\right)}{r^6},
+&&- \frac{\left(3 \cos\theta - 5 {\cos}^3\theta\right)}{r^4} 
+\left( - \frac{19 {\cU_1}^2\alpha^2}{5120} + \frac{97 \cU_1\alpha}{5120} + 
+\frac{3 \cU_2\alpha}{320} + \frac{21}{1280}\right) \\
+&& + \frac{{\cos}^3\theta}{r^2} \left(\frac{15 \cU_1\alpha}{64} + \frac{3}{32}\right)  
++ \frac{{\cos}^3\theta}{r^6} \left(\frac{\cU_1\alpha}{64} + \frac{3}{64}\right),
 \\
@@
 \frac{3 {{\cU_1}}^2\alpha^2 {\cos^3\theta}}{32} + \frac{\cos\theta \left(797 {{\cU_1}}^2\alpha^2 + 419 {\cU_1}\alpha - 512 {\cU_2}\alpha + 174\right)}{2560 r^2} \\
-&&- \frac{\left(3 \cos\theta - 5 {\cos^3\theta}\right) \left(\frac{59 {{\cU_1}}^2\alpha^2}{5120} + \frac{103 {\cU_1}\alpha}{5120} + \frac{69 {\cU_2}\alpha}{320} + \frac{3}{1280}\right)}{r^4} \\
+&&- \left(\frac{59 {{\cU_1}}^2\alpha^2}{5120} + \frac{103 {\cU_1}\alpha}{5120} + \frac{69 {\cU_2}\alpha}{320} + \frac{3}{1280}\right)\frac{\left(3 \cos\theta - 5 {\cos^3\theta}\right)}{r^4} \\
 &&- \frac{3\alpha \cos\theta \left( - 8\alpha {{\cU_1}}^2 {\cos^2\theta} + 7\alpha {{\cU_1}}^2 + 2 {\cU_1} + 32 {\cU_2} {\cos^2\theta} - 32 {\cU_2}\right)}{128 r^3} - \frac{3 {\cU_1}\alpha \cos\theta \left(5 {\cU_1}\alpha + 2\right)}{64} \\
@@
 r^2 {\sin^2\theta} \left(\frac{{\cW_2}}{15} - \frac{{\cW_1}}{3} + \frac{209}{3360}\right) 
- - \frac{{\sin^2\theta} \left(\frac{5 {\cW_2}}{3} - \frac{{\cW_1}}{3} + \frac{35}{264}\right)}{r}
+ - \frac{{\sin^2\theta}}{r} \left(\frac{5 {\cW_2}}{3} - \frac{{\cW_1}}{3} + \frac{35}{264}\right)
 \\ && + \frac{{\sin^4\theta} \left(2 {\cW_2} + \frac{761}{5632}\right)}{r} - \frac{{\sin^2\theta} \left(1848 r^6 {\sin^2\theta} - 2079 r^3 {\sin^2\theta} + 924 r^3 - 7 {\sin^2\theta} + 10\right)}{19712 r^5}
-\\ && + \frac{\left(\frac{2 {\cW_2}}{5} + \frac{829}{28160}\right) \left(4 {\sin^2\theta} - 5 {\sin\theta}^4\right)}{r^3} + \frac{{\sin^2\theta} \left(\frac{{\cU_1}\alpha}{16} - \frac{1}{8}\right) \left(2 r^3 - 3 r^2 + 1\right)}{4 r},
+\\ && + \frac{\left(\frac{2 {\cW_2}}{5} + \frac{829}{28160}\right) \left(4 {\sin^2\theta} - 5 {\sin^4\theta}\right)}{r^3} + \frac{{\sin^2\theta} \left(\frac{{\cU_1}\alpha}{16} - \frac{1}{8}\right) \left(2 r^3 - 3 r^2 + 1\right)}{4 r},
 \\
@@
 Moreover, two interesting phenomena (cubic regime and downstream vortex) were predicted
-using the numerical results, and later verified using asymptotic expansion of the
+using the numerical results, and were verified using asymptotic expansion of the
 nonlinear system.

### 2012-08-26 notes/work/ch01.tex
Review.
Add electrophoresis theory to notes.

@@
 closed-form linear asymptotic solution has been developed for
-spherical ion-exchanging particles and weak electric field in an
-axisymmetric setting \cite{yariv2010migration} but it is hard to extend this
+spherical particles and weak electric field in an
+axisymmetric setting \cite{yariv2010migration, schnitzer2012surface} but it is hard to extend this
 analytic solution to more general systems. Once the electric field
@@
 drug-delivery systems and useful nanomachinery 
-\cite{pumera2010electrochemically,paxton2004catalytic,howse2007self}.
+\cite{howse2007self,paxton2004catalytic,pumera2010electrochemically}.
 However, since the analytic model for these electrokinetic
@@
 
-Spatial coordinates $\br$ are normalized by $a^*$ (the characteristic size of the ion-exchanger).
+Spatial coordinates $\br$ are normalized by $a^*$ (the characteristic size of the particle).
 
@@
 \end{eqnarray}
-where $D^*_\pm \approx D^*$ is the ionic diffusivity.
+where $D^*$ is the ionic diffusivity.
 
@@
 \begin{eqnarray}
-(c^*_+ - c^*_-) z F^* &=& -\eps^* \Laplacian \varphi^*,
+(c^*_+ - c^*_-) z e^* &=& -\eps^* \Laplacian \varphi^*,
 \end{eqnarray}
@@
 \begin{eqnarray}
-c_+ - c_- &=& -\frac{\eps^* \varphi^*}{z F^* c^* (a^*)^2} \Laplacian \varphi = 
--\delta^2 \Laplacian \varphi,
+c_+ - c_- &=& -\frac{\eps^* \varphi^*}{z e^* c^* (a^*)^2} \Laplacian \varphi = 
+-2\delta^2 \Laplacian \varphi,
 \\
-\delta^2 &=& \frac{\eps^* \varphi^*}{c^* F^* z (a^*)^2} = 
+\delta^2 &=& \frac{\eps^* \varphi^*}{2c^* e^* z (a^*)^2} = 
 \pars{\frac{\delta^*}{a^*}}^2.
@@
 \begin{eqnarray}
-\delta^2 \Laplacian \varphi &=& -2q.
+\delta^2 \Laplacian \varphi &=& -q.
 \end{eqnarray}
@@
 An constant electric field $\bE$ is applied to the system, such that $|\bE| = \beta$.
-The ion-exchanger will acquire a non-zero steady-state velocity $\cU$, which is
+The particle will acquire a non-zero steady-state velocity $\cU$, which is
 a function of the applied field, and is not known a priori.
@@
 
-We consider a spherical ion-exchanger. 
+We consider a spherical particle. 
 At its surface $\mathcal{S}$ (defined at $r=1$ with normal $\bn = \brhat$), 
-we have zero slip, anion impermeability, cation selectivity (with fast Butler-Volmer kinetics)
-and high conductance of the particle (yielding uniform electric potential):
+we have zero slip and ion impermeability.
 \begin{eqnarray}
 \bv & = & \bzero, \\
-\bn \cdot \bj_- & = & 0, \\
-\bn \cdot \bj_+ & = & k (1 - c_+/\gamma) \Rightarrow c_+ \rightarrow \gamma, \\
-\varphi & = & \cV.
+\bn \cdot \bj_\pm & = & 0.
 \end{eqnarray}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Separation of scales}
+\subsection{Bulk-scale equations}
 When $\delta \ll 1$, 
@@
 
-\subsubsection  {Bulk-scale equations}
 The Nernst-Planck equations above for the fluid bulk (outside
@@
 
-\subsubsection{Debye-scale effective boundary conditions}
+\subsection{Debye-scale effective boundary conditions}
+The effective boundary conditions depend on the specific physical and chemical properties 
+of the particle. We consider the following scenarios:
+
+\subsubsection{Inert particle}
+
 We define the scaled coordinate $\rho$ (normal to ion-exchanger surface), where $\delta \ll 1$:
@@
 
+Due to ion impermeability and radial flux continuity:
+\begin{eqnarray}
+  \br \cdot \bj_\pm = -\deriv{c_\pm}{r} \mp c_\pm \deriv{\varPhi}{r} &=& 0, \\
+-\deriv{C}{r} \mp C \deriv{\varPhi}{r} &=& 0, \\
+\deriv{C}{r} = \deriv{\varPhi}{r} &=& 0.
+\end{eqnarray}
+
+Using the derivation in Appendix \ref{append:slip} and the fact that $V_r = 0$ 
+on the boundary, the slip condition can be written using the surface
+gradient operator:
+\begin{eqnarray}
+\bV &=& 
+\zeta \cdot \bnabla_\mathcal{S} \varPhi 
++ 2\log\pars{1-\tanh^2\frac{\zeta}{4}} \cdot \bnabla_\mathcal{S} \log C, \\
+\bnabla_\mathcal{S} &=& \pars{\tI - \bn\bn} \bnabla.
+\end{eqnarray}
+
+\subsubsection{Ion-exchanger}
+
 Due to cation selectivity, $c_+|_{\rho=0} = \gamma$.
@@
 
-Using the derivation in Appendix \ref{append:slip} and the fact that $V_r = 0$ 
-on the boundary, the slip condition can be written using the surface
-gradient operator:
+\subsubsection{Highly charged particle}
 \begin{eqnarray}
-\bV &=& 
-\zeta \cdot \bnabla_\mathcal{S} \varPhi 
-+ 2\log\pars{1-\tanh^2\frac{\zeta}{4}} \cdot \bnabla_\mathcal{S} \log C, \\
-\bnabla_\mathcal{S} &=& \pars{\tI - \bn\bn} \bnabla.
+ \deriv{C}{r} + C \deriv{\varPhi}{r} &=& 0, \\
+ \deriv{C}{r} - \mbox{Du} \Laplacian_s (\varPhi - \log C) &=& 0.
 \end{eqnarray}

### 2012-09-08 notes/work/ch01.tex
LaTeX

@@
 can be very useful in transporting and manipulating micro-
-and nanoscale objects for many nanotechnology applications,
-such as the self-assembly of superstructures, roving sensors, 
-drug-delivery systems and useful nanomachinery 
-\cite{howse2007self,paxton2004catalytic,pumera2010electrochemically}.
+and nanoscale objects for many nanotechnology applications
+\cite{howse2007self,paxton2004catalytic,pumera2010electrochemically, nischang2007, leinweber2004}.
 However, since the analytic model for these electrokinetic
@@
 \pars{\frac{\delta^*}{a^*}}^2.
+\end{eqnarray}
+
+The dimensional boundary condition for $\mathbf{D}^* = \eps^*\mathbf{E}^*$ for a charged surface
+with surface charge density $\sigma^*$ is
+\begin{eqnarray}
+\bn \cdot \pars{\eps^*\mathbf{E}^* - \eps^*_s\mathbf{E}^*_s} &=& \sigma^*,
+\end{eqnarray}
+and after nondimensionalization by 
+normalizing the surface charge using $\sigma^* = \eps^* \varphi^* / a^* \delta$
+and $\gamma = \eps^*_s / \eps^*$, yields:
+\begin{eqnarray}
+-\deriv{\varphi}{n} + \gamma \deriv{\varphi_s}{n} &=& \delta^{-1} \sigma.
 \end{eqnarray}
@@
 
+\subsubsection{Highly charged particle}
+Following the derivation at \cite{schnitzer2012surface}, the boundary conditions at a spherical 
+particle with high surface charge, $\sigma = \delta^{-1} \text{Bi}$ 
+(where $\text{Bi} = O(1)$ is the Bikerman number):
+\begin{eqnarray}
+ \deriv{C}{r} + C \deriv{\varPhi}{r} &=& 0, \\
+ \deriv{C}{r} - \mbox{Du} \Laplacian_s (\varPhi - \log C) &=& 0, \\
+ \bV &=& 4 \log 2 \bnabla_\mathcal{S} + \zeta \bnabla_\mathcal{S} \pars{\varPhi -\log C}, \\
+ \zeta &=& \bar{\zeta} - \log C , \\
+ \bar\zeta &=& 2 \log \sigma.
+\end{eqnarray}
+
 \subsubsection{Ion-exchanger}
@@
 Without loss of generality, 
-we assume that $\cV = -\log\gamma$, thus $\zeta = -\log\gamma-\varPhi$:
+we assume that $\cV = -\log\gamma$, thus $\zeta = -\log\gamma-\varPhi = \log (C/\gamma)$:
 \begin{eqnarray}
@@
 
-\subsubsection{Highly charged particle}
+The slip velocity derivation is the same as for the inert particle:
 \begin{eqnarray}
- \deriv{C}{r} + C \deriv{\varPhi}{r} &=& 0, \\
- \deriv{C}{r} - \mbox{Du} \Laplacian_s (\varPhi - \log C) &=& 0.
+\bV &=& 
+\zeta \cdot \bnabla_\mathcal{S} \varPhi 
++ 2\log\pars{1-\tanh^2\frac{\zeta}{4}} \cdot \bnabla_\mathcal{S} \log C. \\
 \end{eqnarray}

### 2012-09-08 notes/work/ch02.tex
Add more figures
Review.
LaTeX

--- 2012-01-21 notes/work/ch02.tex
@@
 System variable $\bx$ is defined as the concatenation $[\,\varPhi, C, V_r, V_\theta, P\,]$,
-taking only values in the interior of the problem domain grid.
+taking values in the interior of the problem domain grid and on the ``ghost'' points.
 Thus, each problem variable can be computed by applying an appropriate projection operator on $\bx$:
@@
 
-The extended variables $\tilde X$ (including ``ghost'' point values) 
-are computed by applying the following nonlinear operators:
-\begin{eqnarray}
-\tilde{\varPhi} &=& \cB_\varPhi(\varPhi, C; \beta), \\
-\tilde{C} &=& \cB_C(C, \varPhi), \\
-\tilde{V_r} &=& \cB_{V_r}(V_r; \cU), \\
-\tilde{V_\theta} &=& \cB_{V_\theta}(V_\theta, C, \varPhi; \cU, \gamma), \\
-\tilde{P} &=& P.
-\end{eqnarray}
-The extended system variable can be written as $\tilde{\bx} = \cB(\bx)$, 
-where $\cB$ is the ``ghost'' point extension operator (derived using boundary conditions)
-so the concatenated equations of the system (as described above) can be written 
-as a non-linear operator $\cE(\tilde\bx) = \bzero$ acting on the extended system variable 
-$\tilde{\bx}$, where $\cE$ is the conservation equations operator 
-(derived by concatenation of the system equations).
-
-The problem can be cast as the following non-linear system:
-\begin{eqnarray}
-\bzero = \cE (\tilde{\bx}) = \cE (\cB (\bx)) = \cO(\bx)
-\end{eqnarray}
- where $\cO = \cE \circ \cB$.
+The concatenated equations of the system (as described above) can be written 
+as a non-linear operator $\cO(\bx) = \bzero$ acting on the system variable 
+$\bx$, where $\cO$ is the concatenation of system equations operator 
+(derived by concatenation of the system equations) together with
+boundary conditions equations operators.
 
@@
 
-$F_\imath = \bF \cdot \ui$ is computed by using the mid-point quadrature method:
+$F_\imath = \bF \cdot \ui$ is computed by using the mid-point quadrature rule:
 \begin{eqnarray}

### 2012-09-08 notes/work/ijnam.tex
LaTeX

--- 2012-04-02 notes/article/main.tex
@@
-\documentclass[final]{elsarticle}
-
-%\usepackage{setspace}\doublespacing
-
+\documentclass[10pt]{ijnam}
+\hsize=5.5 true in
+\textheight=8.4 true in
+\topmargin 1in
+
+%% information for the editor
+\def\currentvolume{1}
+\def\currentissue{1}
+\def\currentyear{2004}
+\def\month{October}
+\pagespan{1}{18}
+\copyrightinfo{2012}{} % copyright year
+
+%% please put your definitions into mydef.sty. Examples can be found in this
+%% file.
 \usepackage{graphicx}
@@
 
-\journal{Journal of Computational Physics}
-
+%\usepackage{mydef}
+
+%%%%%%%%%%%%%%%
 \begin{document}
-
-\begin{frontmatter}
-
-\title{Numerical and asymptotic solution of nonlinear electrokinetic phenomena}
-\author[cs]{Roman Zeyde}
-\author[cs]{Irad Yavneh}
-\author[math]{Ehud Yariv}
-
-\address[cs]{Department of Computer Science, Technion -- Israel Institute of Technology, 
-Haifa 32000, Israel}
-\address[math]{Department of Mathematics, Technion -- Israel Institute of Technology, 
-Haifa 32000, Israel}
-
-\begin{abstract}
-A numerical solver for the simulation of ion-exchanging particles migration in an
+%%%%%%%%%%%%%%%%
+
+\title{Numerical and analytical solution of nonlinear electro-kinetic phenomena}
+
+% author and address
+\author{Roman Zeyde \and Irad Yavneh}
+\address{Department of Computer Science, Technion -- Israel Institute of Technology, Haifa 32000, Israel}
+\email{romanz@cs.technion.ac.il \and irad@cs.technion.ac.il}
+
+% two authors have the same address
+\author{Ory Schnitzer \and Ehud Yariv}
+\address{Department of Mathematics, Technion -- Israel Institute of Technology, Haifa 32000, Israel}
+\email{oschnitt@gmail.com \and udi@math.technion.ac.il}
+
+% dedication
+\dedicatory{This paper is dedicated to our authors}
+
+% communicated
+\commby{Hilbert}
+
+% Received by the editors ?
+\date{January 1, 2004 and, in revised form, March 22, 2004.}
+
+% it is suggested to put it in Acknowledgments
+\thanks{This research was supported by ???}
+
+\subjclass[2000]{35R35, 49J40, 60G40}
+
+\abstract{A numerical solver for the simulation of ion-exchanging particles migration in an
 electrolyte solution is presented. The electrokinetic transport process is
@@
 An asymptotic analytical solution is derived for the validation of the solver. 
-The numerical results are compared to the asymptotic solutions, and good correspondence is achieved.
-\end{abstract}
-
-\begin{keyword}
-CFD \sep electrokinetics \sep asymptotics
-\end{keyword}
-
-\end{frontmatter}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The numerical results are compared to the asymptotic solutions, and good correspondence is achieved.}
+
+\keywords{CFD, electrokinetics, asymptotics}
+
+\maketitle
+
 \section{Introduction} \label{sec:intro}
@@
 dynamics can be found \cite{yariv2010asymptotic}.
-
 \begin{figure}[htbp]
@@
 phenomena that have been observed experimentally.
-One such phenomenon is nonlinear electrokinetic vortex flow (as shown in Figure \ref{fig:Granule}), 
+One such phenomenon is nonlinear electrokinetic vortex flow, 
 which can useful for microfluidic mixing applications \cite{wang2004mix, ben2002vortex},
-
-\begin{figure}[htbp]
-    \begin{center}
-        \includegraphics[width=0.4\textwidth]
-            {figs/vortex.eps}
-        \caption{A micro-vortex electrokinetic flow around a 1 mm spherical ion-exchanger granule. }
-        \label{fig:Granule}
-    \end{center}
-\end{figure}
 
@@
 (using the Einstein relation for the electric mobility, $\mu_q^* = D^* / k_B^* T^*$):
-\begin{eqnarray*}
+\begin{eqnarray}
 \bj^*_\pm &=& 
 -D^* \bnabla c^*_\pm + \bv^* c^*_\pm \mp \frac{z e^* D^*}{k_B^* T^*} c^*_\pm \bnabla \varphi^*,
-\end{eqnarray*}
+\end{eqnarray}
 where $D^*$ is the ionic diffusivity.
@@
 The electric potential $\varphi$ is normalized by the thermal voltage:
-\begin{eqnarray*}
+\begin{eqnarray}
 \varphi^* &=& \frac{k_B^* T^*}{z e^*} = \frac{R^* T^*}{z F^*},
-\end{eqnarray*}
+\end{eqnarray}
 where $R^* = k_B^* N_A$ and $F^* = e^* N_A$ is the Faraday number.
@@
 The dimensional Stokes equations are given by:
-\begin{eqnarray*}
+\begin{eqnarray}
 \bnabla \cdot \bv &=& 0, \\
 -\bnabla p^* + \mu^* \bLaplacian \bv^* + \eps^* \Laplacian \varphi^* \bnabla \varphi^* &=& 0.
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 The nondimensional Nernst-Plank equation is then written as:
-\begin{eqnarray*}
+\begin{eqnarray}
 \bj_\pm &=& 
 -\bnabla c_\pm + \alpha \bv c_\pm \mp c_\pm \bnabla \varphi,
-\end{eqnarray*}
+\end{eqnarray}
 where $\alpha = {v^* a^*}/{D^*} = {\eps^* (\varphi^*)^2}/{\mu^* D^*}$ 
@@
 The dimensional Poisson equation can be written as:
-\begin{eqnarray*}
+\begin{eqnarray}
 (c^*_+ - c^*_-) z F^* &=& -\eps^* \Laplacian \varphi^*,
-\end{eqnarray*}
+\end{eqnarray}
 and after nondimensionalization, is given by:
-\begin{eqnarray*}
+\begin{eqnarray}
 c_+ - c_- &=& -\frac{\eps^* \varphi^*}{z F^* c^* (a^*)^2} \Laplacian \varphi = 
@@
 \pars{\frac{\delta^*}{a^*}}^2.
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 The ionic fluxes are given by ion diffusion, electrostatic forces and ion advection by the fluid:
-\begin{eqnarray*}
+\begin{eqnarray}
   \bj_\pm &=& -\bnabla c_\pm \mp c_\pm \bnabla \varphi + \alpha \bv c_\pm,
-\end{eqnarray*}
+\end{eqnarray}
 
 Due to conservation of ions, the fluxes are divergence-free:
-\begin{eqnarray*}
+\begin{eqnarray}
 \bnabla \cdot \bj_\pm &=& 0.
-\end{eqnarray*}
+\end{eqnarray}
 These equation may be re-written by using the following transformations:
-\begin{eqnarray*}
+\begin{eqnarray}
   c &=& \frac{c_+ + c_-}{2},\\
   q &=& \frac{c_+ - c_-}{2}.
-\end{eqnarray*}
+\end{eqnarray}
 Thus, salt and charge fluxes are defined by:
-\begin{eqnarray*}
+\begin{eqnarray}
   \bj &=& \frac{\bj_+ + \bj_-}{2} = -\bnabla c - q \bnabla \varphi + \alpha \bv c, \\
   \bi &=& \frac{\bj_+ - \bj_-}{2} = -\bnabla q - c \bnabla \varphi + \alpha \bv q,
-\end{eqnarray*}
+\end{eqnarray}
 and are divergence-free as well:
-\begin{eqnarray*}
+\begin{eqnarray}
 \bnabla \cdot \bj &=& 0, \\
 \bnabla \cdot \bi &=& 0. 
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 Mass conservation (due to constant fluid density) reads:
-\begin{eqnarray*}
+\begin{eqnarray}
 \bnabla \cdot \bv &=& 0.
-\end{eqnarray*}
+\end{eqnarray}
 Momentum conservation (force balance) reads:
-\begin{eqnarray*}
+\begin{eqnarray}
 \Laplacian \bv - \bnabla p + \bnabla \varphi \Laplacian \varphi &=& 0.
-\end{eqnarray*}
+\end{eqnarray}
 Finally, free charge density is governed by the Poisson equation:
-\begin{eqnarray*}
+\begin{eqnarray}
 \delta^2 \Laplacian \varphi &=& -2q.
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 and ambient ionic concentrations:
-\begin{eqnarray*}
+\begin{eqnarray}
 -\bv &\rightarrow& \cU \ui, \\
@@
 c_\pm &\rightarrow& 1.
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 $\bn \cdot \bj_+ = k (1 - c_+/\gamma)$, where $k \rightarrow \infty$):
-\begin{eqnarray*}
+\begin{eqnarray}
 \varphi & = & \cV, \\
@@
 c_+ &=& \gamma, \\
-\end{eqnarray*}
+\end{eqnarray}
 where $\gamma$ is the ratio between the cationic concentration on the surface and the cationic
@@
 the boundary layer), using bulk variables denoted by uppercase letters, read:
-\begin{eqnarray*}
+\begin{eqnarray}
   Q & = & 0, \\
@@
 \bI &=& -C \bnabla \varPhi.
-\end{eqnarray*}
+\end{eqnarray}
 Because the flow is incompressible ($\bnabla \cdot V = 0$), 
@@
 \item Salt conservation in macroscale equation:
-\begin{eqnarray*} \label{eq:salt}
+\begin{eqnarray} \label{eq:salt}
 \bnabla \cdot \bJ = \Laplacian C - \alpha \bV \cdot \bnabla C = 0. 
-\end{eqnarray*}
+\end{eqnarray}
 
 \item Charge conservation in macroscale equations:
-\begin{eqnarray*} \label{eq:charge}
+\begin{eqnarray} \label{eq:charge}
 \bnabla \cdot \bI = \bnabla \cdot \pars{ C \bnabla \varPhi } = 0.
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 The macroscale Stokes flow equations have the same form as the microscale equations:
-\begin{eqnarray*}  \label{eq:stokes}
+\begin{eqnarray}  \label{eq:stokes}
 \brc{rcc}{\bnabla \cdot \bV &=& 0, \\  
 \Laplacian \bV - \bnabla P + \bnabla \varPhi \Laplacian \varPhi &=& \bzero.}
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 the effective boundary conditions at the ion-exchanger surface are:
-\begin{eqnarray*}
+\begin{eqnarray}
 0 &=& \varPhi + \log C, \\
@@
 + 2\log\pars{1-\tanh^2\frac{\zeta}{4}} \cdot \bnabla_\mathcal{S} \log C,
-\end{eqnarray*}
+\end{eqnarray}
 where $\zeta = \cV - \varPhi = \log (C / \gamma)$ 
@@
 The stress tensor is composed of Newtonian and Maxwel stresses:
-\begin{eqnarray*}
+\begin{eqnarray}
 \tT &=& \bnabla \bV + (\bnabla \bV)^\dagger - P \tI
@@
 \bnabla \cdot \tT &=& \bzero.
-\end{eqnarray*}
+\end{eqnarray}
 The total force acting on the particle is computed by the following surface integral:
-\begin{eqnarray*}
+\begin{eqnarray}
 \bF &=& \oint_\mathcal{S} \tT \cdot \bnhat dA.
-\end{eqnarray*}
+\end{eqnarray}
 In steady state (constant particle drift velocity $\cU$), 
 the total force must be zero: 
-\begin{eqnarray*}
+\begin{eqnarray}
 \bF = \bzero.
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 The steady-state velocity is thus the solution to the nonlinear scalar equation
-\begin{eqnarray*}
+\begin{eqnarray}
 F(\beta, \cU) = 0,
-\end{eqnarray*}
+\end{eqnarray}
 which we solver by standard secant method.
@@
 The scalar gradient and the divergence can be written as:
-\begin{eqnarray*}
+\begin{eqnarray}
 \bnabla f &=& \deriv{f}{r}\brhat + \frac{1}{r}\deriv{f}{\theta}\bthetahat, \\
@@
                \frac{1}{r \sin\theta}\deriv{}{\theta}\pars{F_\theta \sin\theta}.
-\end{eqnarray*}
+\end{eqnarray}
 The scalar Laplacian can be written as:
-\begin{eqnarray*}
+\begin{eqnarray}
 \Laplacian f = \bnabla \cdot (\bnabla f)&=& 
@@
  \frac{1}{r^2 \sin\theta}\deriv{}{\theta}\pars{\sin\theta \deriv{f}{\theta}}.
-\end{eqnarray*}
+\end{eqnarray}
 The vector gradient can be written as:
-\begin{eqnarray*}
+\begin{eqnarray}
 \bnabla \bF &=& \deriv{F_r}{r} \brhat \brhat + \deriv{F_\theta}{r} \brhat \bthetahat + 
@@
 \frac{1}{r}\pars{\deriv{F_\theta}{\theta} + F_r} \bthetahat \bthetahat.
-\end{eqnarray*}
+\end{eqnarray}
 The vector Laplacian can be written as:
-\begin{eqnarray*}
+\begin{eqnarray}
 \bLaplacian \bF &=& 
@@
 \frac{2}{r^2}\deriv{F_r}{\theta}\right) \bthetahat.
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 a regular grid of size $n_r \times n_\theta$ is defined, with:
-\begin{eqnarray*}
+\begin{eqnarray}
 (r_i,\theta_j) &\in& [1, \infty) \times [0,\pi], \\ 
@@
 \theta_j &=& \Delta_\theta \cdot j,
-\end{eqnarray*}
+\end{eqnarray}
 where a logarithmic grid spacing has been chosen for $r$ and a uniform grid for $\theta$.
@@
 larger than $r_0$. Thus:
-\begin{eqnarray*}
+\begin{eqnarray}
 \Delta_r &=& \pars{R_{max}} ^ \frac{1}{n_r} - 1, \\
 \Delta_\theta &=& \frac{\pi}{n_\theta}.
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 $\Omega = [1, R_{max}] \times [0,\pi]$ into cells:
-\begin{eqnarray*}
+\begin{eqnarray}
 \bigcup_{ij}\Omega_{ij} &=& \Omega.
-\end{eqnarray*}
+\end{eqnarray}
 A specific cell $\Omega_{ij}$ and its center $(\bar{r}_i, \bar{\theta}_j)$ are defined by:
-\begin{eqnarray*}
+\begin{eqnarray}
 \Omega_{ij} &=& [r_{i-1}, r_{i}] \times [\theta_{j-1}, \theta_{j}], \\
@@
 \bar{\theta}_j &=& \frac{\theta_{j-1} + \theta_{j}}{2}.
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 using an all-centered grid:
-\begin{eqnarray*}
+\begin{eqnarray}
 \varPhi^h_{[i,j]} &=& \varPhi(\bar{r}_i, \bar{\theta}_j), \\
@@
 P^h_{[i,j]} &=& P(\bar{r}_i, \bar{\theta}_j).
-\end{eqnarray*}
+\end{eqnarray}
 \item $\bV$ is represented by its values at cell boundaries, using a staggered grid:
-\begin{eqnarray*}
+\begin{eqnarray}
 V_r^h{}_{[i,j]} &=& V_r(r_i, \bar{\theta}_j), \\
 V_\theta^h{}_{[i,j]} &=& V_\theta(\bar{r}_i, {\theta}_j).
-\end{eqnarray*}
+\end{eqnarray}
 \end{itemize}
@@
 Define the following discrete central difference operators:
-\begin{eqnarray*}
+\begin{eqnarray}
 \cD_r(f^h){}_{\left[i+\half,j\right]} &=& \frac{f^h_{\left[i+1,j\right]} - f^h_{\left[i,j\right]}}
@@
 					   {\theta_{\left[i,j+1\right]} - \theta_{\left[i,j\right]}}.
-\end{eqnarray*}
+\end{eqnarray}
 
 Define the following linear interpolation operators:
-\begin{eqnarray*}
+\begin{eqnarray}
 \cI_r(f^h)_{\left[i+\half,j\right]} &=& 
@@
   f^h_{\left[i,j\right]}.
-\end{eqnarray*}
+\end{eqnarray}
 
 The total flux of a cell is equal to zero ($\bnabla \cdot \boldsymbol{f} = 0$):
-\begin{eqnarray*}
+\begin{eqnarray}
 \frac{1}{r^2} \cD_r\pars{f^h_r r^2} + 
@@
 \cD_\theta\pars{f^h_\theta \cdot r \sin\theta}}{r^2 \sin\theta} = 0. 
-\end{eqnarray*}
+\end{eqnarray}
 
 Ion flux ($\bI = - C \bnabla \varPhi$) is discretized on grid cell boundaries:
-\begin{eqnarray*}
+\begin{eqnarray}
 I^h_r &=& -\cI_r(C^h) \cdot \cD_r(\varPhi^h), \\
 I^h_\theta &=& -\cI_\theta(C^h) \cdot \frac{\cD_\theta(\varPhi^h)}{r}.
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 (using upwind scheme $\mathcal{U}$ for numerical stability at large cell Peclet number):
-\begin{eqnarray*}
+\begin{eqnarray}
 J^h_r &=& -\cD_r(C^h) + \alpha V^h_r \cdot \mathcal{U}^{\bV^h}_r (C^h), \\
@@
  \mathcal{U}^{\bV^h}_\theta(C^h)[i,j] &=& C^h\left[i, j-\frac{\sign(V^h_\theta)}{2}\right]. 
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 linear interpolation is used for the Coulomb force and for vector Laplacian components.
-\begin{eqnarray*}
+\begin{eqnarray}
 F^h_r &=& -\cD_r(P^h) 
@@
 \frac{1}{r^2 \sin\theta} \cD_\theta\pars{\cD_\theta(f^h) \cdot \sin\theta}.
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 The boundary conditions at the ion-exchange boundary ($r=1$) are:
-\begin{eqnarray*}
+\begin{eqnarray}
 \cI_r(\varPhi^h) &=& -\cI_r(\log C^h), \\
@@
   \zeta^h &=& - \log \gamma - \cI_r(\varPhi^h).
-\end{eqnarray*}
+\end{eqnarray}
 The equations are discretized using ``ghost'' points outside the interior of the domain:
-\begin{eqnarray*}
+\begin{eqnarray}
  \varPhi^h_{[1/2, j]} = \frac{\varPhi^h_{[0,j]} + \varPhi^h_{[1,j]}}{2} &=& 
@@
 	\frac{\log C^h_{[1,j]} - \log C^h_{[0,j]}}{\Delta r}. 
-\end{eqnarray*}
+\end{eqnarray}
 By adding and subtracting the equations, we have:
-\begin{eqnarray*}
+\begin{eqnarray}
 \varPhi^h_{[0,j]} &=& -\log\brcs{C^h_{[1,j]}}, \\
@@
                      = -\log\gamma -\frac{\varPhi^h_{[0,j]} + \varPhi^h_{[1,j]}}{2}.
-\end{eqnarray*}
+\end{eqnarray}
 The slip condition can be written as:
-\begin{eqnarray*}
+\begin{eqnarray}
 V_r^h{}_{[0,j]} &=& 0, \\
@@
   V^h_\theta{}_{[0,j]} &=& 2 V^h_\theta{}_{[1/2, j]} - V^h_\theta{}_{[1,j]}.
-\end{eqnarray*}
+\end{eqnarray}
 
 For $\theta = 0$ and $\theta = \pi$, the ``ghost'' points are defined by symmetry considerations:
-\begin{eqnarray*} 
+\begin{eqnarray} 
 \brc{l}{
@@
 } 
-\end{eqnarray*}
+\end{eqnarray}
 
 Far away from the ion-exchange boundary ($r\rightarrow\infty$) we have:
-\begin{eqnarray*}
+\begin{eqnarray}
 \frac{\varPhi^h_{[n_r + 1, j]} - \varPhi^h_{[n_r, j]}}{\bar{r}_{n_r + 1} - \bar{r}_{n_r}} 
@@
 V_\theta^h{}_{[n_r + 1, j]} & = & \cU \sin\theta_j.
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 be applied, given an initial solution $\bx_0$:
-\begin{eqnarray*}
+\begin{eqnarray}
 \bzero = \cO(\bx_n + \Delta \bx_n) &\approx& \cO(\bx_n) + \bnabla \cO(\bx_n)\cdot\Delta\bx_n, \\
@@
 \bx_{n+1} &=& \bx_{n} + \Delta \bx_n. 
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 the asymptotic convergence is in general quadratic:
-\begin{eqnarray*}
+\begin{eqnarray}
 \|\bx_{n+1} - \bx_\infty\| \le k \|\bx_{n} - \bx_\infty\|^2.
-\end{eqnarray*}
+\end{eqnarray}
 Thus, when the initial guess is close enough to the solution, the solver
@@
 Thus, each problem variable can be computed by applying an appropriate projection operator on $\bx$:
-\begin{eqnarray*}
+\begin{eqnarray}
 X &=& \cP_X(\bx) \mbox{ for } X \in \left\{\varPhi, C, V_r, V_\theta, P\right\}.
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 are computed by applying the following nonlinear operators:
-\begin{eqnarray*}
+\begin{eqnarray}
 \tilde{\varPhi} &=& \cB_\varPhi(\varPhi, C; \beta), \\
@@
 \tilde{P} &=& P.
-\end{eqnarray*}
+\end{eqnarray}
 The extended system variable can be written as $\tilde{\bx} = \cB(\bx)$, 
@@
 The problem can be cast as the following nonlinear system (where $\cO = \cE \circ \cB$):
-\begin{eqnarray*}
+\begin{eqnarray}
 \cO(\bx) = \bzero.
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 aligned with $\ui$ and it vanishes iff $\ui \cdot \bF = 0$.
-\begin{eqnarray*}
+\begin{eqnarray}
 F_\imath = \ui \cdot \bF &=& 
@@
  \mathcal{S} &=& \{\br : \|\br\|_2 = 1\}.
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 If $\cO$ is linear, it can be represented by a matrix $L$, such that:
-\begin{eqnarray*}
+\begin{eqnarray}
 \cO(\bx) &=& L \bx, \\
 \bnabla\cO &=& L. 
-\end{eqnarray*}
+\end{eqnarray}
 Note that finite difference $\cD$, interpolation $\cI$ and 
@@
 represent pointwise application of $f$:
-\begin{eqnarray*}
+\begin{eqnarray}
 \cF(\bx) &=& [f(x_1); \ldots; f(x_n)], \\
 \bnabla\cF(\bx) &=& \diag\{f'(x_1), \ldots, f'(x_n)\}.
-\end{eqnarray*}
+\end{eqnarray}
 $f$ is defined and differentiated automatically using the MATLAB symbolic toolbox.
@@
 (that does not depend on $\bx$):
-\begin{eqnarray*}
+\begin{eqnarray}
 \mathcal{C}(\bx) &=& \bc, \\
 \bnabla\mathcal{C} &=& \bzero.
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 and multiplication, are defined as follows:
-\begin{eqnarray*}
+\begin{eqnarray}
 (\cO_1 \pm \cO_2)(\bx) &=& \cO_1(\bx) \pm \cO_2(\bx), \\
@@
                                   + \diag(\cO_1(\bx)) \bnabla\cO_2(\bx).
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 Given $N$ operators $\{\cO_i\}_{i=1}^N$, their concatenation $\cO$ is defined as:
-\begin{eqnarray*}
+\begin{eqnarray}
 \cO(\bx) &=& [\cO_1(\bx); \ldots; \cO_N(\bx)], \\
 (\bnabla\cO)(\bx) &=& [(\bnabla\cO_1)(\bx); \ldots; (\bnabla\cO_N)(\bx)].
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 $F_\imath = \bF \cdot \ui$ is computed by using the mid-point quadrature rule:
-\begin{eqnarray*}
+\begin{eqnarray}
 F_\imath &=& \sum_{i=1}^{n_\theta} f(\bar\theta_i) \cdot 
               2 \pi \sin\bar\theta_i \cdot \Delta\theta_i
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 This constraint yields an equation, whose solution is the steady-state velocity $\cU$:
-\begin{eqnarray*}
+\begin{eqnarray}
 F_\imath(\cU) &=& 0
-\end{eqnarray*}
+\end{eqnarray}
 This equation can be solved using a 1D root finding algorithm, e.g., the secant method:
-\begin{eqnarray*}
+\begin{eqnarray}
 \cU_{n+1} = \frac{F_\imath(\cU_{n})\cU_{n-1} - F_\imath(\cU_{n-1})\cU_{n}}
 {F_\imath(\cU_{n}) - F_\imath(\cU_{n-1})} \rightarrow \cU
-\end{eqnarray*}
+\end{eqnarray}
 The result $\cU$ is the 
@@
 \label{PDEs}
-\begin{eqnarray*}
+\begin{eqnarray}
 \bnabla \cdot \pars{C \bnabla \varPhi} &=& 0, \\
@@
 \bLaplacian \bV - \bnabla P + \Laplacian \varPhi \bnabla \varPhi &=& \bzero.
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 $\cV = -\log \gamma$, the boundary conditions at $r = 1$ are given by
-\begin{eqnarray*}
+\begin{eqnarray}
 \varPhi + \log C &=& \cV + \log \gamma = 0, \\
@@
 &=& 4\log\pars{\frac{1 + e^\frac{\zeta}{2}}{2}} \bnabla_S \varPhi.
-\end{eqnarray*}
+\end{eqnarray}
 
 The boundary conditions for $r \rightarrow \infty$ are given by
-\begin{eqnarray*}
+\begin{eqnarray}
 \bnabla \varPhi &=& -\beta \ui, \\
@@
 \bV &=& -\cU \ui,
-\end{eqnarray*}
+\end{eqnarray}
 and the total force acting on the particle is zero: $\bF = \bzero$.
@@
 The nonlinear system can be written as: 
-\begin{eqnarray*}
+\begin{eqnarray}
 \cO(\bx;\beta) &=& \bzero.
-\end{eqnarray*}
+\end{eqnarray}
 
 The solution to the nonlinear system can be expanded in a Taylor series in $\beta$.
-\begin{eqnarray*}
+\begin{eqnarray}
 \bx = \bx(\beta) &\approx& \sum_n \bx_n \beta^n.
-\end{eqnarray*}
+\end{eqnarray}
 
 All the variables are expanded around $\beta = 0$:
-\begin{eqnarray*}
+\begin{eqnarray}
 \varPhi &=& \beta \varPhi_1 + \beta^2 \varPhi_2 + \beta^3 \varPhi_3 + \ldots, \\
@@
 \Psi &=& \beta \Psi_1 + \beta^2 \Psi_2 + \beta^3 \Psi_3 + \ldots ,
-\end{eqnarray*}
+\end{eqnarray}
 where the velocity $\bV$ and pressure $P$ are computed from the streamfunction $\Psi$:
-\begin{eqnarray*}
+\begin{eqnarray}
 \bV &=& \bnabla \times \pars{\frac{\Psi}{r \sin\theta} \bphihat} 
@@
 - \frac{1}{r \sin\theta} \deriv{\Psi}{r} \bthetahat.
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 and arranged by powers of $\beta$:
-\begin{eqnarray*}
+\begin{eqnarray}
 \bzero = \cO(\bx) = \sum_k \cO_k(\bx_0, \ldots \bx_k) \beta^k
-\end{eqnarray*}
+\end{eqnarray}
 This can be rewritten as a system of equations:
-\begin{eqnarray*}
+\begin{eqnarray}
 \brc{rcl}{
@@
 }
-\end{eqnarray*}
+\end{eqnarray}
 Thus, the $O(\beta^k)$ term $\bx_k$ can be found recursively by solving 
@@
 For $\beta = 0$ (no electric field is applied), the steady-state solution is $\cU = 0$:
-\begin{eqnarray*}
+\begin{eqnarray}
 \varPhi_0(r,\theta) &=& 0, \\
@@
 P_0(r,\theta) &=& 0.
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 (as developed in \cite{yariv2010migration}):
-\begin{eqnarray*}
+\begin{eqnarray}
 \Laplacian \varPhi_1 &=& 0, \\
@@
 \bLaplacian \bV_1 - \bnabla P_1 &=& \bzero.
-\end{eqnarray*}
+\end{eqnarray}
 
 The first-order terms are given by
-\begin{eqnarray*}
+\begin{eqnarray}
 \varPhi &=& \beta \pars{\frac{1}{4r^2} - r}\cos\theta, \\
@@
 \bF &=& \bzero.
-\end{eqnarray*}
+\end{eqnarray}
 
 The slip velocity satisfies
-\begin{eqnarray*}
+\begin{eqnarray}
 \beta \cU_1 \frac{3}{2} \sin\theta =
@@
        =  2 \log \pars{\frac{1 + \gamma ^ {-\frac{1}{2}}}{2}}.
-\end{eqnarray*}
+\end{eqnarray}
 because $\varPhi_1 = -C_1 = -\frac{3}{4} \cos\theta$ on $r=1$
@@
 Note that, due to symmetry considerations, $\cU(\beta)$ is an anti-symmetric function:
-\begin{eqnarray*}
+\begin{eqnarray}
 \cU(-\beta) &=& -\cU(\beta).
-\end{eqnarray*}
+\end{eqnarray}
 Therefore, $\cU_2 = 0$ and the next velocity term is the cubic one:
-\begin{eqnarray*}
+\begin{eqnarray}
 \cU(\beta) &\approx& \beta \cU_1 + \beta^3 \cU_3 + O(\beta^5).
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 with a right-hand side determined by the linear terms $\bx_1$:
-\begin{eqnarray*}
+\begin{eqnarray}
 \varPhi_2 &=& \frac{\left(\frac{\cU_1\, \alpha}{32} - \frac{1}{16}\right)\, \left(3\, {\cos^2\theta} - 1\right)}{r^3} - \frac{3}{32\, r^4} - \frac{3\, {\sin^2\theta}\, \left(4\, r^3 - 1\right)}{32\, r^4} - \frac{3\, \cU_1\, \alpha - 6}{32\, r},
@@
 \bF_2 &=& \bzero, \\ \cU_2 &=& 0.
-\end{eqnarray*}
+\end{eqnarray}
 Note that the quadratic term does not contribute to the total force and steady-state 
@@
 with a right-hand side determined by the linear terms $\bx_1$ and the quadratic terms $\bx_2$:
-\begin{eqnarray*}
+\begin{eqnarray}
 \varPhi_3 &=& \cos\theta \left(\frac{15 \cU_1\alpha}{64} + \frac{3}{32}\right) - \frac{3 \cU_1\alpha {\cos}^3\theta}{32} - \frac{\cos\theta \left( - 183 {\cU_1}^2\alpha^2 + 839 \cU_1\alpha + 470\right)}{2560 r^2} \\
@@
 - \frac{297\alpha \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{1024 \left(\sqrt{\gamma} + 1\right)}.
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 The steady-state velocity can be expanded using odd powers of $\beta$:
-\begin{eqnarray*}
+\begin{eqnarray}
 \cU(\beta, \gamma) &=& \cU_1(\gamma) \beta + \cU_3(\gamma) \beta^3.
-\end{eqnarray*}
+\end{eqnarray}
 
 The linear and the cubic velocity terms (for $\alpha = 0$) are then
-\begin{eqnarray*}
+\begin{eqnarray}
 \cU_1(\gamma) &=& 2 \log \pars{\frac{1 + \gamma^{-\frac{1}{2}}}{2}}, \\
 \cU_3(\gamma) &=& \frac{31}{320(\sqrt\gamma + 1)} - \frac{9}{320(\sqrt\gamma + 1)^2} + \frac{1}{1680} - \frac{11}{160} \log \pars{\frac{1 + \gamma^{-\frac{1}{2}}}{2}}.
-\end{eqnarray*}
+\end{eqnarray}
 
 Note that, for $\gamma = 1$, the linear term vanishes and the velocity leading term is $O(\beta^3)$:
-\begin{eqnarray*}
+\begin{eqnarray}
 \cU(\beta) = \frac{1129}{26880}\beta^3.
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 if it satisfies:
-\begin{eqnarray*}
+\begin{eqnarray}
 \beta_c^2 = -\frac{\cU_1(\gamma)}{\cU_3(\gamma)}.
-\end{eqnarray*}
+\end{eqnarray}
 For $\gamma = 1 + \eps$, where $0 < \eps \ll 1$:
-\begin{eqnarray*}
+\begin{eqnarray}
 \beta_c \approx \sqrt{-\frac{\cU_1'(1) \eps}{\cU_3(1)}} = 
  \sqrt{\frac{13440 \eps}{1129}} \approx 3.45 \sqrt{\eps}.
-\end{eqnarray*}
+\end{eqnarray}
 However, for $\gamma \gg 1$, we have:
-\begin{eqnarray*}
+\begin{eqnarray}
 \beta_c =  \pars{\frac{11}{320} + \frac{1}{1680 \log 4}}^{-\frac{1}{2}} \approx 5.36.
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 For $\beta \ll 1$, the linear regime is dominant (for derivation, see \ref{app:linear}):
-\begin{eqnarray*}
+\begin{eqnarray}
 \cU = 2\log\pars{\frac{1 + \gamma^{-\frac{1}{2}}}{2}}\beta.
-\end{eqnarray*}
+\end{eqnarray}
 Thus, for $\gamma > 1$, the Debye layer has a positive space charge, corresponding to a negative
@@
 which can be approximated for small $|\zeta| \ll 1$ as:
-\begin{eqnarray*}
+\begin{eqnarray}
 V_\theta \approx \zeta \cdot \bnabla_S \varPhi.
-\end{eqnarray*} 
+\end{eqnarray} 
 This sign change creates a vortex at the downstream end of the ion-exchanger, 
@@
 
-\bibliographystyle{elsarticle-num}
-\bibliography{main}
+% put your thanks here
+\section*{Acknowledgments}
+The author thanks the anonymous authors whose work largely
+constitutes this sample file. This research was supported by ???.
+
+\bibliographystyle{plain}
+\bibliography{ijnam}
 

### 2012-09-08 notes/work/ijnam.tex
Work on IJNAM.

@@
 
-\title{Numerical and analytical solution of nonlinear electro-kinetic phenomena}
+\title{Asymptotic and Numerical Solution for Electro-Kinetic Flow Around an Ion-Selective Particle}
 
@@
 
-% dedication
-\dedicatory{This paper is dedicated to our authors}
-
 % communicated
@@
 
-\abstract{A numerical solver for the simulation of ion-exchanging particles migration in an
+\abstract{A numerical solver for the simulation of an electrokinetic migration of particles in an
 electrolyte solution is presented. The electrokinetic transport process is
@@
 layer of the fluid bulk.
-In cases where the layer width is much smaller than the particle's
+In cases where the layer width is much smaller than the particle
 size, an analytical asymptotic solution for the Debye layer
@@
         the fluid bulk, which is electrically neutral).
-        The zeta potential is defined as the voltage drop across (2).}
+        The zeta potential is defined as the voltage drop across 
+        the Debye layer (2).}
         \label{fig:EDL}
@@
 Moreover, any numerical solver must handle the scale disparity caused by the
-Debye layer width being much smaller than the particle's size.
-
+Debye layer width being much smaller than the particle size. 
 A closed-form linear asymptotic solution has been developed for
-spherical ion-exchanging particles and weak electric field in an
+spherical particles and weak electric field in an
 axisymmetric setting \cite{yariv2010migration} but it is hard to extend this
@@
 and nanoscale objects in many nanotechnology applications,
-such as the self-assembly of superstructures, roving sensors, 
-drug-delivery systems and useful nanomachinery 
-\cite{howse2007self,paxton2004catalytic,pumera2010electrochemically}.
-
-However, since the model for these electrokinetic
+nano-fluidic devices, packed bed separation, desalination processes and various 
+electrophoresis applications \cite{howse2007self,paxton2004catalytic,pumera2010electrochemically,nischang2007,leinweber2004}.
+Because the model for these electrokinetic
 phenomena has no closed-form analytic solution, a numerical
@@
 One such phenomenon is nonlinear electrokinetic vortex flow, 
-which can useful for microfluidic mixing applications \cite{wang2004mix, ben2002vortex},
+which is useful for microfluidic mixing applications \cite{wang2004mix, ben2002vortex},
 
@@
 and presented in Section \ref{sec:asymp}.
-The numerical results and their comparison to the analytical asymptotic solution 
+The numerical results and their comparison to an analytical asymptotic solution 
 are presented and discussed in Section \ref{sec:results}.
@@
 (the characteristic size of the ion-exchanging particle).
-
 Positive and negative ionic concentrations are denoted by $c_+$ and $c_-$, respectively, and
 are normalized by the ambient ionic concentration $c^*$. The ionic valences are $\pm z$.
-
 The dimensional ionic fluxes, $\bj_\pm$, are given by the Nernst-Plank equation 
@@
 \begin{eqnarray}
-c_+ - c_- &=& -\frac{\eps^* \varphi^*}{z F^* c^* (a^*)^2} \Laplacian \varphi = 
+c_+ - c_- &=& -\frac{\eps^* \varphi^*}{z e^* c^* (a^*)^2} \Laplacian \varphi = 
 -\delta^2 \Laplacian \varphi,
 \\
-\delta^2 &=& \frac{\eps^* \varphi^*}{c^* F^* z (a^*)^2} = 
+\delta^2 &=& \frac{\eps^* \varphi^*}{c^* e^* z (a^*)^2} = 
 \pars{\frac{\delta^*}{a^*}}^2.
@@
 
-\subsection{Micro-scale phenomena}
+\subsection{Governing Equations}
+The electro-kinetic flow is described by the following nondimensional equations:
 
@@
 \begin{eqnarray}
-  c &=& \frac{c_+ + c_-}{2},\\
-  q &=& \frac{c_+ - c_-}{2}.
+  c = \frac{c_+ + c_-}{2} &,& q = \frac{c_+ - c_-}{2}.
 \end{eqnarray}
@@
 \begin{eqnarray}
-  \bj &=& \frac{\bj_+ + \bj_-}{2} = -\bnabla c - q \bnabla \varphi + \alpha \bv c, \\
-  \bi &=& \frac{\bj_+ - \bj_-}{2} = -\bnabla q - c \bnabla \varphi + \alpha \bv q,
+  \bj = \frac{\bj_+ + \bj_-}{2} = -\bnabla c - q \bnabla \varphi + \alpha \bv c &,& 
+  \bi = \frac{\bj_+ - \bj_-}{2} = -\bnabla q - c \bnabla \varphi + \alpha \bv q,
 \end{eqnarray}
@@
 \begin{eqnarray}
-\bnabla \cdot \bj &=& 0, \\
-\bnabla \cdot \bi &=& 0. 
+\bnabla \cdot \bj = 0 &,& 
+\bnabla \cdot \bi = 0. 
 \end{eqnarray}
@@
 We follow the physical setting described in \cite{yariv2010migration}.
-We assume that a constant constant electric field of magnitude $\beta$,
+We assume that a constant constant electric field of nondimensional magnitude $\beta$,
 is applied to the system, in direction denoted by the unit vector $\ui$.
@@
 
-An ion-exchanger fixed reference frame is used.
+We employ the reference frame of the ion exchanger.
 Far away from the particle, we have a uniform applied electrostatic field, uniform flow,
@@
 \begin{eqnarray}
--\bv &\rightarrow& \cU \ui, \\
--\bnabla \varphi &\rightarrow& \beta\ui, \\
-c_\pm &\rightarrow& 1.
-\end{eqnarray}
-
-We consider a spherical ion-exchanger. 
-At its surface $\mathcal{S}$ (defined at $r=1$ with normal $\bn = \brhat$), 
+\bv \rightarrow -\cU \ui, &
+\bnabla \varphi \rightarrow -\beta\ui, &
+ c_\pm \rightarrow 1.
+\end{eqnarray}
+
+We consider a spherical particle.
+The chemical properties of the particle's surface $\mathcal{S}$ (defined at $r=1$ with normal $\bn = \brhat$), determine the boundary conditions on $\mathcal{S}$.
 we assume high conductance of the particle (yielding a uniform electric potential),
@@
 \begin{eqnarray}
-\varphi & = & \cV, \\
-\bv & = & \bzero, \\
-\bn \cdot \bj_- & = & 0, \\
-c_+ &=& \gamma, \\
+\begin{array}{cccc}
+\varphi = \cV, &
+\bv = \bzero, &
+\bn \cdot \bj_- = 0, &
+c_+ = \gamma,
+\end{array}
 \end{eqnarray}
@@
 \begin{eqnarray}
-  Q & = & 0, \\
-  C & = & C_+ = C_-, \\
-\bJ &=& -\bnabla C + \alpha \bV C, \\
-\bI &=& -C \bnabla \varPhi.
-\end{eqnarray}
+\begin{array}{cccc}
+  Q = 0, &
+  C = C_+ = C_-, &
+\bJ = -\bnabla C + \alpha \bV C, &
+\bI = -C \bnabla \varPhi.
+\end{array}\end{eqnarray}
 Because the flow is incompressible ($\bnabla \cdot V = 0$), 
-ion conservation results in the following equations:
-
-\begin{enumerate}
-\item Salt conservation in macroscale equation:
-\begin{eqnarray} \label{eq:salt}
-\bnabla \cdot \bJ = \Laplacian C - \alpha \bV \cdot \bnabla C = 0. 
-\end{eqnarray}
-
-\item Charge conservation in macroscale equations:
-\begin{eqnarray} \label{eq:charge}
-\bnabla \cdot \bI = \bnabla \cdot \pars{ C \bnabla \varPhi } = 0.
-\end{eqnarray}
-
-\end{enumerate}
+ion conservation results in the following 
+salt and charge conservation equations:
+\begin{eqnarray} 
+\label{eq:salt}
+\bnabla \cdot \bJ = \Laplacian C - \alpha \bV \cdot \bnabla C &=& 0, \\
+\label{eq:charge}
+\bnabla \cdot \bI = \bnabla \cdot \pars{ C \bnabla \varPhi } &=& 0.
+\end{eqnarray}
 
@@
 By integrating the microscale equations across the Debye layer
-(see the full derivation in \cite{yariv2010asymptotic}), 
+(see full derivation in \cite{yariv2010asymptotic}), 
 the effective boundary conditions at the ion-exchanger surface are:
@@
 \end{eqnarray}
-The total force acting on the particle is computed by the following surface integral:
-\begin{eqnarray}
-\bF &=& \oint_\mathcal{S} \tT \cdot \bnhat dA.
-\end{eqnarray}
-In steady state (constant particle drift velocity $\cU$), 
-the total force must be zero: 
-\begin{eqnarray}
-\bF = \bzero.
+In steady state (constant particle drift velocity $\cU$), the total force acting on the particle 
+(computed by the following surface integral) must vanish:
+\begin{eqnarray}
+\bF = \oint_\mathcal{S} \tT \cdot \bnhat dA = \bzero.
 \end{eqnarray}
@@
 The resulting nonlinear discrete system is
-solved numerically using Newton's Method, so the total force on the particle can be computed
-numerically. Variation of $\cU$ is used to find the steady-state velocity, 
-which corresponds to zero total force.
-
-The steady-state velocity is thus the solution to the nonlinear scalar equation
+solved numerically using Newton's Method, so the total force on the
+particle can be computed. 
+We seek the steady-state velocity $\cU$, 
+which corresponds to zero total force,
 \begin{eqnarray}
@@
 \end{eqnarray}
-which we solver by standard secant method.
+which we solve by the standard secant method.
 
@@
 \subsubsection{Spherical Coordinates}
-Since the system is axisymmetric, the operators are written in 
+Because the system is axisymmetric, we employ
 spherical coordinates $(r,\theta,\phi)$.
@@
 
-It is important to note that due to the choice of spherical coordinate system,
+Note that in the spherical coordinate system,
 the vector Laplacian operator cannot be computed in a decoupled manner as in the Cartesian system,
@@
 \subsubsection{Computational Grid}
-In order to discretize the differential operators, 
-a regular grid of size $n_r \times n_\theta$ is defined, with:
-\begin{eqnarray}
-(r_i,\theta_j) &\in& [1, \infty) \times [0,\pi], \\ 
-r_i &=& (1+\Delta_r)^i, \\
-\theta_j &=& \Delta_\theta \cdot j,
+A regular grid of size $n_r \times n_\theta$ is defined, with:
+\begin{eqnarray}
+(r_i,\theta_j) \in [1, \infty) \times [0,\pi], & 
+r_i = (1+\Delta_r)^i, &
+ \theta_j = \Delta_\theta \cdot j,
 \end{eqnarray}
@@
 \begin{eqnarray}
-\Delta_r &=& \pars{R_{max}} ^ \frac{1}{n_r} - 1, \\
-\Delta_\theta &=& \frac{\pi}{n_\theta}.
+\Delta_r = \pars{R_{max}} ^ \frac{1}{n_r} - 1 ,& \Delta_\theta = \frac{\pi}{n_\theta}.
 \end{eqnarray}
@@
 \begin{eqnarray}
-\Omega_{ij} &=& [r_{i-1}, r_{i}] \times [\theta_{j-1}, \theta_{j}], \\
-\bar{r}_i &=& \frac{r_{i-1} + r_{i}}{2}, \\
-\bar{\theta}_j &=& \frac{\theta_{j-1} + \theta_{j}}{2}.
-\end{eqnarray}
-
-Each variable is discretized with respect of its cell as follows:
-\begin{itemize}
-\item $\varPhi$, $C$ and $P$ are represented by their value at the center of each cell, 
+\Omega_{ij} = [r_{i-1}, r_{i}] \times [\theta_{j-1}, \theta_{j}], &
+\bar{r}_i = (r_{i-1} + r_{i})/2, &
+\bar{\theta}_j = (\theta_{j-1} + \theta_{j})/2.
+\end{eqnarray}
+
+Each discrete variable is located with respect of its cell as follows:
+$\varPhi$, $C$ and $P$ are represented by their value at the center of each cell, 
 using an all-centered grid:
 \begin{eqnarray}
-\varPhi^h_{[i,j]} &=& \varPhi(\bar{r}_i, \bar{\theta}_j), \\
-C^h_{[i,j]} &=& C(\bar{r}_i, \bar{\theta}_j), \\
-P^h_{[i,j]} &=& P(\bar{r}_i, \bar{\theta}_j).
-\end{eqnarray}
-\item $\bV$ is represented by its values at cell boundaries, using a staggered grid:
-\begin{eqnarray}
-V_r^h{}_{[i,j]} &=& V_r(r_i, \bar{\theta}_j), \\
-V_\theta^h{}_{[i,j]} &=& V_\theta(\bar{r}_i, {\theta}_j).
-\end{eqnarray}
-\end{itemize}
+\varPhi^h_{[i,j]} = \varPhi(\bar{r}_i, \bar{\theta}_j), &
+C^h_{[i,j]} = C(\bar{r}_i, \bar{\theta}_j), &
+P^h_{[i,j]} = P(\bar{r}_i, \bar{\theta}_j).
+\end{eqnarray}
+$\bV$ is represented by its values at cell boundaries, using a staggered grid:
+\begin{eqnarray}
+V_r^h{}_{[i,j]} = V_r(r_i, \bar{\theta}_j), &
+V_\theta^h{}_{[i,j]} = V_\theta(\bar{r}_i, {\theta}_j).
+\end{eqnarray}
 
@@
 A finite-volume method with linear interpolation is used for flux discretization.
-%$\boldsymbol{f}^h$
 
@@
 \begin{eqnarray}
-\cD_r(f^h){}_{\left[i+\half,j\right]} &=& \frac{f^h_{\left[i+1,j\right]} - f^h_{\left[i,j\right]}}
-                       {r_{\left[i+1,j\right]} - r_{\left[i,j\right]}}, \\
-\cD_\theta(f^h){}_{\left[i,j+\half\right]} &=& \frac{f^h_{\left[i,j+1\right]} - f^h_{\left[i,j\right]}}
+\cD_r(f^h){}_{\left[i+\half,j\right]} = \frac{f^h_{\left[i+1,j\right]} - f^h_{\left[i,j\right]}}
+                       {r_{\left[i+1,j\right]} - r_{\left[i,j\right]}}, &
+\cD_\theta(f^h){}_{\left[i,j+\half\right]} = \frac{f^h_{\left[i,j+1\right]} - f^h_{\left[i,j\right]}}
 					   {\theta_{\left[i,j+1\right]} - \theta_{\left[i,j\right]}}.
@@
 
-The total flux of a cell is equal to zero ($\bnabla \cdot \boldsymbol{f} = 0$):
+If the total flux of a cell is equal to zero ($\bnabla \cdot \boldsymbol{f} = 0$), then we have
 \begin{eqnarray}
@@
 \begin{eqnarray}
-I^h_r &=& -\cI_r(C^h) \cdot \cD_r(\varPhi^h), \\
-I^h_\theta &=& -\cI_\theta(C^h) \cdot \frac{\cD_\theta(\varPhi^h)}{r}.
+I^h_r = -\cI_r(C^h) \cdot \cD_r(\varPhi^h), &
+I^h_\theta = -\cI_\theta(C^h) \cdot \frac{\cD_\theta(\varPhi^h)}{r}.
 \end{eqnarray}
@@
 \begin{eqnarray}
-J^h_r &=& -\cD_r(C^h) + \alpha V^h_r \cdot \mathcal{U}^{\bV^h}_r (C^h), \\
-J^h_\theta &=& -\frac{\cD_\theta(C^h)}{r} + \alpha V^h_\theta \cdot \mathcal{U}^{\bV^h}_\theta (C^h), \\
- \mathcal{U}^{\bV^h}_r(C^h)[i,j] &=& C^h\left[i-\frac{\sign(V^h_r)}{2}, j\right], \\
- \mathcal{U}^{\bV^h}_\theta(C^h)[i,j] &=& C^h\left[i, j-\frac{\sign(V^h_\theta)}{2}\right]. 
+J^h_r = -\cD_r(C^h) + \alpha V^h_r \cdot \mathcal{U}^{\bV^h}_r (C^h), &
+J^h_\theta = -\frac{\cD_\theta(C^h)}{r} + \alpha V^h_\theta \cdot \mathcal{U}^{\bV^h}_\theta (C^h), 
+\\
+ \mathcal{U}^{\bV^h}_r(C^h)[i,j] = C^h\left[i-\frac{\sign(V^h_r)}{2}, j\right], &
+ \mathcal{U}^{\bV^h}_\theta(C^h)[i,j] = C^h\left[i, j-\frac{\sign(V^h_\theta)}{2}\right]. 
 \end{eqnarray}
@@
 Mass flux $\bV$ is discretized on grid cells boundaries, 
-using the velocity staggered grid.
+using the staggered velocity grid.
 
 Force components ($\bF = -\bnabla P + \bLaplacian \bV + \bnabla \varPhi \Laplacian \varPhi$) 
-are discretized on the velocity staggered grid, where
+are discretized on the staggered velocity grid, where
 linear interpolation is used for the Coulomb force and for vector Laplacian components.
@@
 \begin{eqnarray}
+\begin{array}{cccc}
 \frac{\varPhi^h_{[n_r + 1, j]} - \varPhi^h_{[n_r, j]}}{\bar{r}_{n_r + 1} - \bar{r}_{n_r}} 
- & = & -\beta \cos\bar{\theta}_j, \\
-C^h_{[n_r + 1, j]} & = & 1 \\
-V_r^h{}_{[n_r + 1, j]} & = & -\cU \cos\bar{\theta}_j, \\
-V_\theta^h{}_{[n_r + 1, j]} & = & \cU \sin\theta_j.
-\end{eqnarray}
+= -\beta \cos\bar{\theta}_j, &
+C^h_{[n_r + 1, j]} = 1 &
+V_r^h{}_{[n_r + 1, j]} = -\cU \cos\bar{\theta}_j, &
+V_\theta^h{}_{[n_r + 1, j]} = \cU \sin\theta_j.
+\end{array}\end{eqnarray}
 
@@
 In order to solve the equation $\cO(\bx) = \bzero$, Newton's method can 
-be applied, given an initial solution $\bx_0$:
-\begin{eqnarray}
-\bzero = \cO(\bx_n + \Delta \bx_n) &\approx& \cO(\bx_n) + \bnabla \cO(\bx_n)\cdot\Delta\bx_n, \\
-\Rightarrow \bnabla \cO(\bx_n) \cdot \Delta \bx_n &=& -\cO(\bx_n), \\
-\bx_{n+1} &=& \bx_{n} + \Delta \bx_n. 
-\end{eqnarray}
-
+be applied, given an initial solution $\bx_0$.
 Each step requires the computation of the residual vector, $\br = \cO(\bx)$, and
@@
 \begin{eqnarray}
-\tilde{\varPhi} &=& \cB_\varPhi(\varPhi, C; \beta), \\
-\tilde{C} &=& \cB_C(C, \varPhi), \\
-\tilde{V_r} &=& \cB_{V_r}(V_r; \cU), \\
-\tilde{V_\theta} &=& \cB_{V_\theta}(V_\theta, C, \varPhi; \cU, \gamma), \\
-\tilde{P} &=& P.
+\begin{array}{ccccc}
+\tilde{\varPhi} = \cB_\varPhi(\varPhi, C; \beta), &
+\tilde{C} = \cB_C(C, \varPhi), &
+\tilde{V_r} = \cB_{V_r}(V_r; \cU), &
+\tilde{V_\theta} = \cB_{V_\theta}(V_\theta, C, \varPhi; \cU, \gamma), &
+\tilde{P} = P.
+\end{array}
 \end{eqnarray}
@@
 \subsubsection{Steady-state}
-Let $\beta$ be a specific field magnitude
+Let $\beta$ be a given nondimensional electric field.
 Assume that $\cU \ui$ is the drift velocity of the ion exchanger 
@@
 && -\pars{\cD_r(V_\theta) - \frac{V_\theta}{r}
-+ \frac{1}{r}\cD_r(\varPhi) \cD_{\theta}(\varPhi)}\sin\theta, \\
- \mathcal{S} &=& \{\br : \|\br\|_2 = 1\}.
++ \frac{1}{r}\cD_r(\varPhi) \cD_{\theta}(\varPhi)}\sin\theta.
 \end{eqnarray}
@@
 (as derived in \cite{yariv2010migration}), and the solver convergence is fast.
-
 However, this is no longer true for $\beta \sim O(1)$, since the nonlinear terms become dominant
@@
 
-Given that $|\beta_{i+1} - \beta_i| < \eps$ for small enough $\eps$, 
-the next solution $\bx_{i+1}$ is close to the previous one $\bx_i$,
-so the iterative solver converges well.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\paragraph{Linear operator}
+\paragraph{\textit{Linear operator}}
 If $\cO$ is linear, it can be represented by a matrix $L$, such that:
@@
 
-\paragraph{Pointwise scalar function}
+\paragraph{\textit{Pointwise scalar function}}
 Let $f: \R \rightarrow \R$ be a differentiable 1D function, whose derivative is
@@
 
-\paragraph{Constant value}
+\paragraph{\textit{Constant value}}
 A constant operator $\mathcal{C}$ is defined by constant vector $\bc$ 
@@
 
-\paragraph{Binary operators}
+\paragraph{\textit{Binary operators}}
 Let $\cO_1$ and $\cO_2$ be two operators, so their pointwise addition, subtraction,
@@
 
-\paragraph{N-ary operators}
+\paragraph{\textit{N-ary operators}}
 Given $N$ operators $\{\cO_i\}_{i=1}^N$, their concatenation $\cO$ is defined as:
@@
 followed by a computation of the total force $\bF$ acting on the ion-exchanger.
-
-$F_\imath = \bF \cdot \ui$ is computed by using the mid-point quadrature rule:
-\begin{eqnarray}
-F_\imath &=& \sum_{i=1}^{n_\theta} f(\bar\theta_i) \cdot 
-              2 \pi \sin\bar\theta_i \cdot \Delta\theta_i
-\end{eqnarray}
-
-\subsubsection{Steady state drift velocity}
+$F_\imath = \bF \cdot \ui$ is computed by using the mid-point quadrature rule
+\begin{eqnarray}
+F_\imath = \sum_{i=1}^{n_\theta} f(\bar\theta_i) \cdot 
+              2 \pi \sin\bar\theta_i \cdot \Delta\theta_i.
+\end{eqnarray}
+
 In steady state, the total force acting on the particle $F_\imath$ must vanish.
-This constraint yields an equation, whose solution is the steady-state velocity $\cU$:
-\begin{eqnarray}
-F_\imath(\cU) &=& 0
-\end{eqnarray}
-This equation can be solved using a 1D root finding algorithm, e.g., the secant method:
-\begin{eqnarray}
-\cU_{n+1} = \frac{F_\imath(\cU_{n})\cU_{n-1} - F_\imath(\cU_{n-1})\cU_{n}}
-{F_\imath(\cU_{n}) - F_\imath(\cU_{n-1})} \rightarrow \cU
-\end{eqnarray}
-The result $\cU$ is the 
+This constraint yields an equation $F_\imath(\cU) = 0$, 
+whose solution is the steady-state velocity $\cU$.
+This equation can be solved using a 1D root finding algorithm (e.g., the secant method). The result $\cU$ is the 
 steady state particle drift velocity for the electric field $\beta$.
@@
 \begin{eqnarray}
-\bnabla \cdot \pars{C \bnabla \varPhi} &=& 0, \\
-\bnabla \cdot \pars{\bnabla C - \alpha \bV C} &=& 0, \\
-\bnabla \cdot \bV &=& 0, \\
-\bLaplacian \bV - \bnabla P + \Laplacian \varPhi \bnabla \varPhi &=& \bzero.
-\end{eqnarray}
+\begin{array}{cccc}
+\bnabla \cdot \pars{C \bnabla \varPhi} = 0, &
+\bnabla \cdot \pars{\bnabla C - \alpha \bV C} = 0, &
+\bnabla \cdot \bV = 0, &
+\bLaplacian \bV - \bnabla P + \Laplacian \varPhi \bnabla \varPhi = \bzero.
+\end{array}\end{eqnarray}
 
@@
 \begin{eqnarray}
+\begin{array}{rcl}
 \varPhi + \log C &=& \cV + \log \gamma = 0, \\
@@
 &=& 4\log\pars{\frac{1 + e^\frac{\zeta}{2}}{2}} \bnabla_S \varPhi.
+\end{array}
 \end{eqnarray}
@@
 \begin{eqnarray}
-\bnabla \varPhi &=& -\beta \ui, \\
-C &=& 1, \\
-\bV &=& -\cU \ui,
+\bnabla \varPhi = -\beta \ui, &
+C = 1, &
+\bV = -\cU \ui,
 \end{eqnarray}
@@
 
-The solution to the nonlinear system can be expanded in a Taylor series in $\beta$.
+For small $\beta$, the solution to the nonlinear system can be expanded in a Taylor series in $\beta$.
 \begin{eqnarray}
@@
 \begin{eqnarray}
-\varPhi &=& \beta \varPhi_1 + \beta^2 \varPhi_2 + \beta^3 \varPhi_3 + \ldots, \\
-C &=& 1 + \beta C_1 + \beta^2 C_2 + \beta^3 C_3 + \ldots, \\
-\Psi &=& \beta \Psi_1 + \beta^2 \Psi_2 + \beta^3 \Psi_3 + \ldots ,
+\varPhi = \sum_i \beta^i \varPhi_i, &
+C = 1 + \sum_i \beta^i C_i, &
+\Psi = \sum_i \beta^i \Psi_i,
 \end{eqnarray}
@@
 
-The nonlinear equations and the boundary conditions are expanded around $\beta = 0$
-and arranged by powers of $\beta$:
-\begin{eqnarray}
-\bzero = \cO(\bx) = \sum_k \cO_k(\bx_0, \ldots \bx_k) \beta^k
-\end{eqnarray}
-This can be rewritten as a system of equations:
-\begin{eqnarray}
-\brc{rcl}{
-\bzero &=& \cO_0(\bx_0), \\
-\bzero &=& \cO_1(\bx_0, \bx_1), \\
-\bzero &=& \cO_2(\bx_0, \bx_1, \bx_2), \\
-& \vdots & \\
-\bzero &=& \cO_k(\bx_0, \bx_1, \bx_2, \ldots \bx_k).
-}
-\end{eqnarray}
+The nonlinear equations and the boundary conditions 
+are expanded around $\beta = 0$:
+\begin{eqnarray}
+\bzero = \cO(\bx) = \sum_i \cO_i(\bx_0, \ldots \bx_i) \beta^i
+\end{eqnarray}
+
 Thus, the $O(\beta^k)$ term $\bx_k$ can be found recursively by solving 

### 2012-09-10 notes/work/ijnam.tex
IJNAM

@@
 
-\title{Asymptotic and Numerical Solution for Electro-Kinetic Flow Around an Ion-Selective Particle}
+\title{Asymptotic and Numerical Solution for Electro-Kinetic Flow Around a Spherical Particle}
 
@@
 % two authors have the same address
-\author{Ory Schnitzer \and Ehud Yariv}
-\address{Department of Mathematics, Technion -- Israel Institute of Technology, Haifa 32000, Israel}
-\email{oschnitt@gmail.com \and udi@math.technion.ac.il}
+%\author{Ory Schnitzer \and Ehud Yariv}
+%\address{Department of Mathematics, Technion -- Israel Institute of Technology, Haifa 32000, Israel}
+%\email{oschnitt@gmail.com \and udi@math.technion.ac.il}
 
 % communicated
-\commby{Hilbert}
+%\commby{Hilbert}
 
 % Received by the editors ?
-\date{January 1, 2004 and, in revised form, March 22, 2004.}
-
-% it is suggested to put it in Acknowledgments
-\thanks{This research was supported by ???}
-
-\subjclass[2000]{35R35, 49J40, 60G40}
-
-\abstract{A numerical solver for the simulation of an electrokinetic migration of particles in an
-electrolyte solution is presented. The electrokinetic transport process is
+\date{DATE}
+
+% \subjclass[2000]{35R35, 49J40, 60G40}
+
+\abstract{
+A numerical solver for the simulation of an electrokinetic 
+migration of particles in an electrolyte solution 
+due to an application of an external electric field is presented.
+The electrokinetic transport process is
 described by a nonlinear partial differential equation system, 
-as well as nonlinear boundary conditions.
-The nonlinear system is discretized and solved iteratively using Newton's method.
+as well as nonlinear effective boundary conditions, which are derived from
+the specific chemical properties of the particle.
+The nonlinear system is discretized and an iterative Newton solver is constructed
+automatically from the discrete equations.
 An asymptotic analytical solution is derived for the validation of the solver. 
-The numerical results are compared to the asymptotic solutions, and good correspondence is achieved.}
+The numerical results are obtained and are compared to the asymptotic solutions, 
+and good correspondence is achieved.}
 
@@
     \begin{center}
-        \includegraphics[width=0.2\textwidth]
-            {figs/ElectricDoubleLayer.eps}
+        \includegraphics[width=0.33\textwidth]
+            {figs/debye.eps}
         \caption{Schematic structure of the double layer:
@@
 solver for nonlinear electrokinetic problems, and apply it to the study
-of systems that have no closed-form solutions.
+of systems that have no closed-form solutions, such as an ion-exchanger migration
+\cite{yariv2010migration} and the electrophoresis problem \cite{schnitzer2012surface}.
 This solver can be used to gain insight into the chemical and physical behavior 
@@
 
-\subsection{Dimensionless Notation}
-
+\subsection{Nondimensionalization}
 Spatial coordinates $\br$ are normalized by $a^*$ 
-(the characteristic size of the ion-exchanging particle).
+(the characteristic size of the particle).
 Positive and negative ionic concentrations are denoted by $c_+$ and $c_-$, respectively, and
@@
 The dimensional ionic fluxes, $\bj_\pm$, are given by the Nernst-Plank equation 
-(using the Einstein relation for the electric mobility, $\mu_q^* = D^* / k_B^* T^*$):
+(using the Einstein relation for the electric mobility, $\mu_q^* = D^* / k_B^* T^*$, 
+where $D^*$ is the ionic diffusivity):
 \begin{eqnarray}
@@
 \end{eqnarray}
-where $D^*$ is the ionic diffusivity.
 
 The electric potential $\varphi$ is normalized by the thermal voltage:
-\begin{eqnarray}
-\varphi^* &=& \frac{k_B^* T^*}{z e^*} = \frac{R^* T^*}{z F^*},
-\end{eqnarray}
-where $R^* = k_B^* N_A$ and $F^* = e^* N_A$ is the Faraday number.
+$\varphi^* = {k_B^* T^*}/{z e^*} = {R^* T^*}/{z F^*},$
+where $R^* = k_B^* N_A$, $F^* = e^* N_A$ is the Faraday number and $N_A$ is the Avogadro constant.
 
@@
 \begin{eqnarray}
-\bnabla \cdot \bv &=& 0, \\
--\bnabla p^* + \mu^* \bLaplacian \bv^* + \eps^* \Laplacian \varphi^* \bnabla \varphi^* &=& 0.
+\bnabla \cdot \bv = 0, &
+-\bnabla p^* + \mu^* \bLaplacian \bv^* + \eps^* \Laplacian \varphi^* \bnabla \varphi^* = 0.
 \end{eqnarray}
@@
 The fluxes $\bj^*_\pm$ are normalized by $j^* = {D^* c^*}/{a^*}$.
-
-The nondimensional Nernst-Plank equation is then written as:
-\begin{eqnarray}
-\bj_\pm &=& 
--\bnabla c_\pm + \alpha \bv c_\pm \mp c_\pm \bnabla \varphi,
-\end{eqnarray}
-where $\alpha = {v^* a^*}/{D^*} = {\eps^* (\varphi^*)^2}/{\mu^* D^*}$ 
-is the dimensionless Peclet number.
 
@@
 \end{eqnarray}
-and after nondimensionalization, is given by:
-\begin{eqnarray}
-c_+ - c_- &=& -\frac{\eps^* \varphi^*}{z e^* c^* (a^*)^2} \Laplacian \varphi = 
--\delta^2 \Laplacian \varphi,
-\\
-\delta^2 &=& \frac{\eps^* \varphi^*}{c^* e^* z (a^*)^2} = 
-\pars{\frac{\delta^*}{a^*}}^2.
+
+After nondimensionalization, the Nernst-Plank, Stokes and Poisson equations are:
+\begin{eqnarray} \label{eq:nernst}
+\bj_\pm &=& 
+-\bnabla c_\pm + \alpha \bv c_\pm \mp c_\pm \bnabla \varphi,
 \end{eqnarray}
-
+\begin{eqnarray} \label{eq:stokes}
+\bnabla \cdot \bv = 0, & -\bnabla p + \bLaplacian \bv + \Laplacian \varphi \bnabla \varphi = 0, 
+\end{eqnarray}
+\begin{eqnarray} \label{poisson}
+c_+ - c_- &=& -2\delta^2 \Laplacian \varphi,
+\end{eqnarray}
+where $\delta = {\delta^*}/{a^*}$ is the dimensionless Debye thickness 
+($\delta^* = \sqrt{{\eps^* \varphi^*}/{2 c^* e^* z}}$) and 
+$\alpha = {v^* a^*}/{D^*} = {\eps^* (\varphi^*)^2}/{\mu^* D^*}$ 
+is the dimensionless Peclet number.
 The force on the particle is denoted by $\bF$ normalized by $\mu^* v^* a^* = \eps^* (\varphi^*)^2$.
@@
 The electric field is denoted by $\bE$ and normalized by $E^* = \varphi^* / a^*$.
-
-\subsection{Governing Equations}
-The electro-kinetic flow is described by the following nondimensional equations:
-
-\subsubsection{Nernst-Planck Equations}
-The ionic fluxes are given by ion diffusion, electrostatic forces and ion advection by the fluid:
-\begin{eqnarray}
-  \bj_\pm &=& -\bnabla c_\pm \mp c_\pm \bnabla \varphi + \alpha \bv c_\pm,
-\end{eqnarray}
-
-Due to conservation of ions, the fluxes are divergence-free:
-\begin{eqnarray}
+The surface charge is denoted by $\sigma$ and normalized by $\sigma^* = \eps^* \varphi^* / \delta^*$.
+
+The ionic fluxes are given by ion diffusion, electrostatic forces and ion advection by the fluid
+at Eq. \ref{eq:nernst}. Due to conservation of ions, the fluxes are divergence-free:
+\begin{eqnarray*}
 \bnabla \cdot \bj_\pm &=& 0.
-\end{eqnarray}
-These equation may be re-written by using the following transformations:
-\begin{eqnarray}
-  c = \frac{c_+ + c_-}{2} &,& q = \frac{c_+ - c_-}{2}.
-\end{eqnarray}
+\end{eqnarray*}
+These equation may be re-written by using salt $c = (c_+ + c_-)/2$ and charge $q = (c_+ - c_-)/2$.
 Thus, salt and charge fluxes are defined by:
-\begin{eqnarray}
+\begin{eqnarray*}
   \bj = \frac{\bj_+ + \bj_-}{2} = -\bnabla c - q \bnabla \varphi + \alpha \bv c &,& 
   \bi = \frac{\bj_+ - \bj_-}{2} = -\bnabla q - c \bnabla \varphi + \alpha \bv q,
-\end{eqnarray}
+\end{eqnarray*}
 and are divergence-free as well:
-\begin{eqnarray}
+\begin{eqnarray*}
 \bnabla \cdot \bj = 0 &,& 
 \bnabla \cdot \bi = 0. 
-\end{eqnarray}
-
-\subsubsection{Incompressible Stokes Flow with Electrostatic Force}
-Mass conservation (due to constant fluid density) reads:
-\begin{eqnarray}
-\bnabla \cdot \bv &=& 0.
-\end{eqnarray}
-Momentum conservation (force balance) reads:
-\begin{eqnarray}
-\Laplacian \bv - \bnabla p + \bnabla \varphi \Laplacian \varphi &=& 0.
-\end{eqnarray}
-Finally, free charge density is governed by the Poisson equation:
-\begin{eqnarray}
-\delta^2 \Laplacian \varphi &=& -2q.
-\end{eqnarray}
-
-\subsubsection{Boundary conditions}
-We follow the physical setting described in \cite{yariv2010migration}.
+\end{eqnarray*}
+In addition, the charge is governed by the Poisson equation:
+\begin{eqnarray*}
+q &=& -\delta^2 \Laplacian \varphi.
+\end{eqnarray*}
+
+\subsection{Boundary conditions}
 We assume that a constant constant electric field of nondimensional magnitude $\beta$,
 is applied to the system, in direction denoted by the unit vector $\ui$.
-As a result, the ion-exchanger will equilibrate in 
+As a result, the particle will equilibrate in 
 a non-zero steady-state velocity $\cU \ui$, which is
@@
 
-We employ the reference frame of the ion exchanger.
-Far away from the particle, we have a uniform applied electrostatic field, uniform flow,
+We employ the reference frame of the particle.
+Far away from it, we have a uniform applied electrostatic field, uniform flow,
 and ambient ionic concentrations:
-\begin{eqnarray}
+\begin{eqnarray*}
 \bv \rightarrow -\cU \ui, &
@@
  c_\pm \rightarrow 1.
-\end{eqnarray}
+\end{eqnarray*}
 
 We consider a spherical particle.
-The chemical properties of the particle's surface $\mathcal{S}$ (defined at $r=1$ with normal $\bn = \brhat$), determine the boundary conditions on $\mathcal{S}$.
-we assume high conductance of the particle (yielding a uniform electric potential),
+The chemical properties of the particle's surface $\mathcal{S}$ (defined at $r=1$ 
+with normal $\bn = \brhat$), determine the boundary conditions on $\mathcal{S}$.
+We consider the following scenarios:
+\subsubsection{Ion-exchanger (\cite{yariv2010migration})}
+We assume high conductance of the particle (yielding a uniform electric potential),
 zero slip, anion impermeability, cation selectivity 
@@
 $\bn \cdot \bj_+ = k (1 - c_+/\gamma)$, where $k \rightarrow \infty$):
-\begin{eqnarray}
+\begin{eqnarray*}
 \begin{array}{cccc}
@@
 \end{array}
-\end{eqnarray}
+\end{eqnarray*}
 where $\gamma$ is the ratio between the cationic concentration on the surface and the cationic
 concentration in the fluid bulk.
+
+\subsubsection{Inert particle (\cite{schnitzer2012surface})}
+We assume constant surface charge
+zero slip and ion impermeability:
+\begin{eqnarray*}
+\begin{array}{cccc}
+\bn \cdot (\bnabla \varphi - \chi \bnabla \varphi_s) = \delta^{-1} \sigma, &
+\bv = \bzero, &
+\bn \cdot \bj_\pm = 0.
+\end{array}
+\end{eqnarray*}
+where $\chi$ is the ratio between the dielectric constants of the 
+particle and the fluid.
 
@@
 except a thin boundary layer of width $O(\delta)$, 
-known as the ``Debye layer'', surrounding the ion exchanger.
+known as the ``Debye layer'', surrounding the particle.
+This boundary layer makes it very hard to construct 
+a direct numerical solver of the electro-kinetic problem.
+
+Due to the scale disparity at the Debye layer, 
+the PDE system can be rewritten in the ``inner'' region 
+as an ODE system and can be integrated and solved analytically,
+yielding an ``effective'' boundary conditions for the ``outer'' bulk region equations.
 
@@
 the boundary layer), using bulk variables denoted by uppercase letters, read:
-\begin{eqnarray}
+\begin{eqnarray*}
 \begin{array}{cccc}
@@
 \bI = -C \bnabla \varPhi.
-\end{array}\end{eqnarray}
+\end{array}\end{eqnarray*}
 Because the flow is incompressible ($\bnabla \cdot V = 0$), 
@@
 salt and charge conservation equations:
-\begin{eqnarray} 
-\label{eq:salt}
-\bnabla \cdot \bJ = \Laplacian C - \alpha \bV \cdot \bnabla C &=& 0, \\
-\label{eq:charge}
-\bnabla \cdot \bI = \bnabla \cdot \pars{ C \bnabla \varPhi } &=& 0.
-\end{eqnarray}
-
+\begin{eqnarray*} 
+0 &=& \bnabla \cdot \bJ = \Laplacian C - \alpha \bV \cdot \bnabla C, \\
+0 &=& \bnabla \cdot \bI = \bnabla \cdot \pars{ C \bnabla \varPhi }.
+\end{eqnarray*}
 The macroscale Stokes flow equations have the same form as the microscale equations:
-\begin{eqnarray}  \label{eq:stokes}
-\brc{rcc}{\bnabla \cdot \bV &=& 0, \\  
-\Laplacian \bV - \bnabla P + \bnabla \varPhi \Laplacian \varPhi &=& \bzero.}
-\end{eqnarray}
-
-\subsubsection{Bulk-scale effective boundary conditions}
-By integrating the microscale equations across the Debye layer
-(see full derivation in \cite{yariv2010asymptotic}), 
-the effective boundary conditions at the ion-exchanger surface are:
-\begin{eqnarray}
+\begin{eqnarray*} 
+0 &=& \bnabla \cdot \bV, \\   
+\bzero &=& \Laplacian \bV - \bnabla P + \bnabla \varPhi \Laplacian \varPhi.
+\end{eqnarray*}
+
+\subsection{Bulk-scale effective boundary conditions}
+By integrating the equations across the Debye layer,
+the effective boundary conditions at the particle surface are:
+\subsubsection{Ion-exchanger} See \cite{yariv2010migration} for full derivation:
+\begin{eqnarray*} 
 0 &=& \varPhi + \log C, \\ 
-0 &=& \bnhat \cdot \bnabla \pars{\varPhi - \log C}, \\
+0 &=& \deriv{}{n} \pars{\varPhi - \log C}, \\ 
 \bV &=& 
@@
 + 2\log\pars{1-\tanh^2\frac{\zeta}{4}} \cdot \bnabla_\mathcal{S} \log C,
-\end{eqnarray}
+\end{eqnarray*}
 where $\zeta = \cV - \varPhi = \log (C / \gamma)$ 
@@
 
+\subsubsection{Highly charged inert particle}
+See \cite{schnitzer2012surface} for full derivation:
+\begin{eqnarray*} 
+0 &=& {\deriv{C}{n} - \text{Du} \nabla^2_s \pars{\varPhi - \log C}} \\ 
+0 &=& {\deriv{C}{n} + C \deriv{\varPhi}{n}}, \\ 
+\bV &=& \zeta \cdot \bnabla_\mathcal{S} \pars{\varPhi - \log C} +
+4 \log 2 \cdot \bnabla_\mathcal{S} \log C,
+\end{eqnarray*}
+where $\zeta = \bar{\zeta} - \log C$ 
+is the zeta potential (the voltage drop across the Debye layer)
+and $\bar{\zeta} = 2 \log \sigma$.
+
 \subsection{Steady state}
 The stress tensor is composed of Newtonian and Maxwel stresses:
-\begin{eqnarray}
+\begin{eqnarray*} 
 \tT &=& \bnabla \bV + (\bnabla \bV)^\dagger - P \tI
@@
  \bnabla \cdot \tT &=& \bzero.
-\end{eqnarray}
+\end{eqnarray*}
 In steady state (constant particle drift velocity $\cU$), the total force acting on the particle 
 (computed by the following surface integral) must vanish:
-\begin{eqnarray}
+\begin{eqnarray*}
  \bF = \oint_\mathcal{S} \tT \cdot \bnhat dA = \bzero.
-\end{eqnarray}
+\end{eqnarray*}
 
@@
 which corresponds to zero total force,
-\begin{eqnarray}
+\begin{eqnarray*} 
 F(\beta, \cU) = 0,
-\end{eqnarray}
+\end{eqnarray*}
 which we solve by the standard secant method.
@@
 The scalar gradient and the divergence can be written as:
-\begin{eqnarray}
+\begin{eqnarray*}
 \bnabla f &=& \deriv{f}{r}\brhat + \frac{1}{r}\deriv{f}{\theta}\bthetahat, \\
@@
                \frac{1}{r \sin\theta}\deriv{}{\theta}\pars{F_\theta \sin\theta}.
-\end{eqnarray}
+\end{eqnarray*}
 The scalar Laplacian can be written as:
-\begin{eqnarray}
+\begin{eqnarray*}
 \Laplacian f = \bnabla \cdot (\bnabla f)&=& 
@@
  \frac{1}{r^2 \sin\theta}\deriv{}{\theta}\pars{\sin\theta \deriv{f}{\theta}}.
-\end{eqnarray}
+\end{eqnarray*}
 The vector gradient can be written as:
-\begin{eqnarray}
+\begin{eqnarray*}
 \bnabla \bF &=& \deriv{F_r}{r} \brhat \brhat + \deriv{F_\theta}{r} \brhat \bthetahat + 
@@
 \frac{1}{r}\pars{\deriv{F_\theta}{\theta} + F_r} \bthetahat \bthetahat.
-\end{eqnarray}
+\end{eqnarray*}
 The vector Laplacian can be written as:
-\begin{eqnarray}
+\begin{eqnarray*}
 \bLaplacian \bF &=& 
@@
 \frac{2}{r^2}\deriv{F_r}{\theta}\right) \bthetahat.
-\end{eqnarray}
+\end{eqnarray*}
 
@@
 A regular grid of size $n_r \times n_\theta$ is defined, with:
-\begin{eqnarray}
+\begin{eqnarray*}
 (r_i,\theta_j) \in [1, \infty) \times [0,\pi], & 
@@
  \theta_j = \Delta_\theta \cdot j,
-\end{eqnarray}
+\end{eqnarray*}
 where a logarithmic grid spacing has been chosen for $r$ and a uniform grid for $\theta$.
@@
 larger than $r_0$. Thus:
-\begin{eqnarray}
+\begin{eqnarray*}
 \Delta_r = \pars{R_{max}} ^ \frac{1}{n_r} - 1 ,& \Delta_\theta = \frac{\pi}{n_\theta}.
-\end{eqnarray}
+\end{eqnarray*}
 
 This grid induces a disjoint subdivision of the domain 
-$\Omega = [1, R_{max}] \times [0,\pi]$ into cells:
-\begin{eqnarray}
-\bigcup_{ij}\Omega_{ij} &=& \Omega.
-\end{eqnarray}
+$\Omega = [1, R_{max}] \times [0,\pi] = \bigcup_{ij}\Omega_{ij}$ into cells.
 A specific cell $\Omega_{ij}$ and its center $(\bar{r}_i, \bar{\theta}_j)$ are defined by:
-\begin{eqnarray}
+\begin{eqnarray*}
 \Omega_{ij} = [r_{i-1}, r_{i}] \times [\theta_{j-1}, \theta_{j}], &
@@
 \bar{\theta}_j = (\theta_{j-1} + \theta_{j})/2.
-\end{eqnarray}
+\end{eqnarray*}
 
@@
 using an all-centered grid:
-\begin{eqnarray}
+\begin{eqnarray*}
 \varPhi^h_{[i,j]} = \varPhi(\bar{r}_i, \bar{\theta}_j), &
@@
 P^h_{[i,j]} = P(\bar{r}_i, \bar{\theta}_j).
-\end{eqnarray}
+\end{eqnarray*}
 $\bV$ is represented by its values at cell boundaries, using a staggered grid:
-\begin{eqnarray}
+\begin{eqnarray*}
 V_r^h{}_{[i,j]} = V_r(r_i, \bar{\theta}_j), &
 V_\theta^h{}_{[i,j]} = V_\theta(\bar{r}_i, {\theta}_j).
-\end{eqnarray}
+\end{eqnarray*}
 
@@
 Define the following discrete central difference operators:
-\begin{eqnarray}
+\begin{eqnarray*}
 \cD_r(f^h){}_{\left[i+\half,j\right]} = \frac{f^h_{\left[i+1,j\right]} - f^h_{\left[i,j\right]}}
@@
 					   {\theta_{\left[i,j+1\right]} - \theta_{\left[i,j\right]}}.
-\end{eqnarray}
+\end{eqnarray*}
 
 Define the following linear interpolation operators:
-\begin{eqnarray}
+\begin{eqnarray*}
+\begin{array}{rcl}
 \cI_r(f^h)_{\left[i+\half,j\right]} &=& 
@@
   f^h_{\left[i,j\right]}.
-\end{eqnarray}
+\end{array}
+\end{eqnarray*}
 
 If the total flux of a cell is equal to zero ($\bnabla \cdot \boldsymbol{f} = 0$), then we have
-\begin{eqnarray}
+\begin{eqnarray*}
 \frac{1}{r^2} \cD_r\pars{f^h_r r^2} + 
@@
 \cD_\theta\pars{f^h_\theta \cdot r \sin\theta}}{r^2 \sin\theta} = 0. 
-\end{eqnarray}
+\end{eqnarray*}
 
 Ion flux ($\bI = - C \bnabla \varPhi$) is discretized on grid cell boundaries:
-\begin{eqnarray}
+\begin{eqnarray*}
 I^h_r = -\cI_r(C^h) \cdot \cD_r(\varPhi^h), &
 I^h_\theta = -\cI_\theta(C^h) \cdot \frac{\cD_\theta(\varPhi^h)}{r}.
-\end{eqnarray}
+\end{eqnarray*}
 
@@
 (using upwind scheme $\mathcal{U}$ for numerical stability at large cell Peclet number):
-\begin{eqnarray}
+\begin{eqnarray*}
 J^h_r = -\cD_r(C^h) + \alpha V^h_r \cdot \mathcal{U}^{\bV^h}_r (C^h), &
@@
  \mathcal{U}^{\bV^h}_\theta(C^h)[i,j] = C^h\left[i, j-\frac{\sign(V^h_\theta)}{2}\right]. 
-\end{eqnarray}
+\end{eqnarray*}
 
@@
 linear interpolation is used for the Coulomb force and for vector Laplacian components.
-\begin{eqnarray}
+\begin{eqnarray*}
 F^h_r &=& -\cD_r(P^h) 
@@
 \frac{1}{r^2 \sin\theta} \cD_\theta\pars{\cD_\theta(f^h) \cdot \sin\theta}.
-\end{eqnarray}
+\end{eqnarray*}
 
@@
 
-The boundary conditions at the ion-exchange boundary ($r=1$) are:
-\begin{eqnarray}
+The boundary conditions at the particle boundary ($r=1$) are:
+\begin{eqnarray*}
+\begin{array}{rcl}
 \cI_r(\varPhi^h) &=& -\cI_r(\log C^h), \\
@@
   \zeta^h &=& - \log \gamma - \cI_r(\varPhi^h).
-\end{eqnarray}
+\end{array}
+\end{eqnarray*}
 The equations are discretized using ``ghost'' points outside the interior of the domain:
-\begin{eqnarray}
+\begin{eqnarray*}
  \varPhi^h_{[1/2, j]} = \frac{\varPhi^h_{[0,j]} + \varPhi^h_{[1,j]}}{2} &=& 
@@
 	\frac{\log C^h_{[1,j]} - \log C^h_{[0,j]}}{\Delta r}. 
-\end{eqnarray}
+\end{eqnarray*}
 By adding and subtracting the equations, we have:
-\begin{eqnarray}
+\begin{eqnarray*}
 \varPhi^h_{[0,j]} &=& -\log\brcs{C^h_{[1,j]}}, \\
@@
                      = -\log\gamma -\frac{\varPhi^h_{[0,j]} + \varPhi^h_{[1,j]}}{2}.
-\end{eqnarray}
+\end{eqnarray*}
 The slip condition can be written as:
-\begin{eqnarray}
+\begin{eqnarray*}
 V_r^h{}_{[0,j]} &=& 0, \\
@@
   V^h_\theta{}_{[0,j]} &=& 2 V^h_\theta{}_{[1/2, j]} - V^h_\theta{}_{[1,j]}.
-\end{eqnarray}
+\end{eqnarray*}
 
 For $\theta = 0$ and $\theta = \pi$, the ``ghost'' points are defined by symmetry considerations:
-\begin{eqnarray} 
+\begin{eqnarray*} 
 \brc{l}{
@@
 } 
-\end{eqnarray}
-
-Far away from the ion-exchange boundary ($r\rightarrow\infty$) we have:
-\begin{eqnarray}
+\end{eqnarray*}
+
+Far away from the particle boundary ($r\rightarrow\infty$) we have:
+\begin{eqnarray*}
 \begin{array}{cccc}
@@
 V_\theta^h{}_{[n_r + 1, j]} = \cU \sin\theta_j.
-\end{array}\end{eqnarray}
+\end{array}\end{eqnarray*}
 
@@
 
-When the method converges, $\bx_n \rightarrow \bx_\infty$, 
+When the method converges, 
 the asymptotic convergence is in general quadratic:
-\begin{eqnarray}
+\begin{eqnarray*}
 \|\bx_{n+1} - \bx_\infty\| \le k \|\bx_{n} - \bx_\infty\|^2.
-\end{eqnarray}
+\end{eqnarray*}
 Thus, when the initial guess is close enough to the solution, the solver
@@
 Thus, each problem variable can be computed by applying an appropriate projection operator on $\bx$:
-\begin{eqnarray}
+\begin{eqnarray*}
 X &=& \cP_X(\bx) \mbox{ for } X \in \left\{\varPhi, C, V_r, V_\theta, P\right\}.
-\end{eqnarray}
+\end{eqnarray*}
 
@@
 are computed by applying the following nonlinear operators:
-\begin{eqnarray}
+\begin{eqnarray*}
 \begin{array}{ccccc}
@@
 \end{array}
-\end{eqnarray}
+\end{eqnarray*}
 The extended system variable can be written as $\tilde{\bx} = \cB(\bx)$, 
@@
 The problem can be cast as the following nonlinear system (where $\cO = \cE \circ \cB$):
-\begin{eqnarray}
+\begin{eqnarray*}
 \cO(\bx) = \bzero.
-\end{eqnarray}
+\end{eqnarray*}
 
@@
 Let $\beta$ be a given nondimensional electric field.
-Assume that $\cU \ui$ is the drift velocity of the ion exchanger 
-(given that the fluid is at rest far away from the particle).
-After the convergence of the solver, $\cO(\bx_\infty) \rightarrow \bzero$, 
-the ``ghost'' point values are updated using $\tilde\bx_\infty = \cB(\bx_\infty)$,
-so  that the surface force $\boldsymbol{f} = \tT \cdot \bn$ acting 
-on the ion-exchanger surface
-can be computed by integration over the ion exchanger's surface $\mathcal S$.
+Assume that $\cU \ui$ is the drift velocity of the particle 
+(given that the fluid is at rest far away from it).
+After the convergence of the solver, when the residual norm is below
+a prescribed threshold $\|\cO(\bx_n)\| < \epsilon$, 
+the ``ghost'' point values are updated using $\tilde\bx = \cB(\bx_n)$,
+so  that the surface force $\boldsymbol{f} = \tT \cdot \bn$ 
+can be computed by integration over the surface.
 
@@
 aligned with $\ui$ and it vanishes iff $\ui \cdot \bF = 0$.
-\begin{eqnarray}
+\begin{eqnarray*}
 F_\imath = \ui \cdot \bF &=& 
@@
 + \frac{1}{r}\cD_r(\varPhi) \cD_{\theta}(\varPhi)}\sin\theta.
-\end{eqnarray}
+\end{eqnarray*}
 
@@
 If $\cO$ is linear, it can be represented by a matrix $L$, such that:
-\begin{eqnarray}
+\begin{eqnarray*}
 \cO(\bx) &=& L \bx, \\
 \bnabla\cO &=& L. 
-\end{eqnarray}
+\end{eqnarray*}
 Note that finite difference $\cD$, interpolation $\cI$ and 
@@
 represent pointwise application of $f$:
-\begin{eqnarray}
+\begin{eqnarray*}
 \cF(\bx) &=& [f(x_1); \ldots; f(x_n)], \\
 \bnabla\cF(\bx) &=& \diag\{f'(x_1), \ldots, f'(x_n)\}.
-\end{eqnarray}
+\end{eqnarray*}
 $f$ is defined and differentiated automatically using the MATLAB symbolic toolbox.
@@
 (that does not depend on $\bx$):
-\begin{eqnarray}
+\begin{eqnarray*}
 \mathcal{C}(\bx) &=& \bc, \\
 \bnabla\mathcal{C} &=& \bzero.
-\end{eqnarray}
+\end{eqnarray*}
 
@@
 and multiplication, are defined as follows:
-\begin{eqnarray}
+\begin{eqnarray*}
 (\cO_1 \pm \cO_2)(\bx) &=& \cO_1(\bx) \pm \cO_2(\bx), \\
@@
                                   + \diag(\cO_1(\bx)) \bnabla\cO_2(\bx).
-\end{eqnarray}
+\end{eqnarray*}
 
@@
 Given $N$ operators $\{\cO_i\}_{i=1}^N$, their concatenation $\cO$ is defined as:
-\begin{eqnarray}
+\begin{eqnarray*}
 \cO(\bx) &=& [\cO_1(\bx); \ldots; \cO_N(\bx)], \\
 (\bnabla\cO)(\bx) &=& [(\bnabla\cO_1)(\bx); \ldots; (\bnabla\cO_N)(\bx)].
-\end{eqnarray}
+\end{eqnarray*}
 
@@
 the ``ghost'' point values are computed via $\cB(\bx_\infty)$,
-followed by a computation of the total force $\bF$ acting on the ion-exchanger.
+followed by a computation of the total force $\bF$ acting on the particle.
 $F_\imath = \bF \cdot \ui$ is computed by using the mid-point quadrature rule
-\begin{eqnarray}
+\begin{eqnarray*}
 F_\imath = \sum_{i=1}^{n_\theta} f(\bar\theta_i) \cdot 
               2 \pi \sin\bar\theta_i \cdot \Delta\theta_i.
-\end{eqnarray}
+\end{eqnarray*}
 
@@
 \label{PDEs}
-\begin{eqnarray}
+\begin{eqnarray*}
 \begin{array}{cccc}
@@
 \bLaplacian \bV - \bnabla P + \Laplacian \varPhi \bnabla \varPhi = \bzero.
-\end{array}\end{eqnarray}
+\end{array}\end{eqnarray*}
 
@@
 $\cV = -\log \gamma$, the boundary conditions at $r = 1$ are given by
-\begin{eqnarray}
+\begin{eqnarray*}
 \begin{array}{rcl}
@@
 \end{array}
-\end{eqnarray}
+\end{eqnarray*}
 
 The boundary conditions for $r \rightarrow \infty$ are given by
-\begin{eqnarray}
+\begin{eqnarray*}
 \bnabla \varPhi = -\beta \ui, &
@@
 \bV = -\cU \ui,
-\end{eqnarray}
+\end{eqnarray*}
 and the total force acting on the particle is zero: $\bF = \bzero$.
@@
 The nonlinear system can be written as: 
-\begin{eqnarray}
+\begin{eqnarray*}
 \cO(\bx;\beta) &=& \bzero.
-\end{eqnarray}
+\end{eqnarray*}
 
 For small $\beta$, the solution to the nonlinear system can be expanded in a Taylor series in $\beta$.
-\begin{eqnarray}
+\begin{eqnarray*}
 \bx = \bx(\beta) &\approx& \sum_n \bx_n \beta^n.
-\end{eqnarray}
+\end{eqnarray*}
 
 All the variables are expanded around $\beta = 0$:
-\begin{eqnarray}
+\begin{eqnarray*}
 \varPhi = \sum_i \beta^i \varPhi_i, &
@@
 \Psi = \sum_i \beta^i \Psi_i,
-\end{eqnarray}
+\end{eqnarray*}
 where the velocity $\bV$ and pressure $P$ are computed from the streamfunction $\Psi$:
-\begin{eqnarray}
+\begin{eqnarray*}
 \bV &=& \bnabla \times \pars{\frac{\Psi}{r \sin\theta} \bphihat} 
@@
 - \frac{1}{r \sin\theta} \deriv{\Psi}{r} \bthetahat.
-\end{eqnarray}
+\end{eqnarray*}
 
@@
 are expanded around $\beta = 0$:
-\begin{eqnarray}
+\begin{eqnarray*}
 \bzero = \cO(\bx) = \sum_i \cO_i(\bx_0, \ldots \bx_i) \beta^i
-\end{eqnarray}
+\end{eqnarray*}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Linear Solution $(k=1)$} \label{app:linear}
+\subsection{First-Order (linear in $\beta$) Solution} \label{app:linear}
 
 For $\beta = 0$ (no electric field is applied), the steady-state solution is $\cU = 0$:
-\begin{eqnarray}
-\varPhi_0(r,\theta) &=& 0, \\
-C_0(r,\theta) &=& 1, \\
-\bV_0(r,\theta) &=& \bzero, \\
-P_0(r,\theta) &=& 0.
-\end{eqnarray}
+\begin{eqnarray*}\begin{array}{cccc}
+\varPhi_0(r,\theta) = 0, &
+C_0(r,\theta) = 1, &
+\bV_0(r,\theta) = \bzero, &
+P_0(r,\theta) = 0.
+\end{array}\end{eqnarray*}
 
 Assuming $\beta \ll 1$, the linearized equations and boundary conditions are 
-(as developed in \cite{yariv2010migration}):
-\begin{eqnarray}
-\Laplacian \varPhi_1 &=& 0, \\
-\Laplacian C_1 &=& 0, \\
-\bLaplacian \bV_1 - \bnabla P_1 &=& \bzero.
-\end{eqnarray}
+(\cite{yariv2010migration}):
+\begin{eqnarray*}
+\Laplacian \varPhi_1 = 0, &
+\Laplacian C_1 = 0, &
+\bLaplacian \bV_1 - \bnabla P_1 = \bzero.
+\end{eqnarray*}
 
 The first-order terms are given by
-\begin{eqnarray}
-\varPhi &=& \beta \pars{\frac{1}{4r^2} - r}\cos\theta, \\
-C &=& 1 + \beta \frac{3}{4r^2} \cos\theta, \\
-\Psi &=& \beta \cU_1 \pars{\frac{1}{r} - r^2} \frac{\sin^2\theta}{2}, \\
-\bV &=& -\beta \cU_1 \brcs{\pars{1 - \frac{1}{r^3}}\cos\theta \cdot \brhat - 
-                               \pars{1 + \frac{1}{2r^3}} \sin\theta \cdot \bthetahat}, \\
-P &=& 0, \\
-\bF &=& \bzero.
-\end{eqnarray}
-
-The slip velocity satisfies
-\begin{eqnarray}
-\beta \cU_1 \frac{3}{2} \sin\theta =
-V_\theta &=& 4 \log \pars{\frac{1 + e ^ \frac{\zeta}{2}}{2}} \deriv{\varPhi}{\theta} 
-=
- 3 \beta \log \pars{\frac{1 + e ^ \frac{\zeta}{2}}{2}} \sin\theta, \\
-\cU_1 &=& 2 \log \pars{\frac{1 + e ^ \frac{\zeta}{2}}{2}} 
-       =  2 \log \pars{\frac{1 + \gamma ^ {-\frac{1}{2}}}{2}}.
-\end{eqnarray}
-because $\varPhi_1 = -C_1 = -\frac{3}{4} \cos\theta$ on $r=1$
-and $\zeta_0 = -\log\gamma$.
+\begin{eqnarray*}
+\begin{array}{ccccc}
+\varPhi = \beta \pars{\frac{1}{4r^2} - r}\cos\theta, &
+C = 1 + \beta \frac{3}{4r^2} \cos\theta, &
+\Psi = \beta \cU_1 \pars{\frac{1}{r} - r^2} \frac{\sin^2\theta}{2}, &
+P = 0, &
+\bF = \bzero.
+\end{array}
+\end{eqnarray*}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Nonlinear Solution ($k > 1$)} \label{app:cubic}
-Note that, due to symmetry considerations, $\cU(\beta)$ is an anti-symmetric function:
-\begin{eqnarray}
-\cU(-\beta) &=& -\cU(\beta).
-\end{eqnarray}
+\subsection{Third-Order (cubic in $\beta$) Solution} \label{app:cubic}
+Note that, due to symmetry considerations, $\cU(\beta)$ is an anti-symmetric function.
 Therefore, $\cU_2 = 0$ and the next velocity term is the cubic one:
-\begin{eqnarray}
+\begin{eqnarray*}
 \cU(\beta) &\approx& \beta \cU_1 + \beta^3 \cU_3 + O(\beta^5).
-\end{eqnarray}
+\end{eqnarray*}
 
 In order to find the cubic terms, the quadratic terms must be computed first.
-
 The quadratic terms $\bx_2$ are computed by solving a linear PDE system 
-with a right-hand side determined by the linear terms $\bx_1$:
-\begin{eqnarray}
-\varPhi_2 &=& \frac{\left(\frac{\cU_1\, \alpha}{32} - \frac{1}{16}\right)\, \left(3\, {\cos^2\theta} - 1\right)}{r^3} - \frac{3}{32\, r^4} - \frac{3\, {\sin^2\theta}\, \left(4\, r^3 - 1\right)}{32\, r^4} - \frac{3\, \cU_1\, \alpha - 6}{32\, r},
-\\
-C_2 &=& \frac{\left(\frac{5\, \cU_1\, \alpha}{32} + \frac{1}{16}\right)\, \left(3\, {\cos^2\theta} - 1\right)}{r^3} - \frac{3\, \cU_1\, \alpha - 6}{32\, r} + \frac{3\, \cU_1\, \alpha\, \left(2\, r^3\, {\sin^2\theta} + {\sin^2\theta} - 1\right)}{16\, r^4},
-\\
-\Psi_2 &=& \pars{\frac{9}{16(\sqrt{\gamma}+1)} - \frac{3}{16} \cU_1 (\cU_1 \alpha + 1)}
- \left(\frac{1}{r^2} - 1\right) \sin^2\theta \cos\theta,  \\
-\bF_2 &=& \bzero, \\ \cU_2 &=& 0.
-\end{eqnarray}
+with a right-hand side determined by the linear terms $\bx_1$.
 Note that the quadratic term does not contribute to the total force and steady-state 
@@
 The cubic terms $\bx_3$ are computed by solving a linear PDE system 
-with a right-hand side determined by the linear terms $\bx_1$ and the quadratic terms $\bx_2$:
-\begin{eqnarray}
-\varPhi_3 &=& \cos\theta \left(\frac{15 \cU_1\alpha}{64} + \frac{3}{32}\right) - \frac{3 \cU_1\alpha {\cos}^3\theta}{32} - \frac{\cos\theta \left( - 183 {\cU_1}^2\alpha^2 + 839 \cU_1\alpha + 470\right)}{2560 r^2} \\
-&&+ \frac{3 \cos\theta \left(5 \cU_1\alpha - 6 {\cos^2\theta} - 4 \cU_1\alpha {\cos^2\theta} + 4\right)}{64 r^3} + \frac{\left(2 \cU_1\alpha - 1\right) \left(\cos\theta - 3 {\cos}^3\theta\right)}{64 r^5}
-\\ 
-&&- \frac{\left(3 \cos\theta - 5 {\cos}^3\theta\right)}{r^4} 
-\left( - \frac{19 {\cU_1}^2\alpha^2}{5120} + \frac{97 \cU_1\alpha}{5120} + 
-\frac{3 \cU_2\alpha}{320} + \frac{21}{1280}\right) \\
-&& + \frac{{\cos}^3\theta}{r^2} \left(\frac{15 \cU_1\alpha}{64} + \frac{3}{32}\right)  
-+ \frac{{\cos}^3\theta}{r^6} \left(\frac{\cU_1\alpha}{64} + \frac{3}{64}\right),
-\\
-C_3 &=&
-\frac{3 {{\cU_1}}^2\alpha^2 {\cos^3\theta}}{32} + \frac{\cos\theta \left(797 {{\cU_1}}^2\alpha^2 + 419 {\cU_1}\alpha - 512 {\cU_2}\alpha + 174\right)}{2560 r^2} \\
-&&- \left(\frac{59 {{\cU_1}}^2\alpha^2}{5120} + \frac{103 {\cU_1}\alpha}{5120} + \frac{69 {\cU_2}\alpha}{320} + \frac{3}{1280}\right)\frac{\left(3 \cos\theta - 5 {\cos^3\theta}\right)}{r^4} \\
-&&- \frac{3\alpha \cos\theta \left( - 8\alpha {{\cU_1}}^2 {\cos^2\theta} + 7\alpha {{\cU_1}}^2 + 2 {\cU_1} + 32 {\cU_2} {\cos^2\theta} - 32 {\cU_2}\right)}{128 r^3} - \frac{3 {\cU_1}\alpha \cos\theta \left(5 {\cU_1}\alpha + 2\right)}{64} \\
-&&+ \frac{\alpha \left(\cos\theta - 3 {\cos^3\theta}\right) \left(5\alpha {{\cU_1}}^2 + 2 {\cU_1} + 16 {\cU_2}\right)}{128 r^5} + \frac{{{\cU_1}}^2\alpha^2 {\cos^3\theta}}{32 r^6} - \frac{3 {\cU_1}\alpha {\cos^3\theta} \left(5 {\cU_1}\alpha + 2\right)}{64 r^2},
-\\
-\Psi_3 &=&
-r^2 {\sin^2\theta} \left(\frac{{\cW_2}}{15} - \frac{{\cW_1}}{3} + \frac{209}{3360}\right) 
- - \frac{{\sin^2\theta}}{r} \left(\frac{5 {\cW_2}}{3} - \frac{{\cW_1}}{3} + \frac{35}{264}\right)
-\\ && + \frac{{\sin^4\theta} \left(2 {\cW_2} + \frac{761}{5632}\right)}{r} - \frac{{\sin^2\theta} \left(1848 r^6 {\sin^2\theta} - 2079 r^3 {\sin^2\theta} + 924 r^3 - 7 {\sin^2\theta} + 10\right)}{19712 r^5}
-\\ && + \frac{\left(\frac{2 {\cW_2}}{5} + \frac{829}{28160}\right) \left(4 {\sin^2\theta} - 5 {\sin^4\theta}\right)}{r^3} + \frac{{\sin^2\theta} \left(\frac{{\cU_1}\alpha}{16} - \frac{1}{8}\right) \left(2 r^3 - 3 r^2 + 1\right)}{4 r},
-\\
-\cW_1 &=& \frac{69}{512 \left(\sqrt{\gamma} + 1\right)} - \frac{1407\alpha^2 {\log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}^3}{1280} - \frac{123 \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{1280} - \frac{27}{512 {\left(\sqrt{\gamma} + 1\right)}^2} \\ && -
-\frac{1899\alpha {\log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}^2}{2560} - \frac{\alpha \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right) \left(\frac{81}{16 \left(\sqrt{\gamma} + 1\right)} - \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right) \left(\frac{27\alpha \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{4} + \frac{27}{8}\right)\right)}{320} \\ && +
-\frac{21\alpha \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{128 \left(\sqrt{\gamma} + 1\right)},
-\\
-\cW_2 &=& \frac{9 \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{256} + \frac{21\alpha^2 {\log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}^3}{64} - \frac{27}{512 \left(\sqrt{\gamma} + 1\right)} - \frac{27}{512 {\left(\sqrt{\gamma} + 1\right)}^2}
- + \frac{15\alpha {\log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}^2}{64} 
-\\ && 
-- \frac{297\alpha \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{1024 \left(\sqrt{\gamma} + 1\right)}.
-\end{eqnarray}
-
+with a right-hand side determined by the linear terms $\bx_1$ and the quadratic terms $\bx_2$.
 The cubic solution satisfies the $\lim_{r\rightarrow\infty}C_3 = 0$ boundary condition, 
@@
 The steady-state velocity can be expanded using odd powers of $\beta$:
-\begin{eqnarray}
+\begin{eqnarray*}
 \cU(\beta, \gamma) &=& \cU_1(\gamma) \beta + \cU_3(\gamma) \beta^3.
-\end{eqnarray}
+\end{eqnarray*}
 
 The linear and the cubic velocity terms (for $\alpha = 0$) are then
-\begin{eqnarray}
+\begin{eqnarray*}
 \cU_1(\gamma) &=& 2 \log \pars{\frac{1 + \gamma^{-\frac{1}{2}}}{2}}, \\
 \cU_3(\gamma) &=& \frac{31}{320(\sqrt\gamma + 1)} - \frac{9}{320(\sqrt\gamma + 1)^2} + \frac{1}{1680} - \frac{11}{160} \log \pars{\frac{1 + \gamma^{-\frac{1}{2}}}{2}}.
-\end{eqnarray}
+\end{eqnarray*}
 
 Note that, for $\gamma = 1$, the linear term vanishes and the velocity leading term is $O(\beta^3)$:
-\begin{eqnarray}
+\begin{eqnarray*}
 \cU(\beta) = \frac{1129}{26880}\beta^3.
-\end{eqnarray}
+\end{eqnarray*}
 
@@
 if it satisfies:
-\begin{eqnarray}
+\begin{eqnarray*}
 \beta_c^2 = -\frac{\cU_1(\gamma)}{\cU_3(\gamma)}.
-\end{eqnarray}
+\end{eqnarray*}
 For $\gamma = 1 + \eps$, where $0 < \eps \ll 1$:
-\begin{eqnarray}
+\begin{eqnarray*}
 \beta_c \approx \sqrt{-\frac{\cU_1'(1) \eps}{\cU_3(1)}} = 
  \sqrt{\frac{13440 \eps}{1129}} \approx 3.45 \sqrt{\eps}.
-\end{eqnarray}
+\end{eqnarray*}
 However, for $\gamma \gg 1$, we have:
-\begin{eqnarray}
+\begin{eqnarray*}
 \beta_c =  \pars{\frac{11}{320} + \frac{1}{1680 \log 4}}^{-\frac{1}{2}} \approx 5.36.
-\end{eqnarray}
+\end{eqnarray*}
 
@@
 The numerical solver is applied to the nonlinear problem of the migration ion-exchanger
-driven by an electric field (as described in \cite{yariv2010migration}).
-
+driven by an electric field (as described in \cite{yariv2010migration})
+and the electrophoresis of highly charged surface inert particle 
+(as described in \cite{schnitzer2012surface}). 
 The computational grid for the problem is chosen to be of size $400 \times 50$.
-
 Because there are five different variables ($\varPhi, C, V_r, V_\theta, P$), the concatenated
 variable $\bx$ has dimension of $\sim 10^5$.
-
 $R_{\max}$ is chosen to be $10^{7}$ so the truncation effect is negligible.
-
 The solver is applied to a series of values of $\beta$, ranging 
@@
 is applied to various values of $\gamma$, representing various ion-exchangers.
-
 The resulting $\cU(\beta)$ is plotted on a log-log scale, so that the asymptotic behaviour
@@
 In order to validate the numerical solver, an asymptotic analysis of the nonlinear system
-is performed as described in \ref{sec:asymp}. The numerical results are compared 
+is performed as described in Section \ref{sec:asymp}. The numerical results are compared 
 to the asymptotic solutions, and good correspondence is achieved.
@@
 \subsection{Linear Regime}
-For $\beta \ll 1$, the linear regime is dominant (for derivation, see \ref{app:linear}):
-\begin{eqnarray}
-\cU = 2\log\pars{\frac{1 + \gamma^{-\frac{1}{2}}}{2}}\beta.
-\end{eqnarray}
+For $\beta \ll 1$, the linear regime is dominant: $\cU = 2\log\pars{\frac{1 + \gamma^{-\frac{1}{2}}}{2}}\beta$.
+
 Thus, for $\gamma > 1$, the Debye layer has a positive space charge, corresponding to a negative
@@
 
-The numerical and asymptotic analytical solutions for the linear regime are compared for 
-for $\gamma > 1$ (in Figure \ref{fig:Linear1})  
-and for $\gamma < 1$ (in Figure \ref{fig:Linear2}).
+The numerical and asymptotic analytical solutions for the linear regime are compared 
+in Figure \ref{fig:Linear}.
 
@@
 When $\gamma \approx 1$, the cubic regime, where $\cU = O(\beta^3)$, 
-dominates the linear one, even for weak electric fields
-(for derivation, see \ref{app:cubic}).
-
+dominates the linear one, even for weak electric fields. 
 This phenomenon is confirmed both by the numerical
@@
 field value $\beta_c = O(\sqrt{|\gamma - 1|})$.
-
 The numerical results, as well as the analytical ones, are given in Figure
@@
 $|\log\gamma| \approx 3\beta / 4$. This results in a sign change in the slip velocity,
-which can be approximated for small $|\zeta| \ll 1$ as:
-\begin{eqnarray}
-V_\theta \approx \zeta \cdot \bnabla_S \varPhi.
-\end{eqnarray} 
+which can be approximated for small $|\zeta| \ll 1$ as $V_\theta \approx \zeta \cdot \bnabla_S \varPhi$.
 This sign change creates a vortex at the downstream end of the ion-exchanger, 
@@
     \begin{center}
-    \includegraphics[width=0.8\textwidth]{figs/linearNeg.eps}
+    \includegraphics[width=0.45\textwidth]{figs/linearNeg.eps}
+    \includegraphics[width=0.45\textwidth]{figs/linearPos.eps}
     \caption{Steady-state velocity $\cU$ as a function of the 
-        electric field magnitude $\beta$, for $\gamma > 1$. 
-        The analytic solution velocity is represented by dashed lines, and the numerical
-        results are represented by squares.}
-    \label{fig:Linear1}
+        electric field magnitude $\beta$, for $\gamma > 1$ (left) 
+        and $\gamma > 1$ (right). 
+        The analytic solution velocity is represented by lines, and the numerical
+        results are represented by markers.}
+    \label{fig:Linear}
     \end{center}
@@
 \begin{figure}[htbp]
-    \begin{center}
-    \includegraphics[width=0.8\textwidth]{figs/linearPos.eps}
-    \caption{Steady-state velocity $\cU$ as a function of the 
-        electric field magnitude $\beta$, for $\gamma < 1$. 
-        The analytic solution velocity is represented by solid lines, and the numerical
-        results are represented by circles.}
-    \label{fig:Linear2}
-    \end{center}
 \end{figure}
@@
     \begin{center}
-    \includegraphics[width=0.45\textwidth]{figs/Cubic/g=0.999900.eps}
-    \includegraphics[width=0.45\textwidth]{figs/Cubic/g=0.999000.eps}
-    \includegraphics[width=0.45\textwidth]{figs/Cubic/g=0.990000.eps}
-    \includegraphics[width=0.45\textwidth]{figs/Cubic/g=0.900000.eps}
+    \includegraphics[width=0.22\textwidth]{figs/Cubic/g=0.999900.eps}
+    \includegraphics[width=0.22\textwidth]{figs/Cubic/g=0.999000.eps}
+    \includegraphics[width=0.22\textwidth]{figs/Cubic/g=0.990000.eps}
+    \includegraphics[width=0.22\textwidth]{figs/Cubic/g=0.900000.eps}
         \caption{Steady-state velocity $\cU$ as a function of the 
@@
     \begin{center}
-    \includegraphics[width=0.45\textwidth]{figs/Cubic/g=1.000100.eps}
-    \includegraphics[width=0.45\textwidth]{figs/Cubic/g=1.001000.eps}
-    \includegraphics[width=0.45\textwidth]{figs/Cubic/g=1.010000.eps}
-    \includegraphics[width=0.45\textwidth]{figs/Cubic/g=1.100000.eps}
+    \includegraphics[width=0.22\textwidth]{figs/Cubic/g=1.000100.eps}
+    \includegraphics[width=0.22\textwidth]{figs/Cubic/g=1.001000.eps}
+    \includegraphics[width=0.22\textwidth]{figs/Cubic/g=1.010000.eps}
+    \includegraphics[width=0.22\textwidth]{figs/Cubic/g=1.100000.eps}
         \caption{Steady-state velocity $\cU$ as a function of the 
@@
 \section*{Acknowledgments}
-The author thanks the anonymous authors whose work largely
-constitutes this sample file. This research was supported by ???.
+...
 

### 2012-09-11 notes/work/ijnam.tex
work on LaTeX

@@
     \begin{center}
-        \includegraphics[width=0.33\textwidth]
+        \includegraphics[width=0.35\textwidth]
             {figs/debye.eps}
@@
 
-The goal of this work is to develop and implement an iterative numerical
-solver for nonlinear electrokinetic problems, and apply it to the study
+The goal of this work is to develop and implement a software toolbox for the generation
+of iterative numerical solvers for nonlinear electrokinetic problems, and apply it to the study
 of systems that have no closed-form solutions, such as an ion-exchanger migration
@@
 \end{eqnarray}
-\begin{eqnarray} \label{poisson}
+\begin{eqnarray} \label{eq:poisson}
 c_+ - c_- &=& -2\delta^2 \Laplacian \varphi,
@@
 The ionic fluxes are given by ion diffusion, electrostatic forces and ion advection by the fluid
-at Eq. \ref{eq:nernst}. Due to conservation of ions, the fluxes are divergence-free:
+at Eq. \eqref{eq:nernst}. Due to conservation of ions, the fluxes are divergence-free:
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-These equation may be re-written by using salt $c = (c_+ + c_-)/2$ and charge $q = (c_+ - c_-)/2$.
+These equations may be re-written by using salt $c = (c_+ + c_-)/2$ and charge $q = (c_+ - c_-)/2$.
 Thus, salt and charge fluxes are defined by:
-\begin{eqnarray*}
+\begin{eqnarray} \label{eq:fluxes}
   \bj = \frac{\bj_+ + \bj_-}{2} = -\bnabla c - q \bnabla \varphi + \alpha \bv c &,& 
   \bi = \frac{\bj_+ - \bj_-}{2} = -\bnabla q - c \bnabla \varphi + \alpha \bv q,
-\end{eqnarray*}
+\end{eqnarray}
 and are divergence-free as well:
-\begin{eqnarray*}
+\begin{eqnarray} \label{eq:zero_flux}
 \bnabla \cdot \bj = 0 &,& 
 \bnabla \cdot \bi = 0. 
-\end{eqnarray*}
-In addition, the charge is governed by the Poisson equation:
-\begin{eqnarray*}
+\end{eqnarray}
+In addition, the charge concentration is governed by the Poisson equation \eqref{eq:poisson}
+\begin{eqnarray}
 q &=& -\delta^2 \Laplacian \varphi.
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 and ambient ionic concentrations:
-\begin{eqnarray*}
+\begin{eqnarray} \label{eq:bndcond_inf}
 \bv \rightarrow -\cU \ui, &
@@
  c_\pm \rightarrow 1.
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 $\bn \cdot \bj_+ = k (1 - c_+/\gamma)$, where $k \rightarrow \infty$):
-\begin{eqnarray*}
+\begin{eqnarray}
 \begin{array}{cccc}
@@
 \end{array}
-\end{eqnarray*}
+\end{eqnarray}
 where $\gamma$ is the ratio between the cationic concentration on the surface and the cationic
@@
 zero slip and ion impermeability:
-\begin{eqnarray*}
+\begin{eqnarray}
 \begin{array}{cccc}
@@
 \end{array}
-\end{eqnarray*}
+\end{eqnarray}
 where $\chi$ is the ratio between the dielectric constants of the 
@@
 This boundary layer makes it very hard to construct 
-a direct numerical solver of the electro-kinetic problem.
+a direct numerical solver for the full electro-kinetic problem.
 
@@
 the PDE system can be rewritten in the ``inner'' region 
-as an ODE system and can be integrated and solved analytically,
-yielding an ``effective'' boundary conditions for the ``outer'' bulk region equations.
+as an ODE system using the asymptotic limit of $\delta \rightarrow 0$ 
+and can be integrated and solved analytically,
+yielding an ``effective'' boundary conditions for the ``outer'' bulk region equations near
+the particle surface.
 
 \subsubsection  {Bulk-scale equations}
-The Nernst-Planck equations above for the fluid bulk (outside
+The Nernst-Planck equations above \eqref{eq:fluxes} for the fluid bulk (outside
 the boundary layer), using bulk variables denoted by uppercase letters, read:
-\begin{eqnarray*}
-\begin{array}{cccc}
+\begin{eqnarray} \begin{array}{cccc} \label{eq:bulk_flux}
   Q = 0, &
@@
 \bI = -C \bnabla \varPhi.
-\end{array}\end{eqnarray*}
+\end{array}\end{eqnarray}
 Because the flow is incompressible ($\bnabla \cdot V = 0$), 
 ion conservation results in the following 
-salt and charge conservation equations:
-\begin{eqnarray*} 
-0 &=& \bnabla \cdot \bJ = \Laplacian C - \alpha \bV \cdot \bnabla C, \\
-0 &=& \bnabla \cdot \bI = \bnabla \cdot \pars{ C \bnabla \varPhi }.
-\end{eqnarray*}
-The macroscale Stokes flow equations have the same form as the microscale equations:
-\begin{eqnarray*} 
-0 &=& \bnabla \cdot \bV, \\   
-\bzero &=& \Laplacian \bV - \bnabla P + \bnabla \varPhi \Laplacian \varPhi.
-\end{eqnarray*}
+salt and charge conservation equations -- the salt and charge fluxes above 
+\eqref{eq:bulk_flux} are divergence-free
+\eqref{eq:zero_flux}:
+\begin{eqnarray} 
+\label{eq:salt_charge}
+\Laplacian C - \alpha \bV \cdot \bnabla C = 0, &
+\bnabla \cdot \pars{ C \bnabla \varPhi } = 0.
+\end{eqnarray}
+The macroscale Stokes flow equations have the same form as before \eqref{eq:stokes}:
+\begin{eqnarray} 
+\bnabla \cdot \bV = 0, &   
+\Laplacian \bV - \bnabla P + \bnabla \varPhi \Laplacian \varPhi = \bzero.
+\end{eqnarray}
 
@@
 \subsubsection{Ion-exchanger} See \cite{yariv2010migration} for full derivation:
-\begin{eqnarray*} 
-0 &=& \varPhi + \log C, \\ 
-0 &=& \deriv{}{n} \pars{\varPhi - \log C}, \\ 
-\bV &=& 
+\begin{eqnarray} \label{eq:ionex_bnd}
+0 = \varPhi + \log C, &
+0 = \deriv{}{n} \pars{\varPhi - \log C}, &
+\bV = 
 \zeta \cdot \bnabla_\mathcal{S} \varPhi 
 + 2\log\pars{1-\tanh^2\frac{\zeta}{4}} \cdot \bnabla_\mathcal{S} \log C,
-\end{eqnarray*}
+\end{eqnarray}
 where $\zeta = \cV - \varPhi = \log (C / \gamma)$ 
-is the zeta potential (the voltage drop across the Debye layer).
+is the zeta potential.
 
@@
 See \cite{schnitzer2012surface} for full derivation:
-\begin{eqnarray*} 
-0 &=& {\deriv{C}{n} - \text{Du} \nabla^2_s \pars{\varPhi - \log C}} \\ 
-0 &=& {\deriv{C}{n} + C \deriv{\varPhi}{n}}, \\ 
-\bV &=& \zeta \cdot \bnabla_\mathcal{S} \pars{\varPhi - \log C} +
+\begin{eqnarray} \label{eq:ephor_bnd}
+0 = {\deriv{C}{n} - \text{Du} \nabla^2_s \pars{\varPhi - \log C}}, & 
+0 = {\deriv{C}{n} + C \deriv{\varPhi}{n}}, &
+\bV = \zeta \cdot \bnabla_\mathcal{S} \pars{\varPhi - \log C} +
 4 \log 2 \cdot \bnabla_\mathcal{S} \log C,
-\end{eqnarray*}
+\end{eqnarray}
 where $\zeta = \bar{\zeta} - \log C$ 
-is the zeta potential (the voltage drop across the Debye layer)
-and $\bar{\zeta} = 2 \log \sigma$.
+is the zeta potential and $\bar{\zeta} = 2 \log \sigma$.
 
 \subsection{Steady state}
-The stress tensor is composed of Newtonian and Maxwel stresses:
-\begin{eqnarray*} 
+The stress tensor in the fluid is composed of Newtonian and Maxwel stresses:
+\begin{eqnarray} \label{eq:tensor}
 \tT &=& \bnabla \bV + (\bnabla \bV)^\dagger - P \tI
-+ \bnabla \varPhi \bnabla \varPhi - \frac{1}{2} (\bnabla \varPhi \cdot \bnabla \varPhi) \tI, \\
- \bnabla \cdot \tT &=& \bzero.
-\end{eqnarray*}
++ \bnabla \varPhi \bnabla \varPhi - \frac{1}{2} (\bnabla \varPhi \cdot \bnabla \varPhi). 
+\end{eqnarray}
 In steady state (constant particle drift velocity $\cU$), the total force acting on the particle 
 (computed by the following surface integral) must vanish:
-\begin{eqnarray*}
+\begin{eqnarray} \label{eq:zero_force}
  \bF = \oint_\mathcal{S} \tT \cdot \bnhat dA = \bzero.
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 We seek the steady-state velocity $\cU$, 
-which corresponds to zero total force,
-\begin{eqnarray*} 
-F(\beta, \cU) = 0,
-\end{eqnarray*}
+which corresponds to zero total force, $F(\beta, \cU) = 0$,
 which we solve by the standard secant method.
 
-\subsection{Discretization}
-\subsubsection{Spherical Coordinates}
+\subsection{Spherical Coordinates}
 Because the system is axisymmetric, we employ
@@
 
-\subsubsection{Computational Grid}
+\subsection{Computational Grid}
 A regular grid of size $n_r \times n_\theta$ is defined, with:
@@
 where a logarithmic grid spacing has been chosen for $r$ and a uniform grid for $\theta$.
-Note that $r_0 = 1$ and $R_{max} = (1+\Delta_r)^{n_r}$ should be much 
-larger than $r_0$. Thus:
+Note that $r_0 = 1$ and $R_{max} = (1+\Delta_r)^{n_r}$, where
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-
+Because the grid is finite, the choice 
+$R_{max}$ must be taken large enough so as to have a negligible effect
+on the solution.
 This grid induces a disjoint subdivision of the domain 
@@
 
-\subsubsection{Operator Discretization}
+\subsection{Operator Discretization} 
 A finite-volume method with linear interpolation is used for flux discretization.
@@
 
-Ion flux ($\bI = - C \bnabla \varPhi$) is discretized on grid cell boundaries:
-\begin{eqnarray*}
+\subsection{System Equations} \label{sec:disc_equations}
+Charge and salt fluxes \eqref{eq:bulk_flux} are discretized on grid cell boundaries 
+(using upwind scheme $\mathcal{U}$ for numerical stability at large cell Peclet number):
+\begin{eqnarray} \nonumber
 I^h_r = -\cI_r(C^h) \cdot \cD_r(\varPhi^h), &
-I^h_\theta = -\cI_\theta(C^h) \cdot \frac{\cD_\theta(\varPhi^h)}{r}.
-\end{eqnarray*}
-
-Salt flux ($\bJ = -\bnabla C + \alpha \bV C$) is discretized on grid cell boundaries 
-(using upwind scheme $\mathcal{U}$ for numerical stability at large cell Peclet number):
-\begin{eqnarray*}
+I^h_\theta = -\cI_\theta(C^h) \cdot \frac{\cD_\theta(\varPhi^h)}{r}, \\
 J^h_r = -\cD_r(C^h) + \alpha V^h_r \cdot \mathcal{U}^{\bV^h}_r (C^h), &
 J^h_\theta = -\frac{\cD_\theta(C^h)}{r} + \alpha V^h_\theta \cdot \mathcal{U}^{\bV^h}_\theta (C^h), 
-\\
+\\ \nonumber
  \mathcal{U}^{\bV^h}_r(C^h)[i,j] = C^h\left[i-\frac{\sign(V^h_r)}{2}, j\right], &
  \mathcal{U}^{\bV^h}_\theta(C^h)[i,j] = C^h\left[i, j-\frac{\sign(V^h_\theta)}{2}\right]. 
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 linear interpolation is used for the Coulomb force and for vector Laplacian components.
-\begin{eqnarray*}
+\begin{eqnarray}
+\nonumber
 F^h_r &=& -\cD_r(P^h) 
@@
 		  + \frac{\cD_\theta(\varPhi^h)}{r} \cdot \cI_\theta(\cL(\varPhi^h)), \\
+\nonumber
 \cL(f^h) &=& \frac{1}{r^2}\cD_r\pars{\cD_r(f^h) r^2} + 
 \frac{1}{r^2 \sin\theta} \cD_\theta\pars{\cD_\theta(f^h) \cdot \sin\theta}.
-\end{eqnarray*}
-
-\subsubsection{Boundary Conditions}
+\end{eqnarray}
+
+\subsection{Boundary Conditions} \label{sec:disc_boundary}
 In order to discretize boundary condtions for $\varPhi$, $C$ and $\bV$, 
@@
 
-The boundary conditions at the particle boundary ($r=1$) are:
+Far away from the particle boundary \eqref{eq:bndcond_inf}, we have:
+\begin{eqnarray*}
+\begin{array}{cccc}
+\cD_r \pars{\varPhi^h} = -\beta \cos\bar{\theta}, &
+\cI_r \pars{C^h} = 1 &
+V_r^h = -\cU \cos\theta, &
+V_\theta^h = \cU \sin\theta.
+\end{array}\end{eqnarray*}
+
+For $\theta = 0$ and $\theta = \pi$, the ``ghost'' points are defined by axial 
+symmetry considerations:
+\begin{eqnarray*} 
+\begin{array}{cccc}
+\cD_\theta \pars{\varPhi^h} = 0, &
+\cD_\theta \pars{C^h} = 0, &
+\cD_\theta \pars{V_r^h} = 0, &
+V_\theta^h = 0
+\end{array}
+\end{eqnarray*}
+
+The specific boundary condition at $r=1$
+depend on the chemical properties of particle surface.
+
+\subsubsection{Ion-exchanger} The boundary conditions \eqref{eq:ionex_bnd} 
+are implemented by:
 \begin{eqnarray*}
 \begin{array}{rcl}
-\cI_r(\varPhi^h) &=& -\cI_r(\log C^h), \\
-\cD_r(\varPhi^h) &=& \cD_r(\log C^h), \\
+0 &=& \cI_r(\varPhi^h + \log C^h), \\
+0 &=& \cD_r(\varPhi^h - \log C^h), \\
 V^h_r &=& 0, \\
-V^h_\theta &=& 4\log\pars{\frac{1 + \exp\left\{\cI_\theta(\zeta^h)/2\right\}}{2}} \cdot 
+V^h_\theta &=& 4\log\pars{\frac{1}{2}\pars{1 + \exp\left\{\cI_\theta(\zeta^h)/2\right\}}} \cdot 
 			\cD_\theta(\zeta^h), \\
@@
 \end{eqnarray*}
-The equations are discretized using ``ghost'' points outside the interior of the domain:
-\begin{eqnarray*}
- \varPhi^h_{[1/2, j]} = \frac{\varPhi^h_{[0,j]} + \varPhi^h_{[1,j]}}{2} &=& 
-	-\frac{\log C^h_{[0,j]} + \log C^h_{[1,j]}}{2} = -\log C^h_{[1/2, j]}, \\
-  \frac{\varPhi^h_{[1,j]} - \varPhi^h_{[0,j]}}{\Delta r} &=& 
-	\frac{\log C^h_{[1,j]} - \log C^h_{[0,j]}}{\Delta r}. 
-\end{eqnarray*}
-By adding and subtracting the equations, we have:
-\begin{eqnarray*}
-\varPhi^h_{[0,j]} &=& -\log\brcs{C^h_{[1,j]}}, \\
-C^h_{[0,j]} &=& \exp\brcs{-\varPhi^h_{[1,j]}}, \\
-  \zeta^h_{[j]} &=& \cV - \varPhi^h_{[1/2,j]}
-                     = -\log\gamma -\frac{\varPhi^h_{[0,j]} + \varPhi^h_{[1,j]}}{2}.
-\end{eqnarray*}
-The slip condition can be written as:
-\begin{eqnarray*}
-V_r^h{}_{[0,j]} &=& 0, \\
-V_\theta^h{}_{[1/2,j]} &=& 
-4\log\pars{\frac{1 + \exp\left\{\frac{1}{2}
- \frac{\zeta^h_{[j]} + \zeta^h[j+1]}{2}\right\}}{2}} 
-\cdot \frac{\zeta^h_{[j+1]} - \zeta^h_{[j]}}{\bar{\theta}_{j+1} - \bar{\theta}_{j}}, \\
-  V^h_\theta{}_{[0,j]} &=& 2 V^h_\theta{}_{[1/2, j]} - V^h_\theta{}_{[1,j]}.
-\end{eqnarray*}
-
-For $\theta = 0$ and $\theta = \pi$, the ``ghost'' points are defined by symmetry considerations:
-\begin{eqnarray*} 
-\brc{l}{
-\varPhi^h_{[i, 0]} = \varPhi^h_{[i, 1]} \\
-C^h_{[i, 0]} = C^h_{[i, 1]} \\
-V_r^h{}_{[i, 0]} = V_r^h{}_{[i, 1]} \\
-V_\theta^h{}_{[i, 0]} = 0
-} 
-\brc{l}{
-\varPhi^h_{[i, n_\theta+1]} = \varPhi^h_{[i, n_\theta]}, \\
-C^h_{[i, n_\theta+1]} = C^h_{[i, n_\theta]}, \\
-V_r^h{}_{[i, n_\theta+1]} = V_r^h{}_{[i, n_\theta]}, \\
-V_\theta^h{}_{[i, n_\theta+1]} = 0.
-} 
-\end{eqnarray*}
-
-Far away from the particle boundary ($r\rightarrow\infty$) we have:
-\begin{eqnarray*}
-\begin{array}{cccc}
-\frac{\varPhi^h_{[n_r + 1, j]} - \varPhi^h_{[n_r, j]}}{\bar{r}_{n_r + 1} - \bar{r}_{n_r}} 
-= -\beta \cos\bar{\theta}_j, &
-C^h_{[n_r + 1, j]} = 1 &
-V_r^h{}_{[n_r + 1, j]} = -\cU \cos\bar{\theta}_j, &
-V_\theta^h{}_{[n_r + 1, j]} = \cU \sin\theta_j.
-\end{array}\end{eqnarray*}
-
-Because the grid is finite, the choice 
-$r_{n_r} = R_{max}$ must be taken large enough so as to have a negligible effect
-on the solution.
+
+\subsubsection{Highly charged inert particle} The boundary conditions \eqref{eq:ephor_bnd} 
+are implemented by:
+\begin{eqnarray*}
+\begin{array}{rcl}
+0 &=& \cD_r(C^h) - \text{Du} \cdot 
+\pars{\cD_\theta \pars{\sin\theta \cdot \cD_\theta \cI_r\pars{\varPhi^h - \log C}}}/{\sin\theta}, \\
+0 &=& \cD_r(C^h) + \cI_r(C^h) \cD_r(\varPhi^h), \\
+V^h_r &=& 0, \\
+V^h_\theta &=& \cI_\theta(\zeta^h) \cdot \cD_\theta(\cI_r \varPhi^h - \log \cI_r C^h) + 
+4 \log 2 \cdot \cD_\theta(\log \cI_r C^h), \\
+  \zeta^h &=& \bar{\zeta} - \log \cI_r C.
+\end{array}
+\end{eqnarray*}
 
@@
 \subsection{Solver Design}
-\subsubsection{Newton's Method}
 An operator $\cO$ is defined by its input vector $\bx$ and its output 
 $\by = \cO(\bx)$.
-
-In order to solve the equation $\cO(\bx) = \bzero$, Newton's method can 
-be applied, given an initial solution $\bx_0$.
+In order to solve the equation $\cO(\bx) = \bzero$, Newton's method is applied, 
+given an initial solution $\bx_0$.
 Each step requires the computation of the residual vector, $\br = \cO(\bx)$, and
 the gradient matrix of the operator, $\bG = \bnabla \cO(\bx)$, 
-given the current solution $\bx = \bx_n$.
+given the current solution $\bx$.
 Then, a sparse linear system needs to be solved to yield the update for the 
-increment $\Delta \bx_n = \bx_{n+1} - \bx_n = -\bG^{-1} \br$.
-
-When the method converges, 
+increment $\Delta \bx = -\bG^{-1} \br$.
+When the method converges, $\bx_n \rightarrow \bx_\infty$, 
 the asymptotic convergence is in general quadratic:
@@
 \subsubsection{Operator Representation}
-System variable $\bx$ is defined as the concatenation $[\,\varPhi, C, V_r, V_\theta, P\,]$,
-taking only values in the interior of the problem domain grid.
-Thus, each problem variable can be computed by applying an appropriate projection operator on $\bx$:
-\begin{eqnarray*}
-X &=& \cP_X(\bx) \mbox{ for } X \in \left\{\varPhi, C, V_r, V_\theta, P\right\}.
-\end{eqnarray*}
-
-The extended variables $\tilde X$ (including ``ghost'' point values) 
-are computed by applying the following nonlinear operators:
-\begin{eqnarray*}
-\begin{array}{ccccc}
-\tilde{\varPhi} = \cB_\varPhi(\varPhi, C; \beta), &
-\tilde{C} = \cB_C(C, \varPhi), &
-\tilde{V_r} = \cB_{V_r}(V_r; \cU), &
-\tilde{V_\theta} = \cB_{V_\theta}(V_\theta, C, \varPhi; \cU, \gamma), &
-\tilde{P} = P.
-\end{array}
-\end{eqnarray*}
-The extended system variable can be written as $\tilde{\bx} = \cB(\bx)$, 
-where $\cB$ is the ``ghost'' point extension operator (derived using boundary conditions)
-so the concatenated equations of the system (as described above) can be written 
-as a nonlinear operator $\cE(\tilde\bx) = \bzero$ acting on the extended system variable 
-$\tilde{\bx}$, where $\cE$ is the conservation equations operator 
-(derived by concatenation of the system equations).
-
-The problem can be cast as the following nonlinear system (where $\cO = \cE \circ \cB$):
-\begin{eqnarray*}
-\cO(\bx) = \bzero.
-\end{eqnarray*}
+System variable $\bx$ is defined as the concatenation $\bx = [\,\varPhi, C, V_r, V_\theta, P\,]$.
+Thus, each problem variable can be computed by applying an appropriate projection operator on $\bx$.
+The system can be written as a nonlinear operator $\cO(\bx) = \bzero$ 
+acting on the system variable ${\bx}$, 
+where $\cO$ is the system equations operator, 
+derived by concatenation of the system equations (described at Subsection \ref{sec:disc_equations})
+and the boundary conditions operators (described at Subsection \ref{sec:disc_boundary}).
+This way, the same numerical solver handles both the nonlinear system equation and nonlinear
+boundary conditions.
 
@@
 a prescribed threshold $\|\cO(\bx_n)\| < \epsilon$, 
-the ``ghost'' point values are updated using $\tilde\bx = \cB(\bx_n)$,
-so  that the surface force $\boldsymbol{f} = \tT \cdot \bn$ 
-can be computed by integration over the surface.
+the total force acting on the particle  
+can be computed by integrating $\tT \cdot \bn$ over the particle surface.
 
@@
 aligned with $\ui$ and it vanishes iff $\ui \cdot \bF = 0$.
-\begin{eqnarray*}
+\begin{eqnarray} \nonumber
 F_\imath = \ui \cdot \bF &=& 
@@
 \frac{1}{2}\pars{\cD_r(\varPhi)}^2 - \frac{1}{2r^2}\pars{\cD_\theta(\varPhi)}^2}\cos\theta 
-\\  
+\\  \nonumber
 && -\pars{\cD_r(V_\theta) - \frac{V_\theta}{r}
 + \frac{1}{r}\cD_r(\varPhi) \cD_{\theta}(\varPhi)}\sin\theta.
-\end{eqnarray*}
-
-The integral for $F_\imath$ is approximated by 1D numerical quadrature
-(using the mid-point rule), to yield 
+\end{eqnarray}
+
+The integral above is approximated by 1D numerical quadrature
+(using the mid-point rule)
+\begin{eqnarray*}
+F_\imath^h &=& \sum_{i=1}^{n_\theta} f^h(\bar\theta_i) \cdot 
+              2 \pi \sin\bar\theta_i \cdot \Delta\theta_i,
+\end{eqnarray*}
+to yield 
 the total force $F_\imath(\cU)$ as a function of the drift velocity $\cU$.
-
 Since the goal is to find the steady-state solution, $F_\imath(\cU)$ 
@@
 and a gradient matrix \verb|Operator::grad()|, given an input vector $\bx$.
-
 This interface is implemented by specific operators classes,
-which are used to construct the system operator $\cO = \cE \circ \cB$, so that 
+which are used to construct the system operator $\cO$, so that 
 the Newton method solver (that requires computing the residual and the gradient) 
 can be applied automatically.
-
 Each such operator may have other operators as its inputs, so the residual
@@
 we apply the following algorithm 
-until convergence ($\|\Delta \bx\| < \eps$):
+until convergence ($\|\boldsymbol{r_n}\| < \eps$):
 \begin{enumerate}
 \item Update the system operator: $\verb|op| = \verb|System|(\bx_{n})$
-\item Compute the gradient: $\boldsymbol{A}_n = \verb|op.grad()|$
-\item Compute the right-hand side: $\boldsymbol{b}_n = \verb|-op.res()|$
-\item Solve sparse linear system: $\boldsymbol{A}_n \Delta \bx_n = \boldsymbol{b}_n$
+\item Compute the gradient: $\boldsymbol{G}_n = \verb|op.grad()|$
+\item Compute the right-hand side: $\boldsymbol{r}_n = \verb|op.res()|$
+\item Solve sparse linear system: $\boldsymbol{G}_n \Delta \bx_n = -\boldsymbol{r}_n$
 \item Update solution: $\bx_{n+1} = \bx_{n} + \Delta \bx_{n}$
@@
 
-\subsubsection{Total force integration}
-After the iterative Newton solver converges ($\bx_n \rightarrow \bx_\infty$), 
-the ``ghost'' point values are computed via $\cB(\bx_\infty)$,
-followed by a computation of the total force $\bF$ acting on the particle.
-$F_\imath = \bF \cdot \ui$ is computed by using the mid-point quadrature rule
-\begin{eqnarray*}
-F_\imath = \sum_{i=1}^{n_\theta} f(\bar\theta_i) \cdot 
-              2 \pi \sin\bar\theta_i \cdot \Delta\theta_i.
-\end{eqnarray*}
-
-In steady state, the total force acting on the particle $F_\imath$ must vanish.
-This constraint yields an equation $F_\imath(\cU) = 0$, 
-whose solution is the steady-state velocity $\cU$.
-This equation can be solved using a 1D root finding algorithm (e.g., the secant method). The result $\cU$ is the 
-steady state particle drift velocity for the electric field $\beta$.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Asymptotic Analysis} \label{sec:asymp}
-The nonlinear system is defined by the following PDEs:
-\label{PDEs}
-\begin{eqnarray*}
-\begin{array}{cccc}
-\bnabla \cdot \pars{C \bnabla \varPhi} = 0, &
-\bnabla \cdot \pars{\bnabla C - \alpha \bV C} = 0, &
-\bnabla \cdot \bV = 0, &
-\bLaplacian \bV - \bnabla P + \Laplacian \varPhi \bnabla \varPhi = \bzero.
-\end{array}\end{eqnarray*}
-
-For $\zeta(\theta) = \cV - \varPhi(1, \theta)$ and 
-$\cV = -\log \gamma$, the boundary conditions at $r = 1$ are given by
-\begin{eqnarray*}
-\begin{array}{rcl}
-\varPhi + \log C &=& \cV + \log \gamma = 0, \\
-\deriv{}{r}\pars{\varPhi - \log C} &=& \frac{J_-}{C} = 0, \\
-\bV = \zeta \cdot \bnabla_\mathcal{S} \varPhi 
-+ 2\log\pars{1-\tanh^2\frac{\zeta}{4}} \cdot \bnabla_\mathcal{S} \log C
-&=& 4\log\pars{\frac{1 + e^\frac{\zeta}{2}}{2}} \bnabla_S \varPhi.
-\end{array}
-\end{eqnarray*}
-
-The boundary conditions for $r \rightarrow \infty$ are given by
-\begin{eqnarray*}
-\bnabla \varPhi = -\beta \ui, &
-C = 1, &
-\bV = -\cU \ui,
-\end{eqnarray*}
-and the total force acting on the particle is zero: $\bF = \bzero$.
-
-The nonlinear system can be written as: 
-\begin{eqnarray*}
-\cO(\bx;\beta) &=& \bzero.
-\end{eqnarray*}
-
-For small $\beta$, the solution to the nonlinear system can be expanded in a Taylor series in $\beta$.
+In order to validate the numerical results, an asymptotic analysis is applied 
+to the nonlinear systems of ion-exchanger migration (\cite{yariv2010migration,zeyde2012report})
+and highly charged particle electrophoresis (\cite{schnitzer2012surface, schnitzer2012cubic})
+
+The nonlinear system is written as $\cO(\bx;\beta) = \bzero$.
+For small $\beta$, the solution to the nonlinear system can be expanded in a Taylor series in $\beta$:
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-
-All the variables are expanded around $\beta = 0$:
+Thus, the system variables are expanded around $\beta = 0$
+(where the velocity $\bV$ and pressure $P$ are computed from the streamfunction $\Psi$):
 \begin{eqnarray*}
@@
 \Psi = \sum_i \beta^i \Psi_i,
-\end{eqnarray*}
-where the velocity $\bV$ and pressure $P$ are computed from the streamfunction $\Psi$:
-\begin{eqnarray*}
-\bV &=& \bnabla \times \pars{\frac{\Psi}{r \sin\theta} \bphihat} 
-= \frac{1}{r^2 \sin\theta} \deriv{\Psi}{\theta} \brhat 
-- \frac{1}{r \sin\theta} \deriv{\Psi}{r} \bthetahat.
 \end{eqnarray*}

### 2012-09-11 notes/work/ijnam.tex
work on LaTeX

@@
 the boundary layer), using bulk variables denoted by uppercase letters, read:
-\begin{eqnarray} \begin{array}{cccc} \label{eq:bulk_flux}
+\begin{eqnarray*}
+\begin{array}{cccc} \label{eq:bulk_flux}
   Q = 0, &
@@
 \subsection{System Equations} \label{sec:disc_equations}
-Charge and salt fluxes \eqref{eq:bulk_flux} are discretized on grid cell boundaries 
+
+Ion flux ($\bI = - C \bnabla \varPhi$) is discretized on grid cell boundaries:
+\begin{eqnarray*}
+I^h_r = -\cI_r(C^h) \cdot \cD_r(\varPhi^h), &
+I^h_\theta = -\cI_\theta(C^h) \cdot \frac{\cD_\theta(\varPhi^h)}{r}.
+\end{eqnarray*}
+
+Salt flux ($\bJ = -\bnabla C + \alpha \bV C$) is discretized on grid cell boundaries 
 (using upwind scheme $\mathcal{U}$ for numerical stability at large cell Peclet number):
-\begin{eqnarray} \nonumber
-I^h_r = -\cI_r(C^h) \cdot \cD_r(\varPhi^h), &
-I^h_\theta = -\cI_\theta(C^h) \cdot \frac{\cD_\theta(\varPhi^h)}{r}, \\
+\begin{eqnarray*}
 J^h_r = -\cD_r(C^h) + \alpha V^h_r \cdot \mathcal{U}^{\bV^h}_r (C^h), &
 J^h_\theta = -\frac{\cD_\theta(C^h)}{r} + \alpha V^h_\theta \cdot \mathcal{U}^{\bV^h}_\theta (C^h), 
-\\ \nonumber
+\\
  \mathcal{U}^{\bV^h}_r(C^h)[i,j] = C^h\left[i-\frac{\sign(V^h_r)}{2}, j\right], &
  \mathcal{U}^{\bV^h}_\theta(C^h)[i,j] = C^h\left[i, j-\frac{\sign(V^h_\theta)}{2}\right]. 
-\end{eqnarray}
+\end{eqnarray*}
 
@@
 linear interpolation is used for the Coulomb force and for vector Laplacian components.
-\begin{eqnarray}
-\nonumber
+\begin{eqnarray*}
 F^h_r &=& -\cD_r(P^h) 
@@
 		  + \frac{\cD_\theta(\varPhi^h)}{r} \cdot \cI_\theta(\cL(\varPhi^h)), \\
-\nonumber
 \cL(f^h) &=& \frac{1}{r^2}\cD_r\pars{\cD_r(f^h) r^2} + 
 \frac{1}{r^2 \sin\theta} \cD_\theta\pars{\cD_\theta(f^h) \cdot \sin\theta}.
-\end{eqnarray}
+\end{eqnarray*}
 
@@
 System variable $\bx$ is defined as the concatenation $\bx = [\,\varPhi, C, V_r, V_\theta, P\,]$.
-Thus, each problem variable can be computed by applying an appropriate projection operator on $\bx$.
+Thus, each problem variable can be computed by applying an appropriate projection operator on $\bx$:
+\begin{eqnarray*}
+X &=& \cP_X(\bx) \text{ for } X \in \left\{\varPhi, C, V_r, V_\theta, P\right\}.
+\end{eqnarray*}
 The system can be written as a nonlinear operator $\cO(\bx) = \bzero$ 
@@
 \section{Asymptotic Analysis} \label{sec:asymp}
-In order to validate the numerical results, an asymptotic analysis is applied 
-to the nonlinear systems of ion-exchanger migration (\cite{yariv2010migration,zeyde2012report})
-and highly charged particle electrophoresis (\cite{schnitzer2012surface, schnitzer2012cubic})
-
-The nonlinear system is written as $\cO(\bx;\beta) = \bzero$.
-For small $\beta$, the solution to the nonlinear system can be expanded in a Taylor series in $\beta$:
+The nonlinear system is defined by the following PDEs:
+\label{PDEs}
+\begin{eqnarray*}
+\begin{array}{cccc}
+\bnabla \cdot \pars{C \bnabla \varPhi} = 0, &
+\bnabla \cdot \pars{\bnabla C - \alpha \bV C} = 0, &
+\bnabla \cdot \bV = 0, &
+\bLaplacian \bV - \bnabla P + \Laplacian \varPhi \bnabla \varPhi = \bzero.
+\end{array}\end{eqnarray*}
+
+For $\zeta(\theta) = \cV - \varPhi(1, \theta)$ and 
+$\cV = -\log \gamma$, the boundary conditions at $r = 1$ are given by
+\begin{eqnarray*}
+\begin{array}{rcl}
+\varPhi + \log C &=& \cV + \log \gamma = 0, \\
+\deriv{}{r}\pars{\varPhi - \log C} &=& \frac{J_-}{C} = 0, \\
+\bV = \zeta \cdot \bnabla_\mathcal{S} \varPhi 
++ 2\log\pars{1-\tanh^2\frac{\zeta}{4}} \cdot \bnabla_\mathcal{S} \log C
+&=& 4\log\pars{\frac{1 + e^\frac{\zeta}{2}}{2}} \bnabla_S \varPhi.
+\end{array}
+\end{eqnarray*}
+
+The boundary conditions for $r \rightarrow \infty$ are given by
+\begin{eqnarray*}
+\bnabla \varPhi = -\beta \ui, &
+C = 1, &
+\bV = -\cU \ui,
+\end{eqnarray*}
+and the total force acting on the particle is zero: $\bF = \bzero$.
+
+The nonlinear system can be written as: 
+\begin{eqnarray*}
+\cO(\bx;\beta) &=& \bzero.
+\end{eqnarray*}
+
+For small $\beta$, the solution to the nonlinear system can be expanded in a Taylor series in $\beta$.
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-Thus, the system variables are expanded around $\beta = 0$
-(where the velocity $\bV$ and pressure $P$ are computed from the streamfunction $\Psi$):
+
+All the variables are expanded around $\beta = 0$:
 \begin{eqnarray*}
@@
 \Psi = \sum_i \beta^i \Psi_i,
+\end{eqnarray*}
+where the velocity $\bV$ and pressure $P$ are computed from the streamfunction $\Psi$:
+\begin{eqnarray*}
+\bV &=& \bnabla \times \pars{\frac{\Psi}{r \sin\theta} \bphihat} 
+= \frac{1}{r^2 \sin\theta} \deriv{\Psi}{\theta} \brhat 
+- \frac{1}{r \sin\theta} \deriv{\Psi}{r} \bthetahat.
 \end{eqnarray*}

### 2012-09-11 notes/work/ijnam.tex
work on LaTeX

--- 2012-09-11 notes/work/ijnam.tex
@@
 In order to validate the numerical results, an asymptotic analysis is applied 
-to the nonlinear systems of ion-exchanger migration (\cite{yariv2010migration,zeyde2012report})
-and highly charged particle electrophoresis (\cite{schnitzer2012surface, schnitzer2012cubic})
-
+to the nonlinear systems of ion-exchanger migration (\cite{yariv2010migration, zeyde2012report})
+and highly charged particle electrophoresis (\cite{schnitzer2012surface, schnitzer2012cubic}).
+
+The derivation works as follows.
 The nonlinear system is written as $\cO(\bx;\beta) = \bzero$.
@@
 \end{eqnarray*}
-Thus, the system variables are expanded around $\beta = 0$
-(where the velocity $\bV$ and pressure $P$ are computed from the streamfunction $\Psi$):
-\begin{eqnarray*}
-\varPhi = \sum_i \beta^i \varPhi_i, &
-C = 1 + \sum_i \beta^i C_i, &
-\Psi = \sum_i \beta^i \Psi_i,
-\end{eqnarray*}
-
 The nonlinear equations and the boundary conditions 
@@
 
-Assuming $\beta \ll 1$, the linearized equations and boundary conditions are 
-(\cite{yariv2010migration}):
+Assuming $\beta \ll 1$, the linearized equations and boundary conditions are:
 \begin{eqnarray*}
@@
 
-The first-order terms are given by
+The first-order terms are given by (see \cite{yariv2010migration} for full derivation):
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-
 In order to find the cubic terms, the quadratic terms must be computed first.
@@
 the electric potential and the ionic concentration.
-
 The cubic terms $\bx_3$ are computed by solving a linear PDE system 
@@
 
-The steady-state velocity can be expanded using odd powers of $\beta$:
-\begin{eqnarray*}
-\cU(\beta, \gamma) &=& \cU_1(\gamma) \beta + \cU_3(\gamma) \beta^3.
-\end{eqnarray*}
-
-The linear and the cubic velocity terms (for $\alpha = 0$) are then
+In the case of ion-exchanger migration, the linear \cite{yariv2010migration}
+and the cubic \cite{zeyde2012report} velocity terms (for $\alpha = 0$)
+ are:
 \begin{eqnarray*}

### 2012-09-15 notes/work/ijnam.tex
Work on paper

@@
         (1) particle surface, (2) Debye layer, (3) fluid bulk.
-        If the particle surface has positive (blue) surface charge,
-        it attracts negative (red) ions from the fluid making the
+        If the particle surface has positive (black) surface charge,
+        it attracts negative (white) ions from the fluid making the
         Debye layer negatively charged (as opposed to the rest of
@@
 The numerical results and their comparison to an analytical asymptotic solution 
-are presented and discussed in Section \ref{sec:results}.
+are presented Section \ref{sec:results} and discussed in Section \ref{sec:discussion}.
 
@@
 where $D^*$ is the ionic diffusivity):
-\begin{eqnarray}
-\bj^*_\pm &=& 
+\begin{equation}
+\bj^*_\pm = 
 -D^* \bnabla c^*_\pm + \bv^* c^*_\pm \mp \frac{z e^* D^*}{k_B^* T^*} c^*_\pm \bnabla \varphi^*,
-\end{eqnarray}
+\end{equation}
 
@@
 The dimensional Stokes equations are given by:
-\begin{eqnarray}
+\begin{equation} \begin{array}{cc}
 \bnabla \cdot \bv = 0, &
--\bnabla p^* + \mu^* \bLaplacian \bv^* + \eps^* \Laplacian \varphi^* \bnabla \varphi^* = 0.
-\end{eqnarray}
+-\bnabla p^* + \mu^* \bLaplacian \bv^* + \eps^* \Laplacian \varphi^* 
+\bnabla \varphi^* = 0.
+\end{array}\end{equation}
 
@@
 The dimensional Poisson equation can be written as:
-\begin{eqnarray}
-(c^*_+ - c^*_-) z e^* &=& -\eps^* \Laplacian \varphi^*,
-\end{eqnarray}
+\begin{equation}
+(c^*_+ - c^*_-) z e^* = -\eps^* \Laplacian \varphi^*,
+\end{equation}
 
 After nondimensionalization, the Nernst-Plank, Stokes and Poisson equations are:
-\begin{eqnarray} \label{eq:nernst}
-\bj_\pm &=& 
+\begin{equation} \label{eq:nernst}
+\bj_\pm = 
 -\bnabla c_\pm + \alpha \bv c_\pm \mp c_\pm \bnabla \varphi,
-\end{eqnarray}
-\begin{eqnarray} \label{eq:stokes}
-\bnabla \cdot \bv = 0, & -\bnabla p + \bLaplacian \bv + \Laplacian \varphi \bnabla \varphi = 0, 
-\end{eqnarray}
-\begin{eqnarray} \label{eq:poisson}
-c_+ - c_- &=& -2\delta^2 \Laplacian \varphi,
-\end{eqnarray}
+\end{equation}
+\begin{equation} \label{eq:stokes}
+\begin{array}{cc}
+\bnabla \cdot \bv = 0, &
+-\bnabla p + \bLaplacian \bv + \Laplacian \varphi \bnabla \varphi = 0, 
+\end{array}
+\end{equation}
+\begin{equation} \label{eq:poisson}
+c_+ - c_- = -2\delta^2 \Laplacian \varphi,
+\end{equation}
 where $\delta = {\delta^*}/{a^*}$ is the dimensionless Debye thickness 
@@
 at Eq. \eqref{eq:nernst}. Due to conservation of ions, the fluxes are divergence-free:
-\begin{eqnarray*}
-\bnabla \cdot \bj_\pm &=& 0.
-\end{eqnarray*}
+\begin{equation*}
+\bnabla \cdot \bj_\pm = 0.
+\end{equation*}
 These equations may be re-written by using salt $c = (c_+ + c_-)/2$ and charge $q = (c_+ - c_-)/2$.
 Thus, salt and charge fluxes are defined by:
-\begin{eqnarray} \label{eq:fluxes}
-  \bj = \frac{\bj_+ + \bj_-}{2} = -\bnabla c - q \bnabla \varphi + \alpha \bv c &,& 
+\begin{equation}\label{eq:fluxes}\begin{array}{cc}
+  \bj = \frac{\bj_+ + \bj_-}{2} = -\bnabla c - q \bnabla \varphi + \alpha \bv c, & 
   \bi = \frac{\bj_+ - \bj_-}{2} = -\bnabla q - c \bnabla \varphi + \alpha \bv q,
-\end{eqnarray}
+\end{array}\end{equation}
 and are divergence-free as well:
-\begin{eqnarray} \label{eq:zero_flux}
-\bnabla \cdot \bj = 0 &,& 
+\begin{equation}\label{eq:zero_flux}\begin{array}{cc}
+\bnabla \cdot \bj = 0, & 
 \bnabla \cdot \bi = 0. 
-\end{eqnarray}
+\end{array}\end{equation}
 In addition, the charge concentration is governed by the Poisson equation \eqref{eq:poisson}
-\begin{eqnarray}
-q &=& -\delta^2 \Laplacian \varphi.
-\end{eqnarray}
+\begin{equation}
+q = -\delta^2 \Laplacian \varphi.
+\end{equation}
 
@@
 and ambient ionic concentrations:
-\begin{eqnarray} \label{eq:bndcond_inf}
+\begin{equation}\label{eq:bndcond_inf}\begin{array}{ccc}
 \bv \rightarrow -\cU \ui, &
@@
  c_\pm \rightarrow 1.
-\end{eqnarray}
+\end{array}\end{equation}
 
@@
 $\bn \cdot \bj_+ = k (1 - c_+/\gamma)$, where $k \rightarrow \infty$):
-\begin{eqnarray}
+\begin{equation}
 \begin{array}{cccc}
@@
 \end{array}
-\end{eqnarray}
+\end{equation}
 where $\gamma$ is the ratio between the cationic concentration on the surface and the cationic
@@
 zero slip and ion impermeability:
-\begin{eqnarray}
+\begin{equation}
 \begin{array}{cccc}
@@
 \end{array}
-\end{eqnarray}
+\end{equation}
 where $\chi$ is the ratio between the dielectric constants of the 
@@
 the boundary layer), using bulk variables denoted by uppercase letters, read:
-\begin{eqnarray} \begin{array}{cccc} \label{eq:bulk_flux}
+\begin{equation} \begin{array}{cccc} \label{eq:bulk_flux}
   Q = 0, &
@@
 \bI = -C \bnabla \varPhi.
-\end{array}\end{eqnarray}
+\end{array}\end{equation}
 Because the flow is incompressible ($\bnabla \cdot V = 0$), 
@@
 \eqref{eq:zero_flux}:
-\begin{eqnarray} 
+\begin{equation} \begin{array}{ccc}
 \label{eq:salt_charge}
@@
 \bnabla \cdot \pars{ C \bnabla \varPhi } = 0.
-\end{eqnarray}
+\end{array}\end{equation}
 The macroscale Stokes flow equations have the same form as before \eqref{eq:stokes}:
-\begin{eqnarray} 
+\begin{equation}
+\begin{array}{ccc}
 \bnabla \cdot \bV = 0, &   
 \Laplacian \bV - \bnabla P + \bnabla \varPhi \Laplacian \varPhi = \bzero.
-\end{eqnarray}
+\end{array}
+\end{equation}
 
@@
 \subsubsection{Ion-exchanger} See \cite{yariv2010migration} for full derivation:
-\begin{eqnarray} \label{eq:ionex_bnd}
+\begin{equation}
+\begin{array}{ccc}
+\label{eq:ionex_bnd}
 0 = \varPhi + \log C, &
@@
 + 2\log\pars{1-\tanh^2\frac{\zeta}{4}} \cdot \bnabla_\mathcal{S} \log C,
-\end{eqnarray}
+\end{array}\end{equation}
 where $\zeta = \cV - \varPhi = \log (C / \gamma)$ 
@@
 See \cite{schnitzer2012surface} for full derivation:
-\begin{eqnarray} \label{eq:ephor_bnd}
+\begin{equation} \label{eq:ephor_bnd}
+\begin{array}{ccc}
 0 = {\deriv{C}{n} - \text{Du} \nabla^2_s \pars{\varPhi - \log C}}, & 
@@
 4 \log 2 \cdot \bnabla_\mathcal{S} \log C,
-\end{eqnarray}
+\end{array}\end{equation}
 where $\zeta = \bar{\zeta} - \log C$ 
@@
 The stress tensor in the fluid is composed of Newtonian and Maxwel stresses:
-\begin{eqnarray} \label{eq:tensor}
-\tT &=& \bnabla \bV + (\bnabla \bV)^\dagger - P \tI
+\begin{equation}
+\label{eq:tensor}
+\tT = \bnabla \bV + (\bnabla \bV)^\dagger - P \tI
 + \bnabla \varPhi \bnabla \varPhi - \frac{1}{2} (\bnabla \varPhi \cdot \bnabla \varPhi). 
-\end{eqnarray}
+\end{equation} 
 In steady state (constant particle drift velocity $\cU$), the total force acting on the particle 
 (computed by the following surface integral) must vanish:
-\begin{eqnarray} \label{eq:zero_force}
- \bF = \oint_\mathcal{S} \tT \cdot \bnhat dA = \bzero.
-\end{eqnarray}
+\begin{equation} \label{eq:zero_force}
+ \bF(\beta, \cU) = \oint_\mathcal{S} \tT \cdot \bnhat dA = \bzero.
+\end{equation}
 
@@
 The scalar gradient and the divergence can be written as:
-\begin{eqnarray*}
-\bnabla f &=& \deriv{f}{r}\brhat + \frac{1}{r}\deriv{f}{\theta}\bthetahat, \\
-\bnabla \cdot \bF &=& \frac{1}{r^2}\deriv{}{r}\pars{F_r r^2 } + 
+\begin{eqnarray}
+\bnabla f = \deriv{f}{r}\brhat + \frac{1}{r}\deriv{f}{\theta}\bthetahat, &
+\bnabla \cdot \bF = \frac{1}{r^2}\deriv{}{r}\pars{F_r r^2 } + 
                \frac{1}{r \sin\theta}\deriv{}{\theta}\pars{F_\theta \sin\theta}.
-\end{eqnarray*}
+\end{eqnarray}
 The scalar Laplacian can be written as:
-\begin{eqnarray*}
-\Laplacian f = \bnabla \cdot (\bnabla f)&=& 
+\begin{eqnarray}
+\Laplacian f = \bnabla \cdot (\bnabla f) = 
  \frac{1}{r^2}\deriv{}{r}\pars{r^2 \deriv{f}{r}} + 
  \frac{1}{r^2 \sin\theta}\deriv{}{\theta}\pars{\sin\theta \deriv{f}{\theta}}.
-\end{eqnarray*}
-The vector gradient can be written as:
-\begin{eqnarray*}
+\end{eqnarray}
+The vector gradient and vector Laplacian can be written as:
+\begin{eqnarray}
 \bnabla \bF &=& \deriv{F_r}{r} \brhat \brhat + \deriv{F_\theta}{r} \brhat \bthetahat + 
 \frac{1}{r}\pars{\deriv{F_r}{\theta} - F_\theta} \bthetahat \brhat + 
-\frac{1}{r}\pars{\deriv{F_\theta}{\theta} + F_r} \bthetahat \bthetahat.
-\end{eqnarray*}
-The vector Laplacian can be written as:
-\begin{eqnarray*}
+\frac{1}{r}\pars{\deriv{F_\theta}{\theta} + F_r} \bthetahat \bthetahat, \\
 \bLaplacian \bF &=& 
@@
 A regular grid of size $n_r \times n_\theta$ is defined, with:
-\begin{eqnarray*}
+\begin{eqnarray} \label{eq:grid}
 (r_i,\theta_j) \in [1, \infty) \times [0,\pi], & 
@@
  \theta_j = \Delta_\theta \cdot j,
-\end{eqnarray*}
+\end{eqnarray}
 where a logarithmic grid spacing has been chosen for $r$ and a uniform grid for $\theta$.
 Note that $r_0 = 1$ and $R_{max} = (1+\Delta_r)^{n_r}$, where
-\begin{eqnarray*}
-\Delta_r = \pars{R_{max}} ^ \frac{1}{n_r} - 1 ,& \Delta_\theta = \frac{\pi}{n_\theta}.
-\end{eqnarray*}
+$\Delta_r = \pars{R_{max}} ^ {1/n_r} - 1$ and $\Delta_\theta = {\pi/n_\theta}$.
 Because the grid is finite, the choice 
@@
 $\Omega = [1, R_{max}] \times [0,\pi] = \bigcup_{ij}\Omega_{ij}$ into cells.
-A specific cell $\Omega_{ij}$ and its center $(\bar{r}_i, \bar{\theta}_j)$ are defined by:
-\begin{eqnarray*}
+A specific cell $\Omega_{ij}$ and its center $(\bar{r}_i, \bar{\theta}_j)$ are defined by \eqref{eq:grid}:
+\begin{eqnarray}
 \Omega_{ij} = [r_{i-1}, r_{i}] \times [\theta_{j-1}, \theta_{j}], &
@@
 \bar{\theta}_j = (\theta_{j-1} + \theta_{j})/2.
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 $\varPhi$, $C$ and $P$ are represented by their value at the center of each cell, 
-using an all-centered grid:
-\begin{eqnarray*}
+using an all-centered grid, whereas $\bV$ is represented by its values at cell 
+boundaries, using a staggered grid:
+\begin{equation}
+\begin{array}{ccccc}
 \varPhi^h_{[i,j]} = \varPhi(\bar{r}_i, \bar{\theta}_j), &
 C^h_{[i,j]} = C(\bar{r}_i, \bar{\theta}_j), &
-P^h_{[i,j]} = P(\bar{r}_i, \bar{\theta}_j).
-\end{eqnarray*}
-$\bV$ is represented by its values at cell boundaries, using a staggered grid:
-\begin{eqnarray*}
+P^h_{[i,j]} = P(\bar{r}_i, \bar{\theta}_j). &
 V_r^h{}_{[i,j]} = V_r(r_i, \bar{\theta}_j), &
 V_\theta^h{}_{[i,j]} = V_\theta(\bar{r}_i, {\theta}_j).
-\end{eqnarray*}
+\end{array}
+\end{equation}
 
@@
 A finite-volume method with linear interpolation is used for flux discretization. 
-
 Define the following discrete central difference operators:
-\begin{eqnarray*}
+\begin{eqnarray} \label{eq:disc_diff}
 \cD_r(f^h){}_{\left[i+\half,j\right]} = \frac{f^h_{\left[i+1,j\right]} - f^h_{\left[i,j\right]}}
@@
 					   {\theta_{\left[i,j+1\right]} - \theta_{\left[i,j\right]}}.
-\end{eqnarray*}
+\end{eqnarray}
 
 Define the following linear interpolation operators:
-\begin{eqnarray*}
+\begin{eqnarray} \label{eq:disc_interp}
 \begin{array}{rcl}
@@
 \end{array}
-\end{eqnarray*}
-
-If the total flux of a cell is equal to zero ($\bnabla \cdot \boldsymbol{f} = 0$), then we have
-\begin{eqnarray*}
+\end{eqnarray}
+
+If the total flux of a cell is equal to zero ($\bnabla \cdot \boldsymbol{f} = 0$), 
+then using \eqref{eq:disc_diff}, we have
+\begin{eqnarray}
 \frac{1}{r^2} \cD_r\pars{f^h_r r^2} + 
@@
 \cD_\theta\pars{f^h_\theta \cdot r \sin\theta}}{r^2 \sin\theta} = 0. 
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 Charge and salt fluxes \eqref{eq:bulk_flux} are discretized on grid cell boundaries 
-(using upwind scheme $\mathcal{U}$ for numerical stability at large cell Peclet number):
+(using upwind scheme $\mathcal{U}$ for numerical stability at large cell Peclet number)  
+using \eqref{eq:disc_diff} and \eqref{eq:disc_interp}:
 \begin{eqnarray} \nonumber
@@
 Far away from the particle boundary \eqref{eq:bndcond_inf}, we have:
-\begin{eqnarray*}
+\begin{equation}
 \begin{array}{cccc}
@@
 V_\theta^h = \cU \sin\theta.
-\end{array}\end{eqnarray*}
+\end{array}\end{equation}
 
@@
 symmetry considerations:
-\begin{eqnarray*} 
+\begin{equation} 
 \begin{array}{cccc}
@@
 \end{array}
-\end{eqnarray*}
+\end{equation}
 
@@
 are implemented by:
-\begin{eqnarray*}
+\begin{equation}
 \begin{array}{rcl}
@@
 the asymptotic convergence is in general quadratic:
-\begin{eqnarray*}
+\begin{equation}
 \|\bx_{n+1} - \bx_\infty\| \le k \|\bx_{n} - \bx_\infty\|^2.
-\end{eqnarray*}
+\end{equation}
 Thus, when the initial guess is close enough to the solution, the solver
@@
 (using the mid-point rule)
-\begin{eqnarray*}
-F_\imath^h &=& \sum_{i=1}^{n_\theta} f^h(\bar\theta_i) \cdot 
+\begin{equation}
+F_\imath^h(\beta, \cU^h) = \sum_{i=1}^{n_\theta} f^h(\bar\theta_i) \cdot 
               2 \pi \sin\bar\theta_i \cdot \Delta\theta_i,
-\end{eqnarray*}
-to yield 
-the total force $F_\imath(\cU)$ as a function of the drift velocity $\cU$.
-Since the goal is to find the steady-state solution, $F_\imath(\cU)$ 
+\end{equation}
+to yield the total force $F_\imath^h(\beta, \cU^h)$ as a function of the drift velocity $\cU^h$.
+Since the goal is to find the steady-state solution, $F_\imath^h$ 
 is required to be zero --
-and the appropriate $\cU$ is found by a simple 1D root-finding algorithm,
-applied as an outer loop.
+and the appropriate $\cU^h$ is found by a simple 1D root-finding algorithm,
+applied as an outer loop:
+\begin{equation} \label{eq:disc_zero_force}
+F_\imath^h(\beta, \cU^h(\beta)) = 0
+\end{equation}
 
@@
 If $\cO$ is linear, it can be represented by a matrix $L$, such that:
-\begin{eqnarray*}
-\cO(\bx) &=& L \bx, \\
-\bnabla\cO &=& L. 
-\end{eqnarray*}
+\begin{equation}\begin{array}{cc}
+\cO(\bx) = L \bx, &
+\bnabla\cO = L. 
+\end{array}\end{equation}
 Note that finite difference $\cD$, interpolation $\cI$ and 
@@
 represent pointwise application of $f$:
-\begin{eqnarray*}
-\cF(\bx) &=& [f(x_1); \ldots; f(x_n)], \\
-\bnabla\cF(\bx) &=& \diag\{f'(x_1), \ldots, f'(x_n)\}.
-\end{eqnarray*}
+\begin{equation}\begin{array}{cc}
+\cF(\bx) = [f(x_1); \ldots; f(x_n)], &
+\bnabla\cF(\bx) = \diag\{f'(x_1), \ldots, f'(x_n)\}.
+\end{array}\end{equation}
 $f$ is defined and differentiated automatically using the MATLAB symbolic toolbox.
@@
 (that does not depend on $\bx$):
-\begin{eqnarray*}
-\mathcal{C}(\bx) &=& \bc, \\
-\bnabla\mathcal{C} &=& \bzero.
-\end{eqnarray*}
+\begin{equation}\begin{array}{cc}
+\mathcal{C}(\bx) = \bc, &
+\bnabla\mathcal{C} = \bzero.
+\end{array}\end{equation}
 
@@
 and multiplication, are defined as follows:
-\begin{eqnarray*}
-(\cO_1 \pm \cO_2)(\bx) &=& \cO_1(\bx) \pm \cO_2(\bx), \\
-\bnabla (\cO_1 \pm \cO_2)(\bx)   &=& \bnabla\cO_1(\bx) \pm \bnabla\cO_2(\bx), \\
-(\cO_1 \cdot \cO_2)(\bx) &=& \diag(\diag(\cO_1(\bx)) \cdot \diag(\cO_2(\bx))), \\
-\bnabla (\cO_1 \cdot \cO_2)(\bx) &=& \diag(\cO_2(\bx)) \bnabla\cO_1(\bx) 
+\begin{equation}\begin{array}{cc}
+(\cO_1 \pm \cO_2)(\bx) = \cO_1(\bx) \pm \cO_2(\bx), &
+\bnabla (\cO_1 \pm \cO_2)(\bx) = \bnabla\cO_1(\bx) \pm \bnabla\cO_2(\bx),
+\end{array}\end{equation}
+\begin{equation}\begin{array}{cc}
+(\cO_1 \cdot \cO_2)(\bx) = \cO_1(\bx) \cdot \cO_2(\bx), &
+\bnabla (\cO_1 \cdot \cO_2)(\bx) = \diag(\cO_2(\bx)) \bnabla\cO_1(\bx) 
                                   + \diag(\cO_1(\bx)) \bnabla\cO_2(\bx).
-\end{eqnarray*}
-
+\end{array}\end{equation}
 \paragraph{\textit{N-ary operators}}
 Given $N$ operators $\{\cO_i\}_{i=1}^N$, their concatenation $\cO$ is defined as:
-\begin{eqnarray*}
-\cO(\bx) &=& [\cO_1(\bx); \ldots; \cO_N(\bx)], \\
-(\bnabla\cO)(\bx) &=& [(\bnabla\cO_1)(\bx); \ldots; (\bnabla\cO_N)(\bx)].
-\end{eqnarray*}
+\begin{equation}\begin{array}{cc}
+\cO(\bx) = [\cO_1(\bx); \ldots; \cO_N(\bx)], &
+(\bnabla\cO)(\bx) = [(\bnabla\cO_1)(\bx); \ldots; (\bnabla\cO_N)(\bx)].
+\end{array}\end{equation}
 
@@
 The derivation works as follows.
-The nonlinear system is written as $\cO(\bx;\beta) = \bzero$.
+The nonlinear system (composed of the governing equations and the boundary conditions) 
+is written as $\cO(\bx;\beta) = \bzero$.
 For small $\beta$, the solution to the nonlinear system can be expanded in a Taylor series in $\beta$:
-\begin{eqnarray*}
-\bx = \bx(\beta) &\approx& \sum_n \bx_n \beta^n.
-\end{eqnarray*}
-The nonlinear equations and the boundary conditions 
+\begin{equation}
+\bx = \bx(\beta) \approx \sum_n \bx_n \beta^n.
+\end{equation}
+The nonlinear 
 are expanded around $\beta = 0$:
@@
 The first-order terms are given by (see \cite{yariv2010migration} for full derivation):
-\begin{eqnarray*}
-\begin{array}{ccccc}
+\begin{equation} \begin{array}{ccccc}
 \varPhi = \beta \pars{\frac{1}{4r^2} - r}\cos\theta, &
@@
 P = 0, &
-\bF = \bzero.
-\end{array}
-\end{eqnarray*}
+\bF = \bzero,
+\end{array} \end{equation}
+and the linear velocity term is:
+\begin{equation} \label{eq:linear_velocity}
+\cU_1(\gamma) = 2 \log \pars{\frac{1 + \gamma^{-\frac{1}{2}}}{2}}
+\end{equation}
+For $\gamma > 1$, the Debye layer has a positive space charge, 
+corresponding to a negative particle charge -- 
+yielding negative drift velocity, $\cU < 0$. 
+For $\gamma < 1$, we have $\cU > 0$.
 
@@
 Therefore, $\cU_2 = 0$ and the next velocity term is the cubic one:
-\begin{eqnarray*}
-\cU(\beta) &\approx& \beta \cU_1 + \beta^3 \cU_3 + O(\beta^5).
-\end{eqnarray*}
+\begin{equation} \label{eq:cubic}
+\cU(\beta) \approx \beta \cU_1 + \beta^3 \cU_3 + O(\beta^5).
+\end{equation}
 In order to find the cubic terms, the quadratic terms must be computed first.
@@
 with a right-hand side determined by the linear terms $\bx_1$ and the quadratic terms $\bx_2$.
-The cubic solution satisfies the $\lim_{r\rightarrow\infty}C_3 = 0$ boundary condition, 
+The cubic solution satisfies the ${r\rightarrow\infty}$ boundary conditions, 
 when $\alpha\cU_1 = 0$.
 
-In the case of ion-exchanger migration, the linear \cite{yariv2010migration}
-and the cubic \cite{zeyde2012report} velocity terms (for $\alpha = 0$)
+In the case of ion-exchanger migration,
+the cubic correction \cite{zeyde2012report} velocity terms (for $\alpha = 0$)
  are:
-\begin{eqnarray*}
-\cU_1(\gamma) &=& 2 \log \pars{\frac{1 + \gamma^{-\frac{1}{2}}}{2}}, \\
-\cU_3(\gamma) &=& \frac{31}{320(\sqrt\gamma + 1)} - \frac{9}{320(\sqrt\gamma + 1)^2} + \frac{1}{1680} - \frac{11}{160} \log \pars{\frac{1 + \gamma^{-\frac{1}{2}}}{2}}.
-\end{eqnarray*}
-
-Note that, for $\gamma = 1$, the linear term vanishes and the velocity leading term is $O(\beta^3)$:
-\begin{eqnarray*}
-\cU(\beta) = \frac{1129}{26880}\beta^3.
-\end{eqnarray*}
-
-Note that a $\cU = 0$ solution may exist for $\beta_c \ne 0$ and $\alpha = 0$, 
+\begin{equation}
+\cU_3(\gamma) = \frac{31}{320(\sqrt\gamma + 1)} - \frac{9}{320(\sqrt\gamma + 1)^2} + \frac{1}{1680} - \frac{11}{160} \log \pars{\frac{1 + \gamma^{-\frac{1}{2}}}{2}}.
+\end{equation}
+
+The cubic term becomes dominant for small $\beta$ when $\gamma \approx 1$.
+Note that, for $\gamma = 1$, the linear term vanishes and the cubic term 
+of the velocity is $\cU(\beta) = \frac{1129}{26880}\beta^3$.
+
+Note that a $\cU = 0$ solution may exist for a critical $\beta_c > 0$ and $\alpha = 0$, 
 if it satisfies:
-\begin{eqnarray*}
+\begin{equation} \label{eq:crit_beta}
 \beta_c^2 = -\frac{\cU_1(\gamma)}{\cU_3(\gamma)}.
-\end{eqnarray*}
-For $\gamma = 1 + \eps$, where $0 < \eps \ll 1$:
-\begin{eqnarray*}
-\beta_c \approx \sqrt{-\frac{\cU_1'(1) \eps}{\cU_3(1)}} = 
- \sqrt{\frac{13440 \eps}{1129}} \approx 3.45 \sqrt{\eps}.
-\end{eqnarray*}
-However, for $\gamma \gg 1$, we have:
-\begin{eqnarray*}
-\beta_c =  \pars{\frac{11}{320} + \frac{1}{1680 \log 4}}^{-\frac{1}{2}} \approx 5.36.
-\end{eqnarray*}
-
-The cubic term becomes dominant for small $\beta$ when $\gamma \approx 1$.
+\end{equation}
+Specifically, for $\gamma = 1 + \eps$, where $0 < \eps \ll 1$, $\beta_c = O\pars{\sqrt{\eps}}$:
+\begin{equation}
+\beta_c \approx \sqrt{-{\cU_1'(1) \eps}/{\cU_3(1)}} = 
+ \sqrt{{13440 \eps}/{1129}} \approx 3.45 \sqrt{\eps}.
+\end{equation}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Numerical Results and Discussion} \label{sec:results}
-The numerical solver is applied to the nonlinear problem of the migration ion-exchanger
-driven by an electric field (as described in \cite{yariv2010migration})
+\section{Numerical Results} \label{sec:results}
+The numerical solver is applied to the nonlinear problem of an ion-exchanger migration 
+driven by an electric field \cite{yariv2010migration}
 and the electrophoresis of highly charged surface inert particle 
-(as described in \cite{schnitzer2012surface}). 
-The computational grid for the problem is chosen to be of size $400 \times 50$.
-Because there are five different variables ($\varPhi, C, V_r, V_\theta, P$), the concatenated
-variable $\bx$ has dimension of $\sim 10^5$.
-$R_{\max}$ is chosen to be $10^{7}$ so the truncation effect is negligible.
+\cite{schnitzer2012surface}. 
 The solver is applied to a series of values of $\beta$, ranging 
 from $\beta \ll 1$ up to $\beta \sim O(1)$.
-For each $\beta$ value, the steady-state velocity $\cU(\beta)$ is computed. The solver
-is applied to various values of $\gamma$, representing various ion-exchangers.
+For each $\beta$ value, the steady-state velocity $\cU(\beta)$ is computed. 
 The resulting $\cU(\beta)$ is plotted on a log-log scale, so that the asymptotic behaviour
@@
 
-In order to validate the numerical solver, an asymptotic analysis of the nonlinear system
-is performed as described in Section \ref{sec:asymp}. The numerical results are compared 
+In order to validate the numerical solver, we employ 
+the results of the asymptotic analysis of the nonlinear 
+system \cite{zeyde2012report, schnitzer2012cubic}. 
+The numerical results are compared 
 to the asymptotic solutions, and good correspondence is achieved.
 
-\subsection{Linear Regime}
-For $\beta \ll 1$, the linear regime is dominant: $\cU = 2\log\pars{\frac{1 + \gamma^{-\frac{1}{2}}}{2}}\beta$.
-
-Thus, for $\gamma > 1$, the Debye layer has a positive space charge, corresponding to a negative
-particle charge -- yielding negative drift velocity, $\cU < 0$. 
-For $\gamma < 1$, we have $\cU > 0$.
-
-The numerical and asymptotic analytical solutions for the linear regime are compared 
-in Figure \ref{fig:Linear}.
-
-\subsection{Cubic Regime}
+\subsection{Ion-exchanger results}
+For $\beta \ll 1$, the linear regime is dominant \eqref{eq:linear_velocity}.
 When $\gamma \approx 1$, the cubic regime, where $\cU = O(\beta^3)$, 
@@
 field value $\beta_c = O(\sqrt{|\gamma - 1|})$.
-The numerical results, as well as the analytical ones, are given in Figure
-\ref{fig:Cubic1} (for $\gamma > 1$) and in Figure \ref{fig:Cubic2} (for $\gamma < 1$).
-Because a log-log scale is employed, positive and negative velocities are shown in
-the same plot using different markers and line styles.
-
-\subsection{Vortices}
+The numerical results $\cU^h$, 
+as well as the analytical ones \eqref{eq:cubic}, are given in Figure \ref{fig:IonExCubic}.
+
 The linear solution for $\gamma \approx 1$, 
@@
 
-\subsection{Discussion}
+\subsection{Electrophoresis results}
+In this scenario the linear regime is dominant \eqref{eq:linear_velocity}.
+In order to verify the solver, the numerical steady-state velocity is compared to the
+analytical solution \cite{schnitzer2012cubic}. Since cubic correction is much smaller than
+the linear regime for $\beta \ll 1$, the difference between numerical results and
+the linear regime is compared to the cubic correction term.
+
+Since the leading order of the solution $\cU(\beta)$ is linear for $\beta \ll 1$, 
+the numerical discretization error is $O(\beta)$ too.
+In order to reduce the discretization error of the numerical solution \eqref{eq:disc_zero_force}
+and after verifying that the discretization error converges as $O(h^2)$,
+we employ Richardson extrapolation to $\cU^h$ and $\cU^{2h}$:
+\begin{equation}
+\hat\cU = \frac{4}{3} \cU^h - \frac{1}{3} \cU^{2h}.
+\end{equation}
+The results of the extrapolation and $\hat\cU$ the analytical results 
+are given at Figure \ref{fig:Electrophoresis}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+\section{Discussion} \label{sec:discussion}
+A numerical solver for nonlinear electrokinetic transport system is described.
 The numerical results exhibit a good correspondence to the asymptotic linear model as
@@
 
+Future work may include replacing the full Newton step by an iterative linear solver, so 
+finer grids could be used and higher electric field magnitudes be achieved.
+
 \begin{figure}[htbp]
     \begin{center}
-    \includegraphics[width=0.45\textwidth]{figs/linearNeg.eps}
-    \includegraphics[width=0.45\textwidth]{figs/linearPos.eps}
+    \includegraphics[width=0.4\textwidth]{figs/Cubic/ionex_cubic1.eps}
+    \includegraphics[width=0.4\textwidth]{figs/Cubic/ionex_cubic2.eps}
         \caption{Steady-state velocity $\cU$ as a function of the 
-        electric field magnitude $\beta$, for $\gamma > 1$ (left) 
-        and $\gamma > 1$ (right). 
-        The analytic solution velocity is represented by lines, and the numerical
-        results are represented by markers.}
-    \label{fig:Linear}
+        electric field magnitude $\beta$, for $\gamma < 1$ (left) and $\gamma > 1$ (right). 
+        The analytic cubic solution \eqref{eq:cubic} is represented by lines 
+        (solid lines for $\cU > 0$, dashed lines for $\cU < 0$), 
+        and the numerical results are represented by markers 
+        (circles for $\cU > 0$, squares for $\cU < 0$). Note that linear and
+        cubic regimes fit well the numerical results, including the critical $\beta$ 
+        behaviour \eqref{eq:crit_beta}.
+        }
+	    \label{fig:IonExCubic}
     \end{center}
@@
 \begin{figure}[htbp]
-\end{figure}
-
-\begin{figure}[htbp]
     \begin{center}
-    \includegraphics[width=0.22\textwidth]{figs/Cubic/g=0.999900.eps}
-    \includegraphics[width=0.22\textwidth]{figs/Cubic/g=0.999000.eps}
-    \includegraphics[width=0.22\textwidth]{figs/Cubic/g=0.990000.eps}
-    \includegraphics[width=0.22\textwidth]{figs/Cubic/g=0.900000.eps}
+    \includegraphics[width=0.4\textwidth]{figs/Electrophoresis/numerical_vs_analytical_alpha=0.3_Du=0.5_zeta=6.0_Rmax=100.eps}
+    \includegraphics[width=0.4\textwidth]{figs/Electrophoresis/departure_from_linear_alpha=0.3_Du=0.5_zeta=6.0_Rmax=100.eps}
         \caption{Steady-state velocity $\cU$ as a function of the 
-        electric field magnitude $\beta$, for $\gamma < 1$. 
+        electric field magnitude $\beta$, for highly-charged surface particle
+        electrophoresis (with $\alpha = 0.3, \text{Du} = 0.5, \bar\zeta = 6$).
         The analytic solution velocity is represented by solid lines, 
-        and the numerical results are represented by square markers.}
-	    \label{fig:Cubic1}
+        and the numerical results are represented by markers.
+        The left figure shows the full numerical solution 
+        compared to the analytical one \eqref{eq:cubic}, and
+        the right figure compares the analytic cubic correction \cite{schnitzer2012cubic} 
+        to the difference between the numerical results and the linear regime.}
+	    \label{fig:Electrophoresis}
     \end{center}
 \end{figure}
-\begin{figure}[htbp]
-    \begin{center}
-    \includegraphics[width=0.22\textwidth]{figs/Cubic/g=1.000100.eps}
-    \includegraphics[width=0.22\textwidth]{figs/Cubic/g=1.001000.eps}
-    \includegraphics[width=0.22\textwidth]{figs/Cubic/g=1.010000.eps}
-    \includegraphics[width=0.22\textwidth]{figs/Cubic/g=1.100000.eps}
-        \caption{Steady-state velocity $\cU$ as a function of the 
-        electric field magnitude $\beta$, for $\gamma < 1$. 
-        The analytic solution velocity is represented by lines 
-        (solid lines for $\cU > 0$, dashed lines for $\cU < 0$), 
-        and the numerical results are represented by markers 
-        (squares for $\cU > 0$, circles for $\cU < 0$).}
-	    \label{fig:Cubic2}
-    \end{center}
-\end{figure}
+
 \begin{figure}[htbp]
@@
 % put your thanks here
-\section*{Acknowledgments}
-...
+%\section*{Acknowledgments}
 

### 2012-09-15 notes/work/figs/Cubic/extract_data.m

@@ -1,0 +1,9 @@
+clc;
+D = dir('*.mat')
+for k = 1:numel(D)
+    s = load(D(k).name, 'solutions');
+    v{k} = cellfun(@(r) r.Vinf, s.solutions);
+    b{k} = cellfun(@(r) r.beta, s.solutions);
+    g{k} = cellfun(@(r) r.gamma, s.solutions);
+end
+save data.mat v b g

### 2012-09-15 notes/work/figs/Cubic/old_show.m

@@ -1,0 +1,169 @@
+function show(name, first)
+    if nargin < 2
+        first = 1;
+    end
+    load(name);
+    figure(1); clf;
+    set(gcf, 'PaperPositionMode', 'auto');
+    set(gcf, 'Position',[100 100 600 800]);
+    try
+        v = attr(solutions, 'Vinf');
+        betas = attr(solutions, 'beta');
+    catch err
+        disp(err)
+        return
+    end
+    disp(name)
+
+    g = sol.gamma;
+    B3 = (31./(320*(g.^(1./2) + 1)) - 9./(320*(g.^(1./2) + 1).^2) + 1./1680);
+    B1 = 2*log(1./(2*g.^(1./2)) + 1./2);
+    b = logspace(log10(min(betas)), log10(max(betas)), 1000);
+    a = sol.alpha;
+    w = (248./(2560.*g.^(1./2) + 2560) - 9./(320.*(g.^(1./2) + 1).^2) - (a.*log(1./(2.*g.^(1./2)) + 1./2))./8 - (11.*log((g.^(1./2) + 1)./(2.*g.^(1./2))))./160 - (61.*a.^2.*log((g.^(1./2) + 1)./(2.*g.^(1./2))).*log(1./(2.*g.^(1./2)) + 1./2).^2)./80 - (83.*a.*log((g.^(1./2) + 1)./(2.*g.^(1./2))).*log(1./(2.*g.^(1./2)) + 1./2))./160 + (176.*a.*log(1./(2.*g.^(1./2)) + 1./2))./(1280.*g.^(1./2) + 1280) + 1./1680).*b.^3 + 2.*log(1./(2.*g.^(1./2)) + 1./2).*b;
+    w3 = b.^3*(B3 - B1*11./320);
+    w1 = b*B1;
+    clf; 
+    hold on; 
+    graph(betas, v, 'o', 's'); 
+    graph(b, w1+w3, '-', '-.'); 
+%     graph(b, w1, '-', '-'); 
+%     graph(b, w3, '-', '-'); 
+    filename = sprintf('grid = [%d x %d], Rmax = %.1e, gamma = %.4f, alpha = %.4f', ...
+        numel(sol.grid.radius), numel(sol.grid.theta), max(sol.grid.radius), ...
+        sol.gamma, sol.alpha);
+    filename = sprintf('g=%f', g);
[…]

### 2012-09-15 notes/work/figs/Cubic/plot_results_for_paper.m

@@ -1,0 +1,62 @@
+function plot_results_for_paper
+
+    load data
+
+    b = b{1};
+    g = cat(2, g{:}); g = g(1, :); g = g(:);
+    v = cat(2, v{:});
+
+    I = b < 5;
+    b = b(I);
+    v = v(I, :);
+
+    [~, I] = sort(abs(1-g));
+    g = g(I);
+    v = v(:, I);
+
+    b_ = logspace(log10(min(b)), log10(max(b)), 1000);
+    for k = 1:numel(g)
+        u(:, k) = analytic(b_, g(k));
+    end
+
+    close all;
+    clr = (0:3)'*0.25*[1 1 1];
+
+    I = g <= 1;
+    figure; hold on;
+    set(gca, 'ColorOrder', clr)
+    plot(b_, u(:, I), '-', 'LineWidth', 2);
+    plot(b, v(:, I), 'o', 'MarkerSize', 8);
+    set(gca, 'XScale', 'log', 'YScale', 'log');
+    xlim([min(b) max(b)])
+    xlabel('Electric field magnitude (\beta)', 'FontSize', 20)
+    ylabel('Steady-state velocity magnitude', 'FontSize', 20)
+    L = cellfun(@(x) sprintf('\\gamma = %.4f', x), num2cell(g(I)), 'UniformOutput', false);
+    legend(L, 'Location', 'SouthEast', 'FontSize', 18); legend boxoff;
+    grid on;
+    print('-depsc2', 'ionex_cubic1.eps')
+
+    I = g > 1;
+    figure; hold on;
+    set(gca, 'ColorOrder', clr)
+    plot(b_, u(:, I), '-', 'LineWidth', 2);
+    plot(b, v(:, I), 'o', 'MarkerSize', 8);
+    plot(b_, -u(:, I), '--', 'LineWidth', 2);
+    plot(b, -v(:, I), 's', 'MarkerSize', 8);
+    set(gca, 'XScale', 'log', 'YScale', 'log');
+    xlim([min(b) max(b)])
+    xlabel('Electric field magnitude (\beta)', 'FontSize', 20)
+    ylabel('Steady-state velocity magnitude', 'FontSize', 20)
+    L = cellfun(@(x) sprintf('\\gamma = %.4f', x), num2cell(g(I)), 'UniformOutput', false);
[…]

### 2012-09-15 notes/work/figs/Electrophoresis/plot_results_for_paper.m

@@ -1,0 +1,53 @@
+function plot_results_for_paper
+
+a = [0.0 0.3 0.5];
+Du = [0.5 0.5 1];
+z = [6 6 10];
+R = [30 100 300];
+U1 = [3.69314718055995, 3.69314718055995, 4.25752957407993];
+U3 = [0.0263988658183029, 0.304452832842969, 0.966868914065528];
+
+close all;
+
+for k = 1:3
+    for j = 2
+        f = sprintf('alpha=%.1f_Du=%.1f_zeta=%.1f_Rmax=%.0f', a(k), Du(k), z(k), R(j));
+        s = load([f '.mat']);
+
+        b = linspace(min(s.b), max(s.b), 1e3);
+        u = s.Vr1; % numerical solution
+        e = abs(s.Vr1 - U1(k) * s.b); % deviation from linear regime
+
+        figure(); hold on;        
+        plot(b, U3(k) * b.^3, '-', 'LineWidth', 2, 'Color', 'k')
+        plot(s.b, e,          'o', 'MarkerSize', 8, 'Color', 'k');
+        set(gca, 'XScale', 'log', 'YScale', 'log');
+        t = sprintf('\\alpha = %.1f, Du = %.1f, \\zeta = %.1f', a(k), Du(k), z(k));
+%         title(t, 'FontSize', 24)
+        set(gca, 'FontSize', 16)
+        xlabel('Electric field magnitude (\beta)', 'FontSize', 20)
+        ylabel('Departure from linear analytic solution', 'FontSize', 20)
+        xlim([3e-2 4])
+        ylim([3e-5 10])
+        legend({'Analytical', 'Numerical'}, 'Location', 'SouthEast', 'FontSize', 18);
+        legend boxoff;
+        grid on;    
+        print('-depsc2', sprintf('departure_from_linear_%s.eps', f))
+
+        figure(); hold on;        
+        plot(b, U1(k) * b + U3(k) * b.^3, '-', 'LineWidth', 2, 'Color', 'k');
+        plot(s.b, u,                      'o', 'MarkerSize', 8, 'Color', 'k');
+        set(gca, 'XScale', 'log', 'YScale', 'log');
+        t = sprintf('\\alpha = %.1f, Du = %.1f, \\zeta = %.1f', a(k), Du(k), z(k));
+%         title(t, 'FontSize', 24)
+        set(gca, 'FontSize', 16)
+        xlabel('Electric field magnitude (\beta)', 'FontSize', 20)
[…]

### 2012-09-15 src/main_ionex.m

@@ -9,7 +9,7 @@ function [sol] = main_ionex(init, g, betas)
     
     sol = Solution(g, init);
     sol.alpha = 0.0;
-    sol.gamma = 1.01;
+    sol.gamma = 1.0;
     force = total_force(sol, g);
     
     betas = betas(:);

### 2012-09-15 src/main_run.m

@@ -1,6 +1,6 @@
 function main_run
 
-    N = 2.^(8);
+    N = 2.^(5:8);
     Rmax = 100;
     betas = 10.^[-2:0.25:0];
     A = 1;

### 2012-09-17 notes/work/ijnam.tex
Fix after Irad review.

@@
 
-\title{Asymptotic and Numerical Solution for Electro-Kinetic Flow Around a Spherical Particle}
+\title{Asymptotic and Numerical Solution for Electrokinetic Flow Around a Spherical Particle}
 
@@
 \abstract{
-A numerical solver for the simulation of an electrokinetic 
+A numerical solver for the simulation of electrokinetic 
 migration of particles in an electrolyte solution 
-due to an application of an external electric field is presented.
+due to the application of an external electric field is presented.
 The electrokinetic transport process is
-described by a nonlinear partial differential equation system, 
+described by a system of partial differential equations (PDE), 
 as well as nonlinear effective boundary conditions, which are derived from
@@
 particle (see Figure \ref{fig:EDL}). This structure, called
-``Debye layer'', electrically screens the surface charge, thus
+``Debye layer'', electrically screens the surface charge,
 creating a potential difference between the particle and the outer
@@
 size, an analytical asymptotic solution for the Debye layer
-dynamics can be found \cite{yariv2010asymptotic}.
+dynamics can be derived \cite{yariv2010asymptotic}.
 \begin{figure}[htbp]
@@
         \caption{Schematic structure of the double layer:
-        (1) particle surface, (2) Debye layer, (3) fluid bulk.
+        (1) charged particle surface, (2) Debye layer, (3) fluid bulk.
         If the particle surface has positive (black) surface charge,
@@
 
-The variables of the electrokinetic problem are the electrostatic
+The variables of the electrokinetic flow equations are the electrostatic
 potential $\varphi$, fluid velocity $\bv$ and its pressure $p$, and
@@
 analytic solution to more general systems. Once the electric field
-becomes stronger, significant nonlinear phenomena are expected.
-This interesting regime has not yet been explored.
+becomes stronger, significant nonlinear phenomena emerge.
+This interesting regime has not yet been explored extensively.
 Recently, it has been conceived that such type of dynamics
@@
 The goal of this work is to develop and implement a software toolbox for the generation
-of iterative numerical solvers for nonlinear electrokinetic problems, and apply it to the study
-of systems that have no closed-form solutions, such as an ion-exchanger migration
+of iterative numerical solvers for nonlinear electrokinetic problems, and to apply it to the study
+of systems that have no closed-form solutions, such as ion-exchanger migration
 \cite{yariv2010migration} and the electrophoresis problem \cite{schnitzer2012surface}.
@@
 the solution of the system is described in Section \ref{sec:algorithm}.
-The analytical asymptotic solution for the non-linear system is derived 
+An analytical asymptotic solution for the non-linear system is derived 
 and presented in Section \ref{sec:asymp}.
-The numerical results and their comparison to an analytical asymptotic solution 
+Numerical results and their comparison to an analytical asymptotic solution 
 are presented Section \ref{sec:results} and discussed in Section \ref{sec:discussion}.
@@
 
-The dimensional Stokes equations are given by:
+The dimensional Stokes equations with electrostatic forces are given by:
 \begin{equation} \begin{array}{cc}
@@
 
-After nondimensionalization, the Nernst-Plank, Stokes and Poisson equations are:
+After nondimensionalization, the Nernst-Plank, Stokes and Poisson equations read:
 \begin{equation} \label{eq:nernst}
@@
 The ionic fluxes are given by ion diffusion, electrostatic forces and ion advection by the fluid
-at Eq. \eqref{eq:nernst}. Due to conservation of ions, the fluxes are divergence-free:
+in \eqref{eq:nernst}. Due to conservation of ions' concentrations, the fluxes are divergence-free:
 \begin{equation*}
@@
 \subsection{Boundary conditions}
-We assume that a constant constant electric field of nondimensional magnitude $\beta$,
-is applied to the system, in direction denoted by the unit vector $\ui$.
-As a result, the particle will equilibrate in 
+We assume that a constant electric field of nondimensional magnitude $\beta$,
+is applied to the system, in the direction denoted by the unit vector $\ui$.
+As a result, the particle will equilibrate at 
 a non-zero steady-state velocity $\cU \ui$, which is
@@
 We employ the reference frame of the particle.
-Far away from it, we have a uniform applied electrostatic field, uniform flow,
+Far away from the particle, we have a uniform applied electrostatic field, uniform flow,
 and ambient ionic concentrations:
@@
 We consider the following scenarios:
-\subsubsection{Ion-exchanger (\cite{yariv2010migration})}
+\subsubsection{Ion-exchanger \cite{yariv2010migration}}
 We assume high conductance of the particle (yielding a uniform electric potential),
@@
 where $\gamma$ is the ratio between the cationic concentration on the surface and the cationic
-concentration in the fluid bulk.
-
-\subsubsection{Inert particle (\cite{schnitzer2012surface})}
+concentration in the fluid bulk and $\cV$ is an unknown constant electric potential at
+the ion-exchanger surface.
+
+\subsubsection{Inert particle \cite{schnitzer2012surface}}
 We assume constant surface charge
@@
 \bv = \bzero, &
-\bn \cdot \bj_\pm = 0.
+\bn \cdot \bj_\pm = 0,
 \end{array}
@@
 When $\delta \ll 1$, 
-most of the fluid remains electroneutral ($q \approx 0$, thus $c_+ \approx c_-$), 
-except a thin boundary layer of width $O(\delta)$, 
-known as the ``Debye layer'', surrounding the particle.
+the fluid remains electroneutral ($q \approx 0$, thus $c_+ \approx c_-$), 
+except a thin boundary layer of width $O(\delta)$ 
+surrounding the particle (the ``Debye layer'').
 This boundary layer makes it very hard to construct 
 a direct numerical solver for the full electro-kinetic problem.
-
-Due to the scale disparity at the Debye layer, 
-the PDE system can be rewritten in the ``inner'' region 
-as an ODE system using the asymptotic limit of $\delta \rightarrow 0$ 
-and can be integrated and solved analytically,
-yielding an ``effective'' boundary conditions for the ``outer'' bulk region equations near
-the particle surface.
+However, we exploit the scale disparity at the Debye layer, 
+which allows the PDE system to be rewritten in the ``inner'' region 
+as an ODE system using the asymptotic limit of $\delta \rightarrow 0$.
+This system can be integrated and solved analytically,
+yielding ``effective'' boundary conditions near
+the particle surface for the ``outer'' bulk region equations.
 
 \subsubsection  {Bulk-scale equations}
-The Nernst-Planck equations above \eqref{eq:fluxes} for the fluid bulk (outside
-the boundary layer), using bulk variables denoted by uppercase letters, read:
+The Nernst-Planck equations above \eqref{eq:fluxes} for the fluid bulk outside
+the boundary layer, using bulk variables denoted by uppercase letters, read:
 \begin{equation} \begin{array}{cccc} \label{eq:bulk_flux}
@@
 approximation for the nonlinear PDE system,
-for a given electric field $\beta$ and a velocity $\cU$. 
+for a given electric field $\beta$ and assumed velocity $\cU$. 
 The resulting nonlinear discrete system is
@@
 Charge and salt fluxes \eqref{eq:bulk_flux} are discretized on grid cell boundaries 
-(using upwind scheme $\mathcal{U}$ for numerical stability at large cell Peclet number)  
+(using an upwind scheme $\mathcal{U}$ for numerical stability at large cell Peclet number)  
 using \eqref{eq:disc_diff} and \eqref{eq:disc_interp}:
@@
 
-The specific boundary condition at $r=1$
+The specific boundary conditions at $r=1$
 depend on the chemical properties of particle surface.
@@
 (given that the fluid is at rest far away from it).
-After the convergence of the solver, when the residual norm is below
+After the convergence of the solver, once the residual norm is below
 a prescribed threshold $\|\cO(\bx_n)\| < \epsilon$, 
@@
 (as derived in \cite{yariv2010migration}), and the solver convergence is fast.
-However, this is no longer true for $\beta \sim O(1)$, since the nonlinear terms become dominant
+However, this is no longer true for $\beta \sim O(1)$, because the nonlinear terms become dominant
 and the iterative solver may not converge at all if we start with an arbitrary initial guess.
-In order to find a solution for such $\beta$, continuation method is used:
+In order to find a solution for such $\beta$, a continuation method is used:
 the solver is applied to a sequence of $\{\beta_i\}_{i=0}^n$ such that $\beta_0 = 0$,
@@
 which are used to construct the system operator $\cO$, so that 
-the Newton method solver (that requires computing the residual and the gradient) 
+the Newton solver (that requires computing the residual and the gradient) 
 can be applied automatically.
@@
 In order to validate the numerical results, an asymptotic analysis is applied 
-to the nonlinear systems of ion-exchanger migration (\cite{yariv2010migration, zeyde2012report})
-and highly charged particle electrophoresis (\cite{schnitzer2012surface, schnitzer2012cubic}).
-
-The derivation works as follows.
+to the nonlinear systems of ion-exchanger migration 
+and highly charged particle electrophoresis.
+We present here the asymptotic analysis for the ion-exchanger case \cite{yariv2010migration}
+and the asymptotic analysis for the electrophoresis case \cite{schnitzer2012surface}
+appears in \cite{schnitzer2012cubic}.
+
+The derivation is performed as follows.
 The nonlinear system (composed of the governing equations and the boundary conditions) 
@@
 \end{equation}
-The nonlinear 
+The nonlinear terms
 are expanded around $\beta = 0$:
@@
 the cubic correction \cite{zeyde2012report} velocity terms (for $\alpha = 0$)
- are:
+turn out to be:
 \begin{equation}
@@
 \end{equation}
+That is, there may be a specific nonzero external field for which the particle remains at rest. The physical viability of this solution has yet to be explored.
 
@@
 \cite{schnitzer2012surface}. 
-The solver is applied to a series of values of $\beta$, ranging 
-from $\beta \ll 1$ up to $\beta \sim O(1)$.
+The solver is applied to a series of values of the electric field $\beta$, ranging 
+from $\beta \ll 1$ to $\beta \sim O(1)$.
 For each $\beta$ value, the steady-state velocity $\cU(\beta)$ is computed. 
@@
 The linear solution for $\gamma \approx 1$, 
-yields a sign change in the zeta potential $\zeta = \log (C/\gamma)$, when
+yields a sign change of the zeta potential $\zeta = \log (C/\gamma)$, when
 $|\log\gamma| \approx 3\beta / 4$. This results in a sign change in the slip velocity,
@@
 In order to verify the solver, the numerical steady-state velocity is compared to the
-analytical solution \cite{schnitzer2012cubic}. Since cubic correction is much smaller than
-the linear regime for $\beta \ll 1$, the difference between numerical results and
-the linear regime is compared to the cubic correction term.
+analytical solution \cite{schnitzer2012cubic}. Since the cubic correction is much smaller than
+the linear solution for $\beta \ll 1$, the difference between numerical results and
+the linear solution is compared to the cubic correction term.
 
 Since the leading order of the solution $\cU(\beta)$ is linear for $\beta \ll 1$, 
-the numerical discretization error is $O(\beta)$ too.
+the numerical discretization error is $O(\beta)$ as well.
 In order to reduce the discretization error of the numerical solution \eqref{eq:disc_zero_force}
@@
 shown above.
-
 Moreover, two interesting phenomena (cubic regime and downstream vortex) were predicted
@@
 nonlinear system.
-
 Future work may include replacing the full Newton step by an iterative linear solver, so 
-finer grids could be used and higher electric field magnitudes be achieved.
+finer grids could be used.
+Since it is expected that a boundary layer should form around the particle for $\beta \gg 1$,
+a numerical solver should be able to handle large grids to achieve good numeric accuracy.
 
@@
         electric field magnitude $\beta$, for $\gamma < 1$ (left) and $\gamma > 1$ (right). 
-        The analytic cubic solution \eqref{eq:cubic} is represented by lines 
-        (solid lines for $\cU > 0$, dashed lines for $\cU < 0$), 
+        The analytic cubic solution \eqref{eq:cubic} is represented by curves
+        (solid for $\cU > 0$, dashed for $\cU < 0$), 
         and the numerical results are represented by markers 
         (circles for $\cU > 0$, squares for $\cU < 0$). Note that linear and
-        cubic regimes fit well the numerical results, including the critical $\beta$ 
+        cubic regimes match well the numerical results, including the critical $\beta$ 
         behaviour \eqref{eq:crit_beta}.
@@
         the right figure compares the analytic cubic correction \cite{schnitzer2012cubic} 
-        to the difference between the numerical results and the linear regime.}
+        to the difference between the numerical results and the linear regime.
+        When $\beta$ is large, the analytical cubic solution loses its validity 
+        because higher-order terms become significant.}
 	    \label{fig:Electrophoresis}
@@
 	\includegraphics[width=0.45\textwidth]{figs/Stream/A0.01.eps}
-	\includegraphics[width=0.45\textwidth]{figs/Stream/N0.02.eps}
-	\includegraphics[width=0.45\textwidth]{figs/Stream/A0.02.eps}
 	\includegraphics[width=0.45\textwidth]{figs/Stream/N0.04.eps}
@@
 
-\bibliographystyle{plain}
+\bibliographystyle{unsrt}
 \bibliography{ijnam}

### 2012-09-18 notes/work/ijnam.tex
Typo Fix for Cubic Solution

@@
 The electrokinetic transport process is
-described by a system of partial differential equations (PDE), 
-as well as nonlinear effective boundary conditions, which are derived from
+described by a system of partial differential equations (PDE).
+A boundary layer forms around the particle, whose scale disparity
+is used to derive nonlinear effective boundary conditions using 
 the specific chemical properties of the particle.
@@
     \begin{center}
-    \includegraphics[width=0.4\textwidth]{figs/Electrophoresis/numerical_vs_analytical_alpha=0.3_Du=0.5_zeta=6.0_Rmax=100.eps}
-    \includegraphics[width=0.4\textwidth]{figs/Electrophoresis/departure_from_linear_alpha=0.3_Du=0.5_zeta=6.0_Rmax=100.eps}
+    \includegraphics[width=0.4\textwidth]{figs/Electrophoresis/numerical_vs_analytical_alpha=0.5_Du=1.0_zeta=10.0_Rmax=100.eps}
+    \includegraphics[width=0.4\textwidth]{figs/Electrophoresis/departure_from_linear_alpha=0.5_Du=1.0_zeta=10.0_Rmax=100.eps}
         \caption{Steady-state velocity $\cU$ as a function of the 
         electric field magnitude $\beta$, for highly-charged surface particle
-        electrophoresis (with $\alpha = 0.3, \text{Du} = 0.5, \bar\zeta = 6$).
+        electrophoresis (with $\alpha = 0.5, \text{Du} = 1, \bar\zeta = 10$).
         The analytic solution velocity is represented by solid lines, 

### 2012-09-18 src/plot_results_for_paper.m

@@ -1,0 +1,53 @@
+function plot_results_for_paper(p)
+
+a = [0.0 0.3 0.5];
+Du = [0.5 0.5 1];
+z = [6 6 10];
+R = [30 100 300];
+U1 = [3.69314718055995, 3.69314718055995, 4.25752957407993];
+U3 = [0.0263988658183029, 0.304452832842969, 0.966868914065528];
+
+close all;
+
+for k = 1:3
+    for j = 2
+        f = sprintf('alpha=%.1f_Du=%.1f_zeta=%.1f_Rmax=%.0f', a(k), Du(k), z(k), R(j));
+        s = load(fullfile(p, [f '.mat']));
+
+        b = linspace(min(s.b), max(s.b), 1e3);
+        u = s.Vr; % numerical solution
+        e = abs(s.Vr - U1(k) * s.b); % deviation from linear regime
+
+        figure(); hold on;        
+        plot(b, U3(k) * b.^3, '-', 'LineWidth', 2, 'Color', 'k')
+        plot(s.b, e,          'o', 'MarkerSize', 8, 'Color', 'k');
+        set(gca, 'XScale', 'log', 'YScale', 'log');
+        t = sprintf('\\alpha = %.1f, Du = %.1f, \\zeta = %.1f', a(k), Du(k), z(k));
+%         title(t, 'FontSize', 24)
+        set(gca, 'FontSize', 16)
+        xlabel('Electric field magnitude (\beta)', 'FontSize', 20)
+        ylabel('Departure from linear analytic solution', 'FontSize', 20)
+        xlim([2e-2 4])
+        ylim([8e-6 10])
+        legend({'Analytical', 'Numerical'}, 'Location', 'SouthEast', 'FontSize', 18);
+        legend boxoff;
+        grid on;    
+        print('-depsc2', fullfile(p, sprintf('departure_from_linear_%s.eps', f)))
+
+        figure(); hold on;        
+        plot(b, U1(k) * b + U3(k) * b.^3, '-', 'LineWidth', 2, 'Color', 'k');
+        plot(s.b, u,                      'o', 'MarkerSize', 8, 'Color', 'k');
+        set(gca, 'XScale', 'log', 'YScale', 'log');
+        t = sprintf('\\alpha = %.1f, Du = %.1f, \\zeta = %.1f', a(k), Du(k), z(k));
+%         title(t, 'FontSize', 24)
+        set(gca, 'FontSize', 16)
[…]

### 2012-09-18 notes/work/figs/Cubic/plot_stream_for_paper.m
Work on LaTeX figurse

@@ -20,13 +20,13 @@ function plot_stream_for_paper(name)
         axis equal;
         axis([-1 1 -.5 .5]*10)        
         hold off;
-        txt = sprintf('Analytical: \\alpha = %.1f, \\beta = %.2f, \\gamma = %.4f', a, b, g);
+        txt = sprintf('Analytical: \\beta = %.2f', b);
         title(txt, 'FontSize', 16, 'FontWeight', 'bold');
         set(gca, 'XTick', [], 'YTick', [])
-        n = sprintf('Stream/A%_4f_%.4f.eps', k, g, b);
+        n = sprintf('Stream/A_%.4f_%.4f.eps', g, b);
         print('-deps2', n)
 
-        %fprintf('\\includegraphics[width=0.45\\textwidth]{figs/%s}\n', n)
+        fprintf('\\includegraphics[width=0.45\\textwidth]{figs/%s}\n', n)
 
         figure(2); clf; hold on        
         psi = [];
@@ -35,13 +35,13 @@ function plot_stream_for_paper(name)
         axis equal;
         axis([-1 1 -.5 .5]*10)        
         hold off;
-        txt = sprintf('Numerical: \\alpha = %.1f, \\beta = %.2f, \\gamma = %.4f', a, b, g);
+        txt = sprintf('Numerical: \\beta = %.2f', b);
         title(txt, 'FontSize', 16, 'FontWeight', 'bold');
         set(gca, 'XTick', [], 'YTick', [])
-        n = sprintf('Stream/N%_4f_%.4f.eps', k, g, b);
+        n = sprintf('Stream/N_%.4f_%.4f.eps', g, b);
         print('-deps2', n)
         
-        %fprintf('\\includegraphics[width=0.45\\textwidth]{figs/%s}\n', n)
+        fprintf('\\includegraphics[width=0.45\\textwidth]{figs/%s}\n', n)
     end
 
 end

### 2012-09-20 notes/work/ijnam.tex
Work on LaTeX figurse
Review and add more results

@@
 \abstract{
-A numerical solver for the simulation of electrokinetic 
+A numerical framework for the simulation of electrokinetic 
 migration of particles in an electrolyte solution 
@@
 The electrokinetic transport process is
-described by a system of partial differential equations (PDE).
-A boundary layer forms around the particle, whose scale disparity
-is used to derive nonlinear effective boundary conditions using 
-the specific chemical properties of the particle.
-The nonlinear system is discretized and an iterative Newton solver is constructed
-automatically from the discrete equations.
-An asymptotic analytical solution is derived for the validation of the solver. 
-The numerical results are obtained and are compared to the asymptotic solutions, 
-and good correspondence is achieved.}
+described by a system of nonlinear partial differential equations (PDE).
+A thin boundary layer forms around the particle due to strong electrostatic forces. The resulting
+scale disparity of the boundary layer
+is used to derive nonlinear effective boundary conditions for the
+numerical solver
+using the specific chemical properties of the particle.
+The nonlinear system is discretized and an iterative Newton solver is
+constructed automatically from the discrete equations and boundary 
+conditions.
+An asymptotic analytical solution is 
+derived for the validation of the solver. 
+The numerical results are obtained for an ion-exchangers and 
+surface charged inert particles. The numerical results 
+are compared to the asymptotic solutions, and good correspondence is achieved.}
 
@@
 given the current solution $\bx$.
-Then, a sparse linear system needs to be solved to yield the update for the 
-increment $\Delta \bx = -\bG^{-1} \br$.
+Then, a sparse linear system $\bG \Delta \bx = \br$
+needs to be solved to yield the update $\Delta \bx$.
 When the method converges, $\bx_n \rightarrow \bx_\infty$, 
@@
 
+\subsubsection{Singularity Handling} \label{sec:singular}
+The electric potential $\varPhi$ (in electrophoresis case) and the pressure $P$ (in both cases) 
+are defined up to an additive constant, since the system equations and the boundary conditions
+contain only their derivatives.
+In order to overcome the singularity of the linear system 
+$\bG \Delta\bx = -\br$, we set the variable at 
+a specific grid point to be $0$.
+In order to have square system, we should remove one conservation equation at this grid point too.
+In case of the pressure $P$, we remove one mass conservation equation,
+$\bnabla \cdot \bV = 0$, at this grid point. 
+In case of the electric potential, we remove the charge conservation
+equation, $\bnabla \cdot \pars{C \bnabla \varPhi} = 0$, at this grid point.
+For $\br = \cO(\bx)$ and $\bG = \bnabla \cO(\bx)$, the new square linear system read:
+\begin{equation}
+\mathbb{R} \bG \mathbb{P} \cdot \delta\bx = -\mathbb{R} \br
+\end{equation}
+where $\mathbb{P}$ matrix is used to remove the columns
+and $\mathbb{R}$ matrix is used to remove the rows of $\bG$,
+whre the update step is $\Delta \bx = \mathbb{P} \cdot \delta \bx$.
+
 \subsubsection{Iterative Newton solver}
@@
 \item Compute the right-hand side: $\boldsymbol{r}_n = \verb|op.res()|$
-\item Solve sparse linear system: $\boldsymbol{G}_n \Delta \bx_n = -\boldsymbol{r}_n$
-\item Update solution: $\bx_{n+1} = \bx_{n} + \Delta \bx_{n}$
+\item Solve sparse linear system: $\mathbb{R}\boldsymbol{G}_n \mathbb{P} \Delta \bx_n = -\mathbb{R}\boldsymbol{r}_n$
+\item Update solution: $\bx_{n+1} = \bx_{n} + \mathbb{P}\Delta \bx_{n}$
 \end{enumerate}
@@
 from $\beta \ll 1$ to $\beta \sim O(1)$.
-For each $\beta$ value, the steady-state velocity $\cU(\beta)$ is computed. 
+For each $\beta$ value, 
+Newton solver is initialized with the linear solution and is iterated $K$ times.
+Secant method iteration is applied $M$ times to find the steady-state velocity 
+by finding $\cU$ such that $F_\imath(\cU, \beta) = 0$, thus computing 
+the steady-state velocity $\cU(\beta)$. 
 The resulting $\cU(\beta)$ is plotted on a log-log scale, so that the asymptotic behaviour
@@
 the results of the asymptotic analysis of the nonlinear 
-system \cite{zeyde2012report, schnitzer2012cubic}. 
+system \cite{schnitzer2012cubic, zeyde2012report}. 
 The numerical results are compared 
@@
 as well as the analytical ones \eqref{eq:cubic}, are given in Figure \ref{fig:IonExCubic}.
+The numerical solver uses $N_r \times N_\theta = (400 \times 50)$, 
+$R_{\max} = 10^7$,
+$K = 3$, $M = 5$ and $\beta = 10^{t}$ for $t = -2:0.1:0.5$.
 
@@
 are given at Figure \ref{fig:Electrophoresis}.
+The numerical solver uses $N_r \times N_\theta = (128 \times 128)$ and $(256 \times 256)$
+for Richardson extrapolation, $R_{\max} = 10^2$,
+$K = 3$, $M = 5$ and $\beta = 0.1 \cdot 2^{t}$ for $t = -2:0.5:5$.
 
@@
 \section{Discussion} \label{sec:discussion}
-A numerical solver for nonlinear electrokinetic transport system is described.
+A numerical framework for solver construction for 
+nonlinear electrokinetic transport system is described.
+The framework is applied to two electrokinetic problems: the migration of ion-exchangers
+and surface-charged inert particle electrophoresis.
 The numerical results exhibit a good correspondence to the asymptotic linear model as
@@
 nonlinear system.
+
 Future work may include replacing the full Newton step by an iterative linear solver, so 
@@
 a numerical solver should be able to handle large grids to achieve good numeric accuracy.
+In addition, the framework may be used for automatic Newton solver construction for 
+other similar nonlinear PDE systems.
 
@@
 	    \label{fig:IonExCubic}
+    \end{center}
+\end{figure}
+
+\begin{figure}[htbp]
+    \begin{center}
+	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/N_0.9000_0.1000.eps}
+	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/A_0.9000_0.1000.eps}
+	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/N_0.9000_0.3981.eps}
+	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/A_0.9000_0.3981.eps}
+	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/N_0.9000_1.0000.eps}
+	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/A_0.9000_1.0000.eps}
+        \caption{Streamlines of the flow for various electric field $\beta$ values: 
+        numerical results (left) and analytical approximation (right) for 
+        $\gamma = 0.99$.  The steady-state velocity $\cU$ is positive, so the
+        ion-exchanger drifts to the right. 
+        Note that there is good correspondence between the numerical
+        results and the analytical solution for $\beta < 1$, validating
+        the vortex formation. For $\beta \ge 1$, the cubic analytical
+        solution does not match the numerical results, probably due
+        to further nonlinear terms in the solution.
+        }
+    \label{fig:Vortex}
     \end{center}
@@
 
-\begin{figure}[htbp]
-    \begin{center}
-	\includegraphics[width=0.45\textwidth]{figs/Stream/N0.01.eps}
-	\includegraphics[width=0.45\textwidth]{figs/Stream/A0.01.eps}
-	\includegraphics[width=0.45\textwidth]{figs/Stream/N0.04.eps}
-	\includegraphics[width=0.45\textwidth]{figs/Stream/A0.04.eps}
-	\includegraphics[width=0.45\textwidth]{figs/Stream/N0.08.eps}
-	\includegraphics[width=0.45\textwidth]{figs/Stream/A0.08.eps}
-        \caption{Streamlines of the flow for various electric field $\beta$ values: 
-        numerical results (left) and analytical approximation (right) for 
-        $\gamma = 0.99$.  The steady-state velocity $\cU$ is positive, so the
-        ion-exchanger drifts to the right. 
-        }
-    \label{fig:Vortex}
-    \end{center}
-\end{figure}
-
 % put your thanks here

### 2012-09-20 src/main_ephor.m

@@ -1,4 +1,4 @@
-function [sol] = main(init, g, betas)
+function [sol] = main_ephor(init, g, betas, conf)
     if isempty(init)
         init.Phi = zeros(g.Phi.size);
         init.C = ones(g.C.size);
@@ -8,16 +8,16 @@ function [sol] = main(init, g, betas)
     end
     
     sol = Solution(g, init);
-    sol.alpha = 0.3;
-    sol.Du = 0.5;
-    sol.zeta = 6;
+    sol.alpha = conf.alpha;
+    sol.Du = conf.Du;
+    sol.zeta = conf.zeta;
     force = total_force(sol, g);
     
     betas = betas(:);
     V = zeros(size(betas));
     tic;
     for k = 1:numel(betas)
-        fprintf('==================================================================\n')
+        fprintf('======================= Electrophoresis ===============================\n')
         sol.beta = betas(k);
         Vinf = sol.beta * (sol.Du*log(16) + sol.zeta)/(1 + 2*sol.Du);
         [iter, v] = secant(Vinf * [0.9, 1.1]);

### 2012-09-20 src/main_run.m

@@ -1,14 +1,15 @@
 function main_run
 
-    N = 2.^(5:8);
+    N = 2.^(6:8);
     Rmax = 100;
-    betas = 10.^[-2:0.25:0];
+    betas = 0.1 * 2.^[-2:0.5:5];
     A = 1;
     for a=A
         for n=N 
             for r=Rmax
                 g = grids(r, n+1, n+1, a);
-                main_ionex([], g, betas);
+                main_ephor([], g, betas, struct('alpha', 0.2, 'Du', 0.5, 'zeta', 6));
+                main_ephor([], g, betas, struct('alpha', 0.4, 'Du', 0.5, 'zeta', 6));
             end
         end
     end

### 2012-09-20 src/plot_results_for_paper.m

@@ -1,15 +1,15 @@
 function plot_results_for_paper(p)
 
-a = [0.0 0.3 0.5];
-Du = [0.5 0.5 1];
-z = [6 6 10];
+a = [0.0 0.2 0.3 0.4 0.5];
+Du = [0.5 0.5 0.5 0.5 1];
+z = [6 6 6 6 10];
 R = [30 100 300];
-U1 = [3.69314718055995, 3.69314718055995, 4.25752957407993];
-U3 = [0.0263988658183029, 0.304452832842969, 0.966868914065528];
+U1 = [3.69314718055995, 3.69314718055995, 3.69314718055995, 3.69314718055995, 4.25752957407993];
+U3 = [0.0263988658183029, 0.196596577997397, 0.304452832842969, 0.427480686859225, 0.966868914065528];
 
 close all;
 
-for k = 1:3
+for k = 1:5
     for j = 2
         f = sprintf('alpha=%.1f_Du=%.1f_zeta=%.1f_Rmax=%.0f', a(k), Du(k), z(k), R(j));
         s = load(fullfile(p, [f '.mat']));
@@ -23,7 +23,7 @@ for k = 1:3
         plot(s.b, e,          'o', 'MarkerSize', 8, 'Color', 'k');
         set(gca, 'XScale', 'log', 'YScale', 'log');
         t = sprintf('\\alpha = %.1f, Du = %.1f, \\zeta = %.1f', a(k), Du(k), z(k));
-%         title(t, 'FontSize', 24)
+        title(t, 'FontSize', 24)
         set(gca, 'FontSize', 16)
         xlabel('Electric field magnitude (\beta)', 'FontSize', 20)
         ylabel('Departure from linear analytic solution', 'FontSize', 20)
@@ -39,7 +39,7 @@ for k = 1:3
         plot(s.b, u,                      'o', 'MarkerSize', 8, 'Color', 'k');
         set(gca, 'XScale', 'log', 'YScale', 'log');
         t = sprintf('\\alpha = %.1f, Du = %.1f, \\zeta = %.1f', a(k), Du(k), z(k));
-%         title(t, 'FontSize', 24)
+        title(t, 'FontSize', 24)
         set(gca, 'FontSize', 16)
         xlabel('Electric field magnitude (\beta)', 'FontSize', 20)
         ylabel('Steady-state velocity', 'FontSize', 20)

### 2012-09-20 src/rename_results.m

@@ -14,8 +14,8 @@ for k = 1:numel(D)
     Nr = numel(S.g.r)-1;
     Nt = numel(S.g.t)-1;
     Rmax = max(S.g.r);
-    t = sprintf('%dx%d_Rmax=%.0f_beta=%.3f_alpha=%.1f_gamma=%.5f.mat', ...
-        Nr, Nt, Rmax, S.sol.beta, S.sol.alpha, S.sol.gamma);
+    t = sprintf('%dx%d_Rmax=%.0f_beta=%.3f_alpha=%.1f_Du=%.1f_zeta=%.1f.mat', ...
+        Nr, Nt, Rmax, S.sol.beta, S.sol.alpha, S.sol.Du, S.sol.zeta);
     dst = fullfile(p, t);
     cmd = sprintf('mv -v %s %s', src, dst);
     % disp(cmd)

### 2012-09-20 notes/work/ijnam.tex
Add Irad remarks.

@@
 derived for the validation of the solver. 
-The numerical results are obtained for an ion-exchangers and 
-surface charged inert particles. The numerical results 
+Numerical results are obtained for an ion-exchanger and 
+for a surface charged inert particle. The numerical results 
 are compared to the asymptotic solutions, and good correspondence is achieved.}
 
-\keywords{CFD, electrokinetics, asymptotics}
+\keywords{CFD, electrokinetics, asymptotics, ion-exchanger, electrophoresis}
 
@@
 the solution of the system is described in Section \ref{sec:algorithm}.
-An analytical asymptotic solution for the non-linear system is derived 
+An analytical asymptotic solution for the nonlinear system is derived 
 and presented in Section \ref{sec:asymp}.
@@
 
-The dimensional Poisson equation can be written as:
+The dimensional Poisson equation can be written as
 \begin{equation}
@@
 The ionic fluxes are given by ion diffusion, electrostatic forces and ion advection by the fluid
-in \eqref{eq:nernst}. Due to conservation of ions' concentrations, the fluxes are divergence-free:
+in \eqref{eq:nernst}. Due to conservation of ion concentrations, the fluxes are divergence-free:
 \begin{equation*}
@@
 the fluid remains electroneutral ($q \approx 0$, thus $c_+ \approx c_-$), 
-except a thin boundary layer of width $O(\delta)$ 
+except inside a thin boundary layer of width $O(\delta)$ 
 surrounding the particle (the ``Debye layer'').
 This boundary layer makes it very hard to construct 
-a direct numerical solver for the full electro-kinetic problem.
+a direct numerical solver for the full electrokinetic problem.
 However, we exploit the scale disparity at the Debye layer, 
@@
 where $\cO$ is the system equations operator, 
-derived by concatenation of the system equations (described at Subsection \ref{sec:disc_equations})
-and the boundary conditions operators (described at Subsection \ref{sec:disc_boundary}).
+derived by concatenation of the system equations (described in Subsection \ref{sec:disc_equations})
+and the boundary conditions operators (described in Subsection \ref{sec:disc_boundary}).
 This way, the same numerical solver handles both the nonlinear system equation and nonlinear
@@
 (as derived in \cite{yariv2010migration}), and the solver convergence is fast.
-However, this is no longer true for $\beta \sim O(1)$, because the nonlinear terms become dominant
+However, this is no longer true for $\beta \gtrsim 1$, because the nonlinear terms become dominant
 and the iterative solver may not converge at all if we start with an arbitrary initial guess.
@@
 can be implemented as linear sparse operators, by constructing 
-an appropriate sparse matrix $L$, having $O(\dim \bx)$ non-zeroes).
+an appropriate sparse matrix $L$, having $O(\dim \bx)$ non-zeroes.
 This way, the computation of the residual is very fast, taking $O(\dim \bx)$ time,
-and the gradient is computed only once.
+and the gradient does not depend on $\bx$.
 
@@
 a specific grid point to be $0$.
-In order to have square system, we should remove one conservation equation at this grid point too.
-In case of the pressure $P$, we remove one mass conservation equation,
+In order to retain square system, we should remove one conservation equation at this grid point too.
+In the case of pressure $P$, we remove one mass conservation equation,
 $\bnabla \cdot \bV = 0$, at this grid point. 
-In case of the electric potential, we remove the charge conservation
+In the case of electric potential, we remove the charge conservation
 equation, $\bnabla \cdot \pars{C \bnabla \varPhi} = 0$, at this grid point.
-For $\br = \cO(\bx)$ and $\bG = \bnabla \cO(\bx)$, the new square linear system read:
-\begin{equation}
-\mathbb{R} \bG \mathbb{P} \cdot \delta\bx = -\mathbb{R} \br
+For $\br = \cO(\bx)$ and $\bG = \bnabla \cO(\bx)$, the new square linear system reads:
+\begin{equation}
+\mathbb{R} \bG \mathbb{P} \cdot \delta\bx = -\mathbb{R} \br,
 \end{equation}
@@
 and $\mathbb{R}$ matrix is used to remove the rows of $\bG$,
-whre the update step is $\Delta \bx = \mathbb{P} \cdot \delta \bx$.
+where the update step is $\Delta \bx = \mathbb{P} \cdot \delta \bx$.
 
@@
 and highly charged particle electrophoresis.
-We present here the asymptotic analysis for the ion-exchanger case \cite{yariv2010migration}
+We present here the asymptotic analysis for the ion-exchanger case \cite{yariv2010migration},
 and the asymptotic analysis for the electrophoresis case \cite{schnitzer2012surface}
@@
 are expanded around $\beta = 0$:
-\begin{eqnarray*}
-\bzero = \cO(\bx) = \sum_i \cO_i(\bx_0, \ldots \bx_i) \beta^i
-\end{eqnarray*}
+\begin{equation}
+\bzero = \cO(\bx) = \sum_i \cO_i(\bx_0, \ldots \bx_i) \beta^i.
+\end{equation}
 
@@
 For $\beta = 0$ (no electric field is applied), the steady-state solution is $\cU = 0$:
-\begin{eqnarray*}\begin{array}{cccc}
+\begin{equation}\begin{array}{cccc}
 \varPhi_0(r,\theta) = 0, &
@@
 P_0(r,\theta) = 0.
-\end{array}\end{eqnarray*}
+\end{array}\end{equation}
 
 Assuming $\beta \ll 1$, the linearized equations and boundary conditions are:
-\begin{eqnarray*}
+\begin{equation} \begin{array}{ccc}
 \Laplacian \varPhi_1 = 0, &
@@
 \bLaplacian \bV_1 - \bnabla P_1 = \bzero.
-\end{eqnarray*}
+\end{array}\end{equation}
 
@@
 \begin{equation} \label{eq:linear_velocity}
-\cU_1(\gamma) = 2 \log \pars{\frac{1 + \gamma^{-\frac{1}{2}}}{2}}
+\cU_1(\gamma) = 2 \log \pars{\frac{1 + \gamma^{-\frac{1}{2}}}{2}}.
 \end{equation}
@@
 The solver is applied to a series of values of the electric field $\beta$, ranging 
-from $\beta \ll 1$ to $\beta \sim O(1)$.
-For each $\beta$ value, 
-Newton solver is initialized with the linear solution and is iterated $K$ times.
+from $\beta \ll 1$ to $\beta \sim 1$.
+For each $\beta$ value, the Newton solver is initialized with the linear solution and is iterated $K$ times.
 Secant method iteration is applied $M$ times to find the steady-state velocity 
@@
 results and by asymptotic expansion of the nonlinear system (for $\alpha=0$).
-The switch from the linear regime to the cubic regime occurs at a critical electric
-field value $\beta_c = O(\sqrt{|\gamma - 1|})$.
+The switch from the linear regime to the cubic regime occurs at 
+an electric field value of $\beta = O(\sqrt{|\gamma - 1|})$.
 The numerical results $\cU^h$, 
@@
 are given at Figure \ref{fig:Electrophoresis}.
-The numerical solver uses $N_r \times N_\theta = (128 \times 128)$ and $(256 \times 256)$
-for Richardson extrapolation, $R_{\max} = 10^2$,
+The numerical solver uses $R_{\max} = 10^2$,
 $K = 3$, $M = 5$ and $\beta = 0.1 \cdot 2^{t}$ for $t = -2:0.5:5$.
+The solver is applied to 2 grids of $N_r \times N_\theta = (128 \times 128)$ as the coarse grid,
+and $N_r \times N_\theta = (256 \times 256)$ as the fine grid, in order to use Richardson extrapolation for $\hat\cU$.
 
@@
 \section{Discussion} \label{sec:discussion}
-A numerical framework for solver construction for 
+A numerical framework for solver construction for a
 nonlinear electrokinetic transport system is described.
@@
 
-Future work may include replacing the full Newton step by an iterative linear solver, so 
-finer grids could be used.
+Future work may include replacing the full Newton step by an iterative linear solver, allowing
+finer grids to be used.
 Since it is expected that a boundary layer should form around the particle for $\beta \gg 1$,
@@
         ion-exchanger drifts to the right. 
-        Note that there is good correspondence between the numerical
+        Note that there is a good correspondence between the numerical
         results and the analytical solution for $\beta < 1$, validating
         the vortex formation. For $\beta \ge 1$, the cubic analytical
-        solution does not match the numerical results, probably due
-        to further nonlinear terms in the solution.
+        solution does not match the numerical results, due
+        to the influence of higher order nonlinear terms in the  solution.
         }

### 2012-09-21 notes/work/cubic_report.tex
Add cubic report

--- 2012-09-18 notes/work/ijnam.tex
@@
-\documentclass[10pt]{ijnam}
+\documentclass[10pt]{article}
 \hsize=5.5 true in
@@
 \topmargin 1in
-
-%% information for the editor
-\def\currentvolume{1}
-\def\currentissue{1}
-\def\currentyear{2004}
-\def\month{October}
-\pagespan{1}{18}
-\copyrightinfo{2012}{} % copyright year
 
@@
 
-\title{Asymptotic and Numerical Solution for Electrokinetic Flow Around a Spherical Particle}
+\title{Asymptotic Nonlinear Solution for 
+Electrokinetic Flow Around an Ion-Exchange Spherical Particle}
 
@@
 \author{Roman Zeyde \and Irad Yavneh}
-\address{Department of Computer Science, Technion -- Israel Institute of Technology, Haifa 32000, Israel}
-\email{romanz@cs.technion.ac.il \and irad@cs.technion.ac.il}
-
-% two authors have the same address
-%\author{Ory Schnitzer \and Ehud Yariv}
-%\address{Department of Mathematics, Technion -- Israel Institute of Technology, Haifa 32000, Israel}
-%\email{oschnitt@gmail.com \and udi@math.technion.ac.il}
-
-% communicated
-%\commby{Hilbert}
-
-% Received by the editors ?
-\date{DATE}
-
-% \subjclass[2000]{35R35, 49J40, 60G40}
-
-\abstract{
-A numerical solver for the simulation of electrokinetic 
-migration of particles in an electrolyte solution 
-due to the application of an external electric field is presented.
-The electrokinetic transport process is
-described by a system of partial differential equations (PDE).
-A boundary layer forms around the particle, whose scale disparity
-is used to derive nonlinear effective boundary conditions using 
-the specific chemical properties of the particle.
-The nonlinear system is discretized and an iterative Newton solver is constructed
-automatically from the discrete equations.
-An asymptotic analytical solution is derived for the validation of the solver. 
-The numerical results are obtained and are compared to the asymptotic solutions, 
-and good correspondence is achieved.}
-
-\keywords{CFD, electrokinetics, asymptotics}
 
@@
 electric forces, creating a double-layer structure around the
-particle (see Figure \ref{fig:EDL}). This structure, called
+particle. This structure, called
 ``Debye layer'', electrically screens the surface charge,
@@
 size, an analytical asymptotic solution for the Debye layer
-dynamics can be derived \cite{yariv2010asymptotic}.
-\begin{figure}[htbp]
-    \begin{center}
-        \includegraphics[width=0.35\textwidth]
-            {figs/debye.eps}
-        \caption{Schematic structure of the double layer:
-        (1) charged particle surface, (2) Debye layer, (3) fluid bulk.
-        If the particle surface has positive (black) surface charge,
-        it attracts negative (white) ions from the fluid making the
-        Debye layer negatively charged (as opposed to the rest of
-        the fluid bulk, which is electrically neutral).
-        The zeta potential is defined as the voltage drop across 
-        the Debye layer (2).}
-        \label{fig:EDL}
-    \end{center}
-\end{figure}
-% \begin{tikzpicture}\end{tikzpicture}
+dynamics can be derived \cite{yariv2010asymptotic},
+yielding ``effective'' boundary conditions near
+the particle surface for the ``outer'' bulk region equations.
 
 The variables of the electrokinetic flow equations are the electrostatic
-potential $\varphi$, fluid velocity $\bv$ and its pressure $p$, and
-ionic concentration $c$.
+potential $\varPhi$, fluid velocity $\bV$ and its pressure $P$, and
+ionic concentration $C$.
 The boundary conditions are determined by the specific
@@
 in general they have no analytic solution.
-Moreover, any numerical solver must handle the scale disparity caused by the
-Debye layer width being much smaller than the particle size. 
+
 A closed-form linear asymptotic solution has been developed for
 spherical particles and weak electric field in an
-axisymmetric setting \cite{yariv2010migration} but it is hard to extend this
-analytic solution to more general systems. Once the electric field
+axisymmetric setting \cite{yariv2010migration}. Once the electric field
 becomes stronger, significant nonlinear phenomena emerge.
 This interesting regime has not yet been explored extensively.
-Recently, it has been conceived that such type of dynamics
-can be very useful in transporting and manipulating micro-
-and nanoscale objects in many nanotechnology applications,
-nano-fluidic devices, packed bed separation, desalination processes and various 
-electrophoresis applications \cite{howse2007self,paxton2004catalytic,pumera2010electrochemically,nischang2007,leinweber2004}.
-Because the model for these electrokinetic
-phenomena has no closed-form analytic solution, a numerical
-solver for this system is of importance.
 
-The goal of this work is to develop and implement a software toolbox for the generation
-of iterative numerical solvers for nonlinear electrokinetic problems, and to apply it to the study
-of systems that have no closed-form solutions, such as ion-exchanger migration
-\cite{yariv2010migration} and the electrophoresis problem \cite{schnitzer2012surface}.
-This solver can be used to gain insight into the chemical and physical behavior 
+The goal of this work is to develop the next nonlinear terms
+in the asymptotic solution of the ion-exchanger migration.
+This solution can be used to gain insight into the chemical and physical behavior 
 in far more general regimes than are currently well-understood, 
-and also to possibly lead to further analytical developments, based on new scaling behavior
-discovered numerically. We may also target interesting physical
-phenomena that have been observed experimentally.
-One such phenomenon is nonlinear electrokinetic vortex flow, 
-which is useful for microfluidic mixing applications \cite{wang2004mix, ben2002vortex},
+and also for numerical solver results verification.
 
-The paper is structured as follows: the governing equations of the electrokinetic model
-are derived in Section \ref{sec:equations}. The algorithm for the discretization and 
-the solution of the system is described in Section \ref{sec:algorithm}.
-An analytical asymptotic solution for the non-linear system is derived 
-and presented in Section \ref{sec:asymp}.
-Numerical results and their comparison to an analytical asymptotic solution 
-are presented Section \ref{sec:results} and discussed in Section \ref{sec:discussion}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Governing Equations} \label{sec:equations}
-
-\subsection{Nondimensionalization}
-Spatial coordinates $\br$ are normalized by $a^*$ 
-(the characteristic size of the particle).
-Positive and negative ionic concentrations are denoted by $c_+$ and $c_-$, respectively, and
-are normalized by the ambient ionic concentration $c^*$. The ionic valences are $\pm z$.
-The dimensional ionic fluxes, $\bj_\pm$, are given by the Nernst-Plank equation 
-(using the Einstein relation for the electric mobility, $\mu_q^* = D^* / k_B^* T^*$, 
-where $D^*$ is the ionic diffusivity):
+The derivation is performed as follows. The governing differential equations are
+\begin{equation} \begin{array}{cccc}
+\bnabla \cdot \pars{ C \bnabla \varPhi } = 0, &
+\Laplacian C - \alpha \bV \cdot \bnabla C = 0, &
+\Laplacian \bV - \bnabla P + \bnabla \varPhi \Laplacian \varPhi = \bzero, &
+\bnabla \cdot \bV = 0.
+\end{array}\end{equation}
+The boundary conditions on the particle surface are
 \begin{equation}
-\bj^*_\pm = 
--D^* \bnabla c^*_\pm + \bv^* c^*_\pm \mp \frac{z e^* D^*}{k_B^* T^*} c^*_\pm \bnabla \varphi^*,
-\end{equation}
-
-The electric potential $\varphi$ is normalized by the thermal voltage:
-$\varphi^* = {k_B^* T^*}/{z e^*} = {R^* T^*}/{z F^*},$
-where $R^* = k_B^* N_A$, $F^* = e^* N_A$ is the Faraday number and $N_A$ is the Avogadro constant.
-
-The dimensional Stokes equations with electrostatic forces are given by:
-\begin{equation} \begin{array}{cc}
-\bnabla \cdot \bv = 0, &
--\bnabla p^* + \mu^* \bLaplacian \bv^* + \eps^* \Laplacian \varphi^* 
-\bnabla \varphi^* = 0.
+\begin{array}{cccc}
+0 = \varPhi + \log C, &
+0 = \deriv{}{n} \pars{\varPhi - \log C}, &
+\bV = \zeta \cdot \bnabla_\mathcal{S} \varPhi 
++ 2\log\pars{1-\tanh^2\frac{\zeta}{4}} \cdot \bnabla_\mathcal{S} \log C, &
+\zeta = \log \frac{C}{\gamma}
+\end{array}\end{equation}
+Far away from the particle, the boundary conditions are
+\begin{equation}\label{eq:bndcond_inf}\begin{array}{ccc}
+\bV \rightarrow -\cU \ui, &
+\bnabla \varPhi \rightarrow -\beta\ui, &
+ C \rightarrow 1.
 \end{array}\end{equation}
 
-The velocity $\bv$ is normalized by $v^* = {\eps^* (\varphi^*)^2}/{a^* \mu^*}$,
-and the pressure $p$ is normalized by $p^* = {\mu^* v^*}/{a^*} = {\eps^* (\varphi^*)^2}/{(a^*)^2}$.
-The fluxes $\bj^*_\pm$ are normalized by $j^* = {D^* c^*}/{a^*}$.
-
-The dimensional Poisson equation can be written as:
+The system can be written as $\cO(\bx;\beta) = \bzero$.
+For small $\beta$, the solution $\bx = [\varPhi; C; \bV; P]$ 
+to the nonlinear system can be expanded in a Taylor series in $\beta$:
 \begin{equation}
-(c^*_+ - c^*_-) z e^* = -\eps^* \Laplacian \varphi^*,
-\end{equation}
-
-After nondimensionalization, the Nernst-Plank, Stokes and Poisson equations read:
-\begin{equation} \label{eq:nernst}
-\bj_\pm = 
--\bnabla c_\pm + \alpha \bv c_\pm \mp c_\pm \bnabla \varphi,
-\end{equation}
-\begin{equation} \label{eq:stokes}
-\begin{array}{cc}
-\bnabla \cdot \bv = 0, &
--\bnabla p + \bLaplacian \bv + \Laplacian \varphi \bnabla \varphi = 0, 
-\end{array}
-\end{equation}
-\begin{equation} \label{eq:poisson}
-c_+ - c_- = -2\delta^2 \Laplacian \varphi,
-\end{equation}
-where $\delta = {\delta^*}/{a^*}$ is the dimensionless Debye thickness 
-($\delta^* = \sqrt{{\eps^* \varphi^*}/{2 c^* e^* z}}$) and 
-$\alpha = {v^* a^*}/{D^*} = {\eps^* (\varphi^*)^2}/{\mu^* D^*}$ 
-is the dimensionless Peclet number.
-The force on the particle is denoted by $\bF$ normalized by $\mu^* v^* a^* = \eps^* (\varphi^*)^2$.
-The stress tensor is denoted by $\tT$ and normalized by $p^* = \mu^* v^* / a^*$.
-The electric field is denoted by $\bE$ and normalized by $E^* = \varphi^* / a^*$.
-The surface charge is denoted by $\sigma$ and normalized by $\sigma^* = \eps^* \varphi^* / \delta^*$.
-
-The ionic fluxes are given by ion diffusion, electrostatic forces and ion advection by the fluid
-in \eqref{eq:nernst}. Due to conservation of ions' concentrations, the fluxes are divergence-free:
-\begin{equation*}
-\bnabla \cdot \bj_\pm = 0.
-\end{equation*}
-These equations may be re-written by using salt $c = (c_+ + c_-)/2$ and charge $q = (c_+ - c_-)/2$.
-Thus, salt and charge fluxes are defined by:
-\begin{equation}\label{eq:fluxes}\begin{array}{cc}
-  \bj = \frac{\bj_+ + \bj_-}{2} = -\bnabla c - q \bnabla \varphi + \alpha \bv c, & 
-  \bi = \frac{\bj_+ - \bj_-}{2} = -\bnabla q - c \bnabla \varphi + \alpha \bv q,
-\end{array}\end{equation}
-and are divergence-free as well:
-\begin{equation}\label{eq:zero_flux}\begin{array}{cc}
-\bnabla \cdot \bj = 0, & 
-\bnabla \cdot \bi = 0. 
-\end{array}\end{equation}
-In addition, the charge concentration is governed by the Poisson equation \eqref{eq:poisson}
-\begin{equation}
-q = -\delta^2 \Laplacian \varphi.
-\end{equation}
-
-\subsection{Boundary conditions}
-We assume that a constant electric field of nondimensional magnitude $\beta$,
-is applied to the system, in the direction denoted by the unit vector $\ui$.
-As a result, the particle will equilibrate at 
-a non-zero steady-state velocity $\cU \ui$, which is
-a function of the applied field, and is not known a priori.
-
-We employ the reference frame of the particle.
-Far away from the particle, we have a uniform applied electrostatic field, uniform flow,
-and ambient ionic concentrations:
-\begin{equation}\label{eq:bndcond_inf}\begin{array}{ccc}
-\bv \rightarrow -\cU \ui, &
-\bnabla \varphi \rightarrow -\beta\ui, &
- c_\pm \rightarrow 1.
-\end{array}\end{equation}
-
-We consider a spherical particle.
-The chemical properties of the particle's surface $\mathcal{S}$ (defined at $r=1$ 
-with normal $\bn = \brhat$), determine the boundary conditions on $\mathcal{S}$.
-We consider the following scenarios:
-\subsubsection{Ion-exchanger \cite{yariv2010migration}}
-We assume high conductance of the particle (yielding a uniform electric potential),
-zero slip, anion impermeability, cation selectivity 
-(with fast Butler-Volmer\cite{bard2000book} kinetics
-$\bn \cdot \bj_+ = k (1 - c_+/\gamma)$, where $k \rightarrow \infty$):
-\begin{equation}
-\begin{array}{cccc}
-\varphi = \cV, &
-\bv = \bzero, &
-\bn \cdot \bj_- = 0, &
-c_+ = \gamma,
-\end{array}
-\end{equation}
-where $\gamma$ is the ratio between the cationic concentration on the surface and the cationic
-concentration in the fluid bulk and $\cV$ is an unknown constant electric potential at
-the ion-exchanger surface.
-
-\subsubsection{Inert particle \cite{schnitzer2012surface}}
-We assume constant surface charge
-zero slip and ion impermeability:
-\begin{equation}
-\begin{array}{cccc}
-\bn \cdot (\bnabla \varphi - \chi \bnabla \varphi_s) = \delta^{-1} \sigma, &
-\bv = \bzero, &
-\bn \cdot \bj_\pm = 0,
-\end{array}
-\end{equation}
-where $\chi$ is the ratio between the dielectric constants of the 
-particle and the fluid.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Separation of scales}
-When $\delta \ll 1$, 
-the fluid remains electroneutral ($q \approx 0$, thus $c_+ \approx c_-$), 
-except a thin boundary layer of width $O(\delta)$ 
-surrounding the particle (the ``Debye layer'').
-This boundary layer makes it very hard to construct 
-a direct numerical solver for the full electro-kinetic problem.
-However, we exploit the scale disparity at the Debye layer, 
-which allows the PDE system to be rewritten in the ``inner'' region 
-as an ODE system using the asymptotic limit of $\delta \rightarrow 0$.
-This system can be integrated and solved analytically,
-yielding ``effective'' boundary conditions near
-the particle surface for the ``outer'' bulk region equations.
-
-\subsubsection  {Bulk-scale equations}
-The Nernst-Planck equations above \eqref{eq:fluxes} for the fluid bulk outside
-the boundary layer, using bulk variables denoted by uppercase letters, read:
-\begin{equation} \begin{array}{cccc} \label{eq:bulk_flux}
-  Q = 0, &
-  C = C_+ = C_-, &
-\bJ = -\bnabla C + \alpha \bV C, &
-\bI = -C \bnabla \varPhi.
-\end{array}\end{equation}
-Because the flow is incompressible ($\bnabla \cdot V = 0$), 
-ion conservation results in the following 
-salt and charge conservation equations -- the salt and charge fluxes above 
-\eqref{eq:bulk_flux} are divergence-free
-\eqref{eq:zero_flux}:
-\begin{equation} \begin{array}{ccc}
-\label{eq:salt_charge}
-\Laplacian C - \alpha \bV \cdot \bnabla C = 0, &
-\bnabla \cdot \pars{ C \bnabla \varPhi } = 0.
-\end{array}\end{equation}
-The macroscale Stokes flow equations have the same form as before \eqref{eq:stokes}:
-\begin{equation}
-\begin{array}{ccc}
-\bnabla \cdot \bV = 0, &   
-\Laplacian \bV - \bnabla P + \bnabla \varPhi \Laplacian \varPhi = \bzero.
-\end{array}
-\end{equation}
-
-\subsection{Bulk-scale effective boundary conditions}
-By integrating the equations across the Debye layer,
-the effective boundary conditions at the particle surface are:
-\subsubsection{Ion-exchanger} See \cite{yariv2010migration} for full derivation:
-\begin{equation}
-\begin{array}{ccc}
-\label{eq:ionex_bnd}
-0 = \varPhi + \log C, &
-0 = \deriv{}{n} \pars{\varPhi - \log C}, &
-\bV = 
-\zeta \cdot \bnabla_\mathcal{S} \varPhi 
-+ 2\log\pars{1-\tanh^2\frac{\zeta}{4}} \cdot \bnabla_\mathcal{S} \log C,
-\end{array}\end{equation}
-where $\zeta = \cV - \varPhi = \log (C / \gamma)$ 
-is the zeta potential.
-
-\subsubsection{Highly charged inert particle}
-See \cite{schnitzer2012surface} for full derivation:
-\begin{equation} \label{eq:ephor_bnd}
-\begin{array}{ccc}
-0 = {\deriv{C}{n} - \text{Du} \nabla^2_s \pars{\varPhi - \log C}}, & 
-0 = {\deriv{C}{n} + C \deriv{\varPhi}{n}}, &
-\bV = \zeta \cdot \bnabla_\mathcal{S} \pars{\varPhi - \log C} +
-4 \log 2 \cdot \bnabla_\mathcal{S} \log C,
-\end{array}\end{equation}
-where $\zeta = \bar{\zeta} - \log C$ 
-is the zeta potential and $\bar{\zeta} = 2 \log \sigma$.
-
-\subsection{Steady state}
-The stress tensor in the fluid is composed of Newtonian and Maxwel stresses:
-\begin{equation}
-\label{eq:tensor}
-\tT = \bnabla \bV + (\bnabla \bV)^\dagger - P \tI
-+ \bnabla \varPhi \bnabla \varPhi - \frac{1}{2} (\bnabla \varPhi \cdot \bnabla \varPhi). 
-\end{equation} 
-In steady state (constant particle drift velocity $\cU$), the total force acting on the particle 
-(computed by the following surface integral) must vanish:
-\begin{equation} \label{eq:zero_force}
- \bF(\beta, \cU) = \oint_\mathcal{S} \tT \cdot \bnhat dA = \bzero.
-\end{equation}
-
-The total force $\bF(\beta, \cU)$ is a function of the applied electric field $\beta$ and
-the velocity $\cU$.
-For any given electric field $\beta$, the force-free constraint above 
-can be solved numerically for $\cU$ to yield the corresponding steady-state velocity.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Algorithm Description} \label{sec:algorithm}
-The numerical solver first requires constructing a discrete 
-approximation for the nonlinear PDE system,
-for a given electric field $\beta$ and assumed velocity $\cU$. 
-The resulting nonlinear discrete system is
-solved numerically using Newton's Method, so the total force on the
-particle can be computed. 
-We seek the steady-state velocity $\cU$, 
-which corresponds to zero total force, $F(\beta, \cU) = 0$,
-which we solve by the standard secant method.
-
-\subsection{Spherical Coordinates}
-Because the system is axisymmetric, we employ
-spherical coordinates $(r,\theta,\phi)$.
-The scalar gradient and the divergence can be written as:
-\begin{eqnarray}
-\bnabla f = \deriv{f}{r}\brhat + \frac{1}{r}\deriv{f}{\theta}\bthetahat, &
-\bnabla \cdot \bF = \frac{1}{r^2}\deriv{}{r}\pars{F_r r^2 } + 
-               \frac{1}{r \sin\theta}\deriv{}{\theta}\pars{F_\theta \sin\theta}.
-\end{eqnarray}
-The scalar Laplacian can be written as:
-\begin{eqnarray}
-\Laplacian f = \bnabla \cdot (\bnabla f) = 
- \frac{1}{r^2}\deriv{}{r}\pars{r^2 \deriv{f}{r}} + 
- \frac{1}{r^2 \sin\theta}\deriv{}{\theta}\pars{\sin\theta \deriv{f}{\theta}}.
-\end{eqnarray}
-The vector gradient and vector Laplacian can be written as:
-\begin{eqnarray}
-\bnabla \bF &=& \deriv{F_r}{r} \brhat \brhat + \deriv{F_\theta}{r} \brhat \bthetahat + 
-\frac{1}{r}\pars{\deriv{F_r}{\theta} - F_\theta} \bthetahat \brhat + 
-\frac{1}{r}\pars{\deriv{F_\theta}{\theta} + F_r} \bthetahat \bthetahat, \\
-\bLaplacian \bF &=& 
-\left(\Laplacian F_r - \frac{2F_r}{r^2} - 
-\frac{2}{r^2 \sin\theta} \deriv{\left(F_\theta \sin\theta \right)}{\theta}\right)\brhat
-+ \left(\Laplacian F_\theta - \frac{F_\theta}{r^2 \sin^2\theta} + 
-\frac{2}{r^2}\deriv{F_r}{\theta}\right) \bthetahat.
-\end{eqnarray}
-
-Note that in the spherical coordinate system,
-the vector Laplacian operator cannot be computed in a decoupled manner as in the Cartesian system,
-since the unit vectors $\brhat, \bthetahat, \bphihat$ are functions of the coordinates
-in a curvilinear coordinate system.
-
-\subsection{Computational Grid}
-A regular grid of size $n_r \times n_\theta$ is defined, with:
-\begin{eqnarray} \label{eq:grid}
-(r_i,\theta_j) \in [1, \infty) \times [0,\pi], & 
-r_i = (1+\Delta_r)^i, &
- \theta_j = \Delta_\theta \cdot j,
-\end{eqnarray}
-where a logarithmic grid spacing has been chosen for $r$ and a uniform grid for $\theta$.
-Note that $r_0 = 1$ and $R_{max} = (1+\Delta_r)^{n_r}$, where
-$\Delta_r = \pars{R_{max}} ^ {1/n_r} - 1$ and $\Delta_\theta = {\pi/n_\theta}$.
-Because the grid is finite, the choice 
-$R_{max}$ must be taken large enough so as to have a negligible effect
-on the solution.
-This grid induces a disjoint subdivision of the domain 
-$\Omega = [1, R_{max}] \times [0,\pi] = \bigcup_{ij}\Omega_{ij}$ into cells.
-A specific cell $\Omega_{ij}$ and its center $(\bar{r}_i, \bar{\theta}_j)$ are defined by \eqref{eq:grid}:
-\begin{eqnarray}
-\Omega_{ij} = [r_{i-1}, r_{i}] \times [\theta_{j-1}, \theta_{j}], &
-\bar{r}_i = (r_{i-1} + r_{i})/2, &
-\bar{\theta}_j = (\theta_{j-1} + \theta_{j})/2.
-\end{eqnarray}
-
-Each discrete variable is located with respect of its cell as follows:
-$\varPhi$, $C$ and $P$ are represented by their value at the center of each cell, 
-using an all-centered grid, whereas $\bV$ is represented by its values at cell 
-boundaries, using a staggered grid:
-\begin{equation}
-\begin{array}{ccccc}
-\varPhi^h_{[i,j]} = \varPhi(\bar{r}_i, \bar{\theta}_j), &
-C^h_{[i,j]} = C(\bar{r}_i, \bar{\theta}_j), &
-P^h_{[i,j]} = P(\bar{r}_i, \bar{\theta}_j). &
-V_r^h{}_{[i,j]} = V_r(r_i, \bar{\theta}_j), &
-V_\theta^h{}_{[i,j]} = V_\theta(\bar{r}_i, {\theta}_j).
-\end{array}
-\end{equation}
-
-\subsection{Operator Discretization} 
-A finite-volume method with linear interpolation is used for flux discretization. 
-Define the following discrete central difference operators:
-\begin{eqnarray} \label{eq:disc_diff}
-\cD_r(f^h){}_{\left[i+\half,j\right]} = \frac{f^h_{\left[i+1,j\right]} - f^h_{\left[i,j\right]}}
-                       {r_{\left[i+1,j\right]} - r_{\left[i,j\right]}}, &
-\cD_\theta(f^h){}_{\left[i,j+\half\right]} = \frac{f^h_{\left[i,j+1\right]} - f^h_{\left[i,j\right]}}
-					   {\theta_{\left[i,j+1\right]} - \theta_{\left[i,j\right]}}.
-\end{eqnarray}
-
-Define the following linear interpolation operators:
-\begin{eqnarray} \label{eq:disc_interp}
-\begin{array}{rcl}
-\cI_r(f^h)_{\left[i+\half,j\right]} &=& 
-\frac{r_{\left[i+\half,j\right]} - r_{\left[i,j\right]}}
-{r_{\left[i+1,j\right]} - r_{\left[i,j\right]}} 
-f^h_{\left[i+1,j\right]} 
-+ 
-\frac{r_{\left[i+1,j\right]} - r_{\left[i+\half,j\right]}}
-{r_{\left[i+1,j\right]} - r_{\left[i,j\right]}}
-f^h_{\left[i,j\right]},
-\\
-\cI_\theta(f^h)_{\left[i,j+\half\right]} &=& 
-\frac{r_{\left[i,j+\half\right]} - r_{\left[i,j\right]}}
-{r_{\left[i,j+1\right]} - r_{\left[i,j\right]}}
-  f^h_{\left[i,j+1\right]} + 
-\frac{ r_{\left[i,j+1\right]} - r_{\left[i,j+\half\right]}}
-{r_{\left[i,j+1\right]} - r_{\left[i,j\right]}}
-  f^h_{\left[i,j\right]}.
-\end{array}
-\end{eqnarray}
-
-If the total flux of a cell is equal to zero ($\bnabla \cdot \boldsymbol{f} = 0$), 
-then using \eqref{eq:disc_diff}, we have
-\begin{eqnarray}
-\frac{1}{r^2} \cD_r\pars{f^h_r r^2} + 
-\frac{1}{r \sin\theta} \cD_\theta\pars{f^h_\theta \sin\theta} =
-\frac{\cD_r\pars{f^h_r \cdot r^2 \sin\theta} + 
-\cD_\theta\pars{f^h_\theta \cdot r \sin\theta}}{r^2 \sin\theta} = 0. 
-\end{eqnarray}
-
-\subsection{System Equations} \label{sec:disc_equations}
-Charge and salt fluxes \eqref{eq:bulk_flux} are discretized on grid cell boundaries 
-(using an upwind scheme $\mathcal{U}$ for numerical stability at large cell Peclet number)  
-using \eqref{eq:disc_diff} and \eqref{eq:disc_interp}:
-\begin{eqnarray} \nonumber
-I^h_r = -\cI_r(C^h) \cdot \cD_r(\varPhi^h), &
-I^h_\theta = -\cI_\theta(C^h) \cdot \frac{\cD_\theta(\varPhi^h)}{r}, \\
-J^h_r = -\cD_r(C^h) + \alpha V^h_r \cdot \mathcal{U}^{\bV^h}_r (C^h), &
-J^h_\theta = -\frac{\cD_\theta(C^h)}{r} + \alpha V^h_\theta \cdot \mathcal{U}^{\bV^h}_\theta (C^h), 
-\\ \nonumber
- \mathcal{U}^{\bV^h}_r(C^h)[i,j] = C^h\left[i-\frac{\sign(V^h_r)}{2}, j\right], &
- \mathcal{U}^{\bV^h}_\theta(C^h)[i,j] = C^h\left[i, j-\frac{\sign(V^h_\theta)}{2}\right]. 
-\end{eqnarray}
-
-Mass flux $\bV$ is discretized on grid cells boundaries, 
-using the staggered velocity grid.
-
-Force components ($\bF = -\bnabla P + \bLaplacian \bV + \bnabla \varPhi \Laplacian \varPhi$) 
-are discretized on the staggered velocity grid, where
-linear interpolation is used for the Coulomb force and for vector Laplacian components.
-\begin{eqnarray}
-\nonumber
-F^h_r &=& -\cD_r(P^h) 
-          + \cL(V^h_r) - \frac{2}{r^2} V^h_r 
-		  - \frac{2}{r^2 \sin\theta} \cI_r(\cD_\theta (V^h_\theta \sin\theta))
-          + \cD_r(\varPhi^h) \cdot \cI_r(\cL(\varPhi^h)), \\
-F^h_\theta &=& -\frac{\cD_\theta(P^h)}{r} 
-		  + \cL(V^h_\theta) - \frac{F^h_\theta}{r^2 \sin^2\theta} 
-		  + \frac{2}{r^2} \cI_\theta(\cD_\theta(F^h_r))
-		  + \frac{\cD_\theta(\varPhi^h)}{r} \cdot \cI_\theta(\cL(\varPhi^h)), \\
-\nonumber
-\cL(f^h) &=& \frac{1}{r^2}\cD_r\pars{\cD_r(f^h) r^2} + 
-\frac{1}{r^2 \sin\theta} \cD_\theta\pars{\cD_\theta(f^h) \cdot \sin\theta}.
-\end{eqnarray}
-
-\subsection{Boundary Conditions} \label{sec:disc_boundary}
-In order to discretize boundary condtions for $\varPhi$, $C$ and $\bV$, 
-``ghost'' points are employed. 
-The grid is extended to include points outside the domain interior,
-and the variables at the ``ghost'' points are set to satisfy 
-the discretized boundary conditions, following the analysis below.
-Note that $P$ has no boundary conditions -- so the pressure variable is defined 
-only in the domain interior.
-
-Far away from the particle boundary \eqref{eq:bndcond_inf}, we have:
-\begin{equation}
-\begin{array}{cccc}
-\cD_r \pars{\varPhi^h} = -\beta \cos\bar{\theta}, &
-\cI_r \pars{C^h} = 1 &
-V_r^h = -\cU \cos\theta, &
-V_\theta^h = \cU \sin\theta.
-\end{array}\end{equation}
-
-For $\theta = 0$ and $\theta = \pi$, the ``ghost'' points are defined by axial 
-symmetry considerations:
-\begin{equation} 
-\begin{array}{cccc}
-\cD_\theta \pars{\varPhi^h} = 0, &
-\cD_\theta \pars{C^h} = 0, &
-\cD_\theta \pars{V_r^h} = 0, &
-V_\theta^h = 0
-\end{array}
-\end{equation}
-
-The specific boundary conditions at $r=1$
-depend on the chemical properties of particle surface.
-
-\subsubsection{Ion-exchanger} The boundary conditions \eqref{eq:ionex_bnd} 
-are implemented by:
-\begin{equation}
-\begin{array}{rcl}
-0 &=& \cI_r(\varPhi^h + \log C^h), \\
-0 &=& \cD_r(\varPhi^h - \log C^h), \\
-V^h_r &=& 0, \\
-V^h_\theta &=& 4\log\pars{\frac{1}{2}\pars{1 + \exp\left\{\cI_\theta(\zeta^h)/2\right\}}} \cdot 
-			\cD_\theta(\zeta^h), \\
-  \zeta^h &=& - \log \gamma - \cI_r(\varPhi^h).
-\end{array}
-\end{equation}
-
-\subsubsection{Highly charged inert particle} The boundary conditions \eqref{eq:ephor_bnd} 
-are implemented by:
-\begin{equation}
-\begin{array}{rcl}
-0 &=& \cD_r(C^h) - \text{Du} \cdot 
-\pars{\cD_\theta \pars{\sin\theta \cdot \cD_\theta \cI_r\pars{\varPhi^h - \log C}}}/{\sin\theta}, \\
-0 &=& \cD_r(C^h) + \cI_r(C^h) \cD_r(\varPhi^h), \\
-V^h_r &=& 0, \\
-V^h_\theta &=& \cI_\theta(\zeta^h) \cdot \cD_\theta(\cI_r \varPhi^h - \log \cI_r C^h) + 
-4 \log 2 \cdot \cD_\theta(\log \cI_r C^h), \\
-  \zeta^h &=& \bar{\zeta} - \log \cI_r C.
-\end{array}
-\end{equation}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Solver Design}
-An operator $\cO$ is defined by its input vector $\bx$ and its output 
-$\by = \cO(\bx)$.
-In order to solve the equation $\cO(\bx) = \bzero$, Newton's method is applied, 
-given an initial solution $\bx_0$.
-Each step requires the computation of the residual vector, $\br = \cO(\bx)$, and
-the gradient matrix of the operator, $\bG = \bnabla \cO(\bx)$, 
-given the current solution $\bx$.
-Then, a sparse linear system needs to be solved to yield the update for the 
-increment $\Delta \bx = -\bG^{-1} \br$.
-When the method converges, $\bx_n \rightarrow \bx_\infty$, 
-the asymptotic convergence is in general quadratic:
-\begin{equation}
-\|\bx_{n+1} - \bx_\infty\| \le k \|\bx_{n} - \bx_\infty\|^2.
-\end{equation}
-Thus, when the initial guess is close enough to the solution, the solver
-will typically converge in very few steps.
-
-\subsubsection{Operator Representation}
-System variable $\bx$ is defined as the concatenation $\bx = [\,\varPhi, C, V_r, V_\theta, P\,]$.
-Thus, each problem variable can be computed by applying an appropriate projection operator on $\bx$.
-The system can be written as a nonlinear operator $\cO(\bx) = \bzero$ 
-acting on the system variable ${\bx}$, 
-where $\cO$ is the system equations operator, 
-derived by concatenation of the system equations (described at Subsection \ref{sec:disc_equations})
-and the boundary conditions operators (described at Subsection \ref{sec:disc_boundary}).
-This way, the same numerical solver handles both the nonlinear system equation and nonlinear
-boundary conditions.
-
-\subsubsection{Steady-state}
-Let $\beta$ be a given nondimensional electric field.
-Assume that $\cU \ui$ is the drift velocity of the particle 
-(given that the fluid is at rest far away from it).
-After the convergence of the solver, once the residual norm is below
-a prescribed threshold $\|\cO(\bx_n)\| < \epsilon$, 
-the total force acting on the particle  
-can be computed by integrating $\tT \cdot \bn$ over the particle surface.
-
-Due to symmetry considerations, the total force $\bF$ is 
-aligned with $\ui$ and it vanishes iff $\ui \cdot \bF = 0$.
-\begin{eqnarray} \nonumber
-F_\imath = \ui \cdot \bF &=& 
-\oint_\mathcal{S} \pars{\ui \cdot \tT \cdot \bnhat} dA = 
-\int_0^\pi f_\imath(\theta) 2\pi \sin\theta d\theta ,
-\\  
-f_\imath = \ui \cdot \tT \cdot \brhat &=& \pars{-P + 2\cD_r(V_r) + 
-\frac{1}{2}\pars{\cD_r(\varPhi)}^2 - \frac{1}{2r^2}\pars{\cD_\theta(\varPhi)}^2}\cos\theta 
-\\  \nonumber
-&& -\pars{\cD_r(V_\theta) - \frac{V_\theta}{r}
-+ \frac{1}{r}\cD_r(\varPhi) \cD_{\theta}(\varPhi)}\sin\theta.
-\end{eqnarray}
-
-The integral above is approximated by 1D numerical quadrature
-(using the mid-point rule)
-\begin{equation}
-F_\imath^h(\beta, \cU^h) = \sum_{i=1}^{n_\theta} f^h(\bar\theta_i) \cdot 
-              2 \pi \sin\bar\theta_i \cdot \Delta\theta_i,
-\end{equation}
-to yield the total force $F_\imath^h(\beta, \cU^h)$ as a function of the drift velocity $\cU^h$.
-Since the goal is to find the steady-state solution, $F_\imath^h$ 
-is required to be zero --
-and the appropriate $\cU^h$ is found by a simple 1D root-finding algorithm,
-applied as an outer loop:
-\begin{equation} \label{eq:disc_zero_force}
-F_\imath^h(\beta, \cU^h(\beta)) = 0
-\end{equation}
-
-\subsubsection{Continuation}
-
-The iterative solver above can in principle be used 
-to compute the steady-state solution for any given $\beta$.
-For $\beta \ll 1$, the linear terms are the dominant ones, 
-so the solution is approximately linear in $\beta$ 
-(as derived in \cite{yariv2010migration}), and the solver convergence is fast.
-However, this is no longer true for $\beta \sim O(1)$, because the nonlinear terms become dominant
-and the iterative solver may not converge at all if we start with an arbitrary initial guess.
-In order to find a solution for such $\beta$, a continuation method is used:
-the solver is applied to a sequence of $\{\beta_i\}_{i=0}^n$ such that $\beta_0 = 0$,
-$\beta_n = \beta$ and the solution $\bx_i$ for $\beta_i$ is used as the solver initializer
-for the problem of $\beta_{i+1}$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Solver Implementation}
-
-Object-Oriented Design methodology is used for implementation.
-The MATLAB programming language is chosen due to strong numerical capabilities
-and high-level language features.
-The source code of the solver is provided in \cite{source}.
-
-\subsubsection{Operator Interface}
-The base \verb|Operator| interface is defined by 
-supporting the computation of a residual vector \verb|Operator::res()|
-and a gradient matrix \verb|Operator::grad()|, given an input vector $\bx$.
-This interface is implemented by specific operators classes,
-which are used to construct the system operator $\cO$, so that 
-the Newton solver (that requires computing the residual and the gradient) 
-can be applied automatically.
-Each such operator may have other operators as its inputs, so the residual
-and the gradient are computed recursively, using the chain rule (applied to operators).
-
-\paragraph{\textit{Linear operator}}
-If $\cO$ is linear, it can be represented by a matrix $L$, such that:
-\begin{equation}\begin{array}{cc}
-\cO(\bx) = L \bx, &
-\bnabla\cO = L. 
-\end{array}\end{equation}
-Note that finite difference $\cD$, interpolation $\cI$ and 
-upwind selection $\mathcal{U}$ operators
-can be implemented as linear sparse operators, by constructing 
-an appropriate sparse matrix $L$, having $O(\dim \bx)$ non-zeroes).
-This way, the computation of the residual is very fast, taking $O(\dim \bx)$ time,
-and the gradient is computed only once.
-
-\paragraph{\textit{Pointwise scalar function}}
-Let $f: \R \rightarrow \R$ be a differentiable 1D function, whose derivative is
-denoted by $f': \R \rightarrow \R$. The operator $\cF$ can be defined to
-represent pointwise application of $f$:
-\begin{equation}\begin{array}{cc}
-\cF(\bx) = [f(x_1); \ldots; f(x_n)], &
-\bnabla\cF(\bx) = \diag\{f'(x_1), \ldots, f'(x_n)\}.
-\end{array}\end{equation}
-$f$ is defined and differentiated automatically using the MATLAB symbolic toolbox.
-
-\paragraph{\textit{Constant value}}
-A constant operator $\mathcal{C}$ is defined by constant vector $\bc$ 
-(that does not depend on $\bx$):
-\begin{equation}\begin{array}{cc}
-\mathcal{C}(\bx) = \bc, &
-\bnabla\mathcal{C} = \bzero.
-\end{array}\end{equation}
-
-\paragraph{\textit{Binary operators}}
-Let $\cO_1$ and $\cO_2$ be two operators, so their pointwise addition, subtraction,
-and multiplication, are defined as follows:
-\begin{equation}\begin{array}{cc}
-(\cO_1 \pm \cO_2)(\bx) = \cO_1(\bx) \pm \cO_2(\bx), &
-\bnabla (\cO_1 \pm \cO_2)(\bx) = \bnabla\cO_1(\bx) \pm \bnabla\cO_2(\bx),
-\end{array}\end{equation}
-\begin{equation}\begin{array}{cc}
-(\cO_1 \cdot \cO_2)(\bx) = \cO_1(\bx) \cdot \cO_2(\bx), &
-\bnabla (\cO_1 \cdot \cO_2)(\bx) = \diag(\cO_2(\bx)) \bnabla\cO_1(\bx) 
-                                  + \diag(\cO_1(\bx)) \bnabla\cO_2(\bx).
-\end{array}\end{equation}
-\paragraph{\textit{N-ary operators}}
-Given $N$ operators $\{\cO_i\}_{i=1}^N$, their concatenation $\cO$ is defined as:
-\begin{equation}\begin{array}{cc}
-\cO(\bx) = [\cO_1(\bx); \ldots; \cO_N(\bx)], &
-(\bnabla\cO)(\bx) = [(\bnabla\cO_1)(\bx); \ldots; (\bnabla\cO_N)(\bx)].
-\end{array}\end{equation}
-
-\subsubsection{Iterative Newton solver}
-Given an initial solution $\bx_0$ and prescribed values for $\beta$ and $\cU$, 
-we apply the following algorithm 
-until convergence ($\|\boldsymbol{r_n}\| < \eps$):
-\begin{enumerate}
-\item Update the system operator: $\verb|op| = \verb|System|(\bx_{n})$
-\item Compute the gradient: $\boldsymbol{G}_n = \verb|op.grad()|$
-\item Compute the right-hand side: $\boldsymbol{r}_n = \verb|op.res()|$
-\item Solve sparse linear system: $\boldsymbol{G}_n \Delta \bx_n = -\boldsymbol{r}_n$
-\item Update solution: $\bx_{n+1} = \bx_{n} + \Delta \bx_{n}$
-\end{enumerate}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Asymptotic Analysis} \label{sec:asymp}
-In order to validate the numerical results, an asymptotic analysis is applied 
-to the nonlinear systems of ion-exchanger migration 
-and highly charged particle electrophoresis.
-We present here the asymptotic analysis for the ion-exchanger case \cite{yariv2010migration}
-and the asymptotic analysis for the electrophoresis case \cite{schnitzer2012surface}
-appears in \cite{schnitzer2012cubic}.
-
-The derivation is performed as follows.
-The nonlinear system (composed of the governing equations and the boundary conditions) 
-is written as $\cO(\bx;\beta) = \bzero$.
-For small $\beta$, the solution to the nonlinear system can be expanded in a Taylor series in $\beta$:
-\begin{equation}
-\bx = \bx(\beta) \approx \sum_n \bx_n \beta^n.
+\bx(\beta) \approx \sum_n \bx_n \beta^n.
 \end{equation}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{First-Order (linear in $\beta$) Solution} \label{app:linear}
+\section{First-Order (linear in $\beta$) Solution} \label{app:linear}
 
 For $\beta = 0$ (no electric field is applied), the steady-state solution is $\cU = 0$:
-\begin{eqnarray*}\begin{array}{cccc}
+\begin{equation}\begin{array}{cccc}
 \varPhi_0(r,\theta) = 0, &
@@
 \bLaplacian \bV_1 - \bnabla P_1 = \bzero.
-\end{eqnarray*}
+\end{array}\end{equation}
 
-The first-order terms are given by (see \cite{yariv2010migration} for full derivation):
+The first-order terms $\bx_1$ are given by (see \cite{yariv2010migration} for full derivation):
 \begin{equation} \begin{array}{ccccc}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Third-Order (cubic in $\beta$) Solution} \label{app:cubic}
+\section{Second-Order (quadratic in $\beta$) Solution} \label{app:quadratic}
+The quadratic terms $\bx_2$ are computed by solving a linear PDE system 
+with a right-hand side determined by the linear terms $\bx_1$:
+\begin{equation}
+\varPhi_2 = \pars{\frac{\cU_1\, \alpha}{32} - \frac{1}{16}}
+\frac{3\, {\cos^2\theta} - 1}{r^3} - \frac{3 + 3\, {\sin^2\theta}\, \left(4\, r^3 - 1\right)}{32\, r^4} - \frac{3\, \cU_1\, \alpha - 6}{32\, r},
+\end{equation}
+\begin{equation}
+C_2 = \left(\frac{5\, \cU_1\, \alpha}{32} + \frac{1}{16}\right)
+\frac{3\, {\cos^2\theta} - 1}{r^3} - \frac{3\, \cU_1\, \alpha - 6}{32\, r} + \frac{3\, \cU_1\, \alpha\, \left(2\, r^3\, {\sin^2\theta} + {\sin^2\theta} - 1\right)}{16\, r^4},
+\end{equation}
+\begin{equation}
+\Psi_2 = \pars{\frac{9}{16(\sqrt{\gamma}+1)} - \frac{3}{16} \cU_1 (\cU_1 \alpha + 1)}
+ \left(\frac{1}{r^2} - 1\right) \sin^2\theta \cos\theta.
+\end{equation}
+Note that the quadratic term does not contribute to the total force and staedy-state 
+velocity terms, but it does change the fluid flow, 
+the electric potential and the ionic concentration.
+
+\section{Third-Order (cubic in $\beta$) Solution} \label{app:cubic}
 Note that, due to symmetry considerations, $\cU(\beta)$ is an anti-symmetric function.
@@
 \end{equation}
-In order to find the cubic terms, the quadratic terms must be computed first.
-The quadratic terms $\bx_2$ are computed by solving a linear PDE system 
-with a right-hand side determined by the linear terms $\bx_1$.
-Note that the quadratic term does not contribute to the total force and steady-state 
-velocity terms, but it does change the fluid flow, 
-the electric potential and the ionic concentration.
 The cubic terms $\bx_3$ are computed by solving a linear PDE system 
 with a right-hand side determined by the linear terms $\bx_1$ and the quadratic terms $\bx_2$.
+\begin{align}
+\varPhi_3 &= \frac{15\cU_1\alpha + 6 }{64}\cos\theta  - \frac{3 \cU_1\alpha}{32} {\cos}^3\theta
+ + \frac{183 {\cU_1}^2\alpha^2 - 839 \cU_1\alpha - 470}{2560 r^2} \cos\theta 
+\\ \nonumber &
++ \frac{3 \cos\theta \left(5 \cU_1\alpha - 6 {\cos^2\theta} - 4 \cU_1\alpha {\cos^2\theta} + 4\right)}{64 r^3} + \frac{\left(2 \cU_1\alpha - 1\right) \left(\cos\theta - 3 {\cos}^3\theta\right)}{64 r^5}
++ {{\cos}^3\theta \left(\frac{15 \cU_1\alpha}{64} + \frac{3}{32}\right)}{r^{-2}} 
+\\ \nonumber &
+- \left(3 \cos\theta - 5 {\cos}^3\theta\right) \left( - \frac{19 {\cU_1}^2\alpha^2}{5120} + \frac{97 \cU_1\alpha}{5120} + \frac{3 \cU_2\alpha}{320} + \frac{21}{1280}\right){r^{-4}} 
+% \\ \nonumber &
++ {{\cos}^3\theta \left(\frac{\cU_1\alpha}{64} + \frac{3}{64}\right)}{r^{-6}},
+\end{align}
+\begin{align}
+C_3 &=
+\frac{3 {{\cU_1}}^2\alpha^2 {\cos^3\theta}}{32} + \frac{\cos\theta \left(797 {{\cU_1}}^2\alpha^2 + 419 {\cU_1}\alpha - 512 {\cU_2}\alpha + 174\right)}{2560 r^2} 
+- \frac{3 {\cU_1}\alpha \cos\theta \left(5 {\cU_1}\alpha + 2\right)}{64} 
+\\ \nonumber &
+- {\left(3 \cos\theta - 5 {\cos^3\theta}\right) \left(\frac{59 {{\cU_1}}^2\alpha^2}{5120} + \frac{103 {\cU_1}\alpha}{5120} + \frac{69 {\cU_2}\alpha}{320} + \frac{3}{1280}\right)}{r^{-4}} 
++ \frac{\alpha \left(\cos\theta - 3 {\cos^3\theta}\right) \left(5\alpha {{\cU_1}}^2 + 2 {\cU_1} + 16 {\cU_2}\right)}{128 r^5} 
+\\ \nonumber &
+- \frac{3\alpha \cos\theta \left( - 8\alpha {{\cU_1}}^2 {\cos^2\theta} + 7\alpha {{\cU_1}}^2 + 2 {\cU_1} + 32 {\cU_2} {\cos^2\theta} - 32 {\cU_2}\right)}{128 r^3} 
+%\\ \nonumber &
++ \frac{{{\cU_1}}^2\alpha^2 {\cos^3\theta}}{32 r^6} - \frac{3 {\cU_1}\alpha {\cos^3\theta} \left(5 {\cU_1}\alpha + 2\right)}{64 r^2},
+\end{align}
+\begin{align}
+\Psi_3 &=
+r^2 {\sin^2\theta} \left(\frac{{\cW_2}}{15} - \frac{{\cW_1}}{3} + \frac{209}{3360}\right) 
+ - {{\sin^2\theta} \left(\frac{5 {\cW_2}}{3} - \frac{{\cW_1}}{3} + \frac{35}{264}\right)}{r^{-1}}
++ \frac{{\sin^4\theta} \left(2 {\cW_2} + \frac{761}{5632}\right)}{r} 
+\\ \nonumber & 
+- \frac{{\sin^2\theta} \left(1848 r^6 {\sin^2\theta} - 2079 r^3 {\sin^2\theta} + 924 r^3 - 7 {\sin^2\theta} + 10\right)}{19712 r^5} 
+%\\ \nonumber & 
+\frac{4 {\sin^2\theta} - 5 {\sin^4\theta}}{r^3} + \left(\frac{{\cU_1}\alpha}{16} - \frac{1}{8}\right) \frac{2 r^3 - 3 r^2 + 1}{4 r} {\sin^2\theta},
+\end{align}
+\begin{align}
+\cW_1 &= \frac{69}{512 \left(\sqrt{\gamma} + 1\right)} - \frac{1407\alpha^2 {\log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}^3}{1280} - \frac{123 \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{1280} - \frac{27}{512 {\left(\sqrt{\gamma} + 1\right)}^2}
+-\frac{1899\alpha {\log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}^2}{2560} 
+\\ \nonumber & 
+- \frac{\alpha \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right) \left(\frac{81}{16 \left(\sqrt{\gamma} + 1\right)} - \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right) \left(\frac{27\alpha \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{4} + \frac{27}{8}\right)\right)}{320}
++ \frac{21\alpha \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{128 \left(\sqrt{\gamma} + 1\right)},
+\end{align}
+\begin{align}
+\cW_2 &= \frac{9 \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{256} 
++ \frac{21\alpha^2 {\log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}^3 + 
+15\alpha {\log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}^2}{64} 
+- \frac{27}{512 {\left(\sqrt{\gamma} + 1\right)}^2}
+%\\ \nonumber &
+- \frac{297\alpha \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right) + 54}{1024 \left(\sqrt{\gamma} + 1\right)}.
+\end{align}
+
 The cubic solution satisfies the ${r\rightarrow\infty}$ boundary conditions, 
 when $\alpha\cU_1 = 0$.
-
-In the case of ion-exchanger migration,
-the cubic correction \cite{zeyde2012report} velocity terms (for $\alpha = 0$)
-turn out to be:
-\begin{equation}
-\cU_3(\gamma) = \frac{31}{320(\sqrt\gamma + 1)} - \frac{9}{320(\sqrt\gamma + 1)^2} + \frac{1}{1680} - \frac{11}{160} \log \pars{\frac{1 + \gamma^{-\frac{1}{2}}}{2}}.
-\end{equation}
-
-The cubic term becomes dominant for small $\beta$ when $\gamma \approx 1$.
-Note that, for $\gamma = 1$, the linear term vanishes and the cubic term 
-of the velocity is $\cU(\beta) = \frac{1129}{26880}\beta^3$.
-
-Note that a $\cU = 0$ solution may exist for a critical $\beta_c > 0$ and $\alpha = 0$, 
-if it satisfies:
-\begin{equation} \label{eq:crit_beta}
-\beta_c^2 = -\frac{\cU_1(\gamma)}{\cU_3(\gamma)}.
-\end{equation}
-Specifically, for $\gamma = 1 + \eps$, where $0 < \eps \ll 1$, $\beta_c = O\pars{\sqrt{\eps}}$:
-\begin{equation}
-\beta_c \approx \sqrt{-{\cU_1'(1) \eps}/{\cU_3(1)}} = 
- \sqrt{{13440 \eps}/{1129}} \approx 3.45 \sqrt{\eps}.
-\end{equation}
-That is, there may be a specific nonzero external field for which the particle remains at rest. The physical viability of this solution has yet to be explored.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Numerical Results} \label{sec:results}
-The numerical solver is applied to the nonlinear problem of an ion-exchanger migration 
-driven by an electric field \cite{yariv2010migration}
-and the electrophoresis of highly charged surface inert particle 
-\cite{schnitzer2012surface}. 
-The solver is applied to a series of values of the electric field $\beta$, ranging 
-from $\beta \ll 1$ to $\beta \sim O(1)$.
-For each $\beta$ value, the steady-state velocity $\cU(\beta)$ is computed. 
-The resulting $\cU(\beta)$ is plotted on a log-log scale, so that the asymptotic behaviour
-of the solution may be examined for a wide range of $\beta$ values.
-
-In order to validate the numerical solver, we employ 
-the results of the asymptotic analysis of the nonlinear 
-system \cite{zeyde2012report, schnitzer2012cubic}. 
-The numerical results are compared 
-to the asymptotic solutions, and good correspondence is achieved.
-
-\subsection{Ion-exchanger results}
-For $\beta \ll 1$, the linear regime is dominant \eqref{eq:linear_velocity}.
-When $\gamma \approx 1$, the cubic regime, where $\cU = O(\beta^3)$, 
-dominates the linear one, even for weak electric fields. 
-This phenomenon is confirmed both by the numerical
-results and by asymptotic expansion of the nonlinear system (for $\alpha=0$).
-The switch from the linear regime to the cubic regime occurs at a critical electric
-field value $\beta_c = O(\sqrt{|\gamma - 1|})$.
-The numerical results $\cU^h$, 
-as well as the analytical ones \eqref{eq:cubic}, are given in Figure \ref{fig:IonExCubic}.
-
-The linear solution for $\gamma \approx 1$, 
-yields a sign change of the zeta potential $\zeta = \log (C/\gamma)$, when
-$|\log\gamma| \approx 3\beta / 4$. This results in a sign change in the slip velocity,
-which can be approximated for small $|\zeta| \ll 1$ as $V_\theta \approx \zeta \cdot \bnabla_S \varPhi$.
-This sign change creates a vortex at the downstream end of the ion-exchanger, 
-as demonstrated by the numerical solution and the asymptotic analysis results 
-in Figure \ref{fig:Vortex}.
-
-\subsection{Electrophoresis results}
-In this scenario the linear regime is dominant \eqref{eq:linear_velocity}.
-In order to verify the solver, the numerical steady-state velocity is compared to the
-analytical solution \cite{schnitzer2012cubic}. Since the cubic correction is much smaller than
-the linear solution for $\beta \ll 1$, the difference between numerical results and
-the linear solution is compared to the cubic correction term.
-
-Since the leading order of the solution $\cU(\beta)$ is linear for $\beta \ll 1$, 
-the numerical discretization error is $O(\beta)$ as well.
-In order to reduce the discretization error of the numerical solution \eqref{eq:disc_zero_force}
-and after verifying that the discretization error converges as $O(h^2)$,
-we employ Richardson extrapolation to $\cU^h$ and $\cU^{2h}$:
-\begin{equation}
-\hat\cU = \frac{4}{3} \cU^h - \frac{1}{3} \cU^{2h}.
-\end{equation}
-The results of the extrapolation and $\hat\cU$ the analytical results 
-are given at Figure \ref{fig:Electrophoresis}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-\section{Discussion} \label{sec:discussion}
-A numerical solver for nonlinear electrokinetic transport system is described.
-The numerical results exhibit a good correspondence to the asymptotic linear model as
-shown above.
-Moreover, two interesting phenomena (cubic regime and downstream vortex) were predicted
-using the numerical results, and were verified using asymptotic expansion of the
-nonlinear system.
-Future work may include replacing the full Newton step by an iterative linear solver, so 
-finer grids could be used.
-Since it is expected that a boundary layer should form around the particle for $\beta \gg 1$,
-a numerical solver should be able to handle large grids to achieve good numeric accuracy.
-
-\begin{figure}[htbp]
-    \begin{center}
-    \includegraphics[width=0.4\textwidth]{figs/Cubic/ionex_cubic1.eps}
-    \includegraphics[width=0.4\textwidth]{figs/Cubic/ionex_cubic2.eps}
-        \caption{Steady-state velocity $\cU$ as a function of the 
-        electric field magnitude $\beta$, for $\gamma < 1$ (left) and $\gamma > 1$ (right). 
-        The analytic cubic solution \eqref{eq:cubic} is represented by curves
-        (solid for $\cU > 0$, dashed for $\cU < 0$), 
-        and the numerical results are represented by markers 
-        (circles for $\cU > 0$, squares for $\cU < 0$). Note that linear and
-        cubic regimes match well the numerical results, including the critical $\beta$ 
-        behaviour \eqref{eq:crit_beta}.
-        }
-	    \label{fig:IonExCubic}
-    \end{center}
-\end{figure}
-
-\begin{figure}[htbp]
-    \begin{center}
-    \includegraphics[width=0.4\textwidth]{figs/Electrophoresis/numerical_vs_analytical_alpha=0.5_Du=1.0_zeta=10.0_Rmax=100.eps}
-    \includegraphics[width=0.4\textwidth]{figs/Electrophoresis/departure_from_linear_alpha=0.5_Du=1.0_zeta=10.0_Rmax=100.eps}
-        \caption{Steady-state velocity $\cU$ as a function of the 
-        electric field magnitude $\beta$, for highly-charged surface particle
-        electrophoresis (with $\alpha = 0.5, \text{Du} = 1, \bar\zeta = 10$).
-        The analytic solution velocity is represented by solid lines, 
-        and the numerical results are represented by markers.
-        The left figure shows the full numerical solution 
-        compared to the analytical one \eqref{eq:cubic}, and
-        the right figure compares the analytic cubic correction \cite{schnitzer2012cubic} 
-        to the difference between the numerical results and the linear regime.
-        When $\beta$ is large, the analytical cubic solution loses its validity 
-        because higher-order terms become significant.}
-	    \label{fig:Electrophoresis}
-    \end{center}
-\end{figure}
-
-\begin{figure}[htbp]
-    \begin{center}
-	\includegraphics[width=0.45\textwidth]{figs/Stream/N0.01.eps}
-	\includegraphics[width=0.45\textwidth]{figs/Stream/A0.01.eps}
-	\includegraphics[width=0.45\textwidth]{figs/Stream/N0.04.eps}
-	\includegraphics[width=0.45\textwidth]{figs/Stream/A0.04.eps}
-	\includegraphics[width=0.45\textwidth]{figs/Stream/N0.08.eps}
-	\includegraphics[width=0.45\textwidth]{figs/Stream/A0.08.eps}
-        \caption{Streamlines of the flow for various electric field $\beta$ values: 
-        numerical results (left) and analytical approximation (right) for 
-        $\gamma = 0.99$.  The steady-state velocity $\cU$ is positive, so the
-        ion-exchanger drifts to the right. 
-        }
-    \label{fig:Vortex}
-    \end{center}
-\end{figure}
-
-% put your thanks here
-%\section*{Acknowledgments}
 

### 2012-09-21 notes/work/cubic_report.tex
Add abstract and validation

@@
 \maketitle
+
+\begin{abstract}
+An asymptotic nonlinear solution of electrokinetic 
+migration of ion-exchange particles in an electrolyte solution 
+due to the application of an external electric field is presented.
+The electrokinetic transport process is
+described by a system of nonlinear partial differential equations (PDE).
+An asymptotic analytical solution is 
+derived and validated. 
+\end{abstract}
 
@@
 
+\section{Validation}
+The derivation above is validated using MATLAB symbolic toolbox by the code 
+at \verb|symbolic/asymp.m| \cite{source}.
+
 \bibliographystyle{unsrt}

### 2012-09-21 notes/work/ijnam.tex
Acknowledgements.
Add cubic report
Add quadratic and cubic terms.

@@
 % Received by the editors ?
-\date{DATE}
+%\date{DATE}
 
@@
 given the previous solutions for $\bx_0, \ldots, \bx_{k-1}$.
+The derivation is validated using MATLAB symbolic toolbox by the code 
+at \verb|symbolic/asymp.m| \cite{source}.
 
@@
 
-The first-order terms are given by (see \cite{yariv2010migration} for full derivation):
+The first-order terms $\bx_1$ are given by (see \cite{yariv2010migration} for full derivation):
 \begin{equation} \begin{array}{ccccc}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Second-Order (quadratic in $\beta$) Solution} \label{app:quadratic}
+The quadratic terms $\bx_2$ are computed by solving a linear PDE system 
+with a right-hand side determined by the linear terms $\bx_1$:
+\begin{equation}
+\varPhi_2 = \pars{\frac{\cU_1\, \alpha}{32} - \frac{1}{16}}
+\frac{3\, {\cos^2\theta} - 1}{r^3} - \frac{3 + 3\, {\sin^2\theta}\, \left(4\, r^3 - 1\right)}{32\, r^4} - \frac{3\, \cU_1\, \alpha - 6}{32\, r},
+\end{equation}
+\begin{equation}
+C_2 = \left(\frac{5\, \cU_1\, \alpha}{32} + \frac{1}{16}\right)
+\frac{3\, {\cos^2\theta} - 1}{r^3} - \frac{3\, \cU_1\, \alpha - 6}{32\, r} + \frac{3\, \cU_1\, \alpha\, \left(2\, r^3\, {\sin^2\theta} + {\sin^2\theta} - 1\right)}{16\, r^4},
+\end{equation}
+\begin{equation}
+\Psi_2 = \pars{\frac{9}{16(\sqrt{\gamma}+1)} - \frac{3}{16} \cU_1 (\cU_1 \alpha + 1)}
+ \left(\frac{1}{r^2} - 1\right) \sin^2\theta \cos\theta.
+\end{equation}
+Note that the quadratic term does not contribute to the total force and staedy-state 
+velocity terms, but it does change the fluid flow, 
+the electric potential and the ionic concentration.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Third-Order (cubic in $\beta$) Solution} \label{app:cubic}
@@
 with a right-hand side determined by the linear terms $\bx_1$ and the quadratic terms $\bx_2$.
+
+\begin{align}
+\varPhi_3 &= \frac{15\cU_1\alpha + 6 }{64}\cos\theta  - \frac{3 \cU_1\alpha}{32} {\cos}^3\theta
+ + \frac{183 {\cU_1}^2\alpha^2 - 839 \cU_1\alpha - 470}{2560 r^2} \cos\theta 
+\\ \nonumber &
++ \frac{3 \cos\theta \left(5 \cU_1\alpha - 6 {\cos^2\theta} - 4 \cU_1\alpha {\cos^2\theta} + 4\right)}{64 r^3} + \frac{\left(2 \cU_1\alpha - 1\right) \left(\cos\theta - 3 {\cos}^3\theta\right)}{64 r^5}
++ {{\cos}^3\theta \left(\frac{15 \cU_1\alpha}{64} + \frac{3}{32}\right)}{r^{-2}} 
+\\ \nonumber &
+- \left(3 \cos\theta - 5 {\cos}^3\theta\right) \left( - \frac{19 {\cU_1}^2\alpha^2}{5120} + \frac{97 \cU_1\alpha}{5120} + \frac{3 \cU_2\alpha}{320} + \frac{21}{1280}\right){r^{-4}} 
+% \\ \nonumber &
++ {{\cos}^3\theta \left(\frac{\cU_1\alpha}{64} + \frac{3}{64}\right)}{r^{-6}},
+\end{align}
+\begin{align}
+C_3 &=
+\frac{3 {{\cU_1}}^2\alpha^2 {\cos^3\theta}}{32} + \frac{\cos\theta \left(797 {{\cU_1}}^2\alpha^2 + 419 {\cU_1}\alpha - 512 {\cU_2}\alpha + 174\right)}{2560 r^2} 
+- \frac{3 {\cU_1}\alpha \cos\theta \left(5 {\cU_1}\alpha + 2\right)}{64} 
+\\ \nonumber &
+- {\left(3 \cos\theta - 5 {\cos^3\theta}\right) \left(\frac{59 {{\cU_1}}^2\alpha^2}{5120} + \frac{103 {\cU_1}\alpha}{5120} + \frac{69 {\cU_2}\alpha}{320} + \frac{3}{1280}\right)}{r^{-4}} 
++ \frac{\alpha \left(\cos\theta - 3 {\cos^3\theta}\right) \left(5\alpha {{\cU_1}}^2 + 2 {\cU_1} + 16 {\cU_2}\right)}{128 r^5} 
+\\ \nonumber &
+- \frac{3\alpha \cos\theta \left( - 8\alpha {{\cU_1}}^2 {\cos^2\theta} + 7\alpha {{\cU_1}}^2 + 2 {\cU_1} + 32 {\cU_2} {\cos^2\theta} - 32 {\cU_2}\right)}{128 r^3} 
+%\\ \nonumber &
++ \frac{{{\cU_1}}^2\alpha^2 {\cos^3\theta}}{32 r^6} - \frac{3 {\cU_1}\alpha {\cos^3\theta} \left(5 {\cU_1}\alpha + 2\right)}{64 r^2},
+\end{align}
+\begin{align}
+\Psi_3 &=
+r^2 {\sin^2\theta} \left(\frac{{\cW_2}}{15} - \frac{{\cW_1}}{3} + \frac{209}{3360}\right) 
+ - {{\sin^2\theta} \left(\frac{5 {\cW_2}}{3} - \frac{{\cW_1}}{3} + \frac{35}{264}\right)}{r^{-1}}
++ \frac{{\sin^4\theta} \left(2 {\cW_2} + \frac{761}{5632}\right)}{r} 
+\\ \nonumber & 
+- \frac{{\sin^2\theta} \left(1848 r^6 {\sin^2\theta} - 2079 r^3 {\sin^2\theta} + 924 r^3 - 7 {\sin^2\theta} + 10\right)}{19712 r^5} 
+%\\ \nonumber & 
+\frac{4 {\sin^2\theta} - 5 {\sin^4\theta}}{r^3} + \left(\frac{{\cU_1}\alpha}{16} - \frac{1}{8}\right) \frac{2 r^3 - 3 r^2 + 1}{4 r} {\sin^2\theta},
+\end{align}
+\begin{align}
+\cW_1 &= \frac{69}{512 \left(\sqrt{\gamma} + 1\right)} - \frac{1407\alpha^2 {\log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}^3}{1280} - \frac{123 \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{1280} - \frac{27}{512 {\left(\sqrt{\gamma} + 1\right)}^2}
+-\frac{1899\alpha {\log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}^2}{2560} 
+\\ \nonumber & 
+- \frac{\alpha \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right) \left(\frac{81}{16 \left(\sqrt{\gamma} + 1\right)} - \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right) \left(\frac{27\alpha \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{4} + \frac{27}{8}\right)\right)}{320}
++ \frac{21\alpha \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{128 \left(\sqrt{\gamma} + 1\right)},
+\end{align}
+\begin{align}
+\cW_2 &= \frac{9 \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{256} 
++ \frac{21\alpha^2 {\log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}^3 + 
+15\alpha {\log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}^2}{64} 
+- \frac{27}{512 {\left(\sqrt{\gamma} + 1\right)}^2}
+%\\ \nonumber &
+- \frac{297\alpha \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right) + 54}{1024 \left(\sqrt{\gamma} + 1\right)}.
+\end{align}
+
 The cubic solution satisfies the ${r\rightarrow\infty}$ boundary conditions, 
@@
 
-% put your thanks here
-%\section*{Acknowledgments}
+\section*{Acknowledgments}
+The authors thank Prof. Ehud Yariv and Ory Schnitzer 
+for introducing us to this problem, 
+for the helpful discussions and valuable advice.
 

### 2012-09-22 notes/ijnam/ijnam.tex
Fix Irad review.

--- 2012-09-21 notes/work/ijnam.tex
@@
 
-\subsubsection{Singularity Handling} \label{sec:singular}
+\subsubsection{Handling the Singularity} \label{sec:singular}
 The electric potential $\varPhi$ (in electrophoresis case) and the pressure $P$ (in both cases) 
@@
 
-Assuming $\beta \ll 1$, the linearized equations and boundary conditions are:
+Assuming $\beta \ll 1$, the linearized equations and boundary conditions are
 \begin{equation} \begin{array}{ccc}
@@
 
-The first-order terms $\bx_1$ are given by (see \cite{yariv2010migration} for full derivation):
-\begin{equation} \begin{array}{ccccc}
-\varPhi = \beta \pars{\frac{1}{4r^2} - r}\cos\theta, &
-C = 1 + \beta \frac{3}{4r^2} \cos\theta, &
-\Psi = \beta \cU_1 \pars{\frac{1}{r} - r^2} \frac{\sin^2\theta}{2}, &
-P = 0, &
-\bF = \bzero,
+The first-order terms $\bx_1$ are given by (see \cite{yariv2010migration} for full derivation)
+\begin{equation} \begin{array}{cccc}
+\varPhi_1 = \pars{\frac{1}{4r^2} - r}\cos\theta, &
+C_1 = \frac{3}{4r^2} \cos\theta, &
+\Psi_1 = \cU_1 \pars{\frac{1}{r} - r^2} \frac{\sin^2\theta}{2}, &
+P_1 = 0,
 \end{array} \end{equation}
@@
 The quadratic terms $\bx_2$ are computed by solving a linear PDE system 
-with a right-hand side determined by the linear terms $\bx_1$:
+with a right-hand side determined by the linear terms $\bx_1$, yielding
 \begin{equation}
@@
 \end{equation}
-Note that the quadratic term does not contribute to the total force and staedy-state 
+Note that the quadratic term does not contribute to the total force and steady-state 
 velocity terms, but it does change the fluid flow, 
@@
 \end{equation}
-In order to find the cubic terms, the quadratic terms must be computed first.
-The quadratic terms $\bx_2$ are computed by solving a linear PDE system 
-with a right-hand side determined by the linear terms $\bx_1$.
-Note that the quadratic term does not contribute to the total force and steady-state 
-velocity terms, but it does change the fluid flow, 
-the electric potential and the ionic concentration.
+
 The cubic terms $\bx_3$ are computed by solving a linear PDE system 
@@
  - {{\sin^2\theta} \left(\frac{5 {\cW_2}}{3} - \frac{{\cW_1}}{3} + \frac{35}{264}\right)}{r^{-1}}
-+ \frac{{\sin^4\theta} \left(2 {\cW_2} + \frac{761}{5632}\right)}{r} 
+ + {{\sin^4\theta} \left(2 {\cW_2} + \frac{761}{5632}\right)}{r^{-1}} 
 \\ \nonumber & 

### 2012-09-22 notes/ijnam/ijnam.tex
Remove report citations.

@@
 
-In the case of ion-exchanger migration,
-the cubic correction \cite{zeyde2012report} velocity terms (for $\alpha = 0$)
+The cubic correction velocity terms (for $\alpha = 0$)
 turn out to be:
@@
 the results of the asymptotic analysis of the nonlinear 
-system \cite{schnitzer2012cubic, zeyde2012report}. 
+system. 
 The numerical results are compared 

### 2012-09-22 notes/ijnam/ijnam.tex
Fix Irad review.

@@
 
-Note that a $\cU = 0$ solution may exist for a critical $\beta_c > 0$ and $\alpha = 0$, 
+Observe that a $\cU = 0$ solution may exist for a critical $\beta_c > 0$ and $\alpha = 0$, 
 if it satisfies:
@@
 	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/A_0.9000_0.1000.eps}
+	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/N_0.9000_0.1995.eps}
+	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/A_0.9000_0.1995.eps}
 	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/N_0.9000_0.3981.eps}
 	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/A_0.9000_0.3981.eps}
-	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/N_0.9000_1.0000.eps}
-	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/A_0.9000_1.0000.eps}
         \caption{Streamlines of the flow for various electric field $\beta$ values: 
         numerical results (left) and analytical approximation (right) for
-        $\gamma = 0.99$.  The steady-state velocity $\cU$ is positive, so the
+        $\gamma = 0.9$.  The steady-state velocity $\cU$ is positive, so the
         ion-exchanger drifts to the right. 
@@
         results and the analytical solution for $\beta < 1$, validating
-        the vortex formation. For $\beta \ge 1$, the cubic analytical
-        solution does not match the numerical results, due
-        to the influence of higher order nonlinear terms in the  solution.
+        the vortex formation.
         }

### 2012-10-05 notes/ijnam/ijnam-style/ijnam.tex
IJNAM

\documentclass[10pt]{ijnam}
\hsize=5.5 true in
\textheight=8.4 true in
\topmargin 1in

%% information for the editor
\def\currentvolume{1}
\def\currentissue{1}
\def\currentyear{2004}
\def\month{March}
\pagespan{1}{18}
\copyrightinfo{2004}{} % copyright year

%% please put your definitions into mydef.sty. Examples can be found in this
%% file.

%\usepackage{mydef}

%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%

\title[Sample for how to use ijnam.cls]
{Enter the title of your paper here\\
  If it is too long, you can use \\
  to break it into several lines}

% author and address
\author[Short Name]{Full Name}
\address{
  Department of Mathematics,
  University of Newland,
  Newland, NL 88888, USA
}
\email{hyang@louisiana.edu}
\urladdr{http://www.ucs.lousiana.edu/$\sim$hxy6615/}

% two authors have the same address
\author[S. Name 1\and S. Name 2]{Full Name 1 \and Full Name 2}
\address{
  Department of Mathematics,
  University of Newland,
  Newland, NL 88888, USA
}
\email{yang@louisiana.edu \and hong@louisiana.edu}
\urladdr{http://www.ucs.lousiana.edu/$\sim$hxy6615/ \and
  http://www.ucs.lousiana.edu/$\sim$hxy6615/}

% dedication
\dedicatory{This paper is dedicated to our authors}

% communicated
\commby{Hilbert}

% Received by the editors ?
\date{January 1, 2004 and, in revised form, March 22, 2004.}

% it is suggested to put it in Acknowledgments
\thanks{This research was supported by ???}

\subjclass[2000]{35R35, 49J40, 60G40}

\abstract{This paper is a sample prepared to illustrate the use of
ijnam.cls. You can use all commands of amsart.cls.}

\keywords{point, line, plane, and space.}

\maketitle

\section{First section}
This is the first section.

\section{Second section}

This is the second section.

\subsection{This section has two subsections}

This is the first subsection of the second section.

\subsection{The second subsection}

This is the first subsection of the second section.
\begin{equation}
c=a+b.
\end{equation}
This equation can rewritten as:
\begin{equation}\label{eq2}
a=c-b.
\end{equation}

\subsubsection{The second subsection has two subsubsections}

This is the first subsubsection of the second subsection.

\subsubsection{The second subsubsection}

This is the second subsubsection of the second subsection.

For $b=1$, $c=4$, we get from (\ref{eq2})
\begin{equation}
a=3.
\end{equation}

%%%%%%%%%%%%%%%%%%%%%%%
\section{Forth section}
%%%%%%%%%%%%%%%%%%%%%%%

This is the forth section.

%%%%%%%%%%%%%%%%%%%%%%%
\section{Third section}
%%%%%%%%%%%%%%%%%%%%%%%

This is the last section.

% put your thanks here
\section*{Acknowledgments}
The author thanks the anonymous authors whose work largely
constitutes this sample file. This research was supported by ???.

\begin{thebibliography}{99}

\bibitem{frie} Friedman, Avner,
Partial Differential Equations of Parabolic Type , Robert E. Krieger
Publishing Company, Malabar, Florida, 1983.

\bibitem {glow} Glowinski, R., Lions, J.~L. and Tr\'{e}moli\`{e}res, R.,
Numerical Analysis of Variational Inequalities, Norh-Holland Publishing
Company, 1981.

\bibitem{lsu} Ladyzenskaya, O.A., Solonnikov, V.A. and Uralceva, N.N.,
Linear and Quasi-linear Equations of Parabolic Type, AMS, 1988.

\bibitem{lions} Lions, J.L. and Magenes, E.,
Non-Homogeneous Boundary Value Problems and Applications I-II,
Springer-Verlag, New York, 1972.

\end{thebibliography}

\end{document}

### 2012-10-13 notes/thesis/ijnam.tex
Add thesis LaTeX.

--- 2012-09-22 notes/ijnam/ijnam.tex
@@
-\documentclass[10pt]{ijnam}
-\hsize=5.5 true in
-\textheight=8.4 true in
-\topmargin 1in
-
-%% information for the editor
-\def\currentvolume{1}
-\def\currentissue{1}
-\def\currentyear{2004}
-\def\month{October}
-\pagespan{1}{18}
-\copyrightinfo{2012}{} % copyright year
-
-%% please put your definitions into mydef.sty. Examples can be found in this
-%% file.
+\documentclass[11pt,reqno]{article}
+
 \usepackage{graphicx}
@@
 
-%\usepackage{mydef}
+\title{Asymptotic and Numerical Solution for Electrokinetic Flow Around a Spherical Particle}
+\author{Roman Zeyde \\ \\  {Advisor: Prof. Irad Yavneh} } \date{}
 
@@
 
-\title{Asymptotic and Numerical Solution for Electrokinetic Flow Around a Spherical Particle}
-
-% author and address
-\author{Roman Zeyde \and Irad Yavneh}
-\address{Department of Computer Science, Technion -- Israel Institute of Technology, Haifa 32000, Israel}
-\email{romanz@cs.technion.ac.il \and irad@cs.technion.ac.il}
-
-% two authors have the same address
-%\author{Ory Schnitzer \and Ehud Yariv}
-%\address{Department of Mathematics, Technion -- Israel Institute of Technology, Haifa 32000, Israel}
-%\email{oschnitt@gmail.com \and udi@math.technion.ac.il}
-
-% communicated
-%\commby{Hilbert}
-
-% Received by the editors ?
-%\date{DATE}
-
-% \subjclass[2000]{35R35, 49J40, 60G40}
+\maketitle
 
@@
 are compared to the asymptotic solutions, and good correspondence is achieved.}
-
-\keywords{CFD, electrokinetics, asymptotics, ion-exchanger, electrophoresis}
-
-\maketitle
 
@@
 	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/A_0.9000_0.1000.eps}
-	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/N_0.9000_0.1995.eps}
-	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/A_0.9000_0.1995.eps}
-	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/N_0.9000_0.3981.eps}
-	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/A_0.9000_0.3981.eps}
+	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/N_0.9000_0.2000.eps}
+	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/A_0.9000_0.2000.eps}
+	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/N_0.9000_0.4000.eps}
+	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/A_0.9000_0.4000.eps}
+	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/N_0.9000_0.6000.eps}
+	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/A_0.9000_0.6000.eps}
         \caption{Streamlines of the flow for various electric field $\beta$ values: 
@@
 
+\appendix
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Slip Condition} \label{append:slip}
+
+\subsection{Electric Potential}
+The leading-order electric potential in the Debye layer:
+\begin{eqnarray}  
+\deriv{^2 \varphi}{\rho^2} = -q = -\frac{c_+ - c_-}{2} = 
+-C\frac{\exp\left[+(\varPhi - \varphi)\right] - \exp\left[-(\varPhi - \varphi)\right]}{2} = 
+C \sinh(\varphi - \varPhi).
+\end{eqnarray}
+Denote $\psi = \varphi - \varPhi$, so that $\psi(0) = \cV - \varPhi = \zeta$ and 
+$\psi(\rho\rightarrow\infty) = 0$:
+\begin{eqnarray}  
+\deriv{^2 \psi}{\rho^2} &=& C \sinh(\psi) = 2 C \sinh{\frac{\psi}{2}}\cosh{\frac{\psi}{2}} ,
+\\
+2\deriv{\psi}{\rho} \deriv{^2 \psi}{\rho^2} &=& 
+4 C \sinh{\frac{\psi}{2}}\cosh{\frac{\psi}{2}} \deriv{\psi}{\rho} ,
+\\
+\deriv{}{\rho} \pars{\deriv{\psi}{\rho}}^2 &=& 
+\deriv{}{\rho} \pars{2 \sqrt{C} \sinh{\frac{\psi}{2}}}^2 .
+\end{eqnarray}
+
+Integrating with respect to boundary condtions yields:
+\begin{eqnarray}  
+\deriv{\psi}{\rho} &=& -2\sqrt{C}\sinh\frac{\psi}{2}, \\  
+\pars{4\sinh\frac{\psi}{4}\cosh\frac{\psi}{4}}^{-1}\deriv{\psi}{\rho} &=& -\sqrt{C}, \\  
+\frac{\pars{\tanh\frac{\psi}{4}}^{-1}}{4\cosh^2\frac{\psi}{4}}
+\deriv{\psi}{\rho} &=& -\sqrt{C}, \\  
+\deriv{}{\rho}\pars{\log\tanh\frac{\psi}{4}} &=& \deriv{}{\rho}\pars{-\rho \sqrt{C}} .
+\end{eqnarray}
+
+Integrating with respect to boundary condtions yields:
+\begin{eqnarray}
+\log\tanh\frac{\psi}{4} - \log\tanh\frac{\zeta}{4} &=& -\rho \sqrt{C}, \\
+\psi = \varphi - \varPhi &=& 
+4 \tanh^{-1}\pars{\tanh{\frac{\zeta}{4}} \cdot \exp\pars{-\rho \sqrt{C}}}.
+\end{eqnarray}
+
+\subsection{Radial Momentum}
+Leading-order $O(\delta^{-3})$ radial momentum balance in the Debye layer yields:
+\begin{eqnarray} 
+- \deriv{p}{\rho} + \deriv{\varphi}{\rho} \deriv{^2\varphi}{\rho^2} &=& 0.
+\end{eqnarray}
+One integration yields:
+\begin{eqnarray} 
+p &=& \frac{1}{2}\pars{\deriv{\varphi}{\rho}}^2 = \frac{1}{2}\pars{\deriv{\psi}{\rho}}^2.
+\end{eqnarray}
+
+\subsection{Tangential Momentum}
+Leading-order $O(\delta^{-2})$ tangential momentum balance in the Debye layer yields:
+\begin{eqnarray} 
+0 &=& \deriv{^2 v_\theta}{\rho^2} - \deriv{p}{\theta} 
+ + \deriv{\varphi}{\theta} \deriv{^2\varphi}{\rho^2} ,
+\\
+\deriv{^2 v_\theta}{\rho^2} &=& \frac{1}{2}\deriv{}{\theta}\pars{\deriv{\psi}{\rho}}^2
+- \deriv{(\psi + \varPhi)}{\theta} \deriv{^2\psi}{\rho^2}  
+\\
+ &=& \deriv{}{\theta}\pars{2C \sinh^2\frac{\psi}{2}}
+- \deriv{\psi}{\theta} C \sinh\psi
+- \deriv{\varPhi}{\theta} \deriv{^2\psi}{\rho^2}  
+\\
+ &=& \deriv{}{\theta}\pars{C \pars{\cosh\psi - 1}}
+- C \sinh\psi \deriv{\psi}{\theta}
+- \deriv{\varPhi}{\theta} \deriv{^2\psi}{\rho^2}  
+\\
+ &=& \deriv{C}{\theta} \pars{\cosh\psi - 1}
+- \deriv{\varPhi}{\theta} \deriv{^2\psi}{\rho^2}  
+ = \deriv{C}{\theta} \pars{2 \sinh^2 \frac{\psi}{2}}
+- \deriv{\varPhi}{\theta} \deriv{^2\psi}{\rho^2}  
+\\
+ &=& -\deriv{C}{\theta} \frac{2}{\sqrt{C}} \pars{\half \sinh \frac{\psi}{2} \deriv{\psi}{\rho}}
+- \deriv{\varPhi}{\theta} \deriv{^2\psi}{\rho^2}  
+ = -\deriv{C}{\theta} \frac{2}{\sqrt{C}} \deriv{}{\rho}\pars{\cosh \frac{\psi}{2}}
+- \deriv{\varPhi}{\theta} \deriv{^2\psi}{\rho^2}  .
+\end{eqnarray}
+By integrating from specific $\rho$ to $\rho \rightarrow \infty$ (where $\psi = 0$):
+\begin{eqnarray}
+\deriv{v_\theta}{\rho} &=& -\deriv{C}{\theta} \frac{2}{\sqrt{C}} 
+\pars{\cosh \frac{\psi}{2} - 1} - \deriv{\varPhi}{\theta} \deriv{\psi}{\rho}   
+= -\deriv{C}{\theta} \frac{4}{\sqrt{C}} \sinh^2 \frac{\psi}{4} 
+  - \deriv{\varPhi}{\theta} \deriv{\psi}{\rho}   .
+\end{eqnarray}
+Note that:
+\begin{eqnarray}
+\deriv{\psi}{\rho} &=& -2\sqrt{C}\sinh\frac{\psi}{2} = 
+                       -4\sqrt{C}\sinh\frac{\psi}{4}\cosh\frac{\psi}{4},
+\\
+-4\sinh\frac{\psi}{4} &=& \frac{1}{\sqrt{C} \cosh\frac{\psi}{4}} \deriv{\psi}{\rho}.
+\end{eqnarray}
+Thus:
+\begin{eqnarray}
+\deriv{v_\theta}{\rho} &=& 
+  \pars{\deriv{C}{\theta} \frac{1}{C}} \cdot
+  \pars{\frac{\sinh\frac{\psi}{4}}{\cosh\frac{\psi}{4}} \deriv{\psi}{\rho}}
+  - \deriv{\varPhi}{\theta} \deriv{\psi}{\rho}
+=  4\deriv{}{\rho} \pars{\log\cosh\frac{\psi}{4}} \deriv{}{\theta} \log C
+  - \deriv{\psi}{\rho} \deriv{\varPhi}{\theta},
+\\
+\deriv{v_\theta}{\rho} &=& 
+\deriv{}{\rho} \pars{ 4\log\cosh\frac{\psi}{4} \deriv{}{\theta} \log C
+  - \psi \deriv{\varPhi}{\theta} }.
+\end{eqnarray}
+
+By integrating from $\rho = 0$ to $\rho \rightarrow \infty$, 
+we have Dukhin-Derjaguin slip formula for tangential velocity component $V_\theta$ 
+(where the radial component is $V_r = 0$) for $\zeta = \cV - \varPhi$:
+\begin{eqnarray} 
+V_\theta = \zeta \cdot \deriv{\varPhi}{\theta} -
+      4\log\cosh \frac{\zeta}{4} \cdot \deriv{}{\theta} \log C 
+= \zeta \cdot \deriv{\varPhi}{\theta} + 
+      2\log\pars{1 - \tanh^2 \frac{\zeta}{4}} \cdot \deriv{}{\theta} \log C .
+\end{eqnarray}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Spherical Coordinates} \label{append:spherical}
+
+The following spherical coordinate system is used:
+\begin{eqnarray}
+x &=& r \sin \theta \cos \phi \\
+y &=& r \sin \theta \sin \phi \\
+z &=& r \cos \theta
+\end{eqnarray}
+
+Assume full symmetry around $z$ axis -- there is no dependence on $\phi$:
+\begin{eqnarray}
+\bnabla f &=& \frac{\partial f}{\partial r} \mathbf{\hat{r}} +
+\frac{1}{r} \frac{\partial f}{\partial \theta} \mathbf{\hat{\theta}} +
+\frac{1}{r \sin\theta} \frac{\partial f}{\partial \phi} \mathbf{\hat{\phi}}
+\\
+\bnabla \mathbf{\cdot} \mathbf{F} &=& 
+\frac{1}{r^2}\frac{\partial}{\partial r} \left( r^2 \cdot F_r\right)
+  + \frac{1}{r \sin\theta} \frac{\partial}{\partial \theta} \left( \sin\theta \cdot F_\theta\right)
+  + \frac{1}{r \sin\theta} \frac{\partial F_\phi}{\partial \phi}
+\end{eqnarray}
+
+\subsection{Scalar Operators}
+Scalar Laplacian derivation:
+\begin{eqnarray}
+\Laplacian f = \bnabla \mathbf{\cdot} \bnabla f = \frac{1}{r^2}\frac{\partial}{\partial r}
+\left( r^2 \frac{\partial f}{\partial r} \right) +
+\frac{1}{r^2 \sin\theta} \frac{\partial}{\partial \theta} \left( \sin\theta \cdot \frac{\partial f}{\partial \theta}\right)
++ \frac{1}{r^2 \sin^2\theta} \frac{\partial^2 f}{\partial \phi^2}
+\end{eqnarray}
+In conservative form:
+\begin{eqnarray}
+r^2 \sin\theta \cdot \bLaplacian f = \frac{\partial}{\partial r} \left( r^2 \sin \theta \frac{\partial f}{\partial r} \right) +
+\frac{\partial}{\partial \theta} \left( \sin\theta \cdot \frac{\partial f}{\partial \theta}\right) +
+\frac{\partial}{\partial \phi} \left( \frac{1}{\sin\theta} \cdot \frac{\partial f}{\partial \phi}\right)
+\end{eqnarray}
+
+The unit vectors in spherical coordinate system are:
+\begin{eqnarray}
+ \br &=& \mat{c}{r\sin\theta \cos\phi \\ r\sin\theta \sin\phi \\ r\cos\theta} \\
+ \brhat &=& \deriv{\br}{r}
+ = \mat{c}{\sin\theta \cos\phi \\ \sin\theta \sin\phi \\ \cos\theta} \\
+ \bthetahat &=& \frac{1}{r} \deriv{\br}{\theta}
+ = \mat{c}{\cos\theta \cos\phi \\ \cos\theta \sin\phi \\ -\sin\theta} \\
+ \bphihat &=& \frac{1}{r \sin \theta} \deriv{\br}{\phi}
+ = \mat{c}{-\sin\phi \\ \cos\phi \\ 0}
+\end{eqnarray}
+Note that:
+\begin{eqnarray}
+  \deriv{\brhat}{r} = \deriv{\bthetahat}{r} = \deriv{\bphihat}{r} = \mathbf{0} \\
+  \deriv{\brhat}{\theta} = \bthetahat \\
+  \deriv{\bthetahat}{\theta} = -\brhat \\
+  \deriv{\bphihat}{\theta} = \mathbf{0} \\
+  \deriv{\brhat}{\phi} = \sin \theta \cdot \bphihat \\
+  \deriv{\bthetahat}{\phi} = \cos \theta \cdot \bphihat \\
+  \deriv{\bphihat}{\phi} = -\sin \theta \cdot \brhat -\cos \theta \cdot \bthetahat
+\end{eqnarray}
+
+\subsection{Vector Operators}
+Vector gradient operator can be written by:
+\begin{eqnarray}
+\bnabla\bV &=& \left\{ \brhat \deriv{}{r} +
+\bthetahat \frac{1}{r} \deriv{}{\theta} +
+\bphihat \frac{1}{r \sin\theta} \deriv{}{\phi} \right\}
+\bV
+\\
+\bnabla\bV &=& \left\{ \brhat \deriv{}{r} +
+\bthetahat \frac{1}{r} \deriv{}{\theta} +
+\bphihat \frac{1}{r \sin\theta} \deriv{}{\phi} \right\}
+\left( V_r \brhat + V_\theta \bthetahat + V_\phi \bphihat \right)
+\\
+\deriv{\bV}{r} &=&
+\deriv{V_r}{r}\brhat + \deriv{V_\theta}{r}\bthetahat + \deriv{V_\phi}{r}\bphihat
+\\
+\deriv{\bV}{\theta} &=&
+\deriv{V_r}{\theta}\brhat + \deriv{V_\theta}{\theta}\bthetahat + \deriv{V_\phi}{\theta}\bphihat
++ V_r\bthetahat - V_\theta\brhat
+\\
+\deriv{\bV}{\phi} &=&
+\deriv{V_r}{\phi}\brhat + \deriv{V_\theta}{\phi}\bthetahat + \deriv{V_\phi}{\phi}\bphihat
++ V_r \sin\theta\bphihat + V_\theta \cos\theta\bphihat -
+V_\phi \left(\brhat \sin\theta + \bthetahat \cos\theta \right)
+\\
+\bnabla\bV &=&
+\mat{ccc}{1&0&0 \\ 0&\frac{1}{r}&0 \\ 0&0&\frac{1}{r \sin\theta}}
+\mat{ccc}{
+\deriv{V_r}{r} & \deriv{V_\theta}{r} & \deriv{V_\phi}{r} \\
+\deriv{V_r}{\theta} - V_\theta &
+\deriv{V_\theta}{\theta} + V_r&
+\deriv{V_\phi}{\theta} \\
+\deriv{V_r}{\phi} - V_\phi \sin\theta &
+\deriv{V_\theta}{\phi} - V_\phi \cos\theta  &
+\deriv{V_\phi}{\phi} + V_r \sin\theta + V_\theta \cos\theta
+}
+\end{eqnarray}
+Vector Laplacian components can be written as:
+\begin{eqnarray}
+\Laplacian \bV = \bnabla \cdot \bnabla \bV &=& \frac{1}{r^2}\deriv{}{r}\left(r^2 \deriv{\bV}{r}\right) +
+\frac{1}{r^2\sin\theta}\deriv{}{\theta}\left(\sin\theta\deriv{\bV}{\theta}\right)+
+\frac{1}{r^2 \sin^2\theta}\deriv{}{\phi}\left(\deriv{\bV}{\phi}\right)
+\end{eqnarray}
+$\brhat$ component:
+\begin{eqnarray}
+\Laplacian (V_r\brhat) &=&
+\frac{1}{r^2}\deriv{}{r}\left(r^2 \deriv{V_r}{r}\right)\brhat
+\\ &+&
+\frac{1}{r^2\sin\theta}\deriv{}{\theta}\left(
+\sin\theta\left(\deriv{V_r}{\theta}\brhat + V_r\bthetahat \right)\right)
+\\ &+&
+\frac{1}{r^2 \sin^2\theta}\deriv{}{\phi}\left(
+\deriv{V_r}{\phi}\brhat + V_r \sin\theta\bphihat
+\right) \\
+\Laplacian (V_r\brhat) &=&
+\left(
+\frac{2}{r}\deriv{V_r}{r}+\deriv{^2V_r}{r^2}\right)\brhat
+\\ &+&
+\frac{1}{r^2\sin\theta}\left(
+\cos\theta\left(\deriv{V_r}{\theta}\brhat + V_r\bthetahat \right) +
+\sin\theta\left(\deriv{^2V_r}{\theta^2}\brhat + \deriv{V_r}{\theta}\bthetahat + \deriv{V_r}{\theta}\bthetahat - V_r\brhat\right)
+\right)
+\\ &+&
+\frac{1}{r^2 \sin^2\theta}\left(
+\deriv{^2V_r}{\phi^2}\brhat + \deriv{V_r}{\phi} \sin\theta\bphihat +
+\deriv{V_r}{\phi}\bphihat\sin\theta - V_r \sin\theta
+\left(\brhat \sin\theta + \bthetahat \cos\theta \right)
+\right)
+\\
+\Laplacian (V_r\brhat) &=&
+\left(
+\frac{2}{r}\deriv{V_r}{r}+\deriv{^2V_r}{r^2}-\frac{2V_r}{r^2}
++ \frac{1}{r^2}\deriv{^2V_r}{\theta^2}
++ \frac{\cot\theta}{r^2} \deriv{V_r}{\theta}
++ \frac{1}{r^2 \sin^2\theta} \deriv{^2V_r}{\phi^2}
+\right)\brhat
+\\ &+& \frac{2}{r^2} \deriv{V_r}{\theta} \bthetahat + \frac{2}{r^2 \sin\theta}\deriv{V_r}{\phi} \bphihat
+\end{eqnarray}
+$\bthetahat$ component:
+\begin{eqnarray}
+\Laplacian (V_\theta\bthetahat) &=&
+\frac{1}{r^2}\deriv{}{r}\left(r^2 \deriv{V_\theta}{r}\right)\bthetahat
+\\ &+&
+\frac{1}{r^2\sin\theta}\deriv{}{\theta}\left(
+\sin\theta\left(\deriv{V_\theta}{\theta}\bthetahat - V_\theta\brhat \right)\right)
+\\ &+&
+\frac{1}{r^2 \sin^2\theta}\deriv{}{\phi}\left(
+\deriv{V_\theta}{\phi}\bthetahat + V_\theta \cos\theta\bphihat
+\right)
+\\
+\Laplacian (V_\theta\bthetahat) &=&
+\left(\frac{2}{r}\deriv{V_\theta}{r} + \deriv{^2V_\theta}{r^2}\right)\bthetahat
+\\ &+&
+\frac{1}{r^2\sin\theta}\left(
+\cos\theta\left(\deriv{V_\theta}{\theta}\bthetahat - V_\theta\brhat \right) +
+\sin\theta\left(\deriv{^2V_\theta}{\theta^2}\bthetahat - \deriv{V_\theta}{\theta}\brhat
+-\deriv{V_\theta}{\theta}\brhat - V_\theta\bthetahat\right)
+\right)
+\\ &+&
+\frac{1}{r^2 \sin^2\theta}\left(
+\deriv{^2V_\theta}{\phi^2}\bthetahat + \deriv{V_\theta}{\phi} \cos\theta\bphihat +
+\deriv{V_\theta}{\phi}\cos\theta\bphihat
+- V_\theta \cos\theta \left(\brhat \sin\theta + \bthetahat \cos\theta \right)
+\right)
+\\
+\Laplacian (V_\theta\bthetahat) &=&
+\left(-\frac{2\cot\theta}{r^2}V_\theta - 2\deriv{V_\theta}{\theta}\right)\brhat +
+\left(\frac{2}{r}\deriv{V_\theta}{r} + \deriv{^2V_\theta}{r^2} +
+\frac{\cot\theta}{r^2} \deriv{V_\theta}{\theta} +
+\frac{1}{r^2}\deriv{^2V_\theta}{\theta^2}\right)\bthetahat
+\\
+\\ &+&
+\frac{1}{r^2 \sin^2\theta}\left(
+\deriv{^2V_\theta}{\phi^2} - V_\theta \right)\bthetahat
++ \frac{2 \cot\theta}{r^2 \sin\theta} \deriv{V_\theta}{\phi} \bphihat
+\end{eqnarray}
+$\bphihat$ component:
+\begin{eqnarray}
+\Laplacian (V_\phi\bphihat) &=&
+\frac{1}{r^2}\deriv{}{r}\left(r^2 \deriv{V_\phi}{r}\right)\bphihat +
+\frac{1}{r^2\sin\theta}\deriv{}{\theta}\left(
+\sin\theta \deriv{V_\phi}{\theta}\bphihat \right)
+\\ &+&
+\frac{1}{r^2 \sin^2\theta}\deriv{}{\phi}\left(
+\deriv{V_\phi}{\phi}\bphihat
+- V_\phi \left(\brhat \sin\theta + \bthetahat \cos\theta\right)
+\right)
+\\
+\Laplacian (V_\phi\bphihat) &=&
+\frac{1}{r^2}\deriv{}{r}\left(r^2 \deriv{V_\phi}{r}\right)\bphihat +
+\frac{1}{r^2\sin\theta}\deriv{}{\theta}\left(
+\sin\theta \deriv{V_\phi}{\theta}\bphihat \right)
+\\ &+&
+\frac{1}{r^2 \sin^2\theta}\deriv{}{\phi}\left(
+\deriv{V_\phi}{\phi}\bphihat
+- V_\phi \left(\brhat \sin\theta + \bthetahat \cos\theta\right)
+\right)
+\\
+\Laplacian (V_\phi\bphihat) &=&
+\left(\frac{2}{r} \deriv{V_\phi}{r} + \deriv{^2V_\phi}{r^2}\right)\bphihat
++
+\frac{1}{r^2\sin\theta}\left(
+\cos\theta \deriv{V_\phi}{\theta} +
+\sin\theta \deriv{^2V_\phi}{\theta^2}
+\right)\bphihat
+\\ &+&
+\frac{1}{r^2 \sin^2\theta}\left(
+\deriv{^2V_\phi}{\phi^2}\bphihat
+- 2 \deriv{V_\phi}{\phi} \left(\brhat \sin\theta + \bthetahat \cos\theta\right)
+- V_\phi \bphihat
+\right)
+\end{eqnarray}
+In summary:
+\begin{eqnarray}
+\Laplacian \bV &=& \left(\Laplacian V_r - \frac{2V_r}{r^2}\right)\brhat
++ \frac{2}{r^2}\deriv{V_r}{\theta} \bthetahat + \frac{2}{r^2 \sin\theta}\deriv{V_r}{\phi} \bphihat \\
+&-&
+\frac{2}{r^2 \sin\theta} \deriv{\left(V_\theta \sin\theta \right)}{\theta}\brhat
++ \left(\Laplacian V_\theta - \frac{V_\theta}{r^2 \sin^2\theta}\right) \bthetahat
++ \frac{2 \cot\theta}{r^2 \sin\theta} \deriv{V_\theta}{\phi} \bphihat \\
+&-&
+\frac{2}{r^2 \sin\theta}\deriv{V_\phi}{\phi}\brhat -
+\frac{2 \cot\theta}{r^2 \sin\theta}\deriv{V_\phi}{\phi}\bthetahat
++ \left(\Laplacian V_\phi - \frac{V_\phi}{r^2 \sin^2\theta}\right)\bphihat
+\end{eqnarray}
+
+Since $V_\phi = 0$ and $\deriv{}{\phi}(\cdot) = 0$, we get:
+\begin{eqnarray}
+\Laplacian \bV &=& \left(\Laplacian V_r - \frac{2V_r}{r^2} - \frac{2}{r^2 \sin\theta} \deriv{\left(V_\theta \sin\theta \right)}{\theta}\right)\brhat
+\\
+&+&
+\left(\Laplacian V_\theta - \frac{V_\theta}{r^2 \sin^2\theta} + \frac{2}{r^2}\deriv{V_r}{\theta}\right) \bthetahat
+\\
+\Laplacian \bV &=& \left(
+\frac{1}{r^2}\deriv{}{r}\left( r^2 \deriv{V_r}{r} \right) + \frac{1}{r^2 \sin\theta} \deriv{}{\theta} \left( \sin\theta \cdot \deriv{V_r}{\theta}\right)
+ - \frac{2V_r}{r^2} - \frac{2}{r^2 \sin\theta} \deriv{\left(V_\theta \sin\theta \right)}{\theta}\right)\brhat \\
+&+& \left(
+\frac{1}{r^2}\deriv{}{r}\left( r^2 \deriv{V_\theta}{r} \right) + \frac{1}{r^2 \sin\theta} \deriv{}{\theta} \left( \sin\theta \cdot \deriv{V_\theta}{\theta}\right)
+ - \frac{V_\theta}{r^2 \sin^2\theta} + \frac{2}{r^2}\deriv{V_r}{\theta}\right) \bthetahat
+\end{eqnarray}
+
 \bibliographystyle{unsrt}

### 2012-10-13 notes/thesis/ijnam.tex
Update thesis.

@@
 
-\abstract{
+\begin{abstract}
 A numerical framework for the simulation of electrokinetic 
@@
 for a surface charged inert particle. The numerical results 
-are compared to the asymptotic solutions, and good correspondence is achieved.}
+are compared to the asymptotic solutions, and good correspondence is achieved.
+\end{abstract}
+
+\newpage
+\tableofcontents
+\newpage
 
@@
 the effective boundary conditions at the particle surface are:
-\subsubsection{Ion-exchanger} See \cite{yariv2010migration} for full derivation:
+\subsubsection{Ion-exchanger} See Appendix \ref{append:slip} for full derivation:
 \begin{equation}
@@
 The scalar gradient and the divergence can be written as:
-\begin{eqnarray}
+\begin{align}
 \bnabla f = \deriv{f}{r}\brhat + \frac{1}{r}\deriv{f}{\theta}\bthetahat, &
@@
                \frac{1}{r \sin\theta}\deriv{}{\theta}\pars{F_\theta \sin\theta}.
-\end{eqnarray}
+\end{align}
 The scalar Laplacian can be written as:
-\begin{eqnarray}
+\begin{align}
 \Laplacian f = \bnabla \cdot (\bnabla f) = 
@@
  \frac{1}{r^2 \sin\theta}\deriv{}{\theta}\pars{\sin\theta \deriv{f}{\theta}}.
-\end{eqnarray}
+\end{align}
 The vector gradient and vector Laplacian can be written as:
-\begin{eqnarray}
-\bnabla \bF &=& \deriv{F_r}{r} \brhat \brhat + \deriv{F_\theta}{r} \brhat \bthetahat + 
+\begin{align}
+\bnabla \bF &= \deriv{F_r}{r} \brhat \brhat + \deriv{F_\theta}{r} \brhat \bthetahat + 
 \frac{1}{r}\pars{\deriv{F_r}{\theta} - F_\theta} \bthetahat \brhat + 
 \frac{1}{r}\pars{\deriv{F_\theta}{\theta} + F_r} \bthetahat \bthetahat, \\
-\bLaplacian \bF &=& 
+\bLaplacian \bF &= 
 \left(\Laplacian F_r - \frac{2F_r}{r^2} - 
@@
 \frac{2}{r^2}\deriv{F_r}{\theta}\right) \bthetahat.
-\end{eqnarray}
+\end{align}
 
@@
 in a curvilinear coordinate system. 
+See Appendix \ref{append:spherical} for the full derivation of the identities above.
 
@@
 A regular grid of size $n_r \times n_\theta$ is defined, with:
-\begin{eqnarray} \label{eq:grid}
+\begin{align} \label{eq:grid}
 (r_i,\theta_j) \in [1, \infty) \times [0,\pi], & 
@@
  \theta_j = \Delta_\theta \cdot j,
-\end{eqnarray}
+\end{align}
 where a logarithmic grid spacing has been chosen for $r$ and a uniform grid for $\theta$.
@@
 A specific cell $\Omega_{ij}$ and its center $(\bar{r}_i, \bar{\theta}_j)$ are defined by \eqref{eq:grid}:
-\begin{eqnarray}
+\begin{align}
 \Omega_{ij} = [r_{i-1}, r_{i}] \times [\theta_{j-1}, \theta_{j}], &
@@
 \bar{\theta}_j = (\theta_{j-1} + \theta_{j})/2.
-\end{eqnarray}
+\end{align}
 
@@
 Define the following discrete central difference operators:
-\begin{eqnarray} \label{eq:disc_diff}
+\begin{align} \label{eq:disc_diff}
 \cD_r(f^h){}_{\left[i+\half,j\right]} = \frac{f^h_{\left[i+1,j\right]} - f^h_{\left[i,j\right]}}
@@
 					   {\theta_{\left[i,j+1\right]} - \theta_{\left[i,j\right]}}.
-\end{eqnarray}
+\end{align}
 
 Define the following linear interpolation operators:
-\begin{eqnarray} \label{eq:disc_interp}
+\begin{align} \label{eq:disc_interp}
 \begin{array}{rcl}
-\cI_r(f^h)_{\left[i+\half,j\right]} &=& 
+\cI_r(f^h)_{\left[i+\half,j\right]} &= 
 \frac{r_{\left[i+\half,j\right]} - r_{\left[i,j\right]}}
@@
 \\
-\cI_\theta(f^h)_{\left[i,j+\half\right]} &=& 
+\cI_\theta(f^h)_{\left[i,j+\half\right]} &= 
 \frac{r_{\left[i,j+\half\right]} - r_{\left[i,j\right]}}
@@
 \end{array}
-\end{eqnarray}
+\end{align}
 
@@
 then using \eqref{eq:disc_diff}, we have
-\begin{eqnarray}
+\begin{align}
 \frac{1}{r^2} \cD_r\pars{f^h_r r^2} + 
@@
 \cD_\theta\pars{f^h_\theta \cdot r \sin\theta}}{r^2 \sin\theta} = 0. 
-\end{eqnarray}
+\end{align}
 
@@
 using \eqref{eq:disc_diff} and \eqref{eq:disc_interp}:
-\begin{eqnarray} \nonumber
+\begin{align} \nonumber
 I^h_r = -\cI_r(C^h) \cdot \cD_r(\varPhi^h), &
@@
  \mathcal{U}^{\bV^h}_\theta(C^h)[i,j] = C^h\left[i, j-\frac{\sign(V^h_\theta)}{2}\right]. 
-\end{eqnarray}
+\end{align}
 
@@
 linear interpolation is used for the Coulomb force and for vector Laplacian components.
-\begin{eqnarray}
+\begin{align}
 \nonumber
-F^h_r &=& -\cD_r(P^h) 
+F^h_r &= -\cD_r(P^h) 
           + \cL(V^h_r) - \frac{2}{r^2} V^h_r 
@@
           + \cD_r(\varPhi^h) \cdot \cI_r(\cL(\varPhi^h)), \\
-F^h_\theta &=& -\frac{\cD_\theta(P^h)}{r} 
+F^h_\theta &= -\frac{\cD_\theta(P^h)}{r} 
 		  + \cL(V^h_\theta) - \frac{F^h_\theta}{r^2 \sin^2\theta} 
@@
 \nonumber
-\cL(f^h) &=& \frac{1}{r^2}\cD_r\pars{\cD_r(f^h) r^2} + 
+\cL(f^h) &= \frac{1}{r^2}\cD_r\pars{\cD_r(f^h) r^2} + 
 \frac{1}{r^2 \sin\theta} \cD_\theta\pars{\cD_\theta(f^h) \cdot \sin\theta}.
-\end{eqnarray}
+\end{align}
 
@@
 \begin{array}{rcl}
-0 &=& \cI_r(\varPhi^h + \log C^h), \\
-0 &=& \cD_r(\varPhi^h - \log C^h), \\
-V^h_r &=& 0, \\
-V^h_\theta &=& 4\log\pars{\frac{1}{2}\pars{1 + \exp\left\{\cI_\theta(\zeta^h)/2\right\}}} \cdot 
+0 &= \cI_r(\varPhi^h + \log C^h), \\
+0 &= \cD_r(\varPhi^h - \log C^h), \\
+V^h_r &= 0, \\
+V^h_\theta &= 4\log\pars{\frac{1}{2}\pars{1 + \exp\left\{\cI_\theta(\zeta^h)/2\right\}}} \cdot 
 			\cD_\theta(\zeta^h), \\
-  \zeta^h &=& - \log \gamma - \cI_r(\varPhi^h).
+  \zeta^h &= - \log \gamma - \cI_r(\varPhi^h).
 \end{array}
@@
 \begin{array}{rcl}
-0 &=& \cD_r(C^h) - \text{Du} \cdot 
+0 &= \cD_r(C^h) - \text{Du} \cdot 
 \pars{\cD_\theta \pars{\sin\theta \cdot \cD_\theta \cI_r\pars{\varPhi^h - \log C}}}/{\sin\theta}, \\
-0 &=& \cD_r(C^h) + \cI_r(C^h) \cD_r(\varPhi^h), \\
-V^h_r &=& 0, \\
-V^h_\theta &=& \cI_\theta(\zeta^h) \cdot \cD_\theta(\cI_r \varPhi^h - \log \cI_r C^h) + 
+0 &= \cD_r(C^h) + \cI_r(C^h) \cD_r(\varPhi^h), \\
+V^h_r &= 0, \\
+V^h_\theta &= \cI_\theta(\zeta^h) \cdot \cD_\theta(\cI_r \varPhi^h - \log \cI_r C^h) + 
 4 \log 2 \cdot \cD_\theta(\log \cI_r C^h), \\
-  \zeta^h &=& \bar{\zeta} - \log \cI_r C.
+  \zeta^h &= \bar{\zeta} - \log \cI_r C.
 \end{array}
@@
 aligned with $\ui$ and it vanishes iff $\ui \cdot \bF = 0$.
-\begin{eqnarray} \nonumber
-F_\imath = \ui \cdot \bF &=& 
+\begin{align} \nonumber
+F_\imath = \ui \cdot \bF &= 
 \oint_\mathcal{S} \pars{\ui \cdot \tT \cdot \bnhat} dA = 
@@
 \\  
-f_\imath = \ui \cdot \tT \cdot \brhat &=& \pars{-P + 2\cD_r(V_r) + 
+f_\imath = \ui \cdot \tT \cdot \brhat &= \pars{-P + 2\cD_r(V_r) + 
 \frac{1}{2}\pars{\cD_r(\varPhi)}^2 - \frac{1}{2r^2}\pars{\cD_\theta(\varPhi)}^2}\cos\theta 
@@
 + \frac{1}{r}\cD_r(\varPhi) \cD_{\theta}(\varPhi)}\sin\theta.
-\end{eqnarray}
+\end{align}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Slip Condition} \label{append:slip}
+\section{Ion-exchanger effective boundary conditions } \label{append:slip}
+
+\subsection{Debye layer scaling}
+
+We define the scaled coordinate $\rho$ (normal to ion-exchanger surface), where $\delta \ll 1$:
+\begin{align}
+  \rho = \frac{r-1}{\delta}. 
+\end{align}
+Thus, the electric potential and the ionic concentrations are $O(1)$ at the Debye layer ($r \approx 1$):
+\begin{align}
+  \varphi(\rho,\theta) &\sim \varphi, \\
+  c_\pm(\rho,\theta) &\sim c_\pm, \\
+  c(\rho,\theta) &\sim c, \\
+  q(\rho,\theta) &\sim q.
+\end{align}
+
+The radial fluxes at the Debye layer are $O(\delta^{-1})$, due to coordinate rescaling:
+\begin{align}
+  j_\pm(\rho, \theta) &\sim \delta^{-1} j_\pm.
+\end{align}
+
+The pressure is $O(\delta^{-2})$, due to momentum balance equations:
+\begin{align}
+  p(\rho, \theta) &\sim \delta^{-2} p.
+\end{align}
+
+The tangential velocity component is $O(1)$ and the radial component is $O(\delta)$.
+
+\subsection{Ion Fluxes}
+
+In order to match bulk $O(1)$ outer radial ionic flux, 
+the $O(\delta^{-1})$ term of the inner ionic radial flux, $j_\pm(\rho, \theta)$ must vanish:
+\begin{align}
+ \nonumber
+  -\deriv{c_\pm}{\rho} \mp c_\pm \deriv{\varphi}{\rho} &= 0, \\
+  \pars{\varPhi - \varphi} \pm\pars{\log C_\pm - \log c_\pm} &= 0, \\
+ \nonumber
+  \varPhi - \varphi \pm \log \frac{C_\pm}{c_\pm} &= 0.
+\end{align}
+This relation can be rewritten as a Boltzmann distribution of $c_\pm$,
+where $\lim_{\rho\rightarrow\infty} c_\pm = C$,
+\begin{equation}
+c_\pm = C \exp\left[\pm(\varPhi - \varphi)\right].
+\end{equation}
 
 \subsection{Electric Potential}
-The leading-order electric potential in the Debye layer:
-\begin{eqnarray}  
+The leading-order Laplace equation in the Debye layer reads
+\begin{align}  
 \deriv{^2 \varphi}{\rho^2} = -q = -\frac{c_+ - c_-}{2} = 
--C\frac{\exp\left[+(\varPhi - \varphi)\right] - \exp\left[-(\varPhi - \varphi)\right]}{2} = 
-C \sinh(\varphi - \varPhi).
-\end{eqnarray}
+-\frac{C}{2} \pars{\exp\left[+(\varPhi - \varphi)\right] - \exp\left[-(\varPhi - \varphi)\right]} = C \sinh(\varphi - \varPhi).
+\end{align}
 Denote $\psi = \varphi - \varPhi$, so that $\psi(0) = \cV - \varPhi = \zeta$ and 
 $\psi(\rho\rightarrow\infty) = 0$:
-\begin{eqnarray}  
-\deriv{^2 \psi}{\rho^2} &=& C \sinh(\psi) = 2 C \sinh{\frac{\psi}{2}}\cosh{\frac{\psi}{2}} ,
+\begin{align}
+\nonumber
+\deriv{^2 \psi}{\rho^2} &= C \sinh(\psi) = 2 C \sinh{\frac{\psi}{2}}\cosh{\frac{\psi}{2}} ,
 \\
-2\deriv{\psi}{\rho} \deriv{^2 \psi}{\rho^2} &=& 
+2\deriv{\psi}{\rho} \deriv{^2 \psi}{\rho^2} &= 
 4 C \sinh{\frac{\psi}{2}}\cosh{\frac{\psi}{2}} \deriv{\psi}{\rho} ,
-\\
-\deriv{}{\rho} \pars{\deriv{\psi}{\rho}}^2 &=& 
+\\ \nonumber
+\deriv{}{\rho} \pars{\deriv{\psi}{\rho}}^2 &= 
 \deriv{}{\rho} \pars{2 \sqrt{C} \sinh{\frac{\psi}{2}}}^2 .
-\end{eqnarray}
+\end{align}
 
 Integrating with respect to boundary condtions yields:
-\begin{eqnarray}  
-\deriv{\psi}{\rho} &=& -2\sqrt{C}\sinh\frac{\psi}{2}, \\  
-\pars{4\sinh\frac{\psi}{4}\cosh\frac{\psi}{4}}^{-1}\deriv{\psi}{\rho} &=& -\sqrt{C}, \\  
-\frac{\pars{\tanh\frac{\psi}{4}}^{-1}}{4\cosh^2\frac{\psi}{4}}
-\deriv{\psi}{\rho} &=& -\sqrt{C}, \\  
-\deriv{}{\rho}\pars{\log\tanh\frac{\psi}{4}} &=& \deriv{}{\rho}\pars{-\rho \sqrt{C}} .
-\end{eqnarray}
+\begin{align}  
+\nonumber
+\deriv{\psi}{\rho} = -2\sqrt{C}\sinh\frac{\psi}{2} &= 
+-4\sinh\frac{\psi}{4}\cosh\frac{\psi}{4} \sqrt{C} = 
+-4\tanh\frac{\psi}{4}\cosh^2\frac{\psi}{4} \sqrt{C}, \\  
+\frac{1/{\tanh\frac{\psi}{4}}}{4\cosh^2\frac{\psi}{4}}
+\deriv{\psi}{\rho}
+&= -\sqrt{C}, \\  
+\nonumber
+\deriv{}{\rho}\pars{\log\tanh\frac{\psi}{4}} &= \deriv{}{\rho}\pars{-\rho \sqrt{C}} .
+\end{align}
 
 Integrating with respect to boundary condtions yields:
-\begin{eqnarray}
-\log\tanh\frac{\psi}{4} - \log\tanh\frac{\zeta}{4} &=& -\rho \sqrt{C}, \\
-\psi = \varphi - \varPhi &=& 
-4 \tanh^{-1}\pars{\tanh{\frac{\zeta}{4}} \cdot \exp\pars{-\rho \sqrt{C}}}.
-\end{eqnarray}
+\begin{align}
+\log\tanh\frac{\psi}{4} - \log\tanh\frac{\zeta}{4} &= -\rho \sqrt{C}, \\
+\psi = \varphi - \varPhi &= 
+4 \tanh^{-1}\pars{\tanh{\frac{\zeta}{4}} \cdot e^{-\rho \sqrt{C}}}.
+\end{align}
 
@@
 Leading-order $O(\delta^{-3})$ radial momentum balance in the Debye layer yields:
-\begin{eqnarray} 
-- \deriv{p}{\rho} + \deriv{\varphi}{\rho} \deriv{^2\varphi}{\rho^2} &=& 0.
-\end{eqnarray}
+\begin{align} 
+- \deriv{p}{\rho} + \deriv{\varphi}{\rho} \deriv{^2\varphi}{\rho^2} &= 0.
+\end{align}
 One integration yields:
-\begin{eqnarray} 
-p &=& \frac{1}{2}\pars{\deriv{\varphi}{\rho}}^2 = \frac{1}{2}\pars{\deriv{\psi}{\rho}}^2.
-\end{eqnarray}
+\begin{align} 
+p &= \frac{1}{2}\pars{\deriv{\varphi}{\rho}}^2 = \frac{1}{2}\pars{\deriv{\psi}{\rho}}^2.
+\end{align}
 
@@
 Leading-order $O(\delta^{-2})$ tangential momentum balance in the Debye layer yields:
-\begin{eqnarray} 
-0 &=& \deriv{^2 v_\theta}{\rho^2} - \deriv{p}{\theta} 
+\begin{align} 
+\nonumber
+0 &= \deriv{^2 v_\theta}{\rho^2} - \deriv{p}{\theta} 
  + \deriv{\varphi}{\theta} \deriv{^2\varphi}{\rho^2} ,
-\\
-\deriv{^2 v_\theta}{\rho^2} &=& \frac{1}{2}\deriv{}{\theta}\pars{\deriv{\psi}{\rho}}^2
+\\ \nonumber
+\deriv{^2 v_\theta}{\rho^2} &= \frac{1}{2}\deriv{}{\theta}\pars{\deriv{\psi}{\rho}}^2
 - \deriv{(\psi + \varPhi)}{\theta} \deriv{^2\psi}{\rho^2}  
-\\
- &=& \deriv{}{\theta}\pars{2C \sinh^2\frac{\psi}{2}}
+ = \deriv{}{\theta}\pars{2C \sinh^2\frac{\psi}{2}}
 - \deriv{\psi}{\theta} C \sinh\psi
@@
 \\
- &=& \deriv{}{\theta}\pars{C \pars{\cosh\psi - 1}}
+ &= \deriv{}{\theta}\pars{C \pars{\cosh\psi - 1}}
 - C \sinh\psi \deriv{\psi}{\theta}
 - \deriv{\varPhi}{\theta} \deriv{^2\psi}{\rho^2}  
-\\
- &=& \deriv{C}{\theta} \pars{\cosh\psi - 1}
+\\ \nonumber
+ &= \deriv{C}{\theta} \pars{\cosh\psi - 1}
 - \deriv{\varPhi}{\theta} \deriv{^2\psi}{\rho^2}  
@@
 - \deriv{\varPhi}{\theta} \deriv{^2\psi}{\rho^2}  
-\\
- &=& -\deriv{C}{\theta} \frac{2}{\sqrt{C}} \pars{\half \sinh \frac{\psi}{2} \deriv{\psi}{\rho}}
+\\ \nonumber
+ &= -\deriv{C}{\theta} \frac{2}{\sqrt{C}} \pars{\half \sinh \frac{\psi}{2} \deriv{\psi}{\rho}}
 - \deriv{\varPhi}{\theta} \deriv{^2\psi}{\rho^2}  
@@
 - \deriv{\varPhi}{\theta} \deriv{^2\psi}{\rho^2}  .
-\end{eqnarray}
+\end{align}
 By integrating from specific $\rho$ to $\rho \rightarrow \infty$ (where $\psi = 0$):
-\begin{eqnarray}
-\deriv{v_\theta}{\rho} &=& -\deriv{C}{\theta} \frac{2}{\sqrt{C}} 
+\begin{align}
+\deriv{v_\theta}{\rho} &= -\deriv{C}{\theta} \frac{2}{\sqrt{C}} 
 \pars{\cosh \frac{\psi}{2} - 1} - \deriv{\varPhi}{\theta} \deriv{\psi}{\rho}   
@@
   - \deriv{\varPhi}{\theta} \deriv{\psi}{\rho}   .
-\end{eqnarray}
+\end{align}
 Note that:
-\begin{eqnarray}
-\deriv{\psi}{\rho} &=& -2\sqrt{C}\sinh\frac{\psi}{2} = 
+\begin{align}
+\deriv{\psi}{\rho} &= -2\sqrt{C}\sinh\frac{\psi}{2} = 
                        -4\sqrt{C}\sinh\frac{\psi}{4}\cosh\frac{\psi}{4},
 \\
--4\sinh\frac{\psi}{4} &=& \frac{1}{\sqrt{C} \cosh\frac{\psi}{4}} \deriv{\psi}{\rho}.
-\end{eqnarray}
+-4\sinh\frac{\psi}{4} &= \frac{1 / \cosh\frac{\psi}{4}}{\sqrt{C}} \deriv{\psi}{\rho}.
+\end{align}
 Thus:
-\begin{eqnarray}
-\deriv{v_\theta}{\rho} &=& 
+\begin{align}
+\deriv{v_\theta}{\rho} &= 
   \pars{\deriv{C}{\theta} \frac{1}{C}} \cdot
@@
 \\
-\deriv{v_\theta}{\rho} &=& 
+\deriv{v_\theta}{\rho} &= 
 \deriv{}{\rho} \pars{ 4\log\cosh\frac{\psi}{4} \deriv{}{\theta} \log C
   - \psi \deriv{\varPhi}{\theta} }.
-\end{eqnarray}
+\end{align}
 
@@
 (where the radial component is $V_r = 0$) for $\zeta = \cV - \varPhi$:
-\begin{eqnarray} 
+\begin{align} 
 V_\theta = \zeta \cdot \deriv{\varPhi}{\theta} -
@@
       2\log\pars{1 - \tanh^2 \frac{\zeta}{4}} \cdot \deriv{}{\theta} \log C .
-\end{eqnarray}
+\end{align}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Spherical Coordinates} \label{append:spherical}
+\section{Differential operators in spherical coordinates} \label{append:spherical}
 
 The following spherical coordinate system is used:
-\begin{eqnarray}
-x &=& r \sin \theta \cos \phi \\
-y &=& r \sin \theta \sin \phi \\
-z &=& r \cos \theta
-\end{eqnarray}
+\begin{align}
+\nonumber
+x &= r \sin \theta \cos \phi \\
+y &= r \sin \theta \sin \phi \\
+\nonumber
+z &= r \cos \theta
+\end{align}
 
 Assume full symmetry around $z$ axis -- there is no dependence on $\phi$:
-\begin{eqnarray}
-\bnabla f &=& \frac{\partial f}{\partial r} \mathbf{\hat{r}} +
+\begin{align}
+\bnabla f &= \frac{\partial f}{\partial r} \mathbf{\hat{r}} +
 \frac{1}{r} \frac{\partial f}{\partial \theta} \mathbf{\hat{\theta}} +
@@
 \\
-\bnabla \mathbf{\cdot} \mathbf{F} &=& 
+\bnabla \mathbf{\cdot} \mathbf{F} &= 
 \frac{1}{r^2}\frac{\partial}{\partial r} \left( r^2 \cdot F_r\right)
@@
   + \frac{1}{r \sin\theta} \frac{\partial F_\phi}{\partial \phi}
-\end{eqnarray}
+\end{align}
 
@@
 Scalar Laplacian derivation:
-\begin{eqnarray}
+\begin{align}
 \Laplacian f = \bnabla \mathbf{\cdot} \bnabla f = \frac{1}{r^2}\frac{\partial}{\partial r}
@@
 + \frac{1}{r^2 \sin^2\theta} \frac{\partial^2 f}{\partial \phi^2}
-\end{eqnarray}
+\end{align}
 In conservative form:
-\begin{eqnarray}
+\begin{align}
 r^2 \sin\theta \cdot \bLaplacian f = \frac{\partial}{\partial r} \left( r^2 \sin \theta \frac{\partial f}{\partial r} \right) +
@@
 \frac{\partial}{\partial \phi} \left( \frac{1}{\sin\theta} \cdot \frac{\partial f}{\partial \phi}\right)
-\end{eqnarray}
+\end{align}
 
 The unit vectors in spherical coordinate system are:
-\begin{eqnarray}
- \br &=& \mat{c}{r\sin\theta \cos\phi \\ r\sin\theta \sin\phi \\ r\cos\theta} \\
- \brhat &=& \deriv{\br}{r}
- = \mat{c}{\sin\theta \cos\phi \\ \sin\theta \sin\phi \\ \cos\theta} \\
- \bthetahat &=& \frac{1}{r} \deriv{\br}{\theta}
- = \mat{c}{\cos\theta \cos\phi \\ \cos\theta \sin\phi \\ -\sin\theta} \\
- \bphihat &=& \frac{1}{r \sin \theta} \deriv{\br}{\phi}
+\begin{align}
+ \brhat &= \deriv{\br}{r}
+ = \mat{c}{\sin\theta \cos\phi \\ \sin\theta \sin\phi \\ \cos\theta} ,&
+ \bthetahat &= \frac{1}{r} \deriv{\br}{\theta}
+ = \mat{c}{\cos\theta \cos\phi \\ \cos\theta \sin\phi \\ -\sin\theta} ,&
+ \bphihat &= \frac{1}{r \sin \theta} \deriv{\br}{\phi}
  = \mat{c}{-\sin\phi \\ \cos\phi \\ 0}
-\end{eqnarray}
+\end{align}
 Note that:
-\begin{eqnarray}
-  \deriv{\brhat}{r} = \deriv{\bthetahat}{r} = \deriv{\bphihat}{r} = \mathbf{0} \\
-  \deriv{\brhat}{\theta} = \bthetahat \\
-  \deriv{\bthetahat}{\theta} = -\brhat \\
-  \deriv{\bphihat}{\theta} = \mathbf{0} \\
-  \deriv{\brhat}{\phi} = \sin \theta \cdot \bphihat \\
-  \deriv{\bthetahat}{\phi} = \cos \theta \cdot \bphihat \\
-  \deriv{\bphihat}{\phi} = -\sin \theta \cdot \brhat -\cos \theta \cdot \bthetahat
-\end{eqnarray}
+\begin{align}
+  \deriv{\brhat}{r} = \mathbf{0} , \nonumber
+  \deriv{\bthetahat}{r} = \mathbf{0} , 
+  \deriv{\bphihat}{r} = \mathbf{0}, \\
+  \deriv{\brhat}{\theta} = \bthetahat , 
+  \deriv{\bthetahat}{\theta} = -\brhat , 
+  \deriv{\bphihat}{\theta} = \mathbf{0}, \\
+  \deriv{\brhat}{\phi} = \sin \theta \cdot \bphihat , \nonumber
+  \deriv{\bthetahat}{\phi} = \cos \theta \cdot \bphihat , 
+  \deriv{\bphihat}{\phi} = -\sin \theta \cdot \brhat -\cos \theta \cdot \bthetahat.
+\end{align}
 
@@
 Vector gradient operator can be written by:
-\begin{eqnarray}
-\bnabla\bV &=& \left\{ \brhat \deriv{}{r} +
+\begin{align} \nonumber
+\bnabla\bV &= \left\{ \brhat \deriv{}{r} +
 \bthetahat \frac{1}{r} \deriv{}{\theta} +
 \bphihat \frac{1}{r \sin\theta} \deriv{}{\phi} \right\}
-\bV
-\\
-\bnabla\bV &=& \left\{ \brhat \deriv{}{r} +
+\bV = \left\{ \brhat \deriv{}{r} +
 \bthetahat \frac{1}{r} \deriv{}{\theta} +
@@
 \left( V_r \brhat + V_\theta \bthetahat + V_\phi \bphihat \right)
-\\
-\deriv{\bV}{r} &=&
+\\ \nonumber
+\deriv{\bV}{r} &=
 \deriv{V_r}{r}\brhat + \deriv{V_\theta}{r}\bthetahat + \deriv{V_\phi}{r}\bphihat
 \\ 
-\deriv{\bV}{\theta} &=&
+\deriv{\bV}{\theta} &=
 \deriv{V_r}{\theta}\brhat + \deriv{V_\theta}{\theta}\bthetahat + \deriv{V_\phi}{\theta}\bphihat
 + V_r\bthetahat - V_\theta\brhat
-\\
-\deriv{\bV}{\phi} &=&
+\\ \nonumber
+\deriv{\bV}{\phi} &=
 \deriv{V_r}{\phi}\brhat + \deriv{V_\theta}{\phi}\bthetahat + \deriv{V_\phi}{\phi}\bphihat
@@
 V_\phi \left(\brhat \sin\theta + \bthetahat \cos\theta \right)
-\\
-\bnabla\bV &=&
+\\ \nonumber
+\bnabla\bV &=
 \mat{ccc}{1&0&0 \\ 0&\frac{1}{r}&0 \\ 0&0&\frac{1}{r \sin\theta}}
@@
 }
-\end{eqnarray}
+\end{align}
 Vector Laplacian components can be written as:
-\begin{eqnarray}
-\Laplacian \bV = \bnabla \cdot \bnabla \bV &=& \frac{1}{r^2}\deriv{}{r}\left(r^2 \deriv{\bV}{r}\right) +
+\begin{align}
+\Laplacian \bV = \bnabla \cdot \bnabla \bV &= \frac{1}{r^2}\deriv{}{r}\left(r^2 \deriv{\bV}{r}\right) +
 \frac{1}{r^2\sin\theta}\deriv{}{\theta}\left(\sin\theta\deriv{\bV}{\theta}\right)+
 \frac{1}{r^2 \sin^2\theta}\deriv{}{\phi}\left(\deriv{\bV}{\phi}\right)
-\end{eqnarray}
+\end{align}
 $\brhat$ component:
-\begin{eqnarray}
-\Laplacian (V_r\brhat) &=&
+\begin{align}
+\Laplacian (V_r\brhat) &= \nonumber
 \frac{1}{r^2}\deriv{}{r}\left(r^2 \deriv{V_r}{r}\right)\brhat
-\\ &+&
+\\ &+ \nonumber
 \frac{1}{r^2\sin\theta}\deriv{}{\theta}\left(
 \sin\theta\left(\deriv{V_r}{\theta}\brhat + V_r\bthetahat \right)\right)
-\\ &+&
+\\ &+ \nonumber
 \frac{1}{r^2 \sin^2\theta}\deriv{}{\phi}\left(
@@
 \right) \\
-\Laplacian (V_r\brhat) &=&
+\Laplacian (V_r\brhat) &= 
 \left(
 \frac{2}{r}\deriv{V_r}{r}+\deriv{^2V_r}{r^2}\right)\brhat
-\\ &+&
+\\ &+ \nonumber
 \frac{1}{r^2\sin\theta}\left(
@@
 \right)
-\\ &+&
+\\ &+ \nonumber
 \frac{1}{r^2 \sin^2\theta}\left(
@@
 \right)
-\\
-\Laplacian (V_r\brhat) &=&
+\\ \nonumber
+\Laplacian (V_r\brhat) &=
 \left(
@@
 \right)\brhat
-\\ &+& \frac{2}{r^2} \deriv{V_r}{\theta} \bthetahat + \frac{2}{r^2 \sin\theta}\deriv{V_r}{\phi} \bphihat
-\end{eqnarray}
+\\ &+ \frac{2}{r^2} \deriv{V_r}{\theta} \bthetahat + \frac{2}{r^2 \sin\theta}\deriv{V_r}{\phi} \bphihat
+\nonumber
+\end{align}
 $\bthetahat$ component:
-\begin{eqnarray}
-\Laplacian (V_\theta\bthetahat) &=&
+\begin{align}
+\Laplacian (V_\theta\bthetahat) &= \nonumber
 \frac{1}{r^2}\deriv{}{r}\left(r^2 \deriv{V_\theta}{r}\right)\bthetahat
-\\ &+&
+\\ &+ \nonumber
 \frac{1}{r^2\sin\theta}\deriv{}{\theta}\left(
 \sin\theta\left(\deriv{V_\theta}{\theta}\bthetahat - V_\theta\brhat \right)\right)
-\\ &+&
+\\ &+ \nonumber
 \frac{1}{r^2 \sin^2\theta}\deriv{}{\phi}\left(
@@
 \\ 
-\Laplacian (V_\theta\bthetahat) &=&
+\Laplacian (V_\theta\bthetahat) &=
 \left(\frac{2}{r}\deriv{V_\theta}{r} + \deriv{^2V_\theta}{r^2}\right)\bthetahat
-\\ &+&
+\\ &+ \nonumber
 \frac{1}{r^2\sin\theta}\left(
@@
 \right)
-\\
-\Laplacian (V_\theta\bthetahat) &=&
+\\ \nonumber
+\Laplacian (V_\theta\bthetahat) &=
 \left(-\frac{2\cot\theta}{r^2}V_\theta - 2\deriv{V_\theta}{\theta}\right)\brhat +
@@
 \frac{1}{r^2}\deriv{^2V_\theta}{\theta^2}\right)\bthetahat
-\\
-\\ &+&
+\\ &+ \nonumber
 \frac{1}{r^2 \sin^2\theta}\left(
@@
 + \frac{2 \cot\theta}{r^2 \sin\theta} \deriv{V_\theta}{\phi} \bphihat
-\end{eqnarray}
+\end{align}
 $\bphihat$ component:
-\begin{eqnarray}
-\Laplacian (V_\phi\bphihat) &=&
+\begin{align} \nonumber
+\Laplacian (V_\phi\bphihat) &= \nonumber
 \frac{1}{r^2}\deriv{}{r}\left(r^2 \deriv{V_\phi}{r}\right)\bphihat +
@@
 \sin\theta \deriv{V_\phi}{\theta}\bphihat \right)
-\\ &+&
+\\ &+ \nonumber
 \frac{1}{r^2 \sin^2\theta}\deriv{}{\phi}\left(
@@
 \\ 
-\Laplacian (V_\phi\bphihat) &=&
+\Laplacian (V_\phi\bphihat) &=
 \frac{1}{r^2}\deriv{}{r}\left(r^2 \deriv{V_\phi}{r}\right)\bphihat +
@@
 \right)
-\\
-\Laplacian (V_\phi\bphihat) &=&
+\\ \nonumber
+\Laplacian (V_\phi\bphihat) &=
 \left(\frac{2}{r} \deriv{V_\phi}{r} + \deriv{^2V_\phi}{r^2}\right)\bphihat
@@
 \right)\bphihat
-\\ &+&
+\\ &+ \nonumber
 \frac{1}{r^2 \sin^2\theta}\left(
@@
 \right)
-\end{eqnarray}
+\end{align}
 In summary:
-\begin{eqnarray}
-\Laplacian \bV &=& \left(\Laplacian V_r - \frac{2V_r}{r^2}\right)\brhat
+\begin{align} \nonumber
+\Laplacian \bV &= \left(\Laplacian V_r - \frac{2V_r}{r^2}\right)\brhat
 + \frac{2}{r^2}\deriv{V_r}{\theta} \bthetahat + \frac{2}{r^2 \sin\theta}\deriv{V_r}{\phi} \bphihat \\
-&-&
+&-
 \frac{2}{r^2 \sin\theta} \deriv{\left(V_\theta \sin\theta \right)}{\theta}\brhat
@@
 + \frac{2 \cot\theta}{r^2 \sin\theta} \deriv{V_\theta}{\phi} \bphihat \\
-&-&
+&- \nonumber
 \frac{2}{r^2 \sin\theta}\deriv{V_\phi}{\phi}\brhat -
@@
 + \left(\Laplacian V_\phi - \frac{V_\phi}{r^2 \sin^2\theta}\right)\bphihat
-\end{eqnarray}
+\end{align}
 
 Since $V_\phi = 0$ and $\deriv{}{\phi}(\cdot) = 0$, we get:
-\begin{eqnarray}
-\Laplacian \bV &=& \left(\Laplacian V_r - \frac{2V_r}{r^2} - \frac{2}{r^2 \sin\theta} \deriv{\left(V_\theta \sin\theta \right)}{\theta}\right)\brhat
-\\
-&+&
+\begin{align} \nonumber
+\Laplacian \bV &= \left(\Laplacian V_r - \frac{2V_r}{r^2} - \frac{2}{r^2 \sin\theta} \deriv{\left(V_\theta \sin\theta \right)}{\theta}\right)\brhat
++
 \left(\Laplacian V_\theta - \frac{V_\theta}{r^2 \sin^2\theta} + \frac{2}{r^2}\deriv{V_r}{\theta}\right) \bthetahat
 \\
-\Laplacian \bV &=& \left(
+\Laplacian \bV &= \left(
 \frac{1}{r^2}\deriv{}{r}\left( r^2 \deriv{V_r}{r} \right) + \frac{1}{r^2 \sin\theta} \deriv{}{\theta} \left( \sin\theta \cdot \deriv{V_r}{\theta}\right)
- - \frac{2V_r}{r^2} - \frac{2}{r^2 \sin\theta} \deriv{\left(V_\theta \sin\theta \right)}{\theta}\right)\brhat \\
-&+& \left(
+ - \frac{2V_r}{r^2} - \frac{2}{r^2 \sin\theta} \deriv{\left(V_\theta \sin\theta \right)}{\theta}\right)\brhat \\ \nonumber
+&+ \left(
 \frac{1}{r^2}\deriv{}{r}\left( r^2 \deriv{V_\theta}{r} \right) + \frac{1}{r^2 \sin\theta} \deriv{}{\theta} \left( \sin\theta \cdot \deriv{V_\theta}{\theta}\right)
  - \frac{V_\theta}{r^2 \sin^2\theta} + \frac{2}{r^2}\deriv{V_r}{\theta}\right) \bthetahat
-\end{eqnarray}
+\end{align}
 

### 2012-10-17 notes/thesis/main.tex
Rename thesis main LATEX file.

--- 2012-10-13 notes/thesis/ijnam.tex
@@
 We consider the following scenarios:
-\subsubsection{Ion-exchanger \cite{yariv2010migration}}
-We assume high conductance of the particle (yielding a uniform electric potential),
+\subsubsection{Ion-exchanger}
+Following \cite{yariv2010migration}, we assume high conductance of the particle (yielding a uniform electric potential),
 zero slip, anion impermeability, cation selectivity 
@@
 
-\subsubsection{Inert particle \cite{schnitzer2012surface}}
-We assume constant surface charge
+\subsubsection{Inert particle}
+Following \cite{schnitzer2012surface}, we assume constant surface charge
 zero slip and ion impermeability:
@@
 
-Each discrete variable is located with respect of its cell as follows:
+Each discrete variable is located with respect of its cell 
+as shown at Figure \ref{fig:grids}.
 $\varPhi$, $C$ and $P$ are represented by their value at the center of each cell, 
@@
 \end{equation}
+
+\begin{figure}[htbp]
+    \begin{center}
+	\includegraphics[width=1\textwidth]{figs/grids.eps}
+        \caption{Computational Grid.}
+    \label{fig:grids}
+    \end{center}
+\end{figure}
 

### 2012-10-18 notes/ijnam/figs/Cubic/Stream/plot_streamlines.m
Add new streamlines to IJNAM.

@@ -10,7 +10,7 @@ Z = s.Psi(I, :);
 X = R.*cos(T);
 Y = R.*sin(T);
 c = s.beta*0.05;
-c = linspace(-c, c, 15);
+c = linspace(-c, c, 40);
 
 fmt = '-deps2';
 
@@ -25,8 +25,8 @@ print(fmt, sprintf('A%d', k))
 
 function show(X, Y, Z, c, r_, b, fmt)
 hold on;
-colormap(ones(2, 3) * 0.5)
-contour([X X], [Y -Y], [Z -Z], c);
+contour(X, Y, Z, c);
+contour(X, -Y, Z, c);
 xlim([-1 1]*r_/2)
 ylim([-.1 .1]*r_/4)
 axis equal

### 2012-11-10 notes/ijnam/ijnam.tex
Right-aligned equations.
Replace streamlines figure.
Add new streamlines to IJNAM.
Fix Udi's remarks

@@
-\documentclass[10pt]{ijnam}
+\documentclass[10pt,reqno]{ijnam}
 \hsize=5.5 true in
@@
 scale disparity of the boundary layer
-is used to derive nonlinear effective boundary conditions for the
-numerical solver
-using the specific chemical properties of the particle.
+has been used to derive nonlinear effective boundary conditions 
+using the specific chemical properties of the particle,
+for an ion-exchanger particle at \cite{yariv2010migration}
+and for a surface charged inert particle at \cite{schnitzer2012surface}.
 The nonlinear system is discretized and an iterative Newton solver is
-constructed automatically from the discrete equations and boundary 
-conditions.
+constructed automatically from the discrete equations and the 
+nonlinear effective boundary conditions.
+Numerical results are obtained for an ion-exchanger and 
+for a surface charged inert particle. 
 An asymptotic analytical solution is 
-derived for the validation of the solver. 
-Numerical results are obtained for an ion-exchanger and 
-for a surface charged inert particle. The numerical results 
-are compared to the asymptotic solutions, and good correspondence is achieved.}
+used for the validation of the solver. 
+The numerical results are compared to the asymptotic solutions, 
+and good correspondence is achieved.}
 
@@
 Debye layer width being much smaller than the particle size. 
-A closed-form linear asymptotic solution has been developed for
-spherical particles and weak electric field in an
-axisymmetric setting \cite{yariv2010migration} but it is hard to extend this
-analytic solution to more general systems. Once the electric field
-becomes stronger, significant nonlinear phenomena emerge.
+An effective boundary condition outside the Debye layer
+has been developed for spherical particles, yielding a macroscale 
+model at \cite{yariv2010migration, schnitzer2012surface}.
+The model is solved for weak electric field in an axisymmetric setting 
+but it is hard to extend this analytic solution to more general systems.
+Once the electric field becomes stronger, 
+significant nonlinear phenomena emerge.
 This interesting regime has not yet been explored extensively.
@@
 and nanoscale objects in many nanotechnology applications,
-nano-fluidic devices, packed bed separation, desalination processes and various 
-electrophoresis applications \cite{howse2007self,paxton2004catalytic,pumera2010electrochemically,nischang2007,leinweber2004}.
-Because the model for these electrokinetic
+nano-fluidic devices, packed bed separation, desalination processes 
+and various electrophoresis applications \cite{howse2007self,paxton2004catalytic,pumera2010electrochemically,nischang2007,leinweber2004}.
+Because the nonlinear macroscale model for these electrokinetic
 phenomena has no closed-form analytic solution, a numerical
@@
 
-The goal of this work is to develop and implement a software toolbox for the generation
-of iterative numerical solvers for nonlinear electrokinetic problems, and to apply it to the study
-of systems that have no closed-form solutions, such as ion-exchanger migration
-\cite{yariv2010migration} and the electrophoresis problem \cite{schnitzer2012surface}.
-This solver can be used to gain insight into the chemical and physical behavior 
-in far more general regimes than are currently well-understood, 
-and also to possibly lead to further analytical developments, based on new scaling behavior
-discovered numerically. We may also target interesting physical
+The goal of this work is to develop and implement a software toolbox 
+for the generation of iterative numerical solvers for nonlinear macroscale 
+electrokinetic problems, and to apply it to the study
+of systems that have no closed-form solutions, 
+such as ion-exchanger migration \cite{yariv2010migration} 
+and the electrophoresis problem \cite{schnitzer2012surface}.
+This solver can be used to gain insight into the chemical 
+and physical behavior in far more general regimes than 
+are currently well-understood, 
+and also to possibly lead to further analytical developments, 
+based on new scaling behavior
+discovered numerically. 
+We may also target interesting physical
 phenomena that have been observed experimentally.
 One such phenomenon is nonlinear electrokinetic vortex flow, 
-which is useful for microfluidic mixing applications \cite{wang2004mix, ben2002vortex},
-
-The paper is structured as follows: the governing equations of the electrokinetic model
-are derived in Section \ref{sec:equations}. The algorithm for the discretization and 
+which is useful for microfluidic mixing applications 
+\cite{wang2004mix, ben2002vortex}.
+
+The paper is structured as follows: the governing equations of 
+the electrokinetic model are presented in Section \ref{sec:equations}, 
+following the derivation at \cite{yariv2010migration, schnitzer2012surface}. 
+The algorithm for the discretization and 
 the solution of the system is described in Section \ref{sec:algorithm}.
-An analytical asymptotic solution for the nonlinear system is derived 
-and presented in Section \ref{sec:asymp}.
+An analytical asymptotic solution for the ion exchanger nonlinear 
+macroscale model is derived and presented in Section \ref{sec:asymp}.
 Numerical results and their comparison to an analytical asymptotic solution 
@@
 We consider the following scenarios:
-\subsubsection{Ion-exchanger \cite{yariv2010migration}}
-We assume high conductance of the particle (yielding a uniform electric potential),
+\subsubsection{Ion-exchanger}
+We follow the microscale model presented at \cite{yariv2010migration}
+and assume high conductance of the particle (yielding a uniform electric potential),
 zero slip, anion impermeability, cation selectivity 
@@
 
-\subsubsection{Inert particle \cite{schnitzer2012surface}}
-We assume constant surface charge
+\subsubsection{Inert particle}
+We follow the microscale model presented at \cite{schnitzer2012surface}
+and assume constant surface charge
 zero slip and ion impermeability:
@@
 The Nernst-Planck equations above \eqref{eq:fluxes} for the fluid bulk outside
-the boundary layer, using bulk variables denoted by uppercase letters, read:
+the boundary layer \cite{yariv2010asymptotic}, 
+using bulk variables denoted by uppercase letters, read:
 \begin{equation} \begin{array}{cccc} \label{eq:bulk_flux}
@@
 the effective boundary conditions at the particle surface are:
-\subsubsection{Ion-exchanger} See \cite{yariv2010migration} for full derivation:
+\subsubsection{Ion-exchanger} See \cite{yariv2010migration} for full derivation
+of the nonlinear effective boundary conditions:
 \begin{equation}
@@
 \subsubsection{Highly charged inert particle}
-See \cite{schnitzer2012surface} for full derivation:
+See \cite{schnitzer2012surface} for full derivation
+of the nonlinear effective boundary conditions:
 \begin{equation} \label{eq:ephor_bnd}
@@
 \section{Asymptotic Analysis} \label{sec:asymp}
-In order to validate the numerical results, an asymptotic analysis is applied 
+In order to validate the numerical results, an asymptotic analysis has been applied 
 to the nonlinear systems of ion-exchanger migration 
@@
 and the asymptotic analysis for the electrophoresis case \cite{schnitzer2012surface}
-appears in \cite{schnitzer2012cubic}.
+is derived by Schnitzer and Yariv at \cite{schnitzer2012cubic}.
 
@@
 
-The cubic solution satisfies the ${r\rightarrow\infty}$ boundary conditions, 
-when $\alpha\cU_1 = 0$.
+The cubic solution satisfies the boundary conditions only when $\alpha\cU_1 = 0$,
+due to boundary conditions mismatch for $C$ at $r \rightarrow \infty$, when
+the diffusion and the advection terms become of the same order of magnitude.
 
@@
     \begin{center}
-	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/N_0.9000_0.1000.eps}
-	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/A_0.9000_0.1000.eps}
-	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/N_0.9000_0.1995.eps}
-	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/A_0.9000_0.1995.eps}
-	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/N_0.9000_0.3981.eps}
-	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/A_0.9000_0.3981.eps}
+	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/N1.eps}
+	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/A1.eps}
+	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/N2.eps}
+	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/A2.eps}
+	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/N5.eps}
+	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/A5.eps}
+	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/N10.eps}
+	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/A10.eps}
         \caption{Streamlines of the flow for various electric field $\beta$ values: 

### 2012-11-12 notes/thesis-latex-template/hebrewPart.tex
Refactor thesis into proper LaTeX template.

\authorHebrew{השם שלך}

\titleHebrew{כותרת התזה}

\supervisorHebrew{המחקר נעשה בהנחיית פרופ'/דר' )פרטי( )משפחה( בפקולטה למדעי המחשב.}

\personalThanksHebrew{תודות אישיות למנחים ולאחרים}

\financialThanksHebrew{
אני מודה לטכניון )ולגוף שנתן מלגה אם קבלת( על התמיכה הכספית הנדיבה בהשתלמותי.
}

\JewishDateHebrew{תשרי ה'תשס"ט}

\GregorianDateHebrew{אוקטובר \beginL2008\endL}

\maketitleHebrew

% 1000-2000 words
\abstractHebrew

צריך לכתוב את התקציר בעברית

\finishedHebrew

### 2012-11-12 notes/thesis-latex-template/thesis.tex
Refactor thesis into proper LaTeX template.

--- 2012-10-17 notes/thesis/main.tex
@@
-\documentclass[11pt,reqno]{article}
+% options are:
+% PhD, MSc (choose one)
+% beforeExam (to make the personal thanks invisible)
+\documentclass[MSc,beforeExam]{iitcsthesis}
 
@@
 \usepackage{url}
+\usepackage{longtable}
 
@@
 
-\setlength{\textheight}{8.7in}
-\setlength{\columnsep}{2.0pc}
-\setlength{\textwidth}{6.6in}
-% \setlength{\footheight}{0.2in}
-\setlength{\topmargin}{0.05in}
-\setlength{\headheight}{0.2in}
-\setlength{\headsep}{0.1in}
-\setlength{\evensidemargin}{0in}
-\setlength{\oddsidemargin}{0in}
-% \setlength{\parindent}{1pc}
-\setlength{\parindent}{0.0 in}
-\setlength{\parskip}{0.1 in}
-
-\title{Asymptotic and Numerical Solution for Electrokinetic Flow Around a Spherical Particle}
-\author{Roman Zeyde \\ \\  {Advisor: Prof. Irad Yavneh} } \date{}
-
-%%%%%%%%%%%%%%%
+% For some reason, the hebrew package clashes with the amsthm package. If you need a proof environment, you can uncomment the following:
+%\usepackage{amssymb} %Needed for \blacksquare. Take care not to add this package twice...
+%\newenvironment{proof}[1][Proof]{\par \textbf{#1.} }{\hspace{10pt}\hfill$\blacksquare$\par}
 \begin{document}
-%%%%%%%%%%%%%%%%
-
-\maketitle
-
-\begin{abstract}
-A numerical framework for the simulation of electrokinetic 
+
+\authorEnglish{Roman Zeyde}
+
+\titleEnglish{Computational Electrokinetics}
+
+\supervisorEnglish{The research thesis was done under the supervision
+of Prof. Irad Yavneh in the Computer Science Department.}
+
+\GregorianDateEnglish{XXXX 2012}
+\JewishDateEnglish{YYYY 5773}
+
+\personalThanksEnglish{Write thanks to professor and others}
+\financialThanksEnglish{The generous financial support of the Technion is gratefully acknowledged.}
+
+\maketitleEnglish
+
+% The English abstract should be 200-500 words long.
+\abstractEnglish
+In this work we study the electrokinetic 
 migration of particles in an electrolyte solution 
-due to the application of an external electric field is presented.
-The electrokinetic transport process is
-described by a system of nonlinear partial differential equations (PDE).
-A thin boundary layer forms around the particle due to strong electrostatic forces. The resulting
-scale disparity of the boundary layer
-is used to derive nonlinear effective boundary conditions for the
-numerical solver
-using the specific chemical properties of the particle.
-The nonlinear system is discretized and an iterative Newton solver is
-constructed automatically from the discrete equations and boundary 
-conditions.
+due to the application of an external electric field,
+and propose a numerical framework for iterative solution of such problems.
+The electrokinetic transport process can be used for
+transporting and manipulating micro- and nanoscale objects in 
+many nanotechnology applications, nano-fluidic devices, packed bed separation, 
+desalination processes and various electrophoresis applications.
+Due to strong electrostatic forces, a thin boundary layer forms near the particle
+surface. This results in scale disparity of the boundary layer, which hinders full numerical solution. 
+We employ nonlinear macroscale effective boundary conditions that are derived
+using the specific chemical properties of the particle
+(for an ion-exchanger particle at \cite{yariv2010migration}
+and for a surface charged inert particle at \cite{schnitzer2012surface}).
+The resulting macroscale nonlinear partial differential system 
+is discretized and an iterative Newton solver is
+constructed automatically from the discrete equations.
+Numerical results are obtained for an ion-exchanger and 
+for a surface charged inert particle. 
 An asymptotic analytical solution is 
-derived for the validation of the solver. 
-Numerical results are obtained for an ion-exchanger and 
-for a surface charged inert particle. The numerical results 
-are compared to the asymptotic solutions, and good correspondence is achieved.
-\end{abstract}
-
-\newpage
-\tableofcontents
-\newpage
-
-\section{Introduction} \label{sec:intro}
-
+used for the validation of the solver. 
+The numerical results are compared to the asymptotic solutions, 
+and good correspondence is achieved.
+
+\abbreviationsAndNotationsEnglish
+
+\begin{longtable}{lcl}
+$\varPhi$ 	& --- & Electric potential \\
+$C$ 		& --- & Ionic concentration \\
+$\bV$		& --- & Fluid velocity \\
+$P$			& --- & Fluid pressure \\
+$\tT$		& --- & Stress tensor \\
+$\bF$		& --- & Force vector \\
+$\bnhat$	& --- & Surface normal \\
+$\cO$ 		& --- & Operator \\
+$\beta$		& --- & Dimensionless electric field magnitude \\
+$\delta$	& --- & Dimensionless Debye layer width \\
+$\cU$		& --- & Dimensionless steady-state velocity 
+\end{longtable}
+
+%Or, if your tables are long, ``\usepackage{longtable}'' at the beginning, and then  ``\begin{longtable}[l]{lcl} ... \end{longtable}''
+
+\chapter{Introduction}
+
+\section{The Physical Problem}
 Electrokinetic theory describes the dynamics of charged particles
@@
 dynamics can be derived \cite{yariv2010asymptotic}.
-\begin{figure}[htbp]
+\begin{figure}
     \begin{center}
-        \includegraphics[width=0.35\textwidth]
+        \includegraphics[width=0.4\textwidth]
             {figs/debye.eps}
-        \caption{Schematic structure of the double layer:
+        \caption[Schematic structure of the double layer]{
+        Schematic structure of the double layer:
         (1) charged particle surface, (2) Debye layer, (3) fluid bulk.
@@
 
-The goal of this work is to develop and implement a software toolbox for the generation
-of iterative numerical solvers for nonlinear electrokinetic problems, and to apply it to the study
-of systems that have no closed-form solutions, such as ion-exchanger migration
-\cite{yariv2010migration} and the electrophoresis problem \cite{schnitzer2012surface}.
-This solver can be used to gain insight into the chemical and physical behavior 
-in far more general regimes than are currently well-understood, 
-and also to possibly lead to further analytical developments, based on new scaling behavior
-discovered numerically. We may also target interesting physical
+The goal of this work is to develop and implement a software toolbox 
+for the generation of iterative numerical solvers for nonlinear macroscale 
+electrokinetic problems, and to apply it to the study
+of systems that have no closed-form solutions, 
+such as ion-exchanger migration \cite{yariv2010migration} 
+and the electrophoresis problem \cite{schnitzer2012surface}.
+This solver can be used to gain insight into the chemical 
+and physical behavior in far more general regimes than 
+are currently well-understood, 
+and also to possibly lead to further analytical developments, 
+based on new scaling behavior
+discovered numerically. 
+We may also target interesting physical
 phenomena that have been observed experimentally.
 One such phenomenon is nonlinear electrokinetic vortex flow, 
-which is useful for microfluidic mixing applications \cite{wang2004mix, ben2002vortex},
-
-The paper is structured as follows: the governing equations of the electrokinetic model
-are derived in Section \ref{sec:equations}. The algorithm for the discretization and 
-the solution of the system is described in Section \ref{sec:algorithm}.
-An analytical asymptotic solution for the nonlinear system is derived 
-and presented in Section \ref{sec:asymp}.
-Numerical results and their comparison to an analytical asymptotic solution 
-are presented Section \ref{sec:results} and discussed in Section \ref{sec:discussion}.
+which is useful for microfluidic mixing applications 
+\cite{wang2004mix, ben2002vortex}.
 
@@
 \subsubsection{Ion-exchanger}
-Following \cite{yariv2010migration}, we assume high conductance of the particle (yielding a uniform electric potential),
+We follow the microscale model presented at \cite{yariv2010migration}
+and assume high conductance of the particle (yielding a uniform electric potential),
 zero slip, anion impermeability, cation selectivity 
@@
 \subsubsection{Inert particle}
-Following \cite{schnitzer2012surface}, we assume constant surface charge
+We follow the microscale model presented at \cite{schnitzer2012surface}
+and assume constant surface charge
 zero slip and ion impermeability:
@@
 the effective boundary conditions at the particle surface are:
-\subsubsection{Ion-exchanger} See Appendix \ref{append:slip} for full derivation:
-\begin{equation}
-\begin{array}{ccc}
+\subsubsection{Ion-exchanger} See \cite{yariv2010migration} for full derivation
+of the nonlinear effective boundary conditions (and also Appendix \ref{append:slip}):
+\begin{align}
 \label{eq:ionex_bnd}
-0 = \varPhi + \log C, &
-0 = \deriv{}{n} \pars{\varPhi - \log C}, &
-\bV = 
+\nonumber 
+0 &= \varPhi + \log C, \\
+0 &= \deriv{}{n} \pars{\varPhi - \log C}, \\
+\nonumber \bV &= 
 \zeta \cdot \bnabla_\mathcal{S} \varPhi 
 + 2\log\pars{1-\tanh^2\frac{\zeta}{4}} \cdot \bnabla_\mathcal{S} \log C,
-\end{array}\end{equation}
+\end{align}
 where $\zeta = \cV - \varPhi = \log (C / \gamma)$ 
@@
 \subsubsection{Highly charged inert particle}
-See \cite{schnitzer2012surface} for full derivation:
-\begin{equation} \label{eq:ephor_bnd}
-\begin{array}{ccc}
-0 = {\deriv{C}{n} - \text{Du} \nabla^2_s \pars{\varPhi - \log C}}, & 
-0 = {\deriv{C}{n} + C \deriv{\varPhi}{n}}, &
-\bV = \zeta \cdot \bnabla_\mathcal{S} \pars{\varPhi - \log C} +
+See \cite{schnitzer2012surface} for full derivation
+of the nonlinear effective boundary conditions. 
+Note that due to surface conduction, the resulting boundary conditions are:
+\begin{align} \label{eq:ephor_bnd}
+\nonumber
+0 &= {\deriv{C}{n} - \text{Du} \nabla^2_s \pars{\varPhi - \log C}}, \\
+0 &= {\deriv{C}{n} + C \deriv{\varPhi}{n}}, \\
+\nonumber
+\bV &= \zeta \cdot \bnabla_\mathcal{S} \pars{\varPhi - \log C} +
 4 \log 2 \cdot \bnabla_\mathcal{S} \log C,
-\end{array}\end{equation}
+\end{align}
 where $\zeta = \bar{\zeta} - \log C$ 
@@
 
-\subsection{Steady state}
+\subsection{Steady-state velocity}
 The stress tensor in the fluid is composed of Newtonian and Maxwel stresses:
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Work Outline}
+
+The work is structured as follows: 
+The numerical scheme for the discretization and 
+the solution of the system is described in Chapter \ref{ch:algorithm}.
+Numerical results and their comparison to the analytical asymptotic solutions 
+are presented and discussed in Chapter \ref{ch:results}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+\chapter{Numerical Scheme} \label{ch:algorithm}
+
+\section{Numerical Framework}
+
 \section{Algorithm Description} \label{sec:algorithm}
@@
 \begin{align}
-\bnabla f = \deriv{f}{r}\brhat + \frac{1}{r}\deriv{f}{\theta}\bthetahat, &
-\bnabla \cdot \bF = \frac{1}{r^2}\deriv{}{r}\pars{F_r r^2 } + 
+\bnabla f &= \deriv{f}{r}\brhat + \frac{1}{r}\deriv{f}{\theta}\bthetahat, \\
+\bnabla \cdot \bF &= \frac{1}{r^2}\deriv{}{r}\pars{F_r r^2 } + 
                \frac{1}{r \sin\theta}\deriv{}{\theta}\pars{F_\theta \sin\theta}.
@@
 \begin{align}
+\nonumber
 \bnabla \bF &= \deriv{F_r}{r} \brhat \brhat + \deriv{F_\theta}{r} \brhat \bthetahat + 
 \frac{1}{r}\pars{\deriv{F_r}{\theta} - F_\theta} \bthetahat \brhat + 
-\frac{1}{r}\pars{\deriv{F_\theta}{\theta} + F_r} \bthetahat \bthetahat, \\
-\bLaplacian \bF &= 
-\left(\Laplacian F_r - \frac{2F_r}{r^2} - 
-\frac{2}{r^2 \sin\theta} \deriv{\left(F_\theta \sin\theta \right)}{\theta}\right)\brhat
-+ \left(\Laplacian F_\theta - \frac{F_\theta}{r^2 \sin^2\theta} + 
-\frac{2}{r^2}\deriv{F_r}{\theta}\right) \bthetahat.
+\frac{1}{r}\pars{\deriv{F_\theta}{\theta} + F_r} \bthetahat \bthetahat, 
+\\
+\brhat \cdot \bLaplacian \bF &=
+\Laplacian F_r - \frac{2F_r}{r^2} - 
+\frac{2}{r^2 \sin\theta} \deriv{\left(F_\theta \sin\theta \right)}{\theta}
+\\
+\nonumber
+\bthetahat \cdot \bLaplacian \bF &= 
+\Laplacian F_\theta - \frac{F_\theta}{r^2 \sin^2\theta} + 
+\frac{2}{r^2}\deriv{F_r}{\theta}.
 \end{align}
@@
 \begin{align} \label{eq:grid}
-(r_i,\theta_j) \in [1, \infty) \times [0,\pi], & 
-r_i = (1+\Delta_r)^i, &
- \theta_j = \Delta_\theta \cdot j,
+\nonumber
+(r_i,\theta_j) &\in [1, \infty) \times [0,\pi], \\ 
+r_i &= (1+\Delta_r)^i, \\
+\nonumber
+\theta_j &= \Delta_\theta \cdot j,
 \end{align}
@@
 \begin{align}
-\Omega_{ij} = [r_{i-1}, r_{i}] \times [\theta_{j-1}, \theta_{j}], &
-\bar{r}_i = (r_{i-1} + r_{i})/2, &
-\bar{\theta}_j = (\theta_{j-1} + \theta_{j})/2.
+\nonumber
+\Omega_{ij} &= [r_{i-1}, r_{i}] \times [\theta_{j-1}, \theta_{j}], \\
+\bar{r}_i &= (r_{i-1} + r_{i})/2, \\
+\nonumber
+\bar{\theta}_j &= (\theta_{j-1} + \theta_{j})/2.
 \end{align}
@@
 boundaries, using a staggered grid:
-\begin{equation}
-\begin{array}{ccccc}
-\varPhi^h_{[i,j]} = \varPhi(\bar{r}_i, \bar{\theta}_j), &
-C^h_{[i,j]} = C(\bar{r}_i, \bar{\theta}_j), &
-P^h_{[i,j]} = P(\bar{r}_i, \bar{\theta}_j). &
-V_r^h{}_{[i,j]} = V_r(r_i, \bar{\theta}_j), &
-V_\theta^h{}_{[i,j]} = V_\theta(\bar{r}_i, {\theta}_j).
-\end{array}
-\end{equation}
+\begin{align}
+\nonumber \varPhi^h_{[i,j]} &= \varPhi(\bar{r}_i, \bar{\theta}_j), \\
+\nonumber C^h_{[i,j]} &= C(\bar{r}_i, \bar{\theta}_j), \\
+P^h_{[i,j]} &= P(\bar{r}_i, \bar{\theta}_j), \\
+\nonumber V_r^h{}_{[i,j]} &= V_r(r_i, \bar{\theta}_j), \\
+\nonumber V_\theta^h{}_{[i,j]} &= V_\theta(\bar{r}_i, {\theta}_j).
+\end{align}
 
@@
     \begin{center}
-	\includegraphics[width=1\textwidth]{figs/grids.eps}
-        \caption{Computational Grid.}
+	\includegraphics[width=0.8\textwidth]{figs/grids.eps}
+        \caption[Computational grid]{The computational grid is defined using
+        spherical coordinates system, due to axisymmetry of the physical problem
+        and boundary conditions discretization on the particle surface.}
     \label{fig:grids}
@@
 \cD_r(f^h){}_{\left[i+\half,j\right]} = \frac{f^h_{\left[i+1,j\right]} - f^h_{\left[i,j\right]}}
-                       {r_{\left[i+1,j\right]} - r_{\left[i,j\right]}}, &
+                       {r_{\left[i+1,j\right]} - r_{\left[i,j\right]}}, \\
 \cD_\theta(f^h){}_{\left[i,j+\half\right]} = \frac{f^h_{\left[i,j+1\right]} - f^h_{\left[i,j\right]}}
@@
 \begin{align} \label{eq:disc_interp}
-\begin{array}{rcl}
-\cI_r(f^h)_{\left[i+\half,j\right]} &= 
+\cI_r(f^h)_{\left[i+\half,j\right]} = 
 \frac{r_{\left[i+\half,j\right]} - r_{\left[i,j\right]}}
@@
 \\
-\cI_\theta(f^h)_{\left[i,j+\half\right]} &= 
+\cI_\theta(f^h)_{\left[i,j+\half\right]} =
 \frac{r_{\left[i,j+\half\right]} - r_{\left[i,j\right]}}
@@
   f^h_{\left[i,j\right]}.
-\end{array}
 \end{align}
@@
 then using \eqref{eq:disc_diff}, we have
-\begin{align}
+\begin{eqnarray}
 \frac{1}{r^2} \cD_r\pars{f^h_r r^2} + 
-\frac{1}{r \sin\theta} \cD_\theta\pars{f^h_\theta \sin\theta} =
-\frac{\cD_r\pars{f^h_r \cdot r^2 \sin\theta} + 
-\cD_\theta\pars{f^h_\theta \cdot r \sin\theta}}{r^2 \sin\theta} = 0. 
-\end{align}
+\frac{1}{r \sin\theta} \cD_\theta\pars{f^h_\theta \sin\theta} = 0. 
+\end{eqnarray}
 
@@
 using \eqref{eq:disc_diff} and \eqref{eq:disc_interp}:
-\begin{align} \nonumber
-I^h_r = -\cI_r(C^h) \cdot \cD_r(\varPhi^h), &
+\begin{align} 
+\nonumber
+I^h_r = -\cI_r(C^h) \cdot \cD_r(\varPhi^h), \\
+\nonumber
 I^h_\theta = -\cI_\theta(C^h) \cdot \frac{\cD_\theta(\varPhi^h)}{r}, \\
-J^h_r = -\cD_r(C^h) + \alpha V^h_r \cdot \mathcal{U}^{\bV^h}_r (C^h), &
+\nonumber
+J^h_r = -\cD_r(C^h) + \alpha V^h_r \cdot \mathcal{U}^{\bV^h}_r (C^h), \\
 J^h_\theta = -\frac{\cD_\theta(C^h)}{r} + \alpha V^h_\theta \cdot \mathcal{U}^{\bV^h}_\theta (C^h), 
 \\ \nonumber
- \mathcal{U}^{\bV^h}_r(C^h)[i,j] = C^h\left[i-\frac{\sign(V^h_r)}{2}, j\right], &
+ \mathcal{U}^{\bV^h}_r(C^h)[i,j] = C^h\left[i-\frac{\sign(V^h_r)}{2}, j\right], 
+\\ \nonumber
  \mathcal{U}^{\bV^h}_\theta(C^h)[i,j] = C^h\left[i, j-\frac{\sign(V^h_\theta)}{2}\right]. 
@@
 Force components ($\bF = -\bnabla P + \bLaplacian \bV + \bnabla \varPhi \Laplacian \varPhi$) 
-are discretized on the staggered velocity grid, where
-linear interpolation is used for the Coulomb force and for vector Laplacian components.
+are discretized on the staggered velocity grid using finite difference
+method, where linear interpolation is used for the Coulomb force and 
+for vector Laplacian components.
 \begin{align}
@@
           + \cD_r(\varPhi^h) \cdot \cI_r(\cL(\varPhi^h)), \\
+\nonumber
 F^h_\theta &= -\frac{\cD_\theta(P^h)}{r} 
@@
 		  + \frac{\cD_\theta(\varPhi^h)}{r} \cdot \cI_\theta(\cL(\varPhi^h)), \\
-\nonumber
 \cL(f^h) &= \frac{1}{r^2}\cD_r\pars{\cD_r(f^h) r^2} + 
@@
 \begin{array}{rcl}
-0 &= \cI_r(\varPhi^h + \log C^h), \\
-0 &= \cD_r(\varPhi^h - \log C^h), \\
-V^h_r &= 0, \\
-V^h_\theta &= 4\log\pars{\frac{1}{2}\pars{1 + \exp\left\{\cI_\theta(\zeta^h)/2\right\}}} \cdot 
+0 &=& \cI_r(\varPhi^h + \log C^h), \\
+0 &=& \cD_r(\varPhi^h - \log C^h), \\
+V^h_r &=& 0, \\
+V^h_\theta &=& 4\log\pars{\frac{1}{2}\pars{1 + \exp\left\{\cI_\theta(\zeta^h)/2\right\}}} \cdot 
 			\cD_\theta(\zeta^h), \\
-  \zeta^h &= - \log \gamma - \cI_r(\varPhi^h).
+  \zeta^h &=& - \log \gamma - \cI_r(\varPhi^h).
 \end{array}
@@
 \begin{array}{rcl}
-0 &= \cD_r(C^h) - \text{Du} \cdot 
+0 &=& \cD_r(C^h) - \text{Du} \cdot 
 \pars{\cD_\theta \pars{\sin\theta \cdot \cD_\theta \cI_r\pars{\varPhi^h - \log C}}}/{\sin\theta}, \\
-0 &= \cD_r(C^h) + \cI_r(C^h) \cD_r(\varPhi^h), \\
-V^h_r &= 0, \\
-V^h_\theta &= \cI_\theta(\zeta^h) \cdot \cD_\theta(\cI_r \varPhi^h - \log \cI_r C^h) + 
+0 &=& \cD_r(C^h) + \cI_r(C^h) \cD_r(\varPhi^h), \\
+V^h_r &=& 0, \\
+V^h_\theta &=& \cI_\theta(\zeta^h) \cdot \cD_\theta(\cI_r \varPhi^h - \log \cI_r C^h) + 
 4 \log 2 \cdot \cD_\theta(\log \cI_r C^h), \\
-  \zeta^h &= \bar{\zeta} - \log \cI_r C.
+  \zeta^h &=& \bar{\zeta} - \log \cI_r C.
 \end{array}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Solver Design}
+\section{Solver Design}
 An operator $\cO$ is defined by its input vector $\bx$ and its output 
@@
 
-\subsubsection{Operator Representation}
+\subsection{Operator Representation}
 System variable $\bx$ is defined as the concatenation $\bx = [\,\varPhi, C, V_r, V_\theta, P\,]$.
@@
 
-\subsubsection{Steady-state}
+\subsection{Steady-state}
 Let $\beta$ be a given nondimensional electric field.
@@
 aligned with $\ui$ and it vanishes iff $\ui \cdot \bF = 0$.
-\begin{align} \nonumber
-F_\imath = \ui \cdot \bF &= 
+\begin{eqnarray} \nonumber
+F_\imath = \ui \cdot \bF &=& 
 \oint_\mathcal{S} \pars{\ui \cdot \tT \cdot \bnhat} dA = 
@@
 \\  
-f_\imath = \ui \cdot \tT \cdot \brhat &= \pars{-P + 2\cD_r(V_r) + 
+f_\imath = \ui \cdot \tT \cdot \brhat &=& \pars{-P + 2\cD_r(V_r) + 
 \frac{1}{2}\pars{\cD_r(\varPhi)}^2 - \frac{1}{2r^2}\pars{\cD_\theta(\varPhi)}^2}\cos\theta 
@@
 + \frac{1}{r}\cD_r(\varPhi) \cD_{\theta}(\varPhi)}\sin\theta.
-\end{align}
+\end{eqnarray}
 
@@
 
-\subsubsection{Continuation}
+\subsection{Continuation}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Solver Implementation}
+\section{Solver Implementation}
 
@@
 
-\subsubsection{Operator Interface}
+\subsection{Operator Interface}
 The base \verb|Operator| interface is defined by 
@@
 
-\paragraph{\textit{Linear operator}}
+\subsubsection{Linear operator}
 If $\cO$ is linear, it can be represented by a matrix $L$, such that:
@@
 
-\paragraph{\textit{Pointwise scalar function}}
+\subsubsection{Pointwise scalar function}
 Let $f: \R \rightarrow \R$ be a differentiable 1D function, whose derivative is
@@
 
-\paragraph{\textit{Constant value}}
+\subsubsection{Constant value}
 A constant operator $\mathcal{C}$ is defined by constant vector $\bc$ 
@@
 
-\paragraph{\textit{Binary operators}}
+\subsubsection{Binary operators}
 Let $\cO_1$ and $\cO_2$ be two operators, so their pointwise addition, subtraction,
@@
 \end{array}\end{equation}
-\paragraph{\textit{N-ary operators}}
+\subsubsection{N-ary operators}
 Given $N$ operators $\{\cO_i\}_{i=1}^N$, their concatenation $\cO$ is defined as:
@@
 
-\subsubsection{Handling the Singularity} \label{sec:singular}
+\subsection{Handling the Singularity} \label{sec:singular}
 The electric potential $\varPhi$ (in electrophoresis case) and the pressure $P$ (in both cases) 
@@
 
-\subsubsection{Iterative Newton solver}
+\subsection{Iterative Newton solver}
 Given an initial solution $\bx_0$ and prescribed values for $\beta$ and $\cU$, 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\chapter{Results and Discussion} \label{ch:results}
+
 \section{Asymptotic Analysis} \label{sec:asymp}
-In order to validate the numerical results, an asymptotic analysis is applied 
+In order to validate the numerical results, an asymptotic analysis has been applied 
 to the nonlinear systems of ion-exchanger migration 
@@
 
-\begin{align}
+\begin{align*}
 \varPhi_3 &= \frac{15\cU_1\alpha + 6 }{64}\cos\theta  - \frac{3 \cU_1\alpha}{32} {\cos}^3\theta
@@
 + \frac{3 \cos\theta \left(5 \cU_1\alpha - 6 {\cos^2\theta} - 4 \cU_1\alpha {\cos^2\theta} + 4\right)}{64 r^3} + \frac{\left(2 \cU_1\alpha - 1\right) \left(\cos\theta - 3 {\cos}^3\theta\right)}{64 r^5}
-+ {{\cos}^3\theta \left(\frac{15 \cU_1\alpha}{64} + \frac{3}{32}\right)}{r^{-2}} 
+\\ &+ {{\cos}^3\theta \left(\frac{15 \cU_1\alpha}{64} + \frac{3}{32}\right)}{r^{-2}} 
+- \left(3 \cos\theta - 5 {\cos}^3\theta\right) \left( - \frac{19 {\cU_1}^2\alpha^2}{5120} + \frac{97 \cU_1\alpha}{5120} + \frac{3 \cU_2\alpha}{320} + \frac{21}{1280}\right){r^{-4}} 
 \\ \nonumber &
-- \left(3 \cos\theta - 5 {\cos}^3\theta\right) \left( - \frac{19 {\cU_1}^2\alpha^2}{5120} + \frac{97 \cU_1\alpha}{5120} + \frac{3 \cU_2\alpha}{320} + \frac{21}{1280}\right){r^{-4}} 
-% \\ \nonumber &
 + {{\cos}^3\theta \left(\frac{\cU_1\alpha}{64} + \frac{3}{64}\right)}{r^{-6}},
-\end{align}
-\begin{align}
+\end{align*}
+\begin{align*}
 C_3 &=
@@
 - {\left(3 \cos\theta - 5 {\cos^3\theta}\right) \left(\frac{59 {{\cU_1}}^2\alpha^2}{5120} + \frac{103 {\cU_1}\alpha}{5120} + \frac{69 {\cU_2}\alpha}{320} + \frac{3}{1280}\right)}{r^{-4}} 
+\\ \nonumber &
 + \frac{\alpha \left(\cos\theta - 3 {\cos^3\theta}\right) \left(5\alpha {{\cU_1}}^2 + 2 {\cU_1} + 16 {\cU_2}\right)}{128 r^5} 
@@
 - \frac{3\alpha \cos\theta \left( - 8\alpha {{\cU_1}}^2 {\cos^2\theta} + 7\alpha {{\cU_1}}^2 + 2 {\cU_1} + 32 {\cU_2} {\cos^2\theta} - 32 {\cU_2}\right)}{128 r^3} 
-%\\ \nonumber &
+\\ \nonumber &
 + \frac{{{\cU_1}}^2\alpha^2 {\cos^3\theta}}{32 r^6} - \frac{3 {\cU_1}\alpha {\cos^3\theta} \left(5 {\cU_1}\alpha + 2\right)}{64 r^2},
-\end{align}
-\begin{align}
+\end{align*}
+\begin{align*}
 \Psi_3 &=
@@
 %\\ \nonumber & 
-\frac{4 {\sin^2\theta} - 5 {\sin^4\theta}}{r^3} + \left(\frac{{\cU_1}\alpha}{16} - \frac{1}{8}\right) \frac{2 r^3 - 3 r^2 + 1}{4 r} {\sin^2\theta},
-\end{align}
-\begin{align}
+\frac{4 {\sin^2\theta} - 5 {\sin^4\theta}}{r^3} \\ & + \left(\frac{{\cU_1}\alpha}{16} - \frac{1}{8}\right) \frac{2 r^3 - 3 r^2 + 1}{4 r} {\sin^2\theta},
+\end{align*}
+\begin{align*}
 \cW_1 &= \frac{69}{512 \left(\sqrt{\gamma} + 1\right)} - \frac{1407\alpha^2 {\log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}^3}{1280} - \frac{123 \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{1280} - \frac{27}{512 {\left(\sqrt{\gamma} + 1\right)}^2}
--\frac{1899\alpha {\log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}^2}{2560} 
-\\ \nonumber & 
+\\ & -\frac{1899\alpha {\log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}^2}{2560} 
 - \frac{\alpha \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right) \left(\frac{81}{16 \left(\sqrt{\gamma} + 1\right)} - \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right) \left(\frac{27\alpha \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{4} + \frac{27}{8}\right)\right)}{320}
-+ \frac{21\alpha \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{128 \left(\sqrt{\gamma} + 1\right)},
-\end{align}
-\begin{align}
+\\ & + \frac{21\alpha \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{128 \left(\sqrt{\gamma} + 1\right)},
+\end{align*}
+\begin{align*}
 \cW_2 &= \frac{9 \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right)}{256} 
@@
 - \frac{27}{512 {\left(\sqrt{\gamma} + 1\right)}^2}
-%\\ \nonumber &
+\\ \nonumber &
 - \frac{297\alpha \log\left(\frac{\sqrt{\gamma} + 1}{2 \sqrt{\gamma}}\right) + 54}{1024 \left(\sqrt{\gamma} + 1\right)}.
-\end{align}
-
-The cubic solution satisfies the ${r\rightarrow\infty}$ boundary conditions, 
-when $\alpha\cU_1 = 0$.
+\end{align*}
+
+The cubic solution satisfies the boundary conditions only when $\alpha\cU_1 = 0$,
+due to boundary conditions mismatch for $C$ at $r \rightarrow \infty$, when
+the diffusion and the advection terms become of the same order of magnitude.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Numerical Results} \label{sec:results}
@@
 as demonstrated by the numerical solution and the asymptotic analysis results 
-in Figure \ref{fig:Vortex}.
+in Figures \ref{fig:Vortex1} and \ref{fig:Vortex2}.
+Note that there is a good correspondence between the numerical
+results and the analytical solution for $\beta < 1$, validating
+the vortex formation.
 
@@
 The results of the extrapolation and $\hat\cU$ the analytical results 
-are given at Figure \ref{fig:Electrophoresis}.
+are given at Figures \ref{fig:Electrophoresis1} and \ref{fig:Electrophoresis2}.
 The numerical solver uses $R_{\max} = 10^2$,
@@
 
-Future work may include replacing the full Newton step by an iterative linear solver, allowing
-finer grids to be used.
+\section{Future Work}
+Future work may include replacing the full Newton step by an iterative linear solver
+(e.g. using preconditioned Krylov subspace methods \cite{saad2003book} or
+Multigrid), allowing finer grids to be used.
 Since it is expected that a boundary layer should form around the particle for $\beta \gg 1$,
 a numerical solver should be able to handle large grids to achieve good numeric accuracy.
-In addition, the framework may be used for automatic Newton solver construction for 
-other similar nonlinear PDE systems.
-
-\begin{figure}[htbp]
+
+In addition, the framework may be used for automatic construction of Newton solvers 
+for other nonlinear PDE systems, for example -- for particle with different surface 
+properties, or different particle shape.
+
+\begin{figure}
     \begin{center}
-    \includegraphics[width=0.4\textwidth]{figs/Cubic/ionex_cubic1.eps}
-    \includegraphics[width=0.4\textwidth]{figs/Cubic/ionex_cubic2.eps}
-        \caption{Steady-state velocity $\cU$ as a function of the 
-        electric field magnitude $\beta$, for $\gamma < 1$ (left) and $\gamma > 1$ (right). 
+    \includegraphics[width=0.8\textwidth]{figs/Cubic/ionex_cubic1.eps}
+    \includegraphics[width=0.8\textwidth]{figs/Cubic/ionex_cubic2.eps}
+        \caption[Ion exchanger steady-state velocity]{
+        Steady-state velocity $\cU$ as a function of the 
+        electric field magnitude $\beta$, for $\gamma < 1$ (top) and $\gamma > 1$ (bottom). 
         The analytic cubic solution \eqref{eq:cubic} is represented by curves
@@
 
-\begin{figure}[htbp]
+\begin{figure}
     \begin{center}
-	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/N_0.9000_0.1000.eps}
-	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/A_0.9000_0.1000.eps}
-	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/N_0.9000_0.2000.eps}
-	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/A_0.9000_0.2000.eps}
-	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/N_0.9000_0.4000.eps}
-	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/A_0.9000_0.4000.eps}
-	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/N_0.9000_0.6000.eps}
-	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/A_0.9000_0.6000.eps}
-        \caption{Streamlines of the flow for various electric field $\beta$ values: 
-        numerical results (left) and analytical approximation (right) for
-        $\gamma = 0.9$.  The steady-state velocity $\cU$ is positive, so the
-        ion-exchanger drifts to the right. 
-        Note that there is a good correspondence between the numerical
-        results and the analytical solution for $\beta < 1$, validating
-        the vortex formation.
-        }
-    \label{fig:Vortex}
+	\includegraphics[width=0.8\textwidth]{figs/Cubic/Stream/N1.eps}
+	\includegraphics[width=0.8\textwidth]{figs/Cubic/Stream/N2.eps}
+	\includegraphics[width=0.8\textwidth]{figs/Cubic/Stream/N5.eps}
+	\includegraphics[width=0.8\textwidth]{figs/Cubic/Stream/N10.eps}
+        \caption[Ion exchanger streamlines -- numerical results]{
+        Streamlines of the flow for various electric field $\beta$ values: 
+        numerical results for $\gamma = 0.9$.  
+        The steady-state velocity $\cU$ is positive, so the
+        ion-exchanger drifts to the right. }
+    \label{fig:Vortex1}
     \end{center}
@@
 
-\begin{figure}[htbp]
+\begin{figure}
     \begin{center}
-    \includegraphics[width=0.4\textwidth]{figs/Electrophoresis/numerical_vs_analytical_alpha=0.5_Du=1.0_zeta=10.0_Rmax=100.eps}
-    \includegraphics[width=0.4\textwidth]{figs/Electrophoresis/departure_from_linear_alpha=0.5_Du=1.0_zeta=10.0_Rmax=100.eps}
-        \caption{Steady-state velocity $\cU$ as a function of the 
+	\includegraphics[width=0.8\textwidth]{figs/Cubic/Stream/A1.eps}
+	\includegraphics[width=0.8\textwidth]{figs/Cubic/Stream/A2.eps}
+	\includegraphics[width=0.8\textwidth]{figs/Cubic/Stream/A5.eps}
+	\includegraphics[width=0.8\textwidth]{figs/Cubic/Stream/A10.eps}
+        \caption[Ion exchanger streamlines -- analytical results]{
+        Streamlines of the flow for various electric field $\beta$ values: 
+        analytical approximation for $\gamma = 0.9$ (see Section \ref{sec:asymp}).
+        The steady-state velocity $\cU$ is positive, so the
+        ion-exchanger drifts to the right.}
+    \label{fig:Vortex2}
+    \end{center}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=0.6\textwidth]{figs/Electrophoresis/numerical_vs_analytical_alpha=0.0_Du=0.5_zeta=6.0_Rmax=100.eps}
+    \includegraphics[width=0.6\textwidth]{figs/Electrophoresis/departure_from_linear_alpha=0.0_Du=0.5_zeta=6.0_Rmax=100.eps}
+        \caption[Highly-charged surface particle steady-state velocity]{
+        Steady-state velocity $\cU$ as a function of the 
+        electric field magnitude $\beta$, for highly-charged surface particle
+        electrophoresis (with $\alpha = 0, \text{Du} = 0.5, \bar\zeta = 6$).
+        The analytic solution velocity is represented by solid lines, 
+        and the numerical results are represented by markers.
+        The top figure shows the full numerical solution 
+        compared to the analytical one \eqref{eq:cubic}, and
+        the bottom figure compares the analytic cubic correction \cite{schnitzer2012cubic} 
+        to the difference between the numerical results and the linear regime.}
+	    \label{fig:Electrophoresis1}
+    \end{center}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=0.6\textwidth]{figs/Electrophoresis/numerical_vs_analytical_alpha=0.5_Du=1.0_zeta=10.0_Rmax=100.eps}
+    \includegraphics[width=0.6\textwidth]{figs/Electrophoresis/departure_from_linear_alpha=0.5_Du=1.0_zeta=10.0_Rmax=100.eps}
+        \caption[Highly-charged surface particle steady-state velocity]{
+        Steady-state velocity $\cU$ as a function of the 
         electric field magnitude $\beta$, for highly-charged surface particle
@@
         and the numerical results are represented by markers.
-        The left figure shows the full numerical solution 
+        The top figure shows the full numerical solution 
         compared to the analytical one \eqref{eq:cubic}, and
-        the right figure compares the analytic cubic correction \cite{schnitzer2012cubic} 
+        the bottom figure compares the analytic cubic correction \cite{schnitzer2012cubic} 
         to the difference between the numerical results and the linear regime.
@@
         because higher-order terms become significant.}
-	    \label{fig:Electrophoresis}
+	    \label{fig:Electrophoresis2}
     \end{center}
@@
 
-\section*{Acknowledgments}
-The authors thank Prof. Ehud Yariv and Ory Schnitzer 
-for introducing us to this problem, 
-for the helpful discussions and valuable advice.
-
 \appendix
 
+\chapter{Effective Boundary Conditions} \label{append:slip}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Ion-exchanger effective boundary conditions } \label{append:slip}
-
-\subsection{Debye layer scaling}
+\section{Debye layer scaling}
 
@@
 
-\subsection{Ion Fluxes}
+\section{Ion Fluxes}
 
@@
 
-\subsection{Electric Potential}
+\section{Electric Potential}
 The leading-order Laplace equation in the Debye layer reads
@@
 \begin{align}
+\nonumber
 \log\tanh\frac{\psi}{4} - \log\tanh\frac{\zeta}{4} &= -\rho \sqrt{C}, \\
@@
 
-\subsection{Radial Momentum}
+\section{Radial Momentum}
 Leading-order $O(\delta^{-3})$ radial momentum balance in the Debye layer yields:
@@
 
-\subsection{Tangential Momentum}
+\section{Tangential Momentum}
 Leading-order $O(\delta^{-2})$ tangential momentum balance in the Debye layer yields:
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Differential operators in spherical coordinates} \label{append:spherical}
+\chapter{Differential operators in spherical coordinates} \label{append:spherical}
 
@@
 
-\subsection{Scalar Operators}
+\section{Scalar Operators}
 Scalar Laplacian derivation:
@@
 
-\subsection{Vector Operators}
+\section{Vector Operators}
 Vector gradient operator can be written by:
@@
 
+\clearpage
+\addcontentsline{toc}{chapter}{Bibliography}
+
 \bibliographystyle{unsrt}
-\bibliography{ijnam}
+\bibliography{thesis}
+
+%\include{hebrewPart}
+
+% Actually, I found it much easier to have each chapter in a file of its own. Except for the Hebrew part, I put it all together in this example just to make things clear.
 

### 2012-11-17 notes/thesis-latex-template/thesis.tex
Work on thesis.

@@
 \section{The Physical Problem}
+\subsection{Electrokinetic Phenomena}
 Electrokinetic theory describes the dynamics of charged particles
@@
 This interesting regime has not yet been explored extensively.
-Recently, it has been conceived that such type of dynamics
-can be very useful in transporting and manipulating micro-
-and nanoscale objects in many nanotechnology applications,
-nano-fluidic devices, packed bed separation, desalination processes 
-and various electrophoresis applications \cite{howse2007self,paxton2004catalytic,pumera2010electrochemically,nischang2007,leinweber2004}.
+
+\subsection{Applications}
+
+Recently, it has been conceived that such type of phenomena
+can be very useful in microfluidics
+devices and methods for controlling and manipulating fluid flows in micro- and nanoscale. 
+Many different components are used in microfluidics such as valves, pumps, sensors, mixers, 
+filters, separators, heaters etc., and are combined into lab-on-a-chip systems.
+
+The manipulation can be achieved by either applying the external field at inlets and outlets, or it can be applied locally in the microchannel by integrated components.
+A typical microchannel is produced with lithographic techniques. Normally the Reynolds
+number is very low (on the order of unity or smaller) which means that viscosity dominates
+and the convective term of the Navier–Stokes equations are insignificant. This means that
+microflows most often are laminar.
+
+In the last decade there has been an increase in microfluidics research, 
+due to the spread of tools for microfluidic systems fabrication, 
+production of cheap and portable devices for fast point-of-care analysis, 
+and fundamental research of physical, chemical and biological processes.
+Various applications are \cite{erickson2004integrated, squires2005microfluidics, hardt2007microfluidic}:
+\begin{enumerate}
+\item DNA and cell analysis \cite{horsman2007forensic, wu2004chemical}.
+\item Separation-based detection \cite{weinberger1993practical}.
+\item Microscale chemical processing \cite{kothare2006dynamics}.
+\item Packed bed separation \cite{leinweber2004, losey2001microfabricated}.
+\item Desalination processes \cite{kim2010direct}.
+\item Drug delivery \cite{santini2000microchips}.
+\end{enumerate}
+
 Because the nonlinear macroscale model for these electrokinetic
@@
 solver for this system is of importance.
-
-The goal of this work is to develop and implement a software toolbox 
-for the generation of iterative numerical solvers for nonlinear macroscale 
-electrokinetic problems, and to apply it to the study
-of systems that have no closed-form solutions, 
-such as ion-exchanger migration \cite{yariv2010migration} 
-and the electrophoresis problem \cite{schnitzer2012surface}.
-This solver can be used to gain insight into the chemical 
-and physical behavior in far more general regimes than 
-are currently well-understood, 
-and also to possibly lead to further analytical developments, 
-based on new scaling behavior
-discovered numerically. 
-We may also target interesting physical
-phenomena that have been observed experimentally.
-One such phenomenon is nonlinear electrokinetic vortex flow, 
-which is useful for microfluidic mixing applications 
-\cite{wang2004mix, ben2002vortex}.
 
@@
 
+The goal of this work is to develop and implement a software toolbox 
+for the generation of iterative numerical solvers for nonlinear macroscale 
+electrokinetic problems, and to apply it to the study
+of systems that have no closed-form solutions, 
+such as ion-exchanger migration \cite{yariv2010migration} 
+and the electrophoresis problem \cite{schnitzer2012surface}.
+This solver can be used to gain insight into the chemical 
+and physical behavior in far more general regimes than 
+are currently well-understood, 
+and also to possibly lead to further analytical developments, 
+based on new scaling behavior
+discovered numerically. 
+We may also target interesting physical
+phenomena that have been observed experimentally.
+One such phenomenon is nonlinear electrokinetic vortex flow, 
+which is useful for microfluidic mixing applications 
+\cite{wang2004mix, ben2002vortex}.
+
 The work is structured as follows: 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \chapter{Numerical Scheme} \label{ch:algorithm}
@@
 \section{Numerical Framework}
+
+We start by presenting the numerical framework used for the nonlinear solver construction.
+
+\subsection{Finite Volume Method}
+
+Finite Volume Methods \cite{ferziger1999computational}
+ are based on a discretization of the integral forms of the conservation equations.
+The simulation domain is divided into a set of discrete non-overlapping control volumes.
+Each conservartion equation is discretized over the control volumes,
+such that the integral form of the conservation law is satisfied using an approximation of the fluxes
+over the control volume faces.
+This method ensures that the discretization is conservative in the discrete sense.
+
+\subsection{Ghost Points}
+
+\subsection{Upwind Discretization}
+
+\subsection{Newton's Method}
+Newton's method is used to solve a nonlinear system of equations of the form $\cO(\bx) = \bzero$.
+For small step $\Delta\bx$, we can linearize the operator by
+\begin{align}
+\cO(\bx + \Delta\bx) \approx \cO(\bx) + \bnabla \cO(\bx) \Delta\bx
+\end{align}
+Thus, we use the following iteration, starting from an initial solution $\bx_0$:
+\begin{align}
+\Delta\bx_n &= - \left[\bnabla \cO(\bx_n)\right]^{-1} \cdot \cO(\bx_n) \\
+\bx_{n+1} &= \bx_n + \Delta\bx_n
+\end{align}
+
+Then, a sparse linear system $\boldsymbol{A} \Delta \bx = \boldsymbol{b}$
+needs to be solved to yield the update $\Delta \bx$.
+When the method converges, $\bx_n \rightarrow \bx_\infty$, 
+the asymptotic convergence is in general quadratic:
+\begin{equation}
+\|\bx_{n+1} - \bx_\infty\| \le k \|\bx_{n} - \bx_\infty\|^2.
+\end{equation}
+Thus, when the initial guess is close enough to the solution, the solver
+will typically converge in very few steps.
+
+\subsection{Richardson Extrapolation}
 
@@
 given the current solution $\bx$.
-Then, a sparse linear system $\bG \Delta \bx = \br$
-needs to be solved to yield the update $\Delta \bx$.
-When the method converges, $\bx_n \rightarrow \bx_\infty$, 
-the asymptotic convergence is in general quadratic:
-\begin{equation}
-\|\bx_{n+1} - \bx_\infty\| \le k \|\bx_{n} - \bx_\infty\|^2.
-\end{equation}
-Thus, when the initial guess is close enough to the solution, the solver
-will typically converge in very few steps.
 
@@
 and multiplication, are defined as follows:
-\begin{equation}\begin{array}{cc}
-(\cO_1 \pm \cO_2)(\bx) = \cO_1(\bx) \pm \cO_2(\bx), &
-\bnabla (\cO_1 \pm \cO_2)(\bx) = \bnabla\cO_1(\bx) \pm \bnabla\cO_2(\bx),
-\end{array}\end{equation}
-\begin{equation}\begin{array}{cc}
-(\cO_1 \cdot \cO_2)(\bx) = \cO_1(\bx) \cdot \cO_2(\bx), &
-\bnabla (\cO_1 \cdot \cO_2)(\bx) = \diag(\cO_2(\bx)) \bnabla\cO_1(\bx) 
+\begin{align}
+(\cO_1 \pm \cO_2)(\bx) &= \cO_1(\bx) \pm \cO_2(\bx), \\
+\nonumber
+\bnabla (\cO_1 \pm \cO_2)(\bx) &= \bnabla\cO_1(\bx) \pm \bnabla\cO_2(\bx), \\
+(\cO_1 \cdot \cO_2)(\bx) &= \cO_1(\bx) \cdot \cO_2(\bx), \\
+\nonumber
+\bnabla (\cO_1 \cdot \cO_2)(\bx) &= \diag(\cO_2(\bx)) \bnabla\cO_1(\bx) 
                                   + \diag(\cO_1(\bx)) \bnabla\cO_2(\bx).
-\end{array}\end{equation}
+\end{align}
 \subsubsection{N-ary operators}
 Given $N$ operators $\{\cO_i\}_{i=1}^N$, their concatenation $\cO$ is defined as:
-\begin{equation}\begin{array}{cc}
-\cO(\bx) = [\cO_1(\bx); \ldots; \cO_N(\bx)], &
-(\bnabla\cO)(\bx) = [(\bnabla\cO_1)(\bx); \ldots; (\bnabla\cO_N)(\bx)].
-\end{array}\end{equation}
+\begin{align}
+\cO(\bx) &= [\cO_1(\bx); \ldots; \cO_N(\bx)], \\
+\nonumber
+(\bnabla\cO)(\bx) &= [(\bnabla\cO_1)(\bx); \ldots; (\bnabla\cO_N)(\bx)].
+\end{align}
 
@@
 Given an initial solution $\bx_0$ and prescribed values for $\beta$ and $\cU$, 
-we apply the following algorithm 
-until convergence ($\|\boldsymbol{r_n}\| < \eps$):
+we apply the following algorithm until convergence ($\|\boldsymbol{r_n}\| < \eps$):
 \begin{enumerate}

### 2012-11-28 notes/thesis-latex-template/thesis.tex
Thesis LaTeX rework

@@
-% options are:
 % PhD, MSc (choose one)
@@
 \usepackage{longtable}
+\usepackage[framed,numbered,autolinebreaks,useliterate]{mcode}
 
@@
 Due to strong electrostatic forces, a thin boundary layer forms near the particle
-surface. This results in scale disparity of the boundary layer, which hinders full numerical solution. 
-We employ nonlinear macroscale effective boundary conditions that are derived
+surface. This results in scale disparity of the boundary layer, which makes a 
+full numerical solution challenging. 
+We employ nonlinear macroscale effective boundary conditions that have been derived
 using the specific chemical properties of the particle
-(for an ion-exchanger particle at \cite{yariv2010migration}
-and for a surface charged inert particle at \cite{schnitzer2012surface}).
+(for an ion-exchanger particle by Yariv in \cite{yariv2010migration}
+and for a surface charged inert particle by Schnitzer and Yariv in \cite{schnitzer2012surface}).
 The resulting macroscale nonlinear partial differential system 
@@
 has been developed for spherical particles, yielding a macroscale 
-model at \cite{yariv2010migration, schnitzer2012surface}.
+model in \cite{yariv2010migration, schnitzer2012surface}.
 The model is solved for weak electric field in an axisymmetric setting 
@@
 number is very low (on the order of unity or smaller) which means that viscosity dominates
-and the convective term of the Navier–Stokes equations are insignificant. This means that
+and the convective term of the Navier-Stokes equations are insignificant. This also means that
 microflows most often are laminar.
@@
 due to the spread of tools for microfluidic systems fabrication, 
-production of cheap and portable devices for fast point-of-care analysis, 
+production of cheap and portable devices for fast medical analysis, 
 and fundamental research of physical, chemical and biological processes.
-Various applications are \cite{erickson2004integrated, squires2005microfluidics, hardt2007microfluidic}:
+Various applications are \cite{whitesides2006origins, erickson2004integrated, squires2005microfluidics, hardt2007microfluidic}:
 \begin{enumerate}
-\item DNA and cell analysis \cite{horsman2007forensic, wu2004chemical}.
-\item Separation-based detection \cite{weinberger1993practical}.
-\item Microscale chemical processing \cite{kothare2006dynamics}.
-\item Packed bed separation \cite{leinweber2004, losey2001microfabricated}.
+\item DNA separation and sequencing \cite{wainright2003preconcentration}.
+\item Cell analysis and forensic identification \cite{wu2004chemical, weinberger1993practical, horsman2007forensic}.
+\item Integrated microchemical systems \cite{kothare2006dynamics}.
+\item Packed-bed separation \cite{leinweber2004, losey2001microfabricated}.
 \item Desalination processes \cite{kim2010direct}.
-\item Drug delivery \cite{santini2000microchips}.
+\item Drug delivery and pathogen detection \cite{santini2000microchips}.
 \end{enumerate}
@@
 \subsection{Nondimensionalization}
+We follow the derivation presented by Yariv in \cite{yariv2010asymptotic}.
 Spatial coordinates $\br$ are normalized by $a^*$ 
@@
 a direct numerical solver for the full electrokinetic problem.
-However, we exploit the scale disparity at the Debye layer, 
+However, the scale disparity at the Debye layer can be exploited
+(as shown by Yariv in \cite{yariv2010asymptotic}), 
 which allows the PDE system to be rewritten in the ``inner'' region 
@@
 
-\section{Work Outline}
+\section{Objective of this work}
 
@@
 
-The work is structured as follows: 
-The numerical scheme for the discretization and 
-the solution of the system is described in Chapter \ref{ch:algorithm}.
-Numerical results and their comparison to the analytical asymptotic solutions 
-are presented and discussed in Chapter \ref{ch:results}.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-We start by presenting the numerical framework used for the nonlinear solver construction.
+We start by presenting the numerical framework
+that is used for the construction of the nonlinear solver.
 
@@
 
-Finite Volume Methods \cite{ferziger1999computational}
- are based on a discretization of the integral forms of the conservation equations.
+Finite Volume methods \cite{ferziger2002computational} 
+are used to define a discretization of the conservation equations' integral forms.
 The simulation domain is divided into a set of discrete non-overlapping control volumes.
-Each conservartion equation is discretized over the control volumes,
+Each conservation equation is discretized over the control volumes,
 such that the integral form of the conservation law is satisfied using an approximation of the fluxes
@@
 
+\subsection{Flux Discretization}
+
+In order to define the fluxes on the boundaries of each control volume, we employ the 
+conservative formulation of the governing equations above. 
+The flux terms are defined using finite differences and linear interpolation of the disrete 
+variables (defined at the centroid of each cell), except for the advection flux which should not be 
+discretized using linear interpolation -- due to a numerical instability 
+for large cell Peclet numbers \cite{strikwerda2004finite}.
+
 \subsection{Ghost Points}
-
-\subsection{Upwind Discretization}
+In order to discretize boundary condtions for $\varPhi$, $C$ and $\bV$, 
+``ghost'' points are employed. 
+The grid is extended to include points outside the domain interior,
+and the variables at the ``ghost'' points are set to satisfy 
+the discretized boundary conditions on the grid boundaries.
+Note that $P$ has no boundary conditions -- so the pressure variable is defined 
+only in the domain interior.
 
@@
 \end{align}
-
 Then, a sparse linear system $\boldsymbol{A} \Delta \bx = \boldsymbol{b}$
@@
 \subsection{Richardson Extrapolation}
+In order to achieve higher numerical accuracy, we employ Richardson extrapolation \cite{sidi2003practical}
+on the resulting steady-state velocity $\cU(h)$, as a scalar function of the grid spacing $h$.
+This method enables us to detect and analyze nonlinear effects for $\beta \ll 1$, where 
+a higher-order discretization is required because otherwise
+the numerical error becomes comparable to the difference between the linear analytical regime 
+and the numerical results.
 
@@
 \subsection{Spherical Coordinates}
-Because the system is axisymmetric, we employ
+Because the system is axisymmetric and the particle is a sphere, we employ
 spherical coordinates $(r,\theta,\phi)$.
@@
 \end{align}
-
 Note that in the spherical coordinate system,
 the vector Laplacian operator cannot be computed in a decoupled manner as in the Cartesian system,
-since the unit vectors $\brhat, \bthetahat, \bphihat$ are functions of the coordinates
+because the unit vectors $\brhat, \bthetahat, \bphihat$ are functions of the coordinates
 in a curvilinear coordinate system.
@@
         \caption[Computational grid]{The computational grid is defined using
-        spherical coordinates system, due to axisymmetry of the physical problem
+        a spherical coordinate system, due to axisymmetry of the physical problem
         and boundary conditions discretization on the particle surface.}
@@
 \end{align}
-
 Mass flux $\bV$ is discretized on grid cells boundaries, 
 using the staggered velocity grid.
-
 Force components ($\bF = -\bnabla P + \bLaplacian \bV + \bnabla \varPhi \Laplacian \varPhi$) 
@@
 \subsection{Boundary Conditions} \label{sec:disc_boundary}
-In order to discretize boundary condtions for $\varPhi$, $C$ and $\bV$, 
-``ghost'' points are employed. 
-The grid is extended to include points outside the domain interior,
-and the variables at the ``ghost'' points are set to satisfy 
-the discretized boundary conditions, following the analysis below.
-Note that $P$ has no boundary conditions -- so the pressure variable is defined 
-only in the domain interior.
 
@@
 \end{array}\end{equation}
-
 For $\theta = 0$ and $\theta = \pi$, the ``ghost'' points are defined by axial 
@@
 \end{equation}
-
 The specific boundary conditions at $r=1$
@@
 \section{Solver Design}
-An operator $\cO$ is defined by its input vector $\bx$ and its output 
-$\by = \cO(\bx)$.
+Let $\cO : \R^N \rightarrow \R^N $ be an nonlinear operator.
 In order to solve the equation $\cO(\bx) = \bzero$, Newton's method is applied, 
@@
 \end{eqnarray}
-
 The integral above is approximated by 1D numerical quadrature
@@
 and a gradient matrix \verb|Operator::grad()|, given an input vector $\bx$.
-This interface is implemented by specific operators classes,
+This interface is implemented by specific operator classes,
 which are used to construct the system operator $\cO$, so that 
@@
 \end{enumerate}
+
+\subsection{Sample source code}
+
+\subsubsection{Variable class}
+\begin{figure}
+\begin{lstlisting}
+classdef Variable < handle
+properties
+    value;
+end
+
+methods
+    function self = Variable(varargin)
+        self.value = col(varargin{:});
+    end
+
+    function r = res(self)
+        r = self.value(:);
+    end
+
+    function G = grad(self) 
+        G = speye(numel(self.value));
+    end
+
+    function update(self, delta)
+        assert(numel(self.value) == numel(delta))
+        self.value = self.value + delta;
+    end
+end
+
+end
+\end{lstlisting}
+\end{figure}
+
+\subsubsection{Operator interface}
+\begin{lstlisting}
+% An operator base class.
+classdef Operator < handle
+properties
+    grid; % a grid object for the output
+end
+methods
+    function op = Operator(grid)
+        op.grid = grid;
+    end
+    function op = plus(op1, op2)
+        op = Sum(op1, op2);
+    end
+    function op = minus(op1, op2)
+        op = Minus(op1, op2);
+    end
+    function op = uminus(op)
+        op = Product(-1, op);
+    end
+    function op = mtimes(op1, op2)
+        op = Product(op1, op2);
+    end
+    function op = log(op)
+        op = Func(op, 'log(x)');
+    end
+    function op = exp(op)
+        op = Func(op, 'exp(x)');
+    end
+    function op = sinh(op)
+        op = Func(op, 'sinh(x)');
+    end
+    function op = cosh(op)
+        op = Func(op, 'cosh(x)');
+    end
+    function op = tanh(op)
+        op = Func(op, 'tanh(x)');
+    end
+end
+end
+\end{lstlisting}
+
+\subsubsection{Linear operators}
+\begin{lstlisting}
+% Linear Sparse operator.
+classdef Linear < Operator
+properties
+    L;
+    op;
+end
+
+methods
+    function self = Linear(grid, op, L)
+        self = self@Operator(grid);
+        self.op = op;
+        if (nargin < 3 || isempty(L))
+            L = 1;
+        end
+        if isequal(L, 1)
+            L = speye(grid.numel); % Default copy operator
+        end
+        assert(size(L, 1) == grid.numel);
+        assert(size(L, 2) == op.grid.numel);
+        self.L = L;
+    end
+    function r = res(self)
+        r = self.L * self.op.res();
+    end
+    function G = grad(self)
+        G = dot_prod(self.L, self.op.grad());
+    end
+end
+
+end
+\end{lstlisting}
+
+\begin{lstlisting}
+classdef Deriv < Linear
+
+methods
+    function self = Deriv(grid, op, dim)
+        dir = (1:2) == dim;
+        assert(any(dir));
+
+        J = true(op.grid.size);
+        J1 = shift(J, dir); % forward mask
+        J0 = shift(J1, -dir); % backward mask
+        J = [find(J0(:)) find(J1(:))]; % column indices
+
+        N = size(J, 1); % # of equations
+        M = op.grid.numel; % # of variables
+        I = repmat(1:N, 1, 2); % row indices
+
+        % Finite difference operator
+        D = sparse(I, J, repmat([-1 1], N, 1), N, M);
+
+        switch dim % Choose coordinate
+            case 1, x = op.grid.R;
+            case 2, x = op.grid.T;
+        end
+
+        % L = D/Dx
+        Dx = D * x(:);
+        assert(all(Dx));
+
+        L = spdiag( 1./Dx ) * D;
+        self = self@Linear(grid, op, L);        
+    end
+end
+
+end
+\end{lstlisting}
+
+\begin{lstlisting}
+classdef Interp < Linear
+
+methods
+    function self = Interp(grid, op)
+        L = interpolate_grids(grid, op.grid);
+        self = self@Linear(grid, op, L);
+    end
+end
+
+end
+
+function S = interpolate_grids(dst, src)
+    n = fieldnames(src);
+    S1 = interpolate_matrix(src.(n{1}), dst.(n{1}));
+    S1 = kron(speye(numel(src.(n{2}))), S1); % Interpolate on 1st dimension
+    S2 = interpolate_matrix(src.(n{2}), dst.(n{2}));
+    S2 = kron(S2, speye(numel(dst.(n{1})))); % Interpolate on 2nd dimension
+    S = S2 * S1;    
+end
+
+function S = interpolate_matrix(x, xi)
+    x = x(:);
+    xi = xi(:);
+    N = numel(xi);
+    L = zeros(N, 1);
+    R = zeros(N, 1);
+    for k = 1:N
+        less = x <= xi(k);
+        more = x >= xi(k);
+        if any(less)
+            L(k) = find(less, 1, 'last');
+        end
+        if any(more)
+            R(k) = find(more, 1, 'first');
+        end
+    end
+    u = L & R; % valid interpolatory points
+    I = find(u);
+    L = L(u);
+    R = R(u);
+    xi = xi(u);
+
+    I = [I I];
+    J = [L R];
+    dx = x(R) - x(L);
+    V = [(x(R)-xi), (xi-x(L))];
+    V(dx>0, :) = spdiag( 1./dx(dx>0) ) * V(dx>0, :);
+    V(~dx, :) = 1/2;
+    S = sparse(I, J, V, N, numel(x));
+end
+\end{lstlisting}
+
+\subsubsection{Binary Operators}
+\begin{lstlisting}
+% Abstract class for a binary operator
+classdef Binary < Operator
+properties
+    op1, op2;
+end
+
+methods
+    function self = Binary(op1, op2)
+        if isa(op1, 'Operator') && isa(op2, 'Operator')
+            assert(op1.grid == op2.grid);
+        end
+        if ~isa(op1, 'Operator')
+            op1 = Const(op2.grid, op1);
+        end
+        if ~isa(op2, 'Operator')
+            op2 = Const(op1.grid, op2);
+        end
+        self = self@Operator(op1.grid);
+        self.op1 = op1;
+        self.op2 = op2;
+    end
+end
+
+end
+\end{lstlisting}
+\begin{lstlisting}
+classdef Product < Binary
+
+methods
+    function self = Product(op1, op2)
+        self = self@Binary(op1, op2);
+    end
+    function r = res(self)
+        r = self.op1.res() .* self.op2.res();
+    end
+    function g = grad(self)
+        g1 = dot_prod(spdiag(self.op2.res()), self.op1.grad());
+        g2 = dot_prod(spdiag(self.op1.res()), self.op2.grad());
+        g = g1 + g2;
+    end
+end
+
+end
+\end{lstlisting}
+
+\begin{lstlisting}
+classdef Sum < Binary
+
+methods
+    function self = Sum(op1, op2)
+        self = self@Binary(op1, op2);
+    end
+    function r = res(self)
+        r = self.op1.res() + self.op2.res();
+    end
+    function g = grad(self)
+        g1 = self.op1.grad();
+        g2 = self.op2.grad();
+        g = g1 + g2;
+    end
+end
+
+end
+\end{lstlisting}
+
+\subsubsection{Unary operator}
+\begin{lstlisting}
+classdef Func < Operator
+properties
+    op; % Input operator
+    func; % y = f(x)
+    deriv; % dy/dx = f'(x)
+end
+
+methods
+    function self = Func(op, func)
+        grid = op.grid; % Reuse operator's grid
+        self = self@Operator(grid);
+        self.op = op;
+        if ~isempty(func)
+            if isa(func, 'char')
+                func = sym(func);
+            end % using symoblic toolbox
+            self.func = matlabFunction(func);
+            self.deriv = matlabFunction(diff(func));
+        else % just copy values to grid
+            self.func = @(x) x;
+            self.deriv = @(x) ones(size(x));
+        end
+    end
+    function r = res(self)
+        r = self.func( self.op.res() );
+    end
+    function G = grad(self)
+        r = self.op.res();
+        G = dot_prod(spdiag( self.deriv(r) ), self.op.grad());
+    end
+end
+
+end
+\end{lstlisting}
+
+\begin{lstlisting}
+classdef Const < Operator
+properties
+    val;
+end
+
+methods
+    function self = Const(grid, val)
+        self = self@Operator(grid);
+        if isa(val, 'float')
+            if numel(val) == 1
+                val = repmat(val, grid.size);
+            end
+            self.val = val;
+        else % function handle evaluated point-wise
+            if isa(val, 'char')
+                val = str2func(['@(r,t) ' val]);
+            end
+            self.val = arrayfun(val, grid.R, grid.T);
+        end
+    end
+    function r = res(self)
+        r = self.val(:);
+    end
+    function G = grad(self)
+        G = sparse(0); % [0]
+    end
+end
+
+end
+\end{lstlisting}
+
+\begin{lstlisting}
+\end{lstlisting}
 
@@
 
+For strong electric field ($\beta \gg 1)$, the nonlinear effects become dominant and
+another boundary-layer structure is expected to form near the particle surface. 
+In order to achieve high numerical accuracy, the grid discretization should be made finer
+near the particle surface (at $r = 1$), while $R_{max}$ can be made smaller.
+In addition, the continuation of the solution between different $\beta$ values
+should advance in finer steps, for Newton method convergence.
+
 \section{Future Work}
@@
 Multigrid), allowing finer grids to be used.
-Since it is expected that a boundary layer should form around the particle for $\beta \gg 1$,
-a numerical solver should be able to handle large grids to achieve good numeric accuracy.
-
 In addition, the framework may be used for automatic construction of Newton solvers 

### 2012-12-19 notes/thesis-latex-template/thesis.tex
Add sample solver code

@@
 
+\setlength{\textheight}{9in}
+\setlength{\textwidth}{7in}
+\setlength{\topmargin}{0.05in}
+\setlength{\headheight}{0.2in}
+\setlength{\headsep}{0.1in}
+\setlength{\evensidemargin}{0in}
+\setlength{\oddsidemargin}{0in}
+\setlength{\parindent}{0.0 in}
+\setlength{\parskip}{0.1 in}
+
 % For some reason, the hebrew package clashes with the amsthm package. If you need a proof environment, you can uncomment the following:
@@
 
-\subsection{Operator Interface}
+\subsection{Operator Interface} \label{sec:operator-interface}
 The base \verb|Operator| interface is defined by 
@@
 a specific grid point to be $0$.
-In order to retain square system, we should remove one conservation equation at this grid point too.
+In order to retain a square system, we remove one conservation equation at this grid point too.
 In the case of pressure $P$, we remove one mass conservation equation,
@@
 
-\subsection{Sample source code}
-
-\subsubsection{Variable class}
-\begin{figure}
+\section{Source code overview}
+
+\subsection{Variable}
+We define the variable vector $\bx$ as \verb|Variable| 
+operator using the following MATLAB code:
+
 \begin{lstlisting}
@@
 end
-
 methods
@@
     end
-
     function r = res(self)
@@
     end
-
     function G = grad(self) 
@@
     end
-
-    function update(self, delta)
-        assert(numel(self.value) == numel(delta))
-        self.value = self.value + delta;
-    end
-end
-
+    function update(self, dv)
+        self.value = self.value + dv;
+    end
 end
 \end{lstlisting}
-\end{figure}
-
-\subsubsection{Operator interface}
+Then the initial solution for the solver is set using
+$\bx = \verb|Variable|(\varPhi, C, V_r, V_t, P)$
+from the initial conditions of the solver.
+
+\subsection{Grid}
+Most of the operators are defined a \verb|Grid| object,
+enabling validation of operators compatibility and 
+convenient interpolation between grids. Note that
+each operator must define its \verb|res()| and \verb|grad()|
+functions, for residual and gradient computation, respectively.
 \begin{lstlisting}
-% An operator base class.
+% Regular structured grid class
+classdef Grid < handle
+properties
+    x, y;
+    X, Y;
+    size;    
+    numel;
+end
+methods
+    function self = Grid(x, y)
+        self.x = x(:);
+        self.y = y(:);
+        [self.X, self.Y] = ndgrid(self.x, self.y);
+        self.size = [numel(self.x), numel(self.y)];
+        self.numel = prod(self.size);
+    end
+end
+\end{lstlisting}
+\begin{lstlisting}
 classdef Operator < handle
@@
 end
-end
 \end{lstlisting}
-
-\subsubsection{Linear operators}
+Thus, various computations can be applied on simple operators, 
+creating more complex operators, such as
+\verb|op4 = op1 * exp(op2 + tanh(op3))|. 
+Since each operator can compute its residual and gradient, we
+can compute automatically the residual and gradient of \verb|o4|
+from these of \verb|o1|, \verb|o2|, \verb|o3| using the derivation
+rules described at \ref{sec:operator-interface}.
+
+\subsection{Operators}
+An operator can be created with $n$ existing operators as input.
+\verb|Const| is an operator that corresponds to $n=0$, whose 
+residual value is constant and gradient matrix is zero.
+
 \begin{lstlisting}
-% Linear Sparse operator.
-classdef Linear < Operator
+classdef Const < Operator
 properties
-    L;
-    op;
-end
-
+    val;
+end
 methods
-    function self = Linear(grid, op, L)
+    function self = Const(grid, val)
         self = self@Operator(grid);
-        self.op = op;
-        if (nargin < 3 || isempty(L))
-            L = 1;
-        end
-        if isequal(L, 1)
-            L = speye(grid.numel); % Default copy operator
-        end
-        assert(size(L, 1) == grid.numel);
-        assert(size(L, 2) == op.grid.numel);
-        self.L = L;
+        if isa(val, 'float')
+            if numel(val) == 1
+                val = repmat(val, grid.size);
+            end
+            self.val = val;
+        else % function handle evaluated point-wise
+            if isa(val, 'char')
+                val = str2func(['@(r,t) ' val]);
+            end
+            self.val = arrayfun(val, grid.R, grid.T);
+        end
     end
     function r = res(self)
-        r = self.L * self.op.res();
+        r = self.val(:);
     end
     function G = grad(self)
-        G = dot_prod(self.L, self.op.grad());
-    end
-end
-
+        G = sparse(0); % [0]
+    end
 end
@@
 
-\begin{lstlisting}
-classdef Deriv < Linear
-
-methods
-    function self = Deriv(grid, op, dim)
-        dir = (1:2) == dim;
-        assert(any(dir));
-
-        J = true(op.grid.size);
-        J1 = shift(J, dir); % forward mask
-        J0 = shift(J1, -dir); % backward mask
-        J = [find(J0(:)) find(J1(:))]; % column indices
-
-        N = size(J, 1); % # of equations
-        M = op.grid.numel; % # of variables
-        I = repmat(1:N, 1, 2); % row indices
-
-        % Finite difference operator
-        D = sparse(I, J, repmat([-1 1], N, 1), N, M);
-
-        switch dim % Choose coordinate
-            case 1, x = op.grid.R;
-            case 2, x = op.grid.T;
-        end
-
-        % L = D/Dx
-        Dx = D * x(:);
-        assert(all(Dx));
-
-        L = spdiag( 1./Dx ) * D;
-        self = self@Linear(grid, op, L);        
-    end
-end
-
-end
-\end{lstlisting}
-
-\begin{lstlisting}
-classdef Interp < Linear
-
-methods
-    function self = Interp(grid, op)
-        L = interpolate_grids(grid, op.grid);
-        self = self@Linear(grid, op, L);
-    end
-end
-
-end
-
-function S = interpolate_grids(dst, src)
-    n = fieldnames(src);
-    S1 = interpolate_matrix(src.(n{1}), dst.(n{1}));
-    S1 = kron(speye(numel(src.(n{2}))), S1); % Interpolate on 1st dimension
-    S2 = interpolate_matrix(src.(n{2}), dst.(n{2}));
-    S2 = kron(S2, speye(numel(dst.(n{1})))); % Interpolate on 2nd dimension
-    S = S2 * S1;    
-end
-
-function S = interpolate_matrix(x, xi)
-    x = x(:);
-    xi = xi(:);
-    N = numel(xi);
-    L = zeros(N, 1);
-    R = zeros(N, 1);
-    for k = 1:N
-        less = x <= xi(k);
-        more = x >= xi(k);
-        if any(less)
-            L(k) = find(less, 1, 'last');
-        end
-        if any(more)
-            R(k) = find(more, 1, 'first');
-        end
-    end
-    u = L & R; % valid interpolatory points
-    I = find(u);
-    L = L(u);
-    R = R(u);
-    xi = xi(u);
-
-    I = [I I];
-    J = [L R];
-    dx = x(R) - x(L);
-    V = [(x(R)-xi), (xi-x(L))];
-    V(dx>0, :) = spdiag( 1./dx(dx>0) ) * V(dx>0, :);
-    V(~dx, :) = 1/2;
-    S = sparse(I, J, V, N, numel(x));
-end
-\end{lstlisting}
-
-\subsubsection{Binary Operators}
-\begin{lstlisting}
-% Abstract class for a binary operator
-classdef Binary < Operator
-properties
-    op1, op2;
-end
-
-methods
-    function self = Binary(op1, op2)
-        if isa(op1, 'Operator') && isa(op2, 'Operator')
-            assert(op1.grid == op2.grid);
-        end
-        if ~isa(op1, 'Operator')
-            op1 = Const(op2.grid, op1);
-        end
-        if ~isa(op2, 'Operator')
-            op2 = Const(op1.grid, op2);
-        end
-        self = self@Operator(op1.grid);
-        self.op1 = op1;
-        self.op2 = op2;
-    end
-end
-
-end
-\end{lstlisting}
-\begin{lstlisting}
-classdef Product < Binary
-
-methods
-    function self = Product(op1, op2)
-        self = self@Binary(op1, op2);
-    end
-    function r = res(self)
-        r = self.op1.res() .* self.op2.res();
-    end
-    function g = grad(self)
-        g1 = dot_prod(spdiag(self.op2.res()), self.op1.grad());
-        g2 = dot_prod(spdiag(self.op1.res()), self.op2.grad());
-        g = g1 + g2;
-    end
-end
-
-end
-\end{lstlisting}
-
-\begin{lstlisting}
-classdef Sum < Binary
-
-methods
-    function self = Sum(op1, op2)
-        self = self@Binary(op1, op2);
-    end
-    function r = res(self)
-        r = self.op1.res() + self.op2.res();
-    end
-    function g = grad(self)
-        g1 = self.op1.grad();
-        g2 = self.op2.grad();
-        g = g1 + g2;
-    end
-end
-
-end
-\end{lstlisting}
-
-\subsubsection{Unary operator}
+\subsubsection{Unary operators}
+Unary operators have one existing operator as input. 
+\verb|Func| operator implements point-wise analytic function
+application (whose derivative is computed using symbolic differentiation toolbox) on the same grid of the input operator. 
+\verb|Linear| operator is implemented
+using multiplication by a constant sparse matrix 
+\verb|L|, which is also the gradient of the operator.
 \begin{lstlisting}
@@
         self.op = op;
-        if ~isempty(func)
         if isa(func, 'char')
         	func = sym(func); 
-            end % using symoblic toolbox
+        end 
         self.func = matlabFunction(func);
         self.deriv = matlabFunction(diff(func));
-        else % just copy values to grid
-            self.func = @(x) x;
-            self.deriv = @(x) ones(size(x));
-        end
     end
@@
         r = self.op.res();
-        G = dot_prod(spdiag( self.deriv(r) ), self.op.grad());
-    end
-end
-
+        G = spdiag( self.deriv(r) ) * self.op.grad();
+    end
 end
 \end{lstlisting}
-
 \begin{lstlisting}
-classdef Const < Operator
+classdef Linear < Operator
 properties
-    val;
-end
-
+    L;
+    op;
+end
 methods
-    function self = Const(grid, val)
+    function self = Linear(grid, op, L)
         self = self@Operator(grid);
-        if isa(val, 'float')
-            if numel(val) == 1
-                val = repmat(val, grid.size);
-            end
-            self.val = val;
-        else % function handle evaluated point-wise
-            if isa(val, 'char')
-                val = str2func(['@(r,t) ' val]);
-            end
-            self.val = arrayfun(val, grid.R, grid.T);
-        end
+        self.op = op;
+        self.L = L;
     end
     function r = res(self)
-        r = self.val(:);
+        r = self.L * self.op.res();
     end
     function G = grad(self)
-        G = sparse(0); % [0]
-    end
-end
-
+        G = self.L * self.op.grad();
+    end
 end
 \end{lstlisting}
+\verb|Deriv| and \verb|Interp| operators (implementing discrete
+differentiation and grid interpolation) derive from \verb|Linear|
+base class operator and specify \verb|L| sparse matrix accordingly.
+
+\subsubsection{Binary operators}
+Binary operators such as addition, subtraction and point-wise 
+multiplication are implemented as operators whose
+output grid is the as the grid of their inputs. 
+The implementation is used by operator overloading in 
+the base class \verb|Operator|.
+
+\subsubsection{$N$-ary operators}
+All equations and boundary condition operators are defined
+as operators \verb|{op1, op2, ... opN}|. 
+Then, they are combined using the $N$-ary operator 
+\verb|op = Join(op1, op2, ... opN)|, creating
+the system operator \verb|op|.
 
 \begin{lstlisting}
+classdef Join < handle
+properties
+    ops;
+end
+methods
+    function self = Join(varargin)
+        self.ops = varargin;
+        for k = 1:numel(self.ops),
+            op = self.ops{k};
+        end
+    end
+    function r = res(self)
+        r = cell(numel(self.ops), 1);
+        for k = 1:numel(self.ops)
+            r{k} = self.ops{k}.res();
+        end
+        r = cat(1, r{:});
+    end
+    function G = grad(self) 
+        G = cell(numel(self.ops), 1);
+        for k = 1:numel(self.ops)
+            G{k} = self.ops{k}.grad();
+        end
+        G = cat(1, G{:});
+    end
+end
+\end{lstlisting}
+
+\subsection{Sample source code}
+The following example shows how to define the following boundary-value problem:
+\begin{align}
+\Laplacian F(x,y) &= 1 & (x,y) &\in [0,1]^2 \\
+F(0, y) = F(1, y) &= 0 & y &\in [0,1] \\
+\deriv{F}{y}(x, 0) = \deriv{F}{y}(x, 1) &= 0 & x &\in [0,1]
+\end{align}
+
+\begin{lstlisting}
+% Grid definition
+x = linspace(0, 1);
+y = linspace(0, 1);
+g = Grid(x, y);
+x_ = (x(1:end-1) + x(2:end)) * 0.5;
+y_ = (y(1:end-1) + y(2:end)) * 0.5;
+xi = x(2:end-1);
+yi = y(2:end-1);
+% Variable Definition
+v = Variable(zeros(g.size));
+F = Linear(g, v, speye(g.numel));
+% Equations
+Fx = Deriv(Grid(x_, y), F, 1);
+Fy = Deriv(Grid(x, y_), F, 2);
+Fxx = Deriv(Grid(xi, yi), Fx, 1);
+Fyy = Deriv(Grid(xi, yi), Fy, 2);
+eq = {(Fxx + Fyy) - Const(1)};             % Laplacian(F) = 1
+% Boundary conditions
+bnd = {Interp(Grid(x(1)  , y(2:end-1)), F); ... % F(0, y) = 0
+	   Interp(Grid(x(end), y(2:end-1)), F); ... % F(1, y) = 0
+       Interp(Grid(x, y_(1)  ), Fy); ...    % dF/dy(x, 0) = 0
+       Interp(Grid(x, y_(end)), Fy)}		% dF/dy(x, 1) = 0
+% System operator
+ops = cat(1, eq, bnd)
+op = Join(ops{:})
+% Solve by Newton iteration
+r = op.res()
+G = op.grad()
+v.update(-(G\r))
 \end{lstlisting}
@@
 We present here the asymptotic analysis for the ion-exchanger case \cite{yariv2010migration},
-and the asymptotic analysis for the electrophoresis case \cite{schnitzer2012surface}
+while the asymptotic analysis for the electrophoresis case \cite{schnitzer2012surface}
 is derived by Schnitzer and Yariv at \cite{schnitzer2012cubic}.
@@
 \end{equation}
-
 Thus, the $O(\beta^k)$ term $\bx_k$ can be found recursively by solving 
@@
 \end{array}\end{equation}
-
 Assuming $\beta \ll 1$, the linearized equations and boundary conditions are
@@
 \end{array}\end{equation}
-
 The first-order terms $\bx_1$ are given by (see \cite{yariv2010migration} for full derivation)
@@
 \end{equation}
-
 The cubic terms $\bx_3$ are computed by solving a linear PDE system 
@@
 \end{align*}
-
 The cubic solution satisfies the boundary conditions only when $\alpha\cU_1 = 0$,
@@
 the diffusion and the advection terms become of the same order of magnitude.
-
 The cubic correction velocity terms (for $\alpha = 0$)
@@
 \end{equation}
-
 The cubic term becomes dominant for small $\beta$ when $\gamma \approx 1$.

### 2012-12-25 notes/thesis-latex-template/thesis.tex
Thesis

@@
 $\Delta_r = \pars{R_{max}} ^ {1/n_r} - 1$ and $\Delta_\theta = {\pi/n_\theta}$.
-Because the grid is finite, the choice 
-$R_{max}$ must be taken large enough so as to have a negligible effect
-on the solution.
+
+Because the grid is finite, the choice $R_{max}$ must be taken large enough 
+so as to have a negligible effect on the solution. 
+On the other hand, in order to have high resolution grid near the particle surface,
+$\Delta_r$ should be minimized. It should be noted that for given grid size $n_r$,
+these requirements cannot be satisfied simultaneously -- thus, a compromise is required
+between large $R_{max}$ and small $\Delta_r$.
+
 This grid induces a disjoint subdivision of the domain 
@@
 \end{align}
-
-\begin{figure}[htbp]
+\begin{figure}[h]
     \begin{center}
@@
 \section{Source code overview}
-
+In the following section we present the source code of the numerical framework and demonstrate its
+usage for solving a boundary-value problem.
 \subsection{Variable}
 We define the variable vector $\bx$ as \verb|Variable| 
-operator using the following MATLAB code:
-
+operator (Figure \ref{fig:variable.m}).
+
+\begin{figure}[htpb]
 \begin{lstlisting}
@@
 \end{lstlisting}
+\caption{Variable class source code.} \label{fig:variable.m}
+\end{figure}
 Then the initial solution for the solver is set using
@@
 \subsection{Grid}
-Most of the operators are defined a \verb|Grid| object,
+Most of the operators are using a \verb|Grid| object (Figure \ref{fig:grid.m}),
 enabling validation of operators compatibility and 
@@
 functions, for residual and gradient computation, respectively.
+An \verb|Operator| interface is used (Figure \ref{fig:operator.m}) 
+to support operator overloading MATLAB syntax.
+\begin{figure}[h]
 \begin{lstlisting}
@@
 \end{lstlisting}
+\caption{Grid class source code.} \label{fig:grid.m}
+\end{figure}
+\begin{figure}[h]
 \begin{lstlisting}
@@
 \end{lstlisting}
+\caption{Operator interface source code.} \label{fig:operator.m}
+\end{figure}
+
 Thus, various computations can be applied on simple operators, 
@@
 \verb|Const| is an operator that corresponds to $n=0$, whose 
-residual value is constant and gradient matrix is zero.
-
+residual value is constant and gradient matrix is zero (see Figure \ref{fig:const.m}).
+
+\begin{figure}[h]
 \begin{lstlisting}
@@
 \end{lstlisting}
+\caption{Constant operator source code.} \label{fig:const.m}
+\end{figure}
 
@@
 \verb|Func| operator implements point-wise analytic function
-application (whose derivative is computed using symbolic differentiation toolbox) on the same grid of the input operator. 
+application (whose derivative is computed using symbolic differentiation toolbox) on the same grid of the input operator (Figure \ref{fig:func.m}). 
 \verb|Linear| operator is implemented
 using multiplication by a constant sparse matrix 
-\verb|L|, which is also the gradient of the operator.
+\verb|L|, which is also the gradient of the operator
+(Figure \ref{fig:linear.m}).
+\verb|Deriv| and \verb|Interp| operators (implementing discrete
+differentiation and grid interpolation) derive from \verb|Linear|
+base class operator and specify \verb|L| sparse matrix accordingly.
+
+\begin{figure}[h]
 \begin{lstlisting}
@@
 \end{lstlisting}
+\caption{Pointwise function source code.} \label{fig:func.m}
+\end{figure}
+\begin{figure}[h]
 \begin{lstlisting}
@@
 \end{lstlisting}
-\verb|Deriv| and \verb|Interp| operators (implementing discrete
-differentiation and grid interpolation) derive from \verb|Linear|
-base class operator and specify \verb|L| sparse matrix accordingly.
+\caption{Linear operator source code.} \label{fig:linear.m}
+\end{figure}
 
@@
 \verb|op = Join(op1, op2, ... opN)|, creating
-the system operator \verb|op|.
-
+the system operator \verb|op| (Figure \ref{fig:join.m}).
+
+\begin{figure}[htpb]
 \begin{lstlisting}
@@
 methods
-    function self = Join(varargin)
-        self.ops = varargin;
-        for k = 1:numel(self.ops),
+    function self = Join(operators)
+        self.ops = operators;
+        for k = 1:numel(self.ops)
         	op = self.ops{k}; 
@@
 \end{lstlisting}
+\caption{Join operator source code.} \label{fig:join.m}
+\end{figure}
 
@@
 \end{align}
-
+and solve it using one Newton method step.
+The source code is presented at Figure \ref{fig:sample.m}.
+\begin{figure}[htpb]
 \begin{lstlisting}
-% Grid definition
 x = linspace(0, 1); 
 y = linspace(0, 1);
-g = Grid(x, y);
+g = Grid(x, y); % Grid definition
 x_ = (x(1:end-1) + x(2:end)) * 0.5;
@@
 yi = y(2:end-1);
-% Variable Definition
 v = Variable(zeros(g.size)); 
-F = Linear(g, v, speye(g.numel));
-% Equations
+F = Linear(g, v, speye(g.numel)); % Variable Definition
 Fx = Deriv(Grid(x_, y), F, 1);
@@
 eq = {(Fxx + Fyy) - Const(1)};               % Laplacian(F) = 1
-% Boundary conditions
-bnd = {Interp(Grid(x(1)  , y(2:end-1)), F); ... % F(0, y) = 0
-	   Interp(Grid(x(end), y(2:end-1)), F); ... % F(1, y) = 0
-       Interp(Grid(x, y_(1)  ), Fy); ...    % dF/dy(x, 0) = 0
-       Interp(Grid(x, y_(end)), Fy)}		% dF/dy(x, 1) = 0
-% System operator
-ops = cat(1, eq, bnd)
-op = Join(ops{:})
-% Solve by Newton iteration
+bnd = {Interp(Grid(0.0, y(2:end-1)), F); ... % F(0, y) = 0
+	   Interp(Grid(1.0, y(2:end-1)), F); ... % F(1, y) = 0
+       Interp(Grid(x, 0.0), Fy); ...         % dF/dy(x, 0) = 0
+       Interp(Grid(x, 1.0), Fy)}		     % dF/dy(x, 1) = 0       
+op = Join([eq; bnd]); % System operator
 r = op.res()
 G = op.grad()
-v.update(-(G\r))
+v.update(-(G\r)) % Solve by Newton iteration
 \end{lstlisting}
+\caption{Sample problem source code.} \label{fig:sample.m}
+\end{figure}
 
@@
 and the linear velocity term is:
-\begin{equation} \label{eq:linear_velocity}
-\cU_1(\gamma) = 2 \log \pars{\frac{1 + \gamma^{-\frac{1}{2}}}{2}}.
-\end{equation}
+\begin{align} \label{eq:linear_velocity}
+\bV_1 &= \cU_1 \pars{ \pars{-1 + r^{-3}}\cos\theta \cdot \brhat 
++ \pars{1 + r^{-3} / 2} \sin\theta \cdot \bthetahat } \\
+\cU_1(\gamma) &= 2 \log \pars{\frac{1 + \gamma^{-\frac{1}{2}}}{2}}.
+\end{align}
 For $\gamma > 1$, the Debye layer has a positive space charge, 
@@
 The numerical solver uses $N_r \times N_\theta = (400 \times 50)$, 
-$R_{\max} = 10^7$,
+$R_{\max} = 10^7$ ($\Delta_r \approx 0.041$),
 $K = 3$, $M = 5$ and $\beta = 10^{t}$ for $t = -2:0.1:0.5$.
@@
 $K = 3$, $M = 5$ and $\beta = 0.1 \cdot 2^{t}$ for $t = -2:0.5:5$.
-The solver is applied to 2 grids of $N_r \times N_\theta = (128 \times 128)$ as the coarse grid,
-and $N_r \times N_\theta = (256 \times 256)$ as the fine grid, in order to use Richardson extrapolation for $\hat\cU$.
+The solver is applied to 2 grids of $N_r \times N_\theta = (128 \times 128)$ as the coarse grid 
+(with $\Delta_r \approx 0.037$), and $N_r \times N_\theta = (256 \times 256)$ as the fine grid
+(with $\Delta_r \approx 0.018$), in order to use Richardson extrapolation for $\hat\cU$.
 
@@
 nonlinear system.
+
+The computational grid is created to have fine resolution near the particle surface, while
+approximating the far-away boundary conditions. The logarithmic discretization is motivated
+by the solution of the linearized Stokes problem, where the largest gradients are near the particle
+and the solution approaches the outer boundary conditions far away from the particle.
 

### 2013-01-03 notes/thesis-latex-template/thesis.tex
Update thesis.

@@
 \newcommand\bpsi{\boldsymbol{\psi}}
+\newcommand\Du{\text{Du}}
 
@@
 \nonumber
-0 &= {\deriv{C}{n} - \text{Du} \nabla^2_s \pars{\varPhi - \log C}}, \\
+0 &= {\deriv{C}{n} - \Du \nabla^2_s \pars{\varPhi - \log C}}, \\
 0 &= {\deriv{C}{n} + C \deriv{\varPhi}{n}}, \\
@@
 \begin{array}{rcl}
-0 &=& \cD_r(C^h) - \text{Du} \cdot 
+0 &=& \cD_r(C^h) - \Du \cdot 
 \pars{\cD_\theta \pars{\sin\theta \cdot \cD_\theta \cI_r\pars{\varPhi^h - \log C}}}/{\sin\theta}, \\
@@
 \begin{align} \label{eq:linear_velocity}
-\bV_1 &= \cU_1 \pars{ \pars{-1 + r^{-3}}\cos\theta \cdot \brhat 
-+ \pars{1 + r^{-3} / 2} \sin\theta \cdot \bthetahat } \\
+\bV_1 &= \cU_1 \pars{ \brhat \pars{-1 + \frac{1}{r^3}}\cos\theta 
++ \bthetahat \pars{1 + \frac{1}{2r^3}} \sin\theta } \\
 \cU_1(\gamma) &= 2 \log \pars{\frac{1 + \gamma^{-\frac{1}{2}}}{2}}.
@@
 In order to reduce the discretization error of the numerical solution \eqref{eq:disc_zero_force}
-and after verifying that the discretization error converges as $O(h^2)$,
+and after verifying that the discretization error converges as $O(h^2)$ (Figure \ref{fig:quadratic}),
 we employ Richardson extrapolation to $\cU^h$ and $\cU^{2h}$:
@@
 approximating the far-away boundary conditions. The logarithmic discretization is motivated
-by the solution of the linearized Stokes problem, where the largest gradients are near the particle
-and the solution approaches the outer boundary conditions far away from the particle.
+by the solution of the linearized system at Section \ref{app:linear}, 
+where the largest gradients in the solution are near the particle surface.
+The discretization of boundary conditions far away from the particle may be improved
+by including the linear correction from the asymptotic solution, or applying
 
@@
     \label{fig:Vortex2}
+    \end{center}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=1\textwidth]{figs/quadratic_order.eps}
+        \caption[Quadratic convergence of steady-state velocity]{
+        The discretization error between the numerical and analytical solutions for 
+        $\alpha = 0$ ,$\Du = 0.5$, $\bar\zeta = 6$ and $R_{max} = 100$. The markers represent
+        the discretization errors for various grid sizes, and the dotted lines correspond to linear
+        functions of $\beta$, scaled by $4^n$. As mesh cell size decreases by 2, the discretization
+        }
+	    \label{fig:quadratic}
     \end{center}

### 2013-01-03 notes/thesis-latex-template/thesis.tex
Update thesis.

@@
 given an initial solution $\bx_0$.
-Each step requires the computation of the residual vector, $\br = \cO(\bx)$, and
-the gradient matrix of the operator, $\bG = \bnabla \cO(\bx)$, 
-given the current solution $\bx$.
+Each step requires the computation of the residual vector, $\br = \cO(\bx)$, 
+the gradient matrix of the operator, $\bG = \bnabla \cO(\bx)$
+(given the current solution $\bx$)
+and the solution of sparse linear system $\bG \Delta \bx = -\br$.
 
@@
 The source code of the solver is provided in \cite{source}.
+
+MATLAB direct solver is applied to solve the sparse linear system for each Newton step,
+using the backslash operator. 
+The library used for solving the linear system is UMFPACK 5.0 \cite{davis2004umfpack}
+(Unsymmetric MultiFrontal Sparse LU Factorization Package),
+as reported by MATLAB function call, \verb|spparms('spumoni', 2)|.
 
@@
 \section{Future Work}
-Future work may include replacing the full Newton step by an iterative linear solver
+Future work may include optimizing the direct sparse linear solver 
+to use the ordering data from previous calls,
+or replacing the full Newton step by an iterative linear solver
 (e.g. using preconditioned Krylov subspace methods \cite{saad2003book} or

### 2013-01-11 notes/thesis-latex-template/thesis.tex
Update thesis.

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Ion-exchanger results}
-For $\beta \ll 1$, the linear regime is dominant \eqref{eq:linear_velocity}.
+For $\beta \ll 1$, the linear regime \cite{yariv2010asymptotic} is dominant.
 When $\gamma \approx 1$, the cubic regime, where $\cU = O(\beta^3)$, 
@@
 
-\subsection{Electrophoresis results}
-In this scenario the linear regime is dominant \eqref{eq:linear_velocity}.
-In order to verify the solver, the numerical steady-state velocity is compared to the
-analytical solution \cite{schnitzer2012cubic}. Since the cubic correction is much smaller than
-the linear solution for $\beta \ll 1$, the difference between numerical results and
-the linear solution is compared to the cubic correction term.
-
-Since the leading order of the solution $\cU(\beta)$ is linear for $\beta \ll 1$, 
-the numerical discretization error is $O(\beta)$ as well.
-In order to reduce the discretization error of the numerical solution \eqref{eq:disc_zero_force}
-and after verifying that the discretization error converges as $O(h^2)$ (Figure \ref{fig:quadratic}),
-we employ Richardson extrapolation to $\cU^h$ and $\cU^{2h}$:
-\begin{equation}
-\hat\cU = \frac{4}{3} \cU^h - \frac{1}{3} \cU^{2h}.
-\end{equation}
-The results of the extrapolation and $\hat\cU$ the analytical results 
-are given at Figures \ref{fig:Electrophoresis1} and \ref{fig:Electrophoresis2}.
-The numerical solver uses $R_{\max} = 10^2$,
-$K = 3$, $M = 5$ and $\beta = 0.1 \cdot 2^{t}$ for $t = -2:0.5:5$.
-The solver is applied to 2 grids of $N_r \times N_\theta = (128 \times 128)$ as the coarse grid 
-(with $\Delta_r \approx 0.037$), and $N_r \times N_\theta = (256 \times 256)$ as the fine grid
-(with $\Delta_r \approx 0.018$), in order to use Richardson extrapolation for $\hat\cU$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-\section{Discussion} \label{sec:discussion}
-A numerical framework for solver construction for a
-nonlinear electrokinetic transport system is described.
-The framework is applied to two electrokinetic problems: the migration of ion-exchangers
-and surface-charged inert particle electrophoresis.
-The numerical results exhibit a good correspondence to the asymptotic linear model as
-shown above.
-Moreover, two interesting phenomena (cubic regime and downstream vortex) were predicted
-using the numerical results, and were verified using asymptotic expansion of the
-nonlinear system.
-
-The computational grid is created to have fine resolution near the particle surface, while
-approximating the far-away boundary conditions. The logarithmic discretization is motivated
-by the solution of the linearized system at Section \ref{app:linear}, 
-where the largest gradients in the solution are near the particle surface.
-The discretization of boundary conditions far away from the particle may be improved
-by including the linear correction from the asymptotic solution, or applying
-
-For strong electric field ($\beta \gg 1)$, the nonlinear effects become dominant and
-another boundary-layer structure is expected to form near the particle surface. 
-In order to achieve high numerical accuracy, the grid discretization should be made finer
-near the particle surface (at $r = 1$), while $R_{max}$ can be made smaller.
-In addition, the continuation of the solution between different $\beta$ values
-should advance in finer steps, for Newton method convergence.
-
-\section{Future Work}
-Future work may include optimizing the direct sparse linear solver 
-to use the ordering data from previous calls,
-or replacing the full Newton step by an iterative linear solver
-(e.g. using preconditioned Krylov subspace methods \cite{saad2003book} or
-Multigrid), allowing finer grids to be used.
-In addition, the framework may be used for automatic construction of Newton solvers 
-for other nonlinear PDE systems, for example -- for particle with different surface 
-properties, or different particle shape.
-
 \begin{figure}
     \begin{center}
-    \includegraphics[width=0.8\textwidth]{figs/Cubic/ionex_cubic1.eps}
-    \includegraphics[width=0.8\textwidth]{figs/Cubic/ionex_cubic2.eps}
+    \includegraphics[width=0.7\textwidth]{figs/Cubic/ionex_cubic1.eps}
+    \includegraphics[width=0.7\textwidth]{figs/Cubic/ionex_cubic2.eps}
         \caption[Ion exchanger steady-state velocity]{
@@
     \begin{center}
-	\includegraphics[width=0.8\textwidth]{figs/Cubic/Stream/N1.eps}
-	\includegraphics[width=0.8\textwidth]{figs/Cubic/Stream/N2.eps}
-	\includegraphics[width=0.8\textwidth]{figs/Cubic/Stream/N5.eps}
-	\includegraphics[width=0.8\textwidth]{figs/Cubic/Stream/N10.eps}
+	\includegraphics[width=0.7\textwidth]{figs/Cubic/Stream/N1.eps}
+	\includegraphics[width=0.7\textwidth]{figs/Cubic/Stream/N2.eps}
+	\includegraphics[width=0.7\textwidth]{figs/Cubic/Stream/N5.eps}
+	\includegraphics[width=0.7\textwidth]{figs/Cubic/Stream/N10.eps}
         \caption[Ion exchanger streamlines -- numerical results]{
@@
     \begin{center}
-	\includegraphics[width=0.8\textwidth]{figs/Cubic/Stream/A1.eps}
-	\includegraphics[width=0.8\textwidth]{figs/Cubic/Stream/A2.eps}
-	\includegraphics[width=0.8\textwidth]{figs/Cubic/Stream/A5.eps}
-	\includegraphics[width=0.8\textwidth]{figs/Cubic/Stream/A10.eps}
+	\includegraphics[width=0.7\textwidth]{figs/Cubic/Stream/A1.eps}
+	\includegraphics[width=0.7\textwidth]{figs/Cubic/Stream/A2.eps}
+	\includegraphics[width=0.7\textwidth]{figs/Cubic/Stream/A5.eps}
+	\includegraphics[width=0.7\textwidth]{figs/Cubic/Stream/A10.eps}
         \caption[Ion exchanger streamlines -- analytical results]{
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Electrophoresis results}
+For $\beta \ll 1$, the linear regime \cite{schnitzer2012surface} is dominant.
+In order to verify the solver, the numerical steady-state velocity is compared to the
+analytical solution \cite{schnitzer2012cubic}, derived by Schnitzer and Yariv. 
+Since the cubic correction is much smaller than
+the linear solution for $\beta \ll 1$, the difference between numerical results and
+the linear solution is compared to the cubic correction term.
+
+Since the leading order of the solution $\cU(\beta)$ is linear for $\beta \ll 1$, 
+the numerical discretization error is $O(\beta)$ as well.
+In order to reduce the discretization error of the numerical solution \eqref{eq:disc_zero_force}
+and after verifying that the discretization error converges as $O(h^2)$ (Figure \ref{fig:quadratic}),
+we employ Richardson extrapolation to $\cU^h$ and $\cU^{2h}$:
+\begin{equation}
+\hat\cU = \frac{4}{3} \cU^h - \frac{1}{3} \cU^{2h}.
+\end{equation}
+The results of the extrapolation and $\hat\cU$ the analytical results 
+are given at Figures \ref{fig:Electrophoresis1} and \ref{fig:Electrophoresis2}.
+The numerical solver uses $R_{\max} = 10^2$,
+$K = 3$, $M = 5$ and $\beta = 0.1 \cdot 2^{t}$ for $t = -2:0.5:5$.
+The solver is applied to 2 grids of $N_r \times N_\theta = (128 \times 128)$ as the coarse grid 
+(with $\Delta_r \approx 0.037$), and $N_r \times N_\theta = (256 \times 256)$ as the fine grid
+(with $\Delta_r \approx 0.018$), in order to use Richardson extrapolation for $\hat\cU$.
+
 \begin{figure}
@@
         The discretization error between the numerical and analytical solutions for 
-        $\alpha = 0$ ,$\Du = 0.5$, $\bar\zeta = 6$ and $R_{max} = 100$. The markers represent
+        $\alpha = 0$, $\Du = 0.5$, $\bar\zeta = 6$ and $R_{max} = 100$. The markers represent
         the discretization errors for various grid sizes, and the dotted lines correspond to linear
-        functions of $\beta$, scaled by $4^n$. As mesh cell size decreases by 2, the discretization
+        functions of $\beta$, scaled by $4^n$. 
+        The graph show that, as the number of grid points in each dimension increases by 2, 
+        the discretization error decreases by 4.
         }
@@
 \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Electrophoresis for large $\beta$ }
+When the electric field is large, nonlinear effects dominate the solution.
+In order to investigate the problem solution for strong electric fields, 
+we have run the solver on the TAMNUN HPC cluster \cite{tamnun}.
+Large grid sizes ($256 \times 256$ and $512 \times 512$)
+are used to verify that the numerical solution converges when the grid becomes finer
+and that no numerical artifacts are present in the solution.
+Moreover, several $R_{max} \in \{10, 30, 100\}$ values are used, to make sure it
+has no major impact on the solution.
+
+The results are shown at the following figures. 
+The steady-state velocity results are shown in Figure \ref{fig:LargeBetaV}. 
+When $\beta$ becomes large, the salt concentration $C$ near the front of the particle approaches zero,
+while creating a wake behind the particle.
+This is results in high gradients in $\log C$ near the front of the particle 
+(Figures \ref{fig:LargeBeta1a}, \ref{fig:LargeBeta1b} and \ref{fig:LargeBeta1c}) 
+and, therefore, strong electric field $\bE$ form near the particle surface 
+(Figures \ref{fig:LargeBeta2a}, \ref{fig:LargeBeta2b} and \ref{fig:LargeBeta2c})
+due to effective boundary conditions at Eq. \ref{eq:ephor_bnd}. 
+The streamline pattern doesn't change drastically for different electric field magnitudes, as shown in Figure \ref{fig:LargeBeta3}.
+
+It appears that a boundary layer starts to form around the front of the particle for strong
+electric fields. This causes numerical problems to the current solver -- yielding a convergence
+problems for $\beta > 5$. The convergence problems start earlier
+for smaller grid size, and for higher $R_{max}$ values, probably
+due to insufficient resolution at the $\brhat$ direction near
+the particle surface.
+
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=1\textwidth]{figs/LargeBetaV.eps}
+        \caption{Large $\beta$ results for $\cU$ ($\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$).}
+	    \label{fig:LargeBetaV}	    
+    \end{center}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=1.000e-01_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=2.000e-01_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=3.000e-01_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=4.000e-01_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=6.000e-01_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=8.000e-01_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=1.000e+00_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=2.000e+00_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=3.000e+00_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=4.000e+00_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=5.000e+00_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=6.000e+00_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
+        \caption{Large $\beta$ results for $C$: grid size $128 \times 128$, 
+        $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.}
+	    \label{fig:LargeBeta1a}	    
+    \end{center}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=1.000e-01_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=2.000e-01_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=3.000e-01_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=4.000e-01_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=6.000e-01_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=8.000e-01_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=1.000e+00_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=2.000e+00_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=3.000e+00_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=4.000e+00_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=5.000e+00_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=6.000e+00_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
+        \caption{Large $\beta$ results for $C$: grid size $256 \times 256$, 
+        $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.}
+	    \label{fig:LargeBeta1b}	    
+    \end{center}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=1.000e-01_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=2.000e-01_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=3.000e-01_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=4.000e-01_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=6.000e-01_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=8.000e-01_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=1.000e+00_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=2.000e+00_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=3.000e+00_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=4.000e+00_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=5.000e+00_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=6.000e+00_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
+        \caption{Large $\beta$ results for $C$: grid size $512 \times 512$, 
+        $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.}
+	    \label{fig:LargeBeta1c}	    
+    \end{center}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=1.000e-01_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=2.000e-01_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=3.000e-01_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=4.000e-01_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=6.000e-01_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=8.000e-01_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=1.000e+00_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=2.000e+00_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=3.000e+00_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=4.000e+00_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=5.000e+00_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=6.000e+00_[129x129]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
+        \caption{Large $\beta$ results for $\varPhi$:
+        grid size $128 \times 128$, $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.}
+	    \label{fig:LargeBeta2a}	    
+    \end{center}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=1.000e-01_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=2.000e-01_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=3.000e-01_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=4.000e-01_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=6.000e-01_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=8.000e-01_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=1.000e+00_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=2.000e+00_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=3.000e+00_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=4.000e+00_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=5.000e+00_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=6.000e+00_[257x257]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
+        \caption{Large $\beta$ results for $\varPhi$:
+        grid size $256 \times 256$, $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.}
+	    \label{fig:LargeBeta2b}	    
+    \end{center}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=1.000e-01_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=2.000e-01_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=3.000e-01_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=4.000e-01_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=6.000e-01_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=8.000e-01_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=1.000e+00_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=2.000e+00_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=3.000e+00_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=4.000e+00_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=5.000e+00_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=6.000e+00_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
+        \caption{Large $\beta$ results for $\varPhi$:
+        grid size $512 \times 512$, $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.}
+	    \label{fig:LargeBeta2c}	    
+    \end{center}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=1.000e-01_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_Psi.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=2.000e-01_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_Psi.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=3.000e-01_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_Psi.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=4.000e-01_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_Psi.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=6.000e-01_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_Psi.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=8.000e-01_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_Psi.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=1.000e+00_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_Psi.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=2.000e+00_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_Psi.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=3.000e+00_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_Psi.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=4.000e+00_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_Psi.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=5.000e+00_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_Psi.eps}
+    \includegraphics[width=0.32\textwidth]{figs/LargeBeta/sol_beta=6.000e+00_[513x513]_Rmax=30.0_Du=1.00_zeta=10.00_alpha=0.50_Psi.eps}
+        \caption{Large $\beta$ streamlines results: grid size $512 \times 512$, 
+        $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.}
+	    \label{fig:LargeBeta3}	    
+    \end{center}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+\section{Discussion} \label{sec:discussion}
+A numerical framework for solver construction for a
+nonlinear electrokinetic transport system is described.
+The framework is applied to two electrokinetic problems: the migration of ion-exchangers
+and surface-charged inert particle electrophoresis.
+The numerical results exhibit a good correspondence to the asymptotic linear model as
+shown above.
+Moreover, two interesting phenomena (cubic regime and downstream vortex) were predicted
+using the numerical results, and were verified using asymptotic expansion of the
+nonlinear system.
+
+The computational grid is created to have fine resolution near the particle surface, while
+approximating the far-away boundary conditions. The logarithmic discretization is motivated
+by the solution of the linearized system at Section \ref{app:linear}, 
+where the largest gradients in the solution are near the particle surface.
+The discretization of boundary conditions far away from the particle may be improved
+by including the linear correction from the asymptotic solution, or applying
+
+For strong electric field ($\beta \gg 1)$, the nonlinear effects become dominant and
+another boundary-layer structure is expected to form near the particle surface. 
+In order to achieve high numerical accuracy, the grid discretization should be made finer
+near the particle surface (at $r = 1$), while $R_{max}$ can be made smaller.
+In addition, the continuation of the solution between different $\beta$ values
+should advance in finer steps, for Newton method convergence.
+
+\section{Future Work}
+Future work may include optimizing the direct sparse linear solver 
+to use the ordering data from previous calls,
+or replacing the full Newton step by an iterative linear solver
+(e.g. using preconditioned Krylov subspace methods \cite{saad2003book} or
+Multigrid), allowing finer grids to be used.
+In addition, the framework may be used for automatic construction of Newton solvers 
+for other nonlinear PDE systems, for example -- for particle with different surface 
+properties, or different particle shape.
 

### 2013-01-11 src/plot_results_for_thesis.m

@@ -7,6 +7,8 @@ function plot_results_for_thesis(filename)
 %             beta, N+1, N+1, Rmax);
 % load([filename '.mat'])
 load(filename)
+[p, n] = fileparts(filename);
+filename = fullfile(p, n);
 disp(filename)
 if 1
     clf;
@@ -28,7 +30,7 @@ if 1
     axis([-1 1 -1 1]*3)
     axis equal
     colorbar
-    title('Salt concentration (C)')
+    title(sprintf('Salt concentration (C): \\beta = %.2f', sol.beta))
     print('-depsc2', [filename '_C.eps'])
 end
 if 1
@@ -41,7 +43,7 @@ if 1
     z = s.Psi(I, :);
     x = R .* cos(T);
     y = R .* sin(T);
-    c = linspace(-1, 1, 61)*3 * sol.beta;
+    c = linspace(-1, 1, 101)*10;
     hold on;
     contour(x, y, z, c)
     contour(x, -y, z, c)
@@ -49,7 +51,7 @@ if 1
     fill(cos(t), sin(t), [1 1 1]*0.5)
     axis([-1 1 -1 1]*3)
     axis equal
-    title('Streamlines (\Psi)')
+    title(sprintf('Streamlines (\\Psi): \\beta = %.2f', sol.beta))
     print('-depsc2', [filename '_Psi.eps'])
 end
 
@@ -87,6 +89,11 @@ if 1
     quiver([x; x], [y; -y], scale*[Ex; Ex], scale*[Ey; -Ey], 0, 'k')
     axis([-1 1 -1 1]*2)
     axis equal
-    title('Electric potential (\phi) and field at the surface (E)')
+    title(sprintf('Electric potential (\\phi) and field at the surface (E): \\beta = %.2f', sol.beta))
     print('-depsc2', [filename '_PhiE.eps'])
+end
+
+if 1
+    sol = rmfield(sol, {'var', 'C', 'Phi', 'Vr', 'Vt', 'P', 'bnd', 'eqn', 'grid'});
+    save([filename '_lite.mat'], 'sol')
 end

### 2013-01-11 src/plot_velocity_vs_beta.m

@@ -1,0 +1,39 @@
+function plot_velocity_vs_beta
+    clf;
+    M = {};
+    hold on;
+    iter(128, 10,  '-s', [1 0 0])
+    iter(128, 30,  '-o', [1 0 0])
+    iter(128, 100, '-d', [1 0 0])
+    iter(256, 10,  '-s', [0 .5 0])
+    iter(256, 30,  '-o', [0 .5 0])
+    iter(256, 100, '-d', [0 .5 0])
+    iter(512, 10,  '-s', [0 0 1])
+    iter(512, 30,  '-o', [0 0 1])
+    iter(512, 100, '-d', [0 0 1])
+    xlim([0 6])
+    legend(M, 'Location', 'NorthWest')
+    print -depsc2 LargeBetaV.eps
+
+    function iter(N, Rmax, linespec, c)
+        if nargin < 3
+            linespec = '-';
+        end
+        f = sprintf('MATs/*[%dx%d]_Rmax=%.1f*_lite.mat', N+1, N+1, Rmax);
+        L = glob(f).';
+        s = cellfun(@load_data, L, 'UniformOutput', false);
+        res = cat(1, s{:});
+        res = sortrows(res);
+        beta = res(:, 1);
+        V = res(:, 2);
+        plot(beta, V, linespec, 'Color', c)
+        M{numel(M)+1} = sprintf('[%dx%d] R_{max}=%.0f', N, N, Rmax);
+    end
+
+end
+
+function res = load_data(f)
+    s = load(f);
+    s = s.sol;
+    res = [s.beta, s.Vinf];
+end

### 2013-01-14 notes/thesis-latex-template/thesis.tex
Update thesis.

@@
 The discretization of boundary conditions far away from the particle may be improved
-by including the linear correction from the asymptotic solution, or applying
+by including the linear correction from the asymptotic solution, or reformulation of
+far-away boundary condition according to the asymptotic behavior of the analytic solution
+far away from the particle.
 
 For strong electric field ($\beta \gg 1)$, the nonlinear effects become dominant and
-another boundary-layer structure is expected to form near the particle surface. 
+another boundary-layer structure is begins to form near the particle surface. 
 In order to achieve high numerical accuracy, the grid discretization should be made finer
-near the particle surface (at $r = 1$), while $R_{max}$ can be made smaller.
+near the particle surface (at $r = 1$), while $R_{max}$ can be made smaller. Moreover, different discretization scheme may be used for
+the $r$ coordinate, to have higher grid resolution near the particle.
 In addition, the continuation of the solution between different $\beta$ values
-should advance in finer steps, for Newton method convergence.
+should advance in finer steps, to ensure Newton method convergence.
 

### 2013-01-14 src/plot_C_vs_beta.m

@@ -1,0 +1,47 @@
+function plot_C_vs_beta
+    clf;
+    M = {};
+    hold on;
+    for b = 0.1:0.1:10
+        iter(b, 128,  10, '-d', [0 0 1]);
+        iter(b, 128,  30, '-d', [0 0.5 0]);
+        iter(b, 128, 100, '-d', [1 0 0]);
+        iter(b, 256,  10, '-s', [0 0 1]);
+        iter(b, 256,  30, '-s', [0 0.5 0]);
+        iter(b, 256, 100, '-s', [1 0 0]);
+        iter(b, 512,  10, '-o', [0 0 1]);
+        iter(b, 512,  30, '-o', [0 0.5 0]);
+        iter(b, 512, 100, '-o', [1 0 0]);
+        drawnow;
+    end
+%     legend(M, 'Location', 'NorthWest')
+    print -depsc2 LargeBetaV.eps
+
+    function iter(b, N, Rmax, linespec, c)
+        0;
+        if nargin < 4
+            linespec = '-';
+        end
+        f = sprintf('MATs/*beta=%.3e_[%dx%d]_Rmax=%.1f*0.mat', b, N+1, N+1, Rmax);
+        L = glob(f).';
+        if isempty(L)
+            1;
+            return;
+        end
+        f = L{1};
+        s = load(f);
+        C = s.sol.C;
+        r = C.grid.r;
+        C = regrid(C);
+        plot(b, mean(C(1:2)), linespec, 'Color', c)
+        M{numel(M)+1} = sprintf('[%dx%d] R_{max}=%.0f', N, N, Rmax);
+%         xlim([1 2])
+    end
+
+end
+
+function res = load_data(f)
+    s = load(f);
+    s = s.sol;
+    res = [s.beta, s.Vinf];
+end

### 2013-01-14 src/plot_Er_vs_beta.m

@@ -1,0 +1,49 @@
+function plot_Er_vs_beta
+    clf;
+    M = {};
+    hold on;
+    for b = 0.1:0.1:10
+        iter(b, 128,  10, '-d', [0 0 1]);
+        iter(b, 128,  30, '-d', [0 0.5 0]);
+        iter(b, 128, 100, '-d', [1 0 0]);
+        iter(b, 256,  10, '-s', [0 0 1]);
+        iter(b, 256,  30, '-s', [0 0.5 0]);
+        iter(b, 256, 100, '-s', [1 0 0]);
+        iter(b, 512,  10, '-o', [0 0 1]);
+        iter(b, 512,  30, '-o', [0 0.5 0]);
+        iter(b, 512, 100, '-o', [1 0 0]);
+        drawnow;
+    end
+%     legend(M, 'Location', 'NorthWest')
+    print -depsc2 LargeBetaV.eps
+
+    function iter(b, N, Rmax, linespec, c)
+        0;
+        if nargin < 4
+            linespec = '-';
+        end
+        f = sprintf('MATs/*beta=%.3e_[%dx%d]_Rmax=%.1f*0.mat', b, N+1, N+1, Rmax);
+        L = glob(f).';
+        if isempty(L)
+            1;
+            return;
+        end
+        f = L{1};
+        s = load(f);
+        Phi = s.sol.Phi;
+        r = Phi.grid.r;
+        Phi = regrid(Phi);
+        Er = -diff(Phi(:, 1)) ./ diff(r);
+        r = convn(r, [1;1]/2, 'valid');
+        plot(b, Er(1) / b, linespec, 'Color', c)
+        M{numel(M)+1} = sprintf('[%dx%d] R_{max}=%.0f', N, N, Rmax);
+%         xlim([1 2])
+    end
+
+end
+
+function res = load_data(f)
+    s = load(f);
+    s = s.sol;
+    res = [s.beta, s.Vinf];
+end

### 2013-01-24 src/plot_results_for_thesis.m
Update thesis plots.

@@ -34,25 +34,27 @@ if 1
     print('-depsc2', [filename '_C.eps'])
 end
 if 1
-    clf;
-    hold on;
-    s = streamfunc(sol);
-    I = find(s.grid.Psi.r < 10);
-    R = s.grid.Psi.R(I, :);
-    T = s.grid.Psi.T(I, :);
-    z = s.Psi(I, :);
-    x = R .* cos(T);
-    y = R .* sin(T);
-    c = linspace(-1, 1, 101)*10;
-    hold on;
-    contour(x, y, z, c)
-    contour(x, -y, z, c)
-    t = linspace(0, 2*pi, 100);
-    fill(cos(t), sin(t), [1 1 1]*0.5)
-    axis([-1 1 -1 1]*3)
-    axis equal
-    title(sprintf('Streamlines (\\Psi): \\beta = %.2f', sol.beta))
-    print('-depsc2', [filename '_Psi.eps'])
+    for d = [1 -1]
+        clf;
+        hold on;
+        s = streamfunc(sol);
+        I = find(s.grid.Psi.r < 10);
+        R = s.grid.Psi.R(I, :);
+        T = s.grid.Psi.T(I, :);
+        z = s.Psi(I, :);
+        x = R .* cos(T);
+        y = R .* sin(T);
+        c = linspace(-1, 1, 101)*sol.beta*10;
+        hold on;
+        contour(d*x, y, z, c)
+        contour(d*x, -y, z, c)
+        t = linspace(0, 2*pi, 100);
+        fill(cos(t), sin(t), [1 1 1]*0.5)
+        axis([-1 1 -1 1]*3)
+        axis equal
+        title(sprintf('Streamlines (\\Psi): \\beta = %.2f', sol.beta))
+        print('-depsc2', [filename sprintf('_[%d]_Psi.eps', d)])
+    end
 end
 
 if 1

### 2013-01-24 src/plot_stokes_solution.m

@@ -1,0 +1,27 @@
+clear all;
+clf;
+
+r = linspace(1, 10, 513);
+t = linspace(0, pi, 513);
+[R, T] = ndgrid(r, t);
+beta = 0.1;
+
+Du = 1;
+zeta = 10;
+U = beta * (Du*log(16) + zeta)/(1 + 2*Du);
+Psi = U * 0.5 * (R.^(-2) - R) .* sin(T);
+
+z = Psi;
+z(:, [1 end]) = 0;
+x = R .* cos(T);
+y = R .* sin(T);
+c = linspace(-1, 1, 101)*beta*10;
+hold on;
+contour(x, y, z, c)
+contour(x, -y, z, c)
+t = linspace(0, 2*pi, 100);
+fill(cos(t), sin(t), [1 1 1]*0.5)
+axis([-1 1 -1 1]*3)
+axis equal
+title(sprintf('Streamlines (\\Psi): \\beta = %.2f', beta))
+print('-depsc2', 'LinearStokes_Psi.eps')

### 2013-01-24 src/plot_velocity_vs_beta.m

@@ -2,20 +2,30 @@ function plot_velocity_vs_beta
     clf;
     M = {};
     hold on;
-    iter(128, 10,  '-s', [1 0 0])
-    iter(128, 30,  '-o', [1 0 0])
-    iter(128, 100, '-d', [1 0 0])
-    iter(256, 10,  '-s', [0 .5 0])
-    iter(256, 30,  '-o', [0 .5 0])
-    iter(256, 100, '-d', [0 .5 0])
-    iter(512, 10,  '-s', [0 0 1])
-    iter(512, 30,  '-o', [0 0 1])
-    iter(512, 100, '-d', [0 0 1])
+    iter(128, 10,  '-s', [1 0 0]);
+    iter(128, 30,  '-o', [1 0 0]);
+    [b1, v1] = iter(128, 100, '-d', [1 0 0]);
+    iter(256, 10,  '-s', [0 .5 0]);
+    iter(256, 30,  '-o', [0 .5 0]);
+    [b2, v2] = iter(256, 100, '-d', [0 .5 0]);
+    iter(512, 10,  '-s', [0 0 1]);
+    iter(512, 30,  '-o', [0 0 1]);
+    [b3, v3] = iter(512, 100, '-d', [0 0 1]);
     xlim([0 6])
     legend(M, 'Location', 'NorthWest')
     print -depsc2 LargeBetaV.eps
+    
+    clf;
+    x_max = 5;
+    [b1, v1] = select(b1, v1, @(x) x < x_max);
+    [b2, v2] = select(b2, v2, @(x) x < x_max);
+    [b3, v3] = select(b3, v3, @(x) x < x_max);
+    plot(b1, [(v2 - v1) ./ (v3 - v2)], '.-');
+    xlabel('\beta')
+    ylabel('(V_{128x128} - V_{256x256}) / (V_{256x256} - V_{512x512})')
+    print -depsc2 LargeBetaRatio.eps
 
-    function iter(N, Rmax, linespec, c)
+    function [beta, V] = iter(N, Rmax, linespec, c)
         if nargin < 3
             linespec = '-';
         end
@@ -36,4 +46,10 @@ function res = load_data(f)
     s = load(f);
     s = s.sol;
     res = [s.beta, s.Vinf];
+end
+
+function [x, y] = select(x, y, pred)
+    I = pred(x);
+    x = x(I);
+    y = y(I);
 end

### 2013-02-01 notes/thesis-latex-template/thesis.tex
Update thesis plots.
Update thesis.

--- 2013-01-03 notes/thesis-latex-template/thesis.tex
@@
 \setlength{\topmargin}{0.05in}
-\setlength{\headheight}{0.2in}
+\setlength{\headheight}{0.05in}
 \setlength{\headsep}{0.1in}
@@
 \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Electrophoresis for large $\beta$ }
+When the electric field is large, nonlinear effects dominate the solution.
+In order to investigate the problem solution for strong electric fields, 
+we have run the solver on the TAMNUN HPC cluster \cite{tamnun}.
+Large grid sizes are used to verify that the numerical solution converges when the grid becomes finer and that no numerical artifacts are present in the solution.
+Moreover, several $R_{max} \in \{10, 30, 100\}$ values are used, to make sure it has no major impact on the solution.
+The results are shown at the following figures. 
+The steady-state velocity results are shown for several grid resolutions and several $R_{max}$ values in Figure \ref{fig:LargeBetaV_grids}, and the estimated rate of convergence is shown at Figure \ref{fig:LargeBetaRatio}.
+
+When $\beta$ becomes large, the salt concentration $C$ near the front of the particle 
+(at $\theta \approx 0$) approaches zero, while creating a wake behind the particle 
+(at $\theta \approx \pi$).
+This is results in high gradients in $\log C$ near the front of the particle (Figures \ref{fig:LargeBeta_C1}, \ref{fig:LargeBeta_C2} and
+\ref{fig:LargeBeta_C3}) and, therefore, strong electric field $\bE$ form near the particle surface (Figures \ref{fig:LargeBeta_Phi1}, \ref{fig:LargeBeta_Phi2} and \ref{fig:LargeBeta_Phi3}) due to effective boundary conditions at Eq.
+\ref{eq:ephor_bnd}.
+The streamline pattern doesn't change drastically for different electric field magnitudes, as shown in Figure \ref{fig:LargeBeta_Psi1}, \ref{fig:LargeBeta_Psi2} and \ref{fig:LargeBeta_Psi3}. 
+The resulting flow pattern is similar to the Stokes creeping flow, as shown in Figure
+\ref{fig:LargeBeta_PsiStokes}.
+
+The numerical results suggest that a boundary 
+layer starts to form around the front of the particle for strong
+electric fields (see Figure \ref{fig:LargeBeta_BoundaryLayer}). 
+This causes numerical problems to the current solver -- yielding a convergence
+problems for large $\beta$. The convergence problems start earlier
+for smaller grid size, and for higher $R_{max}$ values, probably
+due to insufficient resolution at the $\brhat$ direction near
+the particle surface.
+
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=.45\textwidth]{figs/LargeBetaV_[128_256_512]_Rmax=10.eps}
+    \includegraphics[width=.45\textwidth]{figs/LargeBetaV_[512x512]_Rmax=10_30_100.eps}
+        \caption[Large $\beta$ results for $\cU$]
+{Large $\beta$ results for $\cU$ ($\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$). 
+The left figure shows the numerical results of $\cU(\beta)$ for $R_{max} = 10$ and the following grid sizes: $128 \times 128$, $256 \times 256$, $512 \times 512$. 
+The right figure shows the numerical results of $\cU(\beta)$ for
+$512 \times 512$ grid for $R_{max} = 100, 30, 10$. For small values of $\beta$, the linear
+regime of $\cU(\beta)$ is dominant. However, for larger values of $\beta$, the numerical solution
+deviates significantly from the linear regime. For $\beta > 6$, the numerical solver convergence
+is slowing and for $\beta \sim 7$, the solver fails to converge. As the grid resolution near
+the particle surface becomes finer (when $N_r$ increases or $R_{max}$ decreases), the solver
+convergence is better.}
+	    \label{fig:LargeBetaV_grids}	    
+    \end{center}
+\end{figure}
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=.5\textwidth]{figs/LargeBetaRatio.eps}
+        \caption[Rate of convergence estimation for $\cU$ at large $\beta$]
+        {Rate of convergence estimation for $\cU$ at large $\beta$  
+        ($\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$). 
+        The numerical results of $\cU(\beta)$, for the grid sizes of 
+        $128 \times 128$, $256 \times 256$, $512 \times 512$. 
+        The rate of convergence $r(\beta)$ is estimated by 
+        $r(\beta) \triangleq \left(\cU^{4h}(\beta) - \cU^{2h}(\beta)\right)/\left(\cU^{2h}(\beta) - \cU^{h}(\beta)\right)$.
+        For small $\beta$, $r(\beta) \rightarrow 4$, showing 
+        quadratic convergence for the linear regime. 
+        For moderate $\beta$, the convergence rate slows down 
+        and deteriorates for large $\beta$ values.
+        }
+	    \label{fig:LargeBetaRatio}
+    \end{center}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=1\textwidth]{figs/LargeBeta/sol_beta=1.000e-01_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
+        \caption[$\beta = 0.1$ results for $C$]
+        {$\beta = 0.1$ results for $C$: grid size $512 \times 512$, 
+        $R_{max} = 10$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.
+        Here the linear regime dominates the solution for 
+        $C_\beta(r, \theta) \approx 1 - \beta \frac{\cos\theta}{2r^2}$.}
+	    \label{fig:LargeBeta_C1}	    
+    \end{center}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=1\textwidth]{figs/LargeBeta/sol_beta=8.000e-01_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
+        \caption[$\beta = 0.8$ results for $C$]
+        {$\beta = 0.8$ results for $C$: grid size $512 \times 512$, 
+        $R_{max} = 10$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.
+        For moderate $\beta$ values, the salt concentration starts
+        to form a wake behind the particle ($\theta \approx \pi$).}
+	    \label{fig:LargeBeta_C2}	    
+    \end{center}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=1\textwidth]{figs/LargeBeta/sol_beta=5.000e+00_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
+        \caption[$\beta = 5.0$ results for $C$]
+        {$\beta = 5.0$ results for $C$: grid size $512 \times 512$, 
+        $R_{max} = 10$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.
+        For large values of $\beta$, there is a significant drop in
+        salt concentration at the front of the particle -- 
+        $C$ approaches zero at $\theta \approx 0$, such that 
+        $\deriv{C}{r}$ becomes large 
+        (since the change in $C$ happens at a small length scale).
+        Due to the boundary conditions of the electrophoresis problem
+        (given by Eq. \ref{eq:ephor_bnd}), the electric field radial
+        component given by 
+        $E_r = -\deriv{\varPhi}{r} = -\frac{1}{C}\deriv{C}{r}$, 
+        becomes singular where $C \rightarrow 0$.
+        }
+	    \label{fig:LargeBeta_C3}	    
+    \end{center}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=1\textwidth]{figs/LargeBeta/sol_beta=1.000e-01_[129x129]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
+        \caption[$\beta = 0.1$ results for $\varPhi$]
+        {$\beta = 0.1$ results for $\varPhi$:
+        grid size $512 \times 512$, $R_{max} = 10$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$. 
+        The electric potential and the electric field results are multiplied by $\beta^{-1}$,
+	    so the linear regime appears unchanged for different values of $\beta$.
+        Here the linear regime dominates the solution for 
+        $\varPhi_\beta(r, \theta) \approx -\beta {r \cos\theta}$,
+        hence the electric field is constant for weak electric fields:
+        $\bE \approx \beta \ui$.}
+	    \label{fig:LargeBeta_Phi1}
+    \end{center}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=1\textwidth]{figs/LargeBeta/sol_beta=8.000e-01_[129x129]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
+        \caption[$\beta = 0.8$ results for $\varPhi$]
+        {$\beta = 0.8$ results for $\varPhi$:
+        grid size $512 \times 512$, $R_{max} = 10$, $\Du = 1$, 
+        $\bar\zeta = 10$, $\alpha = 0.5$. 
+	    The electric potential and the electric field results are multiplied by $\beta^{-1}$,
+	    so the linear regime appears unchanged for different values of $\beta$.
+        For moderate values of $\beta$,
+        the symmetry breaks and the electric field becomes stronger 
+        near the front of the particle than at the back.}
+	    \label{fig:LargeBeta_Phi2}
+    \end{center}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=1\textwidth]{figs/LargeBeta/sol_beta=5.000e+00_[129x129]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
+        \caption[$\beta = 5.0$ results for $\varPhi$]
+        {$\beta = 5.0$ results for $\varPhi$:
+        grid size $512 \times 512$, $R_{max} = 10$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.
+        The electric potential and the electric field results are multiplied by $\beta^{-1}$,
+	    so the linear regime appears unchanged for different values of $\beta$.
+	    For large values of $\beta$, the electric field radial component $E_r = -\deriv{\varPhi}{r}$
+	    at the particle front becomes much larger than the electric field at the particle back.
+		}
+	    \label{fig:LargeBeta_Phi3}
+    \end{center}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=1\textwidth]{figs/LargeBeta/sol_beta=1.000e-01_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_[1]_Psi.eps}
+        \caption[$\beta = 0.1$ results for $\Psi$]
+        {$\beta = 0.1$ streamlines results: grid size $512 \times 512$, 
+        $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.
+        The numerical results for $\Psi$ is scaled by $\beta^{-1}$, so the linear regime
+        will appear the same for different $\beta$ values.}
+	    \label{fig:LargeBeta_Psi1}	    
+    \end{center}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=1\textwidth]{figs/LargeBeta/sol_beta=8.000e-01_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_[1]_Psi.eps}
+        \caption[$\beta = 0.8$ results for $\Psi$]
+        {$\beta = 0.8$ streamlines results: grid size $512 \times 512$, 
+        $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.
+        The numerical results for $\Psi$ is scaled by $\beta^{-1}$, so the linear regime
+        will appear the same for different $\beta$ values.}
+	    \label{fig:LargeBeta_Psi2}	    
+    \end{center}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=1\textwidth]{figs/LargeBeta/sol_beta=5.000e+00_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_[1]_Psi.eps}
+        \caption[$\beta = 5.0$ results for $\Psi$]
+        {$\beta = 5.0$ streamlines results: grid size $512 \times 512$, 
+        $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.
+        The numerical results for $\Psi$ is scaled by $\beta^{-1}$, so the linear regime
+        will appear the same for different $\beta$ values.}
+	    \label{fig:LargeBeta_Psi3}	    
+    \end{center}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=1\textwidth]{figs/LinearStokes_Psi.eps}
+        \caption[Stokes flow results]
+        {Stokes flow streamlines results: grid size $512 \times 512$, 
+        $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.
+        The numerical results for $\Psi$ is scaled by $\beta^{-1}$, so the linear regime
+        will appear the same for different $\beta$ values. Note that the numerical results
+        show very similar flow pattern to the analytical Stokes flow.}
+	    \label{fig:LargeBeta_PsiStokes}	    
+    \end{center}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=1\textwidth]{figs/BoundaryLayerWidth.eps}
+        \caption[Electric field boundary layer]
+        {Electric field boundary layer formation: grid size $512 \times 512$, 
+        $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$. The left
+        graph shows normalized electric field radial component $E_r$ near the particle front
+        ($\theta \approx 0$). The numerical results for $e(\rho) = E_r(r=1+\rho, \theta=0)$
+        are normalized by $\hat{e}(\rho) = \left(e(\rho) - \beta\right)/\left(e(0) - \beta\right)$,
+        where $e(\rho = \infty) = \beta$.
+        The normalized electric field satisfies $\hat{e}(\rho) \in [0, 1]$ and is shown as function
+        of $\rho = r - 1$ at the left graph.
+        In order to estimate the width of the boundary layer, for each $\beta$, we compute the value 
+        of $\bar\rho(\beta) = \min_\rho \{ \rho : \hat{e}(\rho) < 0.5\}$. Each such $\bar\rho(\beta)$
+        is plotted at the left graph as a solid dot on the corresponding line.
+        In addition, $\bar\rho(\beta)$ is plotted as a function of $\beta$ using logarithmic 
+        $y$ axis at the right graph to show that $\bar\rho(\beta) \propto e^{-A\beta}$.
+        Thus, a boundary layer is indeed forming near the front of the particle.
+        }
+	    \label{fig:LargeBeta_BoundaryLayer}	    
+    \end{center}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+\section{Discussion} \label{sec:discussion}
+A numerical framework for solver construction for a
+nonlinear electrokinetic transport system is described.
+The framework is applied to two electrokinetic problems: the migration of ion-exchangers
+and surface-charged inert particle electrophoresis.
+The numerical results exhibit a good correspondence to the asymptotic linear model as
+shown above.
+Moreover, two interesting phenomena (cubic regime and downstream vortex) were predicted
+using the numerical results, and were verified using asymptotic expansion of the
+nonlinear system.
+
+The computational grid is created to have fine resolution near the particle surface, while
+approximating the far-away boundary conditions. The logarithmic discretization is motivated
+by the solution of the linearized system at Section \ref{app:linear}, 
+where the largest gradients in the solution are near the particle surface.
+The discretization of boundary conditions far away from the particle may be improved
+by including the linear correction from the asymptotic solution, or reformulation of
+far-away boundary condition according to the asymptotic behavior of the analytic solution
+far away from the particle.
+
+For strong electric field ($\beta \gg 1)$, the nonlinear effects become dominant and
+another boundary-layer structure begins to form near the particle surface. 
+In order to achieve high numerical accuracy, the grid discretization should be made finer
+near the particle surface (at $r = 1$), while $R_{max}$ can be made smaller. Moreover, different discretization scheme may be used for
+the $r$ coordinate, to have higher grid resolution near the particle.
+In addition, the continuation of the solution between different $\beta$ values
+should advance in finer steps, to ensure Newton method convergence.
+
+\section{Future Work}
+Future work may include optimizing the direct sparse linear solver 
+to use the ordering data from previous calls,
+or replacing the full Newton step by an iterative linear solver
+(e.g. using preconditioned Krylov subspace methods \cite{saad2003book} or
+Multigrid), allowing finer grids to be used.
+In addition, the framework may be used for automatic construction of Newton solvers 
+for other nonlinear PDE systems, for example -- for particle with different surface 
+properties, or different particle shape.
 

### 2013-02-01 src/plot_velocity_vs_beta.m

@@ -1,20 +1,31 @@
 function plot_velocity_vs_beta
-    clf;
-    M = {};
-    hold on;
-    iter(128, 10,  '-s', [1 0 0]);
-    iter(128, 30,  '-o', [1 0 0]);
-    [b1, v1] = iter(128, 100, '-d', [1 0 0]);
-    iter(256, 10,  '-s', [0 .5 0]);
-    iter(256, 30,  '-o', [0 .5 0]);
-    [b2, v2] = iter(256, 100, '-d', [0 .5 0]);
-    iter(512, 10,  '-s', [0 0 1]);
-    iter(512, 30,  '-o', [0 0 1]);
-    [b3, v3] = iter(512, 100, '-d', [0 0 1]);
+    figure(1)
+    clf; hold on; M = {};
+    iter(128, 10,  '-o', [1 0 0]);
+    iter(256, 10,  '-o', [0 .5 0]);
+    iter(512, 10,  '-o', [0 0 1]);
     xlim([0 6])
     legend(M, 'Location', 'NorthWest')
-    print -depsc2 LargeBetaV.eps
+    xlabel('\beta')
+    ylabel('Steady-state velocity')
+    print -depsc2 LargeBetaV_[128_256_512]_Rmax=10.eps
+
+    figure(2)
+    clf; hold on; M = {};
+    iter(512, 100, '-o', [1 0 0]);
+    iter(512, 30,  '-o', [0 .5 0]);
+    iter(512, 10,  '-o', [0 0 1]);
+    xlim([0 6])
+    legend(M, 'Location', 'NorthWest')
+    xlabel('\beta')
+    ylabel('Steady-state velocity')
+    print -depsc2 LargeBetaV_[512x512]_Rmax=10_30_100.eps
     
+    figure(3)
+    clf; hold on; M = {};
+    [b1, v1] = iter(128, 100, '-d', [1 0 0]);
+    [b2, v2] = iter(256, 100, '-d', [0 .5 0]);
+    [b3, v3] = iter(512, 100, '-d', [0 0 1]);
     clf;
     x_max = 5;
     [b1, v1] = select(b1, v1, @(x) x < x_max);
@@ -26,9 +37,6 @@ function plot_velocity_vs_beta
     print -depsc2 LargeBetaRatio.eps
 
     function [beta, V] = iter(N, Rmax, linespec, c)
-        if nargin < 3
-            linespec = '-';
-        end
[…]

### 2013-02-09 notes/thesis-latex-template/thesis.tex
Update thesis.

@@
 \ref{eq:ephor_bnd}.
-The streamline pattern doesn't change drastically for different electric field magnitudes, as shown in Figure \ref{fig:LargeBeta_Psi1}, \ref{fig:LargeBeta_Psi2} and \ref{fig:LargeBeta_Psi3}. 
+The streamline pattern doesn't change drastically for different electric field magnitudes. 
 The resulting flow pattern is similar to the Stokes creeping flow, as shown in Figure
-\ref{fig:LargeBeta_PsiStokes}.
+\ref{fig:LargeBeta_Psi}.
 
@@
     \begin{center}
-    \includegraphics[width=1\textwidth]{figs/LargeBeta/sol_beta=1.000e-01_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_[1]_Psi.eps}
-        \caption[$\beta = 0.1$ results for $\Psi$]
-        {$\beta = 0.1$ streamlines results: grid size $512 \times 512$, 
+    \includegraphics[width=.45\textwidth]{figs/LargeBeta/sol_beta=1.000e-01_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_[1]_Psi.eps}
+    \includegraphics[width=.45\textwidth]{figs/LargeBeta/sol_beta=8.000e-01_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_[1]_Psi.eps}
+    \includegraphics[width=.45\textwidth]{figs/LargeBeta/sol_beta=5.000e+00_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_[1]_Psi.eps}
+    \includegraphics[width=.45\textwidth]{figs/LinearStokes_Psi.eps}
+        \caption[Streamfunction results]
+        {$\beta = 0.1, 0.8, 5.0$ and Stokes streamlines results: grid size $512 \times 512$, 
         $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.
         The numerical results for $\Psi$ is scaled by $\beta^{-1}$, so the linear regime
-        will appear the same for different $\beta$ values.}
-	    \label{fig:LargeBeta_Psi1}	    
+        will appear the same for different $\beta$ values.
+        Note that the numerical results show very similar flow pattern to the analytical Stokes flow.}
+	    \label{fig:LargeBeta_Psi}	    
     \end{center}
@@
     \begin{center}
-    \includegraphics[width=1\textwidth]{figs/LargeBeta/sol_beta=8.000e-01_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_[1]_Psi.eps}
-        \caption[$\beta = 0.8$ results for $\Psi$]
-        {$\beta = 0.8$ streamlines results: grid size $512 \times 512$, 
+    \includegraphics[width=.45\textwidth]{figs/LargeBeta/sol_beta=1.000e-01_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_[-1]_Psi.eps}
+    \includegraphics[width=.45\textwidth]{figs/LargeBeta/sol_beta=8.000e-01_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_[-1]_Psi.eps}
+    \includegraphics[width=.45\textwidth]{figs/LargeBeta/sol_beta=5.000e+00_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_[-1]_Psi.eps}
+    \includegraphics[width=.45\textwidth]{figs/LinearStokes_Psi.eps}
+        \caption[Streamfunction ''reversed''  results]
+        {$\beta = 0.1, 0.8, 5.0$ and Stokes streamlines ''reversed'' results: grid size $512 \times 512$, 
         $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.
         The numerical results for $\Psi$ is scaled by $\beta^{-1}$, so the linear regime
-        will appear the same for different $\beta$ values.}
-	    \label{fig:LargeBeta_Psi2}	    
-    \end{center}
-\end{figure}
-
-\begin{figure}
-    \begin{center}
-    \includegraphics[width=1\textwidth]{figs/LargeBeta/sol_beta=5.000e+00_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_[1]_Psi.eps}
-        \caption[$\beta = 5.0$ results for $\Psi$]
-        {$\beta = 5.0$ streamlines results: grid size $512 \times 512$, 
-        $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.
-        The numerical results for $\Psi$ is scaled by $\beta^{-1}$, so the linear regime
-        will appear the same for different $\beta$ values.}
-	    \label{fig:LargeBeta_Psi3}	    
-    \end{center}
-\end{figure}
-
-\begin{figure}
-    \begin{center}
-    \includegraphics[width=1\textwidth]{figs/LinearStokes_Psi.eps}
-        \caption[Stokes flow results]
-        {Stokes flow streamlines results: grid size $512 \times 512$, 
-        $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.
-        The numerical results for $\Psi$ is scaled by $\beta^{-1}$, so the linear regime
-        will appear the same for different $\beta$ values. Note that the numerical results
-        show very similar flow pattern to the analytical Stokes flow.}
-	    \label{fig:LargeBeta_PsiStokes}	    
+        will appear the same for different $\beta$ values.
+        Note that the numerical results show very similar flow pattern to the analytical Stokes flow.}
+	    \label{fig:LargeBeta_Psi}	    
     \end{center}

### 2013-02-09 src/plot_velocity_vs_beta.m

@@ -1,10 +1,21 @@
 function plot_velocity_vs_beta
+    Du = 1;
+    zeta = 10;
+    beta = linspace(0, 6);
+    U = beta * (Du*log(16) + zeta)/(1 + 2*Du);
+    
     figure(1)
     clf; hold on; M = {};
     iter(128, 10,  '-o', [1 0 0]);
     iter(256, 10,  '-o', [0 .5 0]);
-    iter(512, 10,  '-o', [0 0 1]);
+    [b, v] = iter(512, 10,  '-o', [0 0 1]);
+    plot(beta, U, '--k');
+    M{end+1} = ['Linear Solution (small \beta): ' sprintf('%.3f \\beta', (Du*log(16) + zeta)/(1 + 2*Du))];
+    r = linreg(b(10:40), v(10:40))
+    plot(beta, r.a * beta + r.b, '-.k')
     xlim([0 6])
+    ylim([0 30])
+    M{end+1} = ['Linear Fit (moderate \beta): ' sprintf('%.3f \\beta %.3f', r.a, r.b)];
     legend(M, 'Location', 'NorthWest')
     xlabel('\beta')
     ylabel('Steady-state velocity')
@@ -14,8 +25,14 @@ function plot_velocity_vs_beta
     clf; hold on; M = {};
     iter(512, 100, '-o', [1 0 0]);
     iter(512, 30,  '-o', [0 .5 0]);
-    iter(512, 10,  '-o', [0 0 1]);
+    [b, v] = iter(512, 10,  '-o', [0 0 1]);
+    plot(beta, U, '--k');
+    M{end+1} = ['Linear Solution (small \beta): ' sprintf('%.3f \\beta', (Du*log(16) + zeta)/(1 + 2*Du))];
+    r = linreg(b(10:40), v(10:40))
+    plot(beta, r.a * beta + r.b, '-.k')
     xlim([0 6])
+    ylim([0 30])
+    M{end+1} = ['Linear Fit (moderate \beta): ' sprintf('%.3f \\beta %.3f', r.a, r.b)];
     legend(M, 'Location', 'NorthWest')
     xlabel('\beta')
     ylabel('Steady-state velocity')

### 2013-02-11 notes/thesis-latex-template/thesis.tex
Update thesis.

@@
 while the asymptotic analysis for the electrophoresis case \cite{schnitzer2012surface}
-is derived by Schnitzer and Yariv at \cite{schnitzer2012cubic}.
+is derived by Schnitzer and Yariv in \cite{schnitzer2012cubic}.
 
@@
 given the previous solutions for $\bx_0, \ldots, \bx_{k-1}$.
-The derivation is validated using MATLAB symbolic toolbox by the code 
+The derivation is validated using the MATLAB symbolic toolbox by the code 
 at \verb|symbolic/asymp.m| \cite{source}.
@@
 \end{align}
-For $\gamma > 1$, the Debye layer has a positive space charge, 
+For $\gamma > 1$, the Debye layer has a positive charge, 
 corresponding to a negative particle charge -- 
@@
 The numerical results are compared 
-to the asymptotic solutions, and good correspondence is achieved.
+to the asymptotic solutions, and a good correspondence is observed.
 
@@
 For $\beta \ll 1$, the linear regime \cite{yariv2010asymptotic} is dominant.
-When $\gamma \approx 1$, the cubic regime, where $\cU = O(\beta^3)$, 
+However, when $\gamma \approx 1$, the cubic regime, where $\cU = O(\beta^3)$, 
 dominates the linear one, even for weak electric fields. 
@@
 
-Since the leading order of the solution $\cU(\beta)$ is linear for $\beta \ll 1$, 
+Because the leading order of the solution $\cU(\beta)$ is linear for $\beta \ll 1$, 
 the numerical discretization error is $O(\beta)$ as well.
@@
 \end{equation}
-The results of the extrapolation and $\hat\cU$ the analytical results 
+The results of the extrapolation $\hat\cU$ 
+and the analytical results 
 are given at Figures \ref{fig:Electrophoresis1} and \ref{fig:Electrophoresis2}.
@@
 When the electric field is large, nonlinear effects dominate the solution.
-In order to investigate the problem solution for strong electric fields, 
+In order to investigate the solution for strong electric fields, 
 we have run the solver on the TAMNUN HPC cluster \cite{tamnun}.
@@
 Moreover, several $R_{max} \in \{10, 30, 100\}$ values are used, to make sure it has no major impact on the solution.
-The results are shown at the following figures. 
-The steady-state velocity results are shown for several grid resolutions and several $R_{max}$ values in Figure \ref{fig:LargeBetaV_grids}, and the estimated rate of convergence is shown at Figure \ref{fig:LargeBetaRatio}.
+The results are shown in the following figures. 
+The steady-state velocity results are shown for several grid resolutions and several $R_{max}$ values in Figure \ref{fig:LargeBetaV_grids}, and the estimated rate of convergence is shown in Figure \ref{fig:LargeBetaRatio}.
 
@@
 (at $\theta \approx \pi$).
-This is results in high gradients in $\log C$ near the front of the particle (Figures \ref{fig:LargeBeta_C1}, \ref{fig:LargeBeta_C2} and
-\ref{fig:LargeBeta_C3}) and, therefore, strong electric field $\bE$ form near the particle surface (Figures \ref{fig:LargeBeta_Phi1}, \ref{fig:LargeBeta_Phi2} and \ref{fig:LargeBeta_Phi3}) due to effective boundary conditions at Eq.
-\ref{eq:ephor_bnd}.
-The streamline pattern doesn't change drastically for different electric field magnitudes. 
+This results in high gradients in $\log C$ near the front of the particle (Figures \ref{fig:LargeBeta_C1}, \ref{fig:LargeBeta_C2} and
+\ref{fig:LargeBeta_C3}) and, therefore, a strong electric field $\bE$ forms near the particle surface (Figures \ref{fig:LargeBeta_Phi1}, \ref{fig:LargeBeta_Phi2} and \ref{fig:LargeBeta_Phi3}) due to effective boundary conditions in (\ref{eq:ephor_bnd}).
+The streamline pattern does not change drastically for different electric field magnitudes. 
 The resulting flow pattern is similar to the Stokes creeping flow, as shown in Figure
@@
 electric fields (see Figure \ref{fig:LargeBeta_BoundaryLayer}). 
-This causes numerical problems to the current solver -- yielding a convergence
+This causes numerical problems to the current solver -- yielding convergence
 problems for large $\beta$. The convergence problems start earlier
@@
         $\deriv{C}{r}$ becomes large 
-        (since the change in $C$ happens at a small length scale).
+        (since the change in $C$ happens on a small length scale).
         Due to the boundary conditions of the electrophoresis problem
-        (given by Eq. \ref{eq:ephor_bnd}), the electric field radial
+        (given by (\ref{eq:ephor_bnd})), the electric field radial
         component given by 
@@
         will appear the same for different $\beta$ values.
-        Note that the numerical results show very similar flow pattern to the analytical Stokes flow.}
+        Note that the numerical results show 
+        flow pattern very similar to that of the analytical Stokes flow.}
 	    \label{fig:LargeBeta_Psi}	    
@@
 
-The computational grid is created to have fine resolution near the particle surface, while
-approximating the far-away boundary conditions. The logarithmic discretization is motivated
-by the solution of the linearized system at Section \ref{app:linear}, 
+The computational grid is created to have fine resolution near the particle surface, where the solutions vary sharply. The logarithmic discretization is motivated
+by the solution of the linearized system of Section \ref{app:linear}, 
 where the largest gradients in the solution are near the particle surface.
@@
 For strong electric field ($\beta \gg 1)$, the nonlinear effects become dominant and
-another boundary-layer structure begins to form near the particle surface. 
+a boundary-layer structure begins to form near the particle surface. 
 In order to achieve high numerical accuracy, the grid discretization should be made finer
-near the particle surface (at $r = 1$), while $R_{max}$ can be made smaller. Moreover, different discretization scheme may be used for
-the $r$ coordinate, to have higher grid resolution near the particle.
+near the particle surface (at $r = 1$), while $R_{max}$ can be made smaller. Moreover, a different discretization scheme may be used for
+the $r$ coordinate, to have higher grid resolution near the particles.
 In addition, the continuation of the solution between different $\beta$ values

### 2013-02-11 src/plot_Er_layer.m

@@ -12,22 +12,28 @@ clf;
 subplot(1,2,1)
 hold on;
 I = 1:2:numel(q);
-plot(r-1, F(:, I), '-');
-plot(q(I)-1, 0.5, '.');
-xlim([0 0.2])
-ylim([0 1])
-xlabel('Radial distance from particle surface')
-ylabel('Normalized electric field radial component')
-
+for i = I
+    f = @(x) x * exp(b(i) / 2);
+    plot(f(r-1), F(:, i), '-');
+    plot(f(q(i)-1), 0.5, '.');
+    drawnow;
+    pause(.1)
+    title(sprintf('\\beta = %.2f', b(i)));
+    xlim([0 1])
+    ylim([0 1])
+    xlabel('Radial distance from particle surface (scaled by e^{\beta/2})')
+    ylabel('Normalized electric field radial component')
+end
+title('')
 subplot(1,2,2)
 %hold on
 y = log(q-1);
-I = 2:2:68;
+I = 10:50;
 r = linreg(b(I), y(I))
-semilogy(b(I), q(I)-1, '.', b, exp(r.a*b + r.b))
+semilogy(b, q-1, '.', b(I), q(I)-1, '.', b, exp(r.a*b + r.b))
 ylim([0.005 0.2])
 func = sprintf('\n%.3f e^{%.3f \\beta}', exp(r.b), r.a);
-legend('Numerical results', ['Exponential fit ' func])
+legend('Numerical results', 'Points to fit', ['Exponential fit ' func])
 xlabel('\beta')
 ylabel('Boudary layer width')
 

### 2013-02-11 src/plot_Psi_symmetry.m

@@ -1,0 +1,20 @@
+function plot_Psi_symmetry
+L = glob('MATs/Psi/*.mat');
+res = cellfun(@show, L, 'UniformOutput', false);
+res = cat(1, res{:});
+res = sortrows(res);
+plot(res(:, 1), res(:, 2), '.-')
+
+function res = show(f)
+s = load(f);
+err = s.z - fliplr(s.z);
+err = norm(err(:)) / s.beta;
+% clf; hold on;
+% contour(s.x, s.y, s.z, s.c)
+% contour(s.x, -s.y, s.z, s.c)
+% t = linspace(0, 2*pi, 100);
+% fill(cos(t), sin(t), [1 1 1]*0.5)
+% axis([-1 1 -1 1]*3)
+% axis equal
+% pause(.1)
+res = [s.beta, err];

### 2013-02-11 src/plot_results_for_thesis.m

@@ -10,7 +10,7 @@ load(filename)
 [p, n] = fileparts(filename);
 filename = fullfile(p, n);
 disp(filename)
-if 1
+if 0
     clf;
     hold on;
     op = sol.C;
@@ -33,7 +33,7 @@ if 1
     title(sprintf('Salt concentration (C): \\beta = %.2f', sol.beta))
     print('-depsc2', [filename '_C.eps'])
 end
-if 0
+if 1
     for d = [1 -1]
         clf;
         hold on;
@@ -54,6 +54,8 @@ if 0
         axis equal
         title(sprintf('Streamlines (\\Psi): \\beta = %.2f', sol.beta))
         print('-depsc2', [filename sprintf('_[%d]_Psi.eps', d)])
+        beta = sol.beta;
+        save([filename sprintf('_[%d]_Psi.mat', d)], 'R', 'T', 'z', 'x', 'y', 'c', 'd', 't', 'beta')
     end
 end
 

### 2013-02-15 notes/thesis-latex-template/thesis.tex
Update results for thesis.

@@
     \begin{center}
-    \includegraphics[width=.45\textwidth]{figs/LargeBeta/sol_beta=1.000e-01_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_[-1]_Psi.eps}
-    \includegraphics[width=.45\textwidth]{figs/LargeBeta/sol_beta=8.000e-01_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_[-1]_Psi.eps}
-    \includegraphics[width=.45\textwidth]{figs/LargeBeta/sol_beta=5.000e+00_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_[-1]_Psi.eps}
-    \includegraphics[width=.45\textwidth]{figs/LinearStokes_Psi.eps}
-        \caption[Streamfunction ''reversed''  results]
-        {$\beta = 0.1, 0.8, 5.0$ and Stokes streamlines ''reversed'' results: grid size $512 \times 512$, 
-        $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.
-        The numerical results for $\Psi$ is scaled by $\beta^{-1}$, so the linear regime
-        will appear the same for different $\beta$ values.
-        Note that the numerical results show very similar flow pattern to the analytical Stokes flow.}
-	    \label{fig:LargeBeta_Psi}	    
-    \end{center}
-\end{figure}
-
-\begin{figure}
-    \begin{center}
     \includegraphics[width=1\textwidth]{figs/BoundaryLayerWidth.eps}

### 2013-02-15 src/plot_C_layer.m

@@ -1,0 +1,62 @@
+function plot_C_layer
+clear
+load results_C(beta)_512x512_Rmax=10.mat
+b = betas(1:end-1);
+clf;
+I = 1:numel(b);
+R = [];
+w = [];
+for i = I
+    subplot(2,2,1)
+    hold on;
+    c = C(:, i);
+    plot(r-1, c)    
+    xlim([0 1])
+    ylim([0 1])
+    xlabel('Radial distance from particle surface')
+    ylabel('Ion concentration (C)')
+    
+    subplot(2,2,2)
+    hold on;
+    c_ = c - c(1);
+    c_ = c_ / c_(end);
+    I = c_ < 0.999;
+    w(i) = interp1(c_(I), r(I)-1, 0.5);
+    plot(r-1, c_, w, 0.5, '.k')
+    xlim([0 1])
+    ylim([0 1])
+    xlabel('Radial distance from particle surface')
+    ylabel('Normalized Ion concentration')
+    
+    subplot(2,2,3)
+    semilogy(b(1:i), C(1, 1:i), '.-')
+    xlim([0 7])
+    ylim([3e-2 1])
+    xlabel('Electric field magnitude (\beta)')
+    ylabel('C(r=1, \theta=0)')
+    
+    subplot(2,2,4)
+    loglog(b(1:i), w(1:i), '.-')
+    xlim([0.1 7])
+    ylim([0.08 0.5])
+    xlabel('Electric field magnitude (\beta)')
+    ylabel('Boundary layer width')
+    
+    drawnow;
+    pause(.1)
+end
+return
+subplot(1,2,2)
+%hold on
+y = log(q-1);
+I = 10:50;
+r = linreg(b(I), y(I))
+semilogy(b, q-1, '.', b(I), q(I)-1, '.', b, exp(r.a*b + r.b))
+ylim([0.005 0.2])
+func = sprintf('\n%.3f e^{%.3f \\beta}', exp(r.b), r.a);
+legend('Numerical results', 'Points to fit', ['Exponential fit ' func])
+xlabel('\beta')
+ylabel('Boudary layer width')
+
+print -depsc2 BoundaryLayerWidth.eps
+% end

### 2013-02-15 src/plot_Er_layer.m

@@ -9,7 +9,21 @@ for j = 1:size(F, 2)
     q(j) = interp1(f, r, 0.5);
 end
 clf;
-subplot(1,2,1)
+subplot(2,2,1)
+hold on;
+I = 1:2:numel(q);
+for i = I
+    f = @(x) x;
+    plot(f(r-1), F(:, i), '-');
+    plot(f(q(i)-1), 0.5, '.');
+    drawnow;
+    pause(.1)
+    xlim([0 1])
+    ylim([0 1])
+    xlabel('Radial distance from particle surface')
+    ylabel('Normalized electric field radial component')
+end
+subplot(2,2,2)
 hold on;
 I = 1:2:numel(q);
 for i = I
@@ -18,14 +32,12 @@ for i = I
     plot(f(q(i)-1), 0.5, '.');
     drawnow;
     pause(.1)
-    title(sprintf('\\beta = %.2f', b(i)));
     xlim([0 1])
     ylim([0 1])
     xlabel('Radial distance from particle surface (scaled by e^{\beta/2})')
     ylabel('Normalized electric field radial component')
 end
-title('')
-subplot(1,2,2)
+subplot(2,2,3)
 %hold on
 y = log(q-1);
 I = 10:50;
@@ -36,6 +48,12 @@ func = sprintf('\n%.3f e^{%.3f \\beta}', exp(r.b), r.a);
 legend('Numerical results', 'Points to fit', ['Exponential fit ' func])
 xlabel('\beta')
 ylabel('Boudary layer width')
+
+subplot(2,2,4)
+%hold on
+semilogy(b, E(1, :) ./ b, '.')
+xlabel('\beta')
+ylabel('E_r(r=1, \theta=0)')
 
 print -depsc2 BoundaryLayerWidth.eps
 end

### 2013-02-25 notes/thesis-latex-template/thesis.tex
Update thesis.

@@
 
+The numerical solver converges well for $\beta < 5$ and the resulting steady-state velocity 
+for moderate $\beta$ values is very close to being an affine function of $\beta$.
 When $\beta$ becomes large, the salt concentration $C$ near the front of the particle 
 (at $\theta \approx 0$) approaches zero, while creating a wake behind the particle 
-(at $\theta \approx \pi$).
-This results in high gradients in $\log C$ near the front of the particle (Figures \ref{fig:LargeBeta_C1}, \ref{fig:LargeBeta_C2} and
-\ref{fig:LargeBeta_C3}) and, therefore, a strong electric field $\bE$ forms near the particle surface (Figures \ref{fig:LargeBeta_Phi1}, \ref{fig:LargeBeta_Phi2} and \ref{fig:LargeBeta_Phi3}) due to effective boundary conditions in (\ref{eq:ephor_bnd}).
+(at $\theta \approx \pi$) as shown in Figures \ref{fig:LargeBeta_C1}, \ref{fig:LargeBeta_C2} and
+\ref{fig:LargeBeta_C3}.
+This results in high gradients in $\log C$ near the front of the particle  and, therefore, a strong electric field $\bE$ forms near the particle surface (Figures \ref{fig:LargeBeta_Phi1}, \ref{fig:LargeBeta_Phi2} and \ref{fig:LargeBeta_Phi3}) due to effective boundary conditions in (\ref{eq:ephor_bnd}).
+From Figs.
+\ref{fig:LargeBetaV_grids}-\ref{fig:LargeBetaRatio} we conclude that even our most accurate numerical solution is valid only up to $\beta = 5$ approximately, and therefore we only further examine solutions in this range.
+
 The streamline pattern does not change drastically for different electric field magnitudes. 
-The resulting flow pattern is similar to the Stokes creeping flow, as shown in Figure
-\ref{fig:LargeBeta_Psi}.
-
-The numerical results suggest that a boundary 
-layer starts to form around the front of the particle for strong
-electric fields (see Figure \ref{fig:LargeBeta_BoundaryLayer}). 
-This causes numerical problems to the current solver -- yielding convergence
-problems for large $\beta$. The convergence problems start earlier
-for smaller grid size, and for higher $R_{max}$ values, probably
-due to insufficient resolution at the $\brhat$ direction near
-the particle surface.
+The resulting fluid flow is nearly proportional to that of the Stokes creeping flow, 
+as shown in Figure \ref{fig:LargeBeta_Psi}. 
+The difference between $\Psi(r, \theta)$ and $\Psi(r, \pi-\theta)$ is shown in Figure \ref{fig:LargeBeta_PsiAsymm}, demonstrating that the flow is almost symmetric (with relative
+difference up to approximately $0.5\%$) for $\beta < 5$.
+
+The numerical results show that a boundary layer starts to form near the front 
+of the particle for strong electric fields (see Figures \ref{fig:LargeBeta_BoundaryLayer_E}
+and \ref{fig:LargeBeta_BoundaryLayer_C}).
+The width of the boundary layer with respect to the electric field scales, to a good approximation, is: $\bar\rho(\beta) \approx 0.2 e^{-0.5 \beta}$.
+This causes numerical problems for the current solver at large $\beta$, due to insufficient
+grid resolution at the boundary layer of $C$ and $\bE$.
 
@@
         \caption[Large $\beta$ results for $\cU$]
-{Large $\beta$ results for $\cU$ ($\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$). 
+{Large $\beta$ results for $\cU(\beta)$ ($\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$). 
 The left figure shows the numerical results of $\cU(\beta)$ for $R_{max} = 10$ and the following grid sizes: $128 \times 128$, $256 \times 256$, $512 \times 512$. 
@@
 $512 \times 512$ grid for $R_{max} = 100, 30, 10$. For small values of $\beta$, the linear
-regime of $\cU(\beta)$ is dominant. However, for larger values of $\beta$, the numerical solution
-deviates significantly from the linear regime. For $\beta > 6$, the numerical solver convergence
-is slowing and for $\beta \sim 7$, the solver fails to converge. As the grid resolution near
-the particle surface becomes finer (when $N_r$ increases or $R_{max}$ decreases), the solver
-convergence is better.}
+regime of $\cU(\beta)$ is dominant. 
+For moderate $\beta$ values, the steady state velocity is very close to affine function of $\beta$.
+However, for larger values of $\beta$, the numerical solution
+deviates significantly from the linear regime, due to convergence problems at $\beta > 6$, 
+and for $\beta \sim 7$, the solver fails to converge. The numerical convergence 
+depends on the grid resolution near the particle surface -- 
+as it becomes finer (when $N_r$ increases or $R_{max}$ decreases), the solver convergence improves.}
 	    \label{fig:LargeBetaV_grids}	    
+    \end{center}
+\end{figure}
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=.45\textwidth]{figs/LargeBetaV_DeltaFromLinear[128_256_512]_Rmax=10.eps}
+    \includegraphics[width=.45\textwidth]{figs/LargeBetaV_DeltaFromLinear[512x512]_Rmax=10_30_100.eps}
+        \caption[Large $\beta$ results for $\cU$ -- difference from linear regime]
+{Large $\beta$ results for $\cU(\beta) - \beta\cU_1$ ($\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$ and $\cU_1 \approx 4.258$ is linear regime coefficient). 
+The left figure shows the numerical results of $\cU(\beta)$ for $R_{max} = 10$ and the following grid sizes: $128 \times 128$, $256 \times 256$, $512 \times 512$. 
+The right figure shows the numerical results of $\cU(\beta)$ for
+$512 \times 512$ grid for $R_{max} = 100, 30, 10$.}
+	    \label{fig:LargeBetaV_DeltaFromLinear_grids}	    
     \end{center}
@@
         {Rate of convergence estimation for $\cU$ at large $\beta$  
-        ($\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$). 
-        The numerical results of $\cU(\beta)$, for the grid sizes of 
+        ($\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$), 
+        based on the numerical results of $\cU(\beta)$, for the grid sizes of 
         $128 \times 128$, $256 \times 256$, $512 \times 512$. 
@@
         quadratic convergence for the linear regime. 
-        For moderate $\beta$, the convergence rate slows down 
-        and deteriorates for large $\beta$ values.
+        For moderate $\beta$, the convergence rate slows down, 
+        and it deteriorates for large $\beta$ values.
         }
@@
     \begin{center}
-    \includegraphics[width=1\textwidth]{figs/BoundaryLayerWidth.eps}
+    \includegraphics[width=1\textwidth]{figs/streamlines_asymmetry.eps}
+        \caption[Streamfunction asymmetry]
+        {Streamline results: grid size $512 \times 512$, 
+        $R_{max} = 10$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.
+        The relative streamline asymmetry is computed by 
+        $\|\Psi(r, \theta) - \Psi(r, \pi-\theta)\|/\|\Psi(r, \theta)\|$
+        as a function of $\beta$. The results show that the streamline pattern is almost 
+        symmetric, even for moderately large $\beta$ values.}
+	    \label{fig:LargeBeta_PsiAsymm}	    
+    \end{center}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=.45\textwidth]{figs/BoundaryLayerWidth_E1.eps}
+    \includegraphics[width=.45\textwidth]{figs/BoundaryLayerWidth_E2.eps}
+    \includegraphics[width=.45\textwidth]{figs/BoundaryLayerWidth_E3.eps}
+    \includegraphics[width=.45\textwidth]{figs/BoundaryLayerWidth_E4.eps}
         \caption[Electric field boundary layer]
         {Electric field boundary layer formation: grid size $512 \times 512$, 
-        $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$. The left
+        $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$. The upper left
         graph shows normalized electric field radial component $E_r$ near the particle front
-        ($\theta \approx 0$). The numerical results for $e(\rho) = E_r(r=1+\rho, \theta=0)$
+        ($\theta = 0$). The numerical results for $e(\rho) = E_r(r=1+\rho, \theta=0)$
         are normalized by $\hat{e}(\rho) = \left(e(\rho) - \beta\right)/\left(e(0) - \beta\right)$,
@@
         The normalized electric field satisfies $\hat{e}(\rho) \in [0, 1]$ and is shown as function
-        of $\rho = r - 1$ at the left graph.
+        of $\rho = r - 1$ at the upper left graph and as function of $\rho e^{0.5 \beta}$ at
+        the upper right graph.
         In order to estimate the width of the boundary layer, for each $\beta$, we compute the value 
@@
         In addition, $\bar\rho(\beta)$ is plotted as a function of $\beta$ using logarithmic 
-        $y$ axis at the right graph to show that $\bar\rho(\beta) \propto e^{-A\beta}$.
+        $y$ axis at the lower left graph to show that $\bar\rho(\beta) \approx 0.2 e^{-0.5 \beta}$.
+        Moreover, $E_r(\beta; r=1, \theta=0) / \beta$ grows exponentially as a function of $\beta$,
+        as shown at the lower right graph.
         Thus, a boundary layer is indeed forming near the front of the particle.
         }
-	    \label{fig:LargeBeta_BoundaryLayer}	    
+	    \label{fig:LargeBeta_BoundaryLayer_E}	    
+    \end{center}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=.45\textwidth]{figs/boundary_layer_C1.eps}
+    \includegraphics[width=.45\textwidth]{figs/boundary_layer_C2.eps}
+        \caption[Ionic concentration boundary layer]
+        {Ionic concentration boundary layer formation: grid size $512 \times 512$, 
+        $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$. The left
+        graph shows the ionic concentration $C$ near the particle front
+        ($\theta = 0$). 
+        In addition, $C_\beta(r=1, \theta=0)$ is plotted as a function of $\beta$ using logarithmic 
+        $y$ axis at the right graph to show that 
+        $C_\beta(r=1, \theta=0) \approx 0.94 e^{-0.45 \beta}$.
+        The ionic concentration becomes very close to zero for $\beta \approx 7$ at $r = 1$, 
+        creating a singularity near the particle front.
+        }
+	    \label{fig:LargeBeta_BoundaryLayer_C}	    
     \end{center}
@@
 \section{Discussion} \label{sec:discussion}
-A numerical framework for solver construction for a
+A numerical framework for a
 nonlinear electrokinetic transport system is described.
-The framework is applied to two electrokinetic problems: the migration of ion-exchangers
+The framework is used to construct numerical solvers 
+for two electrokinetic problems: the migration of ion-exchangers
 and surface-charged inert particle electrophoresis.
-The numerical results exhibit a good correspondence to the asymptotic linear model as
-shown above.
-Moreover, two interesting phenomena (cubic regime and downstream vortex) were predicted
-using the numerical results, and were verified using asymptotic expansion of the
-nonlinear system.
-
-The computational grid is created to have fine resolution near the particle surface, where the solutions vary sharply. The logarithmic discretization is motivated
-by the solution of the linearized system of Section \ref{app:linear}, 
-where the largest gradients in the solution are near the particle surface.
-The discretization of boundary conditions far away from the particle may be improved
-by including the linear correction from the asymptotic solution, or reformulation of
-far-away boundary condition according to the asymptotic behavior of the analytic solution
-far away from the particle.
-
-For strong electric field ($\beta \gg 1)$, the nonlinear effects become dominant and
-a boundary-layer structure begins to form near the particle surface. 
+The numerical results for weak electric field 
+exhibit a good correspondence to the asymptotic models as shown above.
+Two interesting phenomena (cubic regime and downstream vortex) were predicted for the ion-exchanger
+using the numerical results, and were verified using asymptotic expansion of the nonlinear system.
+The electrophoresis problem was solved on a high-resolution grid to validate the asymptotic 
+cubic correction of the steady-state velocity, as well as providing insights of the solution behavior 
+for moderate and strong electric fields.
+For strong electric field, the nonlinear effects become dominant and
+a boundary-layer structure begins to form.
+Due to diminishing ion concentration $C$ at the front of the particle,
+a boundary layer of thickness approximately $0.2 e^{-0.5\beta}$ 
+is formed with respect to the electric field $\bE$ at the front of the particle.
+The value of $E_r$ at ($r = 1$, $\theta = 0$) is given approximately by 
+$e^{\beta/2}$, while the value of $C(r = 1, \theta = 0)$ is given approximately 
+by $e^{-\beta/2}$, and their product remains close to 1 for all $\beta$ that we could compute.
+However, the velocity of the particle remains nearly linear with $\beta$
+and the velocity field is very close to being symmetric.
+
+\section{Future Work}
+Future work may include using the numerical results described in this work to develop
+an analytical solution for the strong field regime of the electrophoresis problem, which is 
+of interest. The solver may be used to investigate how the solution
+(and the evolving boundary layer, in particular) depends on the problem parameters.
+Optimizing the direct sparse linear solver can be done by
+using the ordering data from previous calls,
+or replacing the full Newton step by an iterative linear solver
+(e.g., using preconditioned Krylov subspace methods \cite{saad2003book} or
+Multigrid), allowing finer grids to be used.
 In order to achieve high numerical accuracy, the grid discretization should be made finer
@@
 should advance in finer steps, to ensure Newton method convergence.
-
-\section{Future Work}
-Future work may include optimizing the direct sparse linear solver 
-to use the ordering data from previous calls,
-or replacing the full Newton step by an iterative linear solver
-(e.g. using preconditioned Krylov subspace methods \cite{saad2003book} or
-Multigrid), allowing finer grids to be used.
-In addition, the framework may be used for automatic construction of Newton solvers 
-for other nonlinear PDE systems, for example -- for particle with different surface 
+The discretization of boundary conditions far away from the particle may be improved
+by including the linear correction from the asymptotic solution, or reformulation of
+far-away boundary condition according to the asymptotic behavior of the analytic solution
+far away from the particle.
+Moreover, the framework may be used for automatic construction of Newton solvers 
+for other nonlinear PDE systems, for example, for particles with different surface 
 properties, or different particle shape.

### 2013-02-25 src/plot_C_Er_product.m

@@ -1,0 +1,12 @@
+function plot_C_Er_product
+
+load results_Er(beta)_512x512_Rmax=10.mat
+load results_C(beta)_512x512_Rmax=10.mat
+
+b = betas(1:end-1);
+
+plot(b, E(1, :) .* C(1, :) ./ b, 'LineWidth', 2)
+xlim([0 5])
+xlabel('\beta', 'FontSize', 16)
+ylabel('C \cdot E_r / \beta at r=1, \theta=0', 'FontSize', 16, 'FontSize', 16)
+print -depsc2 C_Er_product

### 2013-02-25 src/plot_C_layer.m

@@ -6,57 +6,27 @@ clf;
 I = 1:numel(b);
 R = [];
 w = [];
-for i = I
-    subplot(2,2,1)
-    hold on;
-    c = C(:, i);
-    plot(r-1, c)    
-    xlim([0 1])
-    ylim([0 1])
-    xlabel('Radial distance from particle surface')
-    ylabel('Ion concentration (C)')
-    
-    subplot(2,2,2)
-    hold on;
-    c_ = c - c(1);
-    c_ = c_ / c_(end);
-    I = c_ < 0.999;
-    w(i) = interp1(c_(I), r(I)-1, 0.5);
-    plot(r-1, c_, w, 0.5, '.k')
-    xlim([0 1])
-    ylim([0 1])
-    xlabel('Radial distance from particle surface')
-    ylabel('Normalized Ion concentration')
-    
-    subplot(2,2,3)
-    semilogy(b(1:i), C(1, 1:i), '.-')
-    xlim([0 7])
-    ylim([3e-2 1])
-    xlabel('Electric field magnitude (\beta)')
-    ylabel('C(r=1, \theta=0)')
-    
-    subplot(2,2,4)
-    loglog(b(1:i), w(1:i), '.-')
-    xlim([0.1 7])
-    ylim([0.08 0.5])
-    xlabel('Electric field magnitude (\beta)')
-    ylabel('Boundary layer width')
-    
-    drawnow;
-    pause(.1)
-end
-return
-subplot(1,2,2)
-%hold on
-y = log(q-1);
+
+clf
+c = C(:, 1:2:end);
+plot(r-1, c, '-', 'MarkerSize', 5, 'LineWidth', 2)    
+xlim([0 1])
+ylim([0 1])
+xlabel('Radial distance from particle surface', 'FontSize', 16)
+ylabel('Ion concentration (C)', 'FontSize', 16)
+print -depsc2 boundary_layer_C1
+
+clf
+c = C(1, :);
+logc = log(c);
 I = 10:50;
-r = linreg(b(I), y(I))
-semilogy(b, q-1, '.', b(I), q(I)-1, '.', b, exp(r.a*b + r.b))
-ylim([0.005 0.2])
+r = linreg(b(I), logc(I));
+semilogy(b, c, 'o', b(I), c(I), 'o', b, exp(b*r.a + r.b), '-', 'MarkerSize', 5, 'LineWidth', 2)
+xlim([0 5])
+ylim([.1 1])
[…]

### 2013-02-25 src/plot_Er_layer.m

@@ -9,51 +9,61 @@ for j = 1:size(F, 2)
     q(j) = interp1(f, r, 0.5);
 end
 clf;
-subplot(2,2,1)
+
 hold on;
 I = 1:2:numel(q);
-for i = I
+% for i = I
     f = @(x) x;
-    plot(f(r-1), F(:, i), '-');
-    plot(f(q(i)-1), 0.5, '.');
-    drawnow;
-    pause(.1)
-    xlim([0 1])
+    plot(f(r-1), F(:, I), '-', 'LineWidth', 2);
+    plot(f(q(I)-1), 0.5, 'o', 'MarkerSize', 5);
+    xlim([0 0.2])
     ylim([0 1])
-    xlabel('Radial distance from particle surface')
-    ylabel('Normalized electric field radial component')
-end
-subplot(2,2,2)
+    xlabel('Radial distance from particle surface', 'FontSize', 16)
+    ylabel('Normalized electric field radial component', 'FontSize', 16)
+% end
+print -depsc2 BoundaryLayerWidth_E1.eps
+
+clf;
 hold on;
 I = 1:2:numel(q);
-for i = I
-    f = @(x) x * exp(b(i) / 2);
-    plot(f(r-1), F(:, i), '-');
-    plot(f(q(i)-1), 0.5, '.');
-    drawnow;
-    pause(.1)
+% for i = I
+    plot((r-1) * exp(b(I) / 2), F(:, I), '-', 'LineWidth', 2);
+    plot((q(I)-1) .* exp(b(I) / 2), 0.5, 'o', 'MarkerSize', 5);
     xlim([0 1])
     ylim([0 1])
-    xlabel('Radial distance from particle surface (scaled by e^{\beta/2})')
-    ylabel('Normalized electric field radial component')
-end
-subplot(2,2,3)
+    xlabel('Radial distance from particle surface (scaled by e^{\beta/2})', 'FontSize', 16)
+    ylabel('Normalized electric field radial component', 'FontSize', 16)
+% end
+print -depsc2 BoundaryLayerWidth_E2.eps
+
+clf;
 %hold on
 y = log(q-1);
 I = 10:50;
 r = linreg(b(I), y(I))
-semilogy(b, q-1, '.', b(I), q(I)-1, '.', b, exp(r.a*b + r.b))
-ylim([0.005 0.2])
[…]

### 2013-02-25 src/plot_Psi_symmetry.m

@@ -1,14 +1,20 @@
 function plot_Psi_symmetry
+clf;
 L = glob('MATs/Psi/*.mat');
 res = cellfun(@show, L, 'UniformOutput', false);
 res = cat(1, res{:});
 res = sortrows(res);
 plot(res(:, 1), res(:, 2), '.-')
+xlabel('\beta')
+ylabel('Relative streamlines asymmetry')
+xlim([0 5])
+ylim([0 0.01])
+print -depsc2 streamlines_asymmetry
 
 function res = show(f)
 s = load(f);
 err = s.z - fliplr(s.z);
-err = norm(err(:)) / s.beta;
+err = norm(err(:)) / norm(s.z);
 % clf; hold on;
 % contour(s.x, s.y, s.z, s.c)
 % contour(s.x, -s.y, s.z, s.c)

### 2013-02-25 src/plot_results_for_thesis.m

@@ -46,11 +46,12 @@ if 1
         y = R .* sin(T);
         c = linspace(-1, 1, 101)*sol.beta*10;
         hold on;
+        z = z + y * sol.Vinf * 0.5;
         contour(d*x, y, z, c)
         contour(d*x, -y, z, c)
         t = linspace(0, 2*pi, 100);
         fill(cos(t), sin(t), [1 1 1]*0.5)
-        axis([-1 1 -1 1]*3)
+        axis([-1 1 -1 1]*2.5)
         axis equal
         title(sprintf('Streamlines (\\Psi): \\beta = %.2f', sol.beta))
         print('-depsc2', [filename sprintf('_[%d]_Psi.eps', d)])

### 2013-02-25 src/plot_velocity_vs_beta.m

@@ -2,7 +2,8 @@ function plot_velocity_vs_beta
     Du = 1;
     zeta = 10;
     beta = linspace(0, 6);
-    U = beta * (Du*log(16) + zeta)/(1 + 2*Du);
+    U1 = (Du*log(16) + zeta)/(1 + 2*Du);
+    U = beta * U1;
     
     figure(1)
     clf; hold on; M = {};
@@ -17,9 +18,22 @@ function plot_velocity_vs_beta
     ylim([0 30])
     M{end+1} = ['Linear Fit (moderate \beta): ' sprintf('%.3f \\beta %.3f', r.a, r.b)];
     legend(M, 'Location', 'NorthWest')
-    xlabel('\beta')
-    ylabel('Steady-state velocity')
+    xlabel('\beta', 'FontSize', 16)
+    ylabel('Steady-state velocity', 'FontSize', 16)
     print -depsc2 LargeBetaV_[128_256_512]_Rmax=10.eps
+    
+    % Plot the difference between linear regime and numerical results
+    clf; hold on; M = {};
+    [b, v] = iter(128, 10,  [], []); plot(b, v - U1*b, '-s', 'Color', [1 0 0])
+    [b, v] = iter(256, 10,  [], []); plot(b, v - U1*b, '-s', 'Color', [0 .5 0])
+    [b, v] = iter(512, 10,  [], []); plot(b, v - U1*b, '-s', 'Color', [0 0 1])
+    
+    xlim([0 5])
+    ylim([0 5])
+    legend(M, 'Location', 'NorthWest')
+    xlabel('\beta', 'FontSize', 16)
+    ylabel('Difference of steady-state velocity from the linear regime', 'FontSize', 16)
+    print -depsc2 LargeBetaV_DeltaFromLinear[128_256_512]_Rmax=10.eps
 
     figure(2)
     clf; hold on; M = {};
@@ -34,10 +48,23 @@ function plot_velocity_vs_beta
     ylim([0 30])
     M{end+1} = ['Linear Fit (moderate \beta): ' sprintf('%.3f \\beta %.3f', r.a, r.b)];
     legend(M, 'Location', 'NorthWest')
-    xlabel('\beta')
-    ylabel('Steady-state velocity')
+    xlabel('\beta', 'FontSize', 16)
+    ylabel('Steady-state velocity', 'FontSize', 16)
[…]

### 2013-02-28 notes/thesis-latex-template/thesis.tex
Update thesis.

@@
 The results are shown in the following figures. 
-The steady-state velocity results are shown for several grid resolutions and several $R_{max}$ values in Figure \ref{fig:LargeBetaV_grids}, and the estimated rate of convergence is shown in Figure \ref{fig:LargeBetaRatio}.
+The steady-state velocity results are shown for several grid resolutions and several $R_{max}$ values in Figure \ref{fig:LargeBetaV_grids}, and the differences between the numerical results for
+steady-state velocity and the linear regime are shown in Figure \ref{fig:LargeBetaV_DeltaFromLinear_grids}.
+The estimated rate of convergence is shown in Figure \ref{fig:LargeBetaRatio}.
 
@@
 The resulting fluid flow is nearly proportional to that of the Stokes creeping flow, 
-as shown in Figure \ref{fig:LargeBeta_Psi}. 
+as shown in Figure \ref{fig:LargeBeta_Psi} and \ref{fig:LargeBeta_PsiMinusUniformFlow}. 
 The difference between $\Psi(r, \theta)$ and $\Psi(r, \pi-\theta)$ is shown in Figure \ref{fig:LargeBeta_PsiAsymm}, demonstrating that the flow is almost symmetric (with relative
@@
 	    \label{fig:LargeBeta_Psi}	    
+    \end{center}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=.45\textwidth]{figs/PsiMinusUniformFlow/sol_beta=1.000e-01_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_[1]_Psi.eps}
+    \includegraphics[width=.45\textwidth]{figs/PsiMinusUniformFlow/sol_beta=8.000e-01_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_[1]_Psi.eps}
+    \includegraphics[width=.45\textwidth]{figs/PsiMinusUniformFlow/sol_beta=5.000e+00_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_[1]_Psi.eps}
+    \includegraphics[width=.45\textwidth]{figs/PsiMinusUniformFlow/LinearStokes_Psi-uniformflow.eps}
+        \caption[Streamfunction results]
+        {$\beta = 0.1, 0.8, 5.0$ and Stokes streamlines results after subtraction of the uniform
+        flow streamfunction ($\frac{\cU}{2}r^2 \sin^2\theta$): grid size $512 \times 512$, 
+        $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.
+        The numerical results for $\Psi$ is scaled by $\beta^{-1}$, so the linear regime
+        will appear the same for different $\beta$ values.
+        Even for the largest beta we could compute, the velocity remains fairly symmetric and 		
+        "uneventful" also in the framework of the "laboratory" rather than that of the particle.}
+	    \label{fig:LargeBeta_PsiMinusUniformFlow}	    
     \end{center}
@@
 
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=.6\textwidth]{figs/C_Er_product.eps}
+        \caption{The product of $C(r=1, \theta=0) E_r(r=1, \theta=0) / \beta$ as
+        a function of $\beta$.}
+	    \label{fig:C_Er_product}	    
+    \end{center}
+\end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
@@
 is formed with respect to the electric field $\bE$ at the front of the particle.
-The value of $E_r$ at ($r = 1$, $\theta = 0$) is given approximately by 
+The value of $E_r / \beta$ at ($r = 1$, $\theta = 0$) is given approximately by 
 $e^{\beta/2}$, while the value of $C(r = 1, \theta = 0)$ is given approximately 
-by $e^{-\beta/2}$, and their product remains close to 1 for all $\beta$ that we could compute.
+by $e^{-\beta/2}$, and their product remains close to 1 for all $\beta$ that we could compute
+(as shown in Figure \ref{fig:C_Er_product}).
 However, the velocity of the particle remains nearly linear with $\beta$

### 2013-02-28 src/plot_stokes_solution.m

@@ -9,7 +9,7 @@ beta = 0.1;
 Du = 1;
 zeta = 10;
 U = beta * (Du*log(16) + zeta)/(1 + 2*Du);
-Psi = U * 0.5 * (R.^(-2) - R) .* sin(T);
+Psi = U * 0.5 * (R.^(-2) - 0*R) .* sin(T);
 
 z = Psi;
 z(:, [1 end]) = 0;
@@ -21,7 +21,7 @@ contour(x, y, z, c)
 contour(x, -y, z, c)
 t = linspace(0, 2*pi, 100);
 fill(cos(t), sin(t), [1 1 1]*0.5)
-axis([-1 1 -1 1]*3)
+axis([-1 1 -1 1]*2.5)
 axis equal
 title(sprintf('Streamlines (\\Psi): \\beta = %.2f', beta))
-print('-depsc2', 'LinearStokes_Psi.eps')
+print('-depsc2', 'LinearStokes_Psi-uniformflow.eps')

### 2013-03-02 notes/thesis-latex-template/hebrewPart.tex
Update thesis.

@@
-\authorHebrew{השם שלך}
+\authorHebrew{רומן זיידה}
 
-\titleHebrew{כותרת התזה}
+\titleHebrew{אלקטרוקינטיקה חישובית}
 
-\supervisorHebrew{המחקר נעשה בהנחיית פרופ'/דר' )פרטי( )משפחה( בפקולטה למדעי המחשב.}
+\supervisorHebrew{המחקר נעשה בהנחיית פרופ' עירד יבנה בפקולטה למדעי המחשב.}
 
@@
 \financialThanksHebrew{
-אני מודה לטכניון )ולגוף שנתן מלגה אם קבלת( על התמיכה הכספית הנדיבה בהשתלמותי.
+אני מודה לטכניון על התמיכה הכספית הנדיבה בהשתלמותי.
 }
 
-\JewishDateHebrew{תשרי ה'תשס"ט}
+\JewishDateHebrew{אדר ה'תשע"ג}
 
-\GregorianDateHebrew{אוקטובר \beginL2008\endL}
+\GregorianDateHebrew{מרץ \beginL2013\endL}
 
@@
 
-% 1000-2000 words
 \abstractHebrew
 
-צריך לכתוב את התקציר בעברית
+בעבודה זו אנו נחקור את התנועה האלקטרוקינטית של חלקיקים בתמיסת אלקטרוליט תחת השפעה של שדה חשמלי,
+ונפתח תשתית נומרית לפיתרון איטרטיבי של בעיות פיזיקליות לא-לינאריות מסוג זה.
+באמצעות תהליכים אלקטרוקינטיים ניתן להניע ולבצע מניפולציות בחלקיקים זעירים בתחומים שונים, כגון:
+ננו-טכנולוגיה, זרימה זעירה, הפרדה וניקוי, התפלת מים, אלקטרופורזה ועוד.
+
+בשל כוחות אלקטרוסטטיים חזקים, נוצרת שכבת שפה דקה קרוב לפני החלקיק. עקב הפער בין סקלת החלקיק
+לבין סקלת שכבת השפה, נוצר קושי להגיע לפתרון נומרי של הבעיה המלאה.
+אנו עושים שימוש בתנאי שפה אפקטיביים המתקבלים מאנליזה אסימטוטית של שכבת השפה והתכונות הכימיות 
+של החלקיק. תנאי שפה אלה פותחו ע"י פרופ' אהוד יריב ואורי שניצר עבור 
+מחליפי יונים וחלקיקים אינרטיים בעלי 
+מטען שפה, ובהם אנו משתמשים לצורך בניית פותר נומרי לפתרון הבעייה הלא-לינארית בסקלת החלקיק.
+אנו מבצעים דיסקטיזציה של המשוואות הדיפרנציאליות ושל תנאי השפה האפקטיביים, 
+והתשתית הנומרית מאפשרת בנייה 
+אוטומטית של פותר איטרטיבי בשיטת ניוטון.
+
+הפותר מאפשר קבלת תוצאות נומריות לתנועת חלקיקים מהסוג שלעיל, בהינתן עוצמת השדה החשמלי המופעל.
+התוצאות עבור שדות חלשים אומתו על ידי השוואה לפתרונות אסימפטוטיים של הבעיה.
 

### 2013-03-02 notes/thesis-latex-template/thesis.tex
Update thesis.

@@
 \usepackage[framed,numbered,autolinebreaks,useliterate]{mcode}
+\usepackage{minted}
 
 \floatstyle{ruled}
-\newfloat{program}{thp}{lop}
+\newfloat{progfram}{thp}{lop}
 %-------------------------------------------
@@
 \newcommand\eps \epsilon
-\newcommand{\R}{\ensuremath{\mathbb{R}}}
+\newcommand{\RR}{\ensuremath{\mathbb{R}}}
 \newcommand{\N}{\ensuremath{\mathbb{N}}}
@@
 
-\GregorianDateEnglish{XXXX 2012}
-\JewishDateEnglish{YYYY 5773}
+\GregorianDateEnglish{March 2013}
+\JewishDateEnglish{Adar 5773}
 
@@
 \subsection{Electrokinetic Phenomena}
+
 Electrokinetic theory describes the dynamics of charged particles
@@
 \section{Solver Design}
-Let $\cO : \R^N \rightarrow \R^N $ be an nonlinear operator.
+Let $\cO : \RR^N \rightarrow \RR^N $ be an nonlinear operator.
 In order to solve the equation $\cO(\bx) = \bzero$, Newton's method is applied, 
@@
 The base \verb|Operator| interface is defined by 
-supporting the computation of a residual vector \verb|Operator::res()|
-and a gradient matrix \verb|Operator::grad()|, given an input vector $\bx$.
+supporting the computation of a residual vector \verb|Operator.res()|
+and a gradient matrix \verb|Operator.grad()|, given an input vector $\bx$.
 This interface is implemented by specific operator classes,
@@
 \subsubsection{Pointwise scalar function}
-Let $f: \R \rightarrow \R$ be a differentiable 1D function, whose derivative is
-denoted by $f': \R \rightarrow \R$. The operator $\cF$ can be defined to
+Let $f: \RR \rightarrow \RR$ be a differentiable 1D function, whose derivative is
+denoted by $f': \RR \rightarrow \RR$. The operator $\cF$ can be defined to
 represent pointwise application of $f$:
@@
 \begin{figure}[htpb]
-\begin{lstlisting}
+\begin{minted}[mathescape,linenos,numbersep=6pt,frame=single,framesep=2mm]{matlab}
 classdef Variable < handle
@@
 end
-\end{lstlisting}
+\end{minted}
 \caption{Variable class source code.} \label{fig:variable.m}
@@
 \begin{figure}[h]
-\begin{lstlisting}
+\begin{minted}[mathescape,linenos,numbersep=6pt,frame=single,framesep=2mm]{matlab}
 % Regular structured grid class
@@
 end
-\end{lstlisting}
+\end{minted}
 \caption{Grid class source code.} \label{fig:grid.m}
@@
 \begin{figure}[h]
-\begin{lstlisting}
+\begin{minted}[mathescape,linenos,numbersep=6pt,frame=single,framesep=2mm]{matlab}
 classdef Operator < handle
@@
 end
-\end{lstlisting}
+\end{minted}
 \caption{Operator interface source code.} \label{fig:operator.m}
@@
 \begin{figure}[h]
-\begin{lstlisting}
+\begin{minted}[mathescape,linenos,numbersep=6pt,frame=single,framesep=2mm]{matlab}
 classdef Const < Operator
@@
 end
-\end{lstlisting}
+\end{minted}
 \caption{Constant operator source code.} \label{fig:const.m}
@@
 \begin{figure}[h]
-\begin{lstlisting}
+\begin{minted}[mathescape,linenos,numbersep=6pt,frame=single,framesep=2mm]{matlab}
 classdef Func < Operator
@@
 end
-\end{lstlisting}
+\end{minted}
 \caption{Pointwise function source code.} \label{fig:func.m}
@@
 \begin{figure}[h]
-\begin{lstlisting}
+\begin{minted}[mathescape,linenos,numbersep=6pt,frame=single,framesep=2mm]{matlab}
 classdef Linear < Operator
@@
 end
-\end{lstlisting}
+\end{minted}
 \caption{Linear operator source code.} \label{fig:linear.m}
@@
 \begin{figure}[htpb]
-\begin{lstlisting}
+\begin{minted}[mathescape,linenos,numbersep=6pt,frame=single,framesep=2mm]{matlab}
 classdef Join < handle
@@
 end
-\end{lstlisting}
+\end{minted}
 \caption{Join operator source code.} \label{fig:join.m}
@@
 \begin{figure}[htpb]
-\begin{lstlisting}
+\begin{minted}[mathescape,linenos,numbersep=6pt,frame=single,framesep=2mm]{matlab}
 x = linspace(0, 1); 
@@
 v.update(-(G\r)) % Solve by Newton iteration
-\end{lstlisting}
+\end{minted}
 \caption{Sample problem source code.} \label{fig:sample.m}
@@
 From Figs.
-\ref{fig:LargeBetaV_grids}-\ref{fig:LargeBetaRatio} we conclude that even our most accurate numerical solution is valid only up to $\beta = 5$ approximately, and therefore we only further examine solutions in this range.
+\ref{fig:LargeBetaV_grids}-\ref{fig:LargeBetaV_DeltaFromLinear_grids} we conclude that even our most accurate numerical solution is valid only up to $\beta = 5$ approximately, and therefore we only further examine solutions in this range.
 
@@
 and \ref{fig:LargeBeta_BoundaryLayer_C}).
-The width of the boundary layer with respect to the electric field scales, to a good approximation, is: $\bar\rho(\beta) \approx 0.2 e^{-0.5 \beta}$.
+The width of the boundary layer with respect to the electric field scales, to a good approximation, as: $\bar\rho(\beta) \approx 0.2 e^{-0.5 \beta}$.
 This causes numerical problems for the current solver at large $\beta$, due to insufficient
@@
         Even for the largest beta we could compute, the velocity remains fairly symmetric and 		
-        "uneventful" also in the framework of the "laboratory" rather than that of the particle.}
+        ``uneventful'' also in the framework of the ``laboratory'' rather than that of the particle.}
 	    \label{fig:LargeBeta_PsiMinusUniformFlow}	    
@@
 cubic correction of the steady-state velocity, as well as providing insights of the solution behavior 
-for moderate and strong electric fields.
+for moderately strong electric fields.
 For strong electric field, the nonlinear effects become dominant and
@@
 
-%\include{hebrewPart}
-
-% Actually, I found it much easier to have each chapter in a file of its own. Except for the Hebrew part, I put it all together in this example just to make things clear.
+\include{hebrewPart}
 

### 2013-03-04 notes/thesis-latex-template/hebrewPart.tex
Update thesis.

@@
 
-בעבודה זו אנו נחקור את התנועה האלקטרוקינטית של חלקיקים בתמיסת אלקטרוליט תחת השפעה של שדה חשמלי,
-ונפתח תשתית נומרית לפיתרון איטרטיבי של בעיות פיזיקליות לא-לינאריות מסוג זה.
+בעבודה זו אנו חוקרים את התנועה האלקטרוקינטית של חלקיקים בתמיסת אלקטרוליט תחת השפעה של שדה חשמלי,
+ומפתחים תשתית נומרית לפיתרון איטרטיבי של בעיות פיזיקליות לא-לינאריות מסוג זה.
 באמצעות תהליכים אלקטרוקינטיים ניתן להניע ולבצע מניפולציות בחלקיקים זעירים בתחומים שונים, כגון:
@@
 התוצאות עבור שדות חלשים אומתו על ידי השוואה לפתרונות אסימפטוטיים של הבעיה.
+כמו כן, קיבלנו באמצעות הפותר הנומרי לראשונה פתרונות בשדות חזקים, אשר אין להם עדיין קירובים אסימפטוטיים.
+מפתרונות אלה ניתן ללמוד על אופי המערכת בשדות חזקים, כולל התנהגות אסימפטוטית של שכבת שפה הנוצרת בחזית החלקיק.
 

### 2013-03-04 notes/thesis-latex-template/thesis.tex
Update thesis.

@@
 
+\usepackage[format=plain]{caption}
 \usepackage{graphicx}
@@
         functions of $\beta$, scaled by $4^n$. 
-        The graph show that, as the number of grid points in each dimension increases by 2, 
+        The graph shows that, as the number of grid points in each dimension increases by 2, 
         the discretization error decreases by 4.
@@
 regime of $\cU(\beta)$ is dominant. 
-For moderate $\beta$ values, the steady state velocity is very close to affine function of $\beta$.
+For moderate $\beta$ values, the steady state velocity is very close to an affine function of $\beta$.
 However, for larger values of $\beta$, the numerical solution
@@
         \caption[Large $\beta$ results for $\cU$ -- difference from linear regime]
-{Large $\beta$ results for $\cU(\beta) - \beta\cU_1$ ($\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$ and $\cU_1 \approx 4.258$ is linear regime coefficient). 
+{Large $\beta$ results for $\cU(\beta) - \beta\cU_1$ ($\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$ and $\cU_1 \approx 4.258$ is the linear regime coefficient). 
 The left figure shows the numerical results of $\cU(\beta)$ for $R_{max} = 10$ and the following grid sizes: $128 \times 128$, $256 \times 256$, $512 \times 512$. 
 The right figure shows the numerical results of $\cU(\beta)$ for
-$512 \times 512$ grid for $R_{max} = 100, 30, 10$.}
+$512 \times 512$ grid for $R_{max} = 100, 30, 10$.
+It is seen that the difference is indeed nearly an affine function of $\beta$ in the large-$\beta$ regime, so long as the numerical solution remains sufficiently accurate.}
 	    \label{fig:LargeBetaV_DeltaFromLinear_grids}	    
@@
         $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.
-        The numerical results for $\Psi$ is scaled by $\beta^{-1}$, so the linear regime
+        The numerical results for $\Psi$ are scaled by $\beta^{-1}$, so the linear regime
         will appear the same for different $\beta$ values.
-        Note that the numerical results show 
+        Note that the numerical results show a
         flow pattern very similar to that of the analytical Stokes flow.}
@@
         $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.
-        The numerical results for $\Psi$ is scaled by $\beta^{-1}$, so the linear regime
+        The numerical results for $\Psi$ are scaled by $\beta^{-1}$, so the linear regime
         will appear the same for different $\beta$ values.
@@
 Two interesting phenomena (cubic regime and downstream vortex) were predicted for the ion-exchanger
-using the numerical results, and were verified using asymptotic expansion of the nonlinear system.
+using the numerical results, and were verified using an asymptotic expansion of the nonlinear system.
 The electrophoresis problem was solved on a high-resolution grid to validate the asymptotic 
-cubic correction of the steady-state velocity, as well as providing insights of the solution behavior 
-for moderately strong electric fields.
+cubic correction of the steady-state velocity, as well as providing insights into
+the solution behavior for moderately strong electric fields.
 For strong electric field, the nonlinear effects become dominant and

### 2013-03-04 src/plot_C_layer.m

@@ -2,6 +2,8 @@ function plot_C_layer
 clear
 load results_C(beta)_512x512_Rmax=10.mat
 b = betas(1:end-1);
+C = C(:, b <= 5);
+b = b(b <= 5);
 clf;
 I = 1:numel(b);
 R = [];

### 2013-03-04 src/plot_Er_layer.m

@@ -2,6 +2,8 @@ function plot_Er_layer
 clear
 load results_Er(beta)_512x512_Rmax=10.mat
 b = betas(1:end-1);
+E = E(:, b <= 5);
+b = b(:, b <= 5);
 F = (E - repmat(E(end, :), size(E, 1), 1));
 F = F * diag(1./max(F));
 for j = 1:size(F, 2)

### 2013-03-04 notes/thesis-latex-template/hebrewPart.tex
Fix.

@@
 
+\section*{הבעיה הפיזיקלית}
+התיאוריה האלקטרוקינטית מתארת את הדינמיקה של חלקיקים טעונים חשמלית בתוך תמיסת יונים.
+כאשר חלקיק צובר מטען על פני שפתו, נוצרת שכבת יונים בעלת מטען נגדי בעקבות כוחות משיכה חשמליים וכך נוצרת מבנה של שכבה כפולה סביב לחלקיק.
+שכבה זו, הנקראת ''שכבת דבאי'', ממסכת את מטען השפה של החלקיק ויוצרת עקב כך הפרש פוטנציאל
+בין שפת החלקיק לבין הנוזל הנייטרלי מחוץ לשכבה.
+במקרה בו רוחב השכבה קטן באופן משמעותי מאשר מימדי החלקיק, ניתן לפתח פתרון אסימפטוטי של שכבת השפה
+
 \finishedHebrew

### 2013-03-04 notes/thesis-latex-template/thesis.tex
Fix.

@@
 due to the application of an external electric field,
-and propose a numerical framework for iterative solution of such problems.
+and propose a numerical framework for the iterative solution of such problems.
 The electrokinetic transport process can be used for
 transporting and manipulating micro- and nanoscale objects in 
-many nanotechnology applications, nano-fluidic devices, packed bed separation, 
+many nanotechnology applications, nano-fluidic devices, packed-bed separation, 
 desalination processes and various electrophoresis applications.
@@
 under an external electric field, are coupled and nonlinear, and
-in general they have no analytic solution. 
+in general have no analytic solution. 
 Moreover, any numerical solver must handle the scale disparity caused by the
@@
 number is very low (on the order of unity or smaller) which means that viscosity dominates
-and the convective term of the Navier-Stokes equations are insignificant. This also means that
+and the convective term of the Navier-Stokes equations is insignificant. This also means that
 microflows most often are laminar.
@@
 
-Because the grid is finite, the choice $R_{max}$ must be taken large enough 
+Because the grid is finite, the choice of $R_{max}$ must be large enough 
 so as to have a negligible effect on the solution. 
-On the other hand, in order to have high resolution grid near the particle surface,
-$\Delta_r$ should be minimized. It should be noted that for given grid size $n_r$,
+On the other hand, in order to have a high resolution grid near the particle surface,
+$\Delta_r$ should be minimized. It should be noted that for a given grid size $n_r$,
 these requirements cannot be satisfied simultaneously -- thus, a compromise is required
@@
 
-Each discrete variable is located with respect of its cell 
+Each discrete variable is located with respect to its cell 
 as shown at Figure \ref{fig:grids}.
@@
 Force components ($\bF = -\bnabla P + \bLaplacian \bV + \bnabla \varPhi \Laplacian \varPhi$) 
-are discretized on the staggered velocity grid using finite difference
+are discretized on the staggered velocity grid using the finite difference
 method, where linear interpolation is used for the Coulomb force and 
@@
 \section{Solver Design}
-Let $\cO : \RR^N \rightarrow \RR^N $ be an nonlinear operator.
+Let $\cO : \RR^N \rightarrow \RR^N $ be a nonlinear operator.
 In order to solve the equation $\cO(\bx) = \bzero$, Newton's method is applied, 
@@
 (given the current solution $\bx$)
-and the solution of sparse linear system $\bG \Delta \bx = -\br$.
+and the solution of the sparse linear system $\bG \Delta \bx = -\br$.
 
 \subsection{Operator Representation}
-System variable $\bx$ is defined as the concatenation $\bx = [\,\varPhi, C, V_r, V_\theta, P\,]$.
+The system variable $\bx$ is defined as the concatenation $\bx = [\,\varPhi, C, V_r, V_\theta, P\,]$.
 Thus, each problem variable can be computed by applying an appropriate projection operator on $\bx$.
@@
 and the boundary conditions operators (described in Subsection \ref{sec:disc_boundary}).
-This way, the same numerical solver handles both the nonlinear system equation and nonlinear
+This way, the same numerical solver handles both the nonlinear system equations and nonlinear
 boundary conditions.
@@
 denoted by $f': \RR \rightarrow \RR$. The operator $\cF$ can be defined to
-represent pointwise application of $f$:
+represent a pointwise application of $f$:
 \begin{equation}\begin{array}{cc}
@@
 \subsubsection{Constant value}
-A constant operator $\mathcal{C}$ is defined by constant vector $\bc$ 
-(that does not depend on $\bx$):
+A constant operator $\mathcal{C}$ is defined by the constant vector $\bc$ 
+(which does not depend on $\bx$):
 \begin{equation}\begin{array}{cc}
@@
 \subsubsection{Binary operators}
-Let $\cO_1$ and $\cO_2$ be two operators, so their pointwise addition, subtraction,
+Let $\cO_1$ and $\cO_2$ be two operators, so that their pointwise addition, subtraction,
 and multiplication, are defined as follows:

### 2013-03-06 notes/thesis-latex-template/hebrewPart.tex
before review

--- 2013-03-04 notes/thesis-latex-template/hebrewPart.tex
@@
 
-בעבודה זו אנו חוקרים את התנועה האלקטרוקינטית של חלקיקים בתמיסת אלקטרוליט תחת השפעה של שדה חשמלי,
-ומפתחים תשתית נומרית לפיתרון איטרטיבי של בעיות פיזיקליות לא-לינאריות מסוג זה.
+\section*{מבוא}
+
+בעבודה זו אנו חוקרים את התנועה האלקטרוקינטית של חלקיקים בתמיסת אלקטרוליט תחת השפעה של שדה חשמלי, ומפתחים תשתית נומרית לפתרון איטרטיבי של בעיות פיזיקליות לא-לינאריות מסוג זה.
 באמצעות תהליכים אלקטרוקינטיים ניתן להניע ולבצע מניפולציות בחלקיקים זעירים בתחומים שונים, כגון:
 ננו-טכנולוגיה, זרימה זעירה, הפרדה וניקוי, התפלת מים, אלקטרופורזה ועוד.
+בשל כוחות אלקטרוסטטיים חזקים, נוצרת שכבת שפה דקה קרוב לפני החלקיק. עקב הפער בין סקלת החלקיק לבין סקלת שכבת השפה, נוצר קושי להגיע לפתרון נומרי של הבעיה המלאה.
 
-בשל כוחות אלקטרוסטטיים חזקים, נוצרת שכבת שפה דקה קרוב לפני החלקיק. עקב הפער בין סקלת החלקיק
-לבין סקלת שכבת השפה, נוצר קושי להגיע לפתרון נומרי של הבעיה המלאה.
-אנו עושים שימוש בתנאי שפה אפקטיביים המתקבלים מאנליזה אסימטוטית של שכבת השפה והתכונות הכימיות 
-של החלקיק. תנאי שפה אלה פותחו ע"י פרופ' אהוד יריב ואורי שניצר עבור 
-מחליפי יונים וחלקיקים אינרטיים בעלי 
-מטען שפה, ובהם אנו משתמשים לצורך בניית פותר נומרי לפתרון הבעייה הלא-לינארית בסקלת החלקיק.
-אנו מבצעים דיסקטיזציה של המשוואות הדיפרנציאליות ושל תנאי השפה האפקטיביים, 
-והתשתית הנומרית מאפשרת בנייה 
-אוטומטית של פותר איטרטיבי בשיטת ניוטון.
-
+אנו עושים שימוש בתנאי שפה אפקטיביים המתקבלים מאנליזה אסימפטוטית של שכבת השפה והתכונות הכימיות של החלקיק.
+תנאי שפה אלה פותחו על ידי פרופ' אהוד יריב ואורי שניצר עבור מחליפי יונים וחלקיקים אינרטיים בעלי מטען שפה, ובהם אנו משתמשים לצורך בניית פותר נומרי לפתרון הבעיה הלא-לינארית בסקלת החלקיק.
+אנו מבצעים דיסקרטיזציה של המשוואות הדיפרנציאליות ושל תנאי השפה האפקטיביים, והתשתית הנומרית מאפשרת בנייה אוטומטית של פותר איטרטיבי בשיטת ניוטון.
 הפותר מאפשר קבלת תוצאות נומריות לתנועת חלקיקים מהסוג שלעיל, בהינתן עוצמת השדה החשמלי המופעל.
@@
 
+\section*{הבעיה הפיזיקלית}
+התאוריה האלקטרוקינטית מתארת את הדינמיקה של חלקיקים טעונים חשמלית בתוך תמיסת יונים.
+כאשר חלקיק צובר מטען על פני שפתו, נוצרת שכבת יונים בעלת מטען נגדי בעקבות כוחות משיכה חשמליים וכך נוצרת מבנה של שכבה כפולה סביב לחלקיק.
+שכבה זו, הנקראת ''שכבת דבאי'', ממסכת את מטען השפה של החלקיק ויוצרת עקב כך הפרש פוטנציאל
+בין שפת החלקיק לבין הנוזל הניטרלי מחוץ לשכבה.
+במקרה בו רוחב השכבה קטן באופן משמעותי מאשר ממדי החלקיק, ניתן לפתח פתרון אנליטי אסימפטוטי של הדינמיקה בשכבת השפה.
+
+המשתנים בבעיית זרימה אלקטרוקינטית הם הפוטנציאל החשמלי, מהירות הנוזל והלחץ, וריכוז היונים. תנאי השפה מוגדרים בהתאם לתנאי הבעיה הספציפית ונקבעים על ידי צורת החלקיק, תכונותיו הכימיות והדינמיקה של הנוזל. 
+המשוואות הדיפרנציאליות החלקיות אשר מתארות את התנהגות המערכת תחת השפעתו של שדה חשמלי חיצוני הן מצומדות, לא-לינאריות, וללא פתרון אנליטי ידוע.
+כמו כן, על כל פותר נומרי יהיה להתמודד עם פער הסקלות שנוצר כתוצאה מכך שעובי שכבת השפה קטן משמעותית לעומת ממדי החלקיק.
+
+על מנת להתמודד עם קושי זה, ניתן לפתח תנאי שפה אפקטיביים מחוץ לשכבת דבאי ולקבל מודל מקרוסקופי לבעיה על ידי שימוש בפתרון האסימפטוטי לשכבת השפה שלעיל.
+מודל זה ניתן לפתרון מקורב עבור חלקיק ספרי שנמצא תחת השפעה של  שדה חשמלי חלש, אך קשה להרחיב פתרון אנליטי זה עבור מקרים כלליים יותר.
+יש לציין כי כאשר השדה החשמלי מתחזק, צפויות להתרחש תופעות לא-לינאריות משמעותיות, אשר עדיין לא נחקרו באופן משמעותי.
+
+\section*{שימושים}
+לתופעות האלקטרוקינטיות שתוארו לעיל נמצאו שימושים רבים בפיתוח התקנים למיקרו-זרימה ושיטות לבקרה ומניפולציה של זרימת נולים בסקלות של מיקרונים וננומטרים.
+לצורך כך, נדרש מחקר ופיתוח של רכיבים מיקרו-זרימה שונים, כגון שסתומים, משאבות, גלאים, מיקסרים, מסננים, התקנים להפרדת חומרים וכדומה.
+רכיבים אלו מורכבים על מערכות זעירות הנראות "מעבדה-על-שבב", ומחוברים על ידי מיקרו-תעלות.
+מערכות אלו מיוצרות בשיטות של ננו-ליטוגרפיה.
+ניתן להשפיע על אופי הזרימה על ידי הפעלת שדה חשמלי חיצוני על פני המערכת כולה, או לחלופין, על ידי הפעלתו באופן לוקלי בתוך מיקרו-תעלה ספציפית.
+לרוב, מספר ריינולדס בזרימה כזו הוא נמוך מאוד. על כן, האפקט הדומיננטי בזרימה זו הוא הצמיגות, ואיבר ההסעה של משוואות נבייר-סטוקס הופך להיות זניח, ולפיכך, מיקרו-זרימה היא לרוב זרימה למינארית.
+
+בעשור האחרונה, התרחשה התקדמות משמעותית בחקר מיקרו-זרימה, הודות לתפוצתם של כלים ושיטות לייצור של מערכות קטנות, זולות וניידות עבור אבחון רפואי מהיר, ועבור מחקר בסיסי של תהליכים פיזיקליים, כימיים וביולוגיים.
+ניתן למנות שימושים לדוגמה וביניהם הפרדה של די.אנ.איי, אנליזה של תאים וזיהוי פלילי, מערכות מיקרו-כימיות מורכבות ומשולבות, הפרדה מבוססת מצע צפוף, התפלת מים, העברה פיזיולוגית של תרופות אל רקמת המטרה, זיהוי גומרי מחלה ועוד.
+
+\section*{מטרת העבודה}
+מטרת עבודה זו הינה לפתח ולממש תשתית תוכנה לצורך ייצור של פותרים נומריים איטרטיביים עבור בעיות אלקטרוקינטיות מקרוסקופיות לא-לינאריות, וליישם תשתית זו לתיאור ומחקר של מערכות אשר אין להן פתרונות אנליטיים ידועים.
+שתי מערכות בהן מתמקדת עבודה זו הן נדידת חלקיק מחליף יונים בשדה חשמלי ואלקטרופורזה של חלקיק אינרטי בעל מטען שפה.
+התשתית מורכבת מאוסף של מודולים המאפשרים לבנות מודל דיסקטי של בעיה אלקטרוקינטית ספציפית.
+בהינתן מודל זה, התשתית מאפשרת לפתור את מערכת המשוואות הלא-לינארית באופן אוטומטי.
+כך ניתן לחקור מערכות שונות מבחינה פיזיקלית ללא שינוי בקוד של הפותר הנומרי.
+התשתית הנומרית והפתרונות הנומריים המתקבלים ממנה מאפשרים לקבל תובנות על התהליכים הכימיים והפיזיקליים במקרים הרבה יותר כלליים מאשר הידוע כיום.
+כמו כן, התוצאות של הפותר צפויות לאפשר פיתוח אנליטי של פתרונות אסימפטוטיים מקורבים, על סמך ההתנהגות האסימפטוטית של הפתרונות הנומריים.
+כמו כן, הפותר הנומרי יכול לשמש למחקר תאורטי של תופעות פיזיקליות מעניינות שנצפו באופן ניסיוני.
+תופעה אחת שניתן לציין כדוגמה היא הופעה של מיקרו-מערבולות בזרימה אלקטרוקינטית לא-לינארית, אשר יכולה לשמש כמיקסר עבור אפליקציות שונות של מיקרו-זרימה.
+
+\section*{השיטה הנומרית}
+על מנת לבנות פותר נומרי לבעיה אלקטרוקינטית ספיציפית, יש לבצע תחילה דיסקרטיזציה של מערכת המשוואות הדיפרניאליות החלקיות ושל תנאי השפה על פני סריג סופי.
+אנו עושים שימוש בסריג רגולרי במערכת קואורדינטות ספרית, על מנת לנצל את הסימטריה הצירית בבעיה בתיאור תנאי השפה וחיסכון בזיכרון הנדרש לפותר, מכיוון שהבעיה הופכת להיות "דו-מימדית".
+מערכת המשוואות הדיסקרטית היא לא לינארית ולכן אנו עושים שימוש בפותר איטרטיבי מסוג ניוטון על מנת לקבל את הפתרון הדיסקרטי אחרי מספר קטן של איטרציות.
+על מנת לעשות שימוש בפותר זה, יש לנסח את מערכת המשוואות כאופרטור רב-ממדי, אשר עבורו אנו נדרשים למצוא את וקטור הקלט שיאפס את תוצאתו.
+בשיטת ניוטון, אנו נדרש לחשב את הגרדיינט של אופרטור זה על מנת לקרב אותו על ידי אופרטור לינארי וכך לחשב את השינוי הנדרש לווקטור הקלט, באמצעות פתרון של מערכת משוואות לינארית, המתקבלת מהגרדיינט ותוצאת האופרטור הנוכחיים.
+
+מכיוון שחישוב אנליטי של הגרדיינט הוא מסובך למדי עבור הבעיות אותן אנו באים לפתור, בחרנו לממש את חישוב הגרדיינט על ידי שיטה של גזירה אוטומטית.
+בשיטה זו, האופרטור הלא-לינארי, אשר מייצג את מערכת המשוואות שיש לפתור, נוצר על ידי אלגברה של אופרטורים בסיסיים ופשוטים יותר, כגון אופרטור קבוע, וקטור הקלט, הפעלת טרנספורמציה לינארית, חישוב של פונקציה אנליטית, חיבור, חיסור, כפל איבר-איבר והרכבה של אופרטורים אחרים.
+כל אופרטור מממש את הממשק הבסיסי, המאפשר את חישוב וקטור התוצאה ואת מטריצת הגרדיינט שלו, בהינתן וקטור הקלט.
+החישוב מתאפשר על ידי הפעלה של כלל השרשרת בגזירה של אופרטורים מורכבים, כך שכל המידע שאופרטור נדרש על מנת לחשב את הגרדיינט שלו, מתקבל מהאופרטורים שמרכיבים אותו באופן היררכי.
+מכיוון שהגרדיינטים המתקבלים ניתנים לייצוג יעיל על ידי מטריצות דלילות, המשאבים הנדרשים לחישוב הגרדיינט בשיטה זו זניחים יחסית למשאבים הנדרשים לפתרון המערכת הלינארית הנדרשת לחישוב צעד ניוטון.
+מבנה נתונים זה מאפשר לבצע אופטימיזציה על הייצוג האופרטורי של מערכת המשוואות.
+כמו כן, נציין כי שינויים במודל הפיזיקלי של המערכת אינם דורשים שינויים במימוש הנומרי של הפותר, אלא רק בשינוי של האופרטורים הרלוונטיים בייצוג הדיסקרטי של הבעיה.
+
 \finishedHebrew

### 2013-03-07 notes/thesis-latex-template/hebrewPart.tex
Review by Irad

@@
 \section*{מבוא}
-
 בעבודה זו אנו חוקרים את התנועה האלקטרוקינטית של חלקיקים בתמיסת אלקטרוליט תחת השפעה של שדה חשמלי, ומפתחים תשתית נומרית לפתרון איטרטיבי של בעיות פיזיקליות לא-לינאריות מסוג זה.
@@
 ננו-טכנולוגיה, זרימה זעירה, הפרדה וניקוי, התפלת מים, אלקטרופורזה ועוד.
-בשל כוחות אלקטרוסטטיים חזקים, נוצרת שכבת שפה דקה קרוב לפני החלקיק. עקב הפער בין סקלת החלקיק לבין סקלת שכבת השפה, נוצר קושי להגיע לפתרון נומרי של הבעיה המלאה.
+בשל כוחות אלקטרוסטטיים חזקים, נוצרת שכבת שפה דקה קרוב לפני החלקיק. עקב הפער בין סקאלת החלקיק לבין סקאלת שכבת השפה, נוצר קושי להגיע לפתרון נומרי של הבעיה המלאה.
 
 אנו עושים שימוש בתנאי שפה אפקטיביים המתקבלים מאנליזה אסימפטוטית של שכבת השפה והתכונות הכימיות של החלקיק.
-תנאי שפה אלה פותחו על ידי פרופ' אהוד יריב ואורי שניצר עבור מחליפי יונים וחלקיקים אינרטיים בעלי מטען שפה, ובהם אנו משתמשים לצורך בניית פותר נומרי לפתרון הבעיה הלא-לינארית בסקלת החלקיק.
-אנו מבצעים דיסקרטיזציה של המשוואות הדיפרנציאליות ושל תנאי השפה האפקטיביים, והתשתית הנומרית מאפשרת בנייה אוטומטית של פותר איטרטיבי בשיטת ניוטון.
+תנאי שפה אלה פותחו על ידי פרופ' אהוד יריב ואורי שניצר עבור מחליפי יונים וחלקיקים אינרטיים בעלי מטען שפה, ובהם אנו משתמשים לצורך בניית פותר נומרי לפתרון הבעיה הלא-לינארית בסקאלת החלקיק.
+אנו מבצעים דיסקרטיזציה של המשוואות הדיפרנציאליות ושל תנאי השפה האפקטיביים, ומפתחים תשתית נומרית אשר מאפשרת בנייה אוטומטית של פותר איטרטיבי בשיטת ניוטון.
 הפותר מאפשר קבלת תוצאות נומריות לתנועת חלקיקים מהסוג שלעיל, בהינתן עוצמת השדה החשמלי המופעל.
@@
 כמו כן, קיבלנו באמצעות הפותר הנומרי לראשונה פתרונות בשדות חזקים, אשר אין להם עדיין קירובים אסימפטוטיים.
-מפתרונות אלה ניתן ללמוד על אופי המערכת בשדות חזקים, כולל התנהגות אסימפטוטית של שכבת שפה הנוצרת בחזית החלקיק.
+מפתרונות אלה ניתן ללמוד על אופי המערכת בשדות חזקים, כולל התנהגות אסימפטוטית של שכבת שפה נוספת אשר נוצרת בחזית החלקיק.
 
 \section*{הבעיה הפיזיקלית}
-התאוריה האלקטרוקינטית מתארת את הדינמיקה של חלקיקים טעונים חשמלית בתוך תמיסת יונים.
+התיאוריה האלקטרוקינטית מתארת את הדינמיקה של חלקיקים טעונים חשמלית בתוך תמיסת יונים.
 כאשר חלקיק צובר מטען על פני שפתו, נוצרת שכבת יונים בעלת מטען נגדי בעקבות כוחות משיכה חשמליים וכך נוצרת מבנה של שכבה כפולה סביב לחלקיק.
@@
 המשוואות הדיפרנציאליות החלקיות אשר מתארות את התנהגות המערכת תחת השפעתו של שדה חשמלי חיצוני הן מצומדות, לא-לינאריות, וללא פתרון אנליטי ידוע.
-כמו כן, על כל פותר נומרי יהיה להתמודד עם פער הסקלות שנוצר כתוצאה מכך שעובי שכבת השפה קטן משמעותית לעומת ממדי החלקיק.
+כמו כן, על כל פותר נומרי יהיה להתמודד עם פער הסקאלות שנוצר כתוצאה מכך שעובי שכבת השפה קטן משמעותית לעומת ממדי החלקיק.
 
 על מנת להתמודד עם קושי זה, ניתן לפתח תנאי שפה אפקטיביים מחוץ לשכבת דבאי ולקבל מודל מקרוסקופי לבעיה על ידי שימוש בפתרון האסימפטוטי לשכבת השפה שלעיל.
-מודל זה ניתן לפתרון מקורב עבור חלקיק ספרי שנמצא תחת השפעה של  שדה חשמלי חלש, אך קשה להרחיב פתרון אנליטי זה עבור מקרים כלליים יותר.
-יש לציין כי כאשר השדה החשמלי מתחזק, צפויות להתרחש תופעות לא-לינאריות משמעותיות, אשר עדיין לא נחקרו באופן משמעותי.
+מודל זה ניתן לפתרון מקורב עבור חלקיק כדורי שנמצא תחת השפעה של  שדה חשמלי חלש, אך קשה להרחיב פתרון אנליטי זה עבור מקרים כלליים יותר.
+יש לציין כי כאשר השדה החשמלי מתחזק, צפויות להתרחש תופעות לא-לינאריות משמעותיות, אשר עדיין לא נחקרו באופן נרחב.
 
 \section*{שימושים}
-לתופעות האלקטרוקינטיות שתוארו לעיל נמצאו שימושים רבים בפיתוח התקנים למיקרו-זרימה ושיטות לבקרה ומניפולציה של זרימת נולים בסקלות של מיקרונים וננומטרים.
-לצורך כך, נדרש מחקר ופיתוח של רכיבים מיקרו-זרימה שונים, כגון שסתומים, משאבות, גלאים, מיקסרים, מסננים, התקנים להפרדת חומרים וכדומה.
-רכיבים אלו מורכבים על מערכות זעירות הנראות "מעבדה-על-שבב", ומחוברים על ידי מיקרו-תעלות.
+לתופעות האלקטרוקינטיות שתוארו לעיל נמצאו שימושים רבים בפיתוח התקנים למיקרו-זרימה ושיטות לבקרה ומניפולציה של זרימת נוזלים בסקאלות של מיקרונים וננומטרים.
+לצורך כך, נדרש מחקר ופיתוח של רכיבי מיקרו-זרימה שונים, כגון שסתומים, משאבות, גלאים, מיקסרים, מסננים, התקנים להפרדת חומרים וכדומה.
+רכיבים אלו מורכבים על מערכות זעירות הנקראות "מעבדה-על-שבב", ומחוברים על ידי מיקרו-תעלות.
 מערכות אלו מיוצרות בשיטות של ננו-ליטוגרפיה.
-ניתן להשפיע על אופי הזרימה על ידי הפעלת שדה חשמלי חיצוני על פני המערכת כולה, או לחלופין, על ידי הפעלתו באופן לוקלי בתוך מיקרו-תעלה ספציפית.
-לרוב, מספר ריינולדס בזרימה כזו הוא נמוך מאוד. על כן, האפקט הדומיננטי בזרימה זו הוא הצמיגות, ואיבר ההסעה של משוואות נבייר-סטוקס הופך להיות זניח, ולפיכך, מיקרו-זרימה היא לרוב זרימה למינארית.
+ניתן להשפיע על אופי הזרימה על ידי הפעלת שדה חשמלי חיצוני על פני המערכת כולה, או לחלופין, על ידי הפעלתו באופן מקומי בתוך מיקרו-תעלה ספציפית.
+לרוב, מספר ריינולדס בזרימה כזו הוא נמוך מאוד. על כן, האפקט הדומיננטי בזרימה זו הוא הצמיגות, ואיבר ההסעה של משוואות נבייה-סטוקס הופך להיות זניח, ולפיכך, מיקרו-זרימה היא לרוב זרימה למינארית.
 
-בעשור האחרונה, התרחשה התקדמות משמעותית בחקר מיקרו-זרימה, הודות לתפוצתם של כלים ושיטות לייצור של מערכות קטנות, זולות וניידות עבור אבחון רפואי מהיר, ועבור מחקר בסיסי של תהליכים פיזיקליים, כימיים וביולוגיים.
-ניתן למנות שימושים לדוגמה וביניהם הפרדה של די.אנ.איי, אנליזה של תאים וזיהוי פלילי, מערכות מיקרו-כימיות מורכבות ומשולבות, הפרדה מבוססת מצע צפוף, התפלת מים, העברה פיזיולוגית של תרופות אל רקמת המטרה, זיהוי גומרי מחלה ועוד.
+בעשור האחרון התרחשה התקדמות משמעותית בחקר מיקרו-זרימה, הודות לתפוצתם של כלים ושיטות לייצור של מערכות קטנות, זולות וניידות עבור אבחון רפואי מהיר, ועבור מחקר בסיסי של תהליכים פיזיקליים, כימיים וביולוגיים.
+ניתן למנות שימושים לדוגמה וביניהם הפרדה של די.אנ.איי, אנליזה של תאים וזיהוי פלילי, מערכות מיקרו-כימיות מורכבות ומשולבות, הפרדה מבוססת מצע צפוף, התפלת מים, העברה פיזיולוגית של תרופות אל רקמת המטרה, זיהוי גורמי מחלה ועוד.
 
@@
 שתי מערכות בהן מתמקדת עבודה זו הן נדידת חלקיק מחליף יונים בשדה חשמלי ואלקטרופורזה של חלקיק אינרטי בעל מטען שפה.
-התשתית מורכבת מאוסף של מודולים המאפשרים לבנות מודל דיסקטי של בעיה אלקטרוקינטית ספציפית.
+התשתית מורכבת מאוסף של מודולים המאפשרים לבנות מודל דיסקרטי של בעיה אלקטרוקינטית ספציפית.
 בהינתן מודל זה, התשתית מאפשרת לפתור את מערכת המשוואות הלא-לינארית באופן אוטומטי.
 כך ניתן לחקור מערכות שונות מבחינה פיזיקלית ללא שינוי בקוד של הפותר הנומרי.
-התשתית הנומרית והפתרונות הנומריים המתקבלים ממנה מאפשרים לקבל תובנות על התהליכים הכימיים והפיזיקליים במקרים הרבה יותר כלליים מאשר הידוע כיום.
-כמו כן, התוצאות של הפותר צפויות לאפשר פיתוח אנליטי של פתרונות אסימפטוטיים מקורבים, על סמך ההתנהגות האסימפטוטית של הפתרונות הנומריים.
-כמו כן, הפותר הנומרי יכול לשמש למחקר תאורטי של תופעות פיזיקליות מעניינות שנצפו באופן ניסיוני.
+התשתית הנומרית והפתרונות הנומריים המתקבלים ממנה מאפשרים לקבל תובנות על התהליכים הכימיים והפיזיקליים במקרים הרבה יותר כלליים מן הידוע כיום.
+כמו כן, התוצאות של הפותר צפויות לקדם פיתוח אנליטי של פתרונות אסימפטוטיים מקורבים, על סמך ההתנהגות האסימפטוטית של הפתרונות הנומריים.
+כמו כן, הפותר הנומרי יכול לשמש למחקר תיאורטי של תופעות פיזיקליות מעניינות שנצפו באופן ניסיוני.
 תופעה אחת שניתן לציין כדוגמה היא הופעה של מיקרו-מערבולות בזרימה אלקטרוקינטית לא-לינארית, אשר יכולה לשמש כמיקסר עבור אפליקציות שונות של מיקרו-זרימה.
@@
 \section*{השיטה הנומרית}
-על מנת לבנות פותר נומרי לבעיה אלקטרוקינטית ספיציפית, יש לבצע תחילה דיסקרטיזציה של מערכת המשוואות הדיפרניאליות החלקיות ושל תנאי השפה על פני סריג סופי.
-אנו עושים שימוש בסריג רגולרי במערכת קואורדינטות ספרית, על מנת לנצל את הסימטריה הצירית בבעיה בתיאור תנאי השפה וחיסכון בזיכרון הנדרש לפותר, מכיוון שהבעיה הופכת להיות "דו-מימדית".
+על מנת לבנות פותר נומרי לבעיה אלקטרוקינטית ספציפית, יש לבצע תחילה דיסקרטיזציה של מערכת המשוואות הדיפרניאליות החלקיות ושל תנאי השפה על פני סריג סופי.
+אנו עושים שימוש בסריג רגולרי במערכת קואורדינטות כדורית, על מנת לנצל את הסימטריה הצירית בבעיה בתיאור תנאי השפה וחיסכון בזיכרון הנדרש לפותר, מכיוון שהבעיה הופכת להיות "דו-מימדית".
 מערכת המשוואות הדיסקרטית היא לא לינארית ולכן אנו עושים שימוש בפותר איטרטיבי מסוג ניוטון על מנת לקבל את הפתרון הדיסקרטי אחרי מספר קטן של איטרציות.

### 2013-03-07 notes/thesis-latex-template/thesis.tex
Review by Irad

@@
 and good correspondence is achieved.
+Finally, the new solver is applied in the regime of moderately large values of the external field, where no analytical results are known.
+The numerical results uncover the strong-field scaling behavior, including a new boundary layer at the front of the particle that scales exponentially with respect to the external field, and also a well-defined dependence of the particle steady-state velocity on this field.
 

### 2013-03-09 notes/thesis-latex-template/thesis.tex
Irad review

@@
 Since each operator can compute its residual and gradient, we
-can compute automatically the residual and gradient of \verb|o4|
-from these of \verb|o1|, \verb|o2|, \verb|o3| using the derivation
+can compute automatically the residual and gradient of \verb|op4|
+from these of \verb|op1|, \verb|op2|, \verb|op3| using the derivation
 rules described at \ref{sec:operator-interface}.
@@
 \verb|Func| operator implements point-wise analytic function
-application (whose derivative is computed using symbolic differentiation toolbox) on the same grid of the input operator (Figure \ref{fig:func.m}). 
+application (whose derivative is computed using the symbolic differentiation toolbox) on the same grid of the input operator (Figure \ref{fig:func.m}). 
 \verb|Linear| operator is implemented
@@
 multiplication are implemented as operators whose
-output grid is the as the grid of their inputs. 
+output grid is the same as the grid of their inputs. 
 The implementation is used by operator overloading in 
@@
         functions of $\beta$, scaled by $4^n$. 
-        The graph shows that, as the number of grid points in each dimension increases by 2, 
-        the discretization error decreases by 4.
+        The graph shows that, as the number of grid points in each dimension increases by a factor of 2, 
+        the discretization error decreases by a factor of 4.
         }
@@
 The electrophoresis problem was solved on a high-resolution grid to validate the asymptotic 
-cubic correction of the steady-state velocity, as well as providing insights into
+cubic correction of the steady-state velocity, as well as to provide insights into
 the solution behavior for moderately strong electric fields.

### 2013-04-20 notes/CompPhys/main.tex
Draft for Computational Physics Journal.

--- 2013-03-09 notes/thesis-latex-template/thesis.tex
@@
-% PhD, MSc (choose one)
-% beforeExam (to make the personal thanks invisible)
-\documentclass[MSc,beforeExam]{iitcsthesis}
+\documentclass[preprint,10pt]{elsarticle}
 
@@
 \usepackage{longtable}
-\usepackage[framed,numbered,autolinebreaks,useliterate]{mcode}
-\usepackage{minted}
 
@@
 
-\setlength{\textheight}{9in}
-\setlength{\textwidth}{7in}
-\setlength{\topmargin}{0.05in}
-\setlength{\headheight}{0.05in}
-\setlength{\headsep}{0.1in}
-\setlength{\evensidemargin}{0in}
-\setlength{\oddsidemargin}{0in}
-\setlength{\parindent}{0.0 in}
-\setlength{\parskip}{0.1 in}
+\journal{Computational Physics}
 
@@
 
-\authorEnglish{Roman Zeyde}
-
-\titleEnglish{Computational Electrokinetics}
-
-\supervisorEnglish{The research thesis was done under the supervision
-of Prof. Irad Yavneh in the Computer Science Department.}
-
-\GregorianDateEnglish{March 2013}
-\JewishDateEnglish{Adar 5773}
-
-\personalThanksEnglish{Write thanks to professor and others}
-\financialThanksEnglish{The generous financial support of the Technion is gratefully acknowledged.}
-
-\maketitleEnglish
-
-% The English abstract should be 200-500 words long.
-\abstractEnglish
+\begin{frontmatter}
+
+\author{Roman Zeyde}
+\ead{romanz@cs.technion.ac.il}
+
+\author{Irad Yavneh}
+\ead{irad@cs.technion.ac.il}
+
+\address{Technion -- Israel Institute of Technology, Haifa 32000, Israel}
+
+\title{Computational Electrokinetics}
+
+\begin{abstract}
 In this work we study the electrokinetic 
@@
 The numerical results uncover the strong-field scaling behavior, including a new boundary layer at the front of the particle that scales exponentially with respect to the external field, and also a well-defined dependence of the particle steady-state velocity on this field.
-
-\abbreviationsAndNotationsEnglish
-
-\begin{longtable}{lcl}
-$\varPhi$ 	& --- & Electric potential \\
-$C$ 		& --- & Ionic concentration \\
-$\bV$		& --- & Fluid velocity \\
-$P$			& --- & Fluid pressure \\
-$\tT$		& --- & Stress tensor \\
-$\bF$		& --- & Force vector \\
-$\bnhat$	& --- & Surface normal \\
-$\cO$ 		& --- & Operator \\
-$\beta$		& --- & Dimensionless electric field magnitude \\
-$\delta$	& --- & Dimensionless Debye layer width \\
-$\cU$		& --- & Dimensionless steady-state velocity 
-\end{longtable}
-
-%Or, if your tables are long, ``\usepackage{longtable}'' at the beginning, and then  ``\begin{longtable}[l]{lcl} ... \end{longtable}''
-
-\chapter{Introduction}
-
-\section{The Physical Problem}
-\subsection{Electrokinetic Phenomena}
+\end{abstract}
+
+\end{frontmatter}
+
+\section{Introduction}
+
+\subsection{The Physical Problem}
 
@@
     \begin{center}
-        \includegraphics[width=0.4\textwidth]
+        \includegraphics[width=0.3\textwidth]
             {figs/debye.eps}
@@
 Various applications are \cite{whitesides2006origins, erickson2004integrated, squires2005microfluidics, hardt2007microfluidic}:
-\begin{enumerate}
-\item DNA separation and sequencing \cite{wainright2003preconcentration}.
-\item Cell analysis and forensic identification \cite{wu2004chemical, weinberger1993practical, horsman2007forensic}.
-\item Integrated microchemical systems \cite{kothare2006dynamics}.
-\item Packed-bed separation \cite{leinweber2004, losey2001microfabricated}.
-\item Desalination processes \cite{kim2010direct}.
-\item Drug delivery and pathogen detection \cite{santini2000microchips}.
-\end{enumerate}
+DNA separation and sequencing \cite{wainright2003preconcentration},
+cell analysis and forensic identification \cite{wu2004chemical, weinberger1993practical, horsman2007forensic},
+integrated microchemical systems \cite{kothare2006dynamics},
+packed-bed separation \cite{leinweber2004, losey2001microfabricated},
+desalination processes \cite{kim2010direct},
+drug delivery and pathogen detection \cite{santini2000microchips}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Governing Equations} \label{sec:equations}
-
-\subsection{Nondimensionalization}
+\subsection{Governing Equations} \label{sec:equations}
+
+\subsubsection{Nondimensionalization}
 We follow the derivation presented by Yariv in \cite{yariv2010asymptotic}.
@@
 
-\subsection{Boundary conditions}
+\subsubsection{Boundary conditions}
 We assume that a constant electric field of nondimensional magnitude $\beta$,
@@
 We consider the following scenarios:
-\subsubsection{Ion-exchanger}
+\paragraph{Ion-exchanger}
 We follow the microscale model presented at \cite{yariv2010migration}
@@
 
-\subsubsection{Inert particle}
+\paragraph{Inert particle}
 We follow the microscale model presented at \cite{schnitzer2012surface}
@@
 \subsubsection{Ion-exchanger} See \cite{yariv2010migration} for full derivation
-of the nonlinear effective boundary conditions (and also Appendix \ref{append:slip}):
+of the nonlinear effective boundary conditions:
 \begin{align}
 \label{eq:ionex_bnd}
-\nonumber 
-0 &= \varPhi + \log C, \\
-0 &= \deriv{}{n} \pars{\varPhi - \log C}, \\
-\nonumber \bV &= 
+0 = \varPhi + \log C, 0 = \deriv{}{n} \pars{\varPhi - \log C}, 
+\bV = 
 \zeta \cdot \bnabla_\mathcal{S} \varPhi 
@@
 \begin{align} \label{eq:ephor_bnd}
-\nonumber
-0 &= {\deriv{C}{n} - \Du \nabla^2_s \pars{\varPhi - \log C}}, \\
-0 &= {\deriv{C}{n} + C \deriv{\varPhi}{n}}, \\
-\nonumber
-\bV &= \zeta \cdot \bnabla_\mathcal{S} \pars{\varPhi - \log C} +
+0 = {\deriv{C}{n} - \Du \nabla^2_s \pars{\varPhi - \log C}}, 
+0 = {\deriv{C}{n} + C \deriv{\varPhi}{n}}, 
+\bV = \zeta \cdot \bnabla_\mathcal{S} \pars{\varPhi - \log C} +
 4 \log 2 \cdot \bnabla_\mathcal{S} \log C,
@@
 
-\section{Objective of this work}
+\subsection{Objective of this work}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\chapter{Numerical Scheme} \label{ch:algorithm}
-
-\section{Numerical Framework}
-
-We start by presenting the numerical framework
-that is used for the construction of the nonlinear solver.
-
-\subsection{Finite Volume Method}
-
-Finite Volume methods \cite{ferziger2002computational} 
-are used to define a discretization of the conservation equations' integral forms.
-The simulation domain is divided into a set of discrete non-overlapping control volumes.
-Each conservation equation is discretized over the control volumes,
-such that the integral form of the conservation law is satisfied using an approximation of the fluxes
-over the control volume faces.
-This method ensures that the discretization is conservative in the discrete sense.
-
-\subsection{Flux Discretization}
-
-In order to define the fluxes on the boundaries of each control volume, we employ the 
-conservative formulation of the governing equations above. 
-The flux terms are defined using finite differences and linear interpolation of the disrete 
-variables (defined at the centroid of each cell), except for the advection flux which should not be 
-discretized using linear interpolation -- due to a numerical instability 
-for large cell Peclet numbers \cite{strikwerda2004finite}.
-
-\subsection{Ghost Points}
-In order to discretize boundary condtions for $\varPhi$, $C$ and $\bV$, 
-``ghost'' points are employed. 
-The grid is extended to include points outside the domain interior,
-and the variables at the ``ghost'' points are set to satisfy 
-the discretized boundary conditions on the grid boundaries.
-Note that $P$ has no boundary conditions -- so the pressure variable is defined 
-only in the domain interior.
-
-\subsection{Newton's Method}
-Newton's method is used to solve a nonlinear system of equations of the form $\cO(\bx) = \bzero$.
-For small step $\Delta\bx$, we can linearize the operator by
-\begin{align}
-\cO(\bx + \Delta\bx) \approx \cO(\bx) + \bnabla \cO(\bx) \Delta\bx
-\end{align}
-Thus, we use the following iteration, starting from an initial solution $\bx_0$:
-\begin{align}
-\Delta\bx_n &= - \left[\bnabla \cO(\bx_n)\right]^{-1} \cdot \cO(\bx_n) \\
-\bx_{n+1} &= \bx_n + \Delta\bx_n
-\end{align}
-Then, a sparse linear system $\boldsymbol{A} \Delta \bx = \boldsymbol{b}$
-needs to be solved to yield the update $\Delta \bx$.
-When the method converges, $\bx_n \rightarrow \bx_\infty$, 
-the asymptotic convergence is in general quadratic:
-\begin{equation}
-\|\bx_{n+1} - \bx_\infty\| \le k \|\bx_{n} - \bx_\infty\|^2.
-\end{equation}
-Thus, when the initial guess is close enough to the solution, the solver
-will typically converge in very few steps.
-
-\subsection{Richardson Extrapolation}
-In order to achieve higher numerical accuracy, we employ Richardson extrapolation \cite{sidi2003practical}
-on the resulting steady-state velocity $\cU(h)$, as a scalar function of the grid spacing $h$.
-This method enables us to detect and analyze nonlinear effects for $\beta \ll 1$, where 
-a higher-order discretization is required because otherwise
-the numerical error becomes comparable to the difference between the linear analytical regime 
-and the numerical results.
-
-\section{Algorithm Description} \label{sec:algorithm}
+\section{Numerical Scheme} \label{ch:algorithm}
+
+\subsection{Algorithm Description} \label{sec:algorithm}
 The numerical solver first requires constructing a discrete 
@@
 
-\subsection{Spherical Coordinates}
+\subsubsection{Spherical Coordinates}
 Because the system is axisymmetric and the particle is a sphere, we employ
-spherical coordinates $(r,\theta,\phi)$.
-The scalar gradient and the divergence can be written as:
-\begin{align}
-\bnabla f &= \deriv{f}{r}\brhat + \frac{1}{r}\deriv{f}{\theta}\bthetahat, \\
-\bnabla \cdot \bF &= \frac{1}{r^2}\deriv{}{r}\pars{F_r r^2 } + 
-               \frac{1}{r \sin\theta}\deriv{}{\theta}\pars{F_\theta \sin\theta}.
-\end{align}
-The scalar Laplacian can be written as:
-\begin{align}
-\Laplacian f = \bnabla \cdot (\bnabla f) = 
- \frac{1}{r^2}\deriv{}{r}\pars{r^2 \deriv{f}{r}} + 
- \frac{1}{r^2 \sin\theta}\deriv{}{\theta}\pars{\sin\theta \deriv{f}{\theta}}.
-\end{align}
-The vector gradient and vector Laplacian can be written as:
-\begin{align}
-\nonumber
-\bnabla \bF &= \deriv{F_r}{r} \brhat \brhat + \deriv{F_\theta}{r} \brhat \bthetahat + 
-\frac{1}{r}\pars{\deriv{F_r}{\theta} - F_\theta} \bthetahat \brhat + 
-\frac{1}{r}\pars{\deriv{F_\theta}{\theta} + F_r} \bthetahat \bthetahat, 
-\\
-\brhat \cdot \bLaplacian \bF &=
-\Laplacian F_r - \frac{2F_r}{r^2} - 
-\frac{2}{r^2 \sin\theta} \deriv{\left(F_\theta \sin\theta \right)}{\theta}
-\\
-\nonumber
-\bthetahat \cdot \bLaplacian \bF &= 
-\Laplacian F_\theta - \frac{F_\theta}{r^2 \sin^2\theta} + 
-\frac{2}{r^2}\deriv{F_r}{\theta}.
-\end{align}
+spherical coordinates $(r,\theta,\phi)$ (as described in the appendix).
+
 Note that in the spherical coordinate system,
@@
 in a curvilinear coordinate system.
-See Appendix \ref{append:spherical} for the full derivation of the identities above.
-
-\subsection{Computational Grid}
+
+\subsubsection{Computational Grid}
 A regular grid of size $n_r \times n_\theta$ is defined, with:
 \begin{align} \label{eq:grid}
-\nonumber
-(r_i,\theta_j) &\in [1, \infty) \times [0,\pi], \\ 
-r_i &= (1+\Delta_r)^i, \\
-\nonumber
-\theta_j &= \Delta_\theta \cdot j,
+(r_i,\theta_j) \in [1, \infty) \times [0,\pi], 
+r_i = (1+\Delta_r)^i, 
+\theta_j = \Delta_\theta \cdot j,
 \end{align}
@@
 \begin{align}
-\nonumber
-\Omega_{ij} &= [r_{i-1}, r_{i}] \times [\theta_{j-1}, \theta_{j}], \\
-\bar{r}_i &= (r_{i-1} + r_{i})/2, \\
-\nonumber
-\bar{\theta}_j &= (\theta_{j-1} + \theta_{j})/2.
+\Omega_{ij} = [r_{i-1}, r_{i}] \times [\theta_{j-1}, \theta_{j}], 
+\bar{r}_i = (r_{i-1} + r_{i})/2, 
+\bar{\theta}_j = (\theta_{j-1} + \theta_{j})/2.
 \end{align}
@@
 \begin{align}
-\nonumber \varPhi^h_{[i,j]} &= \varPhi(\bar{r}_i, \bar{\theta}_j), \\
-\nonumber C^h_{[i,j]} &= C(\bar{r}_i, \bar{\theta}_j), \\
-P^h_{[i,j]} &= P(\bar{r}_i, \bar{\theta}_j), \\
-\nonumber V_r^h{}_{[i,j]} &= V_r(r_i, \bar{\theta}_j), \\
-\nonumber V_\theta^h{}_{[i,j]} &= V_\theta(\bar{r}_i, {\theta}_j).
+\varPhi^h_{[i,j]} = \varPhi(\bar{r}_i, \bar{\theta}_j), 
+C^h_{[i,j]} = C(\bar{r}_i, \bar{\theta}_j), 
+P^h_{[i,j]} = P(\bar{r}_i, \bar{\theta}_j), 
+V_r^h{}_{[i,j]} = V_r(r_i, \bar{\theta}_j), 
+V_\theta^h{}_{[i,j]} = V_\theta(\bar{r}_i, {\theta}_j).
 \end{align}
@@
     \begin{center}
-	\includegraphics[width=0.8\textwidth]{figs/grids.eps}
+	\includegraphics[width=0.5\textwidth]{figs/grids.eps}
         \caption[Computational grid]{The computational grid is defined using
@@
 \cD_r(f^h){}_{\left[i+\half,j\right]} = \frac{f^h_{\left[i+1,j\right]} - f^h_{\left[i,j\right]}}
-                       {r_{\left[i+1,j\right]} - r_{\left[i,j\right]}}, \\
+                       {r_{\left[i+1,j\right]} - r_{\left[i,j\right]}}, 
 \cD_\theta(f^h){}_{\left[i,j+\half\right]} = \frac{f^h_{\left[i,j+1\right]} - f^h_{\left[i,j\right]}}
@@
 \nonumber
-I^h_r = -\cI_r(C^h) \cdot \cD_r(\varPhi^h), \\
-\nonumber
+I^h_r = -\cI_r(C^h) \cdot \cD_r(\varPhi^h), &
 I^h_\theta = -\cI_\theta(C^h) \cdot \frac{\cD_\theta(\varPhi^h)}{r}, \\
-\nonumber
-J^h_r = -\cD_r(C^h) + \alpha V^h_r \cdot \mathcal{U}^{\bV^h}_r (C^h), \\
+J^h_r = -\cD_r(C^h) + \alpha V^h_r \cdot \mathcal{U}^{\bV^h}_r (C^h), &
 J^h_\theta = -\frac{\cD_\theta(C^h)}{r} + \alpha V^h_\theta \cdot \mathcal{U}^{\bV^h}_\theta (C^h), 
 \\ \nonumber
- \mathcal{U}^{\bV^h}_r(C^h)[i,j] = C^h\left[i-\frac{\sign(V^h_r)}{2}, j\right], 
-\\ \nonumber
+ \mathcal{U}^{\bV^h}_r(C^h)[i,j] = C^h\left[i-\frac{\sign(V^h_r)}{2}, j\right], &
  \mathcal{U}^{\bV^h}_\theta(C^h)[i,j] = C^h\left[i, j-\frac{\sign(V^h_\theta)}{2}\right]. 
@@
 \begin{equation}
-\begin{array}{rcl}
-0 &=& \cI_r(\varPhi^h + \log C^h), \\
-0 &=& \cD_r(\varPhi^h - \log C^h), \\
-V^h_r &=& 0, \\
-V^h_\theta &=& 4\log\pars{\frac{1}{2}\pars{1 + \exp\left\{\cI_\theta(\zeta^h)/2\right\}}} \cdot 
-			\cD_\theta(\zeta^h), \\
-  \zeta^h &=& - \log \gamma - \cI_r(\varPhi^h).
+\begin{array}{lll}
+0 = \cI_r(\varPhi^h + \log C^h), & 0 = \cD_r(\varPhi^h - \log C^h), \\
+V^h_r = 0, V^h_\theta = 4\log\pars{\frac{1}{2}\pars{1 + \exp\left\{\cI_\theta(\zeta^h)/2\right\}}} \cdot \cD_\theta(\zeta^h), &
+\zeta^h = - \log \gamma - \cI_r(\varPhi^h)\\.
 \end{array}
@@
 \begin{equation}
-\begin{array}{rcl}
-0 &=& \cD_r(C^h) - \Du \cdot 
-\pars{\cD_\theta \pars{\sin\theta \cdot \cD_\theta \cI_r\pars{\varPhi^h - \log C}}}/{\sin\theta}, \\
-0 &=& \cD_r(C^h) + \cI_r(C^h) \cD_r(\varPhi^h), \\
-V^h_r &=& 0, \\
-V^h_\theta &=& \cI_\theta(\zeta^h) \cdot \cD_\theta(\cI_r \varPhi^h - \log \cI_r C^h) + 
-4 \log 2 \cdot \cD_\theta(\log \cI_r C^h), \\
-  \zeta^h &=& \bar{\zeta} - \log \cI_r C.
+\begin{array}{lll}
+0 = \cD_r(C^h) - \Du \cdot 
+\pars{\cD_\theta \pars{\sin\theta \cdot \cD_\theta \cI_r\pars{\varPhi^h - \log C}}}/{\sin\theta}, &
+0 = \cD_r(C^h) + \cI_r(C^h) \cD_r(\varPhi^h), \\
+V^h_r = 0, 
+V^h_\theta = \cI_\theta(\zeta^h) \cdot \cD_\theta(\cI_r \varPhi^h - \log \cI_r C^h) + 
+4 \log 2 \cdot \cD_\theta(\log \cI_r C^h), 
+& \zeta^h = \bar{\zeta} - \log \cI_r C.
 \end{array}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Solver Design}
+\subsection{Solver Design}
+
+\subsubsection{System Equations}
+
 Let $\cO : \RR^N \rightarrow \RR^N $ be a nonlinear operator.
@@
 
-\subsection{Operator Representation}
 The system variable $\bx$ is defined as the concatenation $\bx = [\,\varPhi, C, V_r, V_\theta, P\,]$.
@@
 
-\subsection{Steady-state}
+\subsubsection{Steady-state}
 Let $\beta$ be a given nondimensional electric field.
@@
 Due to symmetry considerations, the total force $\bF$ is 
-aligned with $\ui$ and it vanishes iff $\ui \cdot \bF = 0$.
-\begin{eqnarray} \nonumber
-F_\imath = \ui \cdot \bF &=& 
-\oint_\mathcal{S} \pars{\ui \cdot \tT \cdot \bnhat} dA = 
-\int_0^\pi f_\imath(\theta) 2\pi \sin\theta d\theta ,
-\\  
-f_\imath = \ui \cdot \tT \cdot \brhat &=& \pars{-P + 2\cD_r(V_r) + 
-\frac{1}{2}\pars{\cD_r(\varPhi)}^2 - \frac{1}{2r^2}\pars{\cD_\theta(\varPhi)}^2}\cos\theta 
-\\  \nonumber
-&& -\pars{\cD_r(V_\theta) - \frac{V_\theta}{r}
-+ \frac{1}{r}\cD_r(\varPhi) \cD_{\theta}(\varPhi)}\sin\theta.
-\end{eqnarray}
+aligned with $\ui$ and it vanishes iff $f_\imath = \ui \cdot \bF = 0$.
+\begin{equation}
+f_\imath = \pars{-P + 2\cD_r(V_r) + 
+\frac{\pars{\cD_r(\varPhi)}^2}{2} - \frac{\pars{\cD_\theta(\varPhi)}^2}{2r^2}}\cos\theta 
+ -\pars{\cD_r(V_\theta) - \frac{V_\theta}{r}
++ \frac{\cD_r(\varPhi)}{r} \cD_{\theta}(\varPhi)}\sin\theta.
+\end{equation}
 The integral above is approximated by 1D numerical quadrature
@@
 
-\subsection{Continuation}
+\subsubsection{Continuation}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Solver Implementation}
+\subsection{Solver Implementation}
 
@@
 The source code of the solver is provided in \cite{source}.
-
 MATLAB direct solver is applied to solve the sparse linear system for each Newton step,
@@
 The library used for solving the linear system is UMFPACK 5.0 \cite{davis2004umfpack}
-(Unsymmetric MultiFrontal Sparse LU Factorization Package),
-as reported by MATLAB function call, \verb|spparms('spumoni', 2)|.
-
-\subsection{Operator Interface} \label{sec:operator-interface}
+(Unsymmetric MultiFrontal Sparse LU Factorization Package).
+
+\subsubsection{Operator Interface} \label{sec:operator-interface}
 The base \verb|Operator| interface is defined by 
@@
 
-\subsubsection{Linear operator}
+\paragraph{Linear operator}
 If $\cO$ is linear, it can be represented by a matrix $L$, such that:
-\begin{equation}\begin{array}{cc}
-\cO(\bx) = L \bx, &
-\bnabla\cO = L. 
-\end{array}\end{equation}
+$\cO(\bx) = L \bx$ and $\bnabla\cO = L$.
 Note that finite difference $\cD$, interpolation $\cI$ and 
@@
 
-\subsubsection{Pointwise scalar function}
+\paragraph{Pointwise scalar function}
 Let $f: \RR \rightarrow \RR$ be a differentiable 1D function, whose derivative is
@@
 represent a pointwise application of $f$:
-\begin{equation}\begin{array}{cc}
-\cF(\bx) = [f(x_1); \ldots; f(x_n)], &
-\bnabla\cF(\bx) = \diag\{f'(x_1), \ldots, f'(x_n)\}.
-\end{array}\end{equation}
+$\cF(\bx) = [f(x_1); \ldots; f(x_n)]$ and $\bnabla\cF(\bx) = \diag\{f'(x_1), \ldots, f'(x_n)\}$.
 $f$ is defined and differentiated automatically using the MATLAB symbolic toolbox.
 
-\subsubsection{Constant value}
+\paragraph{Constant value}
 A constant operator $\mathcal{C}$ is defined by the constant vector $\bc$ 
 (which does not depend on $\bx$):
-\begin{equation}\begin{array}{cc}
-\mathcal{C}(\bx) = \bc, &
-\bnabla\mathcal{C} = \bzero.
-\end{array}\end{equation}
-
-\subsubsection{Binary operators}
+$\mathcal{C}(\bx) = \bc$ and $\bnabla\mathcal{C} = \bzero$.
+
+\paragraph{Binary operators}
 Let $\cO_1$ and $\cO_2$ be two operators, so that their pointwise addition, subtraction,
-and multiplication, are defined as follows:
-\begin{align}
-(\cO_1 \pm \cO_2)(\bx) &= \cO_1(\bx) \pm \cO_2(\bx), \\
-\nonumber
-\bnabla (\cO_1 \pm \cO_2)(\bx) &= \bnabla\cO_1(\bx) \pm \bnabla\cO_2(\bx), \\
-(\cO_1 \cdot \cO_2)(\bx) &= \cO_1(\bx) \cdot \cO_2(\bx), \\
-\nonumber
-\bnabla (\cO_1 \cdot \cO_2)(\bx) &= \diag(\cO_2(\bx)) \bnabla\cO_1(\bx) 
-                                  + \diag(\cO_1(\bx)) \bnabla\cO_2(\bx).
-\end{align}
-\subsubsection{N-ary operators}
+are defined as follows:
+$(\cO_1 \pm \cO_2)(\bx) = \cO_1(\bx) \pm \cO_2(\bx)$ and
+$\bnabla (\cO_1 \pm \cO_2)(\bx) = \bnabla\cO_1(\bx) \pm \bnabla\cO_2(\bx)$.
+The point-wise multiplication of $\cO_1$ and $\cO_2$ is defined as follows: 
+$(\cO_1 \cdot \cO_2)(\bx) = \cO_1(\bx) \cdot \cO_2(\bx)$ and 
+$\bnabla (\cO_1 \cdot \cO_2)(\bx) = \diag(\cO_2(\bx)) \bnabla\cO_1(\bx)
+                                  + \diag(\cO_1(\bx)) \bnabla\cO_2(\bx)$.
+
+\paragraph{N-ary operators}
 Given $N$ operators $\{\cO_i\}_{i=1}^N$, their concatenation $\cO$ is defined as:
-\begin{align}
-\cO(\bx) &= [\cO_1(\bx); \ldots; \cO_N(\bx)], \\
-\nonumber
-(\bnabla\cO)(\bx) &= [(\bnabla\cO_1)(\bx); \ldots; (\bnabla\cO_N)(\bx)].
-\end{align}
-
-\subsection{Handling the Singularity} \label{sec:singular}
+$\cO(\bx) = [\cO_1(\bx); \ldots; \cO_N(\bx)]$ and  
+$(\bnabla\cO)(\bx) = [(\bnabla\cO_1)(\bx); \ldots; (\bnabla\cO_N)(\bx)]$.
+
+\subsubsection{Handling the Singularity} \label{sec:singular}
 The electric potential $\varPhi$ (in electrophoresis case) and the pressure $P$ (in both cases) 
@@
 For $\br = \cO(\bx)$ and $\bG = \bnabla \cO(\bx)$, the new square linear system reads:
-\begin{equation}
-\mathbb{R} \bG \mathbb{P} \cdot \delta\bx = -\mathbb{R} \br,
-\end{equation}
+$\mathbb{R} \bG \mathbb{P} \cdot \delta\bx = -\mathbb{R} \br$,
 where $\mathbb{P}$ matrix is used to remove the columns
@@
 
-\subsection{Iterative Newton solver}
-Given an initial solution $\bx_0$ and prescribed values for $\beta$ and $\cU$, 
-we apply the following algorithm until convergence ($\|\boldsymbol{r_n}\| < \eps$):
-\begin{enumerate}
-\item Update the system operator: $\verb|op| = \verb|System|(\bx_{n})$
-\item Compute the gradient: $\boldsymbol{G}_n = \verb|op.grad()|$
-\item Compute the right-hand side: $\boldsymbol{r}_n = \verb|op.res()|$
-\item Solve sparse linear system: $\mathbb{R}\boldsymbol{G}_n \mathbb{P} \Delta \bx_n = -\mathbb{R}\boldsymbol{r}_n$
-\item Update solution: $\bx_{n+1} = \bx_{n} + \mathbb{P}\Delta \bx_{n}$
-\end{enumerate}
-
-\section{Source code overview}
-In the following section we present the source code of the numerical framework and demonstrate its
-usage for solving a boundary-value problem.
-\subsection{Variable}
-We define the variable vector $\bx$ as \verb|Variable| 
-operator (Figure \ref{fig:variable.m}).
-
-\begin{figure}[htpb]
-\begin{minted}[mathescape,linenos,numbersep=6pt,frame=single,framesep=2mm]{matlab}
-classdef Variable < handle
-properties
-    value;
-end
-methods
-    function self = Variable(varargin)
-        self.value = col(varargin{:});
-    end
-    function r = res(self)
-        r = self.value(:);
-    end
-    function G = grad(self) 
-        G = speye(numel(self.value));
-    end
-    function update(self, dv)
-        self.value = self.value + dv;
-    end
-end
-\end{minted}
-\caption{Variable class source code.} \label{fig:variable.m}
-\end{figure}
-Then the initial solution for the solver is set using
-$\bx = \verb|Variable|(\varPhi, C, V_r, V_t, P)$
-from the initial conditions of the solver.
-
-\subsection{Grid}
-Most of the operators are using a \verb|Grid| object (Figure \ref{fig:grid.m}),
-enabling validation of operators compatibility and 
-convenient interpolation between grids. Note that
-each operator must define its \verb|res()| and \verb|grad()|
-functions, for residual and gradient computation, respectively.
-An \verb|Operator| interface is used (Figure \ref{fig:operator.m}) 
-to support operator overloading MATLAB syntax.
-\begin{figure}[h]
-\begin{minted}[mathescape,linenos,numbersep=6pt,frame=single,framesep=2mm]{matlab}
-% Regular structured grid class
-classdef Grid < handle
-properties
-    x, y;
-    X, Y;
-    size;    
-    numel;
-end
-methods
-    function self = Grid(x, y)
-        self.x = x(:);
-        self.y = y(:);
-        [self.X, self.Y] = ndgrid(self.x, self.y);
-        self.size = [numel(self.x), numel(self.y)];
-        self.numel = prod(self.size);
-    end
-end
-\end{minted}
-\caption{Grid class source code.} \label{fig:grid.m}
-\end{figure}
-\begin{figure}[h]
-\begin{minted}[mathescape,linenos,numbersep=6pt,frame=single,framesep=2mm]{matlab}
-classdef Operator < handle
-properties
-    grid; % a grid object for the output
-end
-methods
-    function op = Operator(grid)
-        op.grid = grid;
-    end
-    function op = plus(op1, op2)
-        op = Sum(op1, op2);
-    end
-    function op = minus(op1, op2)
-        op = Minus(op1, op2);
-    end
-    function op = uminus(op)
-        op = Product(-1, op);
-    end
-    function op = mtimes(op1, op2)
-        op = Product(op1, op2);
-    end
-    function op = log(op)
-        op = Func(op, 'log(x)');
-    end
-    function op = exp(op)
-        op = Func(op, 'exp(x)');
-    end
-    function op = sinh(op)
-        op = Func(op, 'sinh(x)');
-    end
-    function op = cosh(op)
-        op = Func(op, 'cosh(x)');
-    end
-    function op = tanh(op)
-        op = Func(op, 'tanh(x)');
-    end
-end
-\end{minted}
-\caption{Operator interface source code.} \label{fig:operator.m}
-\end{figure}
-
-Thus, various computations can be applied on simple operators, 
-creating more complex operators, such as
-\verb|op4 = op1 * exp(op2 + tanh(op3))|. 
-Since each operator can compute its residual and gradient, we
-can compute automatically the residual and gradient of \verb|op4|
-from these of \verb|op1|, \verb|op2|, \verb|op3| using the derivation
-rules described at \ref{sec:operator-interface}.
-
-\subsection{Operators}
-An operator can be created with $n$ existing operators as input.
-\verb|Const| is an operator that corresponds to $n=0$, whose 
-residual value is constant and gradient matrix is zero (see Figure \ref{fig:const.m}).
-
-\begin{figure}[h]
-\begin{minted}[mathescape,linenos,numbersep=6pt,frame=single,framesep=2mm]{matlab}
-classdef Const < Operator
-properties
-    val;
-end
-methods
-    function self = Const(grid, val)
-        self = self@Operator(grid);
-        if isa(val, 'float')
-            if numel(val) == 1
-                val = repmat(val, grid.size);
-            end
-            self.val = val;
-        else % function handle evaluated point-wise
-            if isa(val, 'char')
-                val = str2func(['@(r,t) ' val]);
-            end
-            self.val = arrayfun(val, grid.R, grid.T);
-        end
-    end
-    function r = res(self)
-        r = self.val(:);
-    end
-    function G = grad(self)
-        G = sparse(0); % [0]
-    end
-end
-\end{minted}
-\caption{Constant operator source code.} \label{fig:const.m}
-\end{figure}
-
-\subsubsection{Unary operators}
-Unary operators have one existing operator as input. 
-\verb|Func| operator implements point-wise analytic function
-application (whose derivative is computed using the symbolic differentiation toolbox) on the same grid of the input operator (Figure \ref{fig:func.m}). 
-\verb|Linear| operator is implemented
-using multiplication by a constant sparse matrix 
-\verb|L|, which is also the gradient of the operator
-(Figure \ref{fig:linear.m}).
-\verb|Deriv| and \verb|Interp| operators (implementing discrete
-differentiation and grid interpolation) derive from \verb|Linear|
-base class operator and specify \verb|L| sparse matrix accordingly.
-
-\begin{figure}[h]
-\begin{minted}[mathescape,linenos,numbersep=6pt,frame=single,framesep=2mm]{matlab}
-classdef Func < Operator
-properties
-    op; % Input operator
-    func; % y = f(x)
-    deriv; % dy/dx = f'(x)
-end
-methods
-    function self = Func(op, func)
-        grid = op.grid; % Reuse operator's grid
-        self = self@Operator(grid);
-        self.op = op;
-        if isa(func, 'char')
-        	func = sym(func); 
-        end 
-        self.func = matlabFunction(func);
-        self.deriv = matlabFunction(diff(func));
-    end
-    function r = res(self)
-        r = self.func( self.op.res() );
-    end
-    function G = grad(self)
-        r = self.op.res();
-        G = spdiag( self.deriv(r) ) * self.op.grad();
-    end
-end
-\end{minted}
-\caption{Pointwise function source code.} \label{fig:func.m}
-\end{figure}
-\begin{figure}[h]
-\begin{minted}[mathescape,linenos,numbersep=6pt,frame=single,framesep=2mm]{matlab}
-classdef Linear < Operator
-properties
-    L;
-    op;
-end
-methods
-    function self = Linear(grid, op, L)
-        self = self@Operator(grid);
-        self.op = op;
-        self.L = L;
-    end
-    function r = res(self)
-        r = self.L * self.op.res();
-    end
-    function G = grad(self)
-        G = self.L * self.op.grad();
-    end
-end
-\end{minted}
-\caption{Linear operator source code.} \label{fig:linear.m}
-\end{figure}
-
-\subsubsection{Binary operators}
-Binary operators such as addition, subtraction and point-wise 
-multiplication are implemented as operators whose
-output grid is the same as the grid of their inputs. 
-The implementation is used by operator overloading in 
-the base class \verb|Operator|.
-
-\subsubsection{$N$-ary operators}
-All equations and boundary condition operators are defined
-as operators \verb|{op1, op2, ... opN}|. 
-Then, they are combined using the $N$-ary operator 
-\verb|op = Join(op1, op2, ... opN)|, creating
-the system operator \verb|op| (Figure \ref{fig:join.m}).
-
-\begin{figure}[htpb]
-\begin{minted}[mathescape,linenos,numbersep=6pt,frame=single,framesep=2mm]{matlab}
-classdef Join < handle
-properties
-    ops;
-end
-methods
-    function self = Join(operators)
-        self.ops = operators;
-        for k = 1:numel(self.ops)
-        	op = self.ops{k}; 
-        end
-    end
-    function r = res(self)
-        r = cell(numel(self.ops), 1);
-        for k = 1:numel(self.ops)
-            r{k} = self.ops{k}.res();
-        end
-        r = cat(1, r{:});
-    end
-    function G = grad(self) 
-        G = cell(numel(self.ops), 1);
-        for k = 1:numel(self.ops)
-            G{k} = self.ops{k}.grad();
-        end
-        G = cat(1, G{:});
-    end
-end
-\end{minted}
-\caption{Join operator source code.} \label{fig:join.m}
-\end{figure}
-
-\subsection{Sample source code}
-The following example shows how to define the following boundary-value problem:
-\begin{align}
-\Laplacian F(x,y) &= 1 & (x,y) &\in [0,1]^2 \\
-F(0, y) = F(1, y) &= 0 & y &\in [0,1] \\
-\deriv{F}{y}(x, 0) = \deriv{F}{y}(x, 1) &= 0 & x &\in [0,1]
-\end{align}
-and solve it using one Newton method step.
-The source code is presented at Figure \ref{fig:sample.m}.
-\begin{figure}[htpb]
-\begin{minted}[mathescape,linenos,numbersep=6pt,frame=single,framesep=2mm]{matlab}
-x = linspace(0, 1); 
-y = linspace(0, 1);
-g = Grid(x, y); % Grid definition
-x_ = (x(1:end-1) + x(2:end)) * 0.5;
-y_ = (y(1:end-1) + y(2:end)) * 0.5;
-xi = x(2:end-1);
-yi = y(2:end-1);
-v = Variable(zeros(g.size)); 
-F = Linear(g, v, speye(g.numel)); % Variable Definition
-Fx = Deriv(Grid(x_, y), F, 1);
-Fy = Deriv(Grid(x, y_), F, 2);
-Fxx = Deriv(Grid(xi, yi), Fx, 1);
-Fyy = Deriv(Grid(xi, yi), Fy, 2);
-eq = {(Fxx + Fyy) - Const(1)};               % Laplacian(F) = 1
-bnd = {Interp(Grid(0.0, y(2:end-1)), F); ... % F(0, y) = 0
-	   Interp(Grid(1.0, y(2:end-1)), F); ... % F(1, y) = 0
-       Interp(Grid(x, 0.0), Fy); ...         % dF/dy(x, 0) = 0
-       Interp(Grid(x, 1.0), Fy)}		     % dF/dy(x, 1) = 0       
-op = Join([eq; bnd]); % System operator
-r = op.res()
-G = op.grad()
-v.update(-(G\r)) % Solve by Newton iteration
-\end{minted}
-\caption{Sample problem source code.} \label{fig:sample.m}
-\end{figure}
-
-\chapter{Results and Discussion} \label{ch:results}
+\section{Results and Discussion} \label{ch:results}
+
+The numerical solver is applied to the nonlinear problem of an ion-exchanger migration 
+driven by an electric field \cite{yariv2010migration}
+and the electrophoresis of highly charged surface inert particle 
+\cite{schnitzer2012surface}. 
+The solver is applied to a series of values of the electric field $\beta$, ranging 
+from $\beta \ll 1$ to $\beta \sim 1$.
+For each $\beta$ value, the Newton solver is initialized with the linear solution and is iterated $K$ times.
+Secant method iteration is applied $M$ times to find the steady-state velocity 
+by finding $\cU$ such that $F_\imath(\cU, \beta) = 0$, thus computing 
+the steady-state velocity $\cU(\beta)$. 
+The resulting $\cU(\beta)$ is plotted on a log-log scale, so that the asymptotic behaviour
+of the solution may be examined for a wide range of $\beta$ values.
+
+In order to validate the numerical solver, we employ 
+the results of the asymptotic analysis of the nonlinear 
+system (which are presented in \ref{sec:asymp}). 
+The numerical results are compared 
+to the asymptotic solutions, and a good correspondence is observed.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Ion-exchanger results}
+For $\beta \ll 1$, the linear regime \cite{yariv2010asymptotic} is dominant.
+However, when $\gamma \approx 1$, the cubic regime, where $\cU = O(\beta^3)$, 
+dominates the linear one, even for weak electric fields. 
+This phenomenon is confirmed both by the numerical
+results and by asymptotic expansion of the nonlinear system (for $\alpha=0$).
+The switch from the linear regime to the cubic regime occurs at 
+an electric field value of $\beta = O(\sqrt{|\gamma - 1|})$.
+The numerical results $\cU^h$, 
+as well as the analytical ones \eqref{eq:cubic}, are given in Figure \ref{fig:IonExCubic}.
+The numerical solver uses $N_r \times N_\theta = (400 \times 50)$, 
+$R_{\max} = 10^7$ ($\Delta_r \approx 0.041$),
+$K = 3$, $M = 5$ and $\beta = 10^{t}$ for $t = -2:0.1:0.5$.
+
+The linear solution for $\gamma \approx 1$, 
+yields a sign change of the zeta potential $\zeta = \log (C/\gamma)$, when
+$|\log\gamma| \approx 3\beta / 4$. This results in a sign change in the slip velocity,
+which can be approximated for small $|\zeta| \ll 1$ as $V_\theta \approx \zeta \cdot \bnabla_S \varPhi$.
+This sign change creates a vortex at the downstream end of the ion-exchanger, 
+as demonstrated by the numerical solution and the asymptotic analysis results 
+in Figures \ref{fig:Vortex1} and \ref{fig:Vortex2}.
+Note that there is a good correspondence between the numerical
+results and the analytical solution for $\beta < 1$, validating
+the vortex formation.
+
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=0.33\textwidth]{figs/Cubic/ionex_cubic1.eps}
+    \includegraphics[width=0.33\textwidth]{figs/Cubic/ionex_cubic2.eps}
+        \caption[Ion exchanger steady-state velocity]{
+        Steady-state velocity $\cU$ as a function of the 
+        electric field magnitude $\beta$, for $\gamma < 1$ (left) and $\gamma > 1$ (right). 
+        The analytic cubic solution \eqref{eq:cubic} is represented by curves
+        (solid for $\cU > 0$, dashed for $\cU < 0$), 
+        and the numerical results are represented by markers 
+        (circles for $\cU > 0$, squares for $\cU < 0$). Note that linear and
+        cubic regimes match well the numerical results, including the critical $\beta$ 
+        behaviour \eqref{eq:crit_beta}. 
+        }
+	    \label{fig:IonExCubic}
+    \end{center}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+	\includegraphics[width=0.33\textwidth]{figs/Cubic/Stream/N1.eps}
+	\includegraphics[width=0.33\textwidth]{figs/Cubic/Stream/N2.eps}
+	\includegraphics[width=0.33\textwidth]{figs/Cubic/Stream/N5.eps}
+	\includegraphics[width=0.33\textwidth]{figs/Cubic/Stream/N10.eps}
+        \caption[Ion exchanger streamlines -- numerical results]{
+        Streamlines of the flow for various electric field $\beta$ values: 
+        numerical results for $\gamma = 0.9$.  
+        The steady-state velocity $\cU$ is positive, so the
+        ion-exchanger drifts to the right. }
+    \label{fig:Vortex1}
+    \end{center}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+	\includegraphics[width=0.33\textwidth]{figs/Cubic/Stream/A1.eps}
+	\includegraphics[width=0.33\textwidth]{figs/Cubic/Stream/A2.eps}
+	\includegraphics[width=0.33\textwidth]{figs/Cubic/Stream/A5.eps}
+	\includegraphics[width=0.33\textwidth]{figs/Cubic/Stream/A10.eps}
+        \caption[Ion exchanger streamlines -- analytical results]{
+        Streamlines of the flow for various electric field $\beta$ values: 
+        analytical approximation for $\gamma = 0.9$ (see Section \ref{sec:asymp}).
+        The steady-state velocity $\cU$ is positive, so the
+        ion-exchanger drifts to the right.}
+    \label{fig:Vortex2}
+    \end{center}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Electrophoresis results}
+For $\beta \ll 1$, the linear regime \cite{schnitzer2012surface} is dominant.
+In order to verify the solver, the numerical steady-state velocity is compared to the
+analytical solution \cite{schnitzer2012cubic}, derived by Schnitzer and Yariv. 
+Since the cubic correction is much smaller than
+the linear solution for $\beta \ll 1$, the difference between numerical results and
+the linear solution is compared to the cubic correction term.
+
+Because the leading order of the solution $\cU(\beta)$ is linear for $\beta \ll 1$, 
+the numerical discretization error is $O(\beta)$ as well.
+In order to reduce the discretization error of the numerical solution \eqref{eq:disc_zero_force}
+and after verifying that the discretization error converges as $O(h^2)$ (Figure \ref{fig:quadratic}),
+we employ Richardson extrapolation to $\cU^h$ and $\cU^{2h}$ using $\hat\cU = \frac{4}{3} \cU^h - \frac{1}{3} \cU^{2h}$.
+
+The results of the extrapolation $\hat\cU$ 
+and the analytical results 
+are given at Figures \ref{fig:Electrophoresis1} and \ref{fig:Electrophoresis2}.
+The numerical solver uses $R_{\max} = 10^2$,
+$K = 3$, $M = 5$ and $\beta = 0.1 \cdot 2^{t}$ for $t = -2:0.5:5$.
+The solver is applied to 2 grids of $N_r \times N_\theta = (128 \times 128)$ as the coarse grid 
+(with $\Delta_r \approx 0.037$), and $N_r \times N_\theta = (256 \times 256)$ as the fine grid
+(with $\Delta_r \approx 0.018$), in order to use Richardson extrapolation for $\hat\cU$.
+
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=.45\textwidth]{figs/quadratic_order.eps}
+        \caption[Quadratic convergence of steady-state velocity]{
+        The discretization error between the numerical and analytical solutions for 
+        $\alpha = 0$, $\Du = 0.5$, $\bar\zeta = 6$ and $R_{max} = 100$. The markers represent
+        the discretization errors for various grid sizes, and the dotted lines correspond to linear
+        functions of $\beta$, scaled by $4^n$. 
+        The graph shows that, as the number of grid points in each dimension increases by a factor of 2, 
+        the discretization error decreases by a factor of 4.
+        }
+	    \label{fig:quadratic}
+    \end{center}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=0.33\textwidth]{figs/Electrophoresis/numerical_vs_analytical_alpha=0.0_Du=0.5_zeta=6.0_Rmax=100.eps}
+    \includegraphics[width=0.33\textwidth]{figs/Electrophoresis/departure_from_linear_alpha=0.0_Du=0.5_zeta=6.0_Rmax=100.eps}
+        \caption[Highly-charged surface particle steady-state velocity]{
+        Steady-state velocity $\cU$ as a function of the 
+        electric field magnitude $\beta$, for highly-charged surface particle
+        electrophoresis (with $\alpha = 0, \text{Du} = 0.5, \bar\zeta = 6$).
+        The analytic solution velocity is represented by solid lines, 
+        and the numerical results are represented by markers.
+        The left figure shows the full numerical solution 
+        compared to the analytical one \eqref{eq:cubic}, and
+        the right figure compares the analytic cubic correction \cite{schnitzer2012cubic} 
+        to the difference between the numerical results and the linear regime.}
+	    \label{fig:Electrophoresis1}
+    \end{center}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=0.33\textwidth]{figs/Electrophoresis/numerical_vs_analytical_alpha=0.5_Du=1.0_zeta=10.0_Rmax=100.eps}
+    \includegraphics[width=0.33\textwidth]{figs/Electrophoresis/departure_from_linear_alpha=0.5_Du=1.0_zeta=10.0_Rmax=100.eps}
+        \caption[Highly-charged surface particle steady-state velocity]{
+        Steady-state velocity $\cU$ as a function of the 
+        electric field magnitude $\beta$, for highly-charged surface particle
+        electrophoresis (with $\alpha = 0.5, \text{Du} = 1, \bar\zeta = 10$).
+        The analytic solution velocity is represented by solid lines, 
+        and the numerical results are represented by markers.
+        The left figure shows the full numerical solution 
+        compared to the analytical one \eqref{eq:cubic}, and
+        the right figure compares the analytic cubic correction \cite{schnitzer2012cubic} 
+        to the difference between the numerical results and the linear regime.
+        When $\beta$ is large, the analytical cubic solution loses its validity 
+        because higher-order terms become significant.}
+	    \label{fig:Electrophoresis2}
+    \end{center}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Electrophoresis for large $\beta$ }
+When the electric field is large, nonlinear effects dominate the solution.
+In order to investigate the solution for strong electric fields, 
+we have run the solver on the TAMNUN HPC cluster \cite{tamnun}.
+Large grid sizes are used to verify that the numerical solution converges when the grid becomes finer and that no numerical artifacts are present in the solution.
+Moreover, several $R_{max} \in \{10, 30, 100\}$ values are used, to make sure it has no major impact on the solution.
+The results are shown in the following figures. 
+The steady-state velocity results are shown for several grid resolutions and several $R_{max}$ values in Figure \ref{fig:LargeBetaV_grids}, and the differences between the numerical results for
+steady-state velocity and the linear regime are shown in Figure \ref{fig:LargeBetaV_DeltaFromLinear_grids}.
+The estimated rate of convergence is shown in Figure \ref{fig:LargeBetaRatio}.
+
+The numerical solver converges well for $\beta < 5$ and the resulting steady-state velocity 
+for moderate $\beta$ values is very close to being an affine function of $\beta$.
+When $\beta$ becomes large, the salt concentration $C$ near the front of the particle 
+(at $\theta \approx 0$) approaches zero, while creating a wake behind the particle 
+(at $\theta \approx \pi$) as shown in Figure \ref{fig:LargeBeta_C}. 
+This results in high gradients in $\log C$ near the front of the particle  and, therefore, a strong electric field $\bE$ forms near the particle surface (Figure \ref{fig:LargeBeta_Phi}) due to effective boundary conditions in (\ref{eq:ephor_bnd}).
+From Figs.
+\ref{fig:LargeBetaV_grids}-\ref{fig:LargeBetaV_DeltaFromLinear_grids} we conclude that even our most accurate numerical solution is valid only up to $\beta = 5$ approximately, and therefore we only further examine solutions in this range.
+
+The streamline pattern does not change drastically for different electric field magnitudes. 
+The resulting fluid flow is nearly proportional to that of the Stokes creeping flow, 
+as shown in Figure \ref{fig:LargeBeta_Psi} and \ref{fig:LargeBeta_PsiMinusUniformFlow}. 
+The difference between $\Psi(r, \theta)$ and $\Psi(r, \pi-\theta)$ is shown in Figure \ref{fig:LargeBeta_PsiAsymm}, demonstrating that the flow is almost symmetric (with relative
+difference up to approximately $0.5\%$) for $\beta < 5$.
+
+The numerical results show that a boundary layer starts to form near the front 
+of the particle for strong electric fields (see Figures \ref{fig:LargeBeta_BoundaryLayer_E}
+and \ref{fig:LargeBeta_BoundaryLayer_C}).
+The width of the boundary layer with respect to the electric field scales, to a good approximation, as: $\bar\rho(\beta) \approx 0.2 e^{-0.5 \beta}$.
+This causes numerical problems for the current solver at large $\beta$, due to insufficient
+grid resolution at the boundary layer of $C$ and $\bE$.
+
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=.3\textwidth]{figs/LargeBetaV_[128_256_512]_Rmax=10.eps}
+    \includegraphics[width=.3\textwidth]{figs/LargeBetaV_[512x512]_Rmax=10_30_100.eps}
+        \caption[Large $\beta$ results for $\cU$]
+{Large $\beta$ results for $\cU(\beta)$ ($\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$). 
+The left figure shows the numerical results of $\cU(\beta)$ for $R_{max} = 10$ and the following grid sizes: $128 \times 128$, $256 \times 256$, $512 \times 512$. 
+The right figure shows the numerical results of $\cU(\beta)$ for
+$512 \times 512$ grid for $R_{max} = 100, 30, 10$. For small values of $\beta$, the linear
+regime of $\cU(\beta)$ is dominant. 
+For moderate $\beta$ values, the steady state velocity is very close to an affine function of $\beta$.
+However, for larger values of $\beta$, the numerical solution
+deviates significantly from the linear regime, due to convergence problems at $\beta > 6$, 
+and for $\beta \sim 7$, the solver fails to converge. The numerical convergence 
+depends on the grid resolution near the particle surface -- 
+as it becomes finer (when $N_r$ increases or $R_{max}$ decreases), the solver convergence improves.}
+	    \label{fig:LargeBetaV_grids}	    
+    \end{center}
+\end{figure}
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=.3\textwidth]{figs/LargeBetaV_DeltaFromLinear[128_256_512]_Rmax=10.eps}
+    \includegraphics[width=.3\textwidth]{figs/LargeBetaV_DeltaFromLinear[512x512]_Rmax=10_30_100.eps}
+        \caption[Large $\beta$ results for $\cU$ -- difference from linear regime]
+{Large $\beta$ results for $\cU(\beta) - \beta\cU_1$ ($\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$ and $\cU_1 \approx 4.258$ is the linear regime coefficient). 
+The left figure shows the numerical results of $\cU(\beta)$ for $R_{max} = 10$ and the following grid sizes: $128 \times 128$, $256 \times 256$, $512 \times 512$. 
+The right figure shows the numerical results of $\cU(\beta)$ for
+$512 \times 512$ grid for $R_{max} = 100, 30, 10$.
+It is seen that the difference is indeed nearly an affine function of $\beta$ in the large-$\beta$ regime, so long as the numerical solution remains sufficiently accurate.}
+	    \label{fig:LargeBetaV_DeltaFromLinear_grids}	    
+    \end{center}
+\end{figure}
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=.33\textwidth]{figs/LargeBetaRatio.eps}
+        \caption[Rate of convergence estimation for $\cU$ at large $\beta$]
+        {Rate of convergence estimation for $\cU$ at large $\beta$  
+        ($\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$), 
+        based on the numerical results of $\cU(\beta)$, for the grid sizes of 
+        $128 \times 128$, $256 \times 256$, $512 \times 512$. 
+        The rate of convergence $r(\beta)$ is estimated by 
+        $r(\beta) \triangleq \left(\cU^{4h}(\beta) - \cU^{2h}(\beta)\right)/\left(\cU^{2h}(\beta) - \cU^{h}(\beta)\right)$.
+        For small $\beta$, $r(\beta) \rightarrow 4$, showing 
+        quadratic convergence for the linear regime. 
+        For moderate $\beta$, the convergence rate slows down, 
+        and it deteriorates for large $\beta$ values.
+        }
+	    \label{fig:LargeBetaRatio}
+    \end{center}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=0.3\textwidth]{figs/LargeBeta/sol_beta=1.000e-01_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
+    \includegraphics[width=0.3\textwidth]{figs/LargeBeta/sol_beta=8.000e-01_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
+    \includegraphics[width=0.3\textwidth]{figs/LargeBeta/sol_beta=5.000e+00_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
+        \caption[Electrophoresis results for $C$]
+        {Electrophoresis results for $C$: grid size $512 \times 512$, 
+        $R_{max} = 10$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.
+
+        For weak field (left), 
+        the linear regime dominates the solution for 
+        $C_\beta(r, \theta) \approx 1 - \beta \frac{\cos\theta}{2r^2}$.
+        For moderate $\beta$ values (middle), the salt concentration starts
+        to form a wake behind the particle ($\theta \approx \pi$).
+        For large values of $\beta$ (right), there is a significant drop in
+        salt concentration at the front of the particle -- 
+        $C$ approaches zero at $\theta \approx 0$, such that 
+        $\deriv{C}{r}$ becomes large 
+        (since the change in $C$ happens on a small length scale).
+        Due to the boundary conditions of the electrophoresis problem
+        (given by (\ref{eq:ephor_bnd})), the electric field radial
+        component given by 
+        $E_r = -\deriv{\varPhi}{r} = -\frac{1}{C}\deriv{C}{r}$, 
+        becomes singular where $C \rightarrow 0$.
+        }
+	    \label{fig:LargeBeta_C}	    
+    \end{center}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=0.3\textwidth]{figs/LargeBeta/sol_beta=1.000e-01_[129x129]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
+    \includegraphics[width=0.3\textwidth]{figs/LargeBeta/sol_beta=8.000e-01_[129x129]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
+    \includegraphics[width=0.3\textwidth]{figs/LargeBeta/sol_beta=5.000e+00_[129x129]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
+        \caption[Electrophoresis results for $\varPhi$]
+        {Electrophoresis results for $\varPhi$:
+        grid size $512 \times 512$, $R_{max} = 10$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.
+
+        The electric potential and the electric field results are multiplied by $\beta^{-1}$,
+	    so the linear regime appears unchanged for different values of $\beta$.
+        For weak field (left), the linear regime dominates the solution for 
+        $\varPhi_\beta(r, \theta) \approx -\beta {r \cos\theta}$,
+        hence the electric field is constant for weak electric fields:
+        $\bE \approx \beta \ui$.
+        For moderate values of $\beta$ (middle),
+        the symmetry breaks and the electric field becomes stronger 
+        near the front of the particle than at the back.
+	    For large values of $\beta$ (right), 
+	    the electric field radial component $E_r = -\deriv{\varPhi}{r}$
+	    at the particle front becomes much larger than the electric field at the particle back.
+        }
+	    \label{fig:LargeBeta_Phi}
+    \end{center}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=.33\textwidth]{figs/LargeBeta/sol_beta=1.000e-01_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_[1]_Psi.eps}
+    \includegraphics[width=.33\textwidth]{figs/LargeBeta/sol_beta=8.000e-01_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_[1]_Psi.eps}
+    \includegraphics[width=.33\textwidth]{figs/LargeBeta/sol_beta=5.000e+00_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_[1]_Psi.eps}
+    \includegraphics[width=.33\textwidth]{figs/LinearStokes_Psi.eps}
+        \caption[Streamfunction results]
+        {$\beta = 0.1, 0.8, 5.0$ and Stokes streamlines results: grid size $512 \times 512$, 
+        $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.
+        The numerical results for $\Psi$ are scaled by $\beta^{-1}$, so the linear regime
+        will appear the same for different $\beta$ values.
+        Note that the numerical results show a
+        flow pattern very similar to that of the analytical Stokes flow.}
+	    \label{fig:LargeBeta_Psi}	    
+    \end{center}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=.33\textwidth]{figs/PsiMinusUniformFlow/sol_beta=1.000e-01_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_[1]_Psi.eps}
+    \includegraphics[width=.33\textwidth]{figs/PsiMinusUniformFlow/sol_beta=8.000e-01_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_[1]_Psi.eps}
+    \includegraphics[width=.33\textwidth]{figs/PsiMinusUniformFlow/sol_beta=5.000e+00_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_[1]_Psi.eps}
+    \includegraphics[width=.33\textwidth]{figs/PsiMinusUniformFlow/LinearStokes_Psi-uniformflow.eps}
+        \caption[Streamfunction results]
+        {$\beta = 0.1, 0.8, 5.0$ and Stokes streamlines results after subtraction of the uniform
+        flow streamfunction ($\frac{\cU}{2}r^2 \sin^2\theta$): grid size $512 \times 512$, 
+        $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.
+        The numerical results for $\Psi$ are scaled by $\beta^{-1}$, so the linear regime
+        will appear the same for different $\beta$ values.
+        Even for the largest beta we could compute, the velocity remains fairly symmetric and 		
+        ``uneventful'' also in the framework of the ``laboratory'' rather than that of the particle.}
+	    \label{fig:LargeBeta_PsiMinusUniformFlow}	    
+    \end{center}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=0.33\textwidth]{figs/streamlines_asymmetry.eps}
+        \caption[Streamfunction asymmetry]
+        {Streamline results: grid size $512 \times 512$, 
+        $R_{max} = 10$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.
+        The relative streamline asymmetry is computed by 
+        $\|\Psi(r, \theta) - \Psi(r, \pi-\theta)\|/\|\Psi(r, \theta)\|$
+        as a function of $\beta$. The results show that the streamline pattern is almost 
+        symmetric, even for moderately large $\beta$ values.}
+	    \label{fig:LargeBeta_PsiAsymm}	    
+    \end{center}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=.33\textwidth]{figs/BoundaryLayerWidth_E1.eps}
+    \includegraphics[width=.33\textwidth]{figs/BoundaryLayerWidth_E2.eps}
+    \includegraphics[width=.33\textwidth]{figs/BoundaryLayerWidth_E3.eps}
+    \includegraphics[width=.33\textwidth]{figs/BoundaryLayerWidth_E4.eps}
+        \caption[Electric field boundary layer]
+        {Electric field boundary layer formation: grid size $512 \times 512$, 
+        $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$. The upper left
+        graph shows normalized electric field radial component $E_r$ near the particle front
+        ($\theta = 0$). The numerical results for $e(\rho) = E_r(r=1+\rho, \theta=0)$
+        are normalized by $\hat{e}(\rho) = \left(e(\rho) - \beta\right)/\left(e(0) - \beta\right)$,
+        where $e(\rho = \infty) = \beta$.
+        The normalized electric field satisfies $\hat{e}(\rho) \in [0, 1]$ and is shown as function
+        of $\rho = r - 1$ at the upper left graph and as function of $\rho e^{0.5 \beta}$ at
+        the upper right graph.
+        In order to estimate the width of the boundary layer, for each $\beta$, we compute the value 
+        of $\bar\rho(\beta) = \min_\rho \{ \rho : \hat{e}(\rho) < 0.5\}$. Each such $\bar\rho(\beta)$
+        is plotted at the left graph as a solid dot on the corresponding line.
+        In addition, $\bar\rho(\beta)$ is plotted as a function of $\beta$ using logarithmic 
+        $y$ axis at the lower left graph to show that $\bar\rho(\beta) \approx 0.2 e^{-0.5 \beta}$.
+        Moreover, $E_r(\beta; r=1, \theta=0) / \beta$ grows exponentially as a function of $\beta$,
+        as shown at the lower right graph.
+        Thus, a boundary layer is indeed forming near the front of the particle.
+        }
+	    \label{fig:LargeBeta_BoundaryLayer_E}	    
+    \end{center}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=.33\textwidth]{figs/boundary_layer_C1.eps}
+    \includegraphics[width=.33\textwidth]{figs/boundary_layer_C2.eps}
+        \caption[Ionic concentration boundary layer]
+        {Ionic concentration boundary layer formation: grid size $512 \times 512$, 
+        $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$. The left
+        graph shows the ionic concentration $C$ near the particle front
+        ($\theta = 0$). 
+        In addition, $C_\beta(r=1, \theta=0)$ is plotted as a function of $\beta$ using logarithmic 
+        $y$ axis at the right graph to show that 
+        $C_\beta(r=1, \theta=0) \approx 0.94 e^{-0.45 \beta}$.
+        The ionic concentration becomes very close to zero for $\beta \approx 7$ at $r = 1$, 
+        creating a singularity near the particle front.
+        }
+	    \label{fig:LargeBeta_BoundaryLayer_C}	    
+    \end{center}
+\end{figure}
+
+\begin{figure}
+    \begin{center}
+    \includegraphics[width=.33\textwidth]{figs/C_Er_product.eps}
+        \caption{The product of $C(r=1, \theta=0) E_r(r=1, \theta=0) / \beta$ as
+        a function of $\beta$.}
+	    \label{fig:C_Er_product}	    
+    \end{center}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+\section{Discussion} \label{sec:discussion}
+A numerical framework for a
+nonlinear electrokinetic transport system is described.
+The framework is used to construct numerical solvers 
+for two electrokinetic problems: the migration of ion-exchangers
+and surface-charged inert particle electrophoresis.
+The numerical results for weak electric field 
+exhibit a good correspondence to the asymptotic models as shown above.
+Two interesting phenomena (cubic regime and downstream vortex) were predicted for the ion-exchanger
+using the numerical results, and were verified using an asymptotic expansion of the nonlinear system.
+The electrophoresis problem was solved on a high-resolution grid to validate the asymptotic 
+cubic correction of the steady-state velocity, as well as to provide insights into
+the solution behavior for moderately strong electric fields.
+For strong electric field, the nonlinear effects become dominant and
+a boundary-layer structure begins to form.
+Due to diminishing ion concentration $C$ at the front of the particle,
+a boundary layer of thickness approximately $0.2 e^{-0.5\beta}$ 
+is formed with respect to the electric field $\bE$ at the front of the particle.
+The value of $E_r / \beta$ at ($r = 1$, $\theta = 0$) is given approximately by 
+$e^{\beta/2}$, while the value of $C(r = 1, \theta = 0)$ is given approximately 
+by $e^{-\beta/2}$, and their product remains close to 1 for all $\beta$ that we could compute
+(as shown in Figure \ref{fig:C_Er_product}).
+However, the velocity of the particle remains nearly linear with $\beta$
+and the velocity field is very close to being symmetric.
+
+\section{Future Work}
+Future work may include using the numerical results described in this work to develop
+an analytical solution for the strong field regime of the electrophoresis problem, which is 
+of interest. The solver may be used to investigate how the solution
+(and the evolving boundary layer, in particular) depends on the problem parameters.
+Optimizing the direct sparse linear solver can be done by
+using the ordering data from previous calls,
+or replacing the full Newton step by an iterative linear solver
+(e.g., using preconditioned Krylov subspace methods \cite{saad2003book} or
+Multigrid), allowing finer grids to be used.
+In order to achieve high numerical accuracy, the grid discretization should be made finer
+near the particle surface (at $r = 1$), while $R_{max}$ can be made smaller. Moreover, a different discretization scheme may be used for
+the $r$ coordinate, to have higher grid resolution near the particles.
+In addition, the continuation of the solution between different $\beta$ values
+should advance in finer steps, to ensure Newton method convergence.
+The discretization of boundary conditions far away from the particle may be improved
+by including the linear correction from the asymptotic solution, or reformulation of
+far-away boundary condition according to the asymptotic behavior of the analytic solution
+far away from the particle.
+Moreover, the framework may be used for automatic construction of Newton solvers 
+for other nonlinear PDE systems, for example, for particles with different surface 
+properties, or different particle shape.
+
+\appendix
 
@@
 
-\section{Numerical Results} \label{sec:results}
-The numerical solver is applied to the nonlinear problem of an ion-exchanger migration 
-driven by an electric field \cite{yariv2010migration}
-and the electrophoresis of highly charged surface inert particle 
-\cite{schnitzer2012surface}. 
-The solver is applied to a series of values of the electric field $\beta$, ranging 
-from $\beta \ll 1$ to $\beta \sim 1$.
-For each $\beta$ value, the Newton solver is initialized with the linear solution and is iterated $K$ times.
-Secant method iteration is applied $M$ times to find the steady-state velocity 
-by finding $\cU$ such that $F_\imath(\cU, \beta) = 0$, thus computing 
-the steady-state velocity $\cU(\beta)$. 
-The resulting $\cU(\beta)$ is plotted on a log-log scale, so that the asymptotic behaviour
-of the solution may be examined for a wide range of $\beta$ values.
-
-In order to validate the numerical solver, we employ 
-the results of the asymptotic analysis of the nonlinear 
-system. 
-The numerical results are compared 
-to the asymptotic solutions, and a good correspondence is observed.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Ion-exchanger results}
-For $\beta \ll 1$, the linear regime \cite{yariv2010asymptotic} is dominant.
-However, when $\gamma \approx 1$, the cubic regime, where $\cU = O(\beta^3)$, 
-dominates the linear one, even for weak electric fields. 
-This phenomenon is confirmed both by the numerical
-results and by asymptotic expansion of the nonlinear system (for $\alpha=0$).
-The switch from the linear regime to the cubic regime occurs at 
-an electric field value of $\beta = O(\sqrt{|\gamma - 1|})$.
-The numerical results $\cU^h$, 
-as well as the analytical ones \eqref{eq:cubic}, are given in Figure \ref{fig:IonExCubic}.
-The numerical solver uses $N_r \times N_\theta = (400 \times 50)$, 
-$R_{\max} = 10^7$ ($\Delta_r \approx 0.041$),
-$K = 3$, $M = 5$ and $\beta = 10^{t}$ for $t = -2:0.1:0.5$.
-
-The linear solution for $\gamma \approx 1$, 
-yields a sign change of the zeta potential $\zeta = \log (C/\gamma)$, when
-$|\log\gamma| \approx 3\beta / 4$. This results in a sign change in the slip velocity,
-which can be approximated for small $|\zeta| \ll 1$ as $V_\theta \approx \zeta \cdot \bnabla_S \varPhi$.
-This sign change creates a vortex at the downstream end of the ion-exchanger, 
-as demonstrated by the numerical solution and the asymptotic analysis results 
-in Figures \ref{fig:Vortex1} and \ref{fig:Vortex2}.
-Note that there is a good correspondence between the numerical
-results and the analytical solution for $\beta < 1$, validating
-the vortex formation.
-
-\begin{figure}
-    \begin{center}
-    \includegraphics[width=0.7\textwidth]{figs/Cubic/ionex_cubic1.eps}
-    \includegraphics[width=0.7\textwidth]{figs/Cubic/ionex_cubic2.eps}
-        \caption[Ion exchanger steady-state velocity]{
-        Steady-state velocity $\cU$ as a function of the 
-        electric field magnitude $\beta$, for $\gamma < 1$ (top) and $\gamma > 1$ (bottom). 
-        The analytic cubic solution \eqref{eq:cubic} is represented by curves
-        (solid for $\cU > 0$, dashed for $\cU < 0$), 
-        and the numerical results are represented by markers 
-        (circles for $\cU > 0$, squares for $\cU < 0$). Note that linear and
-        cubic regimes match well the numerical results, including the critical $\beta$ 
-        behaviour \eqref{eq:crit_beta}. 
-        }
-	    \label{fig:IonExCubic}
-    \end{center}
-\end{figure}
-
-\begin{figure}
-    \begin{center}
-	\includegraphics[width=0.7\textwidth]{figs/Cubic/Stream/N1.eps}
-	\includegraphics[width=0.7\textwidth]{figs/Cubic/Stream/N2.eps}
-	\includegraphics[width=0.7\textwidth]{figs/Cubic/Stream/N5.eps}
-	\includegraphics[width=0.7\textwidth]{figs/Cubic/Stream/N10.eps}
-        \caption[Ion exchanger streamlines -- numerical results]{
-        Streamlines of the flow for various electric field $\beta$ values: 
-        numerical results for $\gamma = 0.9$.  
-        The steady-state velocity $\cU$ is positive, so the
-        ion-exchanger drifts to the right. }
-    \label{fig:Vortex1}
-    \end{center}
-\end{figure}
-
-\begin{figure}
-    \begin{center}
-	\includegraphics[width=0.7\textwidth]{figs/Cubic/Stream/A1.eps}
-	\includegraphics[width=0.7\textwidth]{figs/Cubic/Stream/A2.eps}
-	\includegraphics[width=0.7\textwidth]{figs/Cubic/Stream/A5.eps}
-	\includegraphics[width=0.7\textwidth]{figs/Cubic/Stream/A10.eps}
-        \caption[Ion exchanger streamlines -- analytical results]{
-        Streamlines of the flow for various electric field $\beta$ values: 
-        analytical approximation for $\gamma = 0.9$ (see Section \ref{sec:asymp}).
-        The steady-state velocity $\cU$ is positive, so the
-        ion-exchanger drifts to the right.}
-    \label{fig:Vortex2}
-    \end{center}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Electrophoresis results}
-For $\beta \ll 1$, the linear regime \cite{schnitzer2012surface} is dominant.
-In order to verify the solver, the numerical steady-state velocity is compared to the
-analytical solution \cite{schnitzer2012cubic}, derived by Schnitzer and Yariv. 
-Since the cubic correction is much smaller than
-the linear solution for $\beta \ll 1$, the difference between numerical results and
-the linear solution is compared to the cubic correction term.
-
-Because the leading order of the solution $\cU(\beta)$ is linear for $\beta \ll 1$, 
-the numerical discretization error is $O(\beta)$ as well.
-In order to reduce the discretization error of the numerical solution \eqref{eq:disc_zero_force}
-and after verifying that the discretization error converges as $O(h^2)$ (Figure \ref{fig:quadratic}),
-we employ Richardson extrapolation to $\cU^h$ and $\cU^{2h}$:
-\begin{equation}
-\hat\cU = \frac{4}{3} \cU^h - \frac{1}{3} \cU^{2h}.
-\end{equation}
-The results of the extrapolation $\hat\cU$ 
-and the analytical results 
-are given at Figures \ref{fig:Electrophoresis1} and \ref{fig:Electrophoresis2}.
-The numerical solver uses $R_{\max} = 10^2$,
-$K = 3$, $M = 5$ and $\beta = 0.1 \cdot 2^{t}$ for $t = -2:0.5:5$.
-The solver is applied to 2 grids of $N_r \times N_\theta = (128 \times 128)$ as the coarse grid 
-(with $\Delta_r \approx 0.037$), and $N_r \times N_\theta = (256 \times 256)$ as the fine grid
-(with $\Delta_r \approx 0.018$), in order to use Richardson extrapolation for $\hat\cU$.
-
-\begin{figure}
-    \begin{center}
-    \includegraphics[width=1\textwidth]{figs/quadratic_order.eps}
-        \caption[Quadratic convergence of steady-state velocity]{
-        The discretization error between the numerical and analytical solutions for 
-        $\alpha = 0$, $\Du = 0.5$, $\bar\zeta = 6$ and $R_{max} = 100$. The markers represent
-        the discretization errors for various grid sizes, and the dotted lines correspond to linear
-        functions of $\beta$, scaled by $4^n$. 
-        The graph shows that, as the number of grid points in each dimension increases by a factor of 2, 
-        the discretization error decreases by a factor of 4.
-        }
-	    \label{fig:quadratic}
-    \end{center}
-\end{figure}
-
-\begin{figure}
-    \begin{center}
-    \includegraphics[width=0.6\textwidth]{figs/Electrophoresis/numerical_vs_analytical_alpha=0.0_Du=0.5_zeta=6.0_Rmax=100.eps}
-    \includegraphics[width=0.6\textwidth]{figs/Electrophoresis/departure_from_linear_alpha=0.0_Du=0.5_zeta=6.0_Rmax=100.eps}
-        \caption[Highly-charged surface particle steady-state velocity]{
-        Steady-state velocity $\cU$ as a function of the 
-        electric field magnitude $\beta$, for highly-charged surface particle
-        electrophoresis (with $\alpha = 0, \text{Du} = 0.5, \bar\zeta = 6$).
-        The analytic solution velocity is represented by solid lines, 
-        and the numerical results are represented by markers.
-        The top figure shows the full numerical solution 
-        compared to the analytical one \eqref{eq:cubic}, and
-        the bottom figure compares the analytic cubic correction \cite{schnitzer2012cubic} 
-        to the difference between the numerical results and the linear regime.}
-	    \label{fig:Electrophoresis1}
-    \end{center}
-\end{figure}
-
-\begin{figure}
-    \begin{center}
-    \includegraphics[width=0.6\textwidth]{figs/Electrophoresis/numerical_vs_analytical_alpha=0.5_Du=1.0_zeta=10.0_Rmax=100.eps}
-    \includegraphics[width=0.6\textwidth]{figs/Electrophoresis/departure_from_linear_alpha=0.5_Du=1.0_zeta=10.0_Rmax=100.eps}
-        \caption[Highly-charged surface particle steady-state velocity]{
-        Steady-state velocity $\cU$ as a function of the 
-        electric field magnitude $\beta$, for highly-charged surface particle
-        electrophoresis (with $\alpha = 0.5, \text{Du} = 1, \bar\zeta = 10$).
-        The analytic solution velocity is represented by solid lines, 
-        and the numerical results are represented by markers.
-        The top figure shows the full numerical solution 
-        compared to the analytical one \eqref{eq:cubic}, and
-        the bottom figure compares the analytic cubic correction \cite{schnitzer2012cubic} 
-        to the difference between the numerical results and the linear regime.
-        When $\beta$ is large, the analytical cubic solution loses its validity 
-        because higher-order terms become significant.}
-	    \label{fig:Electrophoresis2}
-    \end{center}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Electrophoresis for large $\beta$ }
-When the electric field is large, nonlinear effects dominate the solution.
-In order to investigate the solution for strong electric fields, 
-we have run the solver on the TAMNUN HPC cluster \cite{tamnun}.
-Large grid sizes are used to verify that the numerical solution converges when the grid becomes finer and that no numerical artifacts are present in the solution.
-Moreover, several $R_{max} \in \{10, 30, 100\}$ values are used, to make sure it has no major impact on the solution.
-The results are shown in the following figures. 
-The steady-state velocity results are shown for several grid resolutions and several $R_{max}$ values in Figure \ref{fig:LargeBetaV_grids}, and the differences between the numerical results for
-steady-state velocity and the linear regime are shown in Figure \ref{fig:LargeBetaV_DeltaFromLinear_grids}.
-The estimated rate of convergence is shown in Figure \ref{fig:LargeBetaRatio}.
-
-The numerical solver converges well for $\beta < 5$ and the resulting steady-state velocity 
-for moderate $\beta$ values is very close to being an affine function of $\beta$.
-When $\beta$ becomes large, the salt concentration $C$ near the front of the particle 
-(at $\theta \approx 0$) approaches zero, while creating a wake behind the particle 
-(at $\theta \approx \pi$) as shown in Figures \ref{fig:LargeBeta_C1}, \ref{fig:LargeBeta_C2} and
-\ref{fig:LargeBeta_C3}.
-This results in high gradients in $\log C$ near the front of the particle  and, therefore, a strong electric field $\bE$ forms near the particle surface (Figures \ref{fig:LargeBeta_Phi1}, \ref{fig:LargeBeta_Phi2} and \ref{fig:LargeBeta_Phi3}) due to effective boundary conditions in (\ref{eq:ephor_bnd}).
-From Figs.
-\ref{fig:LargeBetaV_grids}-\ref{fig:LargeBetaV_DeltaFromLinear_grids} we conclude that even our most accurate numerical solution is valid only up to $\beta = 5$ approximately, and therefore we only further examine solutions in this range.
-
-The streamline pattern does not change drastically for different electric field magnitudes. 
-The resulting fluid flow is nearly proportional to that of the Stokes creeping flow, 
-as shown in Figure \ref{fig:LargeBeta_Psi} and \ref{fig:LargeBeta_PsiMinusUniformFlow}. 
-The difference between $\Psi(r, \theta)$ and $\Psi(r, \pi-\theta)$ is shown in Figure \ref{fig:LargeBeta_PsiAsymm}, demonstrating that the flow is almost symmetric (with relative
-difference up to approximately $0.5\%$) for $\beta < 5$.
-
-The numerical results show that a boundary layer starts to form near the front 
-of the particle for strong electric fields (see Figures \ref{fig:LargeBeta_BoundaryLayer_E}
-and \ref{fig:LargeBeta_BoundaryLayer_C}).
-The width of the boundary layer with respect to the electric field scales, to a good approximation, as: $\bar\rho(\beta) \approx 0.2 e^{-0.5 \beta}$.
-This causes numerical problems for the current solver at large $\beta$, due to insufficient
-grid resolution at the boundary layer of $C$ and $\bE$.
-
-\begin{figure}
-    \begin{center}
-    \includegraphics[width=.45\textwidth]{figs/LargeBetaV_[128_256_512]_Rmax=10.eps}
-    \includegraphics[width=.45\textwidth]{figs/LargeBetaV_[512x512]_Rmax=10_30_100.eps}
-        \caption[Large $\beta$ results for $\cU$]
-{Large $\beta$ results for $\cU(\beta)$ ($\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$). 
-The left figure shows the numerical results of $\cU(\beta)$ for $R_{max} = 10$ and the following grid sizes: $128 \times 128$, $256 \times 256$, $512 \times 512$. 
-The right figure shows the numerical results of $\cU(\beta)$ for
-$512 \times 512$ grid for $R_{max} = 100, 30, 10$. For small values of $\beta$, the linear
-regime of $\cU(\beta)$ is dominant. 
-For moderate $\beta$ values, the steady state velocity is very close to an affine function of $\beta$.
-However, for larger values of $\beta$, the numerical solution
-deviates significantly from the linear regime, due to convergence problems at $\beta > 6$, 
-and for $\beta \sim 7$, the solver fails to converge. The numerical convergence 
-depends on the grid resolution near the particle surface -- 
-as it becomes finer (when $N_r$ increases or $R_{max}$ decreases), the solver convergence improves.}
-	    \label{fig:LargeBetaV_grids}	    
-    \end{center}
-\end{figure}
-\begin{figure}
-    \begin{center}
-    \includegraphics[width=.45\textwidth]{figs/LargeBetaV_DeltaFromLinear[128_256_512]_Rmax=10.eps}
-    \includegraphics[width=.45\textwidth]{figs/LargeBetaV_DeltaFromLinear[512x512]_Rmax=10_30_100.eps}
-        \caption[Large $\beta$ results for $\cU$ -- difference from linear regime]
-{Large $\beta$ results for $\cU(\beta) - \beta\cU_1$ ($\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$ and $\cU_1 \approx 4.258$ is the linear regime coefficient). 
-The left figure shows the numerical results of $\cU(\beta)$ for $R_{max} = 10$ and the following grid sizes: $128 \times 128$, $256 \times 256$, $512 \times 512$. 
-The right figure shows the numerical results of $\cU(\beta)$ for
-$512 \times 512$ grid for $R_{max} = 100, 30, 10$.
-It is seen that the difference is indeed nearly an affine function of $\beta$ in the large-$\beta$ regime, so long as the numerical solution remains sufficiently accurate.}
-	    \label{fig:LargeBetaV_DeltaFromLinear_grids}	    
-    \end{center}
-\end{figure}
-\begin{figure}
-    \begin{center}
-    \includegraphics[width=.5\textwidth]{figs/LargeBetaRatio.eps}
-        \caption[Rate of convergence estimation for $\cU$ at large $\beta$]
-        {Rate of convergence estimation for $\cU$ at large $\beta$  
-        ($\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$), 
-        based on the numerical results of $\cU(\beta)$, for the grid sizes of 
-        $128 \times 128$, $256 \times 256$, $512 \times 512$. 
-        The rate of convergence $r(\beta)$ is estimated by 
-        $r(\beta) \triangleq \left(\cU^{4h}(\beta) - \cU^{2h}(\beta)\right)/\left(\cU^{2h}(\beta) - \cU^{h}(\beta)\right)$.
-        For small $\beta$, $r(\beta) \rightarrow 4$, showing 
-        quadratic convergence for the linear regime. 
-        For moderate $\beta$, the convergence rate slows down, 
-        and it deteriorates for large $\beta$ values.
-        }
-	    \label{fig:LargeBetaRatio}
-    \end{center}
-\end{figure}
-
-\begin{figure}
-    \begin{center}
-    \includegraphics[width=1\textwidth]{figs/LargeBeta/sol_beta=1.000e-01_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
-        \caption[$\beta = 0.1$ results for $C$]
-        {$\beta = 0.1$ results for $C$: grid size $512 \times 512$, 
-        $R_{max} = 10$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.
-        Here the linear regime dominates the solution for 
-        $C_\beta(r, \theta) \approx 1 - \beta \frac{\cos\theta}{2r^2}$.}
-	    \label{fig:LargeBeta_C1}	    
-    \end{center}
-\end{figure}
-
-\begin{figure}
-    \begin{center}
-    \includegraphics[width=1\textwidth]{figs/LargeBeta/sol_beta=8.000e-01_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
-        \caption[$\beta = 0.8$ results for $C$]
-        {$\beta = 0.8$ results for $C$: grid size $512 \times 512$, 
-        $R_{max} = 10$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.
-        For moderate $\beta$ values, the salt concentration starts
-        to form a wake behind the particle ($\theta \approx \pi$).}
-	    \label{fig:LargeBeta_C2}	    
-    \end{center}
-\end{figure}
-
-\begin{figure}
-    \begin{center}
-    \includegraphics[width=1\textwidth]{figs/LargeBeta/sol_beta=5.000e+00_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_C.eps}
-        \caption[$\beta = 5.0$ results for $C$]
-        {$\beta = 5.0$ results for $C$: grid size $512 \times 512$, 
-        $R_{max} = 10$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.
-        For large values of $\beta$, there is a significant drop in
-        salt concentration at the front of the particle -- 
-        $C$ approaches zero at $\theta \approx 0$, such that 
-        $\deriv{C}{r}$ becomes large 
-        (since the change in $C$ happens on a small length scale).
-        Due to the boundary conditions of the electrophoresis problem
-        (given by (\ref{eq:ephor_bnd})), the electric field radial
-        component given by 
-        $E_r = -\deriv{\varPhi}{r} = -\frac{1}{C}\deriv{C}{r}$, 
-        becomes singular where $C \rightarrow 0$.
-        }
-	    \label{fig:LargeBeta_C3}	    
-    \end{center}
-\end{figure}
-
-\begin{figure}
-    \begin{center}
-    \includegraphics[width=1\textwidth]{figs/LargeBeta/sol_beta=1.000e-01_[129x129]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
-        \caption[$\beta = 0.1$ results for $\varPhi$]
-        {$\beta = 0.1$ results for $\varPhi$:
-        grid size $512 \times 512$, $R_{max} = 10$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$. 
-        The electric potential and the electric field results are multiplied by $\beta^{-1}$,
-	    so the linear regime appears unchanged for different values of $\beta$.
-        Here the linear regime dominates the solution for 
-        $\varPhi_\beta(r, \theta) \approx -\beta {r \cos\theta}$,
-        hence the electric field is constant for weak electric fields:
-        $\bE \approx \beta \ui$.}
-	    \label{fig:LargeBeta_Phi1}
-    \end{center}
-\end{figure}
-
-\begin{figure}
-    \begin{center}
-    \includegraphics[width=1\textwidth]{figs/LargeBeta/sol_beta=8.000e-01_[129x129]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
-        \caption[$\beta = 0.8$ results for $\varPhi$]
-        {$\beta = 0.8$ results for $\varPhi$:
-        grid size $512 \times 512$, $R_{max} = 10$, $\Du = 1$, 
-        $\bar\zeta = 10$, $\alpha = 0.5$. 
-	    The electric potential and the electric field results are multiplied by $\beta^{-1}$,
-	    so the linear regime appears unchanged for different values of $\beta$.
-        For moderate values of $\beta$,
-        the symmetry breaks and the electric field becomes stronger 
-        near the front of the particle than at the back.}
-	    \label{fig:LargeBeta_Phi2}
-    \end{center}
-\end{figure}
-
-\begin{figure}
-    \begin{center}
-    \includegraphics[width=1\textwidth]{figs/LargeBeta/sol_beta=5.000e+00_[129x129]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_PhiE.eps}
-        \caption[$\beta = 5.0$ results for $\varPhi$]
-        {$\beta = 5.0$ results for $\varPhi$:
-        grid size $512 \times 512$, $R_{max} = 10$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.
-        The electric potential and the electric field results are multiplied by $\beta^{-1}$,
-	    so the linear regime appears unchanged for different values of $\beta$.
-	    For large values of $\beta$, the electric field radial component $E_r = -\deriv{\varPhi}{r}$
-	    at the particle front becomes much larger than the electric field at the particle back.
-		}
-	    \label{fig:LargeBeta_Phi3}
-    \end{center}
-\end{figure}
-
-\begin{figure}
-    \begin{center}
-    \includegraphics[width=.45\textwidth]{figs/LargeBeta/sol_beta=1.000e-01_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_[1]_Psi.eps}
-    \includegraphics[width=.45\textwidth]{figs/LargeBeta/sol_beta=8.000e-01_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_[1]_Psi.eps}
-    \includegraphics[width=.45\textwidth]{figs/LargeBeta/sol_beta=5.000e+00_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_[1]_Psi.eps}
-    \includegraphics[width=.45\textwidth]{figs/LinearStokes_Psi.eps}
-        \caption[Streamfunction results]
-        {$\beta = 0.1, 0.8, 5.0$ and Stokes streamlines results: grid size $512 \times 512$, 
-        $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.
-        The numerical results for $\Psi$ are scaled by $\beta^{-1}$, so the linear regime
-        will appear the same for different $\beta$ values.
-        Note that the numerical results show a
-        flow pattern very similar to that of the analytical Stokes flow.}
-	    \label{fig:LargeBeta_Psi}	    
-    \end{center}
-\end{figure}
-
-\begin{figure}
-    \begin{center}
-    \includegraphics[width=.45\textwidth]{figs/PsiMinusUniformFlow/sol_beta=1.000e-01_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_[1]_Psi.eps}
-    \includegraphics[width=.45\textwidth]{figs/PsiMinusUniformFlow/sol_beta=8.000e-01_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_[1]_Psi.eps}
-    \includegraphics[width=.45\textwidth]{figs/PsiMinusUniformFlow/sol_beta=5.000e+00_[513x513]_Rmax=10.0_Du=1.00_zeta=10.00_alpha=0.50_[1]_Psi.eps}
-    \includegraphics[width=.45\textwidth]{figs/PsiMinusUniformFlow/LinearStokes_Psi-uniformflow.eps}
-        \caption[Streamfunction results]
-        {$\beta = 0.1, 0.8, 5.0$ and Stokes streamlines results after subtraction of the uniform
-        flow streamfunction ($\frac{\cU}{2}r^2 \sin^2\theta$): grid size $512 \times 512$, 
-        $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.
-        The numerical results for $\Psi$ are scaled by $\beta^{-1}$, so the linear regime
-        will appear the same for different $\beta$ values.
-        Even for the largest beta we could compute, the velocity remains fairly symmetric and 		
-        ``uneventful'' also in the framework of the ``laboratory'' rather than that of the particle.}
-	    \label{fig:LargeBeta_PsiMinusUniformFlow}	    
-    \end{center}
-\end{figure}
-
-\begin{figure}
-    \begin{center}
-    \includegraphics[width=1\textwidth]{figs/streamlines_asymmetry.eps}
-        \caption[Streamfunction asymmetry]
-        {Streamline results: grid size $512 \times 512$, 
-        $R_{max} = 10$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$.
-        The relative streamline asymmetry is computed by 
-        $\|\Psi(r, \theta) - \Psi(r, \pi-\theta)\|/\|\Psi(r, \theta)\|$
-        as a function of $\beta$. The results show that the streamline pattern is almost 
-        symmetric, even for moderately large $\beta$ values.}
-	    \label{fig:LargeBeta_PsiAsymm}	    
-    \end{center}
-\end{figure}
-
-\begin{figure}
-    \begin{center}
-    \includegraphics[width=.45\textwidth]{figs/BoundaryLayerWidth_E1.eps}
-    \includegraphics[width=.45\textwidth]{figs/BoundaryLayerWidth_E2.eps}
-    \includegraphics[width=.45\textwidth]{figs/BoundaryLayerWidth_E3.eps}
-    \includegraphics[width=.45\textwidth]{figs/BoundaryLayerWidth_E4.eps}
-        \caption[Electric field boundary layer]
-        {Electric field boundary layer formation: grid size $512 \times 512$, 
-        $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$. The upper left
-        graph shows normalized electric field radial component $E_r$ near the particle front
-        ($\theta = 0$). The numerical results for $e(\rho) = E_r(r=1+\rho, \theta=0)$
-        are normalized by $\hat{e}(\rho) = \left(e(\rho) - \beta\right)/\left(e(0) - \beta\right)$,
-        where $e(\rho = \infty) = \beta$.
-        The normalized electric field satisfies $\hat{e}(\rho) \in [0, 1]$ and is shown as function
-        of $\rho = r - 1$ at the upper left graph and as function of $\rho e^{0.5 \beta}$ at
-        the upper right graph.
-        In order to estimate the width of the boundary layer, for each $\beta$, we compute the value 
-        of $\bar\rho(\beta) = \min_\rho \{ \rho : \hat{e}(\rho) < 0.5\}$. Each such $\bar\rho(\beta)$
-        is plotted at the left graph as a solid dot on the corresponding line.
-        In addition, $\bar\rho(\beta)$ is plotted as a function of $\beta$ using logarithmic 
-        $y$ axis at the lower left graph to show that $\bar\rho(\beta) \approx 0.2 e^{-0.5 \beta}$.
-        Moreover, $E_r(\beta; r=1, \theta=0) / \beta$ grows exponentially as a function of $\beta$,
-        as shown at the lower right graph.
-        Thus, a boundary layer is indeed forming near the front of the particle.
-        }
-	    \label{fig:LargeBeta_BoundaryLayer_E}	    
-    \end{center}
-\end{figure}
-
-\begin{figure}
-    \begin{center}
-    \includegraphics[width=.45\textwidth]{figs/boundary_layer_C1.eps}
-    \includegraphics[width=.45\textwidth]{figs/boundary_layer_C2.eps}
-        \caption[Ionic concentration boundary layer]
-        {Ionic concentration boundary layer formation: grid size $512 \times 512$, 
-        $R_{max} = 30$, $\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$. The left
-        graph shows the ionic concentration $C$ near the particle front
-        ($\theta = 0$). 
-        In addition, $C_\beta(r=1, \theta=0)$ is plotted as a function of $\beta$ using logarithmic 
-        $y$ axis at the right graph to show that 
-        $C_\beta(r=1, \theta=0) \approx 0.94 e^{-0.45 \beta}$.
-        The ionic concentration becomes very close to zero for $\beta \approx 7$ at $r = 1$, 
-        creating a singularity near the particle front.
-        }
-	    \label{fig:LargeBeta_BoundaryLayer_C}	    
-    \end{center}
-\end{figure}
-
-\begin{figure}
-    \begin{center}
-    \includegraphics[width=.6\textwidth]{figs/C_Er_product.eps}
-        \caption{The product of $C(r=1, \theta=0) E_r(r=1, \theta=0) / \beta$ as
-        a function of $\beta$.}
-	    \label{fig:C_Er_product}	    
-    \end{center}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-\section{Discussion} \label{sec:discussion}
-A numerical framework for a
-nonlinear electrokinetic transport system is described.
-The framework is used to construct numerical solvers 
-for two electrokinetic problems: the migration of ion-exchangers
-and surface-charged inert particle electrophoresis.
-The numerical results for weak electric field 
-exhibit a good correspondence to the asymptotic models as shown above.
-Two interesting phenomena (cubic regime and downstream vortex) were predicted for the ion-exchanger
-using the numerical results, and were verified using an asymptotic expansion of the nonlinear system.
-The electrophoresis problem was solved on a high-resolution grid to validate the asymptotic 
-cubic correction of the steady-state velocity, as well as to provide insights into
-the solution behavior for moderately strong electric fields.
-For strong electric field, the nonlinear effects become dominant and
-a boundary-layer structure begins to form.
-Due to diminishing ion concentration $C$ at the front of the particle,
-a boundary layer of thickness approximately $0.2 e^{-0.5\beta}$ 
-is formed with respect to the electric field $\bE$ at the front of the particle.
-The value of $E_r / \beta$ at ($r = 1$, $\theta = 0$) is given approximately by 
-$e^{\beta/2}$, while the value of $C(r = 1, \theta = 0)$ is given approximately 
-by $e^{-\beta/2}$, and their product remains close to 1 for all $\beta$ that we could compute
-(as shown in Figure \ref{fig:C_Er_product}).
-However, the velocity of the particle remains nearly linear with $\beta$
-and the velocity field is very close to being symmetric.
-
-\section{Future Work}
-Future work may include using the numerical results described in this work to develop
-an analytical solution for the strong field regime of the electrophoresis problem, which is 
-of interest. The solver may be used to investigate how the solution
-(and the evolving boundary layer, in particular) depends on the problem parameters.
-Optimizing the direct sparse linear solver can be done by
-using the ordering data from previous calls,
-or replacing the full Newton step by an iterative linear solver
-(e.g., using preconditioned Krylov subspace methods \cite{saad2003book} or
-Multigrid), allowing finer grids to be used.
-In order to achieve high numerical accuracy, the grid discretization should be made finer
-near the particle surface (at $r = 1$), while $R_{max}$ can be made smaller. Moreover, a different discretization scheme may be used for
-the $r$ coordinate, to have higher grid resolution near the particles.
-In addition, the continuation of the solution between different $\beta$ values
-should advance in finer steps, to ensure Newton method convergence.
-The discretization of boundary conditions far away from the particle may be improved
-by including the linear correction from the asymptotic solution, or reformulation of
-far-away boundary condition according to the asymptotic behavior of the analytic solution
-far away from the particle.
-Moreover, the framework may be used for automatic construction of Newton solvers 
-for other nonlinear PDE systems, for example, for particles with different surface 
-properties, or different particle shape.
-
-\appendix
-
-\chapter{Effective Boundary Conditions} \label{append:slip}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Debye layer scaling}
-
-We define the scaled coordinate $\rho$ (normal to ion-exchanger surface), where $\delta \ll 1$:
-\begin{align}
-  \rho = \frac{r-1}{\delta}. 
-\end{align}
-Thus, the electric potential and the ionic concentrations are $O(1)$ at the Debye layer ($r \approx 1$):
-\begin{align}
-  \varphi(\rho,\theta) &\sim \varphi, \\
-  c_\pm(\rho,\theta) &\sim c_\pm, \\
-  c(\rho,\theta) &\sim c, \\
-  q(\rho,\theta) &\sim q.
-\end{align}
-
-The radial fluxes at the Debye layer are $O(\delta^{-1})$, due to coordinate rescaling:
-\begin{align}
-  j_\pm(\rho, \theta) &\sim \delta^{-1} j_\pm.
-\end{align}
-
-The pressure is $O(\delta^{-2})$, due to momentum balance equations:
-\begin{align}
-  p(\rho, \theta) &\sim \delta^{-2} p.
-\end{align}
-
-The tangential velocity component is $O(1)$ and the radial component is $O(\delta)$.
-
-\section{Ion Fluxes}
-
-In order to match bulk $O(1)$ outer radial ionic flux, 
-the $O(\delta^{-1})$ term of the inner ionic radial flux, $j_\pm(\rho, \theta)$ must vanish:
-\begin{align}
- \nonumber
-  -\deriv{c_\pm}{\rho} \mp c_\pm \deriv{\varphi}{\rho} &= 0, \\
-  \pars{\varPhi - \varphi} \pm\pars{\log C_\pm - \log c_\pm} &= 0, \\
- \nonumber
-  \varPhi - \varphi \pm \log \frac{C_\pm}{c_\pm} &= 0.
-\end{align}
-This relation can be rewritten as a Boltzmann distribution of $c_\pm$,
-where $\lim_{\rho\rightarrow\infty} c_\pm = C$,
-\begin{equation}
-c_\pm = C \exp\left[\pm(\varPhi - \varphi)\right].
-\end{equation}
-
-\section{Electric Potential}
-The leading-order Laplace equation in the Debye layer reads
-\begin{align}  
-\deriv{^2 \varphi}{\rho^2} = -q = -\frac{c_+ - c_-}{2} = 
--\frac{C}{2} \pars{\exp\left[+(\varPhi - \varphi)\right] - \exp\left[-(\varPhi - \varphi)\right]} = C \sinh(\varphi - \varPhi).
-\end{align}
-Denote $\psi = \varphi - \varPhi$, so that $\psi(0) = \cV - \varPhi = \zeta$ and 
-$\psi(\rho\rightarrow\infty) = 0$:
-\begin{align}
-\nonumber
-\deriv{^2 \psi}{\rho^2} &= C \sinh(\psi) = 2 C \sinh{\frac{\psi}{2}}\cosh{\frac{\psi}{2}} ,
-\\
-2\deriv{\psi}{\rho} \deriv{^2 \psi}{\rho^2} &= 
-4 C \sinh{\frac{\psi}{2}}\cosh{\frac{\psi}{2}} \deriv{\psi}{\rho} ,
-\\ \nonumber
-\deriv{}{\rho} \pars{\deriv{\psi}{\rho}}^2 &= 
-\deriv{}{\rho} \pars{2 \sqrt{C} \sinh{\frac{\psi}{2}}}^2 .
-\end{align}
-
-Integrating with respect to boundary condtions yields:
-\begin{align}  
-\nonumber
-\deriv{\psi}{\rho} = -2\sqrt{C}\sinh\frac{\psi}{2} &= 
--4\sinh\frac{\psi}{4}\cosh\frac{\psi}{4} \sqrt{C} = 
--4\tanh\frac{\psi}{4}\cosh^2\frac{\psi}{4} \sqrt{C}, \\  
-\frac{1/{\tanh\frac{\psi}{4}}}{4\cosh^2\frac{\psi}{4}}
-\deriv{\psi}{\rho}
-&= -\sqrt{C}, \\  
-\nonumber
-\deriv{}{\rho}\pars{\log\tanh\frac{\psi}{4}} &= \deriv{}{\rho}\pars{-\rho \sqrt{C}} .
-\end{align}
-
-Integrating with respect to boundary condtions yields:
-\begin{align}
-\nonumber
-\log\tanh\frac{\psi}{4} - \log\tanh\frac{\zeta}{4} &= -\rho \sqrt{C}, \\
-\psi = \varphi - \varPhi &= 
-4 \tanh^{-1}\pars{\tanh{\frac{\zeta}{4}} \cdot e^{-\rho \sqrt{C}}}.
-\end{align}
-
-\section{Radial Momentum}
-Leading-order $O(\delta^{-3})$ radial momentum balance in the Debye layer yields:
-\begin{align} 
-- \deriv{p}{\rho} + \deriv{\varphi}{\rho} \deriv{^2\varphi}{\rho^2} &= 0.
-\end{align}
-One integration yields:
-\begin{align} 
-p &= \frac{1}{2}\pars{\deriv{\varphi}{\rho}}^2 = \frac{1}{2}\pars{\deriv{\psi}{\rho}}^2.
-\end{align}
-
-\section{Tangential Momentum}
-Leading-order $O(\delta^{-2})$ tangential momentum balance in the Debye layer yields:
-\begin{align} 
-\nonumber
-0 &= \deriv{^2 v_\theta}{\rho^2} - \deriv{p}{\theta} 
- + \deriv{\varphi}{\theta} \deriv{^2\varphi}{\rho^2} ,
-\\ \nonumber
-\deriv{^2 v_\theta}{\rho^2} &= \frac{1}{2}\deriv{}{\theta}\pars{\deriv{\psi}{\rho}}^2
-- \deriv{(\psi + \varPhi)}{\theta} \deriv{^2\psi}{\rho^2}  
- = \deriv{}{\theta}\pars{2C \sinh^2\frac{\psi}{2}}
-- \deriv{\psi}{\theta} C \sinh\psi
-- \deriv{\varPhi}{\theta} \deriv{^2\psi}{\rho^2}  
-\\
- &= \deriv{}{\theta}\pars{C \pars{\cosh\psi - 1}}
-- C \sinh\psi \deriv{\psi}{\theta}
-- \deriv{\varPhi}{\theta} \deriv{^2\psi}{\rho^2}  
-\\ \nonumber
- &= \deriv{C}{\theta} \pars{\cosh\psi - 1}
-- \deriv{\varPhi}{\theta} \deriv{^2\psi}{\rho^2}  
- = \deriv{C}{\theta} \pars{2 \sinh^2 \frac{\psi}{2}}
-- \deriv{\varPhi}{\theta} \deriv{^2\psi}{\rho^2}  
-\\ \nonumber
- &= -\deriv{C}{\theta} \frac{2}{\sqrt{C}} \pars{\half \sinh \frac{\psi}{2} \deriv{\psi}{\rho}}
-- \deriv{\varPhi}{\theta} \deriv{^2\psi}{\rho^2}  
- = -\deriv{C}{\theta} \frac{2}{\sqrt{C}} \deriv{}{\rho}\pars{\cosh \frac{\psi}{2}}
-- \deriv{\varPhi}{\theta} \deriv{^2\psi}{\rho^2}  .
-\end{align}
-By integrating from specific $\rho$ to $\rho \rightarrow \infty$ (where $\psi = 0$):
-\begin{align}
-\deriv{v_\theta}{\rho} &= -\deriv{C}{\theta} \frac{2}{\sqrt{C}} 
-\pars{\cosh \frac{\psi}{2} - 1} - \deriv{\varPhi}{\theta} \deriv{\psi}{\rho}   
-= -\deriv{C}{\theta} \frac{4}{\sqrt{C}} \sinh^2 \frac{\psi}{4} 
-  - \deriv{\varPhi}{\theta} \deriv{\psi}{\rho}   .
-\end{align}
-Note that:
-\begin{align}
-\deriv{\psi}{\rho} &= -2\sqrt{C}\sinh\frac{\psi}{2} = 
-                       -4\sqrt{C}\sinh\frac{\psi}{4}\cosh\frac{\psi}{4},
-\\
--4\sinh\frac{\psi}{4} &= \frac{1 / \cosh\frac{\psi}{4}}{\sqrt{C}} \deriv{\psi}{\rho}.
-\end{align}
-Thus:
-\begin{align}
-\deriv{v_\theta}{\rho} &= 
-  \pars{\deriv{C}{\theta} \frac{1}{C}} \cdot
-  \pars{\frac{\sinh\frac{\psi}{4}}{\cosh\frac{\psi}{4}} \deriv{\psi}{\rho}}
-  - \deriv{\varPhi}{\theta} \deriv{\psi}{\rho}
-=  4\deriv{}{\rho} \pars{\log\cosh\frac{\psi}{4}} \deriv{}{\theta} \log C
-  - \deriv{\psi}{\rho} \deriv{\varPhi}{\theta},
-\\
-\deriv{v_\theta}{\rho} &= 
-\deriv{}{\rho} \pars{ 4\log\cosh\frac{\psi}{4} \deriv{}{\theta} \log C
-  - \psi \deriv{\varPhi}{\theta} }.
-\end{align}
-
-By integrating from $\rho = 0$ to $\rho \rightarrow \infty$, 
-we have Dukhin-Derjaguin slip formula for tangential velocity component $V_\theta$ 
-(where the radial component is $V_r = 0$) for $\zeta = \cV - \varPhi$:
-\begin{align} 
-V_\theta = \zeta \cdot \deriv{\varPhi}{\theta} -
-      4\log\cosh \frac{\zeta}{4} \cdot \deriv{}{\theta} \log C 
-= \zeta \cdot \deriv{\varPhi}{\theta} + 
-      2\log\pars{1 - \tanh^2 \frac{\zeta}{4}} \cdot \deriv{}{\theta} \log C .
-\end{align}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\chapter{Differential operators in spherical coordinates} \label{append:spherical}
-
-The following spherical coordinate system is used:
-\begin{align}
-\nonumber
-x &= r \sin \theta \cos \phi \\
-y &= r \sin \theta \sin \phi \\
-\nonumber
-z &= r \cos \theta
-\end{align}
-
-Assume full symmetry around $z$ axis -- there is no dependence on $\phi$:
-\begin{align}
-\bnabla f &= \frac{\partial f}{\partial r} \mathbf{\hat{r}} +
-\frac{1}{r} \frac{\partial f}{\partial \theta} \mathbf{\hat{\theta}} +
-\frac{1}{r \sin\theta} \frac{\partial f}{\partial \phi} \mathbf{\hat{\phi}}
-\\
-\bnabla \mathbf{\cdot} \mathbf{F} &= 
-\frac{1}{r^2}\frac{\partial}{\partial r} \left( r^2 \cdot F_r\right)
-  + \frac{1}{r \sin\theta} \frac{\partial}{\partial \theta} \left( \sin\theta \cdot F_\theta\right)
-  + \frac{1}{r \sin\theta} \frac{\partial F_\phi}{\partial \phi}
-\end{align}
-
-\section{Scalar Operators}
-Scalar Laplacian derivation:
-\begin{align}
-\Laplacian f = \bnabla \mathbf{\cdot} \bnabla f = \frac{1}{r^2}\frac{\partial}{\partial r}
-\left( r^2 \frac{\partial f}{\partial r} \right) +
-\frac{1}{r^2 \sin\theta} \frac{\partial}{\partial \theta} \left( \sin\theta \cdot \frac{\partial f}{\partial \theta}\right)
-+ \frac{1}{r^2 \sin^2\theta} \frac{\partial^2 f}{\partial \phi^2}
-\end{align}
-In conservative form:
-\begin{align}
-r^2 \sin\theta \cdot \bLaplacian f = \frac{\partial}{\partial r} \left( r^2 \sin \theta \frac{\partial f}{\partial r} \right) +
-\frac{\partial}{\partial \theta} \left( \sin\theta \cdot \frac{\partial f}{\partial \theta}\right) +
-\frac{\partial}{\partial \phi} \left( \frac{1}{\sin\theta} \cdot \frac{\partial f}{\partial \phi}\right)
-\end{align}
-
-The unit vectors in spherical coordinate system are:
-\begin{align}
- \brhat &= \deriv{\br}{r}
- = \mat{c}{\sin\theta \cos\phi \\ \sin\theta \sin\phi \\ \cos\theta} ,&
- \bthetahat &= \frac{1}{r} \deriv{\br}{\theta}
- = \mat{c}{\cos\theta \cos\phi \\ \cos\theta \sin\phi \\ -\sin\theta} ,&
- \bphihat &= \frac{1}{r \sin \theta} \deriv{\br}{\phi}
- = \mat{c}{-\sin\phi \\ \cos\phi \\ 0}
-\end{align}
-Note that:
-\begin{align}
-  \deriv{\brhat}{r} = \mathbf{0} , \nonumber
-  \deriv{\bthetahat}{r} = \mathbf{0} , 
-  \deriv{\bphihat}{r} = \mathbf{0}, \\
-  \deriv{\brhat}{\theta} = \bthetahat , 
-  \deriv{\bthetahat}{\theta} = -\brhat , 
-  \deriv{\bphihat}{\theta} = \mathbf{0}, \\
-  \deriv{\brhat}{\phi} = \sin \theta \cdot \bphihat , \nonumber
-  \deriv{\bthetahat}{\phi} = \cos \theta \cdot \bphihat , 
-  \deriv{\bphihat}{\phi} = -\sin \theta \cdot \brhat -\cos \theta \cdot \bthetahat.
-\end{align}
-
-\section{Vector Operators}
-Vector gradient operator can be written by:
-\begin{align} \nonumber
-\bnabla\bV &= \left\{ \brhat \deriv{}{r} +
-\bthetahat \frac{1}{r} \deriv{}{\theta} +
-\bphihat \frac{1}{r \sin\theta} \deriv{}{\phi} \right\}
-\bV = \left\{ \brhat \deriv{}{r} +
-\bthetahat \frac{1}{r} \deriv{}{\theta} +
-\bphihat \frac{1}{r \sin\theta} \deriv{}{\phi} \right\}
-\left( V_r \brhat + V_\theta \bthetahat + V_\phi \bphihat \right)
-\\ \nonumber
-\deriv{\bV}{r} &=
-\deriv{V_r}{r}\brhat + \deriv{V_\theta}{r}\bthetahat + \deriv{V_\phi}{r}\bphihat
-\\ 
-\deriv{\bV}{\theta} &=
-\deriv{V_r}{\theta}\brhat + \deriv{V_\theta}{\theta}\bthetahat + \deriv{V_\phi}{\theta}\bphihat
-+ V_r\bthetahat - V_\theta\brhat
-\\ \nonumber
-\deriv{\bV}{\phi} &=
-\deriv{V_r}{\phi}\brhat + \deriv{V_\theta}{\phi}\bthetahat + \deriv{V_\phi}{\phi}\bphihat
-+ V_r \sin\theta\bphihat + V_\theta \cos\theta\bphihat -
-V_\phi \left(\brhat \sin\theta + \bthetahat \cos\theta \right)
-\\ \nonumber
-\bnabla\bV &=
-\mat{ccc}{1&0&0 \\ 0&\frac{1}{r}&0 \\ 0&0&\frac{1}{r \sin\theta}}
-\mat{ccc}{
-\deriv{V_r}{r} & \deriv{V_\theta}{r} & \deriv{V_\phi}{r} \\
-\deriv{V_r}{\theta} - V_\theta &
-\deriv{V_\theta}{\theta} + V_r&
-\deriv{V_\phi}{\theta} \\
-\deriv{V_r}{\phi} - V_\phi \sin\theta &
-\deriv{V_\theta}{\phi} - V_\phi \cos\theta  &
-\deriv{V_\phi}{\phi} + V_r \sin\theta + V_\theta \cos\theta
-}
-\end{align}
-Vector Laplacian components can be written as:
-\begin{align}
-\Laplacian \bV = \bnabla \cdot \bnabla \bV &= \frac{1}{r^2}\deriv{}{r}\left(r^2 \deriv{\bV}{r}\right) +
-\frac{1}{r^2\sin\theta}\deriv{}{\theta}\left(\sin\theta\deriv{\bV}{\theta}\right)+
-\frac{1}{r^2 \sin^2\theta}\deriv{}{\phi}\left(\deriv{\bV}{\phi}\right)
-\end{align}
-$\brhat$ component:
-\begin{align}
-\Laplacian (V_r\brhat) &= \nonumber
-\frac{1}{r^2}\deriv{}{r}\left(r^2 \deriv{V_r}{r}\right)\brhat
-\\ &+ \nonumber
-\frac{1}{r^2\sin\theta}\deriv{}{\theta}\left(
-\sin\theta\left(\deriv{V_r}{\theta}\brhat + V_r\bthetahat \right)\right)
-\\ &+ \nonumber
-\frac{1}{r^2 \sin^2\theta}\deriv{}{\phi}\left(
-\deriv{V_r}{\phi}\brhat + V_r \sin\theta\bphihat
-\right) \\
-\Laplacian (V_r\brhat) &= 
-\left(
-\frac{2}{r}\deriv{V_r}{r}+\deriv{^2V_r}{r^2}\right)\brhat
-\\ &+ \nonumber
-\frac{1}{r^2\sin\theta}\left(
-\cos\theta\left(\deriv{V_r}{\theta}\brhat + V_r\bthetahat \right) +
-\sin\theta\left(\deriv{^2V_r}{\theta^2}\brhat + \deriv{V_r}{\theta}\bthetahat + \deriv{V_r}{\theta}\bthetahat - V_r\brhat\right)
-\right)
-\\ &+ \nonumber
-\frac{1}{r^2 \sin^2\theta}\left(
-\deriv{^2V_r}{\phi^2}\brhat + \deriv{V_r}{\phi} \sin\theta\bphihat +
-\deriv{V_r}{\phi}\bphihat\sin\theta - V_r \sin\theta
-\left(\brhat \sin\theta + \bthetahat \cos\theta \right)
-\right)
-\\ \nonumber
-\Laplacian (V_r\brhat) &=
-\left(
-\frac{2}{r}\deriv{V_r}{r}+\deriv{^2V_r}{r^2}-\frac{2V_r}{r^2}
-+ \frac{1}{r^2}\deriv{^2V_r}{\theta^2}
-+ \frac{\cot\theta}{r^2} \deriv{V_r}{\theta}
-+ \frac{1}{r^2 \sin^2\theta} \deriv{^2V_r}{\phi^2}
-\right)\brhat
-\\ &+ \frac{2}{r^2} \deriv{V_r}{\theta} \bthetahat + \frac{2}{r^2 \sin\theta}\deriv{V_r}{\phi} \bphihat
-\nonumber
-\end{align}
-$\bthetahat$ component:
-\begin{align}
-\Laplacian (V_\theta\bthetahat) &= \nonumber
-\frac{1}{r^2}\deriv{}{r}\left(r^2 \deriv{V_\theta}{r}\right)\bthetahat
-\\ &+ \nonumber
-\frac{1}{r^2\sin\theta}\deriv{}{\theta}\left(
-\sin\theta\left(\deriv{V_\theta}{\theta}\bthetahat - V_\theta\brhat \right)\right)
-\\ &+ \nonumber
-\frac{1}{r^2 \sin^2\theta}\deriv{}{\phi}\left(
-\deriv{V_\theta}{\phi}\bthetahat + V_\theta \cos\theta\bphihat
-\right)
-\\ 
-\Laplacian (V_\theta\bthetahat) &=
-\left(\frac{2}{r}\deriv{V_\theta}{r} + \deriv{^2V_\theta}{r^2}\right)\bthetahat
-\\ &+ \nonumber
-\frac{1}{r^2\sin\theta}\left(
-\cos\theta\left(\deriv{V_\theta}{\theta}\bthetahat - V_\theta\brhat \right) +
-\sin\theta\left(\deriv{^2V_\theta}{\theta^2}\bthetahat - \deriv{V_\theta}{\theta}\brhat
--\deriv{V_\theta}{\theta}\brhat - V_\theta\bthetahat\right)
-\right)
-\\ &+ \nonumber
-\frac{1}{r^2 \sin^2\theta}\left(
-\deriv{^2V_\theta}{\phi^2}\bthetahat + \deriv{V_\theta}{\phi} \cos\theta\bphihat +
-\deriv{V_\theta}{\phi}\cos\theta\bphihat
-- V_\theta \cos\theta \left(\brhat \sin\theta + \bthetahat \cos\theta \right)
-\right)
-\\ \nonumber
-\Laplacian (V_\theta\bthetahat) &=
-\left(-\frac{2\cot\theta}{r^2}V_\theta - 2\deriv{V_\theta}{\theta}\right)\brhat +
-\left(\frac{2}{r}\deriv{V_\theta}{r} + \deriv{^2V_\theta}{r^2} +
-\frac{\cot\theta}{r^2} \deriv{V_\theta}{\theta} +
-\frac{1}{r^2}\deriv{^2V_\theta}{\theta^2}\right)\bthetahat
-\\ &+ \nonumber
-\frac{1}{r^2 \sin^2\theta}\left(
-\deriv{^2V_\theta}{\phi^2} - V_\theta \right)\bthetahat
-+ \frac{2 \cot\theta}{r^2 \sin\theta} \deriv{V_\theta}{\phi} \bphihat
-\end{align}
-$\bphihat$ component:
-\begin{align} \nonumber
-\Laplacian (V_\phi\bphihat) &= \nonumber
-\frac{1}{r^2}\deriv{}{r}\left(r^2 \deriv{V_\phi}{r}\right)\bphihat +
-\frac{1}{r^2\sin\theta}\deriv{}{\theta}\left(
-\sin\theta \deriv{V_\phi}{\theta}\bphihat \right)
-\\ &+ \nonumber
-\frac{1}{r^2 \sin^2\theta}\deriv{}{\phi}\left(
-\deriv{V_\phi}{\phi}\bphihat
-- V_\phi \left(\brhat \sin\theta + \bthetahat \cos\theta\right)
-\right)
-\\ 
-\Laplacian (V_\phi\bphihat) &=
-\frac{1}{r^2}\deriv{}{r}\left(r^2 \deriv{V_\phi}{r}\right)\bphihat +
-\frac{1}{r^2\sin\theta}\deriv{}{\theta}\left(
-\sin\theta \deriv{V_\phi}{\theta}\bphihat \right)
-\\ &+ \nonumber
-\frac{1}{r^2 \sin^2\theta}\deriv{}{\phi}\left(
-\deriv{V_\phi}{\phi}\bphihat
-- V_\phi \left(\brhat \sin\theta + \bthetahat \cos\theta\right)
-\right)
-\\ \nonumber
-\Laplacian (V_\phi\bphihat) &=
-\left(\frac{2}{r} \deriv{V_\phi}{r} + \deriv{^2V_\phi}{r^2}\right)\bphihat
-+
-\frac{1}{r^2\sin\theta}\left(
-\cos\theta \deriv{V_\phi}{\theta} +
-\sin\theta \deriv{^2V_\phi}{\theta^2}
-\right)\bphihat
-\\ &+ \nonumber
-\frac{1}{r^2 \sin^2\theta}\left(
-\deriv{^2V_\phi}{\phi^2}\bphihat
-- 2 \deriv{V_\phi}{\phi} \left(\brhat \sin\theta + \bthetahat \cos\theta\right)
-- V_\phi \bphihat
-\right)
-\end{align}
-In summary:
-\begin{align} \nonumber
-\Laplacian \bV &= \left(\Laplacian V_r - \frac{2V_r}{r^2}\right)\brhat
-+ \frac{2}{r^2}\deriv{V_r}{\theta} \bthetahat + \frac{2}{r^2 \sin\theta}\deriv{V_r}{\phi} \bphihat \\
-&-
-\frac{2}{r^2 \sin\theta} \deriv{\left(V_\theta \sin\theta \right)}{\theta}\brhat
-+ \left(\Laplacian V_\theta - \frac{V_\theta}{r^2 \sin^2\theta}\right) \bthetahat
-+ \frac{2 \cot\theta}{r^2 \sin\theta} \deriv{V_\theta}{\phi} \bphihat \\
-&- \nonumber
-\frac{2}{r^2 \sin\theta}\deriv{V_\phi}{\phi}\brhat -
-\frac{2 \cot\theta}{r^2 \sin\theta}\deriv{V_\phi}{\phi}\bthetahat
-+ \left(\Laplacian V_\phi - \frac{V_\phi}{r^2 \sin^2\theta}\right)\bphihat
-\end{align}
-
-Since $V_\phi = 0$ and $\deriv{}{\phi}(\cdot) = 0$, we get:
-\begin{align} \nonumber
-\Laplacian \bV &= \left(\Laplacian V_r - \frac{2V_r}{r^2} - \frac{2}{r^2 \sin\theta} \deriv{\left(V_\theta \sin\theta \right)}{\theta}\right)\brhat
-+
-\left(\Laplacian V_\theta - \frac{V_\theta}{r^2 \sin^2\theta} + \frac{2}{r^2}\deriv{V_r}{\theta}\right) \bthetahat
-\\
-\Laplacian \bV &= \left(
-\frac{1}{r^2}\deriv{}{r}\left( r^2 \deriv{V_r}{r} \right) + \frac{1}{r^2 \sin\theta} \deriv{}{\theta} \left( \sin\theta \cdot \deriv{V_r}{\theta}\right)
- - \frac{2V_r}{r^2} - \frac{2}{r^2 \sin\theta} \deriv{\left(V_\theta \sin\theta \right)}{\theta}\right)\brhat \\ \nonumber
-&+ \left(
-\frac{1}{r^2}\deriv{}{r}\left( r^2 \deriv{V_\theta}{r} \right) + \frac{1}{r^2 \sin\theta} \deriv{}{\theta} \left( \sin\theta \cdot \deriv{V_\theta}{\theta}\right)
- - \frac{V_\theta}{r^2 \sin^2\theta} + \frac{2}{r^2}\deriv{V_r}{\theta}\right) \bthetahat
-\end{align}
-
 \clearpage
@@
 
-\include{hebrewPart}
-
 \end{document}

### 2013-04-20 notes/CompPhys/build.sh

@@ -1,0 +1,15 @@
+#!/bin/bash
+rm -v *.aux *.dvi *.log *.pdf *.ps *.spl *.bbl *.out
+
+F=main
+
+latex $F.tex
+bibtex $F.aux
+latex $F.tex
+latex $F.tex
+dvips -o $F.ps $F.dvi
+ps2pdf -sOutputFile=CompPhys_BW.pdf \
+       -sColorConversionStrategy=Gray -dProcessColorModel=/DeviceGray $F.ps
+       
+#ps2pdf -sOutputFile=${F}.pdf $F.ps
+

### 2013-05-11 notes/thesis-latex-template/thesis.tex
Review after exam.

@@
 conservative formulation of the governing equations above. 
-The flux terms are defined using finite differences and linear interpolation of the disrete 
+The flux terms are defined using finite differences and linear interpolation of the discrete 
 variables (defined at the centroid of each cell), except for the advection flux which should not be 
@@
 Because the system is axisymmetric and the particle is a sphere, we employ
-spherical coordinates $(r,\theta,\phi)$.
+spherical coordinates $(r,\theta,\phi)$, as shown in Figure \ref{fig:SphericalCoordinateSystem}.
+
 The scalar gradient and the divergence can be written as:
@@
 
+\begin{figure}[p]
+    \begin{center}
+        \includegraphics[width=0.2\textwidth]
+            {figs/spherical_coordinate_system.eps}
+        \caption[Spherical coordinate system]{Spherical coordinate system is employed for
+        computational grid construction.}
+        \label{fig:SphericalCoordinateSystem}
+    \end{center}
+\end{figure}
+
 \subsection{Computational Grid}
@@
 \end{align}
-\begin{figure}[h]
+\begin{figure}[p]
     \begin{center}
-	\includegraphics[width=0.8\textwidth]{figs/grids.eps}
+	\includegraphics[width=0.5\textwidth]{figs/grids.eps}
         \caption[Computational grid]{The computational grid is defined using
@@
 is written as $\cO(\bx;\beta) = \bzero$.
-For small $\beta$, the solution to the nonlinear system can be expanded in a Taylor series in $\beta$:
+For small $\beta$, the solution to the nonlinear system can be expanded in an asymptotic series in $\beta$:
 \begin{equation}
@@
         (solid for $\cU > 0$, dashed for $\cU < 0$), 
-        and the numerical results are represented by markers 
+        and the numerical results are represented by symbols 
         (circles for $\cU > 0$, squares for $\cU < 0$). Note that linear and
@@
         \caption[Quadratic convergence of steady-state velocity]{
-        The discretization error between the numerical and analytical solutions for 
-        $\alpha = 0$, $\Du = 0.5$, $\bar\zeta = 6$ and $R_{max} = 100$. The markers represent
+        The discretization error $\hat{\cU}^h - \cU_1$ between the numerical results
+        and the linear asymptotic solutions for 
+        $\alpha = 0$, $\Du = 0.5$, $\bar\zeta = 6$ and $R_{max} = 100$. The symbols represent
         the discretization errors for various grid sizes, and the dotted lines correspond to linear
@@
         The analytic solution velocity is represented by solid lines, 
-        and the numerical results are represented by markers.
+        and the numerical results are represented by symbols.
         The top figure shows the full numerical solution 
@@
     \begin{center}
-    \includegraphics[width=.5\textwidth]{figs/LargeBetaRatio.eps}
+    \includegraphics[width=.45\textwidth]{figs/LargeBetaRatio.eps}
+    \includegraphics[width=.45\textwidth]{figs/LargeBetaRatio_p.eps}
         \caption[Rate of convergence estimation for $\cU$ at large $\beta$]
@@
         The rate of convergence $r(\beta)$ is estimated by 
-        $r(\beta) \triangleq \left(\cU^{4h}(\beta) - \cU^{2h}(\beta)\right)/\left(\cU^{2h}(\beta) - \cU^{h}(\beta)\right)$.
-        For small $\beta$, $r(\beta) \rightarrow 4$, showing 
+        $r(\beta) \triangleq \left(\cU^{4h}(\beta) - \cU^{2h}(\beta)\right)/\left(\cU^{2h}(\beta) - \cU^{h}(\beta)\right)$ (left). 
+        The order of convergence is estimated by $p(\beta) \triangleq \log_2 r(\beta)$ (right).
+        For small $\beta$, $p(\beta) \rightarrow 2$, showing 
         quadratic convergence for the linear regime. 
@@
 A numerical framework for a
-nonlinear electrokinetic transport system is described.
+nonlinear electrokinetic transport system is developed.
 The framework is used to construct numerical solvers 
@@
 using the numerical results, and were verified using an asymptotic expansion of the nonlinear system.
-The electrophoresis problem was solved on a high-resolution grid to validate the asymptotic 
+The electrophoresis problem was solved on a high-resolution grid to confirm the asymptotic 
 cubic correction of the steady-state velocity, as well as to provide insights into
@@
 and the velocity field is very close to being symmetric.
+Finally, we emphasize the importance of the analytical asymptotic derivation.
+This approach provides effective boundary conditions for the macroscale problem and thus eliminates the inherent physical scale disparity.
+This elimination enables the construction of the numerical scheme.
+Furthermore, the analytical asymptotic solutions for the weak field regime enable important mutual verification of the numerical results.
 

### 2013-05-18 notes/thesis-latex-template/thesis.tex
Thanks.
Add conclusion statement.

@@
 % beforeExam (to make the personal thanks invisible)
-\documentclass[MSc,beforeExam]{iitcsthesis}
+\documentclass[MSc]{iitcsthesis}
 
@@
 
-\personalThanksEnglish{Write thanks to professor and others}
+\personalThanksEnglish{
+\begin{center}
+{\Large Acknowledgment}
+\end{center}
+I would like to thank my adviser, Prof. Irad Yavneh for his outstanding guidance, helpful discussions and valuable advice. 
+I am deeply grateful to my family, and especially to my wife, Galit, for their love and support.
+}
+
 \financialThanksEnglish{The generous financial support of the Technion is gratefully acknowledged.}
@@
 
+In conclusion, the main contribution of this work is the development 
+of a numerical framework for solving nonlinear coupled PDE steady-state systems, 
+with application to electrokinetic problems such as ion-exchanger migration and 
+particle electrophoresis, and asymptotic analytical verification of the results.
+
 \section{Future Work}

### 2013-05-19 notes/thesis-latex-template/thesis.tex
Update "Summary of achievements" in the introduction chapter.

@@
 
-\section{Objective of this work}
-
-The goal of this work is to develop and implement a software toolbox 
-for the generation of iterative numerical solvers for nonlinear macroscale 
-electrokinetic problems, and to apply it to the study
-of systems that have no closed-form solutions, 
-such as ion-exchanger migration \cite{yariv2010migration} 
-and the electrophoresis problem \cite{schnitzer2012surface}.
-This solver can be used to gain insight into the chemical 
-and physical behavior in far more general regimes than 
-are currently well-understood, 
-and also to possibly lead to further analytical developments, 
-based on new scaling behavior
-discovered numerically. 
-We may also target interesting physical
-phenomena that have been observed experimentally.
-One such phenomenon is nonlinear electrokinetic vortex flow, 
-which is useful for microfluidic mixing applications 
-\cite{wang2004mix, ben2002vortex}.
+\section{Summary of achievements in this work}
+
+In this work, we develop and implement a novel software framework, that enables the generation of iterative numerical solvers for nonlinear macroscale electrokinetic problems, with the boundary layer replaced by nonlinear analytical boundary conditions.
+We apply this framework to the study of systems that have no closed-form solutions, such as ion-exchanger migration \cite{yariv2010migration} and the electrophoresis problem \cite{schnitzer2012surface}.
+The numerical results of the can be used to gain insight into the chemical and physical behavior in far more general regimes than are currently well-understood, and also to possibly lead to further analytical developments, based on new scaling behavior that is discovered numerically.
+We have also discovered interesting physical phenomena that may be observed experimentally.
+One such phenomenon is nonlinear electrokinetic vortex flow, which is useful for microfluidic mixing applications \cite{wang2004mix, ben2002vortex}.
+In addition, we develop and present an asymptotic derivation for the ion-exchanger migration problem up to the third order terms.
+This new analytical result is also used to verify the numerical framework and the obtained numerical results.
 
@@
 
-In conclusion, the main contribution of this work is the development 
-of a numerical framework for solving nonlinear coupled PDE steady-state systems, 
-with application to electrokinetic problems such as ion-exchanger migration and 
-particle electrophoresis, and asymptotic analytical verification of the results.
-
 \section{Future Work}

### 2013-05-20 notes/thesis-latex-template/thesis.tex
Irad review.

@@
 
-In this work, we develop and implement a novel software framework, that enables the generation of iterative numerical solvers for nonlinear macroscale electrokinetic problems, with the boundary layer replaced by nonlinear analytical boundary conditions.
-We apply this framework to the study of systems that have no closed-form solutions, such as ion-exchanger migration \cite{yariv2010migration} and the electrophoresis problem \cite{schnitzer2012surface}.
-The numerical results of the can be used to gain insight into the chemical and physical behavior in far more general regimes than are currently well-understood, and also to possibly lead to further analytical developments, based on new scaling behavior that is discovered numerically.
+In this work, we develop and implement a novel software framework, that enables the generation of iterative numerical solvers for nonlinear macroscale electrokinetic problems.
+A novel feature is the combination of a numerical framework with an analytical solution of the thin Debye layer, that is available from the literature and provides effective boundary conditions.
+Therefore, the Debye layer does not need to be resolved by the computational grid, saving a tremendous amount of numerical resources.
+
+We apply this framework to the study of systems that have no closed-form solutions, such as ion-exchanger migration \cite{yariv2010migration} and the electrophoresis problem \cite{schnitzer2012surface} for a spherical particle in an infinite domain.
+The numerical results can be used to gain insight into the chemical and physical behavior in far more general regimes than are currently well-understood, and also to possibly lead to further analytical developments, based on new scaling behavior that is discovered numerically.
 We have also discovered interesting physical phenomena that may be observed experimentally.
 One such phenomenon is nonlinear electrokinetic vortex flow, which is useful for microfluidic mixing applications \cite{wang2004mix, ben2002vortex}.
-In addition, we develop and present an asymptotic derivation for the ion-exchanger migration problem up to the third order terms.
-This new analytical result is also used to verify the numerical framework and the obtained numerical results.
+
+In addition, we develop and present an asymptotic derivation for the ion-exchanger migration problem up to third order terms.
+This new analytical result is also used to verify the numerical framework and the numerical results.
 
